### 2025-01-17 paper/Main_Article.tex
stage

\documentclass{nature3}
\usepackage{graphicx}
\usepackage{float}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{aas_macros_nature}
\usepackage{lineno}

\linespread{1.0}
\linenumbers % turn line numbering on or off

\newcommand{\starname}{TIC 141146667}

\newcommand{\farcm}{\mbox{\ensuremath{.\mkern-4mu^\prime}}}%    % fractional arcminute symbol: 0.'0
\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}%  % fractional arcsecond symbol: 0.''0

\newcommand{\kms}{\ensuremath{\rm km\,s^{-1}}}
\newcommand{\ms}{\ensuremath{\rm m\,s^{-1}}}

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

%%%%%%%%%%%%%%%%
% INSTITUTIONS %
%%%%%%%%%%%%%%%%
\newcommand{\carnegie}{Observatories of the Carnegie Institution for Science, Pasadena, CA 91101, USA}
%%%%%%%%%%%%%%%%

%%%%%%%%%%
% VALUES %
%%%%%%%%%%
% NOTE: might need to be ingested before submission 
\input{vals_manuscript}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{A Plasma Torus Around a Young Low-Mass Star}

\begin{document}

\author{Luke G. Bouma$^{1,2}$}

\maketitle

\scriptsize
\begin{affiliations}
\item \carnegie
\item Carnegie Fellow
\end{affiliations}
\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
\normalfont
Approximately one percent of red dwarfs younger than 100 million years
show structured, periodic optical light curves suggestive of transiting
clumps of opaque circumstellar material that corotate with the star
\cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.  The composition,
origin, and even the existence of this material are uncertain. The main
alternative hypothesis is that these stars are explained by complex
distributions of dark starspots or bright faculae distributed across
their surfaces \cite{Koen2021}.  Here, we present time-series
spectroscopy and photometry of a \stagemyr\ million year old complex
periodic variable (CPV), TIC 141146667. The spectra show coherent
sinusoidal Balmer emission at up to four times the star's equatorial
velocity, demonstrating the presence of extended clumps of circumstellar
plasma --- a plasma torus. These data rule out ``starspot-only'' and
``dust-only'' origin scenarios for CPVs, instead supporting either a
purely stellar origin for the phenomenon or extrinsic scenarios
involving long-lived disks or outgassing rocky bodies capable of
supplying sufficient gas.  Given that long-lived condensations of cool
($10^4$ K) plasma can persist in the hot ($10^6$ K) coronae of stars
with a wide range of masses
\cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
these data support the idea that such condensations can become optically
thick around the lowest-mass stars, although the exact source of 
opacity remains unclear.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Main}
\label{sec:main}

\subsection{Introduction}

Lorem ipsum whatever...

\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{figures/f1.png}
\caption[]{{\bf Figure 1 (Movie):  TIC 141146667 is a complex periodic
variable (CPV).} For the best experience, please view the online movie
available
\href{https://lgbouma.com/movies/movie_TIC1411_flux_phase.mp4}{here},
which spans a baseline of 5{,}784 cycles irregularly sampled over three
years.  The TESS light curve is phased to the \periodhr\ hour period in
groups of a few cycles per frame.  Raw data acquired with two minute
sampling are in gray; black is their average.  Similar to other members
of this class, the sharp photometric features persist for tens to
thousands of rotational cycles. }
\label{fig:lc}
\end{figure}

\subsection{Results}

\begin{figure}[t]
\centering
\includegraphics[width=0.99\textwidth]{figures/f2.png}
\caption[]{{\bf Figure 2 (Movie):}  
  Hydrogen emission from circumstellar plasma orbiting TIC 141146667.
  {(\bf TODO)}For the best experience, please view the online movie
  available
  \href{https://lgbouma.com/movies/TIC141146667_sixpanel.mp4}{here}.
  {\bf Panel a:} TESS light curve from UT 2024-02-05 to UT
  2024-02-26 folded on the \periodhr\ hour period.  Black points are
  averaged; gray are the raw data.
  {\bf Panel b:} Keck/HIRES H$\alpha$ spectra
  acquired on UT 2024-02-17.  The continuum is set at unity, and the
  darkest color is set at twice the continuum to accentuate emission
  outside the line core ($|v/v_{\rm eq}|>1$, for $v_{\rm eq}$=130\,\kms).
  While emission in the line core originates in the stellar
  chromosphere, the sinusoidal emission features are most readily
  described by a warped plasma torus.
  {\bf Panel c:} Individual epochs of Panel b, visible in the
  online movie.  The dotted line shows a time-averaged spectrum,
  $f_{\langle t \rangle}$.
  {\bf Panel d:} As in Panel a, but overplotting the
  median-normalized H$\alpha$ light curve at $|v/v_{\rm eq}|<1$.
  {\bf Panel e:} As in Panel b, after subtracting the time-averaged
  spectrum. In addition to circumstellar emission, the line core shows
  absorption during the plasma clump transits.  The asymmetric stretch
  is set to match the dynamic range of the data.
  {\bf Panel f:} Individual epochs of Panel e, visible in the online
  movie.}
\label{fig:spec}
\end{figure}

\subsection{Discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\begin{methods}

\renewcommand{\figurename}{Extended Data Figure}
\renewcommand{\tablename}{Extended Data Table}
\setcounter{table}{0}  
\setcounter{figure}{0}

\subsection{Observations}

\subsection{Data Reduction}

\subsection{Modeling the Emitting Clump}

%%%%%%%%%%%%%%%%%%%%%%%%%
% Supplementary Figures %
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
% Supplementary Tables %
%%%%%%%%%%%%%%%%%%%%%%%%

% TEMPLATE: IRAS041
%
\begin{table}
    \centering
    \begin{tabular}{lcr}
    \hline 
    \hline
    Parameter & Host & Source \\
    \hline 
    \multicolumn{3}{c}{Identifiers} \\
    \hline
    TIC & 141146667 & TESS \\
    Gaia & todo & Gaia\ DR3 \\
    %2MASS & J04154278+2909597 & J04154269+2909558 & 2MASS \\
    %ALLWISE & J041542.77+290959.5 & ... & ALLWISE\\
    \hline
    \multicolumn{3}{c}{Astrometry} \\ 
    \hline
    $\alpha$ & todo & Gaia\ DR3 \\
    $\delta$ & todo & Gaia\ DR3 \\
    $\mu_{\alpha}$ (mas yr$^{-1}$ ) & todo & Gaia\ DR3 \\
    $\mu_{\delta}$ (mas yr$^{-1}$ ) & todo & Gaia\ DR3 \\
    $\pi$ (mas) & todo & Gaia\ DR3 \\
    \hline
    \multicolumn{3}{c}{Photometry} \\
    \hline
    $TESS$ (mag) & todo & TESS\ \\
    $G$ (mag) & todo & Gaia\ DR3 \\
    $G_{\rm BP}$ (mag) & todo & Gaia\ DR3\\
    $G_{\rm RP}$ (mag) & todo & Gaia\ DR3\\
    $J$ (mag) & todo & 2MASS\\
    $H$ (mag) & todo & 2MASS\\
    $K_s$ (mag) & todo & 2MASS\\
    $W1$ (mag) & todo & ALLWISE \\
    $W2$ (mag) & todo & ALLWISE \\
    $W3$ (mag) & todo & ALLWISE \\
    $W4$ (mag) & todo & ALLWISE \\
    \hline
    \multicolumn{3}{c}{Kinematics and Position} \\
    \hline
    $RV_{Bary}$ (km s$^{-1}$ ) & $13.35 \pm 3.39$ & Gaia\ DR3 \\
    $U$ (km s$^{-1}$ ) & & \\
    $V$ (km s$^{-1}$ ) & & \\
    $W$ (km s$^{-1}$ ) & & \\
    $X$ (pc)  & & \\
    $Y$ (pc)  & & \\
    $Z$ (pc) & & \\
    \hline
    \multicolumn{3}{c}{Physical Properties} \\
    \hline
    $P_{rot}$ (hours) & $3.930 \pm 0.XXX$ & This work \\ 
    $v \sin i_\star$(km s$^{-1}$) & todo & This work\\
    $i_\star$($^\circ$) & todo & This work \\
    $F_{bol}$ (erg cm$^{-2}$ s$^{-1}$ ) & todo & This work\\
    $T_{eff}$ (K) & todo & This work\\
    $A_V$ (mag) & todo & This work \\
    $R_\star$ ($R_{\odot}$) & todo & This work\\
    $L_\star$ ($L_{\odot}$)  & todo & This work\\
    $M_\star$ ($M_{\odot}$)  & todo & This work\\
    Age (Myr) & todo &  This work \\
    \hline
    \end{tabular}
    \caption{Properties of \starname.}
    \label{tab:stellarParameters}
\end{table}

\end{methods}

\bibliography{cpvbib.bib} % common bib file
\bibliographystyle{naturemagfixed}

\begin{addendum}

\item[Acknowledgments] The author thanks X, Y, Z.
  L.G.B. was suported by...
	Acknowledge TESS...

%TC:ignore
%% Author Contribution
\item[Author Contributions] ...
%TC:endignore

\item[Data Availability] ...

\item[Competing Interests] The authors declare that they have no competing
financial interests.

\item[Correspondence] Correspondence and requests for materials should be
addressed to ...

\item[Code availability] We provide access to a GitHub repository including all
code created for the analysis of this project that is not already publicly
available.

\end{addendum}

\end{document}

### 2025-01-17 paper/collect_figs.sh

@@ -1,0 +1,18 @@
+r="/Users/luke/Dropbox/proj/cpv/results"
+
+##########################################
+# figure1: TIC 141146667 is a complex periodic variable.
+# still: c1265-1268, s48, 2022-02-16 to 2022-02-17
+cp $r/movie_phase_timegroups/TIC_141146667/TIC_141146667_0081_2min_phase_timegroups.png figures/f1.png
+
+# Animated supporting: Movie of S41, S48, S75 TESS photometry, cycle-grouped
+cp $r/movie_phase_timegroups/TIC_141146667/movie_TIC1411_flux_phase_bow.mov movies/m1.mov
+
+##########################################
+# figure2: Hydrogen emission from circumstellar plasma orbiting TIC 141146667.
+# -still: index 0012.  t=3.1hr
+cp $r/movie_sixpanel_specriver/TIC_141146667_science/specriver_141146667_Hα_0012_2min_remove25pct_normbyveq_showlinecoresum.png figures/f2.png
+
+# Animated supporting: Movie of spectral timeseries
+cp $r/movie_sixpanel_specriver/TIC_141146667_science/TIC141146667_sixpanel.mov movies/m2.mov
+

### 2025-01-17 paper/compile.sh

@@ -1,0 +1,7 @@
+./clean.sh
+pdflatex Main_Article.tex
+bibtex Main_Article
+pdflatex Main_Article.tex
+pdflatex Main_Article.tex
+
+rm *.out *.aux *.blg *.log

### 2025-01-17 paper/Main_Article.tex
update

@@
 \normalfont
+% v1: removed a sentence for wordcount.  v0 is under abstract_title.txt
 Approximately one percent of red dwarfs younger than 100 million years
-show structured, periodic optical light curves suggestive of transiting
-clumps of opaque circumstellar material that corotate with the star
-\cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.  The composition,
-origin, and even the existence of this material are uncertain. The main
-alternative hypothesis is that these stars are explained by complex
-distributions of dark starspots or bright faculae distributed across
-their surfaces \cite{Koen2021}.  Here, we present time-series
-spectroscopy and photometry of a \stagemyr\ million year old complex
-periodic variable (CPV), TIC 141146667. The spectra show coherent
-sinusoidal Balmer emission at up to four times the star's equatorial
-velocity, demonstrating the presence of extended clumps of circumstellar
-plasma --- a plasma torus. These data rule out ``starspot-only'' and
-``dust-only'' origin scenarios for CPVs, instead supporting either a
-purely stellar origin for the phenomenon or extrinsic scenarios
-involving long-lived disks or outgassing rocky bodies capable of
-supplying sufficient gas.  Given that long-lived condensations of cool
-($10^4$ K) plasma can persist in the hot ($10^6$ K) coronae of stars
-with a wide range of masses
+show structured, periodic optical light curves suggestive of
+transiting clumps of opaque circumstellar material that corotate
+with the star \cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.
+The composition, origin, and even the existence of this material are
+uncertain. The main alternative hypothesis is that these stars are
+explained by complex distributions of dark starspots or bright
+faculae distributed across their surfaces \cite{Koen2021}.  Here, we
+present time-series spectroscopy and photometry of a \stagemyr\
+million year old complex periodic variable (CPV), TIC~141146667. The
+spectra show coherent sinusoidal Balmer emission at up to four times
+the star's equatorial velocity, demonstrating the presence of
+extended clumps of circumstellar plasma --- a plasma torus.  Given
+that long-lived condensations of cool ($10^4$ K) plasma can persist
+in the hot ($10^6$ K) coronae of stars with a wide range of masses
 \cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
-these data support the idea that such condensations can become optically
-thick around the lowest-mass stars, although the exact source of 
-opacity remains unclear.
+these data support the idea that such condensations can become
+optically thick around the lowest-mass stars, although the exact
+source of opacity remains unclear.
 \end{abstract}
@@
 
+% Main text – up to 3,000 words, excluding abstract, Methods,
+% references and figure legends.
+
 \section{Main}
@@
 
-\subsection{Introduction}
+%\subsection{Introduction}
+M dwarfs, stars with masses below about half that of the Sun, are the
+only type of star to offer near-term prospects for detecting the
+atmospheres of rocky exoplanets with water on their surfaces (CITE).
+Investment with JWST has proceeded accordingly (CITE CITE).  It is
+therefore important to consider how the evolution of an M dwarf might
+impact the evolution of its planets.  Previous work has established
+that most M dwarfs host close-in planets (CITE), and that these
+planets are often subject to long circumstellar disk lifetimes (CITE),
+to large doses of UV radiation (CITE), and to a high incidence of
+flares and coronal mass ejections (CITE).  However, despite excellent
+work in these areas, the properties of the circumstellar plasma
+and magnetospheric environments to which young, close-in exoplanets
+are subject remain largely unexplored.
 
-Lorem ipsum whatever...
+One glaring example of our current ignorance is the complex periodic
+variables (CPVs).  Figure~\ref{fig:lc} highlights the main object of
+interest in this article, but over one hundred analogous objects have
+now been discovered by K2 and TESS (CITE, CITE, CITE, CITE).  These CPVs are
+defined by their highly structured and periodic optical light curves, 
+and most are M dwarfs with rotation periods shorter than two days.
+Within current sensitivity limits, none have primordial disks (CITE).
+However, $\approx$3\% of stars a few million years old show this
+behavior (CITE), and the observed fraction decreases to $\approx$0.3\%
+by $\approx$150\,Myr (CITE).
 
-\begin{figure}[t]
+The two leading hypotheses to explain the CPVs are either that we are
+in the shadow of transiting clumps of circumstellar material that
+corotate with the star (CITE, CITE, CITE), or that these stars
+represent an extreme in naturally-occurring distributions of starspots
+or faculae for young M dwarfs \cite{Koen2021}.  Currently, the main
+argument against a starspot-only explanation invokes the timescales
+and amplitudes of the sharpest photometric features (CITE).  However,
+there has yet to be any direct independent evidence for the presence of
+circumstellar material in any of these objects.  Since transiting
+circumstellar clumps would geometrically imply an occcurrence rate a
+few to ten times the observed rate (CITE), this phenomenon has the
+potential to affect 10-30\% of M dwarfs during their early lives.
+
+The dearth of evidence for circumstellar material around CPVs is
+surprising given that separate studies of young BAFGKM stars have, for
+decades, reported that stellar coronae contain both hot ($10^6$ K) and
+cool ($10^4$ K) plasma. In particular, time-series spectroscopy has
+shown periodic high-velocity absorption and emission in Balmer lines
+such as H$\alpha$, implying long-lived, corotating clumps of cool
+plasma (CITE, CITE, CITE).  Such clumps are forced into corotation by
+the magnetic field, and the geometry of where the plasma can
+accumulate is thought to be dictated by the magnetic field's topology.
+For instance, a tilted dipole field tends to yield an accumulation
+surface of a warped torus \cite{Townsend2005}, whereas in the limit of
+a single strong discrete field line, accumulation occurs along a fixed
+point \cite{Waugh2022}.  However, none of these stars have shown any
+photometric anomalies (CITE), leaving open the issue of whether these
+two separate areas of study have any direct connection.  Nonetheless,
+CPVs do respond to sudden magnetic field changes: there are many
+documented cases of otherwise long-lived eclipse features disappearing
+immediately following stellar flares (CITE, CITE).
+
+In this study, we present the first observations of corotating clumps
+of cool plasma around a CPV.  We identified TIC~141146667 in previous
+work \cite{Bouma2024} by searching the TESS two-minute data for stars
+showing periodic variability with at least three sharp dips.  We
+selected it from the resulting fifty high-quality CPVs for follow-up
+observations because it was the brightest source for which a full
+cycle could be observed in a half-night.  We observed it for five
+hours on UT 2024-02-17 using the High Resolution Echelle Spectrometer
+(HIRES; \cite{vogt_hires_1994}) on the Keck I 10m telescope, roughly
+contemporaneous with TESS, which observed the star from UT 2024-02-05
+to UT 2024-02-26 with a duty cycle of XX\%.  In detail, TESS was
+finishing a data downlink during the HIRES observations, and
+photometric data collection resumed three cycle periods (12 hours)
+after the spectra were acquired.  
+Extended Data Figure~\ref{fig:fulllc} shows the detailed photometric
+behavior of the star before and after the exact epoch of observation;
+the star remained sufficiently stable to not affect any of the
+interpretation that follows.
+
+\begin{figure}[!t]
   \centering
   \includegraphics[width=0.7\textwidth]{figures/f1.png}
-\caption[]{{\bf Figure 1 (Movie):  TIC 141146667 is a complex periodic
+  \caption[]{{\bf Figure 1 (Movie):  TIC~141146667 is a complex periodic
   variable (CPV).} For the best experience, please view the online movie
@@
   years.  The TESS light curve is phased to the \periodhr\ hour period in
-groups of a few cycles per frame.  Raw data acquired with two minute
+  groups of a few cycles per frame.  This is the period both of
+  stellar rotation, and (we hypothesize) of corotating clumps of
+  circumstellar material.  Raw data acquired with two minute
   sampling are in gray; black is their average.  Similar to other members
@@
 
-\begin{figure}[t]
+\begin{figure}[!tp]
   \centering
@@
   {\bf Panel b:} Keck/HIRES H$\alpha$ spectra
-  acquired on UT 2024-02-17.  The continuum is set at unity, and the
+  acquired on UT 2024-02-17.  The continuum is set to unity, and the
   darkest color is set at twice the continuum to accentuate emission
@@
 
+Figure~\ref{fig:spec} shows the available photometry and spectroscopy from
+February 2024.
+While the star's photometric shape changed from February 2022,
+its behavior remained complex:
+the average photometric signal shows a smooth brightening over 45\% of
+the period, followed by a complex eclipse-like feature spanning 55\%
+of the period.
+This photometric eclipse shows two to three local minima, 
+and one to two local maxima at times near the spectroscopic
+observation.
+
+The novelty is the spectroscopy.  Emission from material well beyond
+the star's equatorial velocity ($v_{\rm eq}$=130\,\kms) is visible by
+eye in the raw spectrogram.
+The emission is complex...
+%TODO: what are the features you need to quantify / quote?
+
+slightly less than half the period,
+
+While the two are not exactly simultaneous,
+
 \subsection{Discussion}
+
+These data rule out ``starspot-only'' and ``dust-only''
+origin scenarios for CPVs, instead supporting either a purely stellar
+origin for the phenomenon or extrinsic scenarios involving long-lived
+disks or outgassing rocky bodies capable of supplying sufficient gas.
 
@@
 \subsection{Observations}
+
+\begin{figure}[!b]
+  \centering
+  \includegraphics[width=0.99\textwidth]{figures/sf1.pdf}
+  \caption{Detailed photometric evolution of TIC 141146667 near the
+  epoch of spectroscopic observation (green). 
+  {\bf Panel a}: Subset of TESS SAP\_FLUX acquired near time of
+  Keck/HIRES observation.
+  TESS downlinked data to the Deep Space Network from BTJD XXX to
+  YYY, and was affected by scattered light from the Earth from BTJD
+  3359.4 to 3360.15.
+  %TODO: VERIFY!  Was it scattered light?  Or a legit flare?
+  {\bf Panels b,c}: Folded light curve before and after spectroscopy.
+  {\bf Panel d}: Zoom-in of Panel a, showing decreasing photometric
+  scatter in the over three days (18 cycles).
+  }
+  \label{fig:fulllc}
+\end{figure}
+
+{\bf TESS:}
+
+{\bf Keck/HIRES:}
+We observed using the standard setup and reduction techniques of the
+California Planet Survey \cite{Howard2010}.
+Winds of 30 mph contributed to
+1\farcs2$\pm$0\farcs2 seeing over the spectroscopic observations.
 

### 2025-01-17 paper/collect_figs.sh

@@ -16,3 +16,8 @@ cp $r/movie_sixpanel_specriver/TIC_141146667_science/specriver_141146667_Hα_001
 # Animated supporting: Movie of spectral timeseries
 cp $r/movie_sixpanel_specriver/TIC_141146667_science/TIC141146667_sixpanel.mov movies/m2.mov
 
+##########################################
+# supplementary
+
+# sf1: The data are nearly but not exactly simultaneous
+cp $r/tic1411_obsepoch/tic1411_obsepoch.pdf figures/sf1.pdf

### 2025-01-18 paper/ms.tex
rename + new words

--- 2025-01-17 paper/Main_Article.tex
@@
 
-The two leading hypotheses to explain the CPVs are either that we are
-in the shadow of transiting clumps of circumstellar material that
-corotate with the star (CITE, CITE, CITE), or that these stars
-represent an extreme in naturally-occurring distributions of starspots
-or faculae for young M dwarfs \cite{Koen2021}.  Currently, the main
-argument against a starspot-only explanation invokes the timescales
-and amplitudes of the sharpest photometric features (CITE).  However,
-there has yet to be any direct independent evidence for the presence of
-circumstellar material in any of these objects.  Since transiting
-circumstellar clumps would geometrically imply an occcurrence rate a
-few to ten times the observed rate (CITE), this phenomenon has the
-potential to affect 10-30\% of M dwarfs during their early lives.
-
-The dearth of evidence for circumstellar material around CPVs is
-surprising given that separate studies of young BAFGKM stars have, for
-decades, reported that stellar coronae contain both hot ($10^6$ K) and
-cool ($10^4$ K) plasma. In particular, time-series spectroscopy has
-shown periodic high-velocity absorption and emission in Balmer lines
-such as H$\alpha$, implying long-lived, corotating clumps of cool
-plasma (CITE, CITE, CITE).  Such clumps are forced into corotation by
-the magnetic field, and the geometry of where the plasma can
-accumulate is thought to be dictated by the magnetic field's topology.
-For instance, a tilted dipole field tends to yield an accumulation
-surface of a warped torus \cite{Townsend2005}, whereas in the limit of
-a single strong discrete field line, accumulation occurs along a fixed
-point \cite{Waugh2022}.  However, none of these stars have shown any
-photometric anomalies (CITE), leaving open the issue of whether these
-two separate areas of study have any direct connection.  Nonetheless,
-CPVs do respond to sudden magnetic field changes: there are many
-documented cases of otherwise long-lived eclipse features disappearing
-immediately following stellar flares (CITE, CITE).
-
-In this study, we present the first observations of corotating clumps
-of cool plasma around a CPV.  We identified TIC~141146667 in previous
-work \cite{Bouma2024} by searching the TESS two-minute data for stars
-showing periodic variability with at least three sharp dips.  We
-selected it from the resulting fifty high-quality CPVs for follow-up
-observations because it was the brightest source for which a full
-cycle could be observed in a half-night.  We observed it for five
-hours on UT 2024-02-17 using the High Resolution Echelle Spectrometer
-(HIRES; \cite{vogt_hires_1994}) on the Keck I 10m telescope, roughly
-contemporaneous with TESS, which observed the star from UT 2024-02-05
-to UT 2024-02-26 with a duty cycle of XX\%.  In detail, TESS was
-finishing a data downlink during the HIRES observations, and
-photometric data collection resumed three cycle periods (12 hours)
-after the spectra were acquired.  
-Extended Data Figure~\ref{fig:fulllc} shows the detailed photometric
-behavior of the star before and after the exact epoch of observation;
-the star remained sufficiently stable to not affect any of the
-interpretation that follows.
+The two leading hypotheses to explain the CPVs are either that
+transiting clumps of circumstellar material corotate with the star
+(CITE, CITE, CITE), or that these stars represent an extreme in
+naturally-occurring distributions of starspots or faculae for young M
+dwarfs \cite{Koen2021}.  Currently, the main argument against a
+starspot-only explanation invokes the timescales and amplitudes of the
+sharpest photometric features (CITE).  However, no independent
+evidence has yet been presented for the presence of circumstellar
+material in these objects.  Since transiting circumstellar
+clumps would geometrically imply an occcurrence rate a few to ten
+times the observed rate (CITE), the question of whether it is there
+could potentially teach us about 10-30\% of M dwarfs during their
+early lives.
 
@@
 \end{figure}
+
+The dearth of evidence for circumstellar material around CPVs is
+surprising given that separate studies of young BAFGKM stars have, for
+decades, reported that stellar coronae contain both hot ($10^6$ K) and
+cool ($10^4$ K) plasma. In particular, time-series spectroscopy has
+shown periodic high-velocity absorption and emission in Balmer lines
+such as H$\alpha$, caused by long-lived, corotating clumps of cool
+plasma (CITE, CITE, CITE).  Such clumps are forced into corotation by
+the magnetic field, and the exact geometry of where the plasma can
+accumulate is dictated by the magnetic field's topology.
+For instance, a tilted dipole field tends to yield an accumulation
+surface of a warped torus \cite{Townsend2005}, whereas in the limit of
+a single strong discrete field line, accumulation occurs along a fixed
+point \cite{Waugh2022}.  However, none of these stars have shown any
+photometric anomalies (CITE), leaving open the issue of whether these
+two separate areas of study have any direct connection.  Nonetheless,
+CPVs do respond to sudden magnetic field changes: there are many
+documented cases of otherwise long-lived eclipse features disappearing
+immediately following stellar flares (CITE, CITE).
+
+In this study, we present the first observations of corotating clumps
+of cool plasma around a CPV.  We identified TIC~141146667 in previous
+work \cite{Bouma2024} by searching the TESS two-minute data for stars
+showing periodic variability with at least three sharp dips per cycle.  We
+selected it from the resulting fifty high-quality CPVs for
+spectroscopic observations because it was the brightest source for
+which a full cycle could be observed in a half-night.  We observed it
+for five hours on UT 2024-02-17 using the High Resolution Echelle
+Spectrometer (HIRES; \cite{vogt_hires_1994}) on the Keck I 10m
+telescope, roughly contemporaneous with TESS, which observed the star
+from UT 2024-02-05 to UT 2024-02-26 with a duty cycle of XX\%.  In
+detail, TESS was finishing a data downlink during the HIRES
+observations, and photometric data collection resumed three rotation cycles
+(12 hours) after the spectra were acquired.  Extended Data
+Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
+star before and after the exact epoch of observation; the star
+remained sufficiently stable to not affect any of the interpretation
+that follows.
 
@@
 
-Figure~\ref{fig:spec} shows the available photometry and spectroscopy from
-February 2024.
-While the star's photometric shape changed from February 2022,
-its behavior remained complex:
-the average photometric signal shows a smooth brightening over 45\% of
+% photometry
+Figure~\ref{fig:spec} shows the data from February 2024.  As expected
+based on other CPVs \cite{Bouma2024}, the photometric shape of
+TIC~141146667 evolved over the years following the 2022 discovery
+data, while nonetheless remaining complex.  In February 2024, the
+average photometric signal showed a gradual brightening over 45\% of
 the period, followed by a complex eclipse-like feature spanning 55\%
-of the period.
-This photometric eclipse shows two to three local minima, 
-and one to two local maxima at times near the spectroscopic
-observation.
+of the period.  This eclipse-like feature shows two to three
+local photometric minima, and one to two local maxima.
 
-The novelty is the spectroscopy.  Emission from material well beyond
-the star's equatorial velocity ($v_{\rm eq}$=130\,\kms) is visible by
-eye in the raw spectrogram.
-The emission is complex...
-%TODO: what are the features you need to quantify / quote?
+% ** keck/hires: emission beyond v/veq>1 (2-3 paragraphs)
+The spectroscopy shows emission well outside the star's
+equatorial velocity ($v_{\rm eq}$=130\,\kms).  There are at least two
+distinct emission components, each spaced half a cycle apart in phase.  The
+first has clearer sinusoidal behaviour and is double-peaked, with
+semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.  The
+flux excesses from these two peaks are correlated with one another,
+with amplitudes varying from 100\% of the continuum flux early in the
+observation sequence to 30\% by its end.  The component 180$^\circ$
+opposite in phase is only detected from $\phi$=0.2-1.0, and 
+from $\phi$=0.2-0.5, this latter component appears connected to the
+star in velocity space.  While its peak semi-amplitude of
+$K_1$=3.9\,$v_{\rm eq}$ is achieved at both $\phi$=0.25 and 0.75, its
+amplitude decreases from a 60\% excess beyond the continuum to a 10\%
+excess.   The sinusoidal period in all cases where emission is seen is
+consistent with the photometric \periodhr\ hour period.  As we shall
+discuss below, the only plausible explanation for the behavior at
+$|\Delta v / v_{\rm eq}|>1$ is that circumstellar clumps of hydrogen
+are corotating with the star.  These clumps transit in front of the
+star when passing from negative to positive velocity.
 
-slightly less than half the period,
-
-While the two are not exactly simultaneous,
+% * keck/hires: absorption within v/veq<1
+% * keck/hires: emission within v/veq<1
+Within the stellar H$\alpha$ line core, at $|\Delta v / v_{\rm
+eq}|<1$, the behavior is more complex.  Generally, one would
+expect this region to be generated by the net superposition of bright
+and dark regions on the stellar surface, and then modulated by any
+occulting material capable of absorbing or emitting in H$\alpha$.  In
+Figure~\ref{fig:spec}e, the behavior from $\phi$=0.4-1.2, is most easily
+interpreted: from $\phi$=0.4-0.9, a hot region first gradually crosses
+the stellar line profile, following from $\phi$=0.7-1.2 by the transit
+of a cool region.  The phases $\phi$$<$0.4 seem to be a mix of similar
+events, though the time sampling is sufficiently coarse that the
+interpretation is less clear.
+A final exercise to quantify the behavior in the line core is
+shown in Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes
+the summed flux in the at $|\Delta v / v_{\rm eq}|<1$.
+Changes in the line core flux are usually correlated with the
+broadband variability, except at $\phi$=0.5, during the transit of the
+higher-velocity clump and the occultation of the lower-velocity clump.
 
@@
 
-These data rule out ``starspot-only'' and ``dust-only''
-origin scenarios for CPVs, instead supporting either a purely stellar
-origin for the phenomenon or extrinsic scenarios involving long-lived
-disks or outgassing rocky bodies capable of supplying sufficient gas.
+The sinusoidal emission features require clumps of partially-ionized
+hydrogen to be corotating with the star.
+The velocity semi-amplitude of the sinusoids directly gives the
+distance of these clumps from the stellar surface: 2.1-2.7\,$R_\star$
+for one clump, and 3.9\,$R_\star$ for the other.
+Their motion, rather than being Keplerian, can only be explained by
+plasma being dragged along with the rotating stellar magnetic field.
+
+The new data rule out two plausible origin scenarios for CPVs.
+The ``starspot-only'' scenario \cite{Koen2021} has no means of
+explaining this type of spectroscopic emission.
+Similarly, a ``dust-only'' scenario in which the circumstellar
+material would have a pure dust composition is also ruled out:
+to explain the H$\alpha$ emission, the circumstellar clumps need to be
+made of either a pure plasma, or a dusty plasma.
+A priori, there are three plausible sources of such material:
+the star, an old and undetected disk, or outgassing rocky bodies.
+
+% * mass estimate
+The density and mass of the material...
+
+% TODO TODO: the rest!
+* role of B: comparison to, and need for, RMHD models
+  * massive B star / jupiter cnxn
+
+* more wavelengths:
+    Radio detection.   Relevance for B measurement.
+    UV?  xray?
+    need for jwst
+
+* microphysics: the (probable) need for dust
+    W1,W2,W3 no dust evidence.
+    W4 detection questionable based on WISE images.
 

### 2025-01-18 paper/compile.sh

@@ -1,7 +1,8 @@
-./clean.sh
-pdflatex Main_Article.tex
-bibtex Main_Article
-pdflatex Main_Article.tex
-pdflatex Main_Article.tex
+rm *.out *.aux *.blg *.log
+
+pdflatex ms.tex
+bibtex ms
+pdflatex ms.tex
+pdflatex ms.tex
 
 rm *.out *.aux *.blg *.log

### 2025-01-18 paper/ms.tex
update

@@
 excess.   The sinusoidal period in all cases where emission is seen is
-consistent with the photometric \periodhr\ hour period.  As we shall
-discuss below, the only plausible explanation for the behavior at
-$|\Delta v / v_{\rm eq}|>1$ is that circumstellar clumps of hydrogen
-are corotating with the star.  These clumps transit in front of the
-star when passing from negative to positive velocity.
+consistent with the photometric \periodhr\ hour period.
+
+The sinusoidal emission features require circumstellar clumps of
+partially-ionized hydrogen to be corotating with the star.  The
+velocity semi-amplitude of the sinusoids directly gives the distance
+of these clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
+closer clump, and 3.9\,$R_\star$ for the other.  This material's
+motion, rather than being Keplerian, can only be explained by plasma
+being dragged along with the rotating stellar magnetic field.  These
+clumps transit in front of the star when passing from negative to
+positive velocity.
 
@@
 % * keck/hires: emission within v/veq<1
-Within the stellar H$\alpha$ line core, at $|\Delta v / v_{\rm
-eq}|<1$, the behavior is more complex.  Generally, one would
-expect this region to be generated by the net superposition of bright
-and dark regions on the stellar surface, and then modulated by any
+The behavior within the stellar H$\alpha$ line core, at $|\Delta v /
+v_{\rm eq}|<1$, is more complex than outside it.  Generally, one would
+expect the emission in the line core to be generated near the stellar
+chromosphere, near the star's surface, and then modulated by any
 occulting material capable of absorbing or emitting in H$\alpha$.  In
-Figure~\ref{fig:spec}e, the behavior from $\phi$=0.4-1.2, is most easily
-interpreted: from $\phi$=0.4-0.9, a hot region first gradually crosses
-the stellar line profile, following from $\phi$=0.7-1.2 by the transit
-of a cool region.  The phases $\phi$$<$0.4 seem to be a mix of similar
-events, though the time sampling is sufficiently coarse that the
-interpretation is less clear.
-A final exercise to quantify the behavior in the line core is
-shown in Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes
-the summed flux in the at $|\Delta v / v_{\rm eq}|<1$.
-Changes in the line core flux are usually correlated with the
-broadband variability, except at $\phi$=0.5, during the transit of the
-higher-velocity clump and the occultation of the lower-velocity clump.
+Figure~\ref{fig:spec}e, the behavior from $\phi$=0.4-1.2 is most
+easy to interpret: from $\phi$=0.4-0.9, a hot region first gradually
+crosses the stellar line profile, followed from $\phi$=0.7-1.2 by the
+transit of a cool region.  The phases $\phi$$<$0.4 seem to be a mix of
+similar events, though the time sampling is sufficiently coarse that
+the interpretation is less clear.  A final exercise to quantify the
+behavior in the line core is shown in Figure~\ref{fig:spec}d, where
+$f_{\rm H\alpha\ core}$ denotes the summed flux in the at $|\Delta v /
+v_{\rm eq}|<1$.  Changes in the line core flux are usually correlated
+with the broadband variability, except at $\phi$=0.5, during the
+transit of the higher-velocity clump and the occultation of the
+lower-velocity clump.
 
@@
 
-The sinusoidal emission features require clumps of partially-ionized
-hydrogen to be corotating with the star.
-The velocity semi-amplitude of the sinusoids directly gives the
-distance of these clumps from the stellar surface: 2.1-2.7\,$R_\star$
-for one clump, and 3.9\,$R_\star$ for the other.
-Their motion, rather than being Keplerian, can only be explained by
-plasma being dragged along with the rotating stellar magnetic field.
+Magetically-active, rapidly rotating stars with a wide range of masses
+have been known to exhibit both sinusoidal emission features (CITE,
+CITE, CITE, CITE) as well as sharp transient absorption features in
+their line cores (CITE, CITE, CITE, CITE) similar to those in
+Figure~\ref{fig:spec}.
+None of the low mass stars showing such spectroscopic features have
+previously shown abnormal light curves (CITE).
+The preferred interpretation for such spectroscopic variability comes
+from a loose analogy to quiescent solar prominences and filaments,
+which are cool condensations of plasma in the solar corona that last
+days to weeks (CITE).
+This plasma is called a prominence when viewed in emission against the
+dark backdrop of space, and a filament when viewed in absorption
+against the solar disk.
+In our Sun's magnetosphere, these condensations fall back to
+the solar surface because gravity is stronger than any magnetic or
+centrifugal force capable of sustaining them.
+However for stars with magnetospheric radii $R_{\rm m}$ that exceed the
+corotation radii $R_{\rm c}$, the effective potential experienced by
+the plasma have local minima outside the $R_{\rm c}$, enabling the
+material to be sustained for much longer timescales (see CITE, CITE).
 
-The new data rule out two plausible origin scenarios for CPVs.
-The ``starspot-only'' scenario \cite{Koen2021} has no means of
-explaining this type of spectroscopic emission.
-Similarly, a ``dust-only'' scenario in which the circumstellar
-material would have a pure dust composition is also ruled out:
-to explain the H$\alpha$ emission, the circumstellar clumps need to be
-made of either a pure plasma, or a dusty plasma.
-A priori, there are three plausible sources of such material:
+Our Keck/HIRES observations were the first time a CPV was observed
+with sufficient sensitivity to test for the presence of circumstellar
+plasma clumps, and they showed for TIC~141146667 that they exist and
+are corotating with the star.  
+Characteristic densities and masses of these clumps are $n \sim
+10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see~\ref{subsec:model}),
+a similar density to solar prominences, but ten to one hundred times
+more massive.
+This observation rules out a ``starspot-only'' origin scenario
+for CPVs, \cite{Koen2021} since such scenarios have no means of
+explaining spectroscopic emission beyond the stellar disk.  Similarly,
+scenarios in which the circumstellar material is made only of dust are
+also ruled out.  Although dust may be present, to explain the
+H$\alpha$ emission, the circumstellar clumps must include plasma with
+a significant population of hydrogen atoms in the $n$=3 excited state.
+While the plasma is undoubtedly sculpted by the star's magnetic field,
+there are three a priori plausible origin locations for the material:
 the star, an old and undetected disk, or outgassing rocky bodies.
 
-% * mass estimate
-The density and mass of the material...
+The most intriguing potential known analogs to CPVs 
+are the $\sigma$~Ori~E variables, a rare subset of B stars that almost
+all have tilted-dipole magnetic fields (CITE) which can trap outflowing
+stellar winds into warped plasma tori (CITE). 
+These tori tend to have dense antipodal accumulations of plasma, and
+the transits of these accumulations can produce broadband photometric
+variability through a combination of bound-free scattering (CITE) and
+Thomson scattering (CITE).  For $\sigma$~Ori~E
+and most of its analogs, the result is light curves that almost all
+appear ``simple'', resembling those of eclipsing binaries (CITE,
+CITE).  The two known exceptions, HD~37776 and HD~64740, show complex
+light curves resembling CPVs (Mikulasek2020, CITEBouma2024), and have
+spectropolarimetric magnetic field maps indicating strong
+contributions from higher-order magnetic moments (CITE CITE).  There are two
+implications: firstly, the complexity of CPVs may be a direct
+consequence of magnetic fields with highly multipolar contributions.
+Secondly, CPVs could be a source of astrophysical false positives in
+photometric searches for eclipsing binaries and transiting exoplanets
+around young pre-main-sequence M dwarfs (e.g.  CITE).
 
-% TODO TODO: the rest!
-* role of B: comparison to, and need for, RMHD models
-  * massive B star / jupiter cnxn
+% Need paragraph(s) on the future!
+Pressing issues for future work on CPVs include determining the
+composition and origin of the circumstellar material, understanding
+the exact role of the stellar magnetic field, and exploring the
+implied space weather experienced by the close-in rocky exoplanets
+that, statistically, are likely to be nearby (CITE).
 
-* more wavelengths:
-    Radio detection.   Relevance for B measurement.
-    UV?  xray?
-    need for jwst
+The composition -- either purely plasma, or else a dusty plasma -- can
+be clarified by time-series optical and infrared spectrophotometry.
+While observations of CPVs in the optical have previously suggested
+the presence of dust (CITE), plasma clumps transiting over starspots
+can also produce chromatic features (CITERackham).  The composition
+and size distribution of any dust that is present could be most easily
+resolved by measuring the extinction curve for one or more CPVs from
+$\approx$1-10\,$\mu$m.  A composition similar to debris from rocky
+bodies seen around white dwarfs (CITE Reach+09) would be indicative of
+a rocky-body origin.  A composition closer to the ISM would be
+indicative of condensed dust in an M dwarf wind, similar to that
+formed in the environments of more evolved stars (CITE Marigo2008).
 
-* microphysics: the (probable) need for dust
-    W1,W2,W3 no dust evidence.
-    W4 detection questionable based on WISE images.
+The role of the star's magnetic field could be better understood
+through new observations, and new theory.
+From the theoretical perspective, there is an urgent need for
+rigid-field magnetohydrodynamic (MHD) modeling to go beyond previous work
+(CITE CITE) by exploring the effects of non-dipolar field
+contributions.
+Fully time-dynamic MHD (e.g. CITE DaleyYates) will offer the
+capability of understanding the connection between the plasma and the
+dust.  %TODO: need this sentence to be better
+Observationally, optical spectropolarimetry on sufficiently large
+telescopes has the potential to assess both the field strength and
+topology.
+A more direct probe however might be to search for radio emission from
+mechanisms such as the electron cyclotron maser instability, which can
+provide a direct measurement of the field strength at the site of the
+emitting region (typically an auroral oval).
+Recent work (CITE) has shown that CPVs are variable radio emitters,
+and that they show emission components that can be both persistent, as
+well as short-lived and highly polarized.
+%Observation in the x-ray would similarly inform our view of the hotter
+%plasma in these magnetospheres which otherwise remains undetected.
+
+It is currently unclear what, if any, relationship CPVs have to the
+close-in exoplanets that exist around most M dwarfs (CITE).  However,
+0.3-3\% of young M dwarfs show the CPV phenomenon (CITE),
+and the circumstellar clumps of material need to be viewed
+edge-on for the light curves to be ``complex''.  This implies that an
+appreciable minority (3-30\%) of M dwarfs -- the rapidly rotating ones
+with centrifugal magnetospheres -- seem to have similar circumstellar
+environments to the CPVs.
 
@@
 \subsection{Modeling the Emitting Clump}
+\label{subsec:model}
+
+% * mass estimate
+The density and mass of the material...
 

### 2025-01-19 paper/ms.tex
update

@@
 only type of star to offer near-term prospects for detecting the
-atmospheres of rocky exoplanets with water on their surfaces (CITE).
-Investment with JWST has proceeded accordingly (CITE CITE).  It is
-therefore important to consider how the evolution of an M dwarf might
-impact the evolution of its planets.  Previous work has established
-that most M dwarfs host close-in planets (CITE), and that these
-planets are often subject to long circumstellar disk lifetimes (CITE),
-to large doses of UV radiation (CITE), and to a high incidence of
-flares and coronal mass ejections (CITE).  However, despite excellent
-work in these areas, the properties of the circumstellar plasma
-and magnetospheric environments to which young, close-in exoplanets
-are subject remain largely unexplored.
+atmospheres of rocky exoplanets with water on their surfaces
+\cite{NAP26141}.  Investment with JWST has proceeded accordingly, with
+a few percent of the telescope's time so far having been allocated to
+such objects.  In this context, it is therefore important to consider
+how the evolution of an M dwarf might impact the evolution of its
+planets.  Previous work has established that most M dwarfs host
+close-in planets \cite{Dressing2015}, and that these planets are often
+subject to long circumstellar disk lifetimes \cite{Ribas2015}, to
+large doses of UV radiation \cite{France2013}, and to a high incidence
+of flares and coronal mass ejections \cite{Gunther2020}.  However,
+despite excellent work in these areas, the properties of the
+circumstellar plasma and magnetospheric environments to which young,
+close-in exoplanets are subject remain challenging to explore.
 
@@
 interest in this article, but over one hundred analogous objects have
-now been discovered by K2 and TESS (CITE, CITE, CITE, CITE).  These CPVs are
+now been discovered by K2 and TESS 
+\cite{Rebull2016,Stauffer2017,Rebull2018,Zhan2019,Rebull2020,Bouma2024}.
+These CPVs are
 defined by their highly structured and periodic optical light curves, 
 and most are M dwarfs with rotation periods shorter than two days.
-Within current sensitivity limits, none have primordial disks (CITE).
+Within current sensitivity limits, none have primordial disks
+\cite{Stauffer2017,Bouma2024}.
 However, $\approx$3\% of stars a few million years old show this
-behavior (CITE), and the observed fraction decreases to $\approx$0.3\%
-by $\approx$150\,Myr (CITE).
+behavior, and the observed fraction decreases to $\approx$0.3\%
+by $\approx$150\,Myr \cite{Rebull2020}.
 
@@
 transiting clumps of circumstellar material corotate with the star
-(CITE, CITE, CITE), or that these stars represent an extreme in
+\cite{Stauffer2017,Gunther2022,Bouma2024},
+or that these stars represent an extreme in
 naturally-occurring distributions of starspots or faculae for young M
@@
 starspot-only explanation invokes the timescales and amplitudes of the
-sharpest photometric features (CITE).  However, no independent
+sharpest photometric features.  However, no independent
 evidence has yet been presented for the presence of circumstellar
-material in these objects.  Since transiting circumstellar
-clumps would geometrically imply an occcurrence rate a few to ten
-times the observed rate (CITE), the question of whether it is there
-could potentially teach us about 10-30\% of M dwarfs during their
-early lives.
+material in these objects.  Since transiting circumstellar clumps
+would geometrically imply an occcurrence rate a few to ten times the
+observed rate, the question of whether it is there could potentially
+teach us about 10-30\% of M dwarfs during their early lives.
 
@@
 such as H$\alpha$, caused by long-lived, corotating clumps of cool
-plasma (CITE, CITE, CITE).  Such clumps are forced into corotation by
-the magnetic field, and the exact geometry of where the plasma can
-accumulate is dictated by the magnetic field's topology.
-For instance, a tilted dipole field tends to yield an accumulation
-surface of a warped torus \cite{Townsend2005}, whereas in the limit of
-a single strong discrete field line, accumulation occurs along a fixed
-point \cite{Waugh2022}.  However, none of these stars have shown any
-photometric anomalies (CITE), leaving open the issue of whether these
-two separate areas of study have any direct connection.  Nonetheless,
-CPVs do respond to sudden magnetic field changes: there are many
-documented cases of otherwise long-lived eclipse features disappearing
-immediately following stellar flares (CITE, CITE).
+plasma \cite{CollierCameron1989,Donati2000,Dunstone2006,Skelly2008}.
+Such clumps are forced into corotation by the magnetic field, and the
+exact geometry of where the plasma can accumulate is dictated by the
+magnetic field's topology.  For instance, a tilted dipole field tends
+to yield an accumulation surface of a warped torus
+\cite{Townsend2005}, whereas in the limit of a single strong discrete
+field line, accumulation occurs along a fixed point \cite{Waugh2022}.
+However, none of these stars have shown any photometric anomalies
+\cite{Bouma2024}, leaving open the issue of whether these two separate
+areas of study have any direct connection.  Nonetheless, CPVs do
+respond to sudden magnetic field changes: there are many documented
+cases of otherwise long-lived eclipse features disappearing
+immediately following stellar flares \cite{Stauffer2017,Bouma2024}.
 
@@
 work \cite{Bouma2024} by searching the TESS two-minute data for stars
-showing periodic variability with at least three sharp dips per cycle.  We
-selected it from the resulting fifty high-quality CPVs for
+showing periodic variability with at least three sharp dips per cycle.
+We selected it from the resulting fifty high-quality CPVs for
 spectroscopic observations because it was the brightest source for
@@
 detail, TESS was finishing a data downlink during the HIRES
-observations, and photometric data collection resumed three rotation cycles
-(12 hours) after the spectra were acquired.  Extended Data
+observations, and photometric data collection resumed three rotation
+cycles (12 hours) after the spectra were acquired.  Extended Data
 Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
@@
 
-\subsection{Results}
+\section{Results}
 
@@
 
-\subsection{Discussion}
+\section{Discussion}
 
 Magetically-active, rapidly rotating stars with a wide range of masses
-have been known to exhibit both sinusoidal emission features (CITE,
-CITE, CITE, CITE) as well as sharp transient absorption features in
-their line cores (CITE, CITE, CITE, CITE) similar to those in
-Figure~\ref{fig:spec}.
-None of the low mass stars showing such spectroscopic features have
-previously shown abnormal light curves (CITE).
-The preferred interpretation for such spectroscopic variability comes
-from a loose analogy to quiescent solar prominences and filaments,
-which are cool condensations of plasma in the solar corona that last
-days to weeks (CITE).
-This plasma is called a prominence when viewed in emission against the
-dark backdrop of space, and a filament when viewed in absorption
-against the solar disk.
-In our Sun's magnetosphere, these condensations fall back to
-the solar surface because gravity is stronger than any magnetic or
-centrifugal force capable of sustaining them.
-However for stars with magnetospheric radii $R_{\rm m}$ that exceed the
-corotation radii $R_{\rm c}$, the effective potential experienced by
-the plasma have local minima outside the $R_{\rm c}$, enabling the
-material to be sustained for much longer timescales (see CITE, CITE).
+have been known to exhibit both sinusoidal emission features
+\cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} as well as
+sharp transient absorption features in their line cores
+\cite{CollierCameron1989,CollierCameron1992,Cang2020} similar to those
+in Figure~\ref{fig:spec}.  Such stars generally do not show complex
+light curves \cite{Bouma2024}.  The preferred interpretation for their
+spectroscopic variability comes from a loose analogy to quiescent
+solar prominences and filaments, which are cool condensations of
+plasma in the solar corona that can last days to weeks
+\cite{VialEngvold2015}.  This plasma is called a prominence when
+viewed in emission against the dark backdrop of space, and a filament
+when viewed in absorption against the solar disk.  In our Sun's
+magnetosphere, these condensations fall back to the solar surface
+because gravity is stronger than any magnetic or centrifugal force
+capable of sustaining them.  However for stars with magnetospheric
+radii $R_{\rm m}$ that exceed their corotation radii $R_{\rm c}$, the
+effective potential experienced by the plasma can have a local minimum
+outside the $R_{\rm c}$, enabling the material to be sustained for
+much longer timescales \cite{Petit2013,Daley-Yates2024}.
+Generally speaking, such material need neither transit, nor be
+optically thick.
 
-Our Keck/HIRES observations were the first time a CPV was observed
-with sufficient sensitivity to test for the presence of circumstellar
-plasma clumps, and they showed for TIC~141146667 that they exist and
-are corotating with the star.  
-Characteristic densities and masses of these clumps are $n \sim
-10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see~\ref{subsec:model}),
-a similar density to solar prominences, but ten to one hundred times
-more massive.
-This observation rules out a ``starspot-only'' origin scenario
-for CPVs, \cite{Koen2021} since such scenarios have no means of
-explaining spectroscopic emission beyond the stellar disk.  Similarly,
-scenarios in which the circumstellar material is made only of dust are
-also ruled out.  Although dust may be present, to explain the
-H$\alpha$ emission, the circumstellar clumps must include plasma with
-a significant population of hydrogen atoms in the $n$=3 excited state.
+Our Keck/HIRES observations are the first high-precision,
+high-resolution time-series spectra of a CPV, and they show the
+existence of circumstellar plasma clumps corotating with
+TIC~141146667.  Characteristic densities and masses of these clumps
+are $n \sim 10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see
+Supplementary Methods Section~\ref{subsec:model}), a similar density
+to solar prominences, but ten to one hundred times more massive.  This
+observation rules out a ``starspot-only'' origin scenario for CPVs,
+\cite{Koen2021} since such scenarios have no means of explaining
+spectroscopic emission beyond the stellar disk.  Similarly, scenarios
+in which the circumstellar material is made only of dust are also
+ruled out.  Although dust may be present, to explain the H$\alpha$
+emission, the circumstellar clumps must include plasma with a
+significant population of hydrogen atoms in the $n$=3 excited state.
 While the plasma is undoubtedly sculpted by the star's magnetic field,
@@
 
-The most intriguing potential known analogs to CPVs 
-are the $\sigma$~Ori~E variables, a rare subset of B stars that almost
-all have tilted-dipole magnetic fields (CITE) which can trap outflowing
-stellar winds into warped plasma tori (CITE). 
-These tori tend to have dense antipodal accumulations of plasma, and
-the transits of these accumulations can produce broadband photometric
-variability through a combination of bound-free scattering (CITE) and
-Thomson scattering (CITE).  For $\sigma$~Ori~E
-and most of its analogs, the result is light curves that almost all
-appear ``simple'', resembling those of eclipsing binaries (CITE,
-CITE).  The two known exceptions, HD~37776 and HD~64740, show complex
-light curves resembling CPVs (Mikulasek2020, CITEBouma2024), and have
+The closest potential known analogs to CPVs are the $\sigma$~Ori~E
+variables, a rare subset of B stars that almost all have tilted-dipole
+magnetic fields (CITE) which can trap outflowing stellar winds into
+warped plasma tori \cite{Townsend2005,Townsend2008}.  These tori tend
+to have dense antipodal accumulations of plasma, and the transits of
+these accumulations can produce broadband photometric variability
+through a combination of bound-free scattering \cite{Townsend2005} and
+Thomson scattering \citep{Berry2022}.  For $\sigma$~Ori~E and most of
+its analogs, the result is light curves that almost all appear
+``simple'', resembling those of eclipsing binaries.  The two known
+exceptions, HD~37776 and HD~64740, show complex light curves
+resembling CPVs \cite{Mikulasek2020,Bouma2024} and have
 spectropolarimetric magnetic field maps indicating strong
-contributions from higher-order magnetic moments (CITE CITE).  There are two
-implications: firstly, the complexity of CPVs may be a direct
-consequence of magnetic fields with highly multipolar contributions.
-Secondly, CPVs could be a source of astrophysical false positives in
-photometric searches for eclipsing binaries and transiting exoplanets
-around young pre-main-sequence M dwarfs (e.g.  CITE).
+contributions from higher-order magnetic moments
+\cite{Kochukhov2011,Shultz2018}.  There are two implications: firstly,
+the complexity of CPVs may be a direct consequence of magnetic fields
+with highly multipolar contributions.  Secondly, CPVs could be a
+source of astrophysical false positives in photometric searches for
+eclipsing binaries and transiting exoplanets around young
+pre-main-sequence M dwarfs \cite{Johns-Krull2016,Bouma2020}.
 
-% Need paragraph(s) on the future!
 Pressing issues for future work on CPVs include determining the
@@
 implied space weather experienced by the close-in rocky exoplanets
-that, statistically, are likely to be nearby (CITE).
+that, statistically, are likely to be nearby \cite{Dressing2015}.
 
@@
 While observations of CPVs in the optical have previously suggested
-the presence of dust (CITE), plasma clumps transiting over starspots
-can also produce chromatic features (CITERackham).  The composition
-and size distribution of any dust that is present could be most easily
-resolved by measuring the extinction curve for one or more CPVs from
-$\approx$1-10\,$\mu$m.  A composition similar to debris from rocky
-bodies seen around white dwarfs (CITE Reach+09) would be indicative of
-a rocky-body origin.  A composition closer to the ISM would be
-indicative of condensed dust in an M dwarf wind, similar to that
-formed in the environments of more evolved stars (CITE Marigo2008).
+the presence of dust \cite{Gunther2022,Koen2023}, a gray opacity
+source such as electron scattering in a plasma transiting over
+starspots could also produce chromatic features \cite{Rackham2018}.
+The composition and size distribution of any dust that is present
+could be most easily resolved by measuring the extinction curve for
+one or more CPVs from $\approx$1-10\,$\mu$m.  A composition similar to
+debris from rocky bodies seen around white dwarfs \cite{Reach2009}
+would be indicative of a rocky-body origin.  A composition closer to
+the ISM would be indicative of condensed dust in an M dwarf wind,
+similar to that formed in the environments of more evolved stars
+\cite{Marigo2008}.
 
 The role of the star's magnetic field could be better understood
-through new observations, and new theory.
-From the theoretical perspective, there is an urgent need for
-rigid-field magnetohydrodynamic (MHD) modeling to go beyond previous work
-(CITE CITE) by exploring the effects of non-dipolar field
-contributions.
-Fully time-dynamic MHD (e.g. CITE DaleyYates) will offer the
+through new observations, and new theory.  From the theoretical
+perspective, there is an urgent need for rigid-field
+(magneto)-hydrodynamic modeling to go beyond previous work
+\cite{Townsend2005,Townsend2008} by exploring the effects of
+non-dipolar field contributions.
+Fully time-dynamic MHD \cite{Daley-Yates2024} will offer the
 capability of understanding the connection between the plasma and the
@@
 telescopes has the potential to assess both the field strength and
-topology.
-A more direct probe however might be to search for radio emission from
-mechanisms such as the electron cyclotron maser instability, which can
-provide a direct measurement of the field strength at the site of the
-emitting region (typically an auroral oval).
-Recent work (CITE) has shown that CPVs are variable radio emitters,
-and that they show emission components that can be both persistent, as
-well as short-lived and highly polarized.
+topology.  A more direct probe however might be to search for radio
+emission from mechanisms such as the electron cyclotron maser
+instability, which can provide a direct measurement of the field
+strength at the site of the emitting region (typically an auroral
+oval).  Recent work \cite{Kaur2024} has shown that CPVs are variable
+radio emitters, and that they show emission components that can be
+both persistent, as well as short-lived and highly polarized.
 %Observation in the x-ray would similarly inform our view of the hotter
@@
 It is currently unclear what, if any, relationship CPVs have to the
-close-in exoplanets that exist around most M dwarfs (CITE).  However,
-0.3-3\% of young M dwarfs show the CPV phenomenon (CITE),
-and the circumstellar clumps of material need to be viewed
-edge-on for the light curves to be ``complex''.  This implies that an
+close-in exoplanets that exist around most M dwarfs
+\cite{Dressing2015}.  However, 0.3-3\% of young M dwarfs show the CPV
+phenomenon \cite{Rebull2020}, and the light curves being ``complex''
+seems to be associated with the circumstellar clumps of material
+transiting the star.  This geometric requirement implies that an
 appreciable minority (3-30\%) of M dwarfs -- the rapidly rotating ones
-with centrifugal magnetospheres -- seem to have similar circumstellar
+with centrifugal magnetospheres -- have similar circumstellar
 environments to the CPVs.
@@
 
-\subsection{Observations}
+\section{Observations}
 
@@
 
-\subsection{Data Reduction}
+\section{Data Reduction}
 
-\subsection{Modeling the Emitting Clump}
+\section{Modeling the Emitting Clump}
 \label{subsec:model}

### 2025-01-20 paper/ms.tex
update text

@@
 show structured, periodic optical light curves suggestive of
-transiting clumps of opaque circumstellar material that corotate
-with the star \cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.
+transiting clumps of opaque material corotating with the star
+\cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.
 The composition, origin, and even the existence of this material are
@@
 atmospheres of rocky exoplanets with water on their surfaces
-\cite{NAP26141}.  Investment with JWST has proceeded accordingly, with
-a few percent of the telescope's time so far having been allocated to
-such objects.  In this context, it is therefore important to consider
-how the evolution of an M dwarf might impact the evolution of its
-planets.  Previous work has established that most M dwarfs host
-close-in planets \cite{Dressing2015}, and that these planets are often
-subject to long circumstellar disk lifetimes \cite{Ribas2015}, to
-large doses of UV radiation \cite{France2013}, and to a high incidence
-of flares and coronal mass ejections \cite{Gunther2020}.  However,
-despite excellent work in these areas, the properties of the
-circumstellar plasma and magnetospheric environments to which young,
-close-in exoplanets are subject remain challenging to explore.
+\cite{NAP26141}.  Investment with JWST has proceeded accordingly.  In
+this context, it is therefore important to consider how the evolution
+of an M dwarf might impact the evolution of its planets.  Previous
+work has established that most M dwarfs host close-in planets
+\cite{Dressing2015}, and that these planets are often subject to long
+circumstellar disk lifetimes \cite{Ribas2015}, to large doses of UV
+radiation \cite{France2013}, and to a high incidence of flares and
+coronal mass ejections \cite{Gunther2020}.  However, despite excellent
+work in these areas, the properties of the circumstellar plasma and
+magnetospheric environments to which young, close-in exoplanets are
+subject remain challenging to quantify.
 
@@
 transiting clumps of circumstellar material corotate with the star
-\cite{Stauffer2017,Gunther2022,Bouma2024},
-or that these stars represent an extreme in
-naturally-occurring distributions of starspots or faculae for young M
-dwarfs \cite{Koen2021}.  Currently, the main argument against a
+\cite{Stauffer2017,Gunther2022,Bouma2024}, or that these stars
+represent an extreme in naturally-occurring distributions of starspots
+or faculae \cite{Koen2021}.  Currently, the main argument against a
 starspot-only explanation invokes the timescales and amplitudes of the
-sharpest photometric features.  However, no independent
-evidence has yet been presented for the presence of circumstellar
-material in these objects.  Since transiting circumstellar clumps
-would geometrically imply an occcurrence rate a few to ten times the
-observed rate, the question of whether it is there could potentially
-teach us about 10-30\% of M dwarfs during their early lives.
+sharpest photometric features.  However, no independent evidence has
+yet been acquired for the presence of circumstellar material in these
+objects.  Since transiting circumstellar clumps would geometrically
+imply an intrinsic occurrence a few to ten times the observed rate,
+the question of whether circumstellar clumps exist in these systems
+has the potential to be applicable to 10-30\% of M dwarfs during their
+early lives.
 
@@
 to yield an accumulation surface of a warped torus
-\cite{Townsend2005}, whereas in the limit of a single strong discrete
-field line, accumulation occurs along a fixed point \cite{Waugh2022}.
-However, none of these stars have shown any photometric anomalies
-\cite{Bouma2024}, leaving open the issue of whether these two separate
-areas of study have any direct connection.  Nonetheless, CPVs do
-respond to sudden magnetic field changes: there are many documented
-cases of otherwise long-lived eclipse features disappearing
-immediately following stellar flares \cite{Stauffer2017,Bouma2024}.
+\cite{Townsend2005}, whereas in the limit of a single strong field
+line, accumulation occurs along the apexpoint furthest from the star
+\cite{Waugh2022}.
+However, none of these spectroscopic variables have shown any
+photometric anomalies \cite{Bouma2024}, leaving open the issue of
+whether these two areas of study have any direct connection.
+Nonetheless, CPVs do respond to sudden magnetic field changes: the
+otherwise long-lived eclipse features often disappear immediately
+following stellar flares \cite{Stauffer2017,Bouma2024}.
 
@@
 showing periodic variability with at least three sharp dips per cycle.
-We selected it from the resulting fifty high-quality CPVs for
+We selected TIC~141146667 from the resulting fifty high-quality CPVs for
 spectroscopic observations because it was the brightest source for
@@
 Spectrometer (HIRES; \cite{vogt_hires_1994}) on the Keck I 10m
-telescope, roughly contemporaneous with TESS, which observed the star
-from UT 2024-02-05 to UT 2024-02-26 with a duty cycle of XX\%.  In
-detail, TESS was finishing a data downlink during the HIRES
-observations, and photometric data collection resumed three rotation
-cycles (12 hours) after the spectra were acquired.  Extended Data
-Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
-star before and after the exact epoch of observation; the star
-remained sufficiently stable to not affect any of the interpretation
-that follows.
+telescope.  TESS observed the star from UT 2024-02-05 to UT 2024-02-26
+with a duty cycle of XX\%.  TESS was finishing a data downlink during
+the spectral observations, and photometric data collection resumed
+three rotation cycles (12 hours) after the spectra were acquired.
+Extended Data Figure~\ref{fig:fulllc} shows the detailed photometric
+behavior of the star before and after the exact epoch of observation;
+the star remained sufficiently stable to not affect any of the
+interpretation that follows.
 
@@
 the period, followed by a complex eclipse-like feature spanning 55\%
-of the period.  This eclipse-like feature shows two to three
+of the period.  This eclipse feature shows two to three
 local photometric minima, and one to two local maxima.
+Its W-shape is suggestive of eclipse geometries seen in forward models
+of warped plasma tori \cite{Townsend2008}.
 
-% ** keck/hires: emission beyond v/veq>1 (2-3 paragraphs)
-The spectroscopy shows emission well outside the star's
-equatorial velocity ($v_{\rm eq}$=130\,\kms).  There are at least two
-distinct emission components, each spaced half a cycle apart in phase.  The
-first has clearer sinusoidal behaviour and is double-peaked, with
-semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.  The
-flux excesses from these two peaks are correlated with one another,
-with amplitudes varying from 100\% of the continuum flux early in the
-observation sequence to 30\% by its end.  The component 180$^\circ$
-opposite in phase is only detected from $\phi$=0.2-1.0, and 
-from $\phi$=0.2-0.5, this latter component appears connected to the
+% ** keck/hires: emission beyond v/veq>1
+The spectroscopy shows emission well outside the star's equatorial
+velocity ($v_{\rm eq}$=130\,\kms).  There are at least two distinct
+emission components, each spaced half a cycle apart in phase.  The
+first has clearer sinusoidal behaviour and is double-peaked, with peak
+semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
+There is also significant non-periodic variability in the spectra: for
+instance, the flux excesses from these two peaks begin with amplitudes
+equal to 100\% of the continuum flux early in the observation
+sequence, and both fall to 30\% by its end.  The component 180$^\circ$
+opposite in phase is similarly only detected from $\phi$=0.2-1.0.
+From $\phi$=0.2-0.5, this latter component appears connected to the
 star in velocity space.  While its peak semi-amplitude of
 $K_1$=3.9\,$v_{\rm eq}$ is achieved at both $\phi$=0.25 and 0.75, its
-amplitude decreases from a 60\% excess beyond the continuum to a 10\%
-excess.   The sinusoidal period in all cases where emission is seen is
-consistent with the photometric \periodhr\ hour period.
+amplitude decreases from a 60\% excess over the continuum at the
+beginning of the observation sequence to a 10\% excess by its end.
+The sinusoidal period for all of these emission signals is consistent
+with the photometric \periodhr\ hour period.
 
-The sinusoidal emission features require circumstellar clumps of
+These sinusoidal emission features require circumstellar clumps of
 partially-ionized hydrogen to be corotating with the star.  The
@@
 
-% * keck/hires: absorption within v/veq<1
-% * keck/hires: emission within v/veq<1
+% * keck/hires: behavior at v/veq<1
 The behavior within the stellar H$\alpha$ line core, at $|\Delta v /
-v_{\rm eq}|<1$, is more complex than outside it.  Generally, one would
-expect the emission in the line core to be generated near the stellar
-chromosphere, near the star's surface, and then modulated by any
-occulting material capable of absorbing or emitting in H$\alpha$.  In
-Figure~\ref{fig:spec}e, the behavior from $\phi$=0.4-1.2 is most
-easy to interpret: from $\phi$=0.4-0.9, a hot region first gradually
-crosses the stellar line profile, followed from $\phi$=0.7-1.2 by the
-transit of a cool region.  The phases $\phi$$<$0.4 seem to be a mix of
-similar events, though the time sampling is sufficiently coarse that
-the interpretation is less clear.  A final exercise to quantify the
-behavior in the line core is shown in Figure~\ref{fig:spec}d, where
-$f_{\rm H\alpha\ core}$ denotes the summed flux in the at $|\Delta v /
-v_{\rm eq}|<1$.  Changes in the line core flux are usually correlated
-with the broadband variability, except at $\phi$=0.5, during the
-transit of the higher-velocity clump and the occultation of the
-lower-velocity clump.
+v_{\rm eq}|<1$, is even more complex than outside it.  For stars of
+this age and spectral type, one would expect emission in the line core
+to be generated in the stellar chromosphere, near the star's surface,
+and then modulated by any occulting material capable of absorbing or
+emitting in H$\alpha$.  In Figure~\ref{fig:spec}e, the behavior from
+$\phi$=0.4-1.2 is most easy to interpret: from $\phi$=0.4-0.9, a hot
+region first gradually crosses the stellar line profile, followed from
+$\phi$=0.7-1.2 by the transit of a cool region.  Phases $\phi$$<$0.4
+seem to show a mix of similar events, though the time sampling is
+sufficiently coarse that the interpretation is less clear.  A final
+exercise to quantify the behavior in the line core is shown in
+Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes the
+summed flux at $|\Delta v / v_{\rm eq}|<1$.  Changes in the line core
+flux are usually correlated with the broadband variability, except at
+$\phi$=0.5, during the transit of the higher-velocity clump and the
+occultation of the lower-velocity clump.
 
 \section{Discussion}
+% argue: how does this clarify wider phenomenology?  what general
+% conclusions can be drawn?
 
@@
 \cite{CollierCameron1989,CollierCameron1992,Cang2020} similar to those
-in Figure~\ref{fig:spec}.  Such stars generally do not show complex
-light curves \cite{Bouma2024}.  The preferred interpretation for their
-spectroscopic variability comes from a loose analogy to quiescent
-solar prominences and filaments, which are cool condensations of
-plasma in the solar corona that can last days to weeks
-\cite{VialEngvold2015}.  This plasma is called a prominence when
+in Figure~\ref{fig:spec}.  No such stars were previously known to show
+complex light curves \cite{Bouma2024}.  The usual interpretation for
+their spectroscopic variability comes from a loose analogy to
+quiescent solar prominences and filaments, which are cool
+condensations of plasma in the solar corona that can last days to
+weeks \cite{VialEngvold2015}.  This plasma is called a prominence when
 viewed in emission against the dark backdrop of space, and a filament
@@
 radii $R_{\rm m}$ that exceed their corotation radii $R_{\rm c}$, the
-effective potential experienced by the plasma can have a local minimum
-outside the $R_{\rm c}$, enabling the material to be sustained for
-much longer timescales \cite{Petit2013,Daley-Yates2024}.
-Generally speaking, such material need neither transit, nor be
-optically thick.
+effective potential experienced by a plasma parcel can have a local minimum
+outside $R_{\rm c}$, enabling the material to be sustained for
+much longer timescales \cite{Petit2013,Daley-Yates2024}.  Generally
+speaking, such material need neither transit, nor be optically thick.
 
-Our Keck/HIRES observations are the first high-precision,
-high-resolution time-series spectra of a CPV, and they show the
-existence of circumstellar plasma clumps corotating with
-TIC~141146667.  Characteristic densities and masses of these clumps
-are $n \sim 10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see
+Our Keck/HIRES observations are the first high-resolution time-series
+spectra of a CPV, and they show circumstellar plasma clumps corotating
+with TIC~141146667.  Characteristic densities and masses of these
+clumps are $n \sim 10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see
 Supplementary Methods Section~\ref{subsec:model}), a similar density
@@
 in which the circumstellar material is made only of dust are also
-ruled out.  Although dust may be present, to explain the H$\alpha$
-emission, the circumstellar clumps must include plasma with a
+ruled out.  While dust may be present, to explain the H$\alpha$
+emission the circumstellar clumps must include plasma with a
 significant population of hydrogen atoms in the $n$=3 excited state.
-While the plasma is undoubtedly sculpted by the star's magnetic field,
-there are three a priori plausible origin locations for the material:
+This plasma is undoubtedly sculpted by the star's magnetic field.
+However, it could plausibly originate from three sites:
 the star, an old and undetected disk, or outgassing rocky bodies.
+This latter possibility would render CPVs as extrasolar analogs of
+the Jupiter-Io plasma torus (CITE).
 
-The closest potential known analogs to CPVs are the $\sigma$~Ori~E
-variables, a rare subset of B stars that almost all have tilted-dipole
-magnetic fields (CITE) which can trap outflowing stellar winds into
+The other potential analog for the CPVs are the $\sigma$~Ori~E
+variables, a rare subset of B stars that host which can trap outflowing stellar winds into
 warped plasma tori \cite{Townsend2005,Townsend2008}.  These tori tend
-to have dense antipodal accumulations of plasma, and the transits of
-these accumulations can produce broadband photometric variability
+to have dense antipodal accumulations of plasma sculpted by
+tilted-dipole magnetic fields, and the transits of
+these clumps are thought to produce the observed broadband photometric variability
 through a combination of bound-free scattering \cite{Townsend2005} and
-Thomson scattering \citep{Berry2022}.  For $\sigma$~Ori~E and most of
-its analogs, the result is light curves that almost all appear
-``simple'', resembling those of eclipsing binaries.  The two known
+Thomson scattering \cite{Berry2022}.  For $\sigma$~Ori~E and almost
+all of its analogs, the result is light curves that appear ``simple'',
+resembling those of eclipsing binaries.  The two known
 exceptions, HD~37776 and HD~64740, show complex light curves
@@
 implied space weather experienced by the close-in rocky exoplanets
-that, statistically, are likely to be nearby \cite{Dressing2015}.
+that, statistically \cite{Dressing2015}, are likely to be near our
+observed plasma clumps.
 
-The composition -- either purely plasma, or else a dusty plasma -- can
-be clarified by time-series optical and infrared spectrophotometry.
-While observations of CPVs in the optical have previously suggested
-the presence of dust \cite{Gunther2022,Koen2023}, a gray opacity
-source such as electron scattering in a plasma transiting over
-starspots could also produce chromatic features \cite{Rackham2018}.
-The composition and size distribution of any dust that is present
-could be most easily resolved by measuring the extinction curve for
-one or more CPVs from $\approx$1-10\,$\mu$m.  A composition similar to
-debris from rocky bodies seen around white dwarfs \cite{Reach2009}
-would be indicative of a rocky-body origin.  A composition closer to
-the ISM would be indicative of condensed dust in an M dwarf wind,
-similar to that formed in the environments of more evolved stars
-\cite{Marigo2008}.
+The material's composition -- either purely plasma, or else a dusty
+plasma -- can be clarified by time-series optical and infrared
+spectrophotometry.  While observations of CPVs in the optical have
+previously shown chromaticity consistent with dust \cite{Gunther2022,Koen2023},
+a gray opacity source such as electron scattering in a plasma
+transiting over starspots could also produce chromatic features
+\cite{Rackham2018}.  The composition and size distribution of any dust
+that is present could be most easily resolved by measuring the
+extinction curve for one or more CPVs from $\approx$1-10\,$\mu$m.  A
+dust composition similar to debris from rocky bodies seen around white
+dwarfs \cite{Reach2009} would indicate a rocky-body origin.  A 
+composition closer to the ISM would be indicative of condensed dust in
+an M dwarf wind, similar to that formed in the environments of more
+evolved stars \cite{Marigo2008}.
 
@@
 (magneto)-hydrodynamic modeling to go beyond previous work
-\cite{Townsend2005,Townsend2008} by exploring the effects of
+\cite{Townsend2005,Townsend2008} and to explore the effects of
 non-dipolar field contributions.
@@
 dust.  %TODO: need this sentence to be better
-Observationally, optical spectropolarimetry on sufficiently large
-telescopes has the potential to assess both the field strength and
-topology.  A more direct probe however might be to search for radio
-emission from mechanisms such as the electron cyclotron maser
-instability, which can provide a direct measurement of the field
-strength at the site of the emitting region (typically an auroral
-oval).  Recent work \cite{Kaur2024} has shown that CPVs are variable
-radio emitters, and that they show emission components that can be
-both persistent, as well as short-lived and highly polarized.
-%Observation in the x-ray would similarly inform our view of the hotter
-%plasma in these magnetospheres which otherwise remains undetected.
+Observationally, optical spectropolarimetry has the potential to
+assess both the field strength and topology.  A more direct probe
+however might be to connected the recent work \cite{Kaur2024} showing
+that CPVs are variable radio emitters, exhibiting emission components
+that can be both persistent, as well as short-lived and highly
+polarized.  This opens the prospects for detecting for radio waves
+emitted through the electron cyclotron maser instability, which can
+provide a direct measurement of the field strength at the site of the
+emitting region.
 
@@
 \cite{Dressing2015}.  However, 0.3-3\% of young M dwarfs show the CPV
-phenomenon \cite{Rebull2020}, and the light curves being ``complex''
-seems to be associated with the circumstellar clumps of material
-transiting the star.  This geometric requirement implies that an
-appreciable minority (3-30\%) of M dwarfs -- the rapidly rotating ones
-with centrifugal magnetospheres -- have similar circumstellar
-environments to the CPVs.
+phenomenon \cite{Rebull2020}, and the phenomenon seems to be caused by
+circumstellar clumps of material transiting the star.  The implied
+geometric correction suggests that an appreciable minority (3-30\%) of
+M dwarfs -- the rapidly rotating ones with centrifugal magnetospheres
+-- have similar circumstellar environments to the CPVs.
 

### 2025-01-20 paper/ms.tex
add essentials table

@@
 
+\begin{table*}
+\scriptsize
+\setlength{\tabcolsep}{2pt}
+\centering
+\caption{Selected System Parameters for TIC~141146667}
+\label{tab:params}
+\begin{tabular}{llcc}
+\hline \hline
+Parameter & Description & Value & Source\\
+\hline 
+%
+$T_{\rm eff}$\dotfill                   & Effective Temperature (K) \hspace{9pt}\dotfill                 & 2972 $\pm$ 40    & 1 \\
+%$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & 4.53 $\pm$ 0.05  & 6 \\
+$R_\star$\dotfill                       & Stellar radius ($R_\odot$)\dotfill                             & 0.42$\pm$0.02    & 1 \\
+%
+$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & XXX  & 6 \\
+%
+Age                                     & Adopted stellar age (Myr)\dotfill                              & YYY  & 8 \\
+%
+Spec. Type\dotfill                      & Spectral Type\dotfill                                          & MXV              & X \\
+%
+$P_{\rm rot}$\dotfill                   & Rotation period (hr)\dotfill                                   & $3.930\pm 0.001$ & X \\
+%
+$v_{\rm eq}$\dotfill		                & Equatorial velocity \dotfill                                   &  130$\pm$4       & - \\
+                                        & \hspace{3pt} ($2\pi R_\star/P_{\rm rot}$) (\kms)	             &                      \\
+%
+$v_{\rm eq}\sin{i_\star}$\dotfill		    & Projected rotational\dotfill                                   &  128$\pm$3       & X \\
+                                        & \hspace{3pt} velocity (\kms)	                                 &                      \\
+%
+$i_\star$\dotfill                       & Stellar inclination (deg)\dotfill                              & 	XXX             & X \\
+%
+$d$\dotfill                             & Distance (pc)\dotfill                                          & $57.6 \pm X.X$   & X \\
+%
+$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   &  XXX             & X \\
+                                        & \hspace{3pt} radius ($R_\star$)	                               &                      \\
+%
+$a_1$\dotfill                           & Clump 1 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.1-2.7         & X \\
+$a_2$\dotfill                           & Clump 2 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  3.9             & X \\
+%
+$\langle$EW$_{\rm H\alpha}$$\rangle$    & Time-averaged H$\alpha$ line core                              &  X.X             & Y \\ 
+                                        & \hspace{3pt} equivalent width (\AA)	                           &                      \\
+Range(EW$_{\rm H\alpha}$)$_1$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
+                                        & \hspace{3pt} from Clump 1 (\AA)	                               &                      \\
+Range(EW$_{\rm H\alpha}$)$_2$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
+                                        & \hspace{3pt} from Clump 2 (\AA)	                               &                      \\
+\hline
+\end{tabular}
+\begin{flushleft}
+\footnotesize{ \textsc{NOTE}---
+%$^\dagger$ The GAIADR2 and GAIAEDR3 identifiers for Kepler 1627A are identical.  The secondary
+is not resolved in the Gaia point source catalog.
+$^*$ Given only $v\sin i$ and $2\pi R_\star/P_{\rm rot}$, $\cos i=0.11^{+0.11}_{-0.08}$.
+Provenances are:
+1: SED fit\cite{Bouma2024},
+%$^6$Cluster isochrone (MIST adopted; PARSEC compared for quoted
+%  uncertainty),
+2: TESS light curve,
+%  3: HIRES spectra and specmatch(?),
+%$^8$Pre-main-sequence CAMD interpolation (Section~\ref{sec:camd}),
+}
+\end{flushleft}
+\vspace{-0.5cm}
+\end{table*}
+
 \section{Discussion}

### 2025-01-20 paper/ms.tex
update

@@
 $T_{\rm eff}$\dotfill                   & Effective Temperature (K) \hspace{9pt}\dotfill                 & 2972 $\pm$ 40    & 1 \\
-%$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & 4.53 $\pm$ 0.05  & 6 \\
+%
+%$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & YYY              & X \\
+%
 $R_\star$\dotfill                       & Stellar radius ($R_\odot$)\dotfill                             & 0.42$\pm$0.02    & 1 \\
@@
 
-\section{Observations}
+\subsection{Observations \& Data Reduction}
 
@@
 
-{\bf TESS:}
+{\it TESS:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14, 15, 21, 41, 48,
+and 75.  Two-minute data were acquired during Sectors 41, 48 (TESS
+DDT039, PI: M.~Kunimoto), and 75 (TESS Program G06030, PI: L.~Bouma);
+the earlier data had a 30-minute cadence, which significantly
+phase-smears sharp features over a $<$4\,hour period (see
+\cite{Gunther2022}).
+The nearest star in the TESS images, TIC~141146666 ($T$14.5), is 
+25$''$ from TIC~141146667 and does not appear to photometrically vary.
 
-{\bf Keck/HIRES:}
+{\it Keck/HIRES:}
 We observed using the standard setup and reduction techniques of the
@@
 1\farcs2$\pm$0\farcs2 seeing over the spectroscopic observations.  
+% TODO: mention deblazing 20241115_tic1411_deblazing_notes.txt
 
-\section{Data Reduction}
+\subsection{Stellar Parameters}
+{\it Age}
+While most CPVs can be spatially and kinematically associated with known young
+moving groups using tools such as BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018},
+TIC~141146667 cannot \cite{Bouma2024}.
+%.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
+%git commit \texttt{394b486}}
 
-\section{Modeling the Emitting Clump}
+Isochrone age: $\sim$TucHor or younger.  Maybe 30-35myr?
+NB color puts it at ~M4.5 (main seq).
+BP-RP=3.3..
+
+Lithium?
+Frankly, it's not obviously there!  (but maybe this is bc of the blending, and
+a pEW would show smth small)
+% We have K=10.47, d=57pc - > DM ~= 3.78 -> M_K ~= 6.67
+Figure7 of Wood23 suggests from the Feiden Li depletion curves that no lithium would imply $t$>37Myr.
+However Figure5 frmo the same work suggests maybe try binning up the spectrum, and then comparing against Bochanski+2007 for a lithium-free template.
+
+This is weird.  Are you 100\% sure it's not a binary?  Ups the need for
+the RV analysis.
+
+{\it Effective temperature, radius, and mass}
+We adopt the results from the spectral energy distribution fitting
+exercise described by \cite{Bouma2024}.
+In brief, this approach used
+\texttt{astroARIADNE}...
+\cite{Vines2022} with the BT-Settl stellar
+atmosphere models \cite{Allard2012} assuming the
+\cite{Asplund2009} solar abundances, and the
+\cite{Barber2006} water line lists.  
+We used broadband magnitudes from Gaia DR2, APASS, 2MASS, SDSS, and WISE
+  $W1$ and $W2$.  (explain)...
+%%%%%%%%
+%\texttt{astroARIADNE} compares the measured broadband flux
+%measurements against pre-computed model grids, and by default fits for
+%six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
+%Fe/H}], d \}$.  The distance  prior is drawn from
+%\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
+%generally unconstrained.  Given our selection criteria for the stars,
+%we assumed the following priors for the temperature, stellar size, and
+%extinction:
+%\begin{align}
+%  T_{\rm eff} / {\rm K}    &\sim \mathcal{U}(2000, 8000), \\
+%  R_\star / R_\odot  &\sim \mathcal{U}(0.1, 1.5), \\
+%  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
+%\end{align}
+%for \deleted{$\mathcal{N}$ the Gaussian and }$\mathcal{U}$ the uniform
+%distribution\deleted{s, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
+%truncated normal distribution with mean $\mu$, standard deviation
+%$\sigma$, and lower and upper bounds $a$ and $b$}.  We validated our
+%chosen upper bound on $A_{\rm V}$ using a 2MASS color-color diagram.
+%Finally, using \texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we
+%sampled the posterior probability assuming the default Gaussian
+%likelihood, and set a stopping threshold of ${\rm d}\log \mathcal{Z} <
+%0.01$, where $\mathcal{Z}$ denotes the evidence.
+
+{\it Binarity}
+
+\subsection{Spectral Behavior of Other Lines}
+
+First, chromospheric:
+
+{\it H$\gamma$, H$\delta$}
+Line ratios.
+
+{\it Ca [K]}
+{\it Also} shows some high-velocity emission.  So, the emitting material has
+calcium ions.
+
+{\it He 5880}
+Also variable...
+
+{\it Magnesium b orders}
+Shows some variability that is horrendously blended.
+
+{\it K[I] 7700}
+Literally the only obvious photospheric line.
+
+\subsection{Modeling the Emitting Clump}
 \label{subsec:model}

### 2025-01-21 paper/ms.tex
progress from a days work

@@
 $M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & XXX  & 6 \\
+%
+% TODO: this value is a quicklook from calc_hires_systemic_velocities.py, rj537.166.fits.  should average over whole timeseries.
+$\gamma$\dotfill                       & Systemic radial velocity (\kms)\dotfill                         & 2.2 $\pm$ 0.9  & 1  \\
 %

### 2025-01-21 paper/ms.tex
update

@@
 all of its analogs, the result is light curves that appear ``simple'',
-resembling those of eclipsing binaries.  The two known
+resembling those of eclipsing binaries \cite{Townsend2008}.  The two known
 exceptions, HD~37776 and HD~64740, show complex light curves
@@
 non-dipolar field contributions.
-Fully time-dynamic MHD \cite{Daley-Yates2024} will offer the
-capability of understanding the connection between the plasma and the
-dust.  %TODO: need this sentence to be better
+In particular, dynamo simulations of fully-convective M dwarfs have
+suggested the possibility that global-scale mean fields can be
+confined to a single hemisphere \cite{Brown2020}; such fields would
+significantly alter plausible accumulations of circumstellar material
+from those that have been previously explored \cite{Townsend2008}.
 Observationally, optical spectropolarimetry has the potential to
@@
 \subsection{Stellar Parameters}
-{\it Age}
-While most CPVs can be spatially and kinematically associated with known young
-moving groups using tools such as BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018},
-TIC~141146667 cannot \cite{Bouma2024}.
-%.\footnote{\url{https://github.com/jgagneastro/banyan_sigma},
-%git commit \texttt{394b486}}
+{\it Age: No Obvious Association Membership}---Previous work
+  \cite{Bouma2024} has shown that an overwhelming majority of CPVs can
+  be associated with known young moving groups based on their
+  positions and kinematics using probabilistic tools such as
+  BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018}.  TIC~141146667 cannot;
+  based on the current census of these known groups, we calculated its
+  probability of being part of any of these groups using its known
+  three-dimensional galactic position velocity, and it appears to be a
+  field star at $>$99.9\% confidence.  Searching the local vicinity of
+  the star for neighbors with similar projected on-sky velocity (CITE)
+  similarly yields no strong candidates for co-moving stars with
+  tangential velocity differences below 5\,\kms\ that share its
+  isochronal youth.
 
-Isochrone age: $\sim$TucHor or younger.  Maybe 30-35myr?
-NB color puts it at ~M4.5 (main seq).
-BP-RP=3.3..
+{\it Age: Isochrones}--- $\sim$TucHor or younger.  Maybe 30-35myr?  NB
+  color puts it at ~M4.5 (main seq).  BP-RP=3.3..
+    % uhhh careful w what you mean by "isochrone"
 
-Lithium?
-Frankly, it's not obviously there!  (but maybe this is bc of the blending, and
-a pEW would show smth small)
+{\it Age: Lithium}--- Frankly, it's not obviously there!  (but maybe
+this is bc of the blending, and a pEW would show smth small)
 % We have K=10.47, d=57pc - > DM ~= 3.78 -> M_K ~= 6.67

### 2025-01-22 paper/ms.tex
update

@@
 atmospheres of rocky exoplanets with water on their surfaces
-\cite{NAP26141}.  Investment with JWST has proceeded accordingly.  In
-this context, it is therefore important to consider how the evolution
-of an M dwarf might impact the evolution of its planets.  Previous
-work has established that most M dwarfs host close-in planets
-\cite{Dressing2015}, and that these planets are often subject to long
+\cite{NAP26141}.  Investment with JWST has proceeded accordingly.  How
+an M dwarf's evolution influences its planets---especially the
+retention of their atmospheres--- has concurrently become a major
+theme in exoplanet and stellar astrophysics.  Previous work has
+established that most M dwarfs host close-in planets
+\cite{Dressing2015} that are often subject to long
 circumstellar disk lifetimes \cite{Ribas2015}, to large doses of UV
 radiation \cite{France2013}, and to a high incidence of flares and
-coronal mass ejections \cite{Gunther2020}.  However, despite excellent
+coronal mass ejections \cite{Gunther2020}.  Nevertheless, despite excellent
 work in these areas, the properties of the circumstellar plasma and
-magnetospheric environments to which young, close-in exoplanets are
-subject remain challenging to quantify.
+magnetospheric environments that bathe young, close-in exoplanets have
+remained challenging to quantify.
 
@@
 showing periodic variability with at least three sharp dips per cycle.
-We selected TIC~141146667 from the resulting fifty high-quality CPVs for
-spectroscopic observations because it was the brightest source for
-which a full cycle could be observed in a half-night.  We observed it
-for five hours on UT 2024-02-17 using the High Resolution Echelle
-Spectrometer (HIRES; \cite{vogt_hires_1994}) on the Keck I 10m
-telescope.  TESS observed the star from UT 2024-02-05 to UT 2024-02-26
-with a duty cycle of XX\%.  TESS was finishing a data downlink during
-the spectral observations, and photometric data collection resumed
-three rotation cycles (12 hours) after the spectra were acquired.
-Extended Data Figure~\ref{fig:fulllc} shows the detailed photometric
-behavior of the star before and after the exact epoch of observation;
-the star remained sufficiently stable to not affect any of the
-interpretation that follows.
+We selected the star for spectroscopic observations because its
+brightness and rapid rotation offered sensitivity to small variations
+in the line profiles.  We observed it for five hours on UT 2024-02-17
+using the High Resolution Echelle Spectrometer (HIRES;
+\cite{vogt_hires_1994}) on the Keck I 10m telescope.  TESS observed
+the star from UT 2024-02-05 to UT 2024-02-26 with a duty cycle of
+XX\%.  TESS was finishing a data downlink during the spectral
+observations, and photometric data collection resumed three rotation
+cycles (12 hours) after the spectra were acquired.  Extended Data
+Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
+star before and after the exact epoch of observation; the star
+remained sufficiently stable to not affect the interpretation that
+follows.
 
@@
 based on other CPVs \cite{Bouma2024}, the photometric shape of
-TIC~141146667 evolved over the years following the 2022 discovery
+TIC~141146667 evolved following the 2022 discovery
 data, while nonetheless remaining complex.  In February 2024, the
@@
 % ** keck/hires: emission beyond v/veq>1
-The spectroscopy shows emission well outside the star's equatorial
+The spectroscopy shows emission well beyond the star's equatorial
 velocity ($v_{\rm eq}$=130\,\kms).  There are at least two distinct
-emission components, each spaced half a cycle apart in phase.  The
-first has clearer sinusoidal behaviour and is double-peaked, with peak
+emission components, separated by half a cycle in phase.  The
+first component has clearer sinusoidal behaviour and is double-peaked, with peak
 semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
-There is also significant non-periodic variability in the spectra: for
-instance, the flux excesses from these two peaks begin with amplitudes
+There is significant non-periodic variability in this double-peaked
+component: the flux excess from both peaks begins with an amplitude
 equal to 100\% of the continuum flux early in the observation
-sequence, and both fall to 30\% by its end.  The component 180$^\circ$
+sequence, and falls to 30\% by its end.  The component 180$^\circ$
 opposite in phase is similarly only detected from $\phi$=0.2-1.0.
@@
 beginning of the observation sequence to a 10\% excess by its end.
-The sinusoidal period for all of these emission signals is consistent
+The sinusoidal period for all of these emission components is consistent
 with the photometric \periodhr\ hour period.
@@
 partially-ionized hydrogen to be corotating with the star.  The
-velocity semi-amplitude of the sinusoids directly gives the distance
+velocity semi-amplitude of the sinusoids gives the distance
 of these clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
@@
 The behavior within the stellar H$\alpha$ line core, at $|\Delta v /
-v_{\rm eq}|<1$, is even more complex than outside it.  For stars of
+v_{\rm eq}|<1$, is more complex than outside it.  For stars of
 this age and spectral type, one would expect emission in the line core
-to be generated in the stellar chromosphere, near the star's surface,
+to be generated in the stellar chromosphere
 and then modulated by any occulting material capable of absorbing or
-emitting in H$\alpha$.  In Figure~\ref{fig:spec}e, the behavior from
-$\phi$=0.4-1.2 is most easy to interpret: from $\phi$=0.4-0.9, a hot
+emitting H$\alpha$ photons.  In Figure~\ref{fig:spec}e, the behavior from
+$\phi$=0.4-1.2 has a simple interpretation: from $\phi$=0.4-0.9, a hot
 region first gradually crosses the stellar line profile, followed from
 $\phi$=0.7-1.2 by the transit of a cool region.  Phases $\phi$$<$0.4
-seem to show a mix of similar events, though the time sampling is
+show a mix of similar events, though the time sampling is
 sufficiently coarse that the interpretation is less clear.  A final
@@
 Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes the
-summed flux at $|\Delta v / v_{\rm eq}|<1$.  Changes in the line core
-flux are usually correlated with the broadband variability, except at
-$\phi$=0.5, during the transit of the higher-velocity clump and the
-occultation of the lower-velocity clump.
+summed flux at $|\Delta v / v_{\rm eq}|<1$.  This panel shows that
+changes in the line core flux are usually correlated with the
+broadband variability, except at $\phi$=0.5, during the transit of the
+higher-velocity clump and the occultation of the lower-velocity clump.
 
@@
 
-Magetically-active, rapidly rotating stars with a wide range of masses
+Spectra of magetically-active, rapidly rotating stars with a wide range of masses
 have been known to exhibit both sinusoidal emission features
@@
 complex light curves \cite{Bouma2024}.  The usual interpretation for
-their spectroscopic variability comes from a loose analogy to
+such variability comes from a loose analogy to
 quiescent solar prominences and filaments, which are cool
@@
 Our Keck/HIRES observations are the first high-resolution time-series
-spectra of a CPV, and they show circumstellar plasma clumps corotating
-with TIC~141146667.  Characteristic densities and masses of these
+spectra of a CPV, and they show that corotating circumstellar plasma clumps 
+are present in at least one such star.
+Characteristic densities and masses of these
 clumps are $n \sim 10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see
@@
 significant population of hydrogen atoms in the $n$=3 excited state.
-This plasma is undoubtedly sculpted by the star's magnetic field.
-However, it could plausibly originate from three sites:
-the star, an old and undetected disk, or outgassing rocky bodies.
-This latter possibility would render CPVs as extrasolar analogs of
-the Jupiter-Io plasma torus (CITE).
+While this plasma is undoubtedly sculpted by the star's magnetic
+field, it could plausibly originate from three sites: the star, an old
+and undetected disk, or outgassing rocky bodies.  This latter
+possibility would render CPVs as extrasolar analogs of the Jupiter-Io
+plasma torus (CITE).
 
 The other potential analog for the CPVs are the $\sigma$~Ori~E
-variables, a rare subset of B stars that host which can trap outflowing stellar winds into
+variables, a rare subset of B stars that with radiatively-driven winds
+that can accumulate into
 warped plasma tori \cite{Townsend2005,Townsend2008}.  These tori tend
@@
 these clumps are thought to produce the observed broadband photometric variability
-through a combination of bound-free scattering \cite{Townsend2005} and
+through bound-free scattering \cite{Townsend2005} and
 Thomson scattering \cite{Berry2022}.  For $\sigma$~Ori~E and almost
@@
 contributions from higher-order magnetic moments
-\cite{Kochukhov2011,Shultz2018}.  There are two implications: firstly,
+\cite{Kochukhov2011,Shultz2018}.  There are two implications: first,
 the complexity of CPVs may be a direct consequence of magnetic fields
-with highly multipolar contributions.  Secondly, CPVs could be a
+with highly multipolar contributions.  Second, CPVs could be a
 source of astrophysical false positives in photometric searches for
@@
 
-Pressing issues for future work on CPVs include determining the
-composition and origin of the circumstellar material, understanding
-the exact role of the stellar magnetic field, and exploring the
-implied space weather experienced by the close-in rocky exoplanets
-that, statistically \cite{Dressing2015}, are likely to be near our
-observed plasma clumps.
+Pressing issues for future work include determining the composition
+and origin of the circumstellar material, understanding the exact role
+of the stellar magnetic field, and exploring the implied space weather
+experienced by the close-in rocky exoplanets that, statistically
+\cite{Dressing2015}, are likely to be present in most CPV systems.
 
-The material's composition -- either purely plasma, or else a dusty
+The material's composition -- either pure plasma, or else a dusty
 plasma -- can be clarified by time-series optical and infrared
 spectrophotometry.  While observations of CPVs in the optical have
-previously shown chromaticity consistent with dust \cite{Gunther2022,Koen2023},
+previously shown chromaticity consistent with dust \cite{Tanimoto2020,Gunther2022,Koen2023},
 a gray opacity source such as electron scattering in a plasma
@@
 that is present could be most easily resolved by measuring the
-extinction curve for one or more CPVs from $\approx$1-10\,$\mu$m.  A
+extinction curve for one or more CPVs from 1-10\,$\mu$m.  A
 dust composition similar to debris from rocky bodies seen around white
@@
 confined to a single hemisphere \cite{Brown2020}; such fields would
-significantly alter plausible accumulations of circumstellar material
-from those that have been previously explored \cite{Townsend2008}.
-Observationally, optical spectropolarimetry has the potential to
+yield accumulations of circumstellar material quite different
+from those that have previously been explored \cite{Townsend2008}.
+Observationally, spectropolarimetry has the potential to
 assess both the field strength and topology.  A more direct probe
@@
 that can be both persistent, as well as short-lived and highly
-polarized.  This opens the prospects for detecting for radio waves
-emitted through the electron cyclotron maser instability, which can
+polarized.  This opens the prospects for detecting radio emission
+from the electron cyclotron maser instability, which would
 provide a direct measurement of the field strength at the site of the
@@
 \cite{Dressing2015}.  However, 0.3-3\% of young M dwarfs show the CPV
-phenomenon \cite{Rebull2020}, and the phenomenon seems to be caused by
-circumstellar clumps of material transiting the star.  The implied
-geometric correction suggests that an appreciable minority (3-30\%) of
-M dwarfs -- the rapidly rotating ones with centrifugal magnetospheres
--- have similar circumstellar environments to the CPVs.
+phenomenon \cite{Rebull2020}, and our data show that the phenomenon
+occurs when clumps of circumstellar material transit the star.  The
+implied geometric correction suggests that an appreciable minority
+(3-30\%) of M dwarfs -- the rapidly rotating ones with centrifugal
+magnetospheres -- have similar circumstellar environments to the CPVs.
 
@@
   \caption{Detailed photometric evolution of TIC 141146667 near the
-  epoch of spectroscopic observation (green). 
-  {\bf Panel a}: Subset of TESS SAP\_FLUX acquired near time of
-  Keck/HIRES observation.
-  TESS downlinked data to the Deep Space Network from BTJD XXX to
-  YYY, and was affected by scattered light from the Earth from BTJD
-  3359.4 to 3360.15.
-  %TODO: VERIFY!  Was it scattered light?  Or a legit flare?
+  epoch of spectroscopic observation (green bar). 
+  {\bf Panel a}: TESS simple aperture photometry acquired
+  near time of Keck/HIRES observation.  The main data gaps were caused
+  by scattered light from the Earth and Moon, respectively.
   {\bf Panels b,c}: Folded light curve before and after spectroscopy.
-  {\bf Panel d}: Zoom-in of Panel a, showing decreasing photometric
-  scatter in the over three days (18 cycles).
+  While some evolution in the detailed light curve morphology occurred
+  between the two epochs, the large, complex eclipse feature remained
+  present.
   }
@@
 
-{\it TESS:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14, 15, 21, 41, 48,
-and 75.  Two-minute data were acquired during Sectors 41, 48 (TESS
-DDT039, PI: M.~Kunimoto), and 75 (TESS Program G06030, PI: L.~Bouma);
-the earlier data had a 30-minute cadence, which significantly
-phase-smears sharp features over a $<$4\,hour period (see
-\cite{Gunther2022}).
-The nearest star in the TESS images, TIC~141146666 ($T$14.5), is 
-25$''$ from TIC~141146667 and does not appear to photometrically vary.
+{\it TESS:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14, 15,
+21, 41, 48, and 75.  Two-minute data were acquired during Sectors
+41, 48 (TESS DDT039, PI: Kunimoto), and 75 (TESS Program G06030, PI:
+Bouma).  The data from Sectors 14, 15, and 21 had a 30-minute
+cadence, which significantly phase-smears sharp features over the
+$<$4\,hour period (see \cite{Gunther2022}).  The nearest known star,
+TIC~141146666 ($T$=14.5), is 25$''$ from TIC~141146667 and based on
+the pixel-level TESS data is photometrically stable.
+
+Figure~\ref{fig:fulllc} shows the simple aperture photometry from
+Sector~75, which were acquired using the camera that points closest
+to the ecliptic.  The largest gap in coverage is from BTJD
+3356.0~-~3358.5, and includes the Keck/HIRES observation epoch
+(green bar).   There are no flux measurements reported during this
+interval because the Earth was within 25$\^circ$ the camera's
+boresight, yielding high levels of scattered light.  From BTJD
+3359.4~-~3362.0, the Moon also passed within 25$^\circ$ of the
+camera's boresight.  Based on the observed level of scattered light
+in the local aperture of TIC~141146667, we therefore manually masked
+out times from 3359.4~-~3360.13, and judged the remainder of the
+data to be usable.  The small data gaps from BTJD 3353.55~-3353.77
+and from BTJD 3360.12~-~3360.33 were caused by data downlinks at the
+spacecraft's perigee and apogee, respectively.
 
 {\it Keck/HIRES:}
-We observed using the standard setup and reduction techniques of the
-California Planet Survey \cite{Howard2010}.
-Winds of 30 mph contributed to
-1\farcs2$\pm$0\farcs2 seeing over the spectroscopic observations.  
-% TODO: mention deblazing 20241115_tic1411_deblazing_notes.txt
+We observed TIC~141146667 ($V$=16.2) with HIRES for five hours over a
+second-half night spanning UT 2024-02-17 10:47 to UT 2024-02-17
+16:13.  The star's airmass over this window spanned $z$=1.2-2.2, and
+we opted for a fixed 15 minute cadence over the entire sequence,
+except for a final 10 minute exposure due to increasing sky
+brightness at sunrise.  We observed without the iodine cell and used
+the C2 decker (0$\farcs$86$\times$14$\farcs$0) in the red instrument
+configuration, yielding a spectral resolution $R$$\approx$45{,}0000
+($\delta v$$\approx$6.7\,\kms; $\delta v / v_{\rm
+eq}$$\approx$0.05).  We binned the CCD readout by a factor of three
+in the spatial dimension, yielding $\approx$1,000 counts (S/N=33)
+per pixel in the continuum at 6500\,\AA, at minimum airmass.  Strong
+winds contributed to 1\farcs2$\pm$0\farcs2 seeing over the night,
+but conditions were otherwise favorable.  We reduced the
+echelleogram to a one-dimensional spectrum using the standard
+techniques of the California Planet Survey \cite{Howard2010}.
+Figure~\ref{fig:spec} shows a small segment of the result without
+any additional processing.
+
+\subsection{Spectroscopic Variability}
+
+The full wavelength coverage spans 3650-7960\,\AA, and variable
+  emission is visible in Balmer lines from $n$=10$\rightarrow$2, Ca[H]
+  and Ca[K], the Mg[I] b triplet, and the 5875 He[I] emission line.
+
+%TODO: add figure showing spectral variability!
 
@@
 {\it Age: No Obvious Association Membership}---Previous work
-  \cite{Bouma2024} has shown that an overwhelming majority of CPVs can
-  be associated with known young moving groups based on their
-  positions and kinematics using probabilistic tools such as
-  BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018}.  TIC~141146667 cannot;
-  based on the current census of these known groups, we calculated its
-  probability of being part of any of these groups using its known
-  three-dimensional galactic position velocity, and it appears to be a
-  field star at $>$99.9\% confidence.  Searching the local vicinity of
-  the star for neighbors with similar projected on-sky velocity (CITE)
-  similarly yields no strong candidates for co-moving stars with
-  tangential velocity differences below 5\,\kms\ that share its
+\cite{Bouma2024} has shown that over 90\% of CPVs are associated with
+known young moving groups based on their positions and kinematics.
+TIC~141146667 is one of the exceptions.  We calculated the probability
+of TIC~141146667 being part of any of the nearby known groups using
+BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018}, and based on that model,
+it appears to be a field star at $>$99.9\% confidence.  Searching the
+local vicinity of the star for neighbors with similar projected on-sky
+velocity \cite{Tofflemire2021} similarly yields no strong candidates
+for co-moving ($\Delta v__{\rm T}$$<$5\,\kms) stars that share its
 isochronal youth.
@@
 this is bc of the blending, and a pEW would show smth small)
+
 % We have K=10.47, d=57pc - > DM ~= 3.78 -> M_K ~= 6.67
@@
 However Figure5 frmo the same work suggests maybe try binning up the spectrum, and then comparing against Bochanski+2007 for a lithium-free template.
+
+Try differential comparison against Barnard's star...
 
@@
 
-\item[Acknowledgments] The author thanks X, Y, Z.
+\item[Acknowledgments]
+  % convos w/
+  % M.~Jardine. (line core sum, explaining flux tubes)
+  % A Weinberger (dissolving rocks)
+  % L Hillenbrand (general?)
+  % line profile analysis by B.~Tofflemire.
+  % CPS group for reduction support.
+  The author thanks X, Y, Z.
   L.G.B. was suported by...

### 2025-01-22 drivers/quality_lc.py
update

@@ -1,0 +1,34 @@
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from astropy.io import fits
+import os
+from os.path import join
+from aesthetic.plot import savefig, set_style
+
+fitsdir = '/Users/luke/Dropbox/proj/cpv/data/photometry/tess'
+fitspath = join(fitsdir, 'tess2024030031500-s0075-0000000141146667-0270-s_lc.fits')
+
+hl = fits.open(fitspath)
+d = hl[1].data
+
+
+plt.close("all")
+
+set_style("science")
+fig, ax = plt.subplots(figsize=(8,6))
+
+ax.scatter(d['TIME'], np.log2(d['QUALITY']), c='k', s=0.5, label='log2(quality)')
+
+ax.scatter(d['TIME'], np.zeros(len(d['TIME']))-4, s=0.5, c='b',
+            label='window fn')
+
+ax.scatter(d['TIME'], d['SAP_FLUX']/np.nanmedian(d['SAP_FLUX']), c='g',
+            s=0.1, label='sap_flux');
+
+ax.scatter(d['TIME'], d['SAP_BKG']/np.nanmedian(d['SAP_BKG'])/40-2, c='k',
+            s=0.2, label='SAP_BKG')
+
+ax.legend(fontsize='x-small')
+
+plt.show();
+
+savefig(fig, 'quality_lc.png')

### 2025-01-22 paper/ms.tex
update

@@
 
-{\it TESS:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14, 15,
-21, 41, 48, and 75.  Two-minute data were acquired during Sectors
-41, 48 (TESS DDT039, PI: Kunimoto), and 75 (TESS Program G06030, PI:
-Bouma).  The data from Sectors 14, 15, and 21 had a 30-minute
-cadence, which significantly phase-smears sharp features over the
-$<$4\,hour period (see \cite{Gunther2022}).  The nearest known star,
-TIC~141146666 ($T$=14.5), is 25$''$ from TIC~141146667 and based on
-the pixel-level TESS data is photometrically stable.
+{\it Photometry:} TESS observed
+TIC~141146667 ($T$=13.3) in Sectors 14, 15, 21, 41, 48, and 75.
+Two-minute data were acquired during Sectors 41, 48 (TESS DDT039,
+PI: Kunimoto), and 75 (TESS Program G06030, PI: Bouma).  The data
+from Sectors 14, 15, and 21 had a 30-minute cadence, which
+smears sharp features over the $<$4\,hour period
+(see \cite{Gunther2022}).  The nearest known star, TIC~141146666
+($T$=14.5), is 25$''$ from TIC~141146667 and is photometrically stable
+in the pixel-level TESS data.
 
-Figure~\ref{fig:fulllc} shows the simple aperture photometry from
-Sector~75, which were acquired using the camera that points closest
-to the ecliptic.  The largest gap in coverage is from BTJD
-3356.0~-~3358.5, and includes the Keck/HIRES observation epoch
-(green bar).   There are no flux measurements reported during this
-interval because the Earth was within 25$\^circ$ the camera's
-boresight, yielding high levels of scattered light.  From BTJD
-3359.4~-~3362.0, the Moon also passed within 25$^\circ$ of the
-camera's boresight.  Based on the observed level of scattered light
-in the local aperture of TIC~141146667, we therefore manually masked
-out times from 3359.4~-~3360.13, and judged the remainder of the
-data to be usable.  The small data gaps from BTJD 3353.55~-3353.77
-and from BTJD 3360.12~-~3360.33 were caused by data downlinks at the
-spacecraft's perigee and apogee, respectively.
+Figure~\ref{fig:fulllc} shows the data from Sector~75, which were
+acquired using the camera that points closest to the ecliptic.  The
+largest gap in coverage is from BTJD 3356.0~-~3358.5, and includes
+the Keck/HIRES observation epoch (green bar).   There are no flux
+measurements reported during this interval because the Earth was
+within 25$^\circ$ the camera's boresight, yielding high levels of
+scattered light.  From BTJD 3359.4~-~3362.0, the Moon then passed
+within 25$^\circ$ of the camera's boresight.  Based on the observed
+level of scattered light in the optimal TIC~141146667 aperture, we
+manually masked out times from 3359.4~-~3360.13, and judged the
+remainder of the data during the lunar approach to be usable.  The
+small data gaps from BTJD 3353.55~-~3353.77 and from BTJD
+3360.12~-~3360.33 were caused by data downlinks at the spacecraft's
+perigee and apogee, respectively.
 
-{\it Keck/HIRES:}
-We observed TIC~141146667 ($V$=16.2) with HIRES for five hours over a
+{\it Spectroscopy:}
+We observed TIC~141146667 ($V$=16.2) with Keck/HIRES for five hours over a
 second-half night spanning UT 2024-02-17 10:47 to UT 2024-02-17
@@
 eq}$$\approx$0.05).  We binned the CCD readout by a factor of three
-in the spatial dimension, yielding $\approx$1,000 counts (S/N=33)
+in the spatial dimension, yielding $\approx$1,000 photons (S/N=33)
 per pixel in the continuum at 6500\,\AA, at minimum airmass.  Strong
@@
 techniques of the California Planet Survey \cite{Howard2010}.
-Figure~\ref{fig:spec} shows a small segment of the result without
-any additional processing.
+Figure~\ref{fig:spec} shows the result in the vicinity of H$\alpha$
+without any additional processing.
 
@@
 
-The full wavelength coverage spans 3650-7960\,\AA, and variable
+The full HIRES coverage spans 3650-7960\,\AA, and variable
   emission is visible in Balmer lines from $n$=10$\rightarrow$2, Ca[H]
@@
 \subsection{Stellar Parameters}
+
+{\it Radial Velocity}---We measured the radial velocities of
+TIC~141146667 using a pipeline that we for rapidly rotating
+stars, including M dwarfs.
+%TODO: describe
+
+Standard precision radial velocity pipelines
+fail on stars like  due to their extreme line broadening.
+
 {\it Age: No Obvious Association Membership}---Previous work
@@
 velocity \cite{Tofflemire2021} similarly yields no strong candidates
-for co-moving ($\Delta v__{\rm T}$$<$5\,\kms) stars that share its
+for co-moving ($\Delta v_{\rm T}$$<$5\,\kms) stars that share its
 isochronal youth.

### 2025-01-22 drivers/quality_lc.py
update

@@ -31,4 +31,4 @@ ax.legend(fontsize='x-small')
 
 plt.show();
 
-savefig(fig, 'quality_lc.png')
+savefig(fig, 'results/quality_lc.png')

### 2025-01-24 paper/ms.tex
update

@@
     TIC & 141146667 & TESS \\
-    Gaia & todo & Gaia\ DR3 \\
+    Gaia & 860453786736413568 & Gaia\ DR3 \\
     %2MASS & J04154278+2909597 & J04154269+2909558 & 2MASS \\
@@
     $\delta$ & todo & Gaia\ DR3 \\
-    $\mu_{\alpha}$ (mas yr$^{-1}$ ) & todo & Gaia\ DR3 \\
-    $\mu_{\delta}$ (mas yr$^{-1}$ ) & todo & Gaia\ DR3 \\
-    $\pi$ (mas) & todo & Gaia\ DR3 \\
+    $\mu_{\alpha}$ (mas yr$^{-1}$ ) & -73.933 $\pm$ 0.022 & Gaia\ DR3 \\
+    $\mu_{\delta}$ (mas yr$^{-1}$ ) &  32.262 $\pm$ 0.024 & Gaia\ DR3 \\
+    $\pi$ (mas)                     &  17.324 $\pm$ 0.025 & Gaia\ DR3 \\
+    RUWE                            &  1.23               & Gaia\ DR3 \\
     \hline
@@
     $TESS$ (mag) & todo & TESS\ \\
-    $G$ (mag) & todo & Gaia\ DR3 \\
-    $G_{\rm BP}$ (mag) & todo & Gaia\ DR3\\
-    $G_{\rm RP}$ (mag) & todo & Gaia\ DR3\\
-    $J$ (mag) & todo & 2MASS\\
-    $H$ (mag) & todo & 2MASS\\
-    $K_s$ (mag) & todo & 2MASS\\
-    $W1$ (mag) & todo & ALLWISE \\
-    $W2$ (mag) & todo & ALLWISE \\
-    $W3$ (mag) & todo & ALLWISE \\
-    $W4$ (mag) & todo & ALLWISE \\
+    $G$ (mag)                       & 14.701 $\pm$ 0.002 & Gaia\ DR3 \\
+    $G_{\rm BP}$ (mag)              & 16.664 $\pm$ 0.008 & Gaia\ DR3 \\
+    $G_{\rm RP}$ (mag)              & 13.398 $\pm$ 0.006 & Gaia\ DR3 \\
+    $G_{\rm BP}$-$G_{\rm RP}$ (mag) &  3.276 $\pm$ 0.010 & Gaia\ DR3 \\
+    $J$ (mag)                       & 11.401 $\pm$ 0.022 & 2MASS     \\
+    $H$ (mag)                       & 10.793 $\pm$ 0.021 & 2MASS     \\
+    $K_s$ (mag)                     & 10.473 $\pm$ 0.016 & 2MASS     \\
+    $W1$ (mag)                      & 10.276 $\pm$ 0.023 & ALLWISE   \\ % Cutri+2013 II/328/allwise
+    $W2$ (mag)                      & 10.070 $\pm$ 0.020 & ALLWISE   \\
+    $W3$ (mag)                      &  9.838 $\pm$ 0.045 & ALLWISE   \\
+    %$W4$ (mag)                      &  8.392 $\pm$ NOUNC & ALLWISE \\
+	  %
+    %TODO: eROSITA?  ROSAT is an emitter.  GALEX detection.
+    % Ofek+2011 1.4Ghz emitter.  Helfand+2015 ditto.  Bruzewski+2021.
     \hline
@@
     \hline
-    $RV_{Bary}$ (km s$^{-1}$ ) & $13.35 \pm 3.39$ & Gaia\ DR3 \\
+    $RV_{Bary}$ (km s$^{-1}$ ) & $13.35 \pm 3.39$ & HIRES \\
     $U$ (km s$^{-1}$ ) & & \\
@@
     $W$ (km s$^{-1}$ ) & & \\
-    $X$ (pc)  & & \\
-    $Y$ (pc)  & & \\
-    $Z$ (pc) & & \\
+    $X$ (pc) & -28.4 & \\
+    $Y$ (pc) &  19.8 & \\
+    $Z$ (pc) &  67.0 & \\
     \hline
@@
     $i_\star$($^\circ$) & todo & This work \\
+    $T_{eff}$ (K) & 2972 $\pm$ 40 & \cite{Bouma2024}\\
+%$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & YYY              & X \\
+%
+    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & \cite{Bouma2024} \\
+    $A_V$ (mag) & 0 & \cite{Green2019} \\
     $F_{bol}$ (erg cm$^{-2}$ s$^{-1}$ ) & todo & This work\\
-    $T_{eff}$ (K) & todo & This work\\
-    $A_V$ (mag) & todo & This work \\
-    $R_\star$ ($R_{\odot}$) & todo & This work\\
     $L_\star$ ($L_{\odot}$)  & todo & This work\\
     $M_\star$ ($M_{\odot}$)  & todo & This work\\
-    Age (Myr) & todo &  This work \\
+    $t_{\rm iso}$ (Myr) & $16^{+19}_{-6}$ &  This work \\
     \hline
@@
 \end{table}
-
 \end{methods}

### 2025-01-26 paper/ms.tex
update

@@
 %
-% TODO: this value is a quicklook from calc_hires_systemic_velocities.py, rj537.166.fits.  should average over whole timeseries.
-$\gamma$\dotfill                       & Systemic radial velocity (\kms)\dotfill                         & 2.2 $\pm$ 0.9  & 1  \\
+$\gamma$\dotfill                        & Systemic radial velocity (\kms)\dotfill                        & 0.61 $\pm$ 1.47  & 1  \\
 %
@@
 
-{\it Radial Velocity}---We measured the radial velocities of
-TIC~141146667 using a pipeline that we for rapidly rotating
-stars, including M dwarfs.
-%TODO: describe
+{\it Radial Velocity}---We measured radial velocities of
+TIC~141146667 from each of our spectra using a pipeline that we
+developed specifically for rapidly rotating stars.
+Our method is based on template-matching against synthetic spectra
+produced by the PHOENIX stellar atmosphere code \cite{Husser2013}.
+We used the PHOENIX models with solar metallicity and alpha element
+abundances, and calibrated our absolute velocity zero-points as well
+as viable orders for velocity measurement using the
+standard stars described by \cite{Chubak2012}.
+We used velocity standards spanning spectral types from G2 to M4 (Barnard's
+Star), irrespective of rotation rate.
+We used \texttt{barycorrpy} \cite{Kanodia2018} to calculate the
+velocity corrections due to Earth's motion around the solar system
+barycenter and due to Earth's daily rotation about its axis.
+Our analysis pipeline reproduces the systemic velocities reported by
+\cite{Chubak2012} for their velocity standards with an RMS of
+0.66\,\kms.
 
-Standard precision radial velocity pipelines
-fail on stars like  due to their extreme line broadening.
+For TIC~141146667, we measured the velocities from each of our HIRES
+spectra using regions near the K~I (7700\,\AA) resonance line and
+three TiO bandheads (5160\,\AA, 5450\,\AA, and 5600\,\AA).  These
+regions were selected because they provided
+the best matches between the synthetic and observed spectra.  The
+resulting
+redshift measurements were averaged together.
+The star's 130$\pm$4\,\kms\ equatorial velocity and near-edge on
+viewing orientation yielded a line broadening $\Delta
+\lambda$$\approx$3\,\AA.
+We used the scatter of resulting velocity measurements between 
+orders to assign the RV uncertainty at each epoch.
+The uncertainty-weighted mean systemic velocity over all epochs on UT
+2024-02-17 was
+$\gamma$=0.6$\pm$1.5\,\kms.
+The relative radial velocities about this mean are given in
+Table~\ref{tab:rv}.
+% from calc_max_amplitude_sinusoid_rv_timeseries.py
+This radial velocity time-series rules out any significant periodicity
+in the radial velocities at the rotation period exceeding
+semi-amplitudes of 2.85\,\kms\ (at 3$\sigma$ confidence).
+% from K_to_msini.py, assuming Mstar = 0.18
+This in turn sets an upper limit on the mass of any putative
+companions at this period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.
 
@@
     $RV_{Bary}$ (km s$^{-1}$ ) & $13.35 \pm 3.39$ & HIRES \\
-    $U$ (km s$^{-1}$ ) & & \\
-    $V$ (km s$^{-1}$ ) & & \\
-    $W$ (km s$^{-1}$ ) & & \\
+    $U$ (\kms) & & \\
+    $V$ (\kms) & & \\
+    $W$ (\kms) & & \\
     $X$ (pc) & -28.4 & \\
@@
     %$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & YYY              & X \\
-%
     $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & \cite{Bouma2024} \\
@@
 \end{table}
+
+\begin{table}
+  \centering
+  \begin{tabular}{lcr}
+  %\setlength{\tabcolsep}{2pt}
+  \hline 
+  \hline 
+  Time [JD$_{\rm UTC}$] & RV (\kms) & $\sigma_{\rm RV}$ (\kms) \\
+  % from tables/tab_TIC141146667_rel_rv.tex
+  \hline 
+  60357.450329 & 1.72 & 5.86 \\
+  60357.461255 & -5.41 & 2.37 \\
+  60357.472181 & -1.21 & 2.64 \\
+  60357.483109 & 2.83 & 2.87 \\
+  60357.494030 & 6.52 & 7.53 \\
+  60357.504949 & -3.0 & 1.44 \\
+  60357.515873 & 0.01 & 1.21 \\
+  60357.526794 & -0.38 & 7.03 \\
+  60357.537717 & -3.92 & 2.71 \\
+  60357.548639 & 7.92 & 6.75 \\
+  60357.559566 & 4.94 & 8.84 \\
+  60357.570487 & -3.26 & 3.06 \\
+  60357.581408 & 0.83 & 1.34 \\
+  60357.592330 & 1.4 & 8.24 \\
+  60357.603251 & -8.05 & 3.94 \\
+  60357.614172 & -3.26 & 3.07 \\
+  60357.625095 & -3.84 & 7.55 \\
+  60357.636019 & -1.6 & 2.26 \\
+  60357.646940 & 0.82 & 2.91 \\
+  60357.657861 & 3.53 & 3.95 \\
+  60357.668781 & 5.2 & 12.14 \\
+  \hline
+  \end{tabular}
+  \caption{TIC~141146667 radial velocities.}
+  \label{tab:rv}
+\end{table}
+
 \end{methods}

### 2025-01-26 paper/ms.tex
update

@@
   \includegraphics[width=0.99\textwidth]{figures/sf1.pdf}
-  \caption{Detailed photometric evolution of TIC 141146667 near the
-  epoch of spectroscopic observation (green bar). 
-  {\bf Panel a}: TESS simple aperture photometry acquired
-  near time of Keck/HIRES observation.  The main data gaps were caused
-  by scattered light from the Earth and Moon, respectively.
+  \caption{Photometric evolution of TIC 141146667 near the epoch of
+  spectroscopic observation (green bar). 
+  {\bf Panel a}: TESS simple aperture photometry. 
+  The main data gaps were caused by scattered light from the Earth
+  (BTJD 3356-3358.5) and Moon (BTJD 3359.5-3360.5).
   {\bf Panels b,c}: Folded light curve before and after spectroscopy.
-  While some evolution in the detailed light curve morphology occurred
-  between the two epochs, the large, complex eclipse feature remained
-  present.
+  While some evolution in the light curve morphology occurred between
+  the two epochs, the large, complex eclipse feature remained present.
   }
@@
 three TiO bandheads (5160\,\AA, 5450\,\AA, and 5600\,\AA).  These
-regions were selected because they provided
-the best matches between the synthetic and observed spectra.  The
-resulting
-redshift measurements were averaged together.
-The star's 130$\pm$4\,\kms\ equatorial velocity and near-edge on
-viewing orientation yielded a line broadening $\Delta
-\lambda$$\approx$3\,\AA.
-We used the scatter of resulting velocity measurements between 
-orders to assign the RV uncertainty at each epoch.
-The uncertainty-weighted mean systemic velocity over all epochs on UT
-2024-02-17 was
-$\gamma$=0.6$\pm$1.5\,\kms.
-The relative radial velocities about this mean are given in
-Table~\ref{tab:rv}.
+regions were selected because they provided the best matches between
+the synthetic and observed spectra.  The resulting redshift
+measurements were averaged together.  The star's 130$\pm$4\,\kms\
+equatorial velocity and near-edge on viewing orientation yielded a
+line broadening $\Delta \lambda$$\approx$3\,\AA.  We used the scatter
+of resulting velocity measurements between orders to assign the RV
+uncertainty at each epoch.  The uncertainty-weighted mean systemic
+velocity over all epochs on UT 2024-02-17 was
+$\gamma$=0.6$\pm$1.5\,\kms.  The relative radial velocities about this
+mean are given in Table~\ref{tab:rv}.
 % from calc_max_amplitude_sinusoid_rv_timeseries.py
@@
 {\it Age: No Obvious Association Membership}---Previous work
-\cite{Bouma2024} has shown that over 90\% of CPVs are associated with
+\cite{Bouma2024} has found over 90\% of CPVs to be associated with
 known young moving groups based on their positions and kinematics.
@@
 of TIC~141146667 being part of any of the nearby known groups using
-BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018}, and based on that model,
+BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  Based on that model,
 it appears to be a field star at $>$99.9\% confidence.  Searching the
@@
 velocity \cite{Tofflemire2021} similarly yields no strong candidates
-for co-moving ($\Delta v_{\rm T}$$<$5\,\kms) stars that share its
-isochronal youth.
+for co-moving stars --- defined as those with projected tangential
+velocities $\Delta v_{\rm T}$$<$5\,\kms --- that share its isochronal
+youth.
 

### 2025-01-26 paper/ms.tex
update

@@
 
-\subsection{Observations \& Data Reduction}
+\subsection{Observations \& Data Reduction}\phantom{+}
 
@@
 
-\subsection{Spectroscopic Variability}
-
-The full HIRES coverage spans 3650-7960\,\AA, and variable
-  emission is visible in Balmer lines from $n$=10$\rightarrow$2, Ca[H]
-  and Ca[K], the Mg[I] b triplet, and the 5875 He[I] emission line.
-
-%TODO: add figure showing spectral variability!
-
-\subsection{Stellar Parameters}
+\subsection{Stellar Parameters}\phantom{+}
 
@@
 % from calc_max_amplitude_sinusoid_rv_timeseries.py
-This radial velocity time-series rules out any significant periodicity
-in the radial velocities at the rotation period exceeding
-semi-amplitudes of 2.85\,\kms\ (at 3$\sigma$ confidence).
 % from K_to_msini.py, assuming Mstar = 0.18
-This in turn sets an upper limit on the mass of any putative
-companions at this period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.
+
+{\it No Evidence For Binarity}---Any significant periodicity in the
+radial velocity time-series is ruled out at the rotation period for
+semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This
+sets an upper limit on the mass of any putative companions at the four
+hour period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
+companions at wider separations, the Gaia DR3 renormalized unit weight
+error (RUWE), a proxy for the goodness of fit for a single-source
+astrometric model to the Gaia astrometry, is 1.23, which is within the
+usual range for apparently single sources.  There are no resolved
+sources in the Gaia DR3 point source catalog.  Finally, we checked the
+TESS light curve for evidence of secondary photometric periods by
+subtracting the mean CPV signal over each sector and performing a
+phase-dispersion minimization analysis
+\cite{Stellingwerf1978,2021zndo...1011188B}.  There were no secondary
+periods in the TESS data.  Previous work \cite{Bouma2024} has shown
+that about 30\% of CPVs show evidence for excess noise above the Gaia
+single-source astrometric model, and about 40\% of CPVs show evidence
+for unresolved binary companions based on the presence of secondary
+photometric periods.  This agrees with analyses showing that
+multi-periodic low-mass stars are generally unresolved binaries
+\cite{Tokovinin2018}.  Overall, the CPV binary fraction seems
+consistent with that for field M dwarfs \cite{Winters2019},
+pointing to a weak or non-existent connection between the CPV
+phenomenon and binarity.  For TIC~141146667 specifically, we find 
+no evidence for stellar multiplicity.
 
 {\it Age: No Obvious Association Membership}---Previous work
-\cite{Bouma2024} has found over 90\% of CPVs to be associated with
+\cite{Bouma2024} has found that over 90\% of CPVs are associated with
 known young moving groups based on their positions and kinematics.
@@
 BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  Based on that model,
-it appears to be a field star at $>$99.9\% confidence.  Searching the
-local vicinity of the star for neighbors with similar projected on-sky
-velocity \cite{Tofflemire2021} similarly yields no strong candidates
-for co-moving stars --- defined as those with projected tangential
-velocities $\Delta v_{\rm T}$$<$5\,\kms --- that share its isochronal
-youth.
+it appears to be a field star at $>$99.9\% confidence.  We also searched the
+local vicinity of TIC~141146667 for neighbors with similar projected on-sky
+velocities using \texttt{comove} \cite{Tofflemire2021}.  This yielded
+no strong candidates for co-moving stars --- defined as those with
+projected tangential velocities $\Delta v_{\rm T}$$<$5\,\kms ---
+that share its isochronal youth.
 
-{\it Age: Isochrones}--- $\sim$TucHor or younger.  Maybe 30-35myr?  NB
-  color puts it at ~M4.5 (main seq).  BP-RP=3.3..
-    % uhhh careful w what you mean by "isochrone"
+{\it Age: Isochrones}---The color and absolute magnitude of
+TIC~141146667 suggest that it is a pre-main-sequence M dwarf, similar
+to all other known CPVs \cite{Stauffer2017,Stauffer2021,Bouma2024}.
+The star's proximity ($d$=58\,pc) and its high galactic latitude
+($b$=$+$53$^\circ$) yield negligible interstellar reddening along the
+line of sight \cite{Green2019}.
+{\bf Figure~X} shows the location of the star in the color--absolute
+magnitude diagram (CAMD)
+relative to young stellar populations including Upper Scorpius (USco),
+Upper-Centaurus-Lupus (UCL), IC~2602, and the Pleiades.
+To make this diagram, {\bf TODO}we adopted the USco and UCL members
+from X, the IC~2602 members from Y, and the Pleiades members from Z,
+and applied the same reddening corrections as in \cite{Bouma2022}.
+To measure the isochrone age of TIC~141146667, we then followed the 
+empirical approach proposed by \cite{Gagne2020} and
+implemented in \cite{Bouma2022}.
+The idea is to estimate the star (or star cluster's) age by
+interpolating between the observed isochrones of star clusters with
+ages that have been otherwise calibrated, for instance using
+the lithium depletion-boundary method.
+While this circumvents known modelling issues in molecular opacities
+and starspot coverage for young M dwarfs,
+the ages returned by this procedure depend on the ages
+assumed for each reference cluster.
+In this case, the most important reference is UCL, since TIC~141146667
+overlaps directly on its isochrone on the CAMD.
+We adopted the 16~Myr age for UCL from \cite{PecautMamajek2016}, which
+is consistent with ages determined by more recent sub-clustering
+analyses \cite{Ratzenbock2023} for the largest sub-populations.
+This in turns yields an isochronal age for TIC~141146667 of
+$t_{\rm iso}$=$16^{+19}_{-6}$\,Myr.
+Qualitatively, this range of uncertainty is consistent with no stars
+in the $\approx$40\,Myr IC~2602 cluster with similar redness as
+TIC~141146667 being equally bright.
 
@@
 this is bc of the blending, and a pEW would show smth small)
+%TODO TODO TODO
 
@@
 
-This is weird.  Are you 100\% sure it's not a binary?  Ups the need for
-the RV analysis.
+{\it Age: Summary}---The main indicators for the youth of
+TIC~141146667 are {\it i)} that it is a complex periodic variable;
+{\it ii)} that it is 1.5 magnitudes brighter than main sequence stars
+of the same color, while showing no indicators for binarity; {\it
+iii)} weak lithium absorption.
 
@@
 
-{\it Binarity}
+\subsection{Spectroscopic Variability}\phantom{+}
+
+The full HIRES coverage spans 3650-7960\,\AA, and variable
+  emission is visible in Balmer lines from $n$=10$\rightarrow$2, Ca[H]
+  and Ca[K], the Mg[I] b triplet, and the 5875 He[I] emission line.
+
+%TODO: add figure showing spectral variability!
 

### 2025-01-27 paper/ms.tex
update

@@
 transiting clumps of opaque material corotating with the star
-\cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.
-The composition, origin, and even the existence of this material are
-uncertain. The main alternative hypothesis is that these stars are
-explained by complex distributions of dark starspots or bright
-faculae distributed across their surfaces \cite{Koen2021}.  Here, we
-present time-series spectroscopy and photometry of a \stagemyr\
-million year old complex periodic variable (CPV), TIC~141146667. The
-spectra show coherent sinusoidal Balmer emission at up to four times
-the star's equatorial velocity, demonstrating the presence of
-extended clumps of circumstellar plasma --- a plasma torus.  Given
-that long-lived condensations of cool ($10^4$ K) plasma can persist
-in the hot ($10^6$ K) coronae of stars with a wide range of masses
+\cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.  The
+composition, origin, and even the existence of this material are
+uncertain. The main alternative hypothesis is that these complex
+periodic variables (CPVs) are explained by complex distributions of
+dark starspots or bright faculae distributed across the stellar surfaces
+\cite{Koen2021}.  Here, we present time-series spectroscopy and
+photometry of a young ($t$=16\,Myr), rapidly-rotating
+($P$=3.9\,hr) CPV, TIC~141146667. The spectra show coherent
+sinusoidal Balmer emission at up to four times the star's equatorial
+velocity, demonstrating the presence of extended clumps of
+circumstellar plasma --- a plasma torus.  Given that long-lived
+condensations of cool ($10^4$ K) plasma can persist in the hot
+($10^6$ K) coronae of stars with a wide range of masses
 \cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
@@
 interest in this article, but over one hundred analogous objects have
-now been discovered by K2 and TESS 
+now been found by K2 and TESS 
 \cite{Rebull2016,Stauffer2017,Rebull2018,Zhan2019,Rebull2020,Bouma2024}.
@@
 sharpest photometric features.  However, no independent evidence has
-yet been acquired for the presence of circumstellar material in these
+yet been acquired for the presence of circumstellar material around these
 objects.  Since transiting circumstellar clumps would geometrically
@@
 \cite{Townsend2005}, whereas in the limit of a single strong field
-line, accumulation occurs along the apexpoint furthest from the star
+line, accumulation occurs at the line's apex, furthest from the star
 \cite{Waugh2022}.
@@
 photometric anomalies \cite{Bouma2024}, leaving open the issue of
-whether these two areas of study have any direct connection.
-Nonetheless, CPVs do respond to sudden magnetic field changes: the
-otherwise long-lived eclipse features often disappear immediately
-following stellar flares \cite{Stauffer2017,Bouma2024}.
+whether they are related to CPVs.
+A circumstantial argument that they might is that CPVs do respond to
+sudden magnetic field changes: the otherwise long-lived eclipse
+features often disappear following stellar flares
+\cite{Stauffer2017,Bouma2024}.
 
@@
 % photometry
-Figure~\ref{fig:spec} shows the data from February 2024.  As expected
-based on other CPVs \cite{Bouma2024}, the photometric shape of
+Figure~\ref{fig:spec} shows the data from February 2024.  Similar to
+other CPVs \cite{Bouma2024}, the photometric shape of
 TIC~141146667 evolved following the 2022 discovery
@@
 sharp transient absorption features in their line cores
-\cite{CollierCameron1989,CollierCameron1992,Cang2020} similar to those
-in Figure~\ref{fig:spec}.  No such stars were previously known to show
+\cite{CollierCameron1989,CollierCameron1992,Cang2020} similar to 
+Figure~\ref{fig:spec}.  No such stars were previously known to show
 complex light curves \cite{Bouma2024}.  The usual interpretation for
 such variability comes from a loose analogy to
-quiescent solar prominences and filaments, which are cool
+quiescent solar prominences, which are cool
 condensations of plasma in the solar corona that can last days to
-weeks \cite{VialEngvold2015}.  This plasma is called a prominence when
-viewed in emission against the dark backdrop of space, and a filament
-when viewed in absorption against the solar disk.  In our Sun's
+weeks \cite{VialEngvold2015}.
+In our Sun's
 magnetosphere, these condensations fall back to the solar surface
@@
 
-Our Keck/HIRES observations are the first high-resolution time-series
+Our Keck/HIRES observations are the first reported time-series
 spectra of a CPV, and they show that corotating circumstellar plasma clumps 
@@
 spectrophotometry.  While observations of CPVs in the optical have
-previously shown chromaticity consistent with dust \cite{Tanimoto2020,Gunther2022,Koen2023},
+previously suggested chromaticity consistent with dust \cite{Tanimoto2020,Gunther2022,Koen2023},
 a gray opacity source such as electron scattering in a plasma
@@
 Observationally, spectropolarimetry has the potential to
-assess both the field strength and topology.  A more direct probe
-however might be to connected the recent work \cite{Kaur2024} showing
-that CPVs are variable radio emitters, exhibiting emission components
-that can be both persistent, as well as short-lived and highly
-polarized.  This opens the prospects for detecting radio emission
-from the electron cyclotron maser instability, which would
+assess both the field strength and topology.  An independent
+probe could also be connected the recent work \cite{Kaur2024} showing
+that CPVs are variable radio emitters with emission components
+that can be both persistent, and also short-lived and highly
+polarized.  In particular, detecting radio emission
+from the electron cyclotron maser instability would
 provide a direct measurement of the field strength at the site of the
@@
   $W1$ and $W2$.  (explain)...
+
 %%%%%%%%
@@
 %0.01$, where $\mathcal{Z}$ denotes the evidence.
+
+{\it SED: No evidence for disk}
+...
 

### 2025-03-10 paper/ms.tex
update

@@
 \normalfont
-% v1: removed a sentence for wordcount.  v0 is under abstract_title.txt
 Approximately one percent of red dwarfs younger than 100 million years
 show structured, periodic optical light curves suggestive of
-transiting clumps of opaque material corotating with the star
+transiting opaque material corotating with the star
 \cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.  The
@@
 periodic variables (CPVs) are explained by complex distributions of
-dark starspots or bright faculae distributed across the stellar surfaces
+starspots or faculae distributed across the stellar surfaces
 \cite{Koen2021}.  Here, we present time-series spectroscopy and
-photometry of a young ($t$=16\,Myr), rapidly-rotating
-($P$=3.9\,hr) CPV, TIC~141146667. The spectra show coherent
-sinusoidal Balmer emission at up to four times the star's equatorial
-velocity, demonstrating the presence of extended clumps of
-circumstellar plasma --- a plasma torus.  Given that long-lived
-condensations of cool ($10^4$ K) plasma can persist in the hot
-($10^6$ K) coronae of stars with a wide range of masses
+photometry of a young ($t$=16\,Myr), rapidly-rotating ($P$=3.9\,hr)
+CPV, TIC~141146667. The spectra show coherent sinusoidal Balmer
+emission at twice to four times the star's equatorial velocity,
+demonstrating the presence of extended clumps of circumstellar
+plasma --- a plasma torus.  Given that long-lived condensations of
+cool ($10^4$ K) plasma can persist in the hot ($10^6$ K) coronae of
+stars with a wide range of masses
 \cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
-these data support the idea that such condensations can become
-optically thick around the lowest-mass stars, although the exact
-source of opacity remains unclear.
+these data support the idea that around the lowest-mass stars, such
+condensations can be optically thick; the exact origin of the
+material and its microphysical opacity remain unclear.
 \end{abstract}
@@
 only type of star to offer near-term prospects for detecting the
-atmospheres of rocky exoplanets with water on their surfaces
+atmospheres of rocky exoplanets with surface water
 \cite{NAP26141}.  Investment with JWST has proceeded accordingly.  How
@@
 coronal mass ejections \cite{Gunther2020}.  Nevertheless, despite excellent
-work in these areas, the properties of the circumstellar plasma and
-magnetospheric environments that bathe young, close-in exoplanets have
-remained challenging to quantify.
+work in these areas, the properties of the plasma and magnetospheric
+environments that bathe young, close-in exoplanets have remained
+challenging to quantify.
 
@@
 These CPVs are
-defined by their highly structured and periodic optical light curves, 
-and most are M dwarfs with rotation periods shorter than two days.
+phenomenologically identified based on their highly structured and
+periodic optical light curves;
+most are M dwarfs with rotation periods shorter than two days.
 Within current sensitivity limits, none have primordial disks
@@
 yet been acquired for the presence of circumstellar material around these
-objects.  Since transiting circumstellar clumps would geometrically
-imply an intrinsic occurrence a few to ten times the observed rate,
-the question of whether circumstellar clumps exist in these systems
-has the potential to be applicable to 10-30\% of M dwarfs during their
-early lives.
+objects.  
+Transiting circumstellar clumps would geometrically imply an intrinsic
+occurrence a few to ten times the observed rate.  The question of
+whether circumstellar clumps exist in these systems could therefore be
+relevnat for 10-30\% of M dwarfs during their early lives.
 
@@
 The dearth of evidence for circumstellar material around CPVs is
-surprising given that separate studies of young BAFGKM stars have, for
+surprising given that separate studies of young stars have, for
 decades, reported that stellar coronae contain both hot ($10^6$ K) and
-cool ($10^4$ K) plasma. In particular, time-series spectroscopy has
-shown periodic high-velocity absorption and emission in Balmer lines
-such as H$\alpha$, caused by long-lived, corotating clumps of cool
-plasma \cite{CollierCameron1989,Donati2000,Dunstone2006,Skelly2008}.
+cool ($10^4$ K) plasma. In particular, time-series spectroscopy for
+stars with a wide range of masses has shown periodic high-velocity
+absorption and emission in Balmer lines such as H$\alpha$, interpreted
+as long-lived, corotating clumps of cool plasma
+\cite{CollierCameron1989,Donati2000,Dunstone2006,Skelly2008}.
 Such clumps are forced into corotation by the magnetic field, and the
 exact geometry of where the plasma can accumulate is dictated by the
-magnetic field's topology.  For instance, a tilted dipole field tends
+field's topology.  For instance, a tilted dipole field tends
 to yield an accumulation surface of a warped torus
@@
 \cite{Waugh2022}.
-However, none of these spectroscopic variables have shown any
+To date, none of these spectroscopic variables have shown any
 photometric anomalies \cite{Bouma2024}, leaving open the issue of
 whether they are related to CPVs.
-A circumstantial argument that they might is that CPVs do respond to
-sudden magnetic field changes: the otherwise long-lived eclipse
-features often disappear following stellar flares
-\cite{Stauffer2017,Bouma2024}.
+%A circumstantial argument that they might is that CPVs do respond to
+%sudden magnetic field changes: the otherwise long-lived eclipse
+%features often disappear following stellar flares
+%\cite{Stauffer2017,Bouma2024}.
 
@@
 brightness and rapid rotation offered sensitivity to small variations
-in the line profiles.  We observed it for five hours on UT 2024-02-17
+in the line profiles.  We observed for five hours on UT 2024-02-17
 using the High Resolution Echelle Spectrometer (HIRES;
@@
 the star from UT 2024-02-05 to UT 2024-02-26 with a duty cycle of
-XX\%.  TESS was finishing a data downlink during the spectral
-observations, and photometric data collection resumed three rotation
+XX\%.  
+At the exact instant of spectral observations, TESS was performing a
+data downlink; photometric data collection resumed three rotation
 cycles (12 hours) after the spectra were acquired.  Extended Data
 Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
-star before and after the exact epoch of observation; the star
-remained sufficiently stable to not affect the interpretation that
-follows.
+star before and after the exact epoch of observation; the photometric
+morphology is similar before and after the data gap.
 
@@
 % photometry
-Figure~\ref{fig:spec} shows the data from February 2024.  Similar to
-other CPVs \cite{Bouma2024}, the photometric shape of
-TIC~141146667 evolved following the 2022 discovery
-data, while nonetheless remaining complex.  In February 2024, the
-average photometric signal showed a gradual brightening over 45\% of
-the period, followed by a complex eclipse-like feature spanning 55\%
-of the period.  This eclipse feature shows two to three
-local photometric minima, and one to two local maxima.
-Its W-shape is suggestive of eclipse geometries seen in forward models
-of warped plasma tori \cite{Townsend2008}.
+Figure~\ref{fig:spec} shows the data from February 2024.  Over
+timescales of years, CPVs maintain the same period, while their
+photometric morphology evolves.  TIC~141146667 indeed evolved relative
+to the February 2022 discovery data \cite{Bouma2024}.  In the February
+2024 data, the average photometric signal showed a small brightening
+over 45\% of the period, followed by a complex flux dip spanning 55\%
+of the period.  This eclipse feature shows two to three local
+photometric minima, and one to two local maxima.  Its W-shape is
+suggestive of eclipse geometries seen in some forward models of warped
+plasma tori \cite{Townsend2008}.
 
@@
 velocity ($v_{\rm eq}$=130\,\kms).  There are at least two distinct
-emission components, separated by half a cycle in phase.  The
-first component has clearer sinusoidal behaviour and is double-peaked, with peak
-semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
+emission components, separated by half a cycle in phase.  The first
+component has clearer sinusoidal behaviour and is double-peaked, with
+peak semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
 There is significant non-periodic variability in this double-peaked
@@
 beginning of the observation sequence to a 10\% excess by its end.
-The sinusoidal period for all of these emission components is consistent
-with the photometric \periodhr\ hour period.
+The sinusoidal period for all of these emission components is
+consistent with the photometric \periodhr\ hour period.
 
 These sinusoidal emission features require circumstellar clumps of
-partially-ionized hydrogen to be corotating with the star.  The
-velocity semi-amplitude of the sinusoids gives the distance
-of these clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
-closer clump, and 3.9\,$R_\star$ for the other.  This material's
-motion, rather than being Keplerian, can only be explained by plasma
-being dragged along with the rotating stellar magnetic field.  These
-clumps transit in front of the star when passing from negative to
-positive velocity.
+partially-ionized hydrogen to be corotating with the star.  
+Based on its period, this material's motion is not Keplerian; it can
+only be explained by plasma being dragged along with the rotating
+stellar magnetic field. 
+The velocity semi-amplitude of the sinusoids then gives the distance
+of the clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
+closer clump, and 3.9\,$R_\star$ for the other.   These clumps transit
+in front of the star when passing from negative to positive velocity.
+This implies that the spectroscopic transit of the 2.1-2.7\,$R_\star$
+clump occurs simultaneously with the sharp photometric spike visible
+in the TESS data.
 
@@
 broadband variability, except at $\phi$=0.5, during the transit of the
-higher-velocity clump and the occultation of the lower-velocity clump.
+3.9\,$R_\star$ clump and the occultation of the lower-velocity clump.
 
@@
 \cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} as well as
-sharp transient absorption features in their line cores
+transient absorption features in their line cores
 \cite{CollierCameron1989,CollierCameron1992,Cang2020} similar to 
@@
 complex light curves \cite{Bouma2024}.  The usual interpretation for
-such variability comes from a loose analogy to
+such spectroscopic variability comes from an analogy to
 quiescent solar prominences, which are cool
@@
 radii $R_{\rm m}$ that exceed their corotation radii $R_{\rm c}$, the
-effective potential experienced by a plasma parcel can have a local minimum
+effective potential experienced by a charged particle can have a local minimum
 outside $R_{\rm c}$, enabling the material to be sustained for
@@
 Characteristic densities and masses of these
+%TODO check; quote N_H instead...
 clumps are $n \sim 10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see
@@
 The other potential analog for the CPVs are the $\sigma$~Ori~E
-variables, a rare subset of B stars that with radiatively-driven winds
-that can accumulate into
+variables, a rare subset of B stars with radiatively-driven winds
+that accumulate into
 warped plasma tori \cite{Townsend2005,Townsend2008}.  These tori tend
@@
 In particular, dynamo simulations of fully-convective M dwarfs have
-suggested the possibility that global-scale mean fields can be
+suggested that global-scale mean fields might be
 confined to a single hemisphere \cite{Brown2020}; such fields would
@@
 that can be both persistent, and also short-lived and highly
-polarized.  In particular, detecting radio emission
-from the electron cyclotron maser instability would
-provide a direct measurement of the field strength at the site of the
-emitting region.
+polarized.  In particular, detecting radio emission produced by an electron
+cyclotron maser instability would provide a measurement of the field
+strength at the site of the emitting region.
 
@@
 implied geometric correction suggests that an appreciable minority
-(3-30\%) of M dwarfs -- the rapidly rotating ones with centrifugal
-magnetospheres -- have similar circumstellar environments to the CPVs.
+(10-30\%) of young M dwarfs -- the rapidly rotating ones with
+centrifugal magnetospheres -- host similar circumstellar environments
+to the CPVs.
 
@@
   {\bf Panels b,c}: Folded light curve before and after spectroscopy.
-  While some evolution in the light curve morphology occurred between
+  Although some evolution in the light curve morphology occurred between
   the two epochs, the large, complex eclipse feature remained present.
@@
 Figure~\ref{fig:fulllc} shows the data from Sector~75, which were
-acquired using the camera that points closest to the ecliptic.  The
+acquired using the camera that pointed closest to the ecliptic.  The
 largest gap in coverage is from BTJD 3356.0~-~3358.5, and includes
@@
 level of scattered light in the optimal TIC~141146667 aperture, we
-manually masked out times from 3359.4~-~3360.13, and judged the
+manually masked out times from 3359.40~-~3360.13, and judged the
 remainder of the data during the lunar approach to be usable.  The
@@
 techniques of the California Planet Survey \cite{Howard2010}.
-Figure~\ref{fig:spec} shows the result in the vicinity of H$\alpha$
+Figure~\ref{fig:spec}b shows the result in the vicinity of H$\alpha$
 without any additional processing.
@@
 barycenter and due to Earth's daily rotation about its axis.
-Our analysis pipeline reproduces the systemic velocities reported by
-\cite{Chubak2012} for their velocity standards with an RMS of
-0.66\,\kms.
+Our analysis pipeline reproduces the systemic velocities of known
+velocity standards \cite{Chubak2012} with an RMS of 0.66\,\kms.
 
@@
 the synthetic and observed spectra.  The resulting redshift
-measurements were averaged together.  The star's 130$\pm$4\,\kms\
+measurements over each order were averaged to produce the final measurement.  The star's 130$\pm$4\,\kms\
 equatorial velocity and near-edge on viewing orientation yielded a
@@
 semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This
-sets an upper limit on the mass of any putative companions at the four
+sets an upper limit on the mass of any putative companion at the four
 hour period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
@@
 error (RUWE), a proxy for the goodness of fit for a single-source
-astrometric model to the Gaia astrometry, is 1.23, which is within the
+astrometric model to the Gaia astrometry, is 1.23, within the
 usual range for apparently single sources.  There are no resolved
@@
 pointing to a weak or non-existent connection between the CPV
-phenomenon and binarity.  For TIC~141146667 specifically, we find 
-no evidence for stellar multiplicity.
+phenomenon and binarity.  For TIC~141146667 specifically, while we find 
+no evidence for stellar multiplicity, our data are minimally
+constraining for the scenario of a low-luminosity companion
+($F_1$/$F_2$$\lesssim$0.1) at large orbital separations.
 

### 2025-03-11 paper/ms.tex
update

@@
 possibility would render CPVs as extrasolar analogs of the Jupiter-Io
-plasma torus (CITE).
+plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
 
@@
 the synthetic and observed spectra.  The resulting redshift
-measurements over each order were averaged to produce the final measurement.  The star's 130$\pm$4\,\kms\
-equatorial velocity and near-edge on viewing orientation yielded a
-line broadening $\Delta \lambda$$\approx$3\,\AA.  We used the scatter
-of resulting velocity measurements between orders to assign the RV
-uncertainty at each epoch.  The uncertainty-weighted mean systemic
-velocity over all epochs on UT 2024-02-17 was
-$\gamma$=0.6$\pm$1.5\,\kms.  The relative radial velocities about this
-mean are given in Table~\ref{tab:rv}.
+measurements over each order were averaged to produce the final
+measurement.  The star's 130$\pm$4\,\kms\ equatorial velocity and
+near-edge on viewing orientation yielded a line broadening $\Delta
+\lambda$$\approx$3\,\AA.  We used the scatter of resulting velocity
+measurements between orders to assign the RV uncertainty at each
+epoch.  The uncertainty-weighted mean systemic velocity over all
+epochs on UT 2024-02-17 was $\gamma$=0.6$\pm$1.5\,\kms.  The relative
+radial velocities about this mean are given in Table~\ref{tab:rv}.
 % from calc_max_amplitude_sinusoid_rv_timeseries.py

### 2025-03-11 paper/ms.tex
update

@@
 %
-$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & XXX  & 6 \\
+Age                                     & Adopted stellar age (Myr)\dotfill                              & $16^{+19}_{-6}$  & 2 \\
 %
-$\gamma$\dotfill                        & Systemic radial velocity (\kms)\dotfill                        & 0.61 $\pm$ 1.47  & 1  \\
+$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & XXX  &           & 3 \\
 %
-Age                                     & Adopted stellar age (Myr)\dotfill                              & YYY  & 8 \\
+$\gamma$\dotfill                        & Systemic radial velocity (\kms)\dotfill                        & 0.61 $\pm$ 1.47  & 4 \\
 %
-Spec. Type\dotfill                      & Spectral Type\dotfill                                          & MXV              & X \\
+Spec. Type\dotfill                      & Spectral Type\dotfill                                          & MXV              & 4 \\ % TODO TODO
 %
-$P_{\rm rot}$\dotfill                   & Rotation period (hr)\dotfill                                   & $3.930\pm 0.001$ & X \\
+$P_{\rm rot}$\dotfill                   & Rotation period (hr)\dotfill                                   & $3.930\pm 0.001$ & 5 \\
 %
-$v_{\rm eq}$\dotfill		                & Equatorial velocity \dotfill                                   &  130$\pm$4       & - \\
+$v_{\rm eq}$\dotfill		                & Equatorial velocity \dotfill                                   &  130$\pm$4       & 6 \\
                                         & \hspace{3pt} ($2\pi R_\star/P_{\rm rot}$) (\kms)	             &                      \\
 %
-$v_{\rm eq}\sin{i_\star}$\dotfill		    & Projected rotational\dotfill                                   &  128$\pm$3       & X \\
+$v_{\rm eq}\sin{i_\star}$\dotfill		    & Projected rotational\dotfill                                   &  138$\pm$8       & 4 \\
                                         & \hspace{3pt} velocity (\kms)	                                 &                      \\
 %
-$i_\star$\dotfill                       & Stellar inclination (deg)\dotfill                              & 	XXX             & X \\
+$i_\star$\dotfill                       & Stellar inclination\dotfill                                    & 	$>$63           & 4 \\
+                                        & \hspace{3pt}  2$\sigma$ lower limit (deg)	                     &                      \\
 %
@@
 \footnotesize{ \textsc{NOTE}---
-%$^\dagger$ The GAIADR2 and GAIAEDR3 identifiers for Kepler 1627A are identical.  The secondary
-is not resolved in the Gaia point source catalog.
 $^*$ Given only $v\sin i$ and $2\pi R_\star/P_{\rm rot}$, $\cos i=0.11^{+0.11}_{-0.08}$.
@@
 1: SED fit\cite{Bouma2024},
+2: Gaia DR3 empirical isochrone fit (see~\ref{subsec:stparams}),
+3: PARSEC %(TODO)
 %$^6$Cluster isochrone (MIST adopted; PARSEC compared for quoted
 %  uncertainty),
-2: TESS light curve,
+4: Keck/HIRES.
+5: TESS light curve,
+6: Derived quantity.
 %  3: HIRES spectra and specmatch(?),
@@
 
-Spectra of magetically-active, rapidly rotating stars with a wide range of masses
-have been known to exhibit both sinusoidal emission features
+Spectra of magetically-active, rapidly rotating stars with a wide range
+of masses have been known to exhibit both sinusoidal emission features
 \cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} as well as
@@
 complex light curves \cite{Bouma2024}.  The usual interpretation for
-such spectroscopic variability comes from an analogy to
-quiescent solar prominences, which are cool
-condensations of plasma in the solar corona that can last days to
-weeks \cite{VialEngvold2015}.
-In our Sun's
+such spectroscopic variability comes from an analogy to quiescent solar
+prominences, which are cool condensations of plasma in the solar corona
+that can last days to weeks \cite{VialEngvold2015}.  In our Sun's
 magnetosphere, these condensations fall back to the solar surface
 because gravity is stronger than any magnetic or centrifugal force
-capable of sustaining them.  However for stars with magnetospheric
-radii $R_{\rm m}$ that exceed their corotation radii $R_{\rm c}$, the
-effective potential experienced by a charged particle can have a local minimum
-outside $R_{\rm c}$, enabling the material to be sustained for
+capable of sustaining them.  However for stars with magnetospheric radii
+$R_{\rm m}$ that exceed their corotation radii $R_{\rm c}$, the
+effective potential experienced by a charged particle can have a local
+minimum outside $R_{\rm c}$, enabling the material to be sustained for
 much longer timescales \cite{Petit2013,Daley-Yates2024}.  Generally
@@
 \subsection{Stellar Parameters}\phantom{+}
+\label{subsec:stparams}
 
-{\it Radial Velocity}---We measured radial velocities of
-TIC~141146667 from each of our spectra using a pipeline that we
-developed specifically for rapidly rotating stars.
-Our method is based on template-matching against synthetic spectra
-produced by the PHOENIX stellar atmosphere code \cite{Husser2013}.
-We used the PHOENIX models with solar metallicity and alpha element
-abundances, and calibrated our absolute velocity zero-points as well
-as viable orders for velocity measurement using the
-standard stars described by \cite{Chubak2012}.
-We used velocity standards spanning spectral types from G2 to M4 (Barnard's
-Star), irrespective of rotation rate.
-We used \texttt{barycorrpy} \cite{Kanodia2018} to calculate the
-velocity corrections due to Earth's motion around the solar system
-barycenter and due to Earth's daily rotation about its axis.
-Our analysis pipeline reproduces the systemic velocities of known
-velocity standards \cite{Chubak2012} with an RMS of 0.66\,\kms.
+{\it Radial Velocity}---We measured radial velocities of TIC~141146667
+from each of our spectra using a pipeline that we developed specifically
+for rapidly rotating stars.  Our method is based on template-matching
+against synthetic spectra produced by the PHOENIX stellar atmosphere
+code \cite{Husser2013}.  We used the PHOENIX models with solar
+metallicity and alpha element abundances, and calibrated our absolute
+velocity zero-points as well as viable orders for velocity measurement
+using the standard stars described by \cite{Chubak2012}.  We used
+velocity standards spanning spectral types from G2 to M4 (Barnard's
+Star), irrespective of rotation rate.  We used \texttt{barycorrpy}
+\cite{Kanodia2018} to calculate the velocity corrections due to Earth's
+motion around the solar system barycenter and due to Earth's daily
+rotation about its axis.  Our analysis pipeline reproduces the systemic
+velocities of known velocity standards \cite{Chubak2012} with an RMS of
+0.66\,\kms.
 
-For TIC~141146667, we measured the velocities from each of our HIRES
-spectra using regions near the K~I (7700\,\AA) resonance line and
+For TIC~141146667, we measured the radial velocities from each of our
+HIRES spectra using regions near the K~I (7700\,\AA) resonance line and
 three TiO bandheads (5160\,\AA, 5450\,\AA, and 5600\,\AA).  These
-regions were selected because they provided the best matches between
-the synthetic and observed spectra.  The resulting redshift
-measurements over each order were averaged to produce the final
-measurement.  The star's 130$\pm$4\,\kms\ equatorial velocity and
-near-edge on viewing orientation yielded a line broadening $\Delta
-\lambda$$\approx$3\,\AA.  We used the scatter of resulting velocity
-measurements between orders to assign the RV uncertainty at each
-epoch.  The uncertainty-weighted mean systemic velocity over all
-epochs on UT 2024-02-17 was $\gamma$=0.6$\pm$1.5\,\kms.  The relative
-radial velocities about this mean are given in Table~\ref{tab:rv}.
+regions were selected because they provided the best matches between the
+synthetic and observed spectra.  The resulting redshift measurements
+over each order were averaged to produce the final measurement.  We used
+the scatter of resulting velocity measurements between orders to assign
+the RV uncertainty at each epoch.  The uncertainty-weighted mean
+systemic velocity over all epochs on UT 2024-02-17 was
+$\gamma$=0.6$\pm$1.5\,\kms.  The relative radial velocities about this
+mean are given in Table~\ref{tab:rv}.
+
+{\it Viewing Orientation}---We fitted the rotational broadening of the
+K~I (7700\,\AA) resonance line using the broadening kernel suggested by
+Ref.~\cite{Gray2008}; taking the mean and standard deviation of the
+result value over all epochs yielded $v_{\rm eq} \sin
+i$=138$\pm$8\,\kms, consistent with the visual line broadening $\Delta
+\lambda$$\approx$3\,\AA.  The star's equatorial velocity $v_{\rm eq}$
+based on its apparent size and rotation period is 130$\pm$4\,\kms.
+While this suggests that the viewing orientation could be nearly
+edge-on, the formal constraint is rather weak, with $i$$>$63$^\circ$ at
+2$\sigma$.
 % from calc_max_amplitude_sinusoid_rv_timeseries.py
@@
     $P_{rot}$ (hours) & $3.930 \pm 0.XXX$ & This work \\ 
-    $v \sin i_\star$(km s$^{-1}$) & todo & This work\\
-    $i_\star$($^\circ$) & todo & This work \\
+    $v \sin i_\star$(km s$^{-1}$) & $138 \pm 8$ & This work\\
+    $i_\star$($^\circ$) & $>$63 & This work \\
     $T_{eff}$ (K) & 2972 $\pm$ 40 & \cite{Bouma2024}\\

### 2025-03-11 paper/ms.tex
update

@@
 %
-$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & XXX  &           & 3 \\
+$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & 0.19$\pm$0.01  & 3 \\
 %
@@
 %
-$d$\dotfill                             & Distance (pc)\dotfill                                          & $57.6 \pm X.X$   & X \\
+$d$\dotfill                             & Distance (pc)\dotfill                                          & $57.54 \pm 0.09$   & 7 \\
 %
-$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   &  XXX             & X \\
+$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   & $1.72 \pm 0.06$  & 6 \\
                                         & \hspace{3pt} radius ($R_\star$)	                               &                      \\
@@
 5: TESS light curve,
-6: Derived quantity.
+6: Derived quantity,
+7: Gaia DR3 geometric \cite{GaiaDR3}.
 %  3: HIRES spectra and specmatch(?),
@@
 K~I (7700\,\AA) resonance line using the broadening kernel suggested by
-Ref.~\cite{Gray2008}; taking the mean and standard deviation of the
-result value over all epochs yielded $v_{\rm eq} \sin
+\cite{Gray2008}; taking the mean and standard deviation of the
+resulting value over all epochs yielded $v_{\rm eq} \sin
 i$=138$\pm$8\,\kms, consistent with the visual line broadening $\Delta
@@
 edge-on, the formal constraint is rather weak, with $i$$>$63$^\circ$ at
-2$\sigma$.
+2$\sigma$ (2.5$^{\rm th}$ percentile of the inclination posterior).
 % from calc_max_amplitude_sinusoid_rv_timeseries.py
@@
 of TIC~141146667 being part of any of the nearby known groups using
-BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  Based on that model,
-it appears to be a field star at $>$99.9\% confidence.  We also searched the
+BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  That particular model
+classifies it as a field star at $>$99.9\% confidence.  We also searched the
 local vicinity of TIC~141146667 for neighbors with similar projected on-sky
@@
 {\it Effective temperature, radius, and mass}
-We adopt the results from the spectral energy distribution fitting
-exercise described by \cite{Bouma2024}.
-In brief, this approach used
-\texttt{astroARIADNE}...
-\cite{Vines2022} with the BT-Settl stellar
-atmosphere models \cite{Allard2012} assuming the
-\cite{Asplund2009} solar abundances, and the
-\cite{Barber2006} water line lists.  
-We used broadband magnitudes from Gaia DR2, APASS, 2MASS, SDSS, and WISE
-  $W1$ and $W2$.  (explain)...
+For the stellar effective temperature and radius, we adopted the results
+from the spectral energy distribution fitting methods described by
+\cite{Bouma2024}.
+In brief, this approach used \texttt{astroARIADNE} \cite{Vines2022} with
+the BT-Settl stellar atmosphere models \cite{Allard2012}, assuming the
+\cite{Asplund2009} solar abundances, and the \cite{Barber2006} water
+line lists.  
+This routine fitted for the stellar effective temperature, radius,
+reddening, surface gravity, metallicity, and distance by comparing the
+measured broadband magnitudes against pre-computed model grids.
+Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
+2MASS, SDSS, and WISE $W1$ and $W2$.
+This method has the best constraining power for the star's effective
+temperature and radius; the surface gravity, metallicity, and reddening
+are typically only weakly constrained.
+Given the effective temperature, stellar radius, and previously
+determined age, we then estimated the stellar mass by interpolating
+against the PARSEC v1.2S isochrones \cite{Chen2014}. 
+Specifically, we used the distance metric defined in Equation~8 of
+\cite{Bouma2024}, in order to select the model mass closest to the
+observed temperature, radius, and age.  We derived the uncertainty in
+the mass based by propagating the statistical uncertainties in each of
+these parameters.
 
@@
     $L_\star$ ($L_{\odot}$)  & todo & This work\\
-    $M_\star$ ($M_{\odot}$)  & todo & This work\\
+    $M_\star$ ($M_{\odot}$)  & 0.188 $\pm$ 0.012  & This work\\
     $t_{\rm iso}$ (Myr) & $16^{+19}_{-6}$ &  This work \\

### 2025-03-12 paper/ms.tex
update ms

@@
 %
-Spec. Type\dotfill                      & Spectral Type\dotfill                                          & MXV              & 4 \\ % TODO TODO
+Spec. Type\dotfill                      & Spectral Type\dotfill                                          & M5.5Ve           & 4 \\
 %
@@
 %
-$a_1$\dotfill                           & Clump 1 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.1-2.7         & X \\
-$a_2$\dotfill                           & Clump 2 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  3.9             & X \\
+$a_1$\dotfill                           & Clump 1 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.1-2.7         & 4 \\
+$a_2$\dotfill                           & Clump 2 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  3.9             & 4 \\
 %
@@
 
-{\it Effective temperature, radius, and mass}
+{\it Effective temperature, radius, mass, and spectral type}
 For the stellar effective temperature and radius, we adopted the results
-from the spectral energy distribution fitting methods described by
-\cite{Bouma2024}.
-In brief, this approach used \texttt{astroARIADNE} \cite{Vines2022} with
-the BT-Settl stellar atmosphere models \cite{Allard2012}, assuming the
-\cite{Asplund2009} solar abundances, and the \cite{Barber2006} water
-line lists.  
-This routine fitted for the stellar effective temperature, radius,
+from the spectral energy distribution fits described by
+\cite{Bouma2024}.  To summarize, this approach used
+\texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
+atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
+solar abundances and the \cite{Barber2006} water line lists.  This
+approach fitted for the stellar effective temperature, radius,
 reddening, surface gravity, metallicity, and distance by comparing the
@@
 Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
-2MASS, SDSS, and WISE $W1$ and $W2$.
-This method has the best constraining power for the star's effective
-temperature and radius; the surface gravity, metallicity, and reddening
-are typically only weakly constrained.
-Given the effective temperature, stellar radius, and previously
-determined age, we then estimated the stellar mass by interpolating
-against the PARSEC v1.2S isochrones \cite{Chen2014}. 
-Specifically, we used the distance metric defined in Equation~8 of
-\cite{Bouma2024}, in order to select the model mass closest to the
+2MASS, SDSS, and WISE $W1$ and $W2$.  This method has the most
+constraining power for the star's effective temperature (2972 $\pm$
+40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
+metallicity, and reddening are typically only weakly constrained.  We
+determined the star's spectral type to be M5.5Ve by visually comparing
+against the photometric standards presented by \cite{Bochanski2007};
+this qualitatively agrees with the effective temperature from the SED
+fitting \cite{Pecaut2013}.  With the effective temperature, stellar
+radius, and previously determined age, we then estimated the stellar
+mass by interpolating against the PARSEC v1.2S isochrones
+\cite{Chen2014}.  Specifically, we used the distance metric defined in
+Equation~8 of \cite{Bouma2024} to select the model mass closest to the
 observed temperature, radius, and age.  We derived the uncertainty in

### 2025-03-12 drivers/sptype_by_eye.py
add sptype by eye

@@ -1,0 +1,74 @@
+import os
+from numpy import array as nparr
+from scipy.interpolate import interp1d
+from astropy.io import fits
+from glob import glob
+from os.path import join
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from complexrotators.paths import DATADIR, RESULTSDIR
+from astropy import units as u
+from aesthetic.plot import set_style, savefig
+
+from cdips_followup.spectools import (
+    _get_full_hires_spectrum, bin_spectrum
+)
+from complexrotators.getters import get_bochanski2007_m_standard
+
+def make_sptype_comparison(chip, order):
+
+    fitsdir = join(DATADIR, 'spectra/HIRES/TIC141146667_DEBLAZED')
+    fitspaths = np.sort(glob(join(fitsdir, f"{chip}j*fits")))[1:-1]
+    N = len(fitspaths)
+
+    set_style('science')
+    fig, ax = plt.subplots(figsize=(4,7))
+    colors = [plt.cm.viridis_r(i) for i in np.linspace(0, 0.8, N)]
+
+    bflxs = []
+
+    for spectrum_path, c in zip(fitspaths, colors):
+
+        verbose = 0
+        flx_2d, norm_flx_2d, wav_2d, mjd, ra, dec = _get_full_hires_spectrum(
+            spectrum_path, verbose=verbose
+        )
+
+        flx, wav = norm_flx_2d[order, :], wav_2d[order, :]
+
+        bin_width = 0.2 # angstrom
+        bwav, bflx, bflxerr = bin_spectrum(wav, flx, bin_width)
+        bflxs.append(bflx)
+
+        #plt.plot(bwav, bflx, c=c, lw=0.5, alpha=0.2)
+
+    bflxs = np.array(bflxs)
+    bflxs_tavg = np.nanmedian(bflxs, axis=0)
+    bflxs_tstd = np.nanstd(bflxs, axis=0) / np.sqrt(N)
+    bflxs_tstd[bflxs_tstd > 0.05]  = np.nanmean(bflxs_tstd)
+
+    dlam = 1.5
+    ax.errorbar(bwav+dlam, bflxs_tavg, yerr=bflxs_tstd, c='k', lw=1, label='data')
+
+    sptypes = [f"M{ix}" for ix in range(4,8)]
+    colors = [plt.cm.magma_r(i) for i in np.linspace(0.3, 0.8, len(sptypes))]
[…]

### 2025-03-12 drivers/quality_lc.py
minor

@@ -31,4 +31,4 @@ ax.legend(fontsize='x-small')
 
 plt.show();
 
-savefig(fig, 'results/quality_lc.png')
+savefig(fig, 'results/quality_lc/quality_lc.png')

### 2025-03-12 paper/ms.tex
update

@@
 One glaring example of our current ignorance is the complex periodic
-variables (CPVs).  Figure~\ref{fig:lc} highlights the main object of
-interest in this article, but over one hundred analogous objects have
+variables (CPVs).  While Figure~\ref{fig:lc} highlights the main object of
+interest in this article, over one hundred analogous objects have
 now been found by K2 and TESS 
@@
   available
-  \href{https://lgbouma.com/movies/movie_TIC1411_flux_phase.mp4}{here},
+  \href{https://lgbouma.com/movies/TIC141146667_20250116.mp4}{here},
   which spans a baseline of 5{,}784 cycles irregularly sampled over three
@@
 
-In this study, we present the first observations of corotating clumps
-of cool plasma around a CPV.  We identified TIC~141146667 in previous
-work \cite{Bouma2024} by searching the TESS two-minute data for stars
-showing periodic variability with at least three sharp dips per cycle.
-We selected the star for spectroscopic observations because its
-brightness and rapid rotation offered sensitivity to small variations
-in the line profiles.  We observed for five hours on UT 2024-02-17
-using the High Resolution Echelle Spectrometer (HIRES;
-\cite{vogt_hires_1994}) on the Keck I 10m telescope.  TESS observed
-the star from UT 2024-02-05 to UT 2024-02-26 with a duty cycle of
-XX\%.  
-At the exact instant of spectral observations, TESS was performing a
-data downlink; photometric data collection resumed three rotation
-cycles (12 hours) after the spectra were acquired.  Extended Data
-Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
-star before and after the exact epoch of observation; the photometric
-morphology is similar before and after the data gap.
+In this study, we present the first observations of corotating clumps of
+cool plasma around a CPV.  We identified TIC~141146667 in previous work
+\cite{Bouma2024} by searching the TESS two-minute data \cite{Ricker2015}
+for stars showing at least three sharp and periodic dips per cycle.  We
+selected the star for spectroscopy because its brightness and rapid
+rotation offer sensitivity to small variations in the line profiles.  We
+observed for five hours on 17~February~2024 (UT) using the High
+Resolution Echelle Spectrometer (HIRES; \cite{vogt_hires_1994}) on the
+Keck I 10m telescope.  TESS observed the star over a four week period
+from 30~January~2024 to 26~February~2024 with a duty cycle of 77\%.
+During the spectral observations, TESS was performing a data downlink;
+TESS data collection resumed 12 hours (three rotation cycles) after the
+spectra were acquired.  Extended Data Figure~\ref{fig:fulllc} shows the
+detailed photometric behavior of the star before and after the exact
+epoch of observation; the photometric morphology is similar before and
+after the data gap.
 
@@
 Provenances are:
-1: SED fit\cite{Bouma2024},
-2: Gaia DR3 empirical isochrone fit (see~\ref{subsec:stparams}),
-3: PARSEC %(TODO)
+1: SED fit \cite{Bouma2024}.
+2: Gaia DR3 empirical isochrone fit (see~\ref{subsec:stparams}).
+3: PARSEC v1.2S \cite{Chen2014}.
 %$^6$Cluster isochrone (MIST adopted; PARSEC compared for quoted
@@
 4: Keck/HIRES.
-5: TESS light curve,
-6: Derived quantity,
+5: TESS light curve.
+6: Derived quantity.
 7: Gaia DR3 geometric \cite{GaiaDR3}.

### 2025-03-13 drivers/plot_li_spectrum.py
add plot_li_spectrum

@@ -1,0 +1,115 @@
+"""
+Make a time-averaged spectrum around Li 6708A
+and compare it against a spectral template from Bochanski+2007 (take M6)
+"""
+import os
+from numpy import array as nparr
+from scipy.interpolate import interp1d
+from astropy.io import fits
+from glob import glob
+from os.path import join
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from complexrotators.paths import DATADIR, RESULTSDIR
+from astropy import units as u
+from aesthetic.plot import set_style, savefig
+
+from cdips_followup.spectools import (
+    _get_full_hires_spectrum, bin_spectrum
+)
+from complexrotators.getters import get_bochanski2007_m_standard
+
+def make_li_plot(chip, order):
+
+    fitsdir = join(DATADIR, 'spectra/HIRES/TIC141146667_DEBLAZED')
+    fitspaths = np.sort(glob(join(fitsdir, f"{chip}j*fits")))[1:-1]
+    N = len(fitspaths)
+
+    set_style('science')
+    fig, ax = plt.subplots(figsize=(2,2))
+    colors = [plt.cm.viridis_r(i) for i in np.linspace(0, 0.8, N)]
+
+    bflxs = []
+
+    for spectrum_path, c in zip(fitspaths, colors):
+
+        verbose = 0
+        flx_2d, norm_flx_2d, wav_2d, mjd, ra, dec = _get_full_hires_spectrum(
+            spectrum_path, verbose=verbose
+        )
+
+        flx, wav = norm_flx_2d[order, :], wav_2d[order, :]
+
+        bin_width = 0.5 # angstrom
+        bwav, bflx, bflxerr = bin_spectrum(wav, flx, bin_width)
+        bflxs.append(bflx)
+
+        # NOTE: uncomment to show individual spectra
+        #plt.plot(bwav, bflx, c=c, lw=0.5, alpha=0.2)
+
+    bflxs = np.array(bflxs)
+    bflxs_tavg = np.nanmedian(bflxs, axis=0)
+    bflxs_tstd = np.nanstd(bflxs, axis=0) / np.sqrt(N)
+    bflxs_tstd[bflxs_tstd > 0.05]  = np.nanmean(bflxs_tstd)
+
+    dlam = 1.0
+    bwav += dlam
+
+    ax.errorbar(bwav, bflxs_tavg -0.1, yerr=bflxs_tstd, c='k', lw=1,
+                label='TIC 141146667')
+
[…]

### 2025-03-13 paper/ms.tex
update

@@
 TIC~141146667 being equally bright.
+%FIXME: update discussion following consideration of anomalous CPV
+% brightnesses and colors...
 
-{\it Age: Lithium}--- Frankly, it's not obviously there!  (but maybe
+{\it Age: Lithium}---The depletion of lithium due to $^7$Li(p,
+$\alpha$)$^4$He burning in the cores of low-mass stars has been
+studied for over sixty years
+\cite{Hayashi1963,Bildsten1997,Burke2004}.  \cite{Wood2023} provided
+an instructive recent overview: an abbreviated summary is that the M
+dwarfs that have not yet had time to burn their photospheric lithium
+show the lithium 6707.8\,\AA doublet in absorption, $\gtrsim$10\%
+below their ``continua''.  Relative to Sun-like stars, defining the
+continuum for cool M dwarfs requires care due to their complex
+spectra.  To attempt a lithium measurement, we constructed a
+wavelength-binned and Doppler-corrected TIC~141146667 spectrum,
+assigned its uncertainties based on the measured scatter across the
+five hour dataset, and compared against the nearest matching template
+from \cite{Bochanski2007}.  The data show a slight depression near the
+expected lithium wavelength, potentially consistent with a $\Delta
+\lambda$$\approx$3\,\AA line broadening.  This feature nominally
+yields ${\rm EW}_{Li}$=71$^{+18}_{13}$\,m\AA, where the statistical
+uncertainties are evaluated using a bootstrap resampling technique
+from the statistical uncertainties in the spectrum.  Unfortunately,
+the systematic uncertainties associated with the continuum
+normalization are large, comparable to the amplitude of the feature;
+we therefore prefer to quote the results of this measurement as a
+$2\sigma$ upper limit: ${\rm EW}_{Li}$$<$107\,m\AA.
+
+While
+
+W
+
+Frankly, it's not obviously there!  (but maybe
 this is bc of the blending, and a pEW would show smth small)

### 2025-03-13 drivers/plot_li_vs_population.py
add drivers/plot_li_vs_population.py

@@ -1,0 +1,111 @@
+import os
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib import rcParams
+
+from matplotlib.colors import ListedColormap, LinearSegmentedColormap
+from aesthetic.plot import set_style, savefig
+
+
+def truncate_colormap(
+    cmap: LinearSegmentedColormap, minval: float = 0.0, maxval: float = 1.0,
+    n: int = 100
+) -> LinearSegmentedColormap:
+    """Truncate a colormap to limit its upper range.
+
+    Args:
+        cmap (LinearSegmentedColormap): Original colormap.
+        minval (float, optional): Minimum value fraction. Defaults to 0.0.
+        maxval (float, optional): Maximum value fraction. Defaults to 1.0.
+        n (int, optional): Number of colors in new colormap.
+            Defaults to 100.
+
+    Returns:
+        LinearSegmentedColormap: Truncated colormap.
+    """
+    new_colors = cmap(np.linspace(minval, maxval, n))
+    new_cmap = LinearSegmentedColormap.from_list(
+        f"trunc({cmap.name},{minval:.2f},{maxval:.2f})", new_colors
+    )
+    return new_cmap
+
+
+def plot_li_vs_population() -> None:
+    """Plot LiEW vs TEFF for stars with AGE < 100 binned by AGE.
+
+    Reads data from '../data/EAGLES_table2.csv', filters for rows with
+    AGE < 100, then loops over age bins (0–10, 10–20, etc.) to plot the data.
+    Each bin is assigned a discrete color from a truncated plasma colormap.
+    Stars in older bins are plotted with a higher zorder.
+    The resulting plot is saved to 'results/li_ew/li_vs_population.png'.
+    """
+
+    # Read CSV file and filter by AGE.
+    df = pd.read_csv("../data/EAGLES_table2.csv", skipinitialspace=True)
+    df = df[df["AGE"] < 100]
+
+    # Define age bins.
+    bins = np.arange(0, 60 + 10, 10)  # [0, 10, 20, 30, 40, 50, 60]
+    nbins = len(bins) - 1
+
+    # Create truncated plasma colormap.
+    plasma = plt.get_cmap("plasma")
+    trunc_plasma = truncate_colormap(plasma, 0.0, 0.9)
+    discrete_trunc_plasma = ListedColormap(
+        trunc_plasma(np.linspace(0, 1, nbins)),
[…]

### 2025-03-13 paper/ms.tex
update ms

--- 2025-03-12 paper/ms.tex
@@
 {\it Radial Velocity}---We measured radial velocities of TIC~141146667
-from each of our spectra using a pipeline that we developed specifically
+our HIRES spectra using a pipeline that we developed specifically
 for rapidly rotating stars.  Our method is based on template-matching
@@
 code \cite{Husser2013}.  We used the PHOENIX models with solar
-metallicity and alpha element abundances, and calibrated our absolute
-velocity zero-points as well as viable orders for velocity measurement
+metallicity and alpha element abundances, and calibrated our pipeline
 using the standard stars described by \cite{Chubak2012}.  We used
@@
 motion around the solar system barycenter and due to Earth's daily
-rotation about its axis.  Our analysis pipeline reproduces the systemic
+rotation about its axis.  Our analysis code reproduces the systemic
 velocities of known velocity standards \cite{Chubak2012} with an RMS of
@@
 
-For TIC~141146667, we measured the radial velocities from each of our
-HIRES spectra using regions near the K~I (7700\,\AA) resonance line and
-three TiO bandheads (5160\,\AA, 5450\,\AA, and 5600\,\AA).  These
-regions were selected because they provided the best matches between the
-synthetic and observed spectra.  The resulting redshift measurements
-over each order were averaged to produce the final measurement.  We used
+For TIC~141146667, we measured the radial velocities using regions
+near the K~I (7700\,\AA) resonance line and three TiO bandheads
+(5160\,\AA, 5450\,\AA, and 5600\,\AA).  We
+selected these regions because they provided the best matches between the
+synthetic and observed spectra.  We then averaged the resulting redshift measurements
+over each order to produce the final measurement.  We used
 the scatter of resulting velocity measurements between orders to assign
@@
 
+{\it Effective temperature, radius, mass, and spectral type}
+We determined the stellar effective temperature and radius by adopting
+the results from the spectral energy distribution fitting procedure
+described by \cite{Bouma2024}.  To summarize, this approach used
+\texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
+atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
+solar abundances and the \cite{Barber2006} water line lists.  This
+approach fitted for the stellar effective temperature, radius,
+reddening, surface gravity, metallicity, and distance by comparing the
+measured broadband magnitudes against pre-computed model grids.
+Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
+2MASS, SDSS, and WISE $W1$ and $W2$.  This method has the most
+constraining power for the star's effective temperature (2972 $\pm$
+40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
+metallicity, and reddening are typically only weakly constrained.  We
+determined the star's spectral type to be M5.5Ve by visually comparing
+against the photometric standards presented by \cite{Bochanski2007};
+this qualitatively agrees with the effective temperature from the SED
+fitting \cite{Pecaut2013}.  With the effective temperature, stellar
+radius, and previously determined age, we then estimated the stellar
+mass by interpolating against the PARSEC v1.2S isochrones
+\cite{Chen2014}.  Specifically, we used the distance metric defined in
+Equation~8 of \cite{Bouma2024} to select the model mass closest to the
+observed temperature, radius, and age.  We derived the uncertainty in
+the mass based by propagating the statistical uncertainties in each of
+these parameters.
+
 {\it Age: No Obvious Association Membership}---Previous work
@@
 known young moving groups based on their positions and kinematics.
-TIC~141146667 is one of the exceptions.  We calculated the probability
+TIC~141146667 is in the minority.  We calculated the probability
 of TIC~141146667 being part of any of the nearby known groups using
@@
 velocities using \texttt{comove} \cite{Tofflemire2021}.  This yielded
-no strong candidates for co-moving stars --- defined as those with
-projected tangential velocities $\Delta v_{\rm T}$$<$5\,\kms ---
+no strong candidates for co-moving stars with
+projected tangential velocities $\Delta v_{\rm T}$$<$5\,\kms
 that share its isochronal youth.
@@
 TIC~141146667 being equally bright.
+%FIXME: update discussion following consideration of anomalous CPV
+% brightnesses and colors...
 
-{\it Age: Lithium}--- Frankly, it's not obviously there!  (but maybe
-this is bc of the blending, and a pEW would show smth small)
-%TODO TODO TODO
+{\it Age: Lithium}---The depletion of lithium due to $^7$Li(p,
+$\alpha$)$^4$He burning in the cores of low-mass stars has been
+studied for over sixty years
+\cite{Hayashi1963,Bildsten1997,Burke2004}.  \cite{Wood2023} provided
+an instructive recent overview: an abbreviated summary is that cooler
+and younger M dwarfs can show the 6707.8\,\AA\ doublet in absorption,
+$\gtrsim$10\%
+below their ``continua''.  Unlike Sun-like stars, the continuum for M
+dwarfs is poorly defined due to their molecular absorption.  We
+attempted a lithium measurement by constructing a
+wavelength-binned and Doppler-corrected TIC~141146667 spectrum,
+assigning its uncertainties based on the measured scatter across the
+five hour dataset.  We then compared this average spectrum against the
+nearest matching template from \cite{Bochanski2007}.  The data show a
+slight depression near the
+expected lithium wavelength, potentially consistent with a $\Delta
+\lambda$$\approx$3\,\AA\ line broadening.  This feature nominally
+yields ${\rm EW}_{\rm Li}$=71$^{+18}_{13}$\,m\AA, where the statistical
+uncertainties are evaluated using a bootstrap resampling technique
+from the statistical uncertainties in the spectrum.  Unfortunately,
+the systematic uncertainties associated with the continuum
+normalization are large, comparable to the amplitude of the feature;
+we therefore prefer to quote the result of this measurement as a
+$2\sigma$ upper limit: ${\rm EW}_{\rm Li}$$<$107\,m\AA.
+% FIXME: this is perhaps a hokey way to do it.  Better to quantify the
+% systematic uncertainty, and incorporate that into your quoted
+% value...
 
-% We have K=10.47, d=57pc - > DM ~= 3.78 -> M_K ~= 6.67
-Figure7 of Wood23 suggests from the Feiden Li depletion curves that no lithium would imply $t$>37Myr.
-However Figure5 frmo the same work suggests maybe try binning up the spectrum, and then comparing against Bochanski+2007 for a lithium-free template.
+Desite uncertainties in the details, what can be stated with
+confidence is that lithium is not abundant in the spectrum of
+TIC~141146667.  Figure~\ref{fig:liew_population} compares our upper
+limit against the lithium equivalent width measurements and
+temperatures reported by \cite{Jeffries2023} based on the Gaia-ESO
+spectroscopic survey.  If the star were $\lesssim$20\,Myr old, given
+its temperature we would expect to see lithium in abundance
+($\gtrsim$400\,m\AA).  Since we do not, we conclude that $t_{\rm
+Li,emp}$$\gtrsim$20\,Myr.  The \cite{Feiden2016} isochrones provide a
+point for theoretical comparison, suggesting that since $M_{\rm
+K}$$=$6.67\,mag, $t_{\rm Li,th}$$\gtrsim$35\,Myr for complete
+depletion.
 
-Try differential comparison against Barnard's star...
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/sf2.pdf}
+  \caption[]{todo... }
+  \label{fig:liew_population}
+\end{figure}
 
 {\it Age: Summary}---The main indicators for the youth of
-TIC~141146667 are {\it i)} that it is a complex periodic variable;
+TIC~141146667 are {\it i)} that it is a complex periodic variable, and
 {\it ii)} that it is 1.5 magnitudes brighter than main sequence stars
-of the same color, while showing no indicators for binarity; {\it
-iii)} weak lithium absorption.
-
-{\it Effective temperature, radius, mass, and spectral type}
-For the stellar effective temperature and radius, we adopted the results
-from the spectral energy distribution fits described by
-\cite{Bouma2024}.  To summarize, this approach used
-\texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
-atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
-solar abundances and the \cite{Barber2006} water line lists.  This
-approach fitted for the stellar effective temperature, radius,
-reddening, surface gravity, metallicity, and distance by comparing the
-measured broadband magnitudes against pre-computed model grids.
-Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
-2MASS, SDSS, and WISE $W1$ and $W2$.  This method has the most
-constraining power for the star's effective temperature (2972 $\pm$
-40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
-metallicity, and reddening are typically only weakly constrained.  We
-determined the star's spectral type to be M5.5Ve by visually comparing
-against the photometric standards presented by \cite{Bochanski2007};
-this qualitatively agrees with the effective temperature from the SED
-fitting \cite{Pecaut2013}.  With the effective temperature, stellar
-radius, and previously determined age, we then estimated the stellar
-mass by interpolating against the PARSEC v1.2S isochrones
-\cite{Chen2014}.  Specifically, we used the distance metric defined in
-Equation~8 of \cite{Bouma2024} to select the model mass closest to the
-observed temperature, radius, and age.  We derived the uncertainty in
-the mass based by propagating the statistical uncertainties in each of
-these parameters.
+of the same color, while showing no indicators for binarity.  The
+first item constitutes evidence for youth since all known CPVs are
+$\lesssim$200\,Myr \cite{Bouma2024}.  Reference sequences for
+$\approx$40-50\,Myr clusters show no stars of equal luminosity and the
+same temperature, suggesting a photometric isochronal age upper limit
+of 50\,Myr.  The weak lithium absorption suggests an age of at least
+20\,Myr based on an empirical comparison using Gaia-ESO spectra, or at
+least 35\,Myr based on the \cite{Feiden2016} isochrones.  These
+considerations yield our adopted age range of 20-50\,Myr.
 

### 2025-03-13 paper/collect_figs.sh

@@ -21,3 +21,6 @@ cp $r/movie_sixpanel_specriver/TIC_141146667_science/TIC141146667_sixpanel.mov m
 
 # sf1: The data are nearly but not exactly simultaneous
 cp $r/tic1411_obsepoch/tic1411_obsepoch.pdf figures/sf1.pdf
+
+r="/Users/luke/Dropbox/proj/hotcold/drivers/results"
+cp $r/li_ew/li_vs_population.pdf figures/sf2.pdf

### 2025-03-13 paper/ms.tex
update

@@
 and younger M dwarfs can show the 6707.8\,\AA\ doublet in absorption,
-$\gtrsim$10\%
-below their ``continua''.  Unlike Sun-like stars, the continuum for M
-dwarfs is poorly defined due to their molecular absorption.  We
-attempted a lithium measurement by constructing a
+$\gtrsim$10\% below their ``continua''.  Unlike Sun-like stars, the
+continuum for M dwarfs is poorly defined due to their molecular
+absorption.  We attempted a lithium measurement by constructing a
 wavelength-binned and Doppler-corrected TIC~141146667 spectrum,
@@
 nearest matching template from \cite{Bochanski2007}.  The data show a
-slight depression near the
-expected lithium wavelength, potentially consistent with a $\Delta
-\lambda$$\approx$3\,\AA\ line broadening.  This feature nominally
-yields ${\rm EW}_{\rm Li}$=71$^{+18}_{13}$\,m\AA, where the statistical
-uncertainties are evaluated using a bootstrap resampling technique
-from the statistical uncertainties in the spectrum.  Unfortunately,
-the systematic uncertainties associated with the continuum
-normalization are large, comparable to the amplitude of the feature;
-we therefore prefer to quote the result of this measurement as a
-$2\sigma$ upper limit: ${\rm EW}_{\rm Li}$$<$107\,m\AA.
-% FIXME: this is perhaps a hokey way to do it.  Better to quantify the
-% systematic uncertainty, and incorporate that into your quoted
-% value...
+small depression near the expected lithium wavelength, potentially
+consistent with a $\Delta \lambda$$\approx$3\,\AA\ line broadening.
+This feature nominally yields ${\rm EW}_{\rm
+Li}$=71$^{+18}_{13}$\,m\AA, where the statistical uncertainties are
+evaluated using a bootstrap resampling technique from the statistical
+uncertainties in the spectrum.  The systematic uncertainties
+associated with the continuum normalization are larger, and likely
+comparable to the amplitude of the feature; we therefore treat the
+result of this measurement as a $2\sigma$ upper limit: ${\rm EW}_{\rm
+Li}$$<$107\,m\AA.
 
@@
 TIC~141146667.  Figure~\ref{fig:liew_population} compares our upper
-limit against the lithium equivalent width measurements and
-temperatures reported by \cite{Jeffries2023} based on the Gaia-ESO
-spectroscopic survey.  If the star were $\lesssim$20\,Myr old, given
-its temperature we would expect to see lithium in abundance
-($\gtrsim$400\,m\AA).  Since we do not, we conclude that $t_{\rm
-Li,emp}$$\gtrsim$20\,Myr.  The \cite{Feiden2016} isochrones provide a
-point for theoretical comparison, suggesting that since $M_{\rm
-K}$$=$6.67\,mag, $t_{\rm Li,th}$$\gtrsim$35\,Myr for complete
-depletion.
+limit against the lithium equivalent width measurements reported by
+\cite{Jeffries2023} based on the Gaia-ESO spectroscopic survey.  If
+the star were $\lesssim$20\,Myr old, given its temperature we would
+expect to see lithium in abundance ($>$400\,m\AA).  Since we do not,
+we conclude that $t_{\rm Li,emp}$$\gtrsim$20\,Myr.  The
+\cite{Feiden2016} isochrones provide a point for theoretical
+comparison, suggesting that since $M_{\rm K}$$=$6.67\,mag, $t_{\rm
+Li,th}$$\gtrsim$35\,Myr would be expected for complete depletion (see
+e.g.~Figure 7 from \cite{Wood2023}).
 
@@
   \includegraphics[width=0.7\textwidth]{figures/sf2.pdf}
-  \caption[]{todo... }
+  \caption{An upper limit on photospheric lithium for TIC~141146667
+  (green triangle) yields a lower limit on the star's age of $\gtrsim$20\,Myr.
+  Comparison stars are from the Gaia-ESO survey
+  \cite{Jeffries2023}; rich clusters in each age bin include
+  NGC\,2264 (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel (16.4\,Myr), NGC\,2547
+  (35.0\,Myr), IC\,2602 and IC\,2391 (42.0\,Myr), and NGC\,2451A
+  (50.0\,Myr). }
   \label{fig:liew_population}

### 2025-03-13 drivers/plot_hrd.py
[WIP] add HRD driver
todo: add de-reddening

@@ -1,0 +1,152 @@
+"""
+UCL/LCC : Kerr
+IC2602+/IC2391 : Hunt&Reffert24 2024A&A...686A..42H
+Pleiades : ditto
+TIC1411
+"""
+import os
+from numpy import array as nparr
+from scipy.interpolate import interp1d
+from astropy.io import fits
+from glob import glob
+from os.path import join
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from astropy.table import Table
+from complexrotators.paths import DATADIR, RESULTSDIR
+from astropy import units as u
+from aesthetic.plot import set_style, savefig
+from matplotlib import rcParams
+
+from cdips.utils.gaiaqueries import given_source_ids_get_gaia_data
+
+from rudolf.helpers import get_gaia_catalog_of_nearby_stars
+
+def plot_hrd(smalllims=0):
+
+    ##############################
+    # collect cluster data
+    fitspath = '../data/literature/Hunt_2024_table2.fits'
+    hl = fits.open(fitspath)
+    df_h24 = Table(hl[1].data).to_pandas()
+
+    # Pleiades
+    df_ple = df_h24[df_h24['Name'] == 'Melotte_22']
+    # IC2602
+    df_ic2602 = df_h24[df_h24['Name'] == 'IC_2602']
+
+    # Sco-Cen / USco
+    fitspath = '../data/literature/Kerr_2021_table1.fits'
+    hl = fits.open(fitspath)
+    df_k21t1 = Table(hl[1].data).to_pandas()
+
+    df_usco = df_k21t1[(df_k21t1['TLC'] == 22) & (df_k21t1['EOM'] == 17) &
+                       (df_k21t1['Prob'] > 0.95) & (df_k21t1['Leaf'] == ' ')]
+    df_usco = df_usco.rename({'bp-rp':'BP-RP', 'plx':'Plx'}, axis='columns')
+
+    dr2_source_ids = np.array(df_usco['Gaia'])
+    groupname = 'Kerr21t1_USco'
+    gdf = given_source_ids_get_gaia_data(dr2_source_ids, groupname,
+                                         n_max=10000, overwrite=False,
+                                         enforce_all_sourceids_viable=True,
+                                         which_columns='*',
+                                         table_name='gaia_source',
[…]

### 2025-03-13 drivers/plot_hrd.py
hrd vs clusters working

@@ -20,21 +20,10 @@ from matplotlib import rcParams
 from cdips.utils.gaiaqueries import given_source_ids_get_gaia_data
 
 from rudolf.helpers import get_gaia_catalog_of_nearby_stars
+from rudolf.extinction import append_corrected_gaia_phot_Gaia2018
 
-def plot_hrd(smalllims=0):
+def get_kerr21_usco():
 
-    ##############################
-    # collect cluster data
-    fitspath = '../data/literature/Hunt_2024_table2.fits'
-    hl = fits.open(fitspath)
-    df_h24 = Table(hl[1].data).to_pandas()
-
-    # Pleiades
-    df_ple = df_h24[df_h24['Name'] == 'Melotte_22']
-    # IC2602
-    df_ic2602 = df_h24[df_h24['Name'] == 'IC_2602']
-
-    # Sco-Cen / USco
     fitspath = '../data/literature/Kerr_2021_table1.fits'
     hl = fits.open(fitspath)
     df_k21t1 = Table(hl[1].data).to_pandas()
@@ -55,31 +44,137 @@ def plot_hrd(smalllims=0):
         {'bp_rp': 'BP-RP', 'parallax': 'Plx', 'phot_g_mean_mag': 'Gmag'},
         axis='columns'
     )
+    return gdf_usco
 
-    df_bkgd = get_gaia_catalog_of_nearby_stars()
-    df_bkgd = df_bkgd.rename(
-        {'phot_g_mean_mag': 'Gmag', 'parallax':'Plx'}, axis='columns'
+def get_ratzenbock23_lcc_ucl():
+
+    fitspath = '../data/literature/Ratzenboeck_2023_table1.fits'
+    hl = fits.open(fitspath)
+    df = Table(hl[1].data).to_pandas()
+
+    # select nu Cen (UCL greatest density  and sigma Cen (LCC greatest density)
+    sel = (
+        ( (df['SigMA'] == 20) | (df['SigMA'] == 22) )
+        &
+        (df['stability'] > 95)
     )
-    #df_bkgd = df_bkgd[df.Plx > 0] # < 50pc
-    df_bkgd['BP-RP'] = df_bkgd['phot_bp_mean_mag'] - df_bkgd['phot_rp_mean_mag']
+    df = df[sel]
 
-    # TIC 1411
-    df_1411 = pd.DataFrame({
-        'BP-RP': 3.276,
-        'Gmag': 14.701,
[…]

### 2025-03-13 drivers/plot_hrd.py
hrd: better

@@ -22,6 +22,12 @@ from cdips.utils.gaiaqueries import given_source_ids_get_gaia_data
 from rudolf.helpers import get_gaia_catalog_of_nearby_stars
 from rudolf.extinction import append_corrected_gaia_phot_Gaia2018
 
+EXTINCTIONDICT = {
+    'Pleiades': 0.10209450, # from Hunt+24, table1, A_V
+    'IC_2602': 0.11434174, # from Hunt+24, table1, A_V
+    'UCL/LCC': 0.12 # Pecaut&Mamajek 2016 table7 median
+}
+
 def get_kerr21_usco():
 
     fitspath = '../data/literature/Kerr_2021_table1.fits'
@@ -70,6 +76,34 @@ def get_ratzenbock23_lcc_ucl():
                                          gaia_datarelease='gaiadr3')
 
     return gdf
+
+
+def get_ratzenbock23_usco():
+
+    fitspath = '../data/literature/Ratzenboeck_2023_table1.fits'
+    hl = fits.open(fitspath)
+    df = Table(hl[1].data).to_pandas()
+
+    # select delta sco and sigma sco
+    sel = (
+        ( (df['SigMA'] == 3) | (df['SigMA'] == 5) )
+        &
+        (df['stability'] > 95)
+    )
+    df = df[sel]
+
+    dr3_source_ids = np.array(df['GaiaDR3'])
+    groupname = 'Ratzenboeck_2023_table1_usco'
+    gdf = given_source_ids_get_gaia_data(dr3_source_ids, groupname,
+                                         n_max=20000, overwrite=False,
+                                         enforce_all_sourceids_viable=True,
+                                         which_columns='*',
+                                         table_name='gaia_source_lite',
+                                         gaia_datarelease='gaiadr3')
+
+    return gdf
+
+
 
 def get_tic1411():
 
@@ -132,17 +166,84 @@ def get_ic2602():
     return gdf
 
 
-def plot_hrd(deredden=0, smalllims=0):
+def get_cpv_hrd_data():
 
-    EXTINCTIONDICT = {
-        'Pleiades': 0.10209450, # from Hunt+24, table1, A_V
-        'IC_2602': 0.11434174, # from Hunt+24, table1, A_V
[…]

### 2025-03-13 paper/ms.tex
update

@@
 %
-Age                                     & Adopted stellar age (Myr)\dotfill                              & $16^{+19}_{-6}$  & 2 \\
+Age                                     & Stellar age range (Myr)\dotfill                                & 35-150  & 2 \\
 %
@@
 1: SED fit \cite{Bouma2024}.
-2: Gaia DR3 empirical isochrone fit (see~\ref{subsec:stparams}).
+2: Gaia DR3 photometry and lack of lithium (see~\ref{subsec:stparams}).
 3: PARSEC v1.2S \cite{Chen2014}.
@@
 eclipsing binaries and transiting exoplanets around young
-pre-main-sequence M dwarfs \cite{Johns-Krull2016,Bouma2020}.
+pre-main sequence M dwarfs \cite{Johns-Krull2016,Bouma2020}.
 
@@
 {\it Age: Isochrones}---The color and absolute magnitude of
-TIC~141146667 suggest that it is a pre-main-sequence M dwarf, similar
+TIC~141146667 suggest that it is a pre-main sequence M dwarf, similar
 to all other known CPVs \cite{Stauffer2017,Stauffer2021,Bouma2024}.
@@
 ($b$=$+$53$^\circ$) yield negligible interstellar reddening along the
-line of sight \cite{Green2019}.
-{\bf Figure~X} shows the location of the star in the color--absolute
-magnitude diagram (CAMD)
+line of sight \cite{Green2019}.  Figure~\ref{fig:camd} shows the
+location of the star in the color--absolute magnitude diagram (CAMD)
 relative to young stellar populations including Upper Scorpius (USco),
-Upper-Centaurus-Lupus (UCL), IC~2602, and the Pleiades.
-To make this diagram, {\bf TODO}we adopted the USco and UCL members
-from X, the IC~2602 members from Y, and the Pleiades members from Z,
-and applied the same reddening corrections as in \cite{Bouma2022}.
-To measure the isochrone age of TIC~141146667, we then followed the 
-empirical approach proposed by \cite{Gagne2020} and
-implemented in \cite{Bouma2022}.
-The idea is to estimate the star (or star cluster's) age by
-interpolating between the observed isochrones of star clusters with
-ages that have been otherwise calibrated, for instance using
-the lithium depletion-boundary method.
-While this circumvents known modelling issues in molecular opacities
-and starspot coverage for young M dwarfs,
-the ages returned by this procedure depend on the ages
-assumed for each reference cluster.
-In this case, the most important reference is UCL, since TIC~141146667
-overlaps directly on its isochrone on the CAMD.
-We adopted the 16~Myr age for UCL from \cite{PecautMamajek2016}, which
-is consistent with ages determined by more recent sub-clustering
-analyses \cite{Ratzenbock2023} for the largest sub-populations.
-This in turns yields an isochronal age for TIC~141146667 of
-$t_{\rm iso}$=$16^{+19}_{-6}$\,Myr.
-Qualitatively, this range of uncertainty is consistent with no stars
-in the $\approx$40\,Myr IC~2602 cluster with similar redness as
-TIC~141146667 being equally bright.
+IC~2602, and the Pleiades.  To make this diagram, we adopted the USco
+members in the $\delta$~Sco and $\sigma$~Sco sub-associations from
+\cite{Ratzenbock2023}, and the IC~2602 and Pleiades members from
+\cite{Hunt2024}.  We assumed an average $V$-band extinction $A_{\rm
+V}$=${0.12, 0.11, 0.10}\,{\rm mag}$ for USco \cite{Pecaut2016},
+IC~2602 \cite{Hunt2024}, and the Pleiades \cite{Hunt2024}
+respectively.  We dereddened the photometry using the extinction
+coefficients $k_X\equiv A_X/A_0$ tabulated in
+\citet{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.
+
+Figure~\ref{fig:camd} suggests that TIC~141146667 is
+older than USco, and potentially younger than the Pleiades.  The precision of this
+statement is set by the intrinsic scatter of the calibration
+sequences; the most luminous stars in the Pleiades of the same color
+have a similar absolute magnitude as TIC~141146667.
+Previous work \cite{Stauffer2021} has noted that in the Gaia
+passbands, CPVs tend to be photometrically redder and more luminous
+than single stars in any given cluster.
+While this effect complicates any attempt at age inference based on this
+photometry, it suggests that the Pleiades may be a better comparison
+population than IC~2602.
+Broadly, we take the star's isochrone location to suggest age bounds
+$t_{\rm CAMD}$$\sim$40-150\,Myr.
+
+%  and applied the same reddening corrections as in \cite{Bouma2022}.
+%  To measure the isochrone age of TIC~141146667, we then followed the 
+%  empirical approach proposed by \cite{Gagne2020} and
+%  implemented in \cite{Bouma2022}.
+%  The idea is to estimate the star (or star cluster's) age by
+%  interpolating between the observed isochrones of star clusters with
+%  ages that have been otherwise calibrated, for instance using
+%  the lithium depletion-boundary method.
+%  While this circumvents known modelling issues in molecular opacities
+%  and starspot coverage for young M dwarfs,
+%  the ages returned by this procedure depend on the ages
+%  assumed for each reference cluster.
+%  In this case, the most important reference is UCL, since TIC~141146667
+%  overlaps directly on its isochrone on the CAMD.
+%  We adopted the 16~Myr age for UCL from \cite{PecautMamajek2016}, which
+%  is consistent with ages determined by more recent sub-clustering
+%  analyses \cite{Ratzenbock2023} for the largest sub-populations.
+%  This in turns yields an isochronal age for TIC~141146667 of
+%  $t_{\rm iso}$=$16^{+19}_{-6}$\,Myr.
+%  Qualitatively, this range of uncertainty is consistent with no stars
+%  in the $\approx$40\,Myr IC~2602 cluster with similar redness as
+%  TIC~141146667 being equally bright.
 %FIXME: update discussion following consideration of anomalous CPV
@@
   \centering
+  \includegraphics[width=0.7\textwidth]{figures/sf3.pdf}
+  \caption{Dereddened Gaia DR3 color vs.~absolute magnitude diagram of
+  TIC~141146667 and comparison samples. 
+  TIC~141146667 is on the pre-main sequence; stars with the same color
+  that have arrived at the main sequence are typically 1.5\,magnitudes
+  fainter.  The star's location in this diagram broadly suggests an
+  age of 40-110\,Myr.  }
+  \label{fig:camd}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
   \includegraphics[width=0.7\textwidth]{figures/sf2.pdf}
@@
 first item constitutes evidence for youth since all known CPVs are
-$\lesssim$200\,Myr \cite{Bouma2024}.  Reference sequences for
-$\approx$40-50\,Myr clusters show no stars of equal luminosity and the
-same temperature, suggesting a photometric isochronal age upper limit
-of 50\,Myr.  The weak lithium absorption suggests an age of at least
-20\,Myr based on an empirical comparison using Gaia-ESO spectra, or at
-least 35\,Myr based on the \cite{Feiden2016} isochrones.  These
-considerations yield our adopted age range of 20-50\,Myr.
+$\lesssim$200\,Myr \cite{Bouma2024}.  The reference sequences for the
+Pleiades (112\,Myr, \cite{Dahm2015}) show a few stars of equal
+luminosity and the same temperature, suggesting a photometric
+isochronal age upper limit $\lesssim$150\,Myr.  The weak lithium
+absorption suggests an age of at least 20\,Myr based on an empirical
+comparison using Gaia-ESO spectra, or at least 35\,Myr based on the
+\cite{Feiden2016} isochrones.  These considerations yield our adopted
+age range of 35-150\,Myr.
 

### 2025-03-13 paper/collect_figs.sh

@@ -24,3 +24,5 @@ cp $r/tic1411_obsepoch/tic1411_obsepoch.pdf figures/sf1.pdf
 
 r="/Users/luke/Dropbox/proj/hotcold/drivers/results"
 cp $r/li_ew/li_vs_population.pdf figures/sf2.pdf
+
+cp $r/hrd/hrd_smalllim_dereddened.pdf figures/sf3.pdf

### 2025-03-14 paper/ms.tex
update

@@
 \cite{Koen2021}.  Here, we present time-series spectroscopy and
-photometry of a young ($t$=16\,Myr), rapidly-rotating ($P$=3.9\,hr)
+photometry of a rapidly-rotating ($P$=3.9\,hr)
 CPV, TIC~141146667. The spectra show coherent sinusoidal Balmer
@@
 %
-$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & 0.19$\pm$0.01  & 3 \\
+$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & 0.22$\pm$0.02  & 3 \\
 %
@@
 determined the star's spectral type to be M5.5Ve by visually comparing
-against the photometric standards presented by \cite{Bochanski2007};
-this qualitatively agrees with the effective temperature from the SED
-fitting \cite{Pecaut2013}.  With the effective temperature, stellar
-radius, and previously determined age, we then estimated the stellar
+against the photometric standards tabulated by \cite{Bochanski2007},
+which agrees with the effective temperature from the SED fitting
+\cite{Pecaut2013}.  Given the effective temperature, stellar radius, and
+age range (35-150\,Myr) derived below, we then estimated the stellar
 mass by interpolating against the PARSEC v1.2S isochrones
 \cite{Chen2014}.  Specifically, we used the distance metric defined in
-Equation~8 of \cite{Bouma2024} to select the model mass closest to the
-observed temperature, radius, and age.  We derived the uncertainty in
-the mass based by propagating the statistical uncertainties in each of
-these parameters.
+Equation~8 of \cite{Bouma2024} to select the model mass closest to a
+given observed temperature, radius, and age.  This exercise yielded a
+mass of $M_\star$=$0.20^{+0.02}_{-0.01}$ assuming an age of 35\,Myr, or
+a mass of $0.25^{+0.02}_{-0.01}$ assuming an age of 150\,Myr.  
+These in turn imply Keplerian corotation radii $R_{\rm
+cr}/R_\star$=1.75$\pm$0.07 and $R_{\rm cr}/R_\star$=1.89$\pm$0.07,
+respectively; this particular scale is relevant as it is theoretically
+expected to set the inner boundary at which corotating material can
+accumulate (e.g.~\cite{Townsend2005,Daley-Yates2024}).
+For our final quoted $M_\star$ and $R_{\rm cr}$ values we take a
+geometric mean of the extremes; we caution however that this choice is
+arbitrary, and that a more precise age would be needed to circumvent
+the systematic uncertainties in these parameters.
 
@@
 \cite{Hunt2024}.  We assumed an average $V$-band extinction $A_{\rm
-V}$=${0.12, 0.11, 0.10}\,{\rm mag}$ for USco \cite{Pecaut2016},
+V}$=$\{0.12, 0.11, 0.10\}\,{\rm mag}$ for USco \cite{Pecaut2016},
 IC~2602 \cite{Hunt2024}, and the Pleiades \cite{Hunt2024}
@@
 coefficients $k_X\equiv A_X/A_0$ tabulated in
-\citet{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.
-
-Figure~\ref{fig:camd} suggests that TIC~141146667 is
-older than USco, and potentially younger than the Pleiades.  The precision of this
-statement is set by the intrinsic scatter of the calibration
+\cite{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.
+
+Figure~\ref{fig:camd} shows that TIC~141146667 falls between
+the USco and Pleiades sequences, while nearly overlapping with
+IC~2602.  However, the precision of the implied age
+is set by the intrinsic scatter of these calibration
 sequences; the most luminous stars in the Pleiades of the same color
 have a similar absolute magnitude as TIC~141146667.
-Previous work \cite{Stauffer2021} has noted that in the Gaia
+Previous work \cite{Stauffer2021} has also noted that in the Gaia
 passbands, CPVs tend to be photometrically redder and more luminous
-than single stars in any given cluster.
-While this effect complicates any attempt at age inference based on this
-photometry, it suggests that the Pleiades may be a better comparison
-population than IC~2602.
-Broadly, we take the star's isochrone location to suggest age bounds
-$t_{\rm CAMD}$$\sim$40-150\,Myr.
+than single stars in any given cluster, similar to other rapid
+rotators.
+While this effect complicates any attempt at age inference based on
+the Gaia photometry, it suggests that the Pleiades may be a better
+comparison population than IC~2602.  Broadly, we take the star's
+isochrone location to suggest age bounds $t_{\rm
+CAMD}$$\sim$40-150\,Myr.
 
@@
 comparison, suggesting that since $M_{\rm K}$$=$6.67\,mag, $t_{\rm
-Li,th}$$\gtrsim$35\,Myr would be expected for complete depletion (see
-e.g.~Figure 7 from \cite{Wood2023}).
+Li,th}$$\gtrsim$35\,Myr is the theoretical age at which complete
+depletion occurs in a star with this luminosity (see e.g.~Figure 7
+from \cite{Wood2023}).
 
@@
   TIC~141146667 is on the pre-main sequence; stars with the same color
-  that have arrived at the main sequence are typically 1.5\,magnitudes
+  on the main sequence are $\approx$1.5\,magnitudes
   fainter.  The star's location in this diagram broadly suggests an
-  age of 40-110\,Myr.  }
+  age of 40-150\,Myr.  }
   \label{fig:camd}
@@
 \cite{Feiden2016} isochrones.  These considerations yield our adopted
-age range of 35-150\,Myr.
+age range of 40-150\,Myr.
 

### 2025-03-14 paper/ms.tex
update

@@
 %
-$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   & $1.72 \pm 0.06$  & 6 \\
+$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill
+  & $1.82 \pm 0.10$  & 6 \\
                                         & \hspace{3pt} radius ($R_\star$)	                               &                      \\
@@
 {\it Effective temperature, radius, mass, and spectral type}
-We determined the stellar effective temperature and radius by adopting
-the results from the spectral energy distribution fitting procedure
-described by \cite{Bouma2024}.  To summarize, this approach used
+We adopted the star's effective temperature and radius measured using
+the spectral energy distribution fitting procedure described by
+\cite{Bouma2024}.  To summarize, this approach used
 \texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
@@
 which agrees with the effective temperature from the SED fitting
-\cite{Pecaut2013}.  Given the effective temperature, stellar radius, and
-age range (35-150\,Myr) derived below, we then estimated the stellar
-mass by interpolating against the PARSEC v1.2S isochrones
-\cite{Chen2014}.  Specifically, we used the distance metric defined in
-Equation~8 of \cite{Bouma2024} to select the model mass closest to a
-given observed temperature, radius, and age.  This exercise yielded a
-mass of $M_\star$=$0.20^{+0.02}_{-0.01}$ assuming an age of 35\,Myr, or
-a mass of $0.25^{+0.02}_{-0.01}$ assuming an age of 150\,Myr.  
-These in turn imply Keplerian corotation radii $R_{\rm
-cr}/R_\star$=1.75$\pm$0.07 and $R_{\rm cr}/R_\star$=1.89$\pm$0.07,
-respectively; this particular scale is relevant as it is theoretically
-expected to set the inner boundary at which corotating material can
-accumulate (e.g.~\cite{Townsend2005,Daley-Yates2024}).
-For our final quoted $M_\star$ and $R_{\rm cr}$ values we take a
-geometric mean of the extremes; we caution however that this choice is
-arbitrary, and that a more precise age would be needed to circumvent
-the systematic uncertainties in these parameters.
+\cite{Pecaut2013}.
+
+Given the effective temperature, stellar radius, and age range
+(35-150\,Myr) derived below, we then estimated the stellar mass by
+interpolating against the PARSEC v1.2S isochrones \cite{Chen2014}.
+Specifically, we used the distance metric defined in Equation~8 of
+\cite{Bouma2024} to select the model mass closest to a given observed
+temperature, radius, and age.  This exercise yielded a mass of
+$M_\star$=$0.20\pm0.01$\,$M_\odot$ assuming an age of 35\,Myr, or a mass
+of $0.25\pm0.01$\,$M_\odot$ assuming an age of 150\,Myr.  These masses
+imply Keplerian corotation radii $R_{\rm cr}/R_\star$=1.75$\pm$0.07 and
+$R_{\rm cr}/R_\star$=1.89$\pm$0.07, respectively; this size scale is
+relevant because it is theoretically expected to set the inner boundary
+at which corotating material might accumulate
+(e.g.~\cite{Townsend2005,Daley-Yates2024}).  Our final quoted $M_\star$
+and $R_{\rm cr}$ values adopt the average of these extremes and a
+quadrature sum of their statistical uncertainties; we caution however
+that a more precise age would be needed to resolve the systematic
+uncertainties in these parameters.
 

### 2025-03-14 paper/ms.tex
update

@@
 show structured, periodic optical light curves suggestive of
-transiting opaque material corotating with the star
+transiting opaque material that corotates with the star
 \cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.  The
@@
 periodic variables (CPVs) are explained by complex distributions of
-starspots or faculae distributed across the stellar surfaces
+bright or dark regions on the stellar surfaces
 \cite{Koen2021}.  Here, we present time-series spectroscopy and
@@
 sharpest photometric features.  However, no independent evidence has
-yet been acquired for the presence of circumstellar material around these
-objects.  
-Transiting circumstellar clumps would geometrically imply an intrinsic
-occurrence a few to ten times the observed rate.  The question of
-whether circumstellar clumps exist in these systems could therefore be
-relevnat for 10-30\% of M dwarfs during their early lives.
+yet been acquired for the presence of any circumstellar material.  
+Geometrically, transiting clumps would imply an occurrence
+a few to at most ten times the observed rate.
+Such clumps could therefore exist around 10-30\% of M dwarfs during
+their early lives.
 
@@
 ruled out.  While dust may be present, to explain the H$\alpha$
-emission the circumstellar clumps must include plasma with a
+emission the clumps must include plasma with a
 significant population of hydrogen atoms in the $n$=3 excited state.
@@
 suggested that global-scale mean fields might be
-confined to a single hemisphere \cite{Brown2020}; such fields would
-yield accumulations of circumstellar material quite different
+confined to a single hemisphere \cite{Brown2020}; such fields could
+yield accumulation surfaces quite different
 from those that have previously been explored \cite{Townsend2008}.
@@
 the RV uncertainty at each epoch.  The uncertainty-weighted mean
-systemic velocity over all epochs on UT 2024-02-17 was
+systemic velocity over all epochs on 17~February~2024 (UT) was
 $\gamma$=0.6$\pm$1.5\,\kms.  The relative radial velocities about this
@@
 known young moving groups based on their positions and kinematics.
-TIC~141146667 is in the minority.  We calculated the probability
-of TIC~141146667 being part of any of the nearby known groups using
+TIC~141146667 is in the minority.  We calculated the probability of
+TIC~141146667 being part of any of the nearby known groups using
 BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  That particular model
-classifies it as a field star at $>$99.9\% confidence.  We also searched the
-local vicinity of TIC~141146667 for neighbors with similar projected on-sky
-velocities using \texttt{comove} \cite{Tofflemire2021}.  This yielded
-no strong candidates for co-moving stars with
-projected tangential velocities $\Delta v_{\rm T}$$<$5\,\kms
-that share its isochronal youth.
+classifies it as a field star at $>$99.9\% confidence.  We also searched
+the local vicinity of TIC~141146667 for neighbors with similar projected
+on-sky velocities using \texttt{comove} \cite{Tofflemire2021}.  This
+yielded no strong candidates for co-moving stars with projected
+tangential velocities $\Delta v_{\rm T}$$<$5\,\kms that share its
+isochronal youth.
 
 {\it Age: Isochrones}---The color and absolute magnitude of
-TIC~141146667 suggest that it is a pre-main sequence M dwarf, similar
-to all other known CPVs \cite{Stauffer2017,Stauffer2021,Bouma2024}.
-The star's proximity ($d$=58\,pc) and its high galactic latitude
+TIC~141146667 suggest that it is a pre-main sequence M dwarf, similar to
+all other known CPVs \cite{Stauffer2017,Stauffer2021,Bouma2024}.  The
+star's proximity ($d$=58\,pc) and its high galactic latitude
 ($b$=$+$53$^\circ$) yield negligible interstellar reddening along the
@@
 V}$=$\{0.12, 0.11, 0.10\}\,{\rm mag}$ for USco \cite{Pecaut2016},
-IC~2602 \cite{Hunt2024}, and the Pleiades \cite{Hunt2024}
-respectively.  We dereddened the photometry using the extinction
-coefficients $k_X\equiv A_X/A_0$ tabulated in
-\cite{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.
-
-Figure~\ref{fig:camd} shows that TIC~141146667 falls between
-the USco and Pleiades sequences, while nearly overlapping with
-IC~2602.  However, the precision of the implied age
-is set by the intrinsic scatter of these calibration
-sequences; the most luminous stars in the Pleiades of the same color
-have a similar absolute magnitude as TIC~141146667.
+IC~2602 \cite{Hunt2024}, and the Pleiades \cite{Hunt2024} respectively.
+We dereddened the photometry using the extinction coefficients
+$k_X\equiv A_X/A_0$ tabulated in \cite{GaiaCollaboration2018}, assuming
+that $A_0 = 3.1 E(B-V)$.
+
+Figure~\ref{fig:camd} shows that TIC~141146667 falls between the USco
+and Pleiades sequences, while nearly overlapping with IC~2602.  However,
+the precision of the implied age is set by the intrinsic scatter of
+these calibration sequences; the most luminous stars in the Pleiades of
+the same color have a similar absolute magnitude as TIC~141146667.
 Previous work \cite{Stauffer2021} has also noted that in the Gaia
-passbands, CPVs tend to be photometrically redder and more luminous
-than single stars in any given cluster, similar to other rapid
-rotators.
-While this effect complicates any attempt at age inference based on
-the Gaia photometry, it suggests that the Pleiades may be a better
+passbands, CPVs tend to be photometrically redder and more luminous than
+single stars in any given cluster, similar to other rapid rotators.
+While this effect complicates any attempt at age inference based on the
+Gaia photometry, it suggests that the Pleiades may be a better
 comparison population than IC~2602.  Broadly, we take the star's
-isochrone location to suggest age bounds $t_{\rm
-CAMD}$$\sim$40-150\,Myr.
-
-%  and applied the same reddening corrections as in \cite{Bouma2022}.
-%  To measure the isochrone age of TIC~141146667, we then followed the 
-%  empirical approach proposed by \cite{Gagne2020} and
-%  implemented in \cite{Bouma2022}.
-%  The idea is to estimate the star (or star cluster's) age by
-%  interpolating between the observed isochrones of star clusters with
-%  ages that have been otherwise calibrated, for instance using
-%  the lithium depletion-boundary method.
-%  While this circumvents known modelling issues in molecular opacities
-%  and starspot coverage for young M dwarfs,
-%  the ages returned by this procedure depend on the ages
-%  assumed for each reference cluster.
-%  In this case, the most important reference is UCL, since TIC~141146667
-%  overlaps directly on its isochrone on the CAMD.
-%  We adopted the 16~Myr age for UCL from \cite{PecautMamajek2016}, which
-%  is consistent with ages determined by more recent sub-clustering
-%  analyses \cite{Ratzenbock2023} for the largest sub-populations.
-%  This in turns yields an isochronal age for TIC~141146667 of
-%  $t_{\rm iso}$=$16^{+19}_{-6}$\,Myr.
-%  Qualitatively, this range of uncertainty is consistent with no stars
-%  in the $\approx$40\,Myr IC~2602 cluster with similar redness as
-%  TIC~141146667 being equally bright.
-%FIXME: update discussion following consideration of anomalous CPV
-% brightnesses and colors...
+location in the color--absolute magnitude diagram to suggest age bounds
+$t_{\rm CAMD}$$\sim$30-150\,Myr.
 
 {\it Age: Lithium}---The depletion of lithium due to $^7$Li(p,
-$\alpha$)$^4$He burning in the cores of low-mass stars has been
-studied for over sixty years
-\cite{Hayashi1963,Bildsten1997,Burke2004}.  \cite{Wood2023} provided
-an instructive recent overview: an abbreviated summary is that cooler
-and younger M dwarfs can show the 6707.8\,\AA\ doublet in absorption,
-$\gtrsim$10\% below their ``continua''.  Unlike Sun-like stars, the
-continuum for M dwarfs is poorly defined due to their molecular
-absorption.  We attempted a lithium measurement by constructing a
-wavelength-binned and Doppler-corrected TIC~141146667 spectrum,
-assigning its uncertainties based on the measured scatter across the
-five hour dataset.  We then compared this average spectrum against the
-nearest matching template from \cite{Bochanski2007}.  The data show a
-small depression near the expected lithium wavelength, potentially
-consistent with a $\Delta \lambda$$\approx$3\,\AA\ line broadening.
-This feature nominally yields ${\rm EW}_{\rm
+$\alpha$)$^4$He burning in the cores of low-mass stars has been studied
+for over sixty years \cite{Hayashi1963,Bildsten1997,Burke2004}.
+\cite{Wood2023} provided an instructive recent overview: an abbreviated
+summary is that cooler and younger M dwarfs can show the 6707.8\,\AA\
+doublet in absorption, $\gtrsim$10\% below their ``continua''.  Unlike
+Sun-like stars, the continuum for M dwarfs is poorly defined due to
+their molecular absorption.  We attempted a lithium measurement by
+constructing a wavelength-binned and Doppler-corrected TIC~141146667
+spectrum, assigning its uncertainties based on the measured scatter
+across the five hour dataset.  We then compared this average spectrum
+against the nearest matching template from \cite{Bochanski2007}.  The
+data show a small depression near the expected lithium wavelength,
+potentially consistent with a $\Delta \lambda$$\approx$3\,\AA\ line
+broadening.  This feature nominally yields ${\rm EW}_{\rm
 Li}$=71$^{+18}_{13}$\,m\AA, where the statistical uncertainties are
 evaluated using a bootstrap resampling technique from the statistical
-uncertainties in the spectrum.  The systematic uncertainties
-associated with the continuum normalization are larger, and likely
-comparable to the amplitude of the feature; we therefore treat the
-result of this measurement as a $2\sigma$ upper limit: ${\rm EW}_{\rm
-Li}$$<$107\,m\AA.
-
-Desite uncertainties in the details, what can be stated with
-confidence is that lithium is not abundant in the spectrum of
-TIC~141146667.  Figure~\ref{fig:liew_population} compares our upper
-limit against the lithium equivalent width measurements reported by
-\cite{Jeffries2023} based on the Gaia-ESO spectroscopic survey.  If
-the star were $\lesssim$20\,Myr old, given its temperature we would
-expect to see lithium in abundance ($>$400\,m\AA).  Since we do not,
-we conclude that $t_{\rm Li,emp}$$\gtrsim$20\,Myr.  The
-\cite{Feiden2016} isochrones provide a point for theoretical
-comparison, suggesting that since $M_{\rm K}$$=$6.67\,mag, $t_{\rm
-Li,th}$$\gtrsim$35\,Myr is the theoretical age at which complete
-depletion occurs in a star with this luminosity (see e.g.~Figure 7
-from \cite{Wood2023}).
+uncertainties in the spectrum.  The systematic uncertainties associated
+with the continuum normalization are larger, and likely comparable to
+the amplitude of the feature; we therefore treat the result of this
+measurement as a $2\sigma$ upper limit: ${\rm EW}_{\rm Li}$$<$107\,m\AA.
+
+Despite uncertainties in the details, what can be stated with confidence
+is that lithium is not abundant in the spectrum of TIC~141146667.
+Figure~\ref{fig:liew_population} compares our upper limit against the
+equivalent width measurements reported by \cite{Jeffries2023}
+based on the Gaia-ESO spectroscopic survey.  If the star were
+$\lesssim$20\,Myr old, at its temperature we would expect to see
+lithium in abundance ($>$400\,m\AA).  Since we do not, we can set an
+empirical bound on the lithium-derived age of $t_{\rm
+Li,emp}$$\gtrsim$20\,Myr.  The \cite{Feiden2016} lithium isochrones
+provide a point for theoretical comparison, and suggest that since
+$M_{\rm K}$$=$6.67\,mag, $t_{\rm Li,th}$$\gtrsim$35\,Myr is the
+theoretical age at which complete depletion occurs in a star with this
+luminosity (see e.g.~Figure 7 from \cite{Wood2023}).
 
@@
   fainter.  The star's location in this diagram broadly suggests an
-  age of 40-150\,Myr.  }
+  age of 30-150\,Myr.  }
   \label{fig:camd}
@@
   \caption{An upper limit on photospheric lithium for TIC~141146667
-  (green triangle) yields a lower limit on the star's age of $\gtrsim$20\,Myr.
-  Comparison stars are from the Gaia-ESO survey
-  \cite{Jeffries2023}; rich clusters in each age bin include
-  NGC\,2264 (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel (16.4\,Myr), NGC\,2547
-  (35.0\,Myr), IC\,2602 and IC\,2391 (42.0\,Myr), and NGC\,2451A
-  (50.0\,Myr). }
+  (green triangle) yields a lower limit on the star's age of
+  $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
+  \cite{Jeffries2023}; rich clusters in each age bin include NGC\,2264
+  (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
+  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2602 and IC\,2391 (42.0\,Myr),
+  and NGC\,2451A (50.0\,Myr). }
   \label{fig:liew_population}
@@
 \cite{Feiden2016} isochrones.  These considerations yield our adopted
-age range of 40-150\,Myr.
-
-%%%%%%%%
-%\texttt{astroARIADNE} compares the measured broadband flux
-%measurements against pre-computed model grids, and by default fits for
-%six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
-%Fe/H}], d \}$.  The distance  prior is drawn from
-%\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
-%generally unconstrained.  Given our selection criteria for the stars,
-%we assumed the following priors for the temperature, stellar size, and
-%extinction:
-%\begin{align}
-%  T_{\rm eff} / {\rm K}    &\sim \mathcal{U}(2000, 8000), \\
-%  R_\star / R_\odot  &\sim \mathcal{U}(0.1, 1.5), \\
-%  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
-%\end{align}
-%for \deleted{$\mathcal{N}$ the Gaussian and }$\mathcal{U}$ the uniform
-%distribution\deleted{s, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
-%truncated normal distribution with mean $\mu$, standard deviation
-%$\sigma$, and lower and upper bounds $a$ and $b$}.  We validated our
-%chosen upper bound on $A_{\rm V}$ using a 2MASS color-color diagram.
-%Finally, using \texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we
-%sampled the posterior probability assuming the default Gaussian
-%likelihood, and set a stopping threshold of ${\rm d}\log \mathcal{Z} <
-%0.01$, where $\mathcal{Z}$ denotes the evidence.
-
-{\it SED: No evidence for disk}
+age range of 150\,Myr.
+
+{\it SED: No evidence for disk}---Figure~\ref{fig:sed} shows the 
 ...
@@
     \hline
-    \multicolumn{3}{c}{Astrometry} \\ 
-    \hline
-    $\alpha$ & todo & Gaia\ DR3 \\
-    $\delta$ & todo & Gaia\ DR3 \\
+    \multicolumn{3}{c}{Astrometry \& Radial Velocity} \\ 
+    \hline
+    $\alpha_{2000}$ & 11:05:15.09   & Gaia\ DR3 \\
+    $\delta_{2000}$ & +59 15 05.57  & Gaia\ DR3 \\
     $\mu_{\alpha}$ (mas yr$^{-1}$ ) & -73.933 $\pm$ 0.022 & Gaia\ DR3 \\
@@
     RUWE                            &  1.23               & Gaia\ DR3 \\
+    RV (\kms)                     & 0.61 $\pm$ 1.47     & HIRES \\
     \hline
@@
     \hline
-    $TESS$ (mag) & todo & TESS\ \\
+    $TESS$ (mag)                    & 13.283 $\pm$ 0.010 & TIC8\     \\
     $G$ (mag)                       & 14.701 $\pm$ 0.002 & Gaia\ DR3 \\
@@
     % Ofek+2011 1.4Ghz emitter.  Helfand+2015 ditto.  Bruzewski+2021.
-    \hline
-    \multicolumn{3}{c}{Kinematics and Position} \\
-    \hline
-    $RV_{Bary}$ (km s$^{-1}$ ) & $13.35 \pm 3.39$ & HIRES \\
-    $U$ (\kms) & & \\
-    $V$ (\kms) & & \\
-    $W$ (\kms) & & \\
-    $X$ (pc) & -28.4 & \\
-    $Y$ (pc) &  19.8 & \\
-    $Z$ (pc) &  67.0 & \\
+    %\hline
+    %\multicolumn{3}{c}{Kinematics and Position} \\
+    %\hline
+    %$RV$ (\kms) & 0.61 $\pm$ 1.47 & HIRES \\
+    %$U$ (\kms)  & & \\
+    %$V$ (\kms)  & & \\
+    %$W$ (\kms)  & & \\
+    %$X$ (pc)    & -28.4 & \\
+    %$Y$ (pc)    &  19.8 & \\
+    %$Z$ (pc)    &  67.0 & \\
     \hline
@@
     \hline
-    $P_{rot}$ (hours) & $3.930 \pm 0.XXX$ & This work \\ 
-    $v \sin i_\star$(km s$^{-1}$) & $138 \pm 8$ & This work\\
-    $i_\star$($^\circ$) & $>$63 & This work \\
-    $T_{eff}$ (K) & 2972 $\pm$ 40 & \cite{Bouma2024}\\
-    %$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & YYY              & X \\
-    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & \cite{Bouma2024} \\
+    $T_{eff}$ (K) & 2972 $\pm$ 40 & \cite{Bouma2024} SED fit\\
+    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & \cite{Bouma2024} SED fit \\
+    $P_{\rm rot}$ (hours) & $3.930\pm 0.001$ & TESS \\ 
+    $v_{\rm eq}$ (\kms)  &  130$\pm$4  & Derived \\
+    $v_{\rm eq} \sin i_\star$(km s$^{-1}$) & $138 \pm 8$ & HIRES \\
+    $i_\star$($^\circ$) & $>$63 & Derived \\
     $A_V$ (mag) & 0 & \cite{Green2019} \\
-    $F_{bol}$ (erg cm$^{-2}$ s$^{-1}$ ) & todo & This work\\
-    $L_\star$ ($L_{\odot}$)  & todo & This work\\
-    $M_\star$ ($M_{\odot}$)  & 0.188 $\pm$ 0.012  & This work\\
-    $t_{\rm iso}$ (Myr) & $16^{+19}_{-6}$ &  This work \\
+    %$F_{bol}$ (erg cm$^{-2}$ s$^{-1}$ ) & todo & This work\\
+    %$L_\star$ ($L_{\odot}$)  & todo & This work\\
+    $M_\star$ ($M_{\odot}$)  & 0.22 $\pm$ 0.02  & PARSEC \cite{Chen2014}\\
+    ${\rm EW}_{\rm Li}$ (m\AA) & $<$107 & HIRES (2$\sigma$)\\
+    $t_{\rm CAMD}$ (Myr) & 30-150 &  Gaia DR3 \\
+    $t_{\rm Li,emp}$ (Myr) & $>$20 &  HIRES, \cite{Jeffries2023} \\
+    $t_{\rm Li,th}$ (Myr) & $>$35 &  HIRES, \cite{Feiden2016} \\
+    $t_{\rm adopted}$ (Myr) & 35-150 &  -- \\
     \hline
     \end{tabular}
-    \caption{Properties of \starname.}
-    \label{tab:stellarParameters}
+		\caption{Properties of \starname.  References:
+    Gaia DR3 \cite{GaiaDR3}, TESS \cite{Ricker2015},
+    TIC8 \cite{Stassun2019}, 2MASS \cite{Skrutskie2006}, ALLWISE
+    \cite{Cutri2014}.}
+    \label{tab:stparams}
 \end{table}

### 2025-03-14 drivers/run_SED_analysis.py
add sed analysis plotter

@@ -1,0 +1,323 @@
+"""
+(FORKED FROM CPV/COMPLEXROTATORS/SEDFIT.PY; HACKED FOR SPECIFICS)
+
+environment: (py38_ariadne)
+Citations: https://github.com/jvines/astroARIADNE/blob/master/citations.md
+"""
+
+from astroARIADNE.star import Star
+from astroARIADNE.fitter import Fitter
+#from astroARIADNE.plotter import SEDPlotter
+from astroARIADNE.bonusplotter import SEDPlotter
+
+import os
+from os.path import join
+import pandas as pd, numpy as np
+
+from complexrotators.observability import get_gaia_dr2_rows
+RESULTSDIR = 'results/sed_fit'
+
+from astropy.coordinates import SkyCoord
+from astropy import units as u
+from astroquery.vizier import Vizier
+
+# structure:
+# keys of ticids, values of dictionaries.
+#    the interior dictionaries have keys of "add" or "remove".  And then lists
+#    of the magnitudes to add, or the bandpasses to remove
+knownfailures = {
+    '58084670': { 'add' : [
+        (11.857, 0.021, '2MASS_J'),
+        (11.226, 0.023, '2MASS_H'),
+        (10.988, 0.018, '2MASS_K'),
+        (10.652, 0.023, 'WISE_RSR_W1'),
+        (10.530, 0.020, 'WISE_RSR_W2'),
+    ]  },
+    '267953787': { 'add' : [
+        (11.343, 0.022, '2MASS_J'),
+        (10.713, 0.024, '2MASS_H'),
+        (10.362, 0.021, '2MASS_K'),
+    ]  },
+    '50745567': {  'remove' : [
+        'STROMGREN_y',
+        'SDSS_z'
+    ] },
+    '368129164': {  'remove' : [
+        'SDSS_r',
+        'SDSS_i',
+        'SDSS_z',
+        'TYCHO_B_MvB',
+        'TYCHO_V_MvB',
+        'GROUND_JOHNSON_V',
+    ] },
+}
+
+def run_SED_analysis(ticid, trimlist=None, uniformpriors=0):
+    """
+    Run CQV-specific SED analysis.  Priors assume the star is a nearby M-dwarf
+    if uniformpriors==0, else assumes uniform priors.
+
+    Output goes to either /results/ariadne_sed_fitting/{starname}
+    or /results/ariadne_sed_fitting_UNIFORM/{starname}.
+
[…]

### 2025-03-14 paper/ms.tex
update

@@
 clumps are $n \sim 10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see
-Supplementary Methods Section~\ref{subsec:model}), a similar density
-to solar prominences, but ten to one hundred times more massive.  This
+Supplementary Methods Section~\ref{subsec:model}), a similar density to
+solar prominences, but ten to one hundred times more massive.  This
 observation rules out a ``starspot-only'' origin scenario for CPVs,
 \cite{Koen2021} since such scenarios have no means of explaining
-spectroscopic emission beyond the stellar disk.  Similarly, scenarios
-in which the circumstellar material is made only of dust are also
-ruled out.  While dust may be present, to explain the H$\alpha$
-emission the clumps must include plasma with a
-significant population of hydrogen atoms in the $n$=3 excited state.
-While this plasma is undoubtedly sculpted by the star's magnetic
-field, it could plausibly originate from three sites: the star, an old
-and undetected disk, or outgassing rocky bodies.  This latter
-possibility would render CPVs as extrasolar analogs of the Jupiter-Io
-plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
+spectroscopic emission beyond the stellar disk.  Similarly, scenarios in
+which the circumstellar material is made only of dust are also ruled
+out.  While dust may be present, to explain the H$\alpha$ emission the
+clumps must include plasma with a significant population of hydrogen
+atoms in the $n$=3 excited state.  While this plasma is undoubtedly
+sculpted by the star's magnetic field, it could plausibly originate from
+three sites: the star, an old and undetected disk, or outgassing rocky
+bodies.  This latter possibility would render CPVs as extrasolar analogs
+of the Jupiter-Io plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
 
 The other potential analog for the CPVs are the $\sigma$~Ori~E
-variables, a rare subset of B stars with radiatively-driven winds
-that accumulate into
-warped plasma tori \cite{Townsend2005,Townsend2008}.  These tori tend
-to have dense antipodal accumulations of plasma sculpted by
-tilted-dipole magnetic fields, and the transits of
-these clumps are thought to produce the observed broadband photometric variability
-through bound-free scattering \cite{Townsend2005} and
-Thomson scattering \cite{Berry2022}.  For $\sigma$~Ori~E and almost
-all of its analogs, the result is light curves that appear ``simple'',
-resembling those of eclipsing binaries \cite{Townsend2008}.  The two known
-exceptions, HD~37776 and HD~64740, show complex light curves
-resembling CPVs \cite{Mikulasek2020,Bouma2024} and have
-spectropolarimetric magnetic field maps indicating strong
-contributions from higher-order magnetic moments
-\cite{Kochukhov2011,Shultz2018}.  There are two implications: first,
-the complexity of CPVs may be a direct consequence of magnetic fields
-with highly multipolar contributions.  Second, CPVs could be a
+variables, a rare subset of B stars with radiatively-driven winds that
+accumulate into warped plasma tori \cite{Townsend2005,Townsend2008}.
+These tori tend to have dense antipodal accumulations of plasma sculpted
+by tilted-dipole magnetic fields, and the transits of these clumps are
+thought to produce the observed broadband photometric variability
+through bound-free scattering \cite{Townsend2005} and Thomson scattering
+\cite{Berry2022}.  For $\sigma$~Ori~E and almost all of its analogs, the
+result is light curves that appear ``simple'', resembling those of
+eclipsing binaries \cite{Townsend2008}.  The two known exceptions,
+HD~37776 and HD~64740, show complex light curves resembling CPVs
+\cite{Mikulasek2020,Bouma2024} and have spectropolarimetric magnetic
+field maps indicating strong contributions from higher-order magnetic
+moments \cite{Kochukhov2011,Shultz2018}.  There are two implications:
+first, the complexity of CPVs may be a direct consequence of magnetic
+fields with highly multipolar contributions.  Second, CPVs could be a
 source of astrophysical false positives in photometric searches for
-eclipsing binaries and transiting exoplanets around young
-pre-main sequence M dwarfs \cite{Johns-Krull2016,Bouma2020}.
+eclipsing binaries and transiting exoplanets around young pre-main
+sequence M dwarfs \cite{Johns-Krull2016,Bouma2020}.
 
-Pressing issues for future work include determining the composition
-and origin of the circumstellar material, understanding the exact role
-of the stellar magnetic field, and exploring the implied space weather
+Pressing issues for future work include determining the composition and
+origin of the circumstellar material, understanding the exact role of
+the stellar magnetic field, and exploring the implied space weather
 experienced by the close-in rocky exoplanets that, statistically
@@
 
-The material's composition -- either pure plasma, or else a dusty
-plasma -- can be clarified by time-series optical and infrared
+The material's composition -- either pure plasma, or else a dusty plasma
+-- can be clarified by time-series optical and infrared
 spectrophotometry.  While observations of CPVs in the optical have
-previously suggested chromaticity consistent with dust \cite{Tanimoto2020,Gunther2022,Koen2023},
-a gray opacity source such as electron scattering in a plasma
-transiting over starspots could also produce chromatic features
-\cite{Rackham2018}.  The composition and size distribution of any dust
-that is present could be most easily resolved by measuring the
-extinction curve for one or more CPVs from 1-10\,$\mu$m.  A
-dust composition similar to debris from rocky bodies seen around white
-dwarfs \cite{Reach2009} would indicate a rocky-body origin.  A 
-composition closer to the ISM would be indicative of condensed dust in
-an M dwarf wind, similar to that formed in the environments of more
-evolved stars \cite{Marigo2008}.
+previously suggested chromaticity consistent with dust
+\cite{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such as
+electron scattering in a plasma transiting over starspots might also
+produce chromatic features \cite{Rackham2018}.  The composition and size
+distribution of any dust that is present would be most easily resolved
+by measuring the extinction curve for one or more CPVs from
+1-10\,$\mu$m.  Composition and size distributions similar to debris from
+rocky bodies seen around white dwarfs \cite{Reach2009} would indicate a
+rocky-body origin.  Compositions and sizes to the ISM would be
+indicative of condensed dust in an M dwarf wind, similar to that formed
+in the environments of more evolved stars \cite{Marigo2008}.
 
-The role of the star's magnetic field could be better understood
-through new observations, and new theory.  From the theoretical
-perspective, there is an urgent need for rigid-field
-(magneto)-hydrodynamic modeling to go beyond previous work
-\cite{Townsend2005,Townsend2008} and to explore the effects of
-non-dipolar field contributions.
-In particular, dynamo simulations of fully-convective M dwarfs have
-suggested that global-scale mean fields might be
-confined to a single hemisphere \cite{Brown2020}; such fields could
-yield accumulation surfaces quite different
-from those that have previously been explored \cite{Townsend2008}.
-Observationally, spectropolarimetry has the potential to
-assess both the field strength and topology.  An independent
-probe could also be connected the recent work \cite{Kaur2024} showing
-that CPVs are variable radio emitters with emission components
-that can be both persistent, and also short-lived and highly
-polarized.  In particular, detecting radio emission produced by an electron
-cyclotron maser instability would provide a measurement of the field
-strength at the site of the emitting region.
+The role of the star's magnetic field could be better understood through
+new observations, and new theory.  From the theoretical perspective,
+there is an urgent need for rigid-field (magneto)-hydrodynamic modeling
+to go beyond previous work \cite{Townsend2005,Townsend2008} and to
+explore the effects of non-dipolar field contributions.  In particular,
+dynamo simulations of fully-convective M dwarfs have suggested that
+global-scale mean fields might be confined to a single hemisphere
+\cite{Brown2020}; such fields could yield accumulation surfaces quite
+different from those that have previously been explored
+\cite{Townsend2008}.  Observationally, spectropolarimetry has the
+potential to assess both the field strength and topology.  An
+independent probe could also be connected the recent work
+\cite{Kaur2024} showing that CPVs are variable radio emitters with
+emission components that can be both persistent, and also short-lived
+and highly polarized.  In particular, detecting radio emission produced
+by an electron cyclotron maser instability would provide a measurement
+of the field strength at the site of the emitting region.
 
 It is currently unclear what, if any, relationship CPVs have to the
-close-in exoplanets that exist around most M dwarfs
-\cite{Dressing2015}.  However, 0.3-3\% of young M dwarfs show the CPV
-phenomenon \cite{Rebull2020}, and our data show that the phenomenon
-occurs when clumps of circumstellar material transit the star.  The
-implied geometric correction suggests that an appreciable minority
-(10-30\%) of young M dwarfs -- the rapidly rotating ones with
-centrifugal magnetospheres -- host similar circumstellar environments
-to the CPVs.
+close-in exoplanets that exist around most M dwarfs \cite{Dressing2015}.
+However, 0.3-3\% of young M dwarfs show the CPV phenomenon
+\cite{Rebull2020}, and our data show that the phenomenon occurs when
+clumps of circumstellar material transit the star.  The implied
+geometric correction suggests that an appreciable minority (10-30\%) of
+young M dwarfs -- the rapidly rotating ones with centrifugal
+magnetospheres -- host similar circumstellar environments to the CPVs.
 
@@
 {\it Radial Velocity}---We measured radial velocities of TIC~141146667
-our HIRES spectra using a pipeline that we developed specifically
-for rapidly rotating stars.  Our method is based on template-matching
+our HIRES spectra using a pipeline that we developed specifically for
+rapidly rotating stars.  Our method is based on template-matching
 against synthetic spectra produced by the PHOENIX stellar atmosphere
@@
 
-For TIC~141146667, we measured the radial velocities using regions
-near the K~I (7700\,\AA) resonance line and three TiO bandheads
-(5160\,\AA, 5450\,\AA, and 5600\,\AA).  We
-selected these regions because they provided the best matches between the
-synthetic and observed spectra.  We then averaged the resulting redshift measurements
-over each order to produce the final measurement.  We used
-the scatter of resulting velocity measurements between orders to assign
-the RV uncertainty at each epoch.  The uncertainty-weighted mean
-systemic velocity over all epochs on 17~February~2024 (UT) was
-$\gamma$=0.6$\pm$1.5\,\kms.  The relative radial velocities about this
-mean are given in Table~\ref{tab:rv}.
+For TIC~141146667, we measured the radial velocities using regions near
+the K~I (7700\,\AA) resonance line and three TiO bandheads (5160\,\AA,
+5450\,\AA, and 5600\,\AA).  We selected these regions because they
+provided the best matches between the synthetic and observed spectra.
+We then averaged the resulting redshift measurements over each order to
+produce the final measurement.  We used the scatter of resulting
+velocity measurements between orders to assign the RV uncertainty at
+each epoch.  The uncertainty-weighted mean systemic velocity over all
+epochs on 17~February~2024 (UT) was $\gamma$=0.6$\pm$1.5\,\kms.  The
+relative radial velocities about this mean are given in
+Table~\ref{tab:rv}.
 
@@
 K~I (7700\,\AA) resonance line using the broadening kernel suggested by
-\cite{Gray2008}; taking the mean and standard deviation of the
-resulting value over all epochs yielded $v_{\rm eq} \sin
-i$=138$\pm$8\,\kms, consistent with the visual line broadening $\Delta
+\cite{Gray2008}; taking the mean and standard deviation of the resulting
+value over all epochs yielded $v_{\rm eq} \sin i$=138$\pm$8\,\kms,
+consistent with the visual line broadening $\Delta
 \lambda$$\approx$3\,\AA.  The star's equatorial velocity $v_{\rm eq}$
@@
 2$\sigma$ (2.5$^{\rm th}$ percentile of the inclination posterior).
+
 % from calc_max_amplitude_sinusoid_rv_timeseries.py
@@
 radial velocity time-series is ruled out at the rotation period for
-semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This
-sets an upper limit on the mass of any putative companion at the four
-hour period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
+semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This sets
+an upper limit on the mass of any putative companion at the four hour
+period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
 companions at wider separations, the Gaia DR3 renormalized unit weight
 error (RUWE), a proxy for the goodness of fit for a single-source
-astrometric model to the Gaia astrometry, is 1.23, within the
-usual range for apparently single sources.  There are no resolved
-sources in the Gaia DR3 point source catalog.  Finally, we checked the
-TESS light curve for evidence of secondary photometric periods by
-subtracting the mean CPV signal over each sector and performing a
-phase-dispersion minimization analysis
-\cite{Stellingwerf1978,2021zndo...1011188B}.  There were no secondary
-periods in the TESS data.  Previous work \cite{Bouma2024} has shown
-that about 30\% of CPVs show evidence for excess noise above the Gaia
-single-source astrometric model, and about 40\% of CPVs show evidence
-for unresolved binary companions based on the presence of secondary
-photometric periods.  This agrees with analyses showing that
-multi-periodic low-mass stars are generally unresolved binaries
-\cite{Tokovinin2018}.  Overall, the CPV binary fraction seems
-consistent with that for field M dwarfs \cite{Winters2019},
-pointing to a weak or non-existent connection between the CPV
-phenomenon and binarity.  For TIC~141146667 specifically, while we find 
-no evidence for stellar multiplicity, our data are minimally
-constraining for the scenario of a low-luminosity companion
-($F_1$/$F_2$$\lesssim$0.1) at large orbital separations.
+astrometric model to the Gaia astrometry, is 1.23, within the usual
+range for apparently single sources.  There are no resolved sources in
+the Gaia DR3 point source catalog.  Finally, we checked the TESS light
+curve for evidence of secondary photometric periods by subtracting the
+mean CPV signal over each sector and performing a phase-dispersion
+minimization analysis \cite{Stellingwerf1978,2021zndo...1011188B}.
+There were no secondary periods in the TESS data.  Previous work
+\cite{Bouma2024} has shown that about 30\% of CPVs show evidence for
+excess noise above the Gaia single-source astrometric model, and about
+40\% of CPVs show evidence for unresolved binary companions based on the
+presence of secondary photometric periods.  This agrees with analyses
+showing that multi-periodic low-mass stars are generally unresolved
+binaries \cite{Tokovinin2018}.  Overall, the CPV binary fraction seems
+consistent with that for field M dwarfs \cite{Winters2019}, pointing to
+a weak or non-existent connection between the CPV phenomenon and
+binarity.  For TIC~141146667 specifically, while we find no evidence for
+stellar multiplicity, our data are minimally constraining for the
+scenario of a low-luminosity companion ($F_1$/$F_2$$\lesssim$0.1) at
+large orbital separations.
 
-{\it Effective temperature, radius, mass, and spectral type}
-We adopted the star's effective temperature and radius measured using
-the spectral energy distribution fitting procedure described by
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/sf4.pdf}
+  \caption{
+    Spectral energy distribution of broadband photometric magnitudes
+    plotted over the best-fit BT-Settl stellar atmosphere model
+    \cite{Allard2012}.  This plot was made using \texttt{astroARIADNE}
+    \cite{Vines2022}.  The photometry extends from the Gaia DR3 blue
+    passband to WISE W3;  the redder (22 $\mu$m) W4 passband did not yield
+    a confident detection.  This fit yields the star's temperature and
+    size.  The lack of excess infrared flux relative to the photospheric
+    model sets an upper limit on emission from any circumstellar dust.
+    }
+  \label{fig:sed}
+\end{figure}
+
+{\it Effective temperature, radius, mass, and spectral type} We adopted
+the star's effective temperature and radius measured using the spectral
+energy distribution (SED) fitting procedure described by
 \cite{Bouma2024}.  To summarize, this approach used
@@
 Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
-2MASS, SDSS, and WISE $W1$ and $W2$.  This method has the most
-constraining power for the star's effective temperature (2972 $\pm$
-40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
-metallicity, and reddening are typically only weakly constrained.  We
-determined the star's spectral type to be M5.5Ve by visually comparing
-against the photometric standards tabulated by \cite{Bochanski2007},
-which agrees with the effective temperature from the SED fitting
-\cite{Pecaut2013}.
+2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting best-fit SED is
+shown in Figure~\ref{fig:sed}.  This method has the most constraining
+power for the star's effective temperature (2972 $\pm$ 40\,K) and radius
+(0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity, metallicity, and
+reddening are typically only weakly constrained.  We determined the
+star's spectral type to be M5.5Ve by visually comparing against the
+photometric standards tabulated by \cite{Bochanski2007}, which agrees
+with the effective temperature from the SED fitting \cite{Pecaut2013}.
 
@@
 
-{\it SED: No evidence for disk}---Figure~\ref{fig:sed} shows the 
+{\it Upper and Low Bounds on Dust}---An upper limit on the amount of hot
+dust follows from the lack of an infrared excess.  A lower limit follows
+from the assumption that most of the broadband optical depth comes from 
+dust, rather than some other source.
+Figure~\ref{fig:sed} shows the SED; ...
+%TODO TODO LEFT OFF HERE
 ...

### 2025-03-14 paper/collect_figs.sh

@@ -26,3 +26,5 @@ r="/Users/luke/Dropbox/proj/hotcold/drivers/results"
 cp $r/li_ew/li_vs_population.pdf figures/sf2.pdf
 
 cp $r/hrd/hrd_smalllim_dereddened.pdf figures/sf3.pdf
+
+cp $r/sed_fit/TIC_141146667/plots_irexcess/SED.pdf figures/sf4.pdf

### 2025-03-14 paper/ms.tex
update

@@
 measured broadband magnitudes against pre-computed model grids.
-Specifically, we used the broadband magnitudes from Gaia DR2, APASS,
-2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting best-fit SED is
-shown in Figure~\ref{fig:sed}.  This method has the most constraining
-power for the star's effective temperature (2972 $\pm$ 40\,K) and radius
-(0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity, metallicity, and
-reddening are typically only weakly constrained.  We determined the
-star's spectral type to be M5.5Ve by visually comparing against the
-photometric standards tabulated by \cite{Bochanski2007}, which agrees
-with the effective temperature from the SED fitting \cite{Pecaut2013}.
+Specifically, we performed the fit using the broadband magnitudes from
+Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting
+best-fit SED is shown in Figure~\ref{fig:sed}.  This method has the most
+constraining power for the star's effective temperature (2972 $\pm$
+40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
+metallicity, and reddening are typically only weakly constrained.  We
+determined the star's spectral type to be M5.5Ve by visually comparing
+the HIRES spectra against the photometric standards tabulated by
+\cite{Bochanski2007}, which agrees with the effective temperature from
+the SED fitting \cite{Pecaut2013}.
 
@@
 dust follows from the lack of an infrared excess.  A lower limit follows
-from the assumption that most of the broadband optical depth comes from 
-dust, rather than some other source.
-Figure~\ref{fig:sed} shows the SED; ...
+if one assumes that most of the broadband optical depth comes from
+absorption and scattering by dust, rather than any radiative processes
+associated with the plasma.
+
+How much dust is allowed, given the lack of an infrared excess?
+Figure~\ref{fig:sed} shows the SED.  While AllWISE \cite{Cutri2014}
+yielded a confident W3 detection (9.8$\sigma$), the W4 extraction
+yielded only a marginal (1.7$\sigma$) indication of detectable flux.
+Similar to other CPVs \cite{Stauffer2017,Bouma2024}, the photometric
+uncertainties from WISE W1 and W2 allow at most a $\lesssim$2\% excess
+at 3-5\,$\mu$m relative to the stellar photosphere, and a $\lesssim$5\%
+excess at 10\,$\mu$m (W3).  A simple approximation is to assume $T_{\rm
+dust}$=1500\,K, typical for dust near the star (see \cite{Zhan2019} for
+discussion regarding dust sublimation).  We then treat emission from the
+dust and the star as Planck functions, requiring $F_{\lambda,\star} > f
+\cdot F_{\lambda,\mathrm{dust}}$, for $f$ the scaling factor set by the
+WISE photometric uncertainty.  For this condition to hold, we find that
+the bolometric flux ratio $F_{\rm dust}/F_{\star}$$<$6$\cdot$10$^{-3}$.
+Scaling the associated luminosities ($L = \sigma_{\rm SB} T_{\rm eff}^4
+/ (4\pi R^2)$) implies an emitting area for the dust $<$10\% of the
+star's surface area.  Converting this constraint to a dust mass requires
+an assumption regarding the grain properties; taking a grain density
+$\rho$=3\,g\,cm$^{-3}$ typical for silicate grains, and a fixed size
+$a$=1\,$\mu$m \cite{Tanimoto2020,Gunther2022,Koen2023} yields an upper
+limit of $M_{\rm dust}\lesssim$10$^{17}$\,g.
+
+By way of comparison, the lower limit follows 
+%FIXME TODO finish!!
+
+The associated
+
+which implies a 
+Since the effective temperatures
+
+luminosity
+
+Under this approximation,
+
+, reporting $W4$=8.4 with no uncertainty.  
+The WISE images, available through the IRSA archive, concur.
+
+%WISE_RSR_W3 9.8380 0.0450
+%W4 = 8.392 +/- nan
 %TODO TODO LEFT OFF HERE
@@
 	Acknowledge TESS...
+  Acknowledge use of IRSA.
 

### 2025-03-17 paper/ms.tex
update

@@
 \normalfont
-Approximately one percent of red dwarfs younger than 100 million years
+Roughly one percent of red dwarfs younger than 100 million years
 show structured, periodic optical light curves suggestive of
@@
 emission at twice to four times the star's equatorial velocity,
-demonstrating the presence of extended clumps of circumstellar
+demonstrating the existence of extended clumps of circumstellar
 plasma --- a plasma torus.  Given that long-lived condensations of
@@
 {\it Radial Velocity}---We measured radial velocities of TIC~141146667
-our HIRES spectra using a pipeline that we developed specifically for
+from our HIRES spectra using a pipeline that we developed for
 rapidly rotating stars.  Our method is based on template-matching
@@
 each epoch.  The uncertainty-weighted mean systemic velocity over all
-epochs on 17~February~2024 (UT) was $\gamma$=0.6$\pm$1.5\,\kms.  The
+epochs on 17~February~2024 was $\gamma$=0.6$\pm$1.5\,\kms.  The
 relative radial velocities about this mean are given in
@@
     plotted over the best-fit BT-Settl stellar atmosphere model
-    \cite{Allard2012}.  This plot was made using \texttt{astroARIADNE}
+    \cite{Allard2012}.  This plot was made from an adaptation of \texttt{astroARIADNE}
     \cite{Vines2022}.  The photometry extends from the Gaia DR3 blue
-    passband to WISE W3;  the redder (22 $\mu$m) W4 passband did not yield
+    passband to WISE W3;  the W4 passband (22 $\mu$m) did not yield
     a confident detection.  This fit yields the star's temperature and
     size.  The lack of excess infrared flux relative to the photospheric
-    model sets an upper limit on emission from any circumstellar dust.
+    model sets an upper limit on emission from circumstellar dust.
     }
@@
 if one assumes that most of the broadband optical depth comes from
-absorption and scattering by dust, rather than any radiative processes
+dust absorption and scattering, rather than any radiative processes
 associated with the plasma.
@@
 at 3-5\,$\mu$m relative to the stellar photosphere, and a $\lesssim$5\%
-excess at 10\,$\mu$m (W3).  A simple approximation is to assume $T_{\rm
-dust}$=1500\,K, typical for dust near the star (see \cite{Zhan2019} for
-discussion regarding dust sublimation).  We then treat emission from the
-dust and the star as Planck functions, requiring $F_{\lambda,\star} > f
-\cdot F_{\lambda,\mathrm{dust}}$, for $f$ the scaling factor set by the
-WISE photometric uncertainty.  For this condition to hold, we find that
-the bolometric flux ratio $F_{\rm dust}/F_{\star}$$<$6$\cdot$10$^{-3}$.
-Scaling the associated luminosities ($L = \sigma_{\rm SB} T_{\rm eff}^4
-/ (4\pi R^2)$) implies an emitting area for the dust $<$10\% of the
-star's surface area.  Converting this constraint to a dust mass requires
-an assumption regarding the grain properties; taking a grain density
-$\rho$=3\,g\,cm$^{-3}$ typical for silicate grains, and a fixed size
-$a$=1\,$\mu$m \cite{Tanimoto2020,Gunther2022,Koen2023} yields an upper
-limit of $M_{\rm dust}\lesssim$10$^{17}$\,g.
-
-By way of comparison, the lower limit follows 
-%FIXME TODO finish!!
-
-The associated
-
-which implies a 
-Since the effective temperatures
-
-luminosity
-
-Under this approximation,
-
-, reporting $W4$=8.4 with no uncertainty.  
-The WISE images, available through the IRSA archive, concur.
-
-%WISE_RSR_W3 9.8380 0.0450
-%W4 = 8.392 +/- nan
-%TODO TODO LEFT OFF HERE
-...
+excess at 10\,$\mu$m (W3).  To estimate the implied mass bound, we
+assume $T_{\rm dust}$=1500\,K, typical for dust near the star (see
+\cite{Zhan2019} for discussion regarding dust sublimation).  We then
+treat emission from the dust and the star as Planck functions,
+requiring $F_{\lambda,\star} > f \cdot F_{\lambda,\mathrm{dust}}$, for
+$f$ the scaling factor set by the WISE photometric uncertainty.  For
+this condition to hold, we find that the bolometric flux ratio $F_{\rm
+dust}/F_{\star}$$<$6$\cdot$10$^{-3}$.  Scaling the associated
+luminosities ($L = \sigma_{\rm SB} T_{\rm eff}^4 / (4\pi R^2)$)
+implies an emitting area for the dust $<$10\% of the star's surface
+area.  Converting this constraint to a dust mass requires an
+assumption regarding the grain properties; assuming a grain density
+$\rho_{\rm d}$=3\,g\,cm$^{-3}$ typical for silicate grains, and a fixed grain
+size $a$=1\,$\mu$m \cite{Tanimoto2020,Gunther2022,Koen2023} yields an
+upper limit of $M_{\rm dust}\lesssim$10$^{17}$\,g.
+
+By way of comparison, the lower limit follows from requiring the
+optical depth $\tau$ to be at least unity.
+The optical depth can be written $\tau = n \sigma \ell = N \sigma$,
+where $\sigma$ is the cross-section, $n$ is the number density, $\ell$
+is the path length, and $N$ is the column density.
+For spherical dust grains in the optical, $\sigma = Q_{\rm ext} \pi
+a^2$, where $Q_{\rm ext}$ is the extinction efficiency parameter,
+tabulated e.g.~by \cite{Croll2014} in their Figure 13.
+\cite{Sanderson2023} calculated the relevant cloud mass scaling
+assuming a spherical dust clump of size $r$,
+and they found
+\begin{equation}
+  M_{\rm dust} \gtrsim 1.6 \cdot 10^{15}\, {\rm g}\ 
+  \left( \frac{\tau}{1} \right)
+  \left( \frac{Q_{\rm ext}}{3} \right)^{-1}
+  \left( \frac{r}{0.1\,R_\star} \frac{R_\star}{0.34\,R_\odot} \right)^2
+  \left( \frac{a}{1\,\mathrm{\mu m}} \right)
+  \left( \frac{\rho_{\rm d}}{3\,\mathrm{g\,cm^{-3}}} \right).
+\end{equation}
+By way of comparison, prominences of the Sun typically have gas masses
+of order $10^{14}\,g$-$10^{16}$\,g \cite{VialEngvold2015}, whereas a
+planetesimal of this mass with a bulk density of 1\,g\,cm$^{-3}$ would
+have a diameter of order one kilometer.  Halley's comet has a mass of
+order $10^{17}$\,g \cite{Rickman1989}, of which of order one part in a
+thousand is shed per orbit, most of which inspirals toward the Sun due
+to Poynting-Robertson drag.
+
+Broadly, these calculations suggest that if dust is responsible for
+the broadband variability of CPVs, it would need to be concentrated in
+clumps with masses in the range of $10^{15}$-$10^{17}$\,g.
 
@@
   \hline 
-  60357.450329 & 1.72 & 5.86 \\
-  60357.461255 & -5.41 & 2.37 \\
-  60357.472181 & -1.21 & 2.64 \\
-  60357.483109 & 2.83 & 2.87 \\
-  60357.494030 & 6.52 & 7.53 \\
-  60357.504949 & -3.0 & 1.44 \\
-  60357.515873 & 0.01 & 1.21 \\
-  60357.526794 & -0.38 & 7.03 \\
-  60357.537717 & -3.92 & 2.71 \\
-  60357.548639 & 7.92 & 6.75 \\
-  60357.559566 & 4.94 & 8.84 \\
-  60357.570487 & -3.26 & 3.06 \\
-  60357.581408 & 0.83 & 1.34 \\
-  60357.592330 & 1.4 & 8.24 \\
-  60357.603251 & -8.05 & 3.94 \\
-  60357.614172 & -3.26 & 3.07 \\
-  60357.625095 & -3.84 & 7.55 \\
-  60357.636019 & -1.6 & 2.26 \\
-  60357.646940 & 0.82 & 2.91 \\
-  60357.657861 & 3.53 & 3.95 \\
-  60357.668781 & 5.2 & 12.14 \\
+  60357.450329 & 2.73 & 5.86 \\
+  60357.461255 & -4.40 & 2.37 \\
+  60357.472181 & -0.19 & 2.64 \\
+  60357.483109 & 3.84 & 2.87 \\
+  60357.494030 & 7.53 & 7.53 \\
+  60357.504949 & -1.98 & 1.44 \\
+  60357.515873 & 1.02 & 1.21 \\
+  60357.526794 & 0.64 & 7.03 \\
+  60357.537717 & -2.91 & 2.71 \\
+  60357.548639 & 8.93 & 6.75 \\
+  60357.559566 & 5.95 & 8.84 \\
+  60357.570487 & -2.25 & 3.06 \\
+  60357.581408 & 1.84 & 1.34 \\
+  60357.592330 & 2.41 & 8.24 \\
+  60357.603251 & -7.04 & 3.94 \\
+  60357.614172 & -2.24 & 3.07 \\
+  60357.625095 & -2.83 & 7.55 \\
+  60357.636019 & -0.59 & 2.26 \\
+  60357.646940 & 1.84 & 2.91 \\
+  60357.657861 & 4.54 & 3.95 \\
+  60357.668781 & 6.21 & 12.14 \\
   \hline
   \end{tabular}
-  \caption{TIC~141146667 radial velocities.}
+  \caption{TIC~141146667 radial velocities relative to the systemic velocity.}
   \label{tab:rv}

### 2025-03-17 paper/ms.tex
update

@@
 transiting clumps of circumstellar material corotate with the star
-\cite{Stauffer2017,Gunther2022,Bouma2024}, or that these stars
-represent an extreme in naturally-occurring distributions of starspots
-or faculae \cite{Koen2021}.  Currently, the main argument against a
-starspot-only explanation invokes the timescales and amplitudes of the
-sharpest photometric features.  However, no independent evidence has
-yet been acquired for the presence of any circumstellar material.  
-Geometrically, transiting clumps would imply an occurrence
-a few to at most ten times the observed rate.
-Such clumps could therefore exist around 10-30\% of M dwarfs during
-their early lives.
+\cite{Stauffer2017,Gunther2022,Bouma2024}, or that these stars represent
+an extreme in naturally-occurring distributions of starspots or faculae
+\cite{Koen2021}.  
+% TODO: might want to plug Shapiro, Seager, ACC dark faculae...
+While the main argument against a starspot-only explanation invokes the
+timescales and amplitudes of the sharpest photometric features, no
+independent evidence has yet been acquired for the presence of any
+circumstellar material.  Geometrically, transiting clumps would imply an
+occurrence a few to at most ten times the observed rate.  Such clumps
+could therefore exist around 10-30\% of M dwarfs during their early
+lives.
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/f1.png}
+  \includegraphics[width=0.7\textwidth]{figures/f1.pdf}
   \caption[]{{\bf Figure 1 (Movie):  TIC~141146667 is a complex periodic
-  variable (CPV).} For the best experience, please view the online movie
+  variable (CPV).}  The online movie,
   available
   \href{https://lgbouma.com/movies/TIC141146667_20250116.mp4}{here},
-  which spans a baseline of 5{,}784 cycles irregularly sampled over three
+  shows a baseline of 5{,}784 cycles irregularly sampled over three
   years.  The TESS light curve is phased to the \periodhr\ hour period in
@@
   stellar rotation, and (we hypothesize) of corotating clumps of
-  circumstellar material.  Raw data acquired with two minute
-  sampling are in gray; black is their average.  Similar to other members
-  of this class, the sharp photometric features persist for tens to
-  thousands of rotational cycles. }
+  circumstellar material.  Raw data acquired with two minute sampling
+  are in gray; black averages to 100 points per cycle.  Similar to
+  other stars of this class, the sharp photometric features persist
+  for tens to thousands of rotational cycles. }
   \label{fig:lc}

### 2025-03-17 paper/collect_figs.sh

@@ -3,7 +3,7 @@ r="/Users/luke/Dropbox/proj/cpv/results"
 ##########################################
 # figure1: TIC 141146667 is a complex periodic variable.
 # still: c1265-1268, s48, 2022-02-16 to 2022-02-17
-cp $r/movie_phase_timegroups/TIC_141146667/TIC_141146667_0081_2min_phase_timegroups.png figures/f1.png
+cp $r/movie_phase_timegroups/TIC_141146667/TIC_141146667_0081_2min_phase_timegroups.pdf figures/f1.pdf
 
 # Animated supporting: Movie of S41, S48, S75 TESS photometry, cycle-grouped
 cp $r/movie_phase_timegroups/TIC_141146667/movie_TIC1411_flux_phase_bow.mov movies/m1.mov

### 2025-03-17 drivers/plot_lineevolnpanel.py
add plot_lineevolnpanel.py

@@ -1,0 +1,271 @@
+#############
+## IMPORTS ##
+#############
+import os, pickle
+from os.path import join
+from glob import glob
+from datetime import datetime
+from copy import deepcopy
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from numpy import array as nparr
+
+import matplotlib as mpl
+import matplotlib.colors as colors
+from matplotlib import rcParams
+
+from astropy import units as u, constants as const
+from astropy.coordinates import SkyCoord
+from astropy.io import fits
+from astropy.time import Time
+from astropy.table import Table
+
+import matplotlib.patheffects as pe
+from matplotlib.ticker import MaxNLocator, FixedLocator, FuncFormatter
+from matplotlib.transforms import blended_transform_factory
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes
+
+from scipy.ndimage import gaussian_filter1d
+
+from aesthetic.plot import savefig, format_ax, set_style
+
+
+from scipy.ndimage import gaussian_filter1d
+from specutils.spectra import Spectrum1D, SpectralRegion
+from specutils.fitting import fit_generic_continuum
+import warnings
+from rudolf.plotting import multiline
+
+from complexrotators.getters import get_specriver_data
+from cdips_followup.spectools import remove_cosmic_rays
+
+def plot_lineevolnpanel(outdir, starid=None, jstr=None, remove_cosmics=0):
+    """
+    starid: e.g. 'TIC402980664'
+    jstr: e.g. 'j531',
+    """
+
+    ticid = starid.lstrip("TIC")
+    deltawav = 15
+    dlambda = deltawav*1.
+    # get data
+    lines = [
+        'Hα',
+        'Hγ',
+        'Hδ',
+        'He',
+        #'Ca[K]',
+        'Li',
+        'K',
+        #'Ca[H] + Hε',
+        #'CaI',
+        #'Na D1',
+    ]
+
+    gaussian_filter_sigmas = [
+        4,
+        6,
+        8,
+        6,
+        #40,
+        6,
+        4,
+    ]
+
+    λ0s = [
+        6562.8,
+        4340.0,
+        4101.75,
+        5875.62,
+        #3933.66,
+        6708.,
+        7699.,
+    ]
+
+    ylims = [
+        [0.5, 3.5], # ha
+        [0.3, 8.5], # hgamma
+        [-0.1, 10.5], # hd
[…]

### 2025-03-17 paper/ms.tex
update

@@
 Figure~\ref{fig:spec} shows the data from February 2024.  Over
-timescales of years, CPVs maintain the same period, while their
+timescales of years, CPVs maintain a fixed period while their
 photometric morphology evolves.  TIC~141146667 indeed evolved relative
 to the February 2022 discovery data \cite{Bouma2024}.  In the February
-2024 data, the average photometric signal showed a small brightening
+2024 TESS data, the average photometric signal showed a small brightening
 over 45\% of the period, followed by a complex flux dip spanning 55\%
@@
   \includegraphics[width=0.99\textwidth]{figures/sf1.pdf}
-  \caption{Photometric evolution of TIC 141146667 near the epoch of
-  spectroscopic observation (green bar). 
+  \caption{Photometric evolution of TIC 141146667 near the Keck/HIRES observation (green bar). 
   {\bf Panel a}: TESS simple aperture photometry. 
@@
   (BTJD 3356-3358.5) and Moon (BTJD 3359.5-3360.5).
+  Raw two minute data are in gray; black time-averages ten minute
+  sampling.
   {\bf Panels b,c}: Folded light curve before and after spectroscopy.
-  Although some evolution in the light curve morphology occurred between
-  the two epochs, the large, complex eclipse feature remained present.
+  Raw two minute data are in gray; black phase-averages to 100 points
+  per cycle.
+  In the BTJD 3352-3356 window, a state switch occurred near BTJD 3353,
+  in which the dip at $\phi$$\approx$0.8 disappeared.
+  While the large, complex eclipse feature remained present before and
+  after the HIRES sequence, its photometric shape evolved during the
+  data gap.
   }
@@
 
-{\it Photometry:} TESS observed
-TIC~141146667 ($T$=13.3) in Sectors 14, 15, 21, 41, 48, and 75.
-Two-minute data were acquired during Sectors 41, 48 (TESS DDT039,
-PI: Kunimoto), and 75 (TESS Program G06030, PI: Bouma).  The data
-from Sectors 14, 15, and 21 had a 30-minute cadence, which
-smears sharp features over the $<$4\,hour period
-(see \cite{Gunther2022}).  The nearest known star, TIC~141146666
-($T$=14.5), is 25$''$ from TIC~141146667 and is photometrically stable
-in the pixel-level TESS data.
-
-Figure~\ref{fig:fulllc} shows the data from Sector~75, which were
-acquired using the camera that pointed closest to the ecliptic.  The
-largest gap in coverage is from BTJD 3356.0~-~3358.5, and includes
-the Keck/HIRES observation epoch (green bar).   There are no flux
-measurements reported during this interval because the Earth was
-within 25$^\circ$ the camera's boresight, yielding high levels of
-scattered light.  From BTJD 3359.4~-~3362.0, the Moon then passed
-within 25$^\circ$ of the camera's boresight.  Based on the observed
-level of scattered light in the optimal TIC~141146667 aperture, we
-manually masked out times from 3359.40~-~3360.13, and judged the
-remainder of the data during the lunar approach to be usable.  The
-small data gaps from BTJD 3353.55~-~3353.77 and from BTJD
-3360.12~-~3360.33 were caused by data downlinks at the spacecraft's
-perigee and apogee, respectively.
+{\it Photometry:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14,
+15, 21, 41, 48, and 75.  Two-minute data were acquired during Sectors
+41, 48 (TESS DDT039, PI: Kunimoto), and 75 (TESS Program G06030, PI:
+Bouma).  The data from Sectors 14, 15, and 21 had a 30-minute cadence,
+which smears sharp features over the $<$4\,hour period (see
+\cite{Gunther2022}).  The field is not crowded:  the nearest known
+star, TIC~141146666 ($T$=14.5), is 25$''$ from TIC~141146667 and is
+photometrically stable in the pixel-level TESS data.
+
+Figure~\ref{fig:fulllc} shows the TESS Sector~75 data acquired near
+the epoch of spectroscopy.  The gap in coverage from BTJD
+3356.0~-~3358.5 occurred because the Earth was within 25$^\circ$ of
+the TESS camera's boresight, yielding high levels of scattered light;
+this gap included the Keck/HIRES observation epoch (green bar).  From
+BTJD 3359.4~-~3362.0, the Moon then passed within 25$^\circ$ of the
+camera's boresight.  Based on the observed level of scattered light in
+the optimal TIC~141146667 aperture, we manually masked out times from
+3359.40~-~3360.13, and judged the remainder of the data during the
+lunar approach to be usable.  Small data gaps from BTJD
+3353.55~-~3353.77 and from BTJD 3360.12~-~3360.33 were caused by data
+downlinks at the spacecraft's perigee and apogee, respectively.
+
+Broadly, Figure~\ref{fig:fulllc} shows that a large, complex eclipse
+feature was present before and after the HIRES data were
+acquired.  From BTJD 3352~-~3356, this eclipse had two sharp local
+minima;  the local minimum at $\phi$$\approx$0.8 disappeared following
+the flare at BTJD 3353, yielding an eclipse more closely resembling a
+long ``V'' than a ``W''.  Similar state changes have previously been
+noted and discussed \cite{Stauffer2017,Bouma2024}.  The photometric
+shape therefore evolved during the twelve cycles spanning the
+3356~-~3358 gap, since the average shape from 3358-3363 more
+closely resembles the initial ``W''.
 
 {\it Spectroscopy:}
-We observed TIC~141146667 ($V$=16.2) with Keck/HIRES for five hours over a
-second-half night spanning UT 2024-02-17 10:47 to UT 2024-02-17
-16:13.  The star's airmass over this window spanned $z$=1.2-2.2, and
-we opted for a fixed 15 minute cadence over the entire sequence,
-except for a final 10 minute exposure due to increasing sky
-brightness at sunrise.  We observed without the iodine cell and used
-the C2 decker (0$\farcs$86$\times$14$\farcs$0) in the red instrument
-configuration, yielding a spectral resolution $R$$\approx$45{,}0000
-($\delta v$$\approx$6.7\,\kms; $\delta v / v_{\rm
-eq}$$\approx$0.05).  We binned the CCD readout by a factor of three
-in the spatial dimension, yielding $\approx$1,000 photons (S/N=33)
-per pixel in the continuum at 6500\,\AA, at minimum airmass.  Strong
-winds contributed to 1\farcs2$\pm$0\farcs2 seeing over the night,
-but conditions were otherwise favorable.  We reduced the
-echelleogram to a one-dimensional spectrum using the standard
-techniques of the California Planet Survey \cite{Howard2010}.
+We observed TIC~141146667 ($V$=16.2) with Keck/HIRES for five hours over
+a second-half night spanning 17 February 2024 10:47 to 16:13 (UT).
+The star's airmass over this window spanned $z$=1.2-2.2, and we opted
+for a fixed 15 minute cadence over the entire sequence, except for a
+final 10 minute exposure due to increasing sky brightness at sunrise.
+We observed without the iodine cell and used the C2 decker
+(0$\farcs$86$\times$14$\farcs$0) in the red instrument configuration,
+yielding a spectral resolution $R$$\approx$45{,}0000 ($\delta
+v$$\approx$6.7\,\kms; $\delta v / v_{\rm eq}$$\approx$0.05).  We binned
+the CCD readout by a factor of three in the spatial dimension, yielding
+$\approx$1,000 photons (S/N=33) per pixel in the continuum at 6500\,\AA,
+at minimum airmass.  Strong winds contributed to 1\farcs2$\pm$0\farcs2
+seeing over the night, but conditions were otherwise favorable.  We
+reduced the echelleogram to a one-dimensional spectrum using the
+standard techniques of the California Planet Survey \cite{Howard2010}.
 Figure~\ref{fig:spec}b shows the result in the vicinity of H$\alpha$
@@
 \cite{Wood2023} provided an instructive recent overview: an abbreviated
-summary is that cooler and younger M dwarfs can show the 6707.8\,\AA\
+summary is that sufficiently cool and young M dwarfs show the 6707.8\,\AA\
 doublet in absorption, $\gtrsim$10\% below their ``continua''.  Unlike
-Sun-like stars, the continuum for M dwarfs is poorly defined due to
+for Sun-like stars, the continuum for M dwarfs is poorly defined due to
 their molecular absorption.  We attempted a lithium measurement by
@@
 data show a small depression near the expected lithium wavelength,
-potentially consistent with a $\Delta \lambda$$\approx$3\,\AA\ line
+potentially consistent with the $\Delta \lambda$$\approx$3\,\AA\ line
 broadening.  This feature nominally yields ${\rm EW}_{\rm
-Li}$=71$^{+18}_{13}$\,m\AA, where the statistical uncertainties are
+Li}$=71$^{+18}_{-13}$\,m\AA, where the statistical uncertainties are
 evaluated using a bootstrap resampling technique from the statistical
-uncertainties in the spectrum.  The systematic uncertainties associated
+uncertainties in the spectrum.  However the systematic uncertainties associated
 with the continuum normalization are larger, and likely comparable to
@@
 provide a point for theoretical comparison, and suggest that since
-$M_{\rm K}$$=$6.67\,mag, $t_{\rm Li,th}$$\gtrsim$35\,Myr is the
+$M_{\rm K}$$\approx$6.67\,mag, $t_{\rm Li,th}$$\gtrsim$35\,Myr is the
 theoretical age at which complete depletion occurs in a star with this
@@
 yielded a confident W3 detection (9.8$\sigma$), the W4 extraction
-yielded only a marginal (1.7$\sigma$) indication of detectable flux.
+yielded only a marginal indication (1.7$\sigma$) of detectable flux.
 Similar to other CPVs \cite{Stauffer2017,Bouma2024}, the photometric
@@
 
+Ha
+Hgamma
+Hdelta?
+He5875
+CaK
+K7700
+Li6708
+
 %TODO: add figure showing spectral variability!

### 2025-03-18 paper/ms.tex
update ms

@@
 radiation \cite{France2013}, and to a high incidence of flares and
-coronal mass ejections \cite{Gunther2020}.  Nevertheless, despite excellent
+coronal mass ejections \cite{Gunther2020}.  However, despite excellent
 work in these areas, the properties of the plasma and magnetospheric
@@
 circumstellar material.  Geometrically, transiting clumps would imply an
-occurrence a few to at most ten times the observed rate.  Such clumps
+occurrence a few to at most ten times the observed rate.  The clumps
 could therefore exist around 10-30\% of M dwarfs during their early
@@
 \cite{Bouma2024} by searching the TESS two-minute data \cite{Ricker2015}
-for stars showing at least three sharp and periodic dips per cycle.  We
+for stars showing at least three sharp, periodic dips per cycle.  We
 selected the star for spectroscopy because its brightness and rapid
-rotation offer sensitivity to small variations in the line profiles.  We
+rotation enable efficiently studying small variations in the line profiles.  We
 observed for five hours on 17~February~2024 (UT) using the High
@@
 photometric morphology evolves.  TIC~141146667 indeed evolved relative
-to the February 2022 discovery data \cite{Bouma2024}.  In the February
-2024 TESS data, the average photometric signal showed a small brightening
+to the February 2022 discovery data \cite{Bouma2024}.  In February
+2024, the average photometric signal showed a small brightening
 over 45\% of the period, followed by a complex flux dip spanning 55\%
@@
 These sinusoidal emission features require circumstellar clumps of
-partially-ionized hydrogen to be corotating with the star.  
-Based on its period, this material's motion is not Keplerian; it can
+partially-ionized hydrogen to corotate with the star.  
+Based on the period, this material's motion is not Keplerian; it can
 only be explained by plasma being dragged along with the rotating
@@
 produce chromatic features \cite{Rackham2018}.  The composition and size
-distribution of any dust that is present would be most easily resolved
+distribution of any dust that is present could be determined
 by measuring the extinction curve for one or more CPVs from
@@
 rocky bodies seen around white dwarfs \cite{Reach2009} would indicate a
-rocky-body origin.  Compositions and sizes to the ISM would be
+rocky-body origin.  Compositions and sizes similar to the ISM would be
 indicative of condensed dust in an M dwarf wind, similar to that formed
@@
 \cite{Kaur2024} showing that CPVs are variable radio emitters with
-emission components that can be both persistent, and also short-lived
-and highly polarized.  In particular, detecting radio emission produced
-by an electron cyclotron maser instability would provide a measurement
-of the field strength at the site of the emitting region.
+emission components that can be not only persistent, but also
+short-lived and highly polarized.  In particular, detecting radio
+emission produced by an electron cyclotron maser instability
+\cite{Callingham2021} would provide a measurement of the field
+strength at the site of the emitting region.
 
 It is currently unclear what, if any, relationship CPVs have to the
-close-in exoplanets that exist around most M dwarfs \cite{Dressing2015}.
+close-in rocky exoplanets that exist around most M dwarfs \cite{Dressing2015}.
 However, 0.3-3\% of young M dwarfs show the CPV phenomenon
@@
 
-Broadly, Figure~\ref{fig:fulllc} shows that a large, complex eclipse
+Figure~\ref{fig:fulllc} shows that a large, complex eclipse
 feature was present before and after the HIRES data were
@@
 a weak or non-existent connection between the CPV phenomenon and
-binarity.  For TIC~141146667 specifically, while we find no evidence for
+(wide) binarity.  For TIC~141146667 specifically, while we find no evidence for
 stellar multiplicity, our data are minimally constraining for the
 scenario of a low-luminosity companion ($F_1$/$F_2$$\lesssim$0.1) at
-large orbital separations.
+with apparent separations below 0$\farcs$1.
 
@@
 40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
-metallicity, and reddening are typically only weakly constrained.  We
+metallicity, and reddening are only weakly constrained.  We
 determined the star's spectral type to be M5.5Ve by visually comparing
 the HIRES spectra against the photometric standards tabulated by
-\cite{Bochanski2007}, which agrees with the effective temperature from
-the SED fitting \cite{Pecaut2013}.
+\cite{Bochanski2007}.   This result agrees with the effective
+temperature found from the SED fitting \cite{Pecaut2013}.
 
@@
 yielded no strong candidates for co-moving stars with projected
-tangential velocities $\Delta v_{\rm T}$$<$5\,\kms that share its
+tangential velocities $\Delta v_{\rm T}$$<$5\,\kms\ that share its
 isochronal youth.
@@
 equivalent width measurements reported by \cite{Jeffries2023}
-based on the Gaia-ESO spectroscopic survey.  If the star were
-$\lesssim$20\,Myr old, at its temperature we would expect to see
-lithium in abundance ($>$400\,m\AA).  Since we do not, we can set an
-empirical bound on the lithium-derived age of $t_{\rm
-Li,emp}$$\gtrsim$20\,Myr.  The \cite{Feiden2016} lithium isochrones
-provide a point for theoretical comparison, and suggest that since
-$M_{\rm K}$$\approx$6.67\,mag, $t_{\rm Li,th}$$\gtrsim$35\,Myr is the
-theoretical age at which complete depletion occurs in a star with this
-luminosity (see e.g.~Figure 7 from \cite{Wood2023}).
+based on the Gaia-ESO spectroscopic survey; Figure~\ref{fig:hirescuts}
+shows the associated raw spectra.  If the star were $\lesssim$20\,Myr
+old, at its temperature we would expect to see lithium in abundance
+($>$400\,m\AA).  Since we do not, we can set an empirical bound on the
+lithium-derived age of $t_{\rm Li,emp}$$\gtrsim$20\,Myr.  The
+\cite{Feiden2016} lithium isochrones provide a point for theoretical
+comparison, and suggest that since $M_{\rm K}$$\approx$6.67\,mag,
+$t_{\rm Li,th}$$\gtrsim$35\,Myr is the theoretical age at which
+complete depletion occurs in a star with this luminosity (see
+e.g.~Figure 7 from \cite{Wood2023}).
 
@@
 
-The full HIRES coverage spans 3650-7960\,\AA, and variable
-  emission is visible in Balmer lines from $n$=10$\rightarrow$2, Ca[H]
-  and Ca[K], the Mg[I] b triplet, and the 5875 He[I] emission line.
-
-Ha
-Hgamma
-Hdelta?
-He5875
-CaK
-K7700
-Li6708
-
-%TODO: add figure showing spectral variability!
-
-\subsection{Spectral Behavior of Other Lines}
-
-First, chromospheric:
-
-{\it H$\gamma$, H$\delta$}
-Line ratios.
-
-{\it Ca [K]}
-{\it Also} shows some high-velocity emission.  So, the emitting material has
-calcium ions.
-
-{\it He 5880}
-Also variable...
-
-{\it Magnesium b orders}
-Shows some variability that is horrendously blended.
-
-{\it K[I] 7700}
-Literally the only obvious photospheric line.
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=\textwidth]{figures/sf5.pdf}
+  \caption{Time evolution of select regions in the Keck/HIRES
+  spectra from 17 February 2025.
+  The horizontal axis shows $\Delta v \equiv c (\lambda -
+  \lambda_0)/\lambda_0$, the relative velocity centered on each line's
+  rest wavelength, normalized by the stellar equatorial velocity.
+  }
+  \label{fig:hirescuts}
+\end{figure}
+
+Figure~\ref{fig:hirescuts} shows a few regions of interest in the HIRES
+spectra, which cover 3650-7960\,\AA.
+Higher order Balmer lines including H$\gamma$ and H$\delta$ (the
+$n=5\rightarrow2$ and $n=6\rightarrow2$ transitions respectively) do
+show some variability outside the line core.
+However, this variability is not clearly periodic in the
+same manner as the emission seen in H$\alpha$.
+This could be because there are insufficient hydrogen ions in the
+relevant excited states, or due to the lower precision of the spectra
+in these bluer regions.
+The Ca HK doublet for instance is also detectable in emission, however
+the continuum near it is not.
+Chromospheric emission lines in the magnesium triplet order are
+also detectable, but sufficiently blended to be rendered unusable.
+
+One notable feature is that H$\alpha$, H$\gamma$, H$\delta$, and He
+5876\,\AA\ all show a blue excess at $\phi$$\approx$0.2.  At the same
+epoch, only H$\alpha$ clearly shows a resolved red excess as well,
+although $H\gamma$ and H$\delta$ are broader at this time.  Given the
+sudden rise of this emission in $<$15\,minutes, and the association
+between He 5876\,\AA\ and stellar outflows at high excitation energy,
+this component of the spectra might be more easily associated with a
+flare than with a stable, periodic component.
+
+Finally, the Li\,\textsc{I} 6708\,\AA\ doublet, which shows no obvious
+absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ feature are
+both shown in Figure~\ref{fig:hirescuts}.  In the latter, narrow
+telluric absorption features overlap the blue wing of the line.
+Neither of these regions shows any notable variability.
+
+%\subsection{Spectral Behavior of Other Lines}
+%
+%First, chromospheric:
+%
+%{\it H$\gamma$, H$\delta$}
+%Line ratios.
+%
+%{\it Ca [K]}
+%{\it Also} shows some high-velocity emission.  So, the emitting material has
+%calcium ions.
+%
+%{\it He 5880}
+%Also variable...
+%
+%{\it Magnesium b orders}
+%Shows some variability that is horrendously blended.
+%
+%{\it K[I] 7700}
+%Literally the only obvious photospheric line.
 

### 2025-03-18 paper/collect_figs.sh

@@ -28,3 +28,5 @@ cp $r/li_ew/li_vs_population.pdf figures/sf2.pdf
 cp $r/hrd/hrd_smalllim_dereddened.pdf figures/sf3.pdf
 
 cp $r/sed_fit/TIC_141146667/plots_irexcess/SED.pdf figures/sf4.pdf
+
+cp $r/lineevolnpanel/TIC141146667_j537_lineevolnpanel_removecosmic.pdf figures/sf5.pdf

### 2025-03-18 drivers/plot_lineevolnpanel.py
plot_lineevolnpanel: gray patch

@@ -28,7 +28,6 @@ from scipy.ndimage import gaussian_filter1d
 
 from aesthetic.plot import savefig, format_ax, set_style
 
-
 from scipy.ndimage import gaussian_filter1d
 from specutils.spectra import Spectrum1D, SpectralRegion
 from specutils.fitting import fit_generic_continuum
@@ -37,6 +36,33 @@ from rudolf.plotting import multiline
 
 from complexrotators.getters import get_specriver_data
 from cdips_followup.spectools import remove_cosmic_rays
+
+import matplotlib.patches as patches
+
+def plot_gray_rectangle(ax: plt.Axes) -> None:
+    """Plot a partially transparent gray rectangle from x = -1 to x = 1.
+
+    Generated by ChatGPT on March 17 2025.
+
+    Args:
+        ax (plt.Axes): Matplotlib axis on which the rectangle is drawn.
+
+    Returns:
+        None
+    """
+    y_low, y_high = ax.get_ylim()
+    width = 2
+    height = y_high - y_low
+    rect = patches.Rectangle(
+        xy=(-1, y_low),
+        width=width,
+        height=height,
+        facecolor="gray",
+        alpha=0.1,
+        zorder=-1
+    )
+    ax.add_patch(rect)
+
 
 def plot_lineevolnpanel(outdir, starid=None, jstr=None, remove_cosmics=0):
     """
@@ -209,6 +235,8 @@ def plot_lineevolnpanel(outdir, starid=None, jstr=None, remove_cosmics=0):
         if l == 'K':
             axd[rowkey].set_yticks([0.7,0.9,1.1])
 
+        # inside line core region...
+
         expids = [os.path.basename(s).rstrip('.fits').lstrip('b')
                   for s in specpaths]
         outdict = {
@@ -227,6 +255,8 @@ def plot_lineevolnpanel(outdir, starid=None, jstr=None, remove_cosmics=0):
         with open(cachepath, "wb") as f:
             pickle.dump(outdict, f)
         print(f'Wrote {cachepath}')
+
+        plot_gray_rectangle(axd[rowkey])
 
     # NOTE: inset_axes approach causes pdf rendering error. avoid by
     # directly instantiating a new axis set.

### 2025-03-18 paper/ms.tex
update derivations

@@
 
-{\it Effective temperature, radius, mass, and spectral type} We adopted
+{\it Effective temperature, radius, mass, and spectral type}---We adopted
 the star's effective temperature and radius measured using the spectral
@@
 
-{\it Upper and Low Bounds on Dust}---An upper limit on the amount of hot
-dust follows from the lack of an infrared excess.  A lower limit follows
-if one assumes that most of the broadband optical depth comes from
-dust absorption and scattering, rather than any radiative processes
-associated with the plasma.
-
-How much dust is allowed, given the lack of an infrared excess?
-Figure~\ref{fig:sed} shows the SED.  While AllWISE \cite{Cutri2014}
-yielded a confident W3 detection (9.8$\sigma$), the W4 extraction
-yielded only a marginal indication (1.7$\sigma$) of detectable flux.
-Similar to other CPVs \cite{Stauffer2017,Bouma2024}, the photometric
-uncertainties from WISE W1 and W2 allow at most a $\lesssim$2\% excess
-at 3-5\,$\mu$m relative to the stellar photosphere, and a $\lesssim$5\%
-excess at 10\,$\mu$m (W3).  To estimate the implied mass bound, we
-assume $T_{\rm dust}$=1500\,K, typical for dust near the star (see
+{\it Upper and Low Bounds on Dust}---An upper limit on the amount of
+hot dust follows from the lack of an infrared excess.  A lower limit
+follows if one assumes that most of the broadband optical depth comes
+from dust absorption and scattering, rather than any radiative
+processes associated with the plasma.
+
+Regarding the upper limit, Figure~\ref{fig:sed} shows the SED.  While
+AllWISE \cite{Cutri2014} yielded a confident W3 detection
+(9.8$\sigma$), the W4 extraction yielded only a marginal indication
+(1.7$\sigma$) of detectable flux.  Similar to other CPVs
+\cite{Stauffer2017,Bouma2024}, the photometric uncertainties from WISE
+W1 and W2 allow at most a $\lesssim$2\% excess at 3-5\,$\mu$m relative
+to the stellar photosphere, and a $\lesssim$5\% excess at 10\,$\mu$m
+(W3).  To estimate the implied mass bound, we assume a dust
+temperature $T_{\rm d}$=1500\,K, typical for dust near the star (see
 \cite{Zhan2019} for discussion regarding dust sublimation).  We then
-treat emission from the dust and the star as Planck functions,
-requiring $F_{\lambda,\star} > f \cdot F_{\lambda,\mathrm{dust}}$, for
-$f$ the scaling factor set by the WISE photometric uncertainty.  For
-this condition to hold, we find that the bolometric flux ratio $F_{\rm
-dust}/F_{\star}$$<$6$\cdot$10$^{-3}$.  Scaling the associated
-luminosities ($L = \sigma_{\rm SB} T_{\rm eff}^4 / (4\pi R^2)$)
-implies an emitting area for the dust $<$10\% of the star's surface
-area.  Converting this constraint to a dust mass requires an
-assumption regarding the grain properties; assuming a grain density
-$\rho_{\rm d}$=3\,g\,cm$^{-3}$ typical for silicate grains, and a fixed grain
-size $a$=1\,$\mu$m \cite{Tanimoto2020,Gunther2022,Koen2023} yields an
-upper limit of $M_{\rm dust}\lesssim$10$^{17}$\,g.
-
-By way of comparison, the lower limit follows from requiring the
-optical depth $\tau$ to be at least unity.
-The optical depth can be written $\tau = n \sigma \ell = N \sigma$,
-where $\sigma$ is the cross-section, $n$ is the number density, $\ell$
-is the path length, and $N$ is the column density.
-For spherical dust grains in the optical, $\sigma = Q_{\rm ext} \pi
-a^2$, where $Q_{\rm ext}$ is the extinction efficiency parameter,
-tabulated e.g.~by \cite{Croll2014} in their Figure 13.
-\cite{Sanderson2023} calculated the relevant cloud mass scaling
-assuming a spherical dust clump of size $r$,
-and they found
+treat emission from the dust and the star as Planck functions, and
+require $L_{\rm d} < f L_\star$, where the factor $f$ is set by
+photometric precision of WISE and $L_{\rm d}$ is the bolometric dust
+luminosity.  Given the reported uncertainties, we numerically find
+$f<6\cdot$10$^{-3}$.  From the Stefan-Boltzmann law we can then write
+$A_{\rm d} < f (T_\star / T_{\rm d})^4 Q_{\rm em}^{-1} (4\pi
+R_\star)^2$, for $A_{\rm d}$ the total emitting surface area of the
+dust, and $Q_{\rm em}$ is an emission efficiency parameter.
+Converting this constraint to a dust mass requires an assumption
+regarding the grain properties.  We assume a grain density $\rho_{\rm
+d}$=3\,g\,cm$^{-3}$ typical for silicate grains, a fixed grain size
+$a$=1\,$\mu$m \cite{Tanimoto2020,Gunther2022,Koen2023}, and no
+self-absorption.  This enables the assumption that $A_{\rm d} = N \pi
+a^2$, for $N$ the total number of dust grains.  This in turn yields an
+upper limit on the dust mass of
 \begin{equation}
-  M_{\rm dust} \gtrsim 1.6 \cdot 10^{15}\, {\rm g}\ 
-  \left( \frac{\tau}{1} \right)
-  \left( \frac{Q_{\rm ext}}{3} \right)^{-1}
-  \left( \frac{r}{0.1\,R_\star} \frac{R_\star}{0.34\,R_\odot} \right)^2
+  M_{\rm dust} \lesssim 4 \cdot 10^{17}\, {\rm g}\ 
+  \left( \frac{f}{6\cdot10^{-3}} \right)
+  \left( \frac{T_\star}{3000\,{\rm K}} \frac{1500\,{\rm K}}{T_{\rm d}} \right)^4
+  \left( \frac{Q_{\rm em}}{1} \right)^{-1}
+  \left( \frac{R_\star}{0.4\,R_\odot} \right)^2
   \left( \frac{a}{1\,\mathrm{\mu m}} \right)
@@
 \end{equation}
-By way of comparison, prominences of the Sun typically have gas masses
-of order $10^{14}\,g$-$10^{16}$\,g \cite{VialEngvold2015}, whereas a
-planetesimal of this mass with a bulk density of 1\,g\,cm$^{-3}$ would
-have a diameter of order one kilometer.  Halley's comet has a mass of
-order $10^{17}$\,g \cite{Rickman1989}, of which of order one part in a
-thousand is shed per orbit, most of which inspirals toward the Sun due
-to Poynting-Robertson drag.
-
+
+The analogous lower limit follows from requiring the optical depth
+from absorption and scattering $\tau$ to be at least unity.  The
+optical depth can be written $\tau = n \sigma \ell = N \sigma$, where
+$\sigma$ is the cross-section, $n$ is the number density, $\ell$ is
+the path length, and $N$ is the column density.  For spherical dust
+grains in the optical, $\sigma = Q_{\rm ext} \pi a^2$, where $Q_{\rm
+ext}$ is the extinction efficiency parameter, tabulated e.g.~by
+\cite{Croll2014} in their Figure 13.  \cite{Sanderson2023} calculated
+the relevant cloud mass scaling assuming a spherical dust clump of
+size $r$, and they estimated
+\begin{equation}
+  M_{\rm dust} \gtrsim 2 \cdot 10^{15}\, {\rm g}\ 
+  \left( \frac{\tau}{1} \right)
+  \left( \frac{Q_{\rm ext}}{3} \right)^{-1}
+  \left( \frac{r}{0.1\,R_\star} \frac{R_\star}{0.4\,R_\odot} \right)^2
+  \left( \frac{a}{1\,\mathrm{\mu m}} \right)
+  \left( \frac{\rho_{\rm d}}{3\,\mathrm{g\,cm^{-3}}} \right).
+\end{equation}
+
+Three relevant objects for comparison to these limits include solar
+prominences, planetesimals, and comets.
+Prominences of the Sun typically have gas masses
+of order $10^{14}$\,g-$10^{16}$\,g \cite{VialEngvold2015}.
+A planetesimal of mass $\approx$10$^{15}$\,g with a bulk density of
+1\,g\,cm$^{-3}$ would have a diameter of order one kilometer.
+Halley's comet has a mass of order $10^{17}$\,g \cite{Rickman1989}, of
+which $\sim$$10^{14}$\,g is shed per orbit, most of which inspirals
+toward the Sun due to Poynting-Robertson drag.
 Broadly, these calculations suggest that if dust is responsible for

### 2025-03-18 paper/ms.tex
update

@@
 \usepackage{lineno}
+\usepackage{caption}
 
@@
   \includegraphics[width=0.7\textwidth]{figures/f1.pdf}
-  \caption[]{{\bf Figure 1 (Movie):  TIC~141146667 is a complex periodic
+  \captionsetup{labelformat=empty}
+  \caption{{\bf Figure 1 (Movie):  TIC~141146667 is a complex periodic
   variable (CPV).}  The online movie,
@@
   \includegraphics[width=0.99\textwidth]{figures/f2.png}
-  \caption[]{{\bf Figure 2 (Movie):}  
+  \captionsetup{labelformat=empty}
+  \caption{{\bf Figure 2 (Movie):}  
   Hydrogen emission from circumstellar plasma orbiting TIC 141146667.
@@
   \href{https://lgbouma.com/movies/TIC141146667_sixpanel.mp4}{here}.
-  {\bf Panel a:} TESS light curve from UT 2024-02-05 to UT
-  2024-02-26 folded on the \periodhr\ hour period.  Black points are
-  averaged; gray are the raw data.
+  {\bf Panel a:} TESS light curve from 5 February 2024 to 26 February
+  2024 (UT) folded on the \periodhr\ hour period.  Black points are
+  phase-averaged; gray are the raw data.
   {\bf Panel b:} Keck/HIRES H$\alpha$ spectra
-  acquired on UT 2024-02-17.  The continuum is set to unity, and the
-  darkest color is set at twice the continuum to accentuate emission
+  acquired on UT 17 February 2024.  The continuum is set to unity, and the
+  darkest color is at twice the continuum to accentuate emission
   outside the line core ($|v/v_{\rm eq}|>1$, for $v_{\rm eq}$=130\,\kms).
@@
   {\bf Panel c:} Individual epochs of Panel b, visible in the
-  online movie.  The dotted line shows a time-averaged spectrum,
+  online movie.  The dotted line shows the time-averaged spectrum,
   $f_{\langle t \rangle}$.
@@
 Figure~\ref{fig:spec}.  No such stars were previously known to show
-complex light curves \cite{Bouma2024}.  The usual interpretation for
+complex light curves \cite{Bouma2024}.   One interpretation for
 such spectroscopic variability comes from an analogy to quiescent solar
@@
 magnetosphere, these condensations fall back to the solar surface
-because gravity is stronger than any magnetic or centrifugal force
+because gravity is stronger than any magnetic tension or centrifugal force
 capable of sustaining them.  However for stars with magnetospheric radii
@@
 effective potential experienced by a charged particle can have a local
-minimum outside $R_{\rm c}$, enabling the material to be sustained for
+minimum outside $R_{\rm c}$, enabling the material to accumulate over
 much longer timescales \cite{Petit2013,Daley-Yates2024}.  Generally
@@
 first, the complexity of CPVs may be a direct consequence of magnetic
-fields with highly multipolar contributions.  Second, CPVs could be a
+fields with highly multipolar contributions.  Second, CPVs can be a
 source of astrophysical false positives in photometric searches for
@@
   per cycle.
-  In the BTJD 3352-3356 window, a state switch occurred near BTJD 3353,
+  During BTJD 3352-3356, a state switch occurred near BTJD 3353,
   in which the dip at $\phi$$\approx$0.8 disappeared.
-  While the large, complex eclipse feature remained present before and
-  after the HIRES sequence, its photometric shape evolved during the
-  data gap.
+  While the large eclipse feature remained present before and after
+  the HIRES sequence, its photometric shape evolved during the data
+  gap.
   }

### 2025-03-18 paper/ms.tex
update

@@
 % ** keck/hires: emission beyond v/veq>1
-The spectroscopy shows emission well beyond the star's equatorial
-velocity ($v_{\rm eq}$=130\,\kms).  There are at least two distinct
-emission components, separated by half a cycle in phase.  The first
-component has clearer sinusoidal behaviour and is double-peaked, with
-peak semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
-There is significant non-periodic variability in this double-peaked
-component: the flux excess from both peaks begins with an amplitude
-equal to 100\% of the continuum flux early in the observation
-sequence, and falls to 30\% by its end.  The component 180$^\circ$
-opposite in phase is similarly only detected from $\phi$=0.2-1.0.
-From $\phi$=0.2-0.5, this latter component appears connected to the
-star in velocity space.  While its peak semi-amplitude of
-$K_1$=3.9\,$v_{\rm eq}$ is achieved at both $\phi$=0.25 and 0.75, its
-amplitude decreases from a 60\% excess over the continuum at the
-beginning of the observation sequence to a 10\% excess by its end.
-The sinusoidal period for all of these emission components is
-consistent with the photometric \periodhr\ hour period.
+The spectroscopy shows emission beyond the star's equatorial velocity
+($v_{\rm eq}$=130\,\kms).  There are at least two distinct emission
+components, separated by half a cycle in phase.  The first component
+has clearer sinusoidal behaviour and is double-peaked, with peak
+semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
+There is significant non-periodic variability in the emissivity of
+this double-peaked component: the flux excess begins with an amplitude
+of 70\% of the continuum flux early in the observation sequence, and
+diminishes to 10\% by its end.  The component 180$^\circ$ opposite in
+phase is detected only from $\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this
+latter component appears connected to the star in velocity space.
+While its peak semi-amplitude of $K_1$=3.9\,$v_{\rm eq}$ is achieved
+at both $\phi$=0.25 and 0.75, its amplitude similarly decreases from a
+60\% excess over the continuum at the beginning of the observation
+sequence to a 10\% excess by its end.  The sinusoidal period for all
+of these emission components is consistent with the photometric
+\periodhr\ hour period.
 
@@
 stellar magnetic field. 
-The velocity semi-amplitude of the sinusoids then gives the distance
+The velocity semi-amplitude of the sinusoids gives the distance
 of the clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
@@
 
-%\subsection{Spectral Behavior of Other Lines}
-%
-%First, chromospheric:
-%
-%{\it H$\gamma$, H$\delta$}
-%Line ratios.
-%
-%{\it Ca [K]}
-%{\it Also} shows some high-velocity emission.  So, the emitting material has
-%calcium ions.
-%
-%{\it He 5880}
-%Also variable...
-%
-%{\it Magnesium b orders}
-%Shows some variability that is horrendously blended.
-%
-%{\it K[I] 7700}
-%Literally the only obvious photospheric line.
-
 \subsection{Modeling the Emitting Clump}
@@
 
-% * mass estimate
-The density and mass of the material...
+The physical conditions inside the circumstellar plasma clumps, in
+particular the hydrogen number density, plasma temperature, ionization
+fraction, and magnetic field strength can all be estimated using the
+available data.
+We caution that the following estimates are coarse: detailed
+considerations of radiative transfer and detailed balance are a
+worthwhile topic for future work, but are beyond our immediate scope.
+
+Circumstellar H$\alpha$ emission might be sourced either from
+scattering of stellar H$\alpha$ photons, or from recombination.  We
+neglect scattering because we see the amplitude of the circumstellar
+emission to vary by a factor of $\approx$5, which is not mirrored in
+the chromospheric line core.  The volume emissivity under case B
+recombination (in which Lyman-series photons are trapped by high
+optical depth, so that recombinations cascade through H$\alpha$ and
+other Balmer lines) can be written as
+\begin{equation}
+  j_{\rm H\alpha} = n_{\rm e} n_{\rm p} \alpha^{\rm eff}_{\rm H\alpha}(T) h \nu_{\rm H\alpha},
+\end{equation}
+where $n_{\rm e}$ and $n_{\rm p}$ are the electron and proton densities,
+and $\alpha^{\rm eff}_{\rm H\alpha}(T)$ is the effective recombination
+coefficient, i.e.\ the number of recombinations per unit volume, per
+unit time.
+For hydrogen with temperatures between 1,000 and 10,000\,K with
+densities $n_{\rm H}$$\sim$10$^{10}$\,cm$^{-3}$,
+$\alpha^{\rm eff}_{\rm H\alpha}$ is typically on the order of $10^{-12}$ to
+$10^{-13}$\,cm$^3$\,s$^{-1}$ \cite{Hummer1987}.
+Neglecting the effects of atoms other than hydrogen, we can assume
+an ionization fraction $x$, such that $n_{\rm e} = n_{\rm p} = x
+n_{\rm H}$, for $n_{\rm H}$ the hydrogen number density.  Let $L_{\rm
+H\alpha} = j_{\rm H\alpha} V$, for $V$ the volume of the emitting
+hydrogen.
+The luminosity of circumstellar hydrogen emission, $L_{\rm H\alpha}$,
+is an observable: our SED fitting routine yields
+$L_\star$$\approx$0.012\,$L_\odot$, which gives
+$L_{\rm H\alpha},\star$$\approx$1.0$\times$$10^{28}$erg\,s$^{-1}$, and
+the luminosity of the clump $L_{\rm H\alpha}$ is of order one tenth
+that of the star.
+Assuming an emitting sphere of radius $r$, we can write
+\begin{equation}
+  n_H = \frac{1}{x}
+  \left( 
+    \frac{L_{\rm H\alpha}}{ \alpha^{\rm eff}_{\rm H\alpha}(T) h \nu_{\rm H\alpha} V }
+  \right)^{1/2}.
+\end{equation}
+Taking nominal parameters of $r = 0.1 R_\star$, $x=1/2$, and
+$\alpha^{\rm eff}_{\rm H\alpha}$=$10^{-13}$\,cm$^3$\,s$^{-1}$,
+we find $n_{\rm H}\approx 5\times10^{11}$\,cm$^{-3}$.
+Assuming a uniform density clump, this yields $M_{\rm H}\approx
+8\times10^{16}$\,g.
+A constraint on the magnetic field strength at the site of the clump
+follows from the requirement that the magnetic pressure exceed the
+thermal pressure, $B^2 / 8\pi > n_{\rm H} k T$.
+Although we do not know the plasma temperature,
+if it were significantly outside the range of
+1,000 and 10,000\,K,
+we would either full ionize the hydrogen, or not ionized enough of it.
+We can therefore estimate
+\begin{equation}
+  B \gtrsim 3\,{\rm G}
+  \left(
+  \frac{n_{\rm H}}{5\times10^{11}\,{\rm cm}^{-3}}
+  \frac{T}{5000\,{\rm K}}
+  \right).
+\end{equation}
+Given typical  magnetic field strengths of low-mass stars, this bound
+is easily met.
+%TODO FIXME CITE KOCHUKHOV HERE
 

### 2025-03-18 drivers/calc_halpha_luminosity.py
halpha number density estimates

@@ -1,0 +1,84 @@
+import numpy as np
+import astropy.units as u
+import astropy.constants as const
+from astropy.modeling.physical_models import BlackBody
+
+
+def bolometric_luminosity(T_eff: float, R_star: u.Quantity) -> u.Quantity:
+    """Calculate bolometric luminosity from effective temperature and radius.
+
+    The bolometric luminosity is computed using the Stefan-Boltzmann law:
+    L = 4πR²σT⁴.
+    Generated by ChatGPT o3-mini-high on March 18 2025.
+
+    Args:
+        T_eff (float): Effective temperature in Kelvin.
+        R_star (u.Quantity): Stellar radius with appropriate units.
+
+    Returns:
+        u.Quantity: Bolometric luminosity in erg/s.
+    """
+    sigma = const.sigma_sb
+    L = 4 * np.pi * (R_star**2) * sigma * (T_eff*u.K)**4
+    return L.to(u.erg / u.s)
+
+
+def halpha_luminosity(T_eff: float, R_star: u.Quantity,
+                      equivalent_width: float = 5.0) -> u.Quantity:
+    """Calculate Hα luminosity using the equivalent width of the line.
+
+    The continuum flux density at the Hα wavelength is derived from a
+    blackbody at T_eff using the BlackBody model. Note that BlackBody returns
+    B_nu, the spectral radiance per unit frequency in units of
+    erg/(s cm² sr Hz). We convert B_nu to B_lambda using:
+    B_lambda = (c / λ²) * B_nu.
+    The continuum flux is then F_cont = π * B_lambda, and the line flux is
+    given by F_cont multiplied by the equivalent width (converted to cm).
+    The Hα luminosity is computed as:
+    L_Hα = 4πR² * (F_cont * EW).
+    Generated by ChatGPT o3-mini-high on March 18 2025.
+
+    Args:
+        T_eff (float): Effective temperature in Kelvin.
+        R_star (u.Quantity): Stellar radius with appropriate units.
+        equivalent_width (float, optional): Equivalent width of the Hα line in
+            Angstroms. Defaults to 5.0 Å.
+
+    Returns:
+        u.Quantity: Hα luminosity in erg/s.
+    """
+    wavelength = 6563 * u.AA
[…]

### 2025-03-18 drivers/calc_number_density_constraint_from_ha_emission.py

@@ -1,0 +1,28 @@
+from astropy import units as u, constants as c
+
+x = 0.5
+L_Hα_star = 1e28 * u.erg / u.s # from the STAR (!)
+L_Hα_clump = (1/5) * 1e28 * u.erg / u.s # from the STAR (!)
+
+λ = 6365 * u.Angstrom
+ν = c.c / λ
+
+E = c.h * ν
+
+Rstar = 0.4 * u.Rsun
+r = 0.1 * Rstar
+V = 4 * 3.14/3 * r**3
+
+alpha_eff_Halpha = 1e-13 * u.cm**3 / u.s
+
+n_H = (
+    (1/x) *
+    (L_Hα_clump /
+     (alpha_eff_Halpha * E * V)
+    )**(0.5)
+)
+
+print(f"n_H: {n_H.cgs:.2e}")
+
+M_H = n_H * c.m_p * V
+print(f"M_H: {M_H.cgs:.2e}")

### 2025-03-19 paper/ms.tex
update

@@
   spectra from 17 February 2025.
-  The horizontal axis shows $\Delta v \equiv c (\lambda -
-  \lambda_0)/\lambda_0$, the relative velocity centered on each line's
-  rest wavelength, normalized by the stellar equatorial velocity.
+  The spectra have been smoothed with a Gaussian filter.
+  The horizontal axis shows the relative velocity centered on each
+  line's rest wavelength, normalized by the stellar equatorial
+  velocity.  
+  H$\alpha$ is the only Balmer line to show periodic variability of
+  the form seen in Figure~\ref{fig:spec}.
+  The He 5876\,\AA\ line shows a time-dynamic blueshift that 
+  differs from the Balmer lines.
+  Li 6708\,\AA\ shows no obvious absorption.
   }
@@
 Finally, the Li\,\textsc{I} 6708\,\AA\ doublet, which shows no obvious
-absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ feature are
-both shown in Figure~\ref{fig:hirescuts}.  In the latter, narrow
-telluric absorption features overlap the blue wing of the line.
+absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ resonance
+line are both shown in Figure~\ref{fig:hirescuts}.  In the latter,
+narrow telluric absorption features overlap the blue wing of the line.
 Neither of these regions shows any notable variability.
@@
 \end{equation}
-Given typical  magnetic field strengths of low-mass stars, this bound
-is easily met.
-%TODO FIXME CITE KOCHUKHOV HERE
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-% Supplementary Figures %
-%%%%%%%%%%%%%%%%%%%%%%%%%
+Given that the average surface magnetic field strengths of low-mass
+stars have been measured to span hundreds to thousands of Gauss
+\cite{Kochukhov2021}, this bound is easily met.
 

### 2025-03-19 paper/ms.tex
update

@@
 emission at twice to four times the star's equatorial velocity,
-demonstrating the existence of extended clumps of circumstellar
+demonstrating the existence of extended clumps of corotating circumstellar
 plasma --- a plasma torus.  Given that long-lived condensations of
@@
 condensations can be optically thick; the exact origin of the
-material and its microphysical opacity remain unclear.
+optically thick material and its microphysical opacity remain unclear.
 \end{abstract}
@@
 rocky bodies seen around white dwarfs \cite{Reach2009} would indicate a
-rocky-body origin.  Compositions and sizes similar to the ISM would be
+rocky-body origin.  Compositions and sizes similar to the interstellar
+medium would be
 indicative of condensed dust in an M dwarf wind, similar to that formed
@@
 It is currently unclear what, if any, relationship CPVs have to the
-close-in rocky exoplanets that exist around most M dwarfs \cite{Dressing2015}.
-However, 0.3-3\% of young M dwarfs show the CPV phenomenon
-\cite{Rebull2020}, and our data show that the phenomenon occurs when
-clumps of circumstellar material transit the star.  The implied
-geometric correction suggests that an appreciable minority (10-30\%) of
-young M dwarfs -- the rapidly rotating ones with centrifugal
-magnetospheres -- host similar circumstellar environments to the CPVs.
+close-in rocky exoplanets that exist around most M dwarfs
+\cite{Dressing2015}.  However, 0.3-3\% of young M dwarfs show the CPV
+phenomenon \cite{Rebull2020}, and our data show that the complex
+photometric features occur when clumps of circumstellar material is
+transiting the star.  The implied geometric correction suggests that
+an appreciable minority (10-30\%) of young M dwarfs -- the rapidly
+rotating ones with centrifugal magnetospheres -- host similar
+circumstellar environments to the CPVs.
 
@@
 
-{\it Upper and Low Bounds on Dust}---An upper limit on the amount of
-hot dust follows from the lack of an infrared excess.  A lower limit
-follows if one assumes that most of the broadband optical depth comes
-from dust absorption and scattering, rather than any radiative
-processes associated with the plasma.
-
-Regarding the upper limit, Figure~\ref{fig:sed} shows the SED.  While
-AllWISE \cite{Cutri2014} yielded a confident W3 detection
-(9.8$\sigma$), the W4 extraction yielded only a marginal indication
-(1.7$\sigma$) of detectable flux.  Similar to other CPVs
-\cite{Stauffer2017,Bouma2024}, the photometric uncertainties from WISE
-W1 and W2 allow at most a $\lesssim$2\% excess at 3-5\,$\mu$m relative
-to the stellar photosphere, and a $\lesssim$5\% excess at 10\,$\mu$m
-(W3).  To estimate the implied mass bound, we assume a dust
-temperature $T_{\rm d}$=1500\,K, typical for dust near the star (see
-\cite{Zhan2019} for discussion regarding dust sublimation).  We then
-treat emission from the dust and the star as Planck functions, and
-require $L_{\rm d} < f L_\star$, where the factor $f$ is set by
-photometric precision of WISE and $L_{\rm d}$ is the bolometric dust
-luminosity.  Given the reported uncertainties, we numerically find
-$f<6\cdot$10$^{-3}$.  From the Stefan-Boltzmann law we can then write
-$A_{\rm d} < f (T_\star / T_{\rm d})^4 Q_{\rm em}^{-1} (4\pi
-R_\star)^2$, for $A_{\rm d}$ the total emitting surface area of the
-dust, and $Q_{\rm em}$ is an emission efficiency parameter.
-Converting this constraint to a dust mass requires an assumption
-regarding the grain properties.  We assume a grain density $\rho_{\rm
-d}$=3\,g\,cm$^{-3}$ typical for silicate grains, a fixed grain size
-$a$=1\,$\mu$m \cite{Tanimoto2020,Gunther2022,Koen2023}, and no
-self-absorption.  This enables the assumption that $A_{\rm d} = N \pi
-a^2$, for $N$ the total number of dust grains.  This in turn yields an
-upper limit on the dust mass of
-\begin{equation}
-  M_{\rm dust} \lesssim 4 \cdot 10^{17}\, {\rm g}\ 
-  \left( \frac{f}{6\cdot10^{-3}} \right)
-  \left( \frac{T_\star}{3000\,{\rm K}} \frac{1500\,{\rm K}}{T_{\rm d}} \right)^4
-  \left( \frac{Q_{\rm em}}{1} \right)^{-1}
-  \left( \frac{R_\star}{0.4\,R_\odot} \right)^2
-  \left( \frac{a}{1\,\mathrm{\mu m}} \right)
-  \left( \frac{\rho_{\rm d}}{3\,\mathrm{g\,cm^{-3}}} \right).
-\end{equation}
-
-The analogous lower limit follows from requiring the optical depth
-from absorption and scattering $\tau$ to be at least unity.  The
-optical depth can be written $\tau = n \sigma \ell = N \sigma$, where
-$\sigma$ is the cross-section, $n$ is the number density, $\ell$ is
-the path length, and $N$ is the column density.  For spherical dust
-grains in the optical, $\sigma = Q_{\rm ext} \pi a^2$, where $Q_{\rm
-ext}$ is the extinction efficiency parameter, tabulated e.g.~by
-\cite{Croll2014} in their Figure 13.  \cite{Sanderson2023} calculated
-the relevant cloud mass scaling assuming a spherical dust clump of
-size $r$, and they estimated
-\begin{equation}
-  M_{\rm dust} \gtrsim 2 \cdot 10^{15}\, {\rm g}\ 
-  \left( \frac{\tau}{1} \right)
-  \left( \frac{Q_{\rm ext}}{3} \right)^{-1}
-  \left( \frac{r}{0.1\,R_\star} \frac{R_\star}{0.4\,R_\odot} \right)^2
-  \left( \frac{a}{1\,\mathrm{\mu m}} \right)
-  \left( \frac{\rho_{\rm d}}{3\,\mathrm{g\,cm^{-3}}} \right).
-\end{equation}
-
-Three relevant objects for comparison to these limits include solar
-prominences, planetesimals, and comets.
-Prominences of the Sun typically have gas masses
-of order $10^{14}$\,g-$10^{16}$\,g \cite{VialEngvold2015}.
-A planetesimal of mass $\approx$10$^{15}$\,g with a bulk density of
-1\,g\,cm$^{-3}$ would have a diameter of order one kilometer.
-Halley's comet has a mass of order $10^{17}$\,g \cite{Rickman1989}, of
-which $\sim$$10^{14}$\,g is shed per orbit, most of which inspirals
-toward the Sun due to Poynting-Robertson drag.
-Broadly, these calculations suggest that if dust is responsible for
-the broadband variability of CPVs, it would need to be concentrated in
-clumps with masses in the range of $10^{15}$-$10^{17}$\,g.
-
 \subsection{Spectroscopic Variability}\phantom{+}
@@
   spectra from 17 February 2025.
-  The spectra have been smoothed with a Gaussian filter.
+  The spectra have been smoothed with a Gaussian filter, and cosmic
+  rays have been removed.
   The horizontal axis shows the relative velocity centered on each
@@
 
-\subsection{Modeling the Emitting Clump}
-\label{subsec:model}
+\subsection{Properties of the Plasma and Magnetospheric Environment}\phantom{+}
+\label{subsec:gas}
 
@@
 fraction, and magnetic field strength can all be estimated using the
-available data.
-We caution that the following estimates are coarse: detailed
-considerations of radiative transfer and detailed balance are a
-worthwhile topic for future work, but are beyond our immediate scope.
+available data.  We caution that the following estimates are coarse:
+detailed considerations of radiative transfer and detailed balance are
+a worthwhile topic for future work, but are beyond the scope of this
+article.
 
@@
 we find $n_{\rm H}\approx 5\times10^{11}$\,cm$^{-3}$.
-Assuming a uniform density clump, this yields $M_{\rm H}\approx
+Assuming a uniform density clump, this yields $M_{\rm gas}\approx
 8\times10^{16}$\,g.
-A constraint on the magnetic field strength at the site of the clump
+
+Finally, a constraint on the magnetic field strength at the site of the clump
 follows from the requirement that the magnetic pressure exceed the
@@
 \cite{Kochukhov2021}, this bound is easily met.
+
+\subsection{Upper and Low Bounds on Dust}\phantom{+}
+\label{subsec:dust}
+
+The material's exact composition -- either pure plasma, or else a
+dusty plasma -- is not known.  In particular, the idea of dust being
+present seems plausible given observations of chromatic transits in
+analogous objects \cite{Tanimoto2020,Gunther2022,Koen2023}.
+This scenario is highly constrained.  An upper limit on the amount of
+hot dust follows from the lack of an infrared excess.  A lower limit
+follows if one assumes that most of the broadband optical depth comes
+from dust absorption and scattering, rather than any radiative
+processes associated with the plasma.
+
+Regarding the upper limit, Figure~\ref{fig:sed} shows the SED.  While
+AllWISE \cite{Cutri2014} yielded a confident W3 detection
+(9.8$\sigma$), the W4 extraction yielded only a marginal indication
+(1.7$\sigma$) of detectable flux.  Similar to other CPVs
+\cite{Stauffer2017,Bouma2024}, the photometric uncertainties from WISE
+W1 and W2 allow at most a $\lesssim$2\% excess at 3-5\,$\mu$m relative
+to the stellar photosphere, and a $\lesssim$5\% excess at 10\,$\mu$m
+(W3).  To estimate the implied mass bound, we assume a dust
+temperature $T_{\rm d}$=1500\,K, typical for dust near the star (see
+\cite{Zhan2019} for discussion regarding dust sublimation).  We then
+treat emission from the dust and the star as Planck functions, and
+require $L_{\rm d} < f L_\star$, where the factor $f$ is set by
+photometric precision of WISE and $L_{\rm d}$ is the bolometric dust
+luminosity.  Given the reported uncertainties, we numerically find
+$f<6\cdot$10$^{-3}$.  From the Stefan-Boltzmann law we can then write
+$A_{\rm d} < f (T_\star / T_{\rm d})^4 Q_{\rm em}^{-1} (4\pi
+R_\star)^2$, for $A_{\rm d}$ the total emitting surface area of the
+dust, and $Q_{\rm em}$ is an emission efficiency parameter.
+Converting this constraint to a dust mass requires an assumption
+regarding the grain properties.  We assume a grain density $\rho_{\rm
+d}$=3\,g\,cm$^{-3}$ typical for silicate grains, a fixed grain size
+$a$=1\,$\mu$m \cite{Tanimoto2020,Gunther2022,Koen2023}, and no
+self-absorption.  This enables the assumption that $A_{\rm d} = N \pi
+a^2$, for $N$ the total number of dust grains.  This in turn yields an
+upper limit on the dust mass of
+\begin{equation}
+  M_{\rm dust} \lesssim 4 \cdot 10^{17}\, {\rm g}\ 
+  \left( \frac{f}{6\cdot10^{-3}} \right)
+  \left( \frac{T_\star}{3000\,{\rm K}} \frac{1500\,{\rm K}}{T_{\rm d}} \right)^4
+  \left( \frac{Q_{\rm em}}{1} \right)^{-1}
+  \left( \frac{R_\star}{0.4\,R_\odot} \right)^2
+  \left( \frac{a}{1\,\mathrm{\mu m}} \right)
+  \left( \frac{\rho_{\rm d}}{3\,\mathrm{g\,cm^{-3}}} \right).
+\end{equation}
+
+The analogous lower limit follows from requiring the optical depth
+from absorption and scattering $\tau$ to be at least unity.  The
+optical depth can be written $\tau = n \sigma \ell = N \sigma$, where
+$\sigma$ is the cross-section, $n$ is the number density, $\ell$ is
+the path length, and $N$ is the column density.  For spherical dust
+grains in the optical, $\sigma = Q_{\rm ext} \pi a^2$, where $Q_{\rm
+ext}$ is the extinction efficiency parameter, tabulated e.g.~by
+\cite{Croll2014} in their Figure 13.  \cite{Sanderson2023} calculated
+the relevant cloud mass scaling assuming a spherical dust clump of
+size $r$, and they estimated
+\begin{equation}
+  M_{\rm dust} \gtrsim 2 \cdot 10^{15}\, {\rm g}\ 
+  \left( \frac{\tau}{1} \right)
+  \left( \frac{Q_{\rm ext}}{3} \right)^{-1}
+  \left( \frac{r}{0.1\,R_\star} \frac{R_\star}{0.4\,R_\odot} \right)^2
+  \left( \frac{a}{1\,\mathrm{\mu m}} \right)
+  \left( \frac{\rho_{\rm d}}{3\,\mathrm{g\,cm^{-3}}} \right).
+\end{equation}
+
+Three relevant objects for comparison to these limits include solar
+prominences, planetesimals, and comets.  Prominences of the Sun
+typically have gas masses of order $10^{14}$\,g-$10^{16}$\,g
+\cite{VialEngvold2015}.  A planetesimal of mass $\approx$10$^{15}$\,g
+with a bulk density of 1\,g\,cm$^{-3}$ would have a diameter of order
+one kilometer.  Halley's comet has a mass of order $10^{17}$\,g
+\cite{Rickman1989}, of which $\sim$$10^{14}$\,g is shed per orbit,
+most of which inspirals toward the Sun due to Poynting-Robertson drag.
+
+Broadly, our calculations suggest that if dust is responsible for the
+broadband variability of CPVs, it would need to be concentrated in
+clumps with masses in the range of $10^{15}$-$10^{17}$\,g.  Given
+$M_{\rm gas}$$\approx$8$\times$10$^{16}$\,g from
+Section~\ref{subsec:gas}, this range spans mass ratio ranges $M_{\rm
+gas}/M_{\rm dust}$ of 100 to 1.  More careful measurements of this
+ratio---in particular enabled by inferring the dust mass through high
+precision infrared spectrophotometry---would provide a pathway for
+distinguishing between environments that more closely resemble the
+interstellar medium versus protoplanetary disks.
 

### 2025-03-19 paper/ms.tex
update

@@
 
-The physical conditions inside the circumstellar plasma clumps, in
-particular the hydrogen number density, plasma temperature, ionization
-fraction, and magnetic field strength can all be estimated using the
-available data.  We caution that the following estimates are coarse:
-detailed considerations of radiative transfer and detailed balance are
-a worthwhile topic for future work, but are beyond the scope of this
+The physical conditions inside the plasma clumps, in particular the
+hydrogen number density, plasma temperature, ionization fraction, and
+magnetic field strength can all be estimated using the available data.
+We caution however that the following estimates are coarse: detailed
+considerations of radiative transfer and detailed balance are a
+worthwhile topic for future work, but are beyond the scope of this
 article.
@@
 Circumstellar H$\alpha$ emission might be sourced either from
-scattering of stellar H$\alpha$ photons, or from recombination.  We
-neglect scattering because we see the amplitude of the circumstellar
-emission to vary by a factor of $\approx$5, which is not mirrored in
-the chromospheric line core.  The volume emissivity under case B
-recombination (in which Lyman-series photons are trapped by high
-optical depth, so that recombinations cascade through H$\alpha$ and
-other Balmer lines) can be written as
+scattering of stellar H$\alpha$ photons, or from radiative
+recombination.  We neglect scattering because Figures~\ref{fig:spec}
+and~\ref{fig:hirescuts} show the amplitude of the circumstellar
+H$\alpha$ emission varying by a factor of $\approx$5, in a manner
+uncorrelated with any variability in the chromospheric line core.  The
+volume emissivity under case B recombination (in which Lyman-series
+photons are trapped by high optical depth, so that recombinations
+cascade through H$\alpha$ and other Balmer lines) can be written as
 \begin{equation}
@@
 we find $n_{\rm H}\approx 5\times10^{11}$\,cm$^{-3}$.
-Assuming a uniform density clump, this yields $M_{\rm gas}\approx
+Assuming a uniform density clump, this yields a total gas mass $M_{\rm gas}\approx
 8\times10^{16}$\,g.
@@
 Although we do not know the plasma temperature,
-if it were significantly outside the range of
-1,000 and 10,000\,K,
+if it were significantly beyond 1,000-10,000\,K,
 we would either full ionize the hydrogen, or not ionized enough of it.
@@
 ratio---in particular enabled by inferring the dust mass through high
-precision infrared spectrophotometry---would provide a pathway for
-distinguishing between environments that more closely resemble the
-interstellar medium versus protoplanetary disks.
+precision infrared spectrophotometry---could provide a pathway for
+distinguishing the scenario of a stellar outflow from an 
+accumulation of extrinsically-sourced material.
 
@@
 \item[Acknowledgments]
-  % convos w/
-  % M.~Jardine. (line core sum, explaining flux tubes)
-  % A Weinberger (dissolving rocks)
-  % L Hillenbrand (general?)
-  % line profile analysis by B.~Tofflemire.
-  % CPS group for reduction support.
-  The author thanks X, Y, Z.
-  L.G.B. was suported by...
-	Acknowledge TESS...
-  Acknowledge use of IRSA.
-
-%TC:ignore
-%% Author Contribution
-\item[Author Contributions] ...
-%TC:endignore
-
-\item[Data Availability] ...
-
-\item[Competing Interests] The authors declare that they have no competing
-financial interests.
-
-\item[Correspondence] Correspondence and requests for materials should be
-addressed to ...
-
-\item[Code availability] We provide access to a GitHub repository including all
-code created for the analysis of this project that is not already publicly
-available.
+  LGB is grateful to M.~Jardine for insightful conversations,
+  A.~Weinberger for clarification of infrared dust spectroscopy,
+  B.~Tofflemire for a clarifying line profile analysis, and to both
+  A.~Howard and H.~Isaacson for their assistance reducing the HIRES
+  spectra.
+  LGB was supported by the Carnegie Institution for Science's Carnegie
+  Fellowship and the Heising-Simons 51~Pegasi~b Fellowship.
+  Funding for the TESS mission is provided by NASA’s
+  Science Mission directorate.
+  The TESS mission is a product of millions of hours of work by
+  thousands of people, and we thank the many TESS team members for
+  their efforts to make the mission a continued success.
+  The HIRES data were obtained at the Keck Observatory, which exists
+  through a similar scale of community effort.
+  We recognize the importance that the summit of Maunakea has always had
+  within the indigenous Hawaiian community, and we are deeply grateful 
+  for the opportunity to conduct observations from this mountain.
+
+\item[Author Contributions] LGB is responsible for all aspects of this
+  work, including conceptualization, data analysis, interpretation,
+  manuscript preparation, and revision.
+
+\item[Data Availability] The TESS two-minute cadence data used in this
+  work are publicly available from the Mikulski Archive for Space
+  Telescopes (MAST; \url{https://mast.stsci.edu}). The Keck/HIRES
+  spectra analyzed here are accessible via the Keck Observatory
+  Archive (KOA; \url{https://koa.ipac.caltech.edu}).
+
+\item[Competing Interests] The author declares no competing financial
+  interests.
+
+\item[Correspondence] Correspondence and requests for materials should
+  be addressed to Luke Bouma, at either lbouma@carnegiescience.edu or
+  bouma.luke@gmail.com.
+
+\item[Code availability] We provide access to a GitHub repository
+  including all code created for the analysis of this project that is
+  not already publicly available.
 

### 2025-03-19 paper/ms.tex
update

@@
 emission at twice to four times the star's equatorial velocity,
-demonstrating the existence of extended clumps of corotating circumstellar
+demonstrating the existence of corotating clumps of circumstellar
 plasma --- a plasma torus.  Given that long-lived condensations of
@@
 these data support the idea that around the lowest-mass stars, such
-condensations can be optically thick; the exact origin of the
-optically thick material and its microphysical opacity remain unclear.
+condensations can sustain an optically thick component; the 
+origin of the optically thick material and its microphysical opacity
+remain unclear.
 \end{abstract}
@@
 only type of star to offer near-term prospects for detecting the
-atmospheres of rocky exoplanets with surface water
-\cite{NAP26141}.  Investment with JWST has proceeded accordingly.  How
-an M dwarf's evolution influences its planets---especially the
-retention of their atmospheres--- has concurrently become a major
-theme in exoplanet and stellar astrophysics.  Previous work has
-established that most M dwarfs host close-in planets
-\cite{Dressing2015} that are often subject to long
-circumstellar disk lifetimes \cite{Ribas2015}, to large doses of UV
-radiation \cite{France2013}, and to a high incidence of flares and
-coronal mass ejections \cite{Gunther2020}.  However, despite excellent
-work in these areas, the properties of the plasma and magnetospheric
-environments that bathe young, close-in exoplanets have remained
-challenging to quantify.
+atmospheres of rocky exoplanets with surface water \cite{NAP26141}.
+Investment with JWST has been proceeding accordingly
+\cite{Redfield2024,TRAPPIST1JWSTCommunityInitiative2024}.  How an M
+dwarf's evolution influences its planets---especially the retention of
+their atmospheres--- has concurrently become a major theme in
+exoplanet and stellar astrophysics.  Previous work has established
+that most M dwarfs host close-in planets \cite{Dressing2015} that are
+on average subject to long circumstellar disk lifetimes \cite{Ribas2015},
+to large doses of UV radiation \cite{France2013}, and to a high
+incidence of flares and coronal mass ejections \cite{Gunther2020}.
+However, despite excellent work in these areas, the properties of the
+plasma and magnetospheric environments that bathe young, close-in
+exoplanets have remained challenging to quantify.
 
@@
 These CPVs are
-phenomenologically identified based on their highly structured and
-periodic optical light curves;
+phenomenologically identified based on their structured, periodic
+optical light curves;
 most are M dwarfs with rotation periods shorter than two days.
@@
 However, $\approx$3\% of stars a few million years old show this
-behavior, and the observed fraction decreases to $\approx$0.3\%
+behavior, an  observed fraction which decreases to $\approx$0.3\%
 by $\approx$150\,Myr \cite{Rebull2020}.
@@
 \cite{Koen2021}.  
-% TODO: might want to plug Shapiro, Seager, ACC dark faculae...
-While the main argument against a starspot-only explanation invokes the
-timescales and amplitudes of the sharpest photometric features, no
-independent evidence has yet been acquired for the presence of any
-circumstellar material.  Geometrically, transiting clumps would imply an
-occurrence a few to at most ten times the observed rate.  The clumps
-could therefore exist around 10-30\% of M dwarfs during their early
-lives.
+The main argument against a starspot-only explanation invokes the
+timescales and amplitudes of the sharpest photometric features.
+However, no independent evidence has yet been acquired for the
+presence of any circumstellar material.  Geometrically, transiting
+clumps would imply an occurrence a few to at most ten times the
+observed rate.  The clumps could therefore exist around 10-30\% of M
+dwarfs during their early lives.
 
@@
   \href{https://lgbouma.com/movies/TIC141146667_20250116.mp4}{here},
-  shows a baseline of 5{,}784 cycles irregularly sampled over three
+  covers a baseline of 5{,}784 cycles irregularly sampled over three
   years.  The TESS light curve is phased to the \periodhr\ hour period in
@@
 decades, reported that stellar coronae contain both hot ($10^6$ K) and
-cool ($10^4$ K) plasma. In particular, time-series spectroscopy for
-stars with a wide range of masses has shown periodic high-velocity
+cool ($10^4$ K) plasma. In particular, time-series spectra of
+stars with a wide range of masses have shown periodic high-velocity
 absorption and emission in Balmer lines such as H$\alpha$, interpreted
 as long-lived, corotating clumps of cool plasma
-\cite{CollierCameron1989,Donati2000,Dunstone2006,Skelly2008}.
-Such clumps are forced into corotation by the magnetic field, and the
+\cite{CollierCameron1989,CollierCameron1992,Barnes2000,Donati2000,Dunstone2006,Skelly2008,Leitzinger2016,Cang2021}.
+Such clumps are thought to be forced into corotation by the magnetic field, and the
 exact geometry of where the plasma can accumulate is dictated by the
@@
 
-In this study, we present the first observations of corotating clumps of
+In this study, we present the first detection of corotating clumps of
 cool plasma around a CPV.  We identified TIC~141146667 in previous work
@@
 for stars showing at least three sharp, periodic dips per cycle.  We
-selected the star for spectroscopy because its brightness and rapid
-rotation enable efficiently studying small variations in the line profiles.  We
+selected the star for spectroscopy because its brightness and 
+rotation rate enable efficiently mapping out any line profile variability.  We
 observed for five hours on 17~February~2024 (UT) using the High
-Resolution Echelle Spectrometer (HIRES; \cite{vogt_hires_1994}) on the
-Keck I 10m telescope.  TESS observed the star over a four week period
+Resolution Echelle Spectrometer (HIRES \cite{vogt_hires_1994}) on the
+Keck I 10m telescope.  TESS observed the star over a four week interval
 from 30~January~2024 to 26~February~2024 with a duty cycle of 77\%.
@@
 detailed photometric behavior of the star before and after the exact
-epoch of observation; the photometric morphology is similar before and
+epoch of observation; the general photometric morphology is similar before and
 after the data gap.
@@
   Hydrogen emission from circumstellar plasma orbiting TIC 141146667.
-  {(\bf TODO)}For the best experience, please view the online movie
-  available
-  \href{https://lgbouma.com/movies/TIC141146667_sixpanel.mp4}{here}.
-  {\bf Panel a:} TESS light curve from 5 February 2024 to 26 February
-  2024 (UT) folded on the \periodhr\ hour period.  Black points are
-  phase-averaged; gray are the raw data.
-  {\bf Panel b:} Keck/HIRES H$\alpha$ spectra
-  acquired on UT 17 February 2024.  The continuum is set to unity, and the
-  darkest color is at twice the continuum to accentuate emission
-  outside the line core ($|v/v_{\rm eq}|>1$, for $v_{\rm eq}$=130\,\kms).
-  While emission in the line core originates in the stellar
-  chromosphere, the sinusoidal emission features are most readily
-  described by a warped plasma torus.
+  The online movie, available
+  \href{https://lgbouma.com/movies/TIC141146667_sixpanel.mp4}{here},
+  shows the spectral evolution over five hours.
+  {\bf Panel a:} Average TESS light curve from 5 February 2024 to 26
+  February 2024 (UT) folded on the \periodhr\ hour period.  Black
+  points are phase-averaged; gray are the raw data.
+  {\bf Panel b:} Keck/HIRES H$\alpha$ spectra acquired on UT 17
+  February 2024.  The continuum is set to unity, and the darkest color
+  is at twice the continuum to accentuate emission outside the line
+  core ($|v/v_{\rm eq}|>1$, for $v_{\rm eq}$=130\,\kms).  While
+  emission in the line core originates in the star's chromosphere,
+  the sinusoidal emission features are most readily described by a
+  warped plasma torus.
   {\bf Panel c:} Individual epochs of Panel b, visible in the
@@
 % photometry
-Figure~\ref{fig:spec} shows the data from February 2024.  Over
-timescales of years, CPVs maintain a fixed period while their
-photometric morphology evolves.  TIC~141146667 indeed evolved relative
-to the February 2022 discovery data \cite{Bouma2024}.  In February
-2024, the average photometric signal showed a small brightening
-over 45\% of the period, followed by a complex flux dip spanning 55\%
-of the period.  This eclipse feature shows two to three local
-photometric minima, and one to two local maxima.  Its W-shape is
+Figure~\ref{fig:spec} shows the TESS and HIRES data from February
+2024.  Over timescales of years, CPVs maintain a fixed period while
+their photometric morphology evolves.  TIC~141146667 indeed evolved
+relative to the February 2022 discovery data (see Figure~\ref{fig:lc}.
+In February 2024, the average photometric signal showed a small
+brightening over 45\% of the period, followed by a complex flux dip
+spanning 55\% of the period.  This eclipse feature shows two to three
+local photometric minima, and one to two local maxima.  Its W-shape is
 suggestive of eclipse geometries seen in some forward models of warped
@@
 this age and spectral type, one would expect emission in the line core
-to be generated in the stellar chromosphere
+to be generated in the star's chromosphere
 and then modulated by any occulting material capable of absorbing or
@@
 prominences, which are cool condensations of plasma in the solar corona
-that can last days to weeks \cite{VialEngvold2015}.  In our Sun's
-magnetosphere, these condensations fall back to the solar surface
-because gravity is stronger than any magnetic tension or centrifugal force
-capable of sustaining them.  However for stars with magnetospheric radii
-$R_{\rm m}$ that exceed their corotation radii $R_{\rm c}$, the
-effective potential experienced by a charged particle can have a local
-minimum outside $R_{\rm c}$, enabling the material to accumulate over
-much longer timescales \cite{Petit2013,Daley-Yates2024}.  Generally
+that can last days to weeks \cite{VialEngvold2015}.  These
+condensations fall back to the solar surface because gravity is
+stronger than any magnetic tension or centrifugal force capable of
+sustaining them.  However for stars with magnetospheric radii $R_{\rm
+m}$ that exceed their corotation radii $R_{\rm c}$, the effective
+potential experienced by a charged particle can have a local minimum
+outside $R_{\rm c}$, enabling the material to accumulate over much
+longer timescales \cite{Petit2013,Daley-Yates2024}.  Generally
 speaking, such material need neither transit, nor be optically thick.
+For instance, the H$\alpha$ emission clump at 3.9\,$R_\star$ shows no 
+photometric signal in the February 2024 photometry.
 
@@
 are present in at least one such star.
-Characteristic densities and masses of these
-%TODO check; quote N_H instead...
-clumps are $n \sim 10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see
-Supplementary Methods Section~\ref{subsec:model}), a similar density to
-solar prominences, but ten to one hundred times more massive.  This
+Based on the observed H$\alpha$ luminosity, the characteristic
+densities and masses of the gaseous component of these clumps are
+$n_{\rm H} \sim 10^{11}$-$10^{12}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g
+(see Section~\ref{subsec:gas}).
+Any dust, if present, is independently constrained to have a total
+mass $10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm g}$ (see
+Section~\ref{subsec:dust}).
+This
 observation rules out a ``starspot-only'' origin scenario for CPVs,
-\cite{Koen2021} since such scenarios have no means of explaining
+\cite{Koen2021} because such scenarios have no means of explaining
 spectroscopic emission beyond the stellar disk.  Similarly, scenarios in
@@
 result is light curves that appear ``simple'', resembling those of
-eclipsing binaries \cite{Townsend2008}.  The two known exceptions,
+eclipsing binaries, and ``S-wave'' H$\alpha$ spectra similar to those
+in Figure~\ref{fig:spec} \cite{Townsend2005,Townsend2008}.  The two known exceptions,
 HD~37776 and HD~64740, show complex light curves resembling CPVs
@@
 fields with highly multipolar contributions.  Second, CPVs can be a
-source of astrophysical false positives in photometric searches for
-eclipsing binaries and transiting exoplanets around young pre-main
+source of astrophysical false positives in photometric classification
+of eclipsing binaries and transiting exoplanets around young pre-main
 sequence M dwarfs \cite{Johns-Krull2016,Bouma2020}.
@@
 rocky-body origin.  Compositions and sizes similar to the interstellar
-medium would be
-indicative of condensed dust in an M dwarf wind, similar to that formed
-in the environments of more evolved stars \cite{Marigo2008}.
+medium could be indicative of condensed dust in an M dwarf wind,
+similar to that formed in the environments of more evolved stars
+\cite{Marigo2008}.
 
@@
 emission produced by an electron cyclotron maser instability
-\cite{Callingham2021} would provide a measurement of the field
+(e.g. \cite{Callingham2021}) would provide a measurement of the field
 strength at the site of the emitting region.
@@
 phenomenon \cite{Rebull2020}, and our data show that the complex
-photometric features occur when clumps of circumstellar material is
-transiting the star.  The implied geometric correction suggests that
+photometric features occur when clumps of circumstellar material 
+transit the star.  The implied geometric correction suggests that
 an appreciable minority (10-30\%) of young M dwarfs -- the rapidly
@@
 \subsection{Spectroscopic Variability}\phantom{+}
+\label{subsec:specvar}
 

### 2025-03-19 paper/ms.tex
update

@@
 
-Figure~\ref{fig:hirescuts} shows a few regions of interest in the HIRES
-spectra, which cover 3650-7960\,\AA.
-Higher order Balmer lines including H$\gamma$ and H$\delta$ (the
-$n=5\rightarrow2$ and $n=6\rightarrow2$ transitions respectively) do
-show some variability outside the line core.
-However, this variability is not clearly periodic in the
-same manner as the emission seen in H$\alpha$.
-This could be because there are insufficient hydrogen ions in the
-relevant excited states, or due to the lower precision of the spectra
-in these bluer regions.
-The Ca HK doublet for instance is also detectable in emission, however
-the continuum near it is not.
-Chromospheric emission lines in the magnesium triplet order are
-also detectable, but sufficiently blended to be rendered unusable.
+Figure~\ref{fig:hirescuts} shows a few regions of interest in the
+HIRES spectra, which cover 3650-7960\,\AA.  Higher order Balmer lines
+including H$\gamma$ and H$\delta$ (the $n=5\rightarrow2$ and
+$n=6\rightarrow2$ transitions respectively) do show some variability
+outside the line core.  However, this variability is not clearly
+periodic in the same manner as the emission seen in H$\alpha$.  This
+could be because there are insufficient hydrogen ions recombining from
+the relevant excited states, or due to the lower precision of the
+spectra in these bluer regions.  The Ca HK doublet for instance is
+also detectable in emission, however the continuum near it is not.
+Chromospheric emission lines in the magnesium triplet order are also
+detectable, but sufficiently blended to be rendered unusable.
 
@@
 	  %
-    %TODO: eROSITA?  ROSAT is an emitter.  GALEX detection.
+    % NOTE: ROSAT is an emitter.  GALEX detection.
     % Ofek+2011 1.4Ghz emitter.  Helfand+2015 ditto.  Bruzewski+2021.
-    %\hline
-    %\multicolumn{3}{c}{Kinematics and Position} \\
-    %\hline
-    %$RV$ (\kms) & 0.61 $\pm$ 1.47 & HIRES \\
-    %$U$ (\kms)  & & \\
-    %$V$ (\kms)  & & \\
-    %$W$ (\kms)  & & \\
-    %$X$ (pc)    & -28.4 & \\
-    %$Y$ (pc)    &  19.8 & \\
-    %$Z$ (pc)    &  67.0 & \\
     \hline
@@
     $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & \cite{Bouma2024} SED fit \\
+    $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & \cite{Bouma2024} SED fit \\
     $P_{\rm rot}$ (hours) & $3.930\pm 0.001$ & TESS \\ 
@@
     $A_V$ (mag) & 0 & \cite{Green2019} \\
-    %$F_{bol}$ (erg cm$^{-2}$ s$^{-1}$ ) & todo & This work\\
-    %$L_\star$ ($L_{\odot}$)  & todo & This work\\
     $M_\star$ ($M_{\odot}$)  & 0.22 $\pm$ 0.02  & PARSEC \cite{Chen2014}\\
@@
   \begin{tabular}{lcr}
-  %\setlength{\tabcolsep}{2pt}
-  \hline 
-  \hline 
-  Time [JD$_{\rm UTC}$] & RV (\kms) & $\sigma_{\rm RV}$ (\kms) \\
-  % from tables/tab_TIC141146667_rel_rv.tex
-  \hline 
-  60357.450329 & 2.73 & 5.86 \\
-  60357.461255 & -4.40 & 2.37 \\
-  60357.472181 & -0.19 & 2.64 \\
-  60357.483109 & 3.84 & 2.87 \\
-  60357.494030 & 7.53 & 7.53 \\
-  60357.504949 & -1.98 & 1.44 \\
-  60357.515873 & 1.02 & 1.21 \\
-  60357.526794 & 0.64 & 7.03 \\
-  60357.537717 & -2.91 & 2.71 \\
-  60357.548639 & 8.93 & 6.75 \\
-  60357.559566 & 5.95 & 8.84 \\
-  60357.570487 & -2.25 & 3.06 \\
-  60357.581408 & 1.84 & 1.34 \\
-  60357.592330 & 2.41 & 8.24 \\
-  60357.603251 & -7.04 & 3.94 \\
-  60357.614172 & -2.24 & 3.07 \\
-  60357.625095 & -2.83 & 7.55 \\
-  60357.636019 & -0.59 & 2.26 \\
-  60357.646940 & 1.84 & 2.91 \\
-  60357.657861 & 4.54 & 3.95 \\
-  60357.668781 & 6.21 & 12.14 \\
+  \hline 
+  \hline 
+  Time [BJD$_{\rm TDB}$] & RV (\kms) & $\sigma_{\rm RV}$ (\kms) \\
+  % from tables/tab_TIC141146667_rel_rv.tex and
+  % tables/tab_TIC141146667_times_rounded.csv
+  \hline 
+  2460357.954919 & 2.73 & 5.86 \\
+  2460357.965845 & -4.40 & 2.37 \\
+  2460357.976770 & -0.19 & 2.64 \\
+  2460357.987698 & 3.84 & 2.87 \\
+  2460357.998619 & 7.53 & 7.53 \\
+  2460358.009538 & -1.98 & 1.44 \\
+  2460358.020462 & 1.02 & 1.21 \\
+  2460358.031383 & 0.64 & 7.03 \\
+  2460358.042306 & -2.91 & 2.71 \\
+  2460358.053228 & 8.93 & 6.75 \\
+  2460358.064154 & 5.95 & 8.84 \\
+  2460358.075075 & -2.25 & 3.06 \\
+  2460358.085996 & 1.84 & 1.34 \\
+  2460358.096918 & 2.41 & 8.24 \\
+  2460358.107839 & -7.04 & 3.94 \\
+  2460358.118760 & -2.24 & 3.07 \\
+  2460358.129683 & -2.83 & 7.55 \\
+  2460358.140606 & -0.59 & 2.26 \\
+  2460358.151527 & 1.84 & 2.91 \\
+  2460358.162448 & 4.54 & 3.95 \\
+  2460358.173368 & 6.21 & 12.14 \\
   \hline

### 2025-03-19 paper/ms.tex
update

@@
 \normalfont
-Roughly one percent of red dwarfs younger than 100 million years
-show structured, periodic optical light curves suggestive of
-transiting opaque material that corotates with the star
+Roughly one percent of red dwarfs younger than 100 million years show
+structured, periodic optical light curves suggestive of transiting
+opaque material that corotates with the star
 \cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.  The
@@
 periodic variables (CPVs) are explained by complex distributions of
-bright or dark regions on the stellar surfaces
-\cite{Koen2021}.  Here, we present time-series spectroscopy and
-photometry of a rapidly-rotating ($P$=3.9\,hr)
-CPV, TIC~141146667. The spectra show coherent sinusoidal Balmer
-emission at twice to four times the star's equatorial velocity,
-demonstrating the existence of corotating clumps of circumstellar
-plasma --- a plasma torus.  Given that long-lived condensations of
-cool ($10^4$ K) plasma can persist in the hot ($10^6$ K) coronae of
-stars with a wide range of masses
+bright or dark regions on the stellar surfaces \cite{Koen2021}.
+Here, we present time-series spectroscopy and photometry of a
+rapidly-rotating ($P$=3.9\,hr) CPV, TIC~141146667. The spectra show
+coherent sinusoidal Balmer emission at twice to four times the
+star's equatorial velocity, demonstrating the existence of
+corotating clumps of circumstellar plasma --- a plasma torus.  Given
+that long-lived condensations of cool ($10^4$ K) plasma can persist
+in the hot ($10^6$ K) coronae of stars with a wide range of masses
 \cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
 these data support the idea that around the lowest-mass stars, such
-condensations can sustain an optically thick component; the 
-origin of the optically thick material and its microphysical opacity
-remain unclear.
+condensations can sustain an optically thick component; the origin
+of the optically thick material and its microphysical opacity remain
+unclear.
 \end{abstract}
@@
 
-%\subsection{Introduction}
 M dwarfs, stars with masses below about half that of the Sun, are the
@@
 that most M dwarfs host close-in planets \cite{Dressing2015} that are
-on average subject to long circumstellar disk lifetimes \cite{Ribas2015},
-to large doses of UV radiation \cite{France2013}, and to a high
-incidence of flares and coronal mass ejections \cite{Gunther2020}.
-However, despite excellent work in these areas, the properties of the
-plasma and magnetospheric environments that bathe young, close-in
-exoplanets have remained challenging to quantify.
+on average subject to long circumstellar disk lifetimes
+\cite{Ribas2015}, to large doses of UV radiation \cite{France2013},
+and to a high incidence of flares and coronal mass ejections
+\cite{Gunther2020}.  However, despite excellent work in these areas,
+the properties of the plasma and magnetospheric environments that
+bathe young, close-in exoplanets have remained challenging to
+quantify.
 
 One glaring example of our current ignorance is the complex periodic
-variables (CPVs).  While Figure~\ref{fig:lc} highlights the main object of
-interest in this article, over one hundred analogous objects have
-now been found by K2 and TESS 
+variables (CPVs).  While Figure~\ref{fig:lc} highlights the main
+object of interest in this article, over one hundred analogous objects
+have now been found by K2 and TESS
 \cite{Rebull2016,Stauffer2017,Rebull2018,Zhan2019,Rebull2020,Bouma2024}.
-These CPVs are
-phenomenologically identified based on their structured, periodic
-optical light curves;
-most are M dwarfs with rotation periods shorter than two days.
-Within current sensitivity limits, none have primordial disks
-\cite{Stauffer2017,Bouma2024}.
+These CPVs are phenomenologically identified based on their
+structured, periodic optical light curves; most are M dwarfs with
+rotation periods shorter than two days.  Within current sensitivity
+limits, none have primordial disks \cite{Stauffer2017,Bouma2024}.
 However, $\approx$3\% of stars a few million years old show this
-behavior, an  observed fraction which decreases to $\approx$0.3\%
-by $\approx$150\,Myr \cite{Rebull2020}.
+behavior, an  observed fraction which decreases to $\approx$0.3\% by
+$\approx$150\,Myr \cite{Rebull2020}.
 
@@
 transiting clumps of circumstellar material corotate with the star
-\cite{Stauffer2017,Gunther2022,Bouma2024}, or that these stars represent
-an extreme in naturally-occurring distributions of starspots or faculae
-\cite{Koen2021}.  
-The main argument against a starspot-only explanation invokes the
-timescales and amplitudes of the sharpest photometric features.
-However, no independent evidence has yet been acquired for the
-presence of any circumstellar material.  Geometrically, transiting
-clumps would imply an occurrence a few to at most ten times the
-observed rate.  The clumps could therefore exist around 10-30\% of M
-dwarfs during their early lives.
+\cite{Stauffer2017,Gunther2022,Bouma2024}, or that these stars
+represent an extreme in naturally-occurring distributions of starspots
+or faculae \cite{Koen2021}.  The main argument against a starspot-only
+explanation invokes the timescales and amplitudes of the sharpest
+photometric features.  However, no independent evidence has yet been
+acquired for the presence of any circumstellar material.
+Geometrically, transiting clumps would imply an occurrence a few to at
+most ten times the observed rate.  The clumps could therefore exist
+around 10-30\% of M dwarfs during their early lives.
 
@@
   \caption{{\bf Figure 1 (Movie):  TIC~141146667 is a complex periodic
-  variable (CPV).}  The online movie,
-  available
+  variable (CPV).}  The online movie, available
   \href{https://lgbouma.com/movies/TIC141146667_20250116.mp4}{here},
   covers a baseline of 5{,}784 cycles irregularly sampled over three
-  years.  The TESS light curve is phased to the \periodhr\ hour period in
-  groups of a few cycles per frame.  This is the period both of
+  years.  The TESS light curve is phased to the \periodhr\ hour period
+  in groups of a few cycles per frame.  This is the period both of
   stellar rotation, and (we hypothesize) of corotating clumps of
@@
 decades, reported that stellar coronae contain both hot ($10^6$ K) and
-cool ($10^4$ K) plasma. In particular, time-series spectra of
-stars with a wide range of masses have shown periodic high-velocity
+cool ($10^4$ K) plasma. In particular, time-series spectra of stars
+with a wide range of masses have shown periodic high-velocity
 absorption and emission in Balmer lines such as H$\alpha$, interpreted
@@
 \cite{CollierCameron1989,CollierCameron1992,Barnes2000,Donati2000,Dunstone2006,Skelly2008,Leitzinger2016,Cang2021}.
-Such clumps are thought to be forced into corotation by the magnetic field, and the
-exact geometry of where the plasma can accumulate is dictated by the
-field's topology.  For instance, a tilted dipole field tends
-to yield an accumulation surface of a warped torus
+Such clumps are thought to be forced into corotation by the magnetic
+field, and the exact geometry of where the plasma can accumulate is
+dictated by the field's topology.  For instance, a tilted dipole field
+tends to yield an accumulation surface of a warped torus
 \cite{Townsend2005}, whereas in the limit of a single strong field
 line, accumulation occurs at the line's apex, furthest from the star
-\cite{Waugh2022}.
-To date, none of these spectroscopic variables have shown any
-photometric anomalies \cite{Bouma2024}, leaving open the issue of
-whether they are related to CPVs.
-%A circumstantial argument that they might is that CPVs do respond to
-%sudden magnetic field changes: the otherwise long-lived eclipse
-%features often disappear following stellar flares
-%\cite{Stauffer2017,Bouma2024}.
+\cite{Waugh2022}.  To date, none of these spectroscopic variables have
+shown any photometric anomalies \cite{Bouma2024}, leaving open the
+issue of whether they are related to CPVs.
 
 In this study, we present the first detection of corotating clumps of
-cool plasma around a CPV.  We identified TIC~141146667 in previous work
-\cite{Bouma2024} by searching the TESS two-minute data \cite{Ricker2015}
-for stars showing at least three sharp, periodic dips per cycle.  We
-selected the star for spectroscopy because its brightness and 
-rotation rate enable efficiently mapping out any line profile variability.  We
-observed for five hours on 17~February~2024 (UT) using the High
-Resolution Echelle Spectrometer (HIRES \cite{vogt_hires_1994}) on the
-Keck I 10m telescope.  TESS observed the star over a four week interval
-from 30~January~2024 to 26~February~2024 with a duty cycle of 77\%.
-During the spectral observations, TESS was performing a data downlink;
-TESS data collection resumed 12 hours (three rotation cycles) after the
-spectra were acquired.  Extended Data Figure~\ref{fig:fulllc} shows the
+cool plasma around a CPV.  We identified TIC~141146667 in previous
+work \cite{Bouma2024} by searching the TESS two-minute data
+\cite{Ricker2015} for stars showing at least three sharp, periodic
+dips per cycle.  We selected the star for spectroscopy because its
+brightness and rotation rate enable efficiently mapping out any line
+profile variability.  We observed for five hours on 17~February~2024
+(UT) using the High Resolution Echelle Spectrometer (HIRES
+\cite{vogt_hires_1994}) on the Keck I 10m telescope.  TESS observed
+the star over a four week interval from 30~January~2024 to
+26~February~2024 with a duty cycle of 77\%.  During the spectral
+observations, TESS was performing a data downlink; TESS data
+collection resumed 12 hours (three rotation cycles) after the spectra
+were acquired.  Extended Data Figure~\ref{fig:fulllc} shows the
 detailed photometric behavior of the star before and after the exact
-epoch of observation; the general photometric morphology is similar before and
-after the data gap.
+epoch of observation; the general photometric morphology is similar
+before and after the data gap.
 
@@
 %
-%$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & YYY              & X \\
-%
 $R_\star$\dotfill                       & Stellar radius ($R_\odot$)\dotfill                             & 0.42$\pm$0.02    & 1 \\
@@
 %
-$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill
-  & $1.82 \pm 0.10$  & 6 \\
+$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   & $1.82 \pm 0.10$  & 6 \\
                                         & \hspace{3pt} radius ($R_\star$)	                               &                      \\
@@
 1: SED fit \cite{Bouma2024}.
-2: Gaia DR3 photometry and lack of lithium (see~\ref{subsec:stparams}).
+2: Pre-main sequence Gaia DR3 photometry, but lacks of lithium (see~\ref{subsec:stparams}).
 3: PARSEC v1.2S \cite{Chen2014}.
-%$^6$Cluster isochrone (MIST adopted; PARSEC compared for quoted
-%  uncertainty),
 4: Keck/HIRES.
@@
 7: Gaia DR3 geometric \cite{GaiaDR3}.
-%  3: HIRES spectra and specmatch(?),
-%$^8$Pre-main-sequence CAMD interpolation (Section~\ref{sec:camd}),
 }
@@
 
-Finally, a constraint on the magnetic field strength at the site of the clump
-follows from the requirement that the magnetic pressure exceed the
-thermal pressure, $B^2 / 8\pi > n_{\rm H} k T$.
-Although we do not know the plasma temperature,
-if it were significantly beyond 1,000-10,000\,K,
-we would either full ionize the hydrogen, or not ionized enough of it.
-We can therefore estimate
+Finally, a constraint on the magnetic field strength at the site of
+the clump follows from the requirement that the magnetic pressure
+exceed the thermal pressure, $B^2 / 8\pi > n_{\rm H} k T$.  Although
+we do not know the plasma temperature, if it were significantly beyond
+1,000-10,000\,K, we would either full ionize the hydrogen, or not
+ionized enough of it.  We can therefore estimate
 \begin{equation}
@@
 present seems plausible given observations of chromatic transits in
-analogous objects \cite{Tanimoto2020,Gunther2022,Koen2023}.
-This scenario is highly constrained.  An upper limit on the amount of
-hot dust follows from the lack of an infrared excess.  A lower limit
+analogous objects \cite{Tanimoto2020,Gunther2022,Koen2023}.  This
+scenario is highly constrained.  An upper limit on the amount of hot
+dust follows from the lack of an infrared excess.  A lower limit
 follows if one assumes that most of the broadband optical depth comes
@@
 
-% TEMPLATE: IRAS041
-%
 \begin{table}
@@
     Gaia & 860453786736413568 & Gaia\ DR3 \\
-    %2MASS & J04154278+2909597 & J04154269+2909558 & 2MASS \\
-    %ALLWISE & J041542.77+290959.5 & ... & ALLWISE\\
     \hline
@@
 
-\bibliography{cpvbib.bib} % common bib file
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliography{cpvbib.bib}
 \bibliographystyle{naturemagfixed}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{addendum}
@@
 \item[Acknowledgments]
-  LGB is grateful to M.~Jardine for insightful conversations,
-  A.~Weinberger for clarification of infrared dust spectroscopy,
-  B.~Tofflemire for a clarifying line profile analysis, and to both
-  A.~Howard and H.~Isaacson for their assistance reducing the HIRES
-  spectra.
+  LGB is grateful to M.~Jardine, A.~Weinberger, and B.~Tofflemire for
+  insightful conversations, and to A.~Howard and H.~Isaacson for their
+  assistance reducing the HIRES spectra.
   LGB was supported by the Carnegie Institution for Science's Carnegie
   Fellowship and the Heising-Simons 51~Pegasi~b Fellowship.
-  Funding for the TESS mission is provided by NASA’s
-  Science Mission directorate.
+  %
+  Funding for the TESS mission is provided by NASA’s Science Mission
+  directorate.
   The TESS mission is a product of millions of hours of work by
-  thousands of people, and we thank the many TESS team members for
-  their efforts to make the mission a continued success.
+  thousands of people; we thank the TESS team for their efforts to
+  make the mission a continued success.
   The HIRES data were obtained at the Keck Observatory, which exists

### 2025-03-19 drivers/plot_lineevolnpanel.py
update

@@ -264,7 +264,6 @@ def plot_lineevolnpanel(outdir, starid=None, jstr=None, remove_cosmics=0):
     cb = fig.colorbar(_lc, cax=cax, orientation="horizontal")
 
     cb.ax.tick_params(labelsize='x-small', pad=0.7)
-    #cb.ax.set_title('$t$ [hours]', fontsize='x-small', pad=0.3)
     cb.ax.set_title('Phase $\phi$', fontsize='x-small', pad=0.4)
 
     #cb.ax.set_xticks([0,2,4])

### 2025-03-19 paper/collect_figs.sh

@@ -6,15 +6,15 @@ r="/Users/luke/Dropbox/proj/cpv/results"
 cp $r/movie_phase_timegroups/TIC_141146667/TIC_141146667_0081_2min_phase_timegroups.pdf figures/f1.pdf
 
 # Animated supporting: Movie of S41, S48, S75 TESS photometry, cycle-grouped
-cp $r/movie_phase_timegroups/TIC_141146667/movie_TIC1411_flux_phase_bow.mov movies/m1.mov
+cp $r/movie_phase_timegroups/TIC_141146667/movie_TIC1411_flux_phase_wob.mov movies/m1.mov
 
 ##########################################
 # figure2: Hydrogen emission from circumstellar plasma orbiting TIC 141146667.
 # -still: index 0012.  t=3.1hr
-cp $r/movie_sixpanel_specriver/TIC_141146667_science/specriver_141146667_Hα_0012_2min_remove25pct_normbyveq_showlinecoresum.png figures/f2.png
+cp $r/movie_sixpanel_specriver/TIC_141146667_science/specriver_141146667_Hα_0012_2min_remove25pct_normbyveq_showlinecoresum.pdf figures/f2.pdf
 
 # Animated supporting: Movie of spectral timeseries
-cp $r/movie_sixpanel_specriver/TIC_141146667_science/TIC141146667_sixpanel.mov movies/m2.mov
+cp $r/movie_sixpanel_specriver/TIC_141146667_science_wob/TIC141146667_sixpanel.mov movies/m2.mov
 
 ##########################################
 # supplementary

### 2025-03-20 paper/ms.tex
update

@@
 atmospheres of rocky exoplanets with surface water \cite{NAP26141}.
-Investment with JWST has been proceeding accordingly
+Community investment with JWST has proceeded accordingly
 \cite{Redfield2024,TRAPPIST1JWSTCommunityInitiative2024}.  How an M
 dwarf's evolution influences its planets---especially the retention of
-their atmospheres--- has concurrently become a major theme in
+their atmospheres--- has in turn become a major theme in
 exoplanet and stellar astrophysics.  Previous work has established
@@
 and to a high incidence of flares and coronal mass ejections
-\cite{Gunther2020}.  However, despite excellent work in these areas,
+\cite{Gunther2020}.  However, despite the excellent work in these areas,
 the properties of the plasma and magnetospheric environments that
@@
   \caption{{\bf Figure 1 (Movie):  TIC~141146667 is a complex periodic
-  variable (CPV).}  The online movie, available
-  \href{https://lgbouma.com/movies/TIC141146667_20250116.mp4}{here},
+  variable (CPV).}  The online movie,
+  \href{https://lgbouma.com/movies/TIC141146667_20250116.mp4}{available here},
   covers a baseline of 5{,}784 cycles irregularly sampled over three
@@
 
-In this study, we present the first detection of corotating clumps of
+In this study, we present the first spectroscopic detection of corotating clumps of
 cool plasma around a CPV.  We identified TIC~141146667 in previous
 work \cite{Bouma2024} by searching the TESS two-minute data
-\cite{Ricker2015} for stars showing at least three sharp, periodic
-dips per cycle.  We selected the star for spectroscopy because its
-brightness and rotation rate enable efficiently mapping out any line
-profile variability.  We observed for five hours on 17~February~2024
+\cite{Ricker2015} for stars showing highly structured, periodic light
+curves.  We selected the star for spectroscopy because its
+brightness and rotation rate enable efficiently mapping out line
+profile variability.  We observed it for five hours on 17~February~2024
 (UT) using the High Resolution Echelle Spectrometer (HIRES
@@
 the star over a four week interval from 30~January~2024 to
-26~February~2024 with a duty cycle of 77\%.  During the spectral
+26~February~2024 with a duty cycle of 77\%.  During the HIRES
 observations, TESS was performing a data downlink; TESS data
@@
 were acquired.  Extended Data Figure~\ref{fig:fulllc} shows the
-detailed photometric behavior of the star before and after the exact
+detailed photometric behavior of the star near the
 epoch of observation; the general photometric morphology is similar
@@
   \centering
-  \includegraphics[width=0.99\textwidth]{figures/f2.png}
+  \includegraphics[width=0.99\textwidth]{figures/f2.pdf}
   \captionsetup{labelformat=empty}
   \caption{{\bf Figure 2 (Movie):}  
-  Hydrogen emission from circumstellar plasma orbiting TIC 141146667.
-  The online movie, available
-  \href{https://lgbouma.com/movies/TIC141146667_sixpanel.mp4}{here},
+  Emission from circumstellar plasma orbiting TIC 141146667.
+  The online movie,
+  \href{https://lgbouma.com/movies/TIC141146667_sixpanel.mp4}{available here},
   shows the spectral evolution over five hours.
@@
   points are phase-averaged; gray are the raw data.
-  {\bf Panel b:} Keck/HIRES H$\alpha$ spectra acquired on UT 17
+  {\bf Panel b:} Keck/HIRES H$\alpha$ spectra acquired on 17
   February 2024.  The continuum is set to unity, and the darkest color
@@
   {\bf Panel e:} As in Panel b, after subtracting the time-averaged
-  spectrum. In addition to circumstellar emission, the line core shows
-  absorption during the plasma clump transits.  The asymmetric stretch
+  spectrum.  The line core shows H$\alpha$ excesses and decrements
+  advancing from the blue to red wings.
+  The asymmetric color stretch
   is set to match the dynamic range of the data.
@@
 % photometry
-Figure~\ref{fig:spec} shows the TESS and HIRES data from February
+Figure~\ref{fig:spec} compiles the TESS and HIRES data from February
 2024.  Over timescales of years, CPVs maintain a fixed period while
 their photometric morphology evolves.  TIC~141146667 indeed evolved
-relative to the February 2022 discovery data (see Figure~\ref{fig:lc}.
+relative to the February 2022 discovery data (see Figure~\ref{fig:lc}).
 In February 2024, the average photometric signal showed a small
@@
 local photometric minima, and one to two local maxima.  Its W-shape is
-suggestive of eclipse geometries seen in some forward models of warped
+suggestive of eclipse geometries seen in certain forward models of warped
 plasma tori \cite{Townsend2008}.
@@
 % * keck/hires: behavior at v/veq<1
-The behavior within the stellar H$\alpha$ line core, at $|\Delta v /
-v_{\rm eq}|<1$, is more complex than outside it.  For stars of
-this age and spectral type, one would expect emission in the line core
-to be generated in the star's chromosphere
-and then modulated by any occulting material capable of absorbing or
-emitting H$\alpha$ photons.  In Figure~\ref{fig:spec}e, the behavior from
-$\phi$=0.4-1.2 has a simple interpretation: from $\phi$=0.4-0.9, a hot
-region first gradually crosses the stellar line profile, followed from
-$\phi$=0.7-1.2 by the transit of a cool region.  Phases $\phi$$<$0.4
+Within the stellar H$\alpha$ line core, at $|\Delta v /
+v_{\rm eq}|<1$, we observe a superposition of emission from the star's
+chromosphere,
+modulated by any occulting material capable of absorbing or
+emitting H$\alpha$ photons.  In Figure~\ref{fig:spec}e, the data from
+$\phi$=0.4-1.2 have a simple interpretation: from $\phi$=0.4-0.9, a hot
+(emitting) region first gradually crosses the stellar line profile, followed from
+$\phi$=0.7-1.2 by the transit of a cool (absorbing) region. Phases $\phi$$<$0.4
 show a mix of similar events, though the time sampling is
@@
 summed flux at $|\Delta v / v_{\rm eq}|<1$.  This panel shows that
-changes in the line core flux are usually correlated with the
-broadband variability, except at $\phi$=0.5, during the transit of the
-3.9\,$R_\star$ clump and the occultation of the lower-velocity clump.
+changes in the line core flux are correlated with the
+broadband variability over most of the light curve, except at
+$\phi$$\approx$0.5, during the transit of the 3.9\,$R_\star$ clump and
+the occultation of the lower-velocity clump.
 
 \begin{table*}
-\scriptsize
+\small
 \setlength{\tabcolsep}{2pt}
@@
 %
-$\langle$EW$_{\rm H\alpha}$$\rangle$    & Time-averaged H$\alpha$ line core                              &  X.X             & Y \\ 
+$\langle$EW$_{\rm H\alpha}$$\rangle$    & Time-averaged H$\alpha$ line core                              &  7.2 $\pm$ 0.2   & 4 \\ 
                                         & \hspace{3pt} equivalent width (\AA)	                           &                      \\
-Range(EW$_{\rm H\alpha}$)$_1$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
-                                        & \hspace{3pt} from Clump 1 (\AA)	                               &                      \\
-Range(EW$_{\rm H\alpha}$)$_2$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
-                                        & \hspace{3pt} from Clump 2 (\AA)	                               &                      \\
 \hline
@@
 \footnotesize{ \textsc{NOTE}---
-$^*$ Given only $v\sin i$ and $2\pi R_\star/P_{\rm rot}$, $\cos i=0.11^{+0.11}_{-0.08}$.
 Provenances are:
 1: SED fit \cite{Bouma2024}.
-2: Pre-main sequence Gaia DR3 photometry, but lacks of lithium (see~\ref{subsec:stparams}).
+2: Gaia DR3 photometry shows the star is on the pre-main sequence,
+   while the spectrum lacks lithium (see~\ref{subsec:stparams}).
 3: PARSEC v1.2S \cite{Chen2014}.
@@
 \cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} as well as
-transient absorption features in their line cores
+transient absorption features
 \cite{CollierCameron1989,CollierCameron1992,Cang2020} similar to
@@
 are present in at least one such star.
-Based on the observed H$\alpha$ luminosity, the characteristic
-densities and masses of the gaseous component of these clumps are
-$n_{\rm H} \sim 10^{11}$-$10^{12}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g
-(see Section~\ref{subsec:gas}).
-Any dust, if present, is independently constrained to have a total
-mass $10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm g}$ (see
-Section~\ref{subsec:dust}).
 This
@@
 clumps must include plasma with a significant population of hydrogen
-atoms in the $n$=3 excited state.  While this plasma is undoubtedly
-sculpted by the star's magnetic field, it could plausibly originate from
+atoms in the $n$=3 excited state.  
+More quantitatively, the observed H$\alpha$ luminosity suggests
+characteristic densities and masses for the gaseous component of these
+clumps of $n_{\rm H} \sim 10^{11}$-$10^{12}$\,cm$^{-3}$ and $M_{\rm
+gas} \sim 10^{17}$\,g (see Section~\ref{subsec:gas}).
+Dust, if present, is independently constrained to have a total
+mass $10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm g}$ (see
+Section~\ref{subsec:dust}).
+This circumstellar material could plausibly originate from
 three sites: the star, an old and undetected disk, or outgassing rocky
@@
 result is light curves that appear ``simple'', resembling those of
-eclipsing binaries, and ``S-wave'' H$\alpha$ spectra similar to those
+eclipsing binaries, and time-dynamic H$\alpha$ spectra similar to those
 in Figure~\ref{fig:spec} \cite{Townsend2005,Townsend2008}.  The two known exceptions,
@@
 (e.g. \cite{Callingham2021}) would provide a measurement of the field
-strength at the site of the emitting region.
+strength at the site of the emitting region, further clarifying the
+magnetic field's structure.
 
@@
   (BTJD 3356-3358.5) and Moon (BTJD 3359.5-3360.5).
-  Raw two minute data are in gray; black time-averages ten minute
+  Raw two minute data are in gray; black time-averages to ten minute
   sampling.
@@
   in which the dip at $\phi$$\approx$0.8 disappeared.
-  While the large eclipse feature remained present before and after
+  While the large eclipse feature was present both before and after
   the HIRES sequence, its photometric shape evolved during the data
@@
 41, 48 (TESS DDT039, PI: Kunimoto), and 75 (TESS Program G06030, PI:
-Bouma).  The data from Sectors 14, 15, and 21 had a 30-minute cadence,
+Bouma).  The data from Sectors 14, 15, and 21 had 30-minute cadence,
 which smears sharp features over the $<$4\,hour period (see
@@
 {\it Viewing Orientation}---We fitted the rotational broadening of the
-K~I (7700\,\AA) resonance line using the broadening kernel suggested by
+K~I (7700\,\AA) resonance line using the kernel suggested by
 \cite{Gray2008}; taking the mean and standard deviation of the resulting
@@
     Spectral energy distribution of broadband photometric magnitudes
+    (filled markers)
     plotted over the best-fit BT-Settl stellar atmosphere model
-    \cite{Allard2012}.  This plot was made from an adaptation of \texttt{astroARIADNE}
-    \cite{Vines2022}.  The photometry extends from the Gaia DR3 blue
-    passband to WISE W3;  the W4 passband (22 $\mu$m) did not yield
-    a confident detection.  This fit yields the star's temperature and
-    size.  The lack of excess infrared flux relative to the photospheric
-    model sets an upper limit on emission from circumstellar dust.
+    \cite{Allard2012} and the associated photometric predictions
+    (empty markers).  This plot was made from an adaptation of
+    \texttt{astroARIADNE} \cite{Vines2022}.  The photometry extends
+    from the Gaia DR3 blue passband to WISE W3;  the W4 passband (22
+    $\mu$m) did not yield a confident detection.  This fit yields the
+    star's temperature and size.  The lack of excess infrared flux
+    relative to the photospheric model sets an upper limit on emission
+    from circumstellar dust.
     }
@@
 
-{\it Effective temperature, radius, mass, and spectral type}---We adopted
+{\it Effective temperature, radius, mass, and spectral classification}---We adopted
 the star's effective temperature and radius measured using the spectral
@@
 temperature found from the SED fitting \cite{Pecaut2013}.
+We measured the equivalent width of the H$\alpha$ line by fitting a
+range of models to the time-averaged line profile shown in
+Figure~\ref{fig:spec}, selecting the model that minimized the Bayesian
+information criterion (a sum of two Gaussians), and numerically
+integrating it.
+Our quoted result, EW$_{{\rm H}\alpha}$=7.2$\pm$0.2\,\AA, comes from
+numerically integrating within $|\Delta v/v_{\rm eq}|<1$; 
+integrating the entire line profile (including the broad wings) would yield
+EW$_{{\rm H}\alpha}$=10.2$\pm$0.3\,\AA
+Either value would classify the star as a ``weak-lined'' T Tauri \cite{Briceno2019}.
 
@@
 Gaia photometry, it suggests that the Pleiades may be a better
-comparison population than IC~2602.  Broadly, we take the star's
+comparison population than IC~2602.  We take the star's
 location in the color--absolute magnitude diagram to suggest age bounds
@@
   on the main sequence are $\approx$1.5\,magnitudes
-  fainter.  The star's location in this diagram broadly suggests an
+  fainter.  The star's location in this diagram suggests an
   age of 30-150\,Myr.  }
@@
   \caption{An upper limit on photospheric lithium for TIC~141146667
-  (green triangle) yields a lower limit on the star's age of
+  (green triangle) yields a lower bound on the star's age of
   $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
@@
   rays have been removed.
-  The horizontal axis shows the relative velocity centered on each
+  The horizontal axis shows the velocity relative to each
   line's rest wavelength, normalized by the stellar equatorial
@@
 magnetic field strength can all be estimated using the available data.
-We caution however that the following estimates are coarse: detailed
+We caution that the following estimates are simple order of magnitude
+calculations: detailed
 considerations of radiative transfer and detailed balance are a
@@
 unit time.
-For hydrogen with temperatures between 1,000 and 10,000\,K with
-densities $n_{\rm H}$$\sim$10$^{10}$\,cm$^{-3}$,
+For hydrogen with 
+densities $n_{\rm H}$$\sim$10$^{10}$\,cm$^{-3}$ and 
+temperatures between 1,000-10,000\,K,
 $\alpha^{\rm eff}_{\rm H\alpha}$ is typically on the order of $10^{-12}$ to
@@
 \end{equation}
-Taking nominal parameters of $r = 0.1 R_\star$, $x=1/2$, and
-$\alpha^{\rm eff}_{\rm H\alpha}$=$10^{-13}$\,cm$^3$\,s$^{-1}$,
-we find $n_{\rm H}\approx 5\times10^{11}$\,cm$^{-3}$.
-Assuming a uniform density clump, this yields a total gas mass $M_{\rm gas}\approx
-8\times10^{16}$\,g.
+Nominal parameters of $r = 0.1 R_\star$, $x=1/2$, and
+$\alpha^{\rm eff}_{\rm H\alpha}$=$10^{-13}$\,cm$^3$\,s$^{-1}$ suggest
+$n_{\rm H}\approx 5\times10^{11}$\,cm$^{-3}$.
+We have assumed a uniform density clump, and so this yields a total
+gas mass $M_{\rm gas}\approx 8\times10^{16}$\,g.
 
@@
 stars have been measured to span hundreds to thousands of Gauss
-\cite{Kochukhov2021}, this bound is easily met.
+\cite{Donati2009,Kochukhov2021,Reiners2022}, this bound is easily met.
 
@@
 
-The material's exact composition -- either pure plasma, or else a
-dusty plasma -- is not known.  In particular, the idea of dust being
+The material's composition -- either pure plasma, or a
+dusty plasma -- is not known.  The idea of dust being
 present seems plausible given observations of chromatic transits in
-analogous objects \cite{Tanimoto2020,Gunther2022,Koen2023}.  This
+analogous objects \cite{Tanimoto2020,Gunther2022,Koen2023}.  However, this
 scenario is highly constrained.  An upper limit on the amount of hot
@@
 \cite{Zhan2019} for discussion regarding dust sublimation).  We then
-treat emission from the dust and the star as Planck functions, and
+treat emission from the dust and star as Planck functions, and
 require $L_{\rm d} < f L_\star$, where the factor $f$ is set by
-photometric precision of WISE and $L_{\rm d}$ is the bolometric dust
+the photometric precision of WISE and $L_{\rm d}$ is the bolometric dust
 luminosity.  Given the reported uncertainties, we numerically find
@@
 R_\star)^2$, for $A_{\rm d}$ the total emitting surface area of the
-dust, and $Q_{\rm em}$ is an emission efficiency parameter.
+dust, and $Q_{\rm em}$ an emission efficiency parameter.
 Converting this constraint to a dust mass requires an assumption
@@
 d}$=3\,g\,cm$^{-3}$ typical for silicate grains, a fixed grain size
-$a$=1\,$\mu$m \cite{Tanimoto2020,Gunther2022,Koen2023}, and no
+$a$=1\,$\mu$m, and no
 self-absorption.  This enables the assumption that $A_{\rm d} = N \pi
@@
 \cite{Croll2014} in their Figure 13.  \cite{Sanderson2023} calculated
-the relevant cloud mass scaling assuming a spherical dust clump of
-size $r$, and they estimated
+the relevant cloud mass for this problem assuming a spherical dust clump of
+size $r$, and they found
 \begin{equation}
@@
 
-Three relevant objects for comparison to these limits include solar
+Three relevant objects for comparison to these limits are solar
 prominences, planetesimals, and comets.  Prominences of the Sun
-typically have gas masses of order $10^{14}$\,g-$10^{16}$\,g
+have gas masses of order $10^{14}$\,g-$10^{16}$\,g
 \cite{VialEngvold2015}.  A planetesimal of mass $\approx$10$^{15}$\,g
@@
 
-Broadly, our calculations suggest that if dust is responsible for the
+These calculations suggest that if dust is responsible for the
 broadband variability of CPVs, it would need to be concentrated in
@@
 $M_{\rm gas}$$\approx$8$\times$10$^{16}$\,g from
-Section~\ref{subsec:gas}, this range spans mass ratio ranges $M_{\rm
-gas}/M_{\rm dust}$ of 100 to 1.  More careful measurements of this
+Section~\ref{subsec:gas}, the allowed dust masses imply $M_{\rm
+gas}/M_{\rm dust}$ ranges of 1-100.  More careful measurements of this
 ratio---in particular enabled by inferring the dust mass through high
-precision infrared spectrophotometry---could provide a pathway for
+precision infrared spectrophotometry---could provide a path for
 distinguishing the scenario of a stellar outflow from an 
-accumulation of extrinsically-sourced material.
+accumulation of externally-sourced material.
 
@@
     $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & \cite{Bouma2024} SED fit \\
-    $P_{\rm rot}$ (hours) & $3.930\pm 0.001$ & TESS \\ 
+    $P_{\rm rot}$ (hours) & 3.930 $\pm$ 0.001 & TESS \\ 
     $v_{\rm eq}$ (\kms)  &  130$\pm$4  & Derived \\
-    $v_{\rm eq} \sin i_\star$(km s$^{-1}$) & $138 \pm 8$ & HIRES \\
+    $v_{\rm eq} \sin i_\star$ (\kms) & 138 $\pm$ 8 & HIRES \\
     $i_\star$($^\circ$) & $>$63 & Derived \\

### 2025-03-20 drivers/analyze_mean_halpha.py
add mean halpha analysis

@@ -1,0 +1,375 @@
+"""
+Take the mean Halpha line, run a model comparison analysis over gaussian,
+lorentzian, voigt, double gaussian, double lorentzian.  Calc red chi2, delta
+BIC, and best-fit parameters.
+
+Finally, calculate and report an equivalent width.
+
+(This entire thing was Generated by ChatGPT o3-mini-high on March 20 2025.)
+"""
+from os.path import join
+import os
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+from scipy.optimize import curve_fit
+from cdips.utils.lcutils import p2p_rms
+
+
+def load() -> tuple:
+    """Load spectrum data from a pickle file and estimate flux error.
+
+    Args:
+        None.
+
+    Returns:
+        tuple: Relative velocity array (dv), normalized flux (flx),
+            and estimated flux uncertainty (flx_err).
+
+    Generated by ChatGPT o3-mini-high on March 20 2025.
+    """
+    datadir = (
+        '/Users/luke/Dropbox/proj/cpv/results/movie_sixpanel_specriver/'
+        'TIC_141146667_science_wob'
+    )
+    pklpath = join(datadir, '141146667_specriver_cache.pkl')
+
+    with open(pklpath, 'rb') as f:
+        d = pickle.load(f)
+
+    dv = d['xvals'][0]
+    flx = d['smooth_mean_flux']
+    sel = np.abs(dv) > 3
+    flx_err = p2p_rms(flx[sel]) * 50
+    return dv, flx, flx_err
+
+
+def gauss_model(x: np.ndarray, amp: float, center: float, sigma: float,
+                offset: float) -> np.ndarray:
+    """Gaussian model for an emission line.
+
+    Args:
+        x (np.ndarray): Array of velocities.
+        amp (float): Amplitude of the Gaussian.
+        center (float): Center position of the Gaussian.
+        sigma (float): Gaussian width (standard deviation).
+        offset (float): Baseline offset.
+
+    Returns:
+        np.ndarray: Gaussian function evaluated at x.
+
+    Generated by ChatGPT o3-mini-high on March 20 2025.
+    """
+    return offset + amp * np.exp(-((x - center) ** 2) / (2 * sigma ** 2))
+
+
+def lorentz_model(x: np.ndarray, amp: float, center: float, gamma: float,
+                  offset: float) -> np.ndarray:
+    """Lorentzian model for an emission line.
+
+    Args:
[…]

### 2025-03-21 paper/ms.tex
update ms

@@
 new observations, and new theory.  From the theoretical perspective,
-there is an urgent need for rigid-field (magneto)-hydrodynamic modeling
-to go beyond previous work \cite{Townsend2005,Townsend2008} and to
-explore the effects of non-dipolar field contributions.  In particular,
-dynamo simulations of fully-convective M dwarfs have suggested that
-global-scale mean fields might be confined to a single hemisphere
-\cite{Brown2020}; such fields could yield accumulation surfaces quite
-different from those that have previously been explored
-\cite{Townsend2008}.  Observationally, spectropolarimetry has the
+there is an urgent need for rigid-field magneto-hydrodynamic modeling to
+go beyond previous work \cite{Townsend2005,Townsend2008,Krticka2022} and
+to explore what field topologies might explain the observed light curve
+morphologies \cite{Bouma2024}.  In particular, dynamo simulations of
+fully-convective M dwarfs have suggested that global-scale mean fields
+might be confined to a single hemisphere \cite{Brown2020}; such fields
+could yield accumulation surfaces quite different from those that have
+previously been explored.  Observationally, spectropolarimetry has the
 potential to assess both the field strength and topology.  An
@@
 short-lived and highly polarized.  In particular, detecting radio
-emission produced by an electron cyclotron maser instability
-(e.g. \cite{Callingham2021}) would provide a measurement of the field
-strength at the site of the emitting region, further clarifying the
-magnetic field's structure.
+emission produced by an electron cyclotron maser instability (e.g.
+\cite{Callingham2021}) would provide a measurement of the field strength
+at the site of the emitting region, further clarifying the magnetic
+field's structure.
 
@@
 Figure~\ref{fig:spec}, selecting the model that minimized the Bayesian
-information criterion (a sum of two Gaussians), and numerically
-integrating it.
+information criterion (we found a sum of two Gaussians to be preferred), and numerically
+integrating this best fit model.
 Our quoted result, EW$_{{\rm H}\alpha}$=7.2$\pm$0.2\,\AA, comes from
 numerically integrating within $|\Delta v/v_{\rm eq}|<1$; 
-integrating the entire line profile (including the broad wings) would yield
+integrating over the entire line profile (including the broad wings) would yield
 EW$_{{\rm H}\alpha}$=10.2$\pm$0.3\,\AA
-Either value would classify the star as a ``weak-lined'' T Tauri \cite{Briceno2019}.
+Either value would classify the star as a weak-lined T Tauri \cite{Briceno2019}.
 
@@
 $\alpha^{\rm eff}_{\rm H\alpha}$ is typically on the order of $10^{-12}$ to
-$10^{-13}$\,cm$^3$\,s$^{-1}$ \cite{Hummer1987}.
+$10^{-13}$\,cm$^3$\,s$^{-1}$ \cite{Hummer1987,Draine2011}.
 Neglecting the effects of atoms other than hydrogen, we can assume

### 2025-03-21 drivers/plot_lineevolnpanel.py
plot tweak

@@ -263,8 +263,11 @@ def plot_lineevolnpanel(outdir, starid=None, jstr=None, remove_cosmics=0):
     cax = fig.add_axes([0.92, 0.2, 0.05, 0.02])  # [left, bottom, width, height]
     cb = fig.colorbar(_lc, cax=cax, orientation="horizontal")
 
-    cb.ax.tick_params(labelsize='x-small', pad=0.7)
-    cb.ax.set_title('Phase $\phi$', fontsize='x-small', pad=0.4)
+    #cb.ax.tick_params(labelsize='x-small', pad=1.2)
+    #cb.ax.set_title('Phase $\phi$', fontsize='x-small', pad=0.6)
+
+    cb.ax.tick_params(labelsize='x-small', pad=1.5)
+    cb.ax.set_title('Phase $\phi$', fontsize='x-small', pad=2)
 
     #cb.ax.set_xticks([0,2,4])
     cb.ax.tick_params(size=0, which='both') # remove the ticks

### 2025-03-21 paper/ms.tex
update

@@
   shows the spectral evolution over five hours.
-  {\bf Panel a:} Average TESS light curve from 5 February 2024 to 26
+  {\bf a,} Average TESS light curve from 5 February 2024 to 26
   February 2024 (UT) folded on the \periodhr\ hour period.  Black
   points are phase-averaged; gray are the raw data.
-  {\bf Panel b:} Keck/HIRES H$\alpha$ spectra acquired on 17
+  {\bf b,} Keck/HIRES H$\alpha$ spectra acquired on 17
   February 2024.  The continuum is set to unity, and the darkest color
@@
   warped plasma torus.
-  {\bf Panel c:} Individual epochs of Panel b, visible in the
+  {\bf c,} Individual epochs of Panel b, visible in the
   online movie.  The dotted line shows the time-averaged spectrum,
   $f_{\langle t \rangle}$.
-  {\bf Panel d:} As in Panel a, but overplotting the
+  {\bf d,} As in Panel a, but overplotting the
   median-normalized H$\alpha$ light curve at $|v/v_{\rm eq}|<1$.
-  {\bf Panel e:} As in Panel b, after subtracting the time-averaged
+  {\bf e,} As in Panel b, after subtracting the time-averaged
   spectrum.  The line core shows H$\alpha$ excesses and decrements
@@
   is set to match the dynamic range of the data.
-  {\bf Panel f:} Individual epochs of Panel e, visible in the online
+  {\bf f,} Individual epochs of Panel e, visible in the online
   movie.}
@@
 spectra of a CPV, and they show that corotating circumstellar plasma clumps 
-are present in at least one such star.
+are present around at least one such star.
 This
@@
   \caption{Photometric evolution of TIC 141146667 near the Keck/HIRES observation (green bar). 
-  {\bf Panel a}: TESS simple aperture photometry. 
+  {\bf a,} TESS simple aperture photometry. 
   The main data gaps were caused by scattered light from the Earth
@@
   sampling.
-  {\bf Panels b,c}: Folded light curve before and after spectroscopy.
+  {\bf b-c,} Folded light curve before and after spectroscopy.
   Raw two minute data are in gray; black phase-averages to 100 points
@@
 For hydrogen with 
-densities $n_{\rm H}$$\sim$10$^{10}$\,cm$^{-3}$ and 
+%densities $n_{\rm H}$$\sim$10$^{10}$\,cm$^{-3}$ and 
 temperatures between 1,000-10,000\,K,
@@
 
-\subsection{Upper and Low Bounds on Dust}\phantom{+}
+\subsection{Upper and Lower Bounds on Dust}\phantom{+}
 \label{subsec:dust}

### 2025-03-21 paper/ms.tex
update

@@
 that of the star.
-Assuming an emitting sphere of radius $r$, we can write
-\begin{equation}
-  n_H = \frac{1}{x}
+Assuming the emitting volume is a homogeneous sphere of radius $r$, we can write
+\begin{align}
+  n_{\rm H} &= 
+  %\frac{1}{x}
+  %\left(
+  %  \frac{L_{\rm H\alpha}}{ \alpha^{\rm eff}_{\rm H\alpha} h \nu_{\rm H\alpha} V }
+  %\right)^{1/2},
+  %\\
+  %n_{\rm H} &=
+  5 \cdot 10^{11}\,{\rm cm}^{-3}
   \left(
-    \frac{L_{\rm H\alpha}}{ \alpha^{\rm eff}_{\rm H\alpha}(T) h \nu_{\rm H\alpha} V }
-  \right)^{1/2}.
-\end{equation}
-Nominal parameters of $r = 0.1 R_\star$, $x=1/2$, and
-$\alpha^{\rm eff}_{\rm H\alpha}$=$10^{-13}$\,cm$^3$\,s$^{-1}$ suggest
-$n_{\rm H}\approx 5\times10^{11}$\,cm$^{-3}$.
-We have assumed a uniform density clump, and so this yields a total
-gas mass $M_{\rm gas}\approx 8\times10^{16}$\,g.
+    \frac{0.5}{x}
+  \right)
+  \left( 
+    \frac{ L_{\rm H\alpha} }{ 10^{27}\,{\rm erg\,s^{-1}} }
+    \frac{ 10^{-13}\,{\rm cm^{3}\,s^{-1}} }{ \alpha^{\rm eff}_{\rm H\alpha} }
+  \right)^{1/2}
+  \left(
+    \frac{ 0.04\,R_\odot }{ r }
+  \right)^{3/2}.
+\end{align}
+Given that we have assumed a uniform density clump, this suggests a total
+gas mass at the stated nominal parameters of $M_{\rm gas}\approx 8\times10^{16}$\,g.
 

### 2025-03-24 drivers/plot_lineevolnpanel.py
update plot

@@ -130,7 +130,7 @@ def plot_lineevolnpanel(outdir, starid=None, jstr=None, remove_cosmics=0):
     rowkeys = [x for x in 'abcdef']
 
     f = 0.7
-    fig = plt.figure(figsize=(f*6,f*3.2))
+    fig = plt.figure(figsize=(f*6,f*4))
     axd = fig.subplot_mosaic(
         """
         abc

### 2025-03-24 paper/ms.tex
update

@@
 
-\newcommand{\starname}{TIC 141146667}
-
 \newcommand{\farcm}{\mbox{\ensuremath{.\mkern-4mu^\prime}}}%    % fractional arcminute symbol: 0.'0
@@
 \newcommand{\carnegie}{Observatories of the Carnegie Institution for Science, Pasadena, CA 91101, USA}
+\newcommand{\caltech}{Department of Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
 %%%%%%%%%%%%%%%%
@@
 \item \carnegie
-\item Carnegie Fellow
+\item \caltech
+\item Carnegie Fellow; 51 Pegasi b Fellow
 \end{affiliations}
@@
 
-In this study, we present the first spectroscopic detection of corotating clumps of
-cool plasma around a CPV.  We identified TIC~141146667 in previous
-work \cite{Bouma2024} by searching the TESS two-minute data
-\cite{Ricker2015} for stars showing highly structured, periodic light
-curves.  We selected the star for spectroscopy because its
-brightness and rotation rate enable efficiently mapping out line
-profile variability.  We observed it for five hours on 17~February~2024
-(UT) using the High Resolution Echelle Spectrometer (HIRES
-\cite{vogt_hires_1994}) on the Keck I 10m telescope.  TESS observed
-the star over a four week interval from 30~January~2024 to
+In this study, we present the first spectroscopic detection of
+corotating clumps of cool plasma around a CPV.  We identified
+TIC~141146667 in previous work \cite{Bouma2024} by searching the TESS
+two-minute data \cite{Ricker2015} for stars showing highly structured,
+periodic light curves.  We selected the star for spectroscopy because
+its brightness and rotation rate enable efficiently mapping out line
+profile variability.  We observed it for five hours on
+17~February~2024 (UT) using the High Resolution Echelle Spectrometer
+(HIRES \cite{vogt_hires_1994}) on the Keck I 10m telescope.  TESS
+observed the star over a four week interval from 30~January~2024 to
 26~February~2024 with a duty cycle of 77\%.  During the HIRES
@@
 were acquired.  Extended Data Figure~\ref{fig:fulllc} shows the
-detailed photometric behavior of the star near the
-epoch of observation; the general photometric morphology is similar
-before and after the data gap.
+detailed photometric behavior of the star near the epoch of
+observation; the general photometric morphology is similar before and
+after the data gap.
 
@@
   {\bf a,} Average TESS light curve from 5 February 2024 to 26
-  February 2024 (UT) folded on the \periodhr\ hour period.  Black
+  February 2024 folded on the \periodhr\ hour period.  Black
   points are phase-averaged; gray are the raw data.
@@
   The asymmetric color stretch
-  is set to match the dynamic range of the data.
+  is set to mirror the dynamic range of the data.
   {\bf f,} Individual epochs of Panel e, visible in the online
@@
 60\% excess over the continuum at the beginning of the observation
-sequence to a 10\% excess by its end.  The sinusoidal period for all
+sequence to a 10\% excess by its end.  The apparent period for all
 of these emission components is consistent with the photometric
@@
 These sinusoidal emission features require circumstellar clumps of
-partially-ionized hydrogen to corotate with the star.  
-Based on the period, this material's motion is not Keplerian; it can
-only be explained by plasma being dragged along with the rotating
-stellar magnetic field. 
-The velocity semi-amplitude of the sinusoids gives the distance
-of the clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
-closer clump, and 3.9\,$R_\star$ for the other.   These clumps transit
-in front of the star when passing from negative to positive velocity.
-This implies that the spectroscopic transit of the 2.1-2.7\,$R_\star$
-clump occurs simultaneously with the sharp photometric spike visible
-in the TESS data.
+partially-ionized hydrogen to corotate with the star.  Based on the
+period, this material's motion is not Keplerian; it can only be
+explained by plasma being dragged along with the rotating stellar
+magnetic field.  The velocity semi-amplitude of the sinusoids gives
+the distance of the clumps from the stellar surface:
+2.1-2.7\,$R_\star$ for the closer clump, and 3.9\,$R_\star$ for the
+other.   These clumps transit in front of the star when passing from
+negative to positive velocity.  This implies that the spectroscopic
+transit of the 2.1-2.7\,$R_\star$ clump occurs simultaneously with the
+sharp photometric spike visible in the TESS data.
 
 % * keck/hires: behavior at v/veq<1
-Within the stellar H$\alpha$ line core, at $|\Delta v /
-v_{\rm eq}|<1$, we observe a superposition of emission from the star's
-chromosphere,
-modulated by any occulting material capable of absorbing or
-emitting H$\alpha$ photons.  In Figure~\ref{fig:spec}e, the data from
-$\phi$=0.4-1.2 have a simple interpretation: from $\phi$=0.4-0.9, a hot
-(emitting) region first gradually crosses the stellar line profile, followed from
-$\phi$=0.7-1.2 by the transit of a cool (absorbing) region. Phases $\phi$$<$0.4
-show a mix of similar events, though the time sampling is
-sufficiently coarse that the interpretation is less clear.  A final
-exercise to quantify the behavior in the line core is shown in
-Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes the
-summed flux at $|\Delta v / v_{\rm eq}|<1$.  This panel shows that
-changes in the line core flux are correlated with the
-broadband variability over most of the light curve, except at
-$\phi$$\approx$0.5, during the transit of the 3.9\,$R_\star$ clump and
-the occultation of the lower-velocity clump.
+The stellar H$\alpha$ line core, at $|\Delta v / v_{\rm
+eq}|<1$, captures a superposition of emission from the star's
+chromosphere, modulated by any occulting material capable of absorbing
+or emitting H$\alpha$ photons.  In Figure~\ref{fig:spec}e, the data
+from $\phi$=0.4-1.2 have a simple interpretation: from $\phi$=0.4-0.9,
+a hot (emitting) region first gradually crosses the stellar line
+profile, followed from $\phi$=0.7-1.2 by the transit of a cool
+(absorbing) region. Phases $\phi$$<$0.4 show a mix of similar events,
+though the time sampling is sufficiently coarse that the
+interpretation is less clear.  A final exercise to quantify the
+behavior in the line core is shown in Figure~\ref{fig:spec}d, where
+$f_{\rm H\alpha\ core}$ denotes the summed flux at $|\Delta v / v_{\rm
+eq}|<1$.  This panel shows that changes in the line core flux are
+correlated with the broadband variability over most of the light
+curve, except at $\phi$$\approx$0.5, during the transit of the
+3.9\,$R_\star$ clump and the occultation of the lower-velocity clump.
 
@@
 of masses have been known to exhibit both sinusoidal emission features
-\cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} as well as
+\cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} and
 transient absorption features
@@
 that can last days to weeks \cite{VialEngvold2015}.  These
-condensations fall back to the solar surface because gravity is
+condensations fall back to the Sun's surface because gravity is
 stronger than any magnetic tension or centrifugal force capable of
@@
 
-Our Keck/HIRES observations are the first reported time-series
-spectra of a CPV, and they show that corotating circumstellar plasma clumps 
-are present around at least one such star.
-This
-observation rules out a ``starspot-only'' origin scenario for CPVs,
-\cite{Koen2021} because such scenarios have no means of explaining
-spectroscopic emission beyond the stellar disk.  Similarly, scenarios in
-which the circumstellar material is made only of dust are also ruled
-out.  While dust may be present, to explain the H$\alpha$ emission the
-clumps must include plasma with a significant population of hydrogen
-atoms in the $n$=3 excited state.  
-More quantitatively, the observed H$\alpha$ luminosity suggests
-characteristic densities and masses for the gaseous component of these
-clumps of $n_{\rm H} \sim 10^{11}$-$10^{12}$\,cm$^{-3}$ and $M_{\rm
-gas} \sim 10^{17}$\,g (see Section~\ref{subsec:gas}).
-Dust, if present, is independently constrained to have a total
-mass $10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm g}$ (see
-Section~\ref{subsec:dust}).
-This circumstellar material could plausibly originate from
-three sites: the star, an old and undetected disk, or outgassing rocky
-bodies.  This latter possibility would render CPVs as extrasolar analogs
-of the Jupiter-Io plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
+Our Keck/HIRES observations are the first reported time-series spectra
+of a CPV, and they show that corotating circumstellar plasma clumps
+are present around at least one such star.  This observation rules out
+a ``starspot-only'' origin scenario for CPVs, \cite{Koen2021} because
+such scenarios have no means of explaining spectroscopic emission
+beyond the stellar disk.  Similarly, scenarios in which the
+circumstellar material is made only of dust are also ruled out.  While
+dust may be present, to explain the H$\alpha$ emission the clumps must
+include plasma with a significant population of hydrogen atoms in the
+$n$=3 excited state, for $n$ the principal quantum number.  More quantitatively, the observed H$\alpha$
+luminosity suggests characteristic densities and masses for the
+gaseous component of these clumps of $n_{\rm H} \sim
+10^{11}$-$10^{12}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g (see
+Section~\ref{subsec:gas}).  Dust, if present, is independently
+constrained to have a total mass $10^{15}\,{\rm g} < M_{\rm dust} <
+10^{17}\,{\rm g}$ (see Section~\ref{subsec:dust}).  This circumstellar
+material could originate either from the star or from an external
+source.  Plausible external sources include an old and undetected
+disk, comets, or a close-in exoplanet.
+This latter possibility would render CPVs as extrasolar analogs of the
+Jupiter-Io plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
 
@@
 accumulate into warped plasma tori \cite{Townsend2005,Townsend2008}.
-These tori tend to have dense antipodal accumulations of plasma sculpted
-by tilted-dipole magnetic fields, and the transits of these clumps are
-thought to produce the observed broadband photometric variability
-through bound-free scattering \cite{Townsend2005} and Thomson scattering
-\cite{Berry2022}.  For $\sigma$~Ori~E and almost all of its analogs, the
-result is light curves that appear ``simple'', resembling those of
-eclipsing binaries, and time-dynamic H$\alpha$ spectra similar to those
-in Figure~\ref{fig:spec} \cite{Townsend2005,Townsend2008}.  The two known exceptions,
-HD~37776 and HD~64740, show complex light curves resembling CPVs
+These tori tend to have dense antipodal accumulations of plasma
+sculpted by tilted-dipole magnetic fields, and the transits of these
+clumps produce the observed broadband photometric
+variability through bound-free scattering \cite{Townsend2005} and
+Thomson scattering \cite{Berry2022}.  For $\sigma$~Ori~E and almost
+all of its analogs, the result is light curves that appear ``simple'',
+resembling those of eclipsing binaries, and time-dynamic H$\alpha$
+spectra similar to those in Figure~\ref{fig:spec}
+\cite{Townsend2005,Townsend2008}.  The two known exceptions, HD~37776
+and HD~64740, show complex light curves resembling CPVs
 \cite{Mikulasek2020,Bouma2024} and have spectropolarimetric magnetic
@@
 
-Pressing issues for future work include determining the composition and
-origin of the circumstellar material, understanding the exact role of
-the stellar magnetic field, and exploring the implied space weather
+Pressing issues for future work include determining the composition
+and origin of the circumstellar material, understanding the exact role
+of the stellar magnetic field, and exploring the implied space weather
 experienced by the close-in rocky exoplanets that, statistically
@@
 
-The material's composition -- either pure plasma, or else a dusty plasma
--- can be clarified by time-series optical and infrared
-spectrophotometry.  While observations of CPVs in the optical have
-previously suggested chromaticity consistent with dust
-\cite{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such as
-electron scattering in a plasma transiting over starspots might also
-produce chromatic features \cite{Rackham2018}.  The composition and size
-distribution of any dust that is present could be determined
+The material's composition -- either pure plasma, or else a dusty
+plasma -- can be clarified by time-series optical and infrared
+spectrophotometry.  While observations of CPVs in the optical may
+suggest chromaticity consistent with dust
+\cite{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such
+as electron scattering in a plasma transiting over starspots might
+also produce chromatic features \cite{Rackham2018}.  The composition
+and size distribution of any dust that is present could be determined
 by measuring the extinction curve for one or more CPVs from
-1-10\,$\mu$m.  Composition and size distributions similar to debris from
-rocky bodies seen around white dwarfs \cite{Reach2009} would indicate a
-rocky-body origin.  Compositions and sizes similar to the interstellar
-medium could be indicative of condensed dust in an M dwarf wind,
-similar to that formed in the environments of more evolved stars
-\cite{Marigo2008}.
-
-The role of the star's magnetic field could be better understood through
-new observations, and new theory.  From the theoretical perspective,
-there is an urgent need for rigid-field magneto-hydrodynamic modeling to
-go beyond previous work \cite{Townsend2005,Townsend2008,Krticka2022} and
-to explore what field topologies might explain the observed light curve
-morphologies \cite{Bouma2024}.  In particular, dynamo simulations of
+1-10\,$\mu$m.  Composition and size distributions similar to debris
+from rocky bodies seen around white dwarfs \cite{Reach2009} would
+indicate a rocky-body origin.  Compositions and sizes similar to the
+interstellar medium could be indicative of condensed dust in an M
+dwarf wind, similar to that formed in the environments of more evolved
+stars \cite{Marigo2008}.
+
+The role of the star's magnetic field could be better understood
+through new observations, and new theory.  From the theoretical
+perspective, there is an urgent need for rigid-field
+magneto-hydrodynamic modeling to go beyond previous work
+\cite{Townsend2005,Townsend2008,Krticka2022} and to explore what field
+topologies might explain the observed light curve morphologies
+\cite{Bouma2024}.  In particular, dynamo simulations of
 fully-convective M dwarfs have suggested that global-scale mean fields
 might be confined to a single hemisphere \cite{Brown2020}; such fields
-could yield accumulation surfaces quite different from those that have
+would yield accumulation surfaces quite different from those that have
 previously been explored.  Observationally, spectropolarimetry has the
@@
 emission produced by an electron cyclotron maser instability (e.g.
-\cite{Callingham2021}) would provide a measurement of the field strength
-at the site of the emitting region, further clarifying the magnetic
-field's structure.
+\cite{Callingham2021}) would provide a measurement of the field
+strength at the site of the emitting region, further clarifying the
+magnetic field's structure.
 
@@
 photometric features occur when clumps of circumstellar material
-transit the star.  The implied geometric correction suggests that
-an appreciable minority (10-30\%) of young M dwarfs -- the rapidly
+transit the star.  The implied geometric correction suggests that an
+appreciable minority (10-30\%) of young M dwarfs -- the rapidly
 rotating ones with centrifugal magnetospheres -- host similar
@@
   \includegraphics[width=0.99\textwidth]{figures/sf1.pdf}
-  \caption{Photometric evolution of TIC 141146667 near the Keck/HIRES observation (green bar). 
-  {\bf a,} TESS simple aperture photometry. 
-  The main data gaps were caused by scattered light from the Earth
-  (BTJD 3356-3358.5) and Moon (BTJD 3359.5-3360.5).
-  Raw two minute data are in gray; black time-averages to ten minute
-  sampling.
-  {\bf b-c,} Folded light curve before and after spectroscopy.
-  Raw two minute data are in gray; black phase-averages to 100 points
-  per cycle.
-  During BTJD 3352-3356, a state switch occurred near BTJD 3353,
-  in which the dip at $\phi$$\approx$0.8 disappeared.
-  While the large eclipse feature was present both before and after
-  the HIRES sequence, its photometric shape evolved during the data
-  gap.
+  \caption{Photometric evolution of TIC 141146667 near the Keck/HIRES
+  observation (green bar). 
+  {\bf a,} TESS simple aperture photometry.  The main data gaps were
+  caused by scattered light from the Earth (BTJD 3356-3358.5) and Moon
+  (BTJD 3359.5-3360.5).  Raw two minute data are in gray; black
+  time-averages to ten minute sampling.
+  {\bf b-c,} Folded light curve before and after spectroscopy.  Raw
+  two minute data are in gray; black phase-averages to 100 points per
+  cycle.  During BTJD 3352-3356, a state switch occurred near BTJD
+  3353, in which the dip at $\phi$$\approx$0.8 disappeared.  While the
+  large eclipse feature was present both before and after the HIRES
+  sequence, its photometric shape evolved during the data gap.
   }
@@
 
-{\it No Evidence For Binarity}---Any significant periodicity in the
+{\it No Evidence For Binarity}---Any periodicity in the
 radial velocity time-series is ruled out at the rotation period for
-semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This sets
-an upper limit on the mass of any putative companion at the four hour
-period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
+semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This
+sets an upper limit on the mass of any putative companion at the four
+hour period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
 companions at wider separations, the Gaia DR3 renormalized unit weight
@@
 astrometric model to the Gaia astrometry, is 1.23, within the usual
-range for apparently single sources.  There are no resolved sources in
+range for apparently single sources.  There are no resolved companions in
 the Gaia DR3 point source catalog.  Finally, we checked the TESS light
@@
 excess noise above the Gaia single-source astrometric model, and about
-40\% of CPVs show evidence for unresolved binary companions based on the
-presence of secondary photometric periods.  This agrees with analyses
-showing that multi-periodic low-mass stars are generally unresolved
-binaries \cite{Tokovinin2018}.  Overall, the CPV binary fraction seems
-consistent with that for field M dwarfs \cite{Winters2019}, pointing to
-a weak or non-existent connection between the CPV phenomenon and
-(wide) binarity.  For TIC~141146667 specifically, while we find no evidence for
-stellar multiplicity, our data are minimally constraining for the
-scenario of a low-luminosity companion ($F_1$/$F_2$$\lesssim$0.1) at
-with apparent separations below 0$\farcs$1.
+40\% of CPVs show evidence for unresolved binary companions based on
+the presence of secondary photometric periods.  This agrees with
+analyses showing that multi-periodic low-mass stars are generally
+unresolved binaries \cite{Tokovinin2018}.  Overall, the CPV binary
+fraction seems consistent with that for field M dwarfs
+\cite{Winters2019}, pointing to a weak or non-existent connection
+between the CPV phenomenon and (wide) binarity.  For TIC~141146667
+specifically, although we find no evidence for stellar multiplicity, our
+data are minimally constraining for the scenario of a low-luminosity
+companion ($F_1$/$F_2$$\lesssim$0.1) with apparent separation
+below 0$\farcs$1.
 
@@
     Spectral energy distribution of broadband photometric magnitudes
-    (filled markers)
-    plotted over the best-fit BT-Settl stellar atmosphere model
-    \cite{Allard2012} and the associated photometric predictions
-    (empty markers).  This plot was made from an adaptation of
-    \texttt{astroARIADNE} \cite{Vines2022}.  The photometry extends
-    from the Gaia DR3 blue passband to WISE W3;  the W4 passband (22
-    $\mu$m) did not yield a confident detection.  This fit yields the
-    star's temperature and size.  The lack of excess infrared flux
-    relative to the photospheric model sets an upper limit on emission
-    from circumstellar dust.
+    (filled markers) plotted over the best-fit BT-Settl stellar
+    atmosphere model \cite{Allard2012} and the associated photometric
+    predictions (empty markers).  This plot was made from an
+    adaptation of \texttt{astroARIADNE} \cite{Vines2022}.  The
+    photometry extends from the Gaia DR3 blue passband to WISE W3;
+    the W4 passband (22 $\mu$m) did not yield a confident detection.
+    This fit yields the star's temperature and size.  The lack of
+    excess infrared flux relative to the photospheric model sets an
+    upper limit on emission from circumstellar dust.
     }
@@
 
-{\it Effective temperature, radius, mass, and spectral classification}---We adopted
-the star's effective temperature and radius measured using the spectral
-energy distribution (SED) fitting procedure described by
-\cite{Bouma2024}.  To summarize, this approach used
-\texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
+{\it Effective temperature, radius, mass, and spectral
+classification}---We adopted the star's effective temperature and
+radius measured using the spectral energy distribution (SED) fitting
+procedure described by \cite{Bouma2024}.  To summarize, this approach
+used \texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
 atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
@@
 Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting
-best-fit SED is shown in Figure~\ref{fig:sed}.  This method has the most
-constraining power for the star's effective temperature (2972 $\pm$
-40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
-metallicity, and reddening are only weakly constrained.  We
+best-fit SED is shown in Figure~\ref{fig:sed}.  This method has the
+most constraining power for the star's effective temperature (2972
+$\pm$ 40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface
+gravity, metallicity, and reddening are only weakly constrained.  We
 determined the star's spectral type to be M5.5Ve by visually comparing
@@
 \cite{Bochanski2007}.   This result agrees with the effective
-temperature found from the SED fitting \cite{Pecaut2013}.
-We measured the equivalent width of the H$\alpha$ line by fitting a
-range of models to the time-averaged line profile shown in
+temperature found from the SED fitting \cite{Pecaut2013}.  We measured
+the equivalent width of the H$\alpha$ line by fitting a range of
+models to the time-averaged line profile shown in
 Figure~\ref{fig:spec}, selecting the model that minimized the Bayesian
-information criterion (we found a sum of two Gaussians to be preferred), and numerically
-integrating this best fit model.
-Our quoted result, EW$_{{\rm H}\alpha}$=7.2$\pm$0.2\,\AA, comes from
-numerically integrating within $|\Delta v/v_{\rm eq}|<1$; 
-integrating over the entire line profile (including the broad wings) would yield
-EW$_{{\rm H}\alpha}$=10.2$\pm$0.3\,\AA
-Either value would classify the star as a weak-lined T Tauri \cite{Briceno2019}.
+information criterion, and numerically integrating this best fit model.  
+We found a sum of two Gaussians to be the preferred model; our quoted
+result, EW$_{{\rm H}\alpha}$=7.2$\pm$0.2\,\AA, comes from numerically
+integrating within $|\Delta v/v_{\rm eq}|<1$.  Integrating over the
+entire line profile, including the broad wings, would yield EW$_{{\rm
+H}\alpha}$=10.2$\pm$0.3\,\AA. Either value would classify the star as
+a weak-lined T Tauri \cite{Briceno2019}.
 
@@
 temperature, radius, and age.  This exercise yielded a mass of
-$M_\star$=$0.20\pm0.01$\,$M_\odot$ assuming an age of 35\,Myr, or a mass
-of $0.25\pm0.01$\,$M_\odot$ assuming an age of 150\,Myr.  These masses
-imply Keplerian corotation radii $R_{\rm cr}/R_\star$=1.75$\pm$0.07 and
-$R_{\rm cr}/R_\star$=1.89$\pm$0.07, respectively; this size scale is
-relevant because it is theoretically expected to set the inner boundary
-at which corotating material might accumulate
-(e.g.~\cite{Townsend2005,Daley-Yates2024}).  Our final quoted $M_\star$
-and $R_{\rm cr}$ values adopt the average of these extremes and a
-quadrature sum of their statistical uncertainties; we caution however
-that a more precise age would be needed to resolve the systematic
-uncertainties in these parameters.
+$M_\star$=$0.20\pm0.01$\,$M_\odot$ assuming an age of 35\,Myr, or a
+mass of $0.25\pm0.01$\,$M_\odot$ assuming an age of 150\,Myr.  These
+masses imply Keplerian corotation radii $R_{\rm
+cr}/R_\star$=1.75$\pm$0.07 and $R_{\rm cr}/R_\star$=1.89$\pm$0.07,
+respectively; this size scale is relevant because it is theoretically
+expected to set the inner boundary at which corotating material might
+accumulate (e.g.~\cite{Townsend2005,Daley-Yates2024}).  Our final
+quoted $M_\star$ and $R_{\rm cr}$ values adopt the average of these
+extremes and a quadrature sum of their statistical uncertainties; we
+caution however that a more precise age would be needed to resolve the
+systematic uncertainties in these parameters.
 
@@
 TIC~141146667 is in the minority.  We calculated the probability of
-TIC~141146667 being part of any of the nearby known groups using
+TIC~141146667 being part of any nearby known group using
 BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  That particular model
-classifies it as a field star at $>$99.9\% confidence.  We also searched
-the local vicinity of TIC~141146667 for neighbors with similar projected
-on-sky velocities using \texttt{comove} \cite{Tofflemire2021}.  This
-yielded no strong candidates for co-moving stars with projected
-tangential velocities $\Delta v_{\rm T}$$<$5\,\kms\ that share its
-isochronal youth.
+classifies it as a field star at $>$99.9\% confidence.  We also
+searched the local vicinity of TIC~141146667 for neighbors with
+similar projected on-sky velocities using \texttt{comove}
+\cite{Tofflemire2021}.  This yielded no strong candidates for
+co-moving stars with projected tangential velocities $\Delta v_{\rm
+T}$$<$5\,\kms\ that share its isochronal youth.
 
@@
 all other known CPVs \cite{Stauffer2017,Stauffer2021,Bouma2024}.  The
-star's proximity ($d$=58\,pc) and its high galactic latitude
+star's proximity ($d$=58\,pc) and high galactic latitude
 ($b$=$+$53$^\circ$) yield negligible interstellar reddening along the
@@
 for over sixty years \cite{Hayashi1963,Bildsten1997,Burke2004}.
-\cite{Wood2023} provided an instructive recent overview: an abbreviated
+\cite{Wood2023} provided a recent overview: an abbreviated
 summary is that sufficiently cool and young M dwarfs show the 6707.8\,\AA\
@@
 for Sun-like stars, the continuum for M dwarfs is poorly defined due to
-their molecular absorption.  We attempted a lithium measurement by
+their molecular absorption.  We therefore attempted a lithium measurement by
 constructing a wavelength-binned and Doppler-corrected TIC~141146667
@@
 across the five hour dataset.  We then compared this average spectrum
-against the nearest matching template from \cite{Bochanski2007}.  The
+against the nearest matching M6 template from \cite{Bochanski2007}.  The
 data show a small depression near the expected lithium wavelength,
@@
 evaluated using a bootstrap resampling technique from the statistical
-uncertainties in the spectrum.  However the systematic uncertainties associated
-with the continuum normalization are larger, and likely comparable to
-the amplitude of the feature; we therefore treat the result of this
+uncertainties in the HIRES spectrum.  However, the systematic uncertainties associated
+with the continuum normalization are likely comparable to
+the amplitude of this feature; we therefore treat the result of this
 measurement as a $2\sigma$ upper limit: ${\rm EW}_{\rm Li}$$<$107\,m\AA.
@@
 TIC~141146667 are {\it i)} that it is a complex periodic variable, and
-{\it ii)} that it is 1.5 magnitudes brighter than main sequence stars
-of the same color, while showing no indicators for binarity.  The
-first item constitutes evidence for youth since all known CPVs are
-$\lesssim$200\,Myr \cite{Bouma2024}.  The reference sequences for the
-Pleiades (112\,Myr, \cite{Dahm2015}) show a few stars of equal
-luminosity and the same temperature, suggesting a photometric
-isochronal age upper limit $\lesssim$150\,Myr.  The weak lithium
-absorption suggests an age of at least 20\,Myr based on an empirical
-comparison using Gaia-ESO spectra, or at least 35\,Myr based on the
-\cite{Feiden2016} isochrones.  These considerations yield our adopted
-age range of 150\,Myr.
+{\it ii)} that it is 1.5 magnitudes brighter (four times more
+luminous) than main sequence stars of the same color, while showing no
+indicators for binarity.  The first item constitutes evidence for
+youth since all known CPVs are $\lesssim$200\,Myr \cite{Bouma2024}.
+The reference sequences for the Pleiades (112\,Myr, \cite{Dahm2015})
+show a few stars of equal luminosity and the same temperature,
+suggesting a photometric isochronal age upper limit
+$\lesssim$150\,Myr.  The weak lithium absorption suggests an age of at
+least 20\,Myr based on an empirical comparison using Gaia-ESO spectra,
+or at least 35\,Myr based on the \cite{Feiden2016} isochrones.  These
+considerations yield our adopted age range of 150\,Myr.
 
@@
   spectra from 17 February 2025.
-  The spectra have been smoothed with a Gaussian filter, and cosmic
-  rays have been removed.
+  We made this plot by applying a windowed outlier rejection to remove
+  cosmic rays and then smoothing each spectrum with a Gaussian filter.
   The horizontal axis shows the velocity relative to each
@@
 HIRES spectra, which cover 3650-7960\,\AA.  Higher order Balmer lines
-including H$\gamma$ and H$\delta$ (the $n=5\rightarrow2$ and
-$n=6\rightarrow2$ transitions respectively) do show some variability
+including H$\gamma$ and H$\delta$ ($n=5\rightarrow2$ and
+$n=6\rightarrow2$) do show some variability
 outside the line core.  However, this variability is not clearly
@@
 the relevant excited states, or due to the lower precision of the
-spectra in these bluer regions.  The Ca HK doublet for instance is
-also detectable in emission, however the continuum near it is not.
-Chromospheric emission lines in the magnesium triplet order are also
-detectable, but sufficiently blended to be rendered unusable.
-
-One notable feature is that H$\alpha$, H$\gamma$, H$\delta$, and He
-5876\,\AA\ all show a blue excess at $\phi$$\approx$0.2.  At the same
-epoch, only H$\alpha$ clearly shows a resolved red excess as well,
-although $H\gamma$ and H$\delta$ are broader at this time.  Given the
-sudden rise of this emission in $<$15\,minutes, and the association
-between He 5876\,\AA\ and stellar outflows at high excitation energy,
-this component of the spectra might be more easily associated with a
-flare than with a stable, periodic component.
+spectra in these bluer regions.  The Ca HK doublet is
+also detected in emission, however the continuum near it is not.
+Chromospheric emission from the magnesium triplet are also
+detected, but are sufficiently blended to be rendered unusable.
+
+A sudden blue excess appeared at $\phi$$\approx$0.2 in H$\alpha$,
+H$\gamma$, H$\delta$, and He 5876\,\AA.  At the same epoch, only
+H$\alpha$ clearly shows a resolved red excess as well, although
+H$\gamma$ and H$\delta$ do broaden at this time.  Given the sudden
+rise of this emission in $<$15\,minutes, and the association between
+He 5876\,\AA\ and stellar outflows at high excitation energy, this
+component of the spectra might be associated with a flare, rather
+than with a stable, periodic component.
 
@@
 hydrogen number density, plasma temperature, ionization fraction, and
-magnetic field strength can all be estimated using the available data.
+magnetic field strength can be estimated from the available data.
 We caution that the following estimates are simple order of magnitude
-calculations: detailed
-considerations of radiative transfer and detailed balance are a
-worthwhile topic for future work, but are beyond the scope of this
+calculations: detailed considerations of radiative transfer are a
+worthy topic for future work, but are beyond the scope of this
 article.
 
-Circumstellar H$\alpha$ emission might be sourced either from
+Circumstellar H$\alpha$ emission might be sourced either from resonant
 scattering of stellar H$\alpha$ photons, or from radiative
@@
 uncorrelated with any variability in the chromospheric line core.  The
-volume emissivity under case B recombination (in which Lyman-series
-photons are trapped by high optical depth, so that recombinations
-cascade through H$\alpha$ and other Balmer lines) can be written as
-\begin{equation}
-  j_{\rm H\alpha} = n_{\rm e} n_{\rm p} \alpha^{\rm eff}_{\rm H\alpha}(T) h \nu_{\rm H\alpha},
-\end{equation}
-where $n_{\rm e}$ and $n_{\rm p}$ are the electron and proton densities,
-and $\alpha^{\rm eff}_{\rm H\alpha}(T)$ is the effective recombination
-coefficient, i.e.\ the number of recombinations per unit volume, per
-unit time.
-For hydrogen with 
-%densities $n_{\rm H}$$\sim$10$^{10}$\,cm$^{-3}$ and 
-temperatures between 1,000-10,000\,K,
-$\alpha^{\rm eff}_{\rm H\alpha}$ is typically on the order of $10^{-12}$ to
-$10^{-13}$\,cm$^3$\,s$^{-1}$ \cite{Hummer1987,Draine2011}.
-Neglecting the effects of atoms other than hydrogen, we can assume
-an ionization fraction $x$, such that $n_{\rm e} = n_{\rm p} = x
-n_{\rm H}$, for $n_{\rm H}$ the hydrogen number density.  Let $L_{\rm
-H\alpha} = j_{\rm H\alpha} V$, for $V$ the volume of the emitting
-hydrogen.
-The luminosity of circumstellar hydrogen emission, $L_{\rm H\alpha}$,
-is an observable: our SED fitting routine yields
-$L_\star$$\approx$0.012\,$L_\odot$, which gives
-$L_{\rm H\alpha},\star$$\approx$1.0$\times$$10^{28}$erg\,s$^{-1}$, and
-the luminosity of the clump $L_{\rm H\alpha}$ is of order one tenth
-that of the star.
-Assuming the emitting volume is a homogeneous sphere of radius $r$, we can write
+volume emissivity under case B recombination can be written
+\begin{equation} j_{\rm H\alpha} = n_{\rm e} n_{\rm p} \alpha^{\rm
+eff}_{\rm H\alpha} h \nu_{\rm H\alpha}, \end{equation} where $n_{\rm
+e}$ and $n_{\rm p}$ are the electron and proton densities, and
+$\alpha^{\rm eff}_{\rm H\alpha}$ is the effective recombination
+coefficient, defined to include all recombination routes that produce
+an H$\alpha$ photon.  For hydrogen with temperatures between
+1,000-10,000\,K, $\alpha^{\rm eff}_{\rm H\alpha}$ is typically on the
+order of $10^{-12}$ to $10^{-13}$\,cm$^3$\,s$^{-1}$
+\cite{Hummer1987,Draine2011}.  Neglecting the effects of atoms other
+than hydrogen, we can assume an ionization fraction $x$, such that
+$n_{\rm e} = n_{\rm p} = x n_{\rm H}$, for $n_{\rm H}$ the hydrogen
+number density.  Let $L_{\rm H\alpha} = j_{\rm H\alpha} V$, for $V$
+the volume of the emitting hydrogen.  The luminosity of circumstellar
+hydrogen emission, $L_{\rm H\alpha}$, is an observable: our SED
+fitting routine yields $L_\star$$\approx$0.012\,$L_\odot$, which
+implies that the stellar H$\alpha$ line radiates at
+$\approx$1.0$\times$$10^{28}$erg\,s$^{-1}$.  The luminosity of the
+clumps $L_{\rm H\alpha}$ are of order one tenth that of the star.  If
+we approximate the emitting volume as a homogeneous sphere of radius
+$r$, we can write
 \begin{align}
@@
   \right)^{3/2}.
+  \label{eq:numdensity}
 \end{align}
-Given that we have assumed a uniform density clump, this suggests a total
-gas mass at the stated nominal parameters of $M_{\rm gas}\approx 8\times10^{16}$\,g.
+For a uniform density clump, this suggests a total gas mass of $M_{\rm
+gas}\approx 8\times10^{16}$\,g.
+We emphasize that Equation~\ref{eq:numdensity} in intended to provide
+only an order of magnitude estimate for the number density implied by
+the observed H$\alpha$ emission.  In detail, the effective
+recombination rate and the ionization fraction each vary with density
+and temperature; a more thorough estimate would iteratively solve the
+equations of detailed balance and radiative transfer
+(e.g.~\cite{CollierCameron1989} Figure~8), and potentially also
+consider departures from local thermodynamic equilibrium.
 
@@
 we do not know the plasma temperature, if it were significantly beyond
-1,000-10,000\,K, we would either full ionize the hydrogen, or not
-ionized enough of it.  We can therefore estimate
+1,000-10,000\,K, we would either fully ionize the hydrogen, or not
+ionize enough of it.  We can therefore estimate
 \begin{equation}
@@
   \frac{T}{5000\,{\rm K}}
-  \right).
+  \right)^{1/2}.
 \end{equation}
@@
 
-The material's composition -- either pure plasma, or a
-dusty plasma -- is not known.  The idea of dust being
-present seems plausible given observations of chromatic transits in
-analogous objects \cite{Tanimoto2020,Gunther2022,Koen2023}.  However, this
-scenario is highly constrained.  An upper limit on the amount of hot
-dust follows from the lack of an infrared excess.  A lower limit
-follows if one assumes that most of the broadband optical depth comes
-from dust absorption and scattering, rather than any radiative
-processes associated with the plasma.
+The material's composition -- either pure plasma, or a dusty plasma --
+is not known.  The idea of dust being present seems plausible given
+observations of chromatic transits in analogous objects
+\cite{Tanimoto2020,Gunther2022,Koen2023}.  However, this scenario is
+highly constrained.  An upper limit on the amount of hot dust follows
+from the lack of an infrared excess.  A lower limit follows if one
+assumes that most of the broadband optical depth comes from dust
+absorption and scattering, rather than any radiative processes
+associated with the plasma.
 
@@
 \cite{Zhan2019} for discussion regarding dust sublimation).  We then
-treat emission from the dust and star as Planck functions, and
-require $L_{\rm d} < f L_\star$, where the factor $f$ is set by
-the photometric precision of WISE and $L_{\rm d}$ is the bolometric dust
+treat emission from the dust and star as Planck functions, and require
+$L_{\rm d} < f L_\star$, where the factor $f$ is set by the
+photometric precision of WISE and $L_{\rm d}$ is the bolometric dust
 luminosity.  Given the reported uncertainties, we numerically find
@@
 R_\star)^2$, for $A_{\rm d}$ the total emitting surface area of the
-dust, and $Q_{\rm em}$ an emission efficiency parameter.
-Converting this constraint to a dust mass requires an assumption
-regarding the grain properties.  We assume a grain density $\rho_{\rm
+dust, and $Q_{\rm em}$ an emission efficiency parameter.  Converting
+this constraint to a dust mass requires an assumption regarding the
+grain properties.  We assume a grain density $\rho_{\rm
 d}$=3\,g\,cm$^{-3}$ typical for silicate grains, a fixed grain size
-$a$=1\,$\mu$m, and no
-self-absorption.  This enables the assumption that $A_{\rm d} = N \pi
-a^2$, for $N$ the total number of dust grains.  This in turn yields an
-upper limit on the dust mass of
+$a$=1\,$\mu$m, and no self-absorption.  This enables the assumption
+that $A_{\rm d} = N \pi a^2$, for $N$ the total number of dust grains.
+This in turn yields an upper limit on the dust mass of
 \begin{equation}
@@
 from absorption and scattering $\tau$ to be at least unity.  The
-optical depth can be written $\tau = n \sigma \ell = N \sigma$, where
+optical depth can be written $\tau = n \sigma \ell$, where
 $\sigma$ is the cross-section, $n$ is the number density, $\ell$ is
-the path length, and $N$ is the column density.  For spherical dust
+the path length.  For spherical dust
 grains in the optical, $\sigma = Q_{\rm ext} \pi a^2$, where $Q_{\rm
@@
 \cite{Croll2014} in their Figure 13.  \cite{Sanderson2023} calculated
-the relevant cloud mass for this problem assuming a spherical dust clump of
-size $r$, and they found
+the relevant cloud mass for this problem assuming a spherical dust
+clump of size $r$, and they found
 \begin{equation}
@@
 Three relevant objects for comparison to these limits are solar
-prominences, planetesimals, and comets.  Prominences of the Sun
-have gas masses of order $10^{14}$\,g-$10^{16}$\,g
-\cite{VialEngvold2015}.  A planetesimal of mass $\approx$10$^{15}$\,g
-with a bulk density of 1\,g\,cm$^{-3}$ would have a diameter of order
-one kilometer.  Halley's comet has a mass of order $10^{17}$\,g
-\cite{Rickman1989}, of which $\sim$$10^{14}$\,g is shed per orbit,
-most of which inspirals toward the Sun due to Poynting-Robertson drag.
+prominences, planetesimals, and comets.  Prominences of the Sun have
+gas masses of order $10^{14}$\,g-$10^{16}$\,g \cite{VialEngvold2015}.
+A planetesimal of mass $\approx$10$^{15}$\,g with a bulk density of
+1\,g\,cm$^{-3}$ would have a diameter of order one kilometer.
+Halley's comet has a mass of order $10^{17}$\,g \cite{Rickman1989}, of
+which $\sim$$10^{14}$\,g is shed per orbit, most of which inspirals
+toward the Sun due to Poynting-Robertson drag.
 
@@
 precision infrared spectrophotometry---could provide a path for
-distinguishing the scenario of a stellar outflow from an 
-accumulation of externally-sourced material.
+distinguishing the scenario of a trapped stellar outflow from an accumulation
+of externally-sourced material.
 
@@
     \end{tabular}
-		\caption{Properties of \starname.  References:
+		\caption{Properties of TIC~141146667.  References:
     Gaia DR3 \cite{GaiaDR3}, TESS \cite{Ricker2015},
@@
   assistance reducing the HIRES spectra.
-  LGB was supported by the Carnegie Institution for Science's Carnegie
-  Fellowship and the Heising-Simons 51~Pegasi~b Fellowship.
+  This work was supported by the Carnegie Fellowship and by the
+  Heising-Simons 51~Pegasi~b Fellowship.
   %

### 2025-03-24 paper/compile.sh

@@ -6,3 +6,5 @@ pdflatex ms.tex
 pdflatex ms.tex
 
 rm *.out *.aux *.blg *.log
+
+cp ms.pdf ../STATIC/.

### 2025-03-24 paper/ms.tex
update

@@
 line of sight \cite{Green2019}.  Figure~\ref{fig:camd} shows the
-location of the star in the color--absolute magnitude diagram (CAMD)
-relative to young stellar populations including Upper Scorpius (USco),
-IC~2602, and the Pleiades.  To make this diagram, we adopted the USco
-members in the $\delta$~Sco and $\sigma$~Sco sub-associations from
-\cite{Ratzenbock2023}, and the IC~2602 and Pleiades members from
+location of TIC~141146667 in the color--absolute magnitude diagram
+(CAMD) relative to young stellar populations including Upper Scorpius
+(USco), IC~2602, and the Pleiades.  To make this diagram, we adopted
+the USco members in the $\delta$~Sco and $\sigma$~Sco sub-associations
+from \cite{Ratzenbock2023}, and the IC~2602 and Pleiades members from
 \cite{Hunt2024}.  We assumed an average $V$-band extinction $A_{\rm
 V}$=$\{0.12, 0.11, 0.10\}\,{\rm mag}$ for USco \cite{Pecaut2016},
-IC~2602 \cite{Hunt2024}, and the Pleiades \cite{Hunt2024} respectively.
-We dereddened the photometry using the extinction coefficients
-$k_X\equiv A_X/A_0$ tabulated in \cite{GaiaCollaboration2018}, assuming
-that $A_0 = 3.1 E(B-V)$.
+IC~2602 \cite{Hunt2024}, and the Pleiades \cite{Hunt2024}
+respectively, and ages of 8\,Myr \cite{Ratzenbock2023}, 40\,Myr
+\cite{Randich2018}, and 112\,Myr \cite{Dahm2015} for each respective
+cluster.  We dereddened the photometry using the extinction
+coefficients $k_X\equiv A_X/A_0$ tabulated in
+\cite{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.
 
 Figure~\ref{fig:camd} shows that TIC~141146667 falls between the USco
-and Pleiades sequences, while nearly overlapping with IC~2602.  However,
+and Pleiades sequences, and approximately overlaps IC~2602.  However,
 the precision of the implied age is set by the intrinsic scatter of
@@
 the clump follows from the requirement that the magnetic pressure
-exceed the thermal pressure, $B^2 / 8\pi > n_{\rm H} k T$.  Although
+exceed the thermal pressure, $B_{\rm c}^2 / 8\pi > n_{\rm H} k T$.  Although
 we do not know the plasma temperature, if it were significantly beyond
 1,000-10,000\,K, we would either fully ionize the hydrogen, or not
-ionize enough of it.  We can therefore estimate
+ionize enough of it.  The field strength at the clump must therefore
+exceed
 \begin{equation}
-  B \gtrsim 3\,{\rm G}
+  B_{\rm c} \gtrsim 3\,{\rm G}
   \left(

### 2025-03-24 paper/ms.tex
update

@@
 coherent sinusoidal Balmer emission at twice to four times the
-star's equatorial velocity, demonstrating the existence of
-corotating clumps of circumstellar plasma --- a plasma torus.  Given
-that long-lived condensations of cool ($10^4$ K) plasma can persist
-in the hot ($10^6$ K) coronae of stars with a wide range of masses
-\cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
+star's equatorial velocity, directly demonstrating for the first
+time the existence of corotating circumstellar plasma around a CPV.
+Given that long-lived condensations of cool ($10^4$ K) plasma can
+persist in the hot ($10^6$ K) coronae of stars with a wide range of
+masses \cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
 these data support the idea that around the lowest-mass stars, such
@@
 and to a high incidence of flares and coronal mass ejections
-\cite{Gunther2020}.  However, despite the excellent work in these areas,
-the properties of the plasma and magnetospheric environments that
-bathe young, close-in exoplanets have remained challenging to
-quantify.
+\cite{Gunther2020}.  However, despite extensive work in these areas,
+the plasma and magnetospheric environments that bathe young, close-in
+exoplanets remain challenging to quantify.
+Understanding these environments is crucial because they directly
+impact atmospheric retention and habitability of close-in planets.
 
@@
 $f_{\rm H\alpha\ core}$ denotes the summed flux at $|\Delta v / v_{\rm
-eq}|<1$.  This panel shows that changes in the line core flux are
-correlated with the broadband variability over most of the light
-curve, except at $\phi$$\approx$0.5, during the transit of the
+eq}|<1$.  This panel shows that changes in the line core flux 
+correlate with the broadband variability throughout most of the light
+curve, except near $\phi$$\approx$0.5, corresponding to the transit of the
 3.9\,$R_\star$ clump and the occultation of the lower-velocity clump.
@@
 
-Spectra of magetically-active, rapidly rotating stars with a wide range
+Spectra of magnetically-active, rapidly rotating stars with a wide range
 of masses have been known to exhibit both sinusoidal emission features
@@
 disk, comets, or a close-in exoplanet.
-This latter possibility would render CPVs as extrasolar analogs of the
+This latter scenario would make CPVs extrasolar analogs of the
 Jupiter-Io plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
@@
 perspective, there is an urgent need for rigid-field
-magneto-hydrodynamic modeling to go beyond previous work
+magnetohydrodynamic modeling to go beyond previous work
 \cite{Townsend2005,Townsend2008,Krticka2022} and to explore what field
@@
 potential to assess both the field strength and topology.  An
-independent probe could also be connected the recent work
-\cite{Kaur2024} showing that CPVs are variable radio emitters with
-emission components that can be not only persistent, but also
-short-lived and highly polarized.  In particular, detecting radio
-emission produced by an electron cyclotron maser instability (e.g.
-\cite{Callingham2021}) would provide a measurement of the field
-strength at the site of the emitting region, further clarifying the
-magnetic field's structure.
+independent constraint on magnetic field topology may also come from
+radio observations, which have shown \cite{Kaur2024} that CPVs emit
+variable radio signals, including persistent and polarized components.
+Detecting radio emission produced by an electron cyclotron maser
+instability (e.g. \cite{Callingham2021}) in particular would provide
+a measurement of the field strength at the site of the emitting
+region, further clarifying the magnetosphere's structure.
 
@@
 circumstellar environments to the CPVs.
+Future studies that combine spectroscopic, polarimetric, and
+multi-wavelength observations, along with magnetohydrodynamic
+modeling, will be key to understanding the complex magnetospheric
+environments of these young stars.
 
@@
 {\it Spectroscopy:}
-We observed TIC~141146667 ($V$=16.2) with Keck/HIRES for five hours over
-a second-half night spanning 17 February 2024 10:47 to 16:13 (UT).
+We observed TIC~141146667 ($V$=16.2) with Keck/HIRES for five hours
+during the second half of the night, spanning 17 February 2024 10:47
+to 16:13 (UT).
 The star's airmass over this window spanned $z$=1.2-2.2, and we opted
@@
   \caption{Time evolution of select regions in the Keck/HIRES
-  spectra from 17 February 2025.
+  spectra from 17 February 2024.
   We made this plot by applying a windowed outlier rejection to remove
@@
 including H$\gamma$ and H$\delta$ ($n=5\rightarrow2$ and
-$n=6\rightarrow2$) do show some variability
-outside the line core.  However, this variability is not clearly
-periodic in the same manner as the emission seen in H$\alpha$.  This
-could be because there are insufficient hydrogen ions recombining from
-the relevant excited states, or due to the lower precision of the
-spectra in these bluer regions.  The Ca HK doublet is
-also detected in emission, however the continuum near it is not.
-Chromospheric emission from the magnesium triplet are also
-detected, but are sufficiently blended to be rendered unusable.
-
-A sudden blue excess appeared at $\phi$$\approx$0.2 in H$\alpha$,
-H$\gamma$, H$\delta$, and He 5876\,\AA.  At the same epoch, only
-H$\alpha$ clearly shows a resolved red excess as well, although
-H$\gamma$ and H$\delta$ do broaden at this time.  Given the sudden
-rise of this emission in $<$15\,minutes, and the association between
-He 5876\,\AA\ and stellar outflows at high excitation energy, this
-component of the spectra might be associated with a flare, rather
-than with a stable, periodic component.
+$n=6\rightarrow2$) do show variability outside the line core.
+However, this variability is not clearly periodic in the same manner
+as the emission seen in H$\alpha$.  This could be because there are
+insufficient hydrogen ions in the relevant excited states, or because
+the spectra have lower precision in these bluer regions.  The Ca HK
+doublet is also detected in emission, while the continuum near it is
+not.  Chromospheric emission from the magnesium triplet is also
+detected, but these lines are sufficiently blended to be rendered
+unusable.
+
+Figure~\ref{fig:hirescuts} provides a novel view on the sudden blue
+excess that appeared at $\phi$$\approx$0.2 in H$\alpha$, H$\gamma$,
+H$\delta$, and He 5876\,\AA.  At the same epoch, only H$\alpha$
+clearly shows a resolved red excess as well, although H$\gamma$ and
+H$\delta$ are broadened at this time.  Given the sudden rise of this
+emission in $<$15\,minutes, this sudden blue excess might suggest a
+more sudden flow, rather than a stable, periodic component.  A stellar
+flare could be a plausible explanation for such a sudden rise.
+However this idea seems incompatible with the sinusoidal emission seen
+from $\phi$$\approx$0.5-1.0, and with the fact that flares often
+excite iron lines in the blue HIRES orders, which are not observed.
+More time-series spectroscopy would be needed to provide a definitive
+clarification for this type of non-periodic variability.
 
@@
 magnetic field strength can be estimated from the available data.
-We caution that the following estimates are simple order of magnitude
-calculations: detailed considerations of radiative transfer are a
-worthy topic for future work, but are beyond the scope of this
-article.
+We caution that the following estimates are order of magnitude
+calculations that assume a simple uniform-density plasma: detailed
+considerations of radiative transfer are a worthy topic for future
+work, but are beyond the scope of this article.
 

### 2025-03-26 paper/ms.tex
update ms

@@
 exoplanet and stellar astrophysics.  Previous work has established
-that most M dwarfs host close-in planets \cite{Dressing2015} that are
-on average subject to long circumstellar disk lifetimes
+that most M dwarfs host close-in planets \cite{Dressing2015} that 
+on average are subject to long circumstellar disk lifetimes
 \cite{Ribas2015}, to large doses of UV radiation \cite{France2013},
@@
 periodic light curves.  We selected the star for spectroscopy because
-its brightness and rotation rate enable efficiently mapping out line
-profile variability.  We observed it for five hours on
+its brightness and rotation rate enable measuring variability in its line
+profile.  We observed it for five hours on
 17~February~2024 (UT) using the High Resolution Echelle Spectrometer
-(HIRES \cite{vogt_hires_1994}) on the Keck I 10m telescope.  TESS
+(HIRES \cite{vogt_hires_1994}) on the 10\,m Keck I telescope.  TESS
 observed the star over a four week interval from 30~January~2024 to
@@
 this double-peaked component: the flux excess begins with an amplitude
-of 70\% of the continuum flux early in the observation sequence, and
+of 70\% above the continuum early in the observation sequence, and
 diminishes to 10\% by its end.  The component 180$^\circ$ opposite in
@@
 % * keck/hires: behavior at v/veq<1
-The stellar H$\alpha$ line core, at $|\Delta v / v_{\rm
-eq}|<1$, captures a superposition of emission from the star's
-chromosphere, modulated by any occulting material capable of absorbing
+The H$\alpha$ line core at $|\Delta v / v_{\rm
+eq}|<1$ originates from a superposition of emission from the star's
+chromosphere, modulated by occulting material capable of absorbing
 or emitting H$\alpha$ photons.  In Figure~\ref{fig:spec}e, the data
@@
 are present around at least one such star.  This observation rules out
-a ``starspot-only'' origin scenario for CPVs, \cite{Koen2021} because
+a ``starspot-only'' origin for the CPVs, \cite{Koen2021} because
 such scenarios have no means of explaining spectroscopic emission
@@
 include plasma with a significant population of hydrogen atoms in the
-$n$=3 excited state, for $n$ the principal quantum number.  More quantitatively, the observed H$\alpha$
-luminosity suggests characteristic densities and masses for the
-gaseous component of these clumps of $n_{\rm H} \sim
-10^{11}$-$10^{12}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g (see
-Section~\ref{subsec:gas}).  Dust, if present, is independently
-constrained to have a total mass $10^{15}\,{\rm g} < M_{\rm dust} <
-10^{17}\,{\rm g}$ (see Section~\ref{subsec:dust}).  This circumstellar
-material could originate either from the star or from an external
-source.  Plausible external sources include an old and undetected
-disk, comets, or a close-in exoplanet.
-This latter scenario would make CPVs extrasolar analogs of the
-Jupiter-Io plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
+$n$=3 excited state, where $n$ denotes the principal quantum number.
+More quantitatively, the observed H$\alpha$ luminosity suggests
+characteristic densities and masses for the gaseous component of these
+clumps of $n_{\rm H} \sim 10^{11}$-$10^{12}$\,cm$^{-3}$ and $M_{\rm
+gas} \sim 10^{17}$\,g (see Section~\ref{subsec:gas}).  Dust, if
+present, is independently constrained to have a total mass
+$10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm g}$ (see
+Section~\ref{subsec:dust}).  This circumstellar material could
+originate either from the star or from an external source.  Plausible
+external sources include an old and undetected disk, comets, or a
+close-in exoplanet.  This latter scenario would make CPVs extrasolar
+analogs of the Jupiter-Io plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
 
@@
 sculpted by tilted-dipole magnetic fields, and the transits of these
-clumps produce the observed broadband photometric
+clumps produce broadband photometric
 variability through bound-free scattering \cite{Townsend2005} and
@@
 plasma -- can be clarified by time-series optical and infrared
-spectrophotometry.  While observations of CPVs in the optical may
-suggest chromaticity consistent with dust
+spectrophotometry.  While observations of CPVs in the optical 
+suggest a chromaticity consistent with dust
 \cite{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such
@@
 by measuring the extinction curve for one or more CPVs from
-1-10\,$\mu$m.  Composition and size distributions similar to debris
+1-20\,$\mu$m.  Composition and size distributions similar to debris
 from rocky bodies seen around white dwarfs \cite{Reach2009} would

### 2025-03-26 drivers/explore_hydrogen_equilibrium.py

@@ -1,0 +1,382 @@
+"""
+This module implements a statistical equilibrium model for a
+hydrogen sphere with five bound levels plus the continuum under
+Case B conditions. It solves for the level populations given the
+temperature T, total hydrogen number density n_Htot, and a fixed
+ionization fraction x = n_e/n_Htot. The model includes radiative
+downward transitions (with Einstein A‐coefficients) and electron‐
+impact collisional excitation/de‐excitation. Recombination into
+levels 2–5 is included with effective recombination fractions
+(f2 = 0.60, f3 = 0.15, f4 = 0.15, f5 = 0.10) and a total Case B
+coefficient alpha_B(T) = 2.59e-13 (T/1e4)^(-0.7) cm^3 s^-1
+(Osterbrock & Ferland 2006; Storey & Hummer 1995).
+
+The Hα emissivity (from the n=3→2 transition) is then computed
+as
+
+  ε_Hα = h ν_32 n_3 A_32 β(τ)
+
+where β(τ) = (1 – exp(–τ))/τ is an escape probability that
+parameterizes the effect of optical depth τ (log10(τ) spanning
+–3 to +4).
+
+Generated by ChatGPT o3-mini-high on March 20 2025.
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Physical constants (cgs units)
+h = 6.62607015e-27      # Planck constant [erg s]
+c = 2.99792458e10       # Speed of light [cm/s]
+k_B = 1.380649e-16      # Boltzmann constant [erg/K]
+eV_to_erg = 1.60218e-12  # 1 eV in erg
+
+# Recombination coefficient parameters
+alphaB_1e4 = 2.59e-13   # cm^3 s^-1 at 1e4 K
+
+# Effective recombination fractions for levels 2-5 (Case B)
+f_recomb = {2: 0.60, 3: 0.15, 4: 0.15, 5: 0.10}
+
+# Einstein A coefficients for allowed transitions (s^-1)
+# Keys: (upper_level, lower_level)
+A_dict = {
+    (2, 1): 6.265e8,
+    (3, 1): 1.672e8,
+    (3, 2): 4.410e7,
+    (4, 1): 8.200e7,
+    (4, 2): 1.260e7,
+    (4, 3): 2.100e7,
+    (5, 1): 3.000e7,
+    (5, 2): 4.000e6,
+    (5, 3): 7.000e6,
+    (5, 4): 1.000e7
+}
+
[…]

### 2025-03-26 drivers/plot_mdot_B_regime.py
add mdot / B plot

@@ -1,0 +1,123 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy import units as u
+from astropy import constants as const
+
+
+def dividing_line_B_accretion(mdot: u.Quantity, R: u.Quantity, 
+                              M: u.Quantity, P: u.Quantity) -> u.Quantity:
+    """Compute the dividing magnetic field for the accretion regime.
+
+    This function returns the magnetic field such that the
+    Alfvén radius equals the corotation radius in the accretion
+    regime, i.e., when
+      (B^4 R^12/(G M mdot^2))^(1/7) = (G M P^2/(4π^2))^(1/3).
+
+    Args:
+        mdot (u.Quantity): Mass accretion rate (g/s).
+        R (u.Quantity): Stellar radius (cm).
+        M (u.Quantity): Stellar mass (g).
+        P (u.Quantity): Rotation period (s).
+
+    Returns:
+        u.Quantity: Magnetic field (Gauss) dividing the two regimes.
+    
+    Generated by ChatGPT o3-mini-high on March 26 2025.
+    """
+    factor1 = ((const.G * M * mdot**2) / (R**12))**(1/4)
+    factor2 = ((const.G * M * P**2) / (4 * np.pi**2))**(7/12)
+    return factor1 * factor2
+
+
+def dividing_line_B_wind(mdot: u.Quantity, R: u.Quantity, 
+                         M: u.Quantity, P: u.Quantity, 
+                         f: float) -> u.Quantity:
+    """Compute the dividing magnetic field for the wind regime.
+
+    This function returns the magnetic field such that the
+    Alfvén radius equals the corotation radius in the wind
+    regime, using the substitution
+      v_inf = f * sqrt(2GM/R).
+    The equality leads to
+      B > [(mdot f)^(1/2) (G M)^(11/12) P^(4/3)] /
+          [2^(13/12) π^(4/3) R^(13/4)].
+
+    Args:
+        mdot (u.Quantity): Mass loss rate (g/s).
+        R (u.Quantity): Stellar radius (cm).
+        M (u.Quantity): Stellar mass (g).
+        P (u.Quantity): Rotation period (s).
+        f (float): Factor for the terminal wind speed relative to the
[…]

### 2025-03-26 paper/ms.tex
update

@@
 local photometric minima, and one to two local maxima.  Its W-shape is
-suggestive of eclipse geometries seen in certain forward models of warped
-plasma tori \cite{Townsend2008}.
+suggestive of eclipse geometries seen in forward models of warped
+plasma tori (see \cite{Townsend2008} and the associated
+\href{http://user.astro.wisc.edu/~townsend/static.php?ref=rrm-movies#Download_Bundles}{movies}).
+% particularly ω/ωc = 0.5, beta = 30, i = 90.
 
@@
 % * keck/hires: behavior at v/veq<1
-The H$\alpha$ line core at $|\Delta v / v_{\rm
-eq}|<1$ originates from a superposition of emission from the star's
-chromosphere, modulated by occulting material capable of absorbing
-or emitting H$\alpha$ photons.  In Figure~\ref{fig:spec}e, the data
-from $\phi$=0.4-1.2 have a simple interpretation: from $\phi$=0.4-0.9,
-a hot (emitting) region first gradually crosses the stellar line
-profile, followed from $\phi$=0.7-1.2 by the transit of a cool
-(absorbing) region. Phases $\phi$$<$0.4 show a mix of similar events,
-though the time sampling is sufficiently coarse that the
-interpretation is less clear.  A final exercise to quantify the
-behavior in the line core is shown in Figure~\ref{fig:spec}d, where
-$f_{\rm H\alpha\ core}$ denotes the summed flux at $|\Delta v / v_{\rm
-eq}|<1$.  This panel shows that changes in the line core flux 
-correlate with the broadband variability throughout most of the light
-curve, except near $\phi$$\approx$0.5, corresponding to the transit of the
-3.9\,$R_\star$ clump and the occultation of the lower-velocity clump.
+The data in the H$\alpha$ line core are more complex.  At $|\Delta v /
+v_{\rm eq}|<1$, most observed H$\alpha$ photons come from the star's
+chromosphere; circumstellar material may additionally modulate the
+line profile.
+Figure~\ref{fig:spec}e suggests line core variability caused by both
+bright and dark regions on the star's surface, superposed
+with smaller-amplitude variability from the transiting circumstellar
+material.
+For instance, from $\phi$=0-0.3, the double-peaked emission feature
+is visible when it is being viewed both on and off-limb.
+However, the large emission feature that crosses the star from
+$\phi$=0.4-0.9 cannot be circumstellar in origin; it emits at an
+amplitude greater than that observed from the circumstellar
+components, and it crosses the stellar velocity surface too slowly.
+It must therefore originate from a chromospherically bright region
+near the stellar surface.
+While the origin of the other bright and dark streaks passing across the
+line core are more ambiguous,
+a final exercise to quantify the behavior of this region is shown in
+Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes the
+summed flux at $|\Delta v / v_{\rm eq}|<1$.  This panel shows that
+changes in the line core flux correlate with the broadband variability
+throughout most of the light curve, except near $\phi$$\approx$0.5,
+corresponding to the transit of the 3.9\,$R_\star$ clump and the
+occultation of the lower-velocity clump.
 
@@
                                         & \hspace{3pt} velocity (\kms)	                                 &                      \\
+%
+$v_{\rm break}$\dotfill		              & Breakup velocity \dotfill                                      &  316$\pm$16      & 6 \\
+                                        & \hspace{3pt} ($G M_\star / R_\star$)$^{1/2}$ (\kms)	           &                      \\
 %
@@
 sculpted by tilted-dipole magnetic fields, and the transits of these
-clumps produce broadband photometric
-variability through bound-free scattering \cite{Townsend2005} and
-Thomson scattering \cite{Berry2022}.  For $\sigma$~Ori~E and almost
+clumps produce broadband photometric variability through bound-free
+scattering \cite{Townsend2005} and Thomson scattering
+\cite{Berry2022}.  
+The plasma accumulates at antipodes 180$^\circ$ apart because the
+deepest local minima in the effective potential exist along the line
+of intersection between the rotational and magnetic equators (see
+Equation~22 of \cite{Townsend2005}).
+For $\sigma$~Ori~E and almost
 all of its analogs, the result is light curves that appear ``simple'',
@@
     % NOTE: ROSAT is an emitter.  GALEX detection.
+    % ROSAT: 3.25e-13 mW/m^2 = erg/cm^2/s
     % Ofek+2011 1.4Ghz emitter.  Helfand+2015 ditto.  Bruzewski+2021.
@@
 \item[Acknowledgments]
-  LGB is grateful to M.~Jardine, A.~Weinberger, and B.~Tofflemire for
+  LGB is grateful to M.~Jardine, A.~Weinberger, B.~Tofflemire, and
+  J.~Spake for
   insightful conversations, and to A.~Howard and H.~Isaacson for their

### 2025-03-28 paper/ms.tex
update ms: JSS comments v0

@@
 opaque material that corotates with the star
-\cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.  The
+\cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.  However, the
 composition, origin, and even the existence of this material are
@@
   years.  The TESS light curve is phased to the \periodhr\ hour period
-  in groups of a few cycles per frame.  This is the period both of
+  in groups of three cycles per frame.  This is the period both of
   stellar rotation, and (we hypothesize) of corotating clumps of
@@
 periodic light curves.  We selected the star for spectroscopy because
-its brightness and rotation rate enable measuring variability in its line
-profile.  We observed it for five hours on
+its brightness and rotation rate enable efficiently measuring
+variability in its line profile.  We observed it for five hours on
 17~February~2024 (UT) using the High Resolution Echelle Spectrometer
@@
 longer timescales \cite{Petit2013,Daley-Yates2024}.  Generally
-speaking, such material need neither transit, nor be optically thick.
+speaking, such material need neither transit nor be opaque in
+broadband optical light.
 For instance, the H$\alpha$ emission clump at 3.9\,$R_\star$ shows no 
@@
 For $\sigma$~Ori~E and almost
-all of its analogs, the result is light curves that appear ``simple'',
-resembling those of eclipsing binaries, and time-dynamic H$\alpha$
+all of its analogs, the result is ``simple'' light curves that 
+resemble those of eclipsing binaries, and time-dynamic H$\alpha$
 spectra similar to those in Figure~\ref{fig:spec}
@@
 
-Figure~\ref{fig:fulllc} shows the TESS Sector~75 data acquired near
+Extended Data Figure~\ref{fig:fulllc} shows the TESS Sector~75 data acquired near
 the epoch of spectroscopy.  The gap in coverage from BTJD
@@
 
-Figure~\ref{fig:fulllc} shows that a large, complex eclipse
+Extended Data Figure~\ref{fig:fulllc} shows that a large, complex eclipse
 feature was present before and after the HIRES data were
@@
 Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting
-best-fit SED is shown in Figure~\ref{fig:sed}.  This method has the
+best-fit SED is shown in Extended Data Figure Figure~\ref{fig:sed}.  This method has the
 most constraining power for the star's effective temperature (2972
@@
 ($b$=$+$53$^\circ$) yield negligible interstellar reddening along the
-line of sight \cite{Green2019}.  Figure~\ref{fig:camd} shows the
+line of sight \cite{Green2019}.  Extended Data Figure~\ref{fig:camd} shows the
 location of TIC~141146667 in the color--absolute magnitude diagram
@@
 
-Figure~\ref{fig:camd} shows that TIC~141146667 falls between the USco
+Extended Data Figure~\ref{fig:camd} shows that TIC~141146667 falls between the USco
 and Pleiades sequences, and approximately overlaps IC~2602.  However,
@@
 is that lithium is not abundant in the spectrum of TIC~141146667.
-Figure~\ref{fig:liew_population} compares our upper limit against the
+Extended Data Figure~\ref{fig:liew_population} compares our upper limit against the
 equivalent width measurements reported by \cite{Jeffries2023}
-based on the Gaia-ESO spectroscopic survey; Figure~\ref{fig:hirescuts}
+based on the Gaia-ESO spectroscopic survey; Extended Data Figure~\ref{fig:hirescuts}
 shows the associated raw spectra.  If the star were $\lesssim$20\,Myr
@@
 luminous) than main sequence stars of the same color, while showing no
-indicators for binarity.  The first item constitutes evidence for
-youth since all known CPVs are $\lesssim$200\,Myr \cite{Bouma2024}.
-The reference sequences for the Pleiades (112\,Myr, \cite{Dahm2015})
-show a few stars of equal luminosity and the same temperature,
-suggesting a photometric isochronal age upper limit
+indicators for binarity.  Being a CPV suggests that the star is young
+because a previous CPV search unbiased in age found 90\% of its
+detections to be in $\lesssim$200\,Myr old clusters \cite{Bouma2024};
+the remaining 10\% could not be associated with any coeval
+population.
+Similarly, studies of rotation in $\lesssim$100\,Myr clusters serendipitously found
+$\approx$50-100 examples of the class
+\cite{Rebull2016,Stauffer2017,Stauffer2018,Rebull2018,Zhan2019,Rebull2020,Stauffer2021,Rebull2022,Popinchalk2023},
+whereas analogous studies of Praesepe and the Hyades did not report
+any evidence for CPVs in a set of approximately one thousand
+$\approx$700\,Myr stars \cite{Rebull2017,Douglas2019,Rampalli2021}.
+Regarding the isochronal age constraint, the Pleiades (112\,Myr,
+\cite{Dahm2015}) shows a few stars of equal luminosity and the same
+temperature, suggesting a photometric isochronal age upper limit
 $\lesssim$150\,Myr.  The weak lithium absorption suggests an age of at
@@
 or at least 35\,Myr based on the \cite{Feiden2016} isochrones.  These
-considerations yield our adopted age range of 150\,Myr.
+considerations yield our adopted age range of 35-150\,Myr.
 
@@
 
-Figure~\ref{fig:hirescuts} shows a few regions of interest in the
+Extended Data Figure~\ref{fig:hirescuts} shows a few regions of interest in the
 HIRES spectra, which cover 3650-7960\,\AA.  Higher order Balmer lines
@@
 
-Figure~\ref{fig:hirescuts} provides a novel view on the sudden blue
+Extended Data Figure~\ref{fig:hirescuts} provides a novel view on the sudden blue
 excess that appeared at $\phi$$\approx$0.2 in H$\alpha$, H$\gamma$,
@@
 absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ resonance
-line are both shown in Figure~\ref{fig:hirescuts}.  In the latter,
+line are both shown in Extended Data Figure~\ref{fig:hirescuts}.  In the latter,
 narrow telluric absorption features overlap the blue wing of the line.
@@
 scattering of stellar H$\alpha$ photons, or from radiative
-recombination.  We neglect scattering because Figures~\ref{fig:spec}
-and~\ref{fig:hirescuts} show the amplitude of the circumstellar
+recombination.  We neglect scattering because Figure~\ref{fig:spec}
+and Extended Data Figure~\ref{fig:hirescuts} show the amplitude of the circumstellar
 H$\alpha$ emission varying by a factor of $\approx$5, in a manner
@@
 
-Regarding the upper limit, Figure~\ref{fig:sed} shows the SED.  While
+Regarding the upper limit, Extended Data Figure~\ref{fig:sed} shows the SED.  While
 AllWISE \cite{Cutri2014} yielded a confident W3 detection
@@
     \hline
-    $T_{eff}$ (K) & 2972 $\pm$ 40 & \cite{Bouma2024} SED fit\\
-    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & \cite{Bouma2024} SED fit \\
-    $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & \cite{Bouma2024} SED fit \\
+    $T_{\rm eff}$ (K) & 2972 $\pm$ 40 & SED fit \cite{Bouma2024} \\
+    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & SED fit \cite{Bouma2024} \\
+    $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & SED fit \cite{Bouma2024} \\
     $P_{\rm rot}$ (hours) & 3.930 $\pm$ 0.001 & TESS \\ 

### 2025-03-29 paper/ms.tex
update

@@
 rapidly-rotating ($P$=3.9\,hr) CPV, TIC~141146667. The spectra show
-coherent sinusoidal Balmer emission at twice to four times the
+sinusoidal time-varying Balmer emission at twice to four times the
 star's equatorial velocity, directly demonstrating for the first
@@
 rotation periods shorter than two days.  Within current sensitivity
-limits, none have primordial disks \cite{Stauffer2017,Bouma2024}.
-However, $\approx$3\% of stars a few million years old show this
-behavior, an  observed fraction which decreases to $\approx$0.3\% by
+limits, none host disks \cite{Stauffer2017,Bouma2024}.
+However, $\approx$3\% of stars a few million years old show complex
+photometric behavior, an observed fraction which decreases to $\approx$0.3\% by
 $\approx$150\,Myr \cite{Rebull2020}.
@@
 field, and the exact geometry of where the plasma can accumulate is
-dictated by the field's topology.  For instance, a tilted dipole field
-tends to yield an accumulation surface of a warped torus
+dictated by the field's topology.  For instance, a magnetic dipole field
+tilted with respect to the stellar spin axis
+yields accumulations in a warped torus geometry
 \cite{Townsend2005}, whereas in the limit of a single strong field
@@
 components, separated by half a cycle in phase.  The first component
-has clearer sinusoidal behaviour and is double-peaked, with peak
+has clearer sinusoidal behaviour in time and is double-peaked, with peak
 semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
@@
 partially-ionized hydrogen to corotate with the star.  Based on the
-period, this material's motion is not Keplerian; it can only be
+observed sinusoidal period and peak velocity, this material's motion
+is not controlled by gravitational attraction to the star; it can only be
 explained by plasma being dragged along with the rotating stellar
@@
 of masses have been known to exhibit both sinusoidal emission features
+in time
 \cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} and
@@
 AllWISE \cite{Cutri2014} yielded a confident W3 detection
-(9.8$\sigma$), the W4 extraction yielded only a marginal indication
+(9.8$\sigma$) consistent with the photometric extrapolation from bluer
+bandpasses, the W4 extraction yielded only a marginal indication
 (1.7$\sigma$) of detectable flux.  Similar to other CPVs
@@
 
-Three relevant objects for comparison to these limits are solar
+Three relevant objects for comparison include solar
 prominences, planetesimals, and comets.  Prominences of the Sun have
-gas masses of order $10^{14}$\,g-$10^{16}$\,g \cite{VialEngvold2015}.
+gas masses of $10^{14}$\,g-$10^{16}$\,g \cite{VialEngvold2015}.
 A planetesimal of mass $\approx$10$^{15}$\,g with a bulk density of
@@
 
-These calculations suggest that if dust is responsible for the
-broadband variability of CPVs, it would need to be concentrated in
+Broadly, these considerations suggest that if dust is responsible for
+the broadband variability of CPVs, it would need to be concentrated in
 clumps with masses in the range of $10^{15}$-$10^{17}$\,g.  Given
@@
 gas}/M_{\rm dust}$ ranges of 1-100.  More careful measurements of this
-ratio---in particular enabled by inferring the dust mass through high
+ratio---in particular by inferring the dust mass through high
 precision infrared spectrophotometry---could provide a path for
-distinguishing the scenario of a trapped stellar outflow from an accumulation
-of externally-sourced material.
+distinguishing the scenario of a trapped stellar outflow from an
+accumulation of externally-sourced material.  While there are several
+plausible external sources, feeding through a low-mass disk in
+particular cannot be ruled out based on typical disk depletion times
+\cite{Haisch2001}.  Observations of infrared excesses and accretion
+signatures in low-mass stars tens of millions of years old suggest a
+broad lifetime distribution for such disks
+\cite{Silverberg2020,Lee2020,Gaidos2022,Pfalzner2024}.
 

### 2025-03-31 paper/ms.tex
update

@@
 AllWISE \cite{Cutri2014} yielded a confident W3 detection
-(9.8$\sigma$) consistent with the photometric extrapolation from bluer
+(9.8$\sigma$) consistent with the photospheric extrapolation from bluer
 bandpasses, the W4 extraction yielded only a marginal indication
@@
 
-Broadly, these considerations suggest that if dust is responsible for
+To summarize, if dust is responsible for
 the broadband variability of CPVs, it would need to be concentrated in

### 2025-03-31 drivers/calc_1d_arc_model.py
add drivers/calc_1d_arc_model.py

@@ -1,0 +1,103 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy import constants as const
+from astropy import units as u
+from aesthetic.plot import set_style
+
+def compute_rv_range(phi: float,
+                     delta_phi_deg: float,
+                     torus_radius: u.Quantity = None) -> tuple:
+    """Compute the min and max radial velocities for an arc on a torus.
+
+    Given the central azimuthal angle phi of the emitting arc and its
+    azimuthal extent in degrees, this function computes the minimum and
+    maximum radial velocities for that arc in an edge-on circular orbit.
+    The orbital period is fixed at 3.93 hours and the stellar radius is fixed
+    at 0.42 R_sun. By default, the torus radius is set to 2.4 * R_star.
+    The radial velocity for a point at azimuth theta is defined as
+    v_r = - v_orb * sin(theta), with v_orb = 2π * torus_radius / period.
+
+    Args:
+        phi (float): Central azimuthal angle of the arc in radians.
+        delta_phi_deg (float): Azimuthal extent of the arc in degrees.
+        torus_radius (astropy.units.Quantity, optional): Radius of the torus.
+            Defaults to 2.4 * (0.42 R_sun).
+
+    Returns:
+        tuple: (v_min, v_max) in km/s, where v_min is the minimum and
+        v_max is the maximum radial velocity spanned by the arc.
+
+    Generated by ChatGPT o3-mini-high on March 31 2025.
+    """
+    delta_phi_rad = np.deg2rad(delta_phi_deg)
+    r_star = 0.42 * const.R_sun
+    if torus_radius is None:
+        torus_radius = 2.4 * r_star
+    period = 3.93 * u.hour
+    v_orb = (2 * np.pi * torus_radius / period).to(u.km / u.s)
+    num_points = 100
+    arc_angles = np.linspace(phi - delta_phi_rad / 2,
+                             phi + delta_phi_rad / 2,
+                             num_points)
+    velocities = -v_orb.value * np.sin(arc_angles)
+    v_min = np.min(velocities)
+    v_max = np.max(velocities)
+    return v_min, v_max
+
+
+def compute_rv_range_over_phi(delta_phi_deg: float,
+                              torus_radius: u.Quantity = None,
+                              num_phi: int = 360) -> tuple:
[…]

### 2025-03-31 drivers/calc_2d_annulus_model.py
add drivers/calc_2d_annulus_model.py

@@ -1,0 +1,153 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy import constants as const
+from astropy import units as u
+from aesthetic.plot import set_style
+
+def compute_blob_vrange_at_phi(phi: float, delta_phi_deg: float,
+                               Delta_r: u.Quantity,
+                               torus_radius: u.Quantity = None,
+                               n_r: int = 100,
+                               n_theta: int = 100) -> tuple:
+    """Compute the velocity range for a blob segment of an annulus.
+
+    The blob is defined by its central azimuth phi (radians), azimuthal
+    extent delta_phi_deg (degrees), and radial width Delta_r. The torus is
+    assumed to be centered at R0 = 2.4 * (0.42 R_sun) by default. The system
+    rotates rigidly with period 3.93 hours, so that the orbital angular speed
+    is Omega = 2π/P. A 2D polar grid in (r, theta) is constructed over the blob,
+    and the observed radial velocity is calculated as:
+        v_obs = - (Omega * r) * sin(theta)
+    for an edge-on view. The overall velocity range is the difference between
+    the maximum and minimum v_obs values over the grid.
+
+    Generated by ChatGPT o3-mini-high on March 31 2025.
+
+    Args:
+        phi (float): Central azimuthal angle of the blob in radians.
+        delta_phi_deg (float): Azimuthal extent of the blob in degrees.
+        Delta_r (astropy.units.Quantity): Radial width of the blob.
+        torus_radius (astropy.units.Quantity, optional): Central radius of the
+            torus. Defaults to 2.4 * (0.42 R_sun).
+        n_r (int, optional): Number of radial grid points. Defaults to 100.
+        n_theta (int, optional): Number of azimuthal grid points.
+            Defaults to 100.
+
+    Returns:
+        tuple: (v_min, v_max, v_range, v_obs_flat)
+            v_min (float): Minimum radial velocity (km/s).
+            v_max (float): Maximum radial velocity (km/s).
+            v_range (float): Difference (v_max - v_min) in km/s.
+            v_obs_flat (numpy.ndarray): Flattened array of v_obs values (km/s).
+    """
[…]

### 2025-03-31 drivers/webapp_2d_annulus.py
[WIP] stage webapp 2d annulus

@@ -1,0 +1,276 @@
+import numpy as np
+import plotly.graph_objs as go
+from dash import Dash, dcc, html, Input, Output
+from astropy import constants as const
+from astropy import units as u
+from aesthetic.plot import set_style
+
+set_style('science')
+
+
+def compute_blob_vrange_at_phi(phi: float, delta_phi_deg: float,
+                               Delta_r: u.Quantity,
+                               torus_radius: u.Quantity,
+                               n_r: int = 100,
+                               n_theta: int = 100) -> tuple:
+    """Compute the velocity range for a blob segment at a given phi.
+
+    The blob is defined as a segment of an annulus with radial width Delta_r
+    and azimuthal extent delta_phi_deg (in degrees). The torus is in rigid
+    corotation with period 3.93 hours. The observed radial velocity at a point
+    is given by v_obs = - (Omega * r) * sin(theta), where Omega = 2π/P.
+    The function computes v_min, v_max and the overall v_range (v_max - v_min)
+    by constructing a 2D grid in (r, theta).
+
+    Generated by ChatGPT o3-mini-high on March 31 2025.
+
+    Args:
+        phi (float): Central azimuthal angle (radians) of the blob.
+        delta_phi_deg (float): Azimuthal extent of the blob (degrees).
+        Delta_r (u.Quantity): Radial width of the blob.
+        torus_radius (u.Quantity): Central radius of the torus.
+        n_r (int, optional): Number of radial grid points. Defaults to 100.
+        n_theta (int, optional): Number of azimuthal grid points.
+            Defaults to 100.
+
+    Returns:
+        tuple: (v_min, v_max, v_range, v_obs_flat) where velocities are in km/s.
+    """
+    delta_phi_rad = np.deg2rad(delta_phi_deg)
+    # Radial limits of the blob segment.
+    r_min = (torus_radius - Delta_r / 2).to(u.m)
+    r_max = (torus_radius + Delta_r / 2).to(u.m)
+    r_vals = np.linspace(r_min.value, r_max.value, n_r) * u.m
+    theta_min = phi - delta_phi_rad / 2
+    theta_max = phi + delta_phi_rad / 2
+    theta_vals = np.linspace(theta_min, theta_max, n_theta)
+    r_grid, theta_grid = np.meshgrid(r_vals, theta_vals, indexing='ij')
+    period = 3.93 * u.hour
[…]

### 2025-03-31 drivers/webapp_2d_annulus.py
update annulus webapp

@@ -27,8 +27,8 @@ def compute_blob_vrange_at_phi(phi: float, delta_phi_deg: float,
     Args:
         phi (float): Central azimuthal angle (radians) of the blob.
         delta_phi_deg (float): Azimuthal extent of the blob (degrees).
-        Delta_r (u.Quantity): Radial width of the blob.
-        torus_radius (u.Quantity): Central radius of the torus.
+        Delta_r (astropy.units.Quantity): Radial width of the blob.
+        torus_radius (astropy.units.Quantity): Central radius of the torus.
         n_r (int, optional): Number of radial grid points. Defaults to 100.
         n_theta (int, optional): Number of azimuthal grid points.
             Defaults to 100.
@@ -37,7 +37,6 @@ def compute_blob_vrange_at_phi(phi: float, delta_phi_deg: float,
         tuple: (v_min, v_max, v_range, v_obs_flat) where velocities are in km/s.
     """
     delta_phi_rad = np.deg2rad(delta_phi_deg)
-    # Radial limits of the blob segment.
     r_min = (torus_radius - Delta_r / 2).to(u.m)
     r_max = (torus_radius + Delta_r / 2).to(u.m)
     r_vals = np.linspace(r_min.value, r_max.value, n_r) * u.m
@@ -63,16 +62,16 @@ def compute_blob_vrange_over_phi(delta_phi_deg: float, Delta_r: u.Quantity,
     """Compute the velocity range over all central blob angles.
 
     For an annulus segment (blob) defined by its azimuthal extent delta_phi_deg
-    and radial width Delta_r, this function computes v_min, v_max, and v_range
-    as functions of the central blob angle phi spanning 0 to 2π, using rigid
-    corotation.
+    and radial width Delta_r, this function computes v_min, v_max, v_range,
+    and the central point's radial velocity (v_center) as functions of the
+    central blob angle phi spanning 0 to 2π, using rigid corotation.
 
     Generated by ChatGPT o3-mini-high on March 31 2025.
 
     Args:
         delta_phi_deg (float): Azimuthal extent of the blob in degrees.
-        Delta_r (u.Quantity): Radial width of the blob.
-        torus_radius (u.Quantity): Central radius of the torus.
+        Delta_r (astropy.units.Quantity): Radial width of the blob.
[…]

### 2025-03-31 drivers/webapp_3d_gaussian.py
stage broken 3d gaussian webapp

@@ -1,0 +1,481 @@
+"""
+Semi-working 3D Gaussian blob orbiting a star.
+
+(by "semi" this means that the light curve and RV curve calculation seems ok.  but the viz is out of whack, and this approach is probably WAY too complex.)
+"""
+import numpy as np
+import dash
+from dash import dcc, html, Input, Output
+import plotly.graph_objs as go
+from astropy import constants as const
+from astropy import units as u
+import math
+
+# Global constants
+T_SEC = 3.93 * 3600  # period in seconds
+OMEGA = 2 * np.pi / T_SEC  # angular velocity (rad/s)
+R_STAR = const.R_sun  # assume star radius = 1 R_star = 1 R_sun
+
+
+def compute_blob_rotation(blob_center: np.ndarray,
+                          tilt: float) -> np.ndarray:
+    """Compute rotation matrix for blob's local frame.
+
+    The blob's local frame is defined so that:
+      - The x' axis points radially from the star to the blob center.
+      - The z' axis is aligned with the orbital angular momentum.
+      - The y' axis = cross(z', x').
+
+    Generated by ChatGPT o3-mini-high on March 31 2025.
+
+    Args:
+        blob_center (np.ndarray): 3-element array of blob center coordinates.
+        tilt (float): Tilt angle in radians (0 means orbit in xy plane).
+
+    Returns:
+        np.ndarray: 3x3 rotation matrix with columns [x', y', z'].
+    """
+    # x' axis: unit vector from star to blob center.
+    r_norm = np.linalg.norm(blob_center)
+    if r_norm == 0:
+        x_prime = np.array([1, 0, 0])
+    else:
+        x_prime = blob_center / r_norm
+    # Orbital angular momentum vector.
+    # For an orbit tilted by 'tilt' about the y-axis:
+    z_prime = np.array([np.sin(tilt), 0, np.cos(tilt)])
+    # y' axis:
+    y_prime = np.cross(z_prime, x_prime)
+    y_norm = np.linalg.norm(y_prime)
+    if y_norm == 0:
+        y_prime = np.array([0, 1, 0])
+    else:
+        y_prime = y_prime / y_norm
+    # Recompute z_prime for orthonormality.
+    z_prime = np.cross(x_prime, y_prime)
+    R = np.column_stack((x_prime, y_prime, z_prime))
+    return R
+
+
+def compute_blob_density(x: np.ndarray, y: np.ndarray, z: np.ndarray,
[…]

### 2025-04-02 drivers/sandbox/sandbox_profile_fit.py
stage sandbox

@@ -1,0 +1,58 @@
+import pandas as pd
+import numpy as np
+from aesthetic.plot import set_style
+from scipy.optimize import curve_fit
+import matplotlib.pyplot as plt
+
+# Set the plot style to 'science'
+set_style('science')
+
+# Load CSV data with pandas
+df = pd.read_csv('profile_check_inner.csv')
+
+x, y = df['xval'], df['yval']
+
+def single_gauss(x, a, mu, sigma):
+    return a * np.exp(-((x - mu)**2) / (2 * sigma**2))
+
+def double_gauss(x, a1, mu1, sigma1, a2, mu2, sigma2):
+    return a1*np.exp(-((x-mu1)**2) / (2*sigma1**2)) + a2*np.exp(-((x-mu2)**2) / (2*sigma2**2))
+
+# Initial parameter guesses:
+# Amplitudes are 0.5, means are 2 and 2.1 (ensuring at least 0.1 apart), and sigmas are 0.2.
+p0 = [0.5, 2.0, 0.2, 0.5, 2.1, 0.2]
+
+# Optionally, set bounds to ensure physically meaningful values:
+lower_bounds = [0, -5, 0.01, 0, -5, 0.01]
+upper_bounds = [1, 5, 0.4, 1, 5, 0.4]
+
+params, cov = curve_fit(double_gauss, x, y, p0=p0, bounds=(lower_bounds, upper_bounds))
+
+# Generate fitted curve data
+x_fit = np.linspace(np.min(x), np.max(x), 500)
+y_fit = double_gauss(x_fit, *params)
+
+# Plot the fitted curve with the original data
+y_component1 = single_gauss(x_fit, params[0], params[1], params[2])
+y_component2 = single_gauss(x_fit, params[3], params[4], params[5])
+
+plt.plot(x_fit, y_fit, label='Fitted Sum of Two Gaussians', alpha=0.5)
+plt.plot(x_fit, y_component1, '--', label='Gaussian Component 1', alpha=0.5)
+plt.plot(x_fit, y_component2, '--', label='Gaussian Component 2', alpha=0.5)
+plt.legend()
+
+print("Fitted parameters:")
+print(f"Amplitude1 = {params[0]:.4f}, Mean1 = {params[1]:.4f}, Sigma1 = {params[2]:.4f}")
[…]

### 2025-04-02 drivers/halpha_to_rv_timeseries.py
stage profile fitting to dynamic spectrum

@@ -1,0 +1,541 @@
+import pickle
+import os
+from os.path import join
+from scipy.ndimage import gaussian_filter1d
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+import numpy as np
+import pandas as pd
+from aesthetic.plot import savefig, set_style
+from scipy.optimize import curve_fit
+from typing import List, Optional, Tuple
+
+
+def double_gauss(x: np.ndarray, a1: float, mu1: float, sigma1: float,
+                 a2: float, mu2: float, sigma2: float) -> np.ndarray:
+    """Double Gaussian function.
+
+    Computes the sum of two Gaussian functions given the amplitudes,
+    means, and standard deviations.
+
+    Parameters:
+        x (np.ndarray): Independent variable.
+        a1 (float): Amplitude of the first Gaussian.
+        mu1 (float): Mean of the first Gaussian.
+        sigma1 (float): Standard deviation of the first Gaussian.
+        a2 (float): Amplitude of the second Gaussian.
+        mu2 (float): Mean of the second Gaussian.
+        sigma2 (float): Standard deviation of the second Gaussian.
+
+    Returns:
+        np.ndarray: Evaluated double Gaussian function.
+
+    Generated by ChatGPT o3-mini-high on April 1 2025.
+    """
+    return (a1 * np.exp(-((x - mu1)**2) / (2 * sigma1**2)) +
+            a2 * np.exp(-((x - mu2)**2) / (2 * sigma2**2)))
+
+
+def single_gauss(x: np.ndarray, a: float, mu: float, sigma: float) -> np.ndarray:
+    """Single Gaussian function.
+
+    Computes a single Gaussian function given its amplitude, mean, and
+    standard deviation.
+
+    Parameters:
+        x (np.ndarray): Independent variable.
+        a (float): Amplitude of the Gaussian.
+        mu (float): Mean of the Gaussian.
+        sigma (float): Standard deviation of the Gaussian.
+
+    Returns:
+        np.ndarray: Evaluated Gaussian function.
+
+    Generated by ChatGPT o3-mini-high on April 1 2025.
+    """
+    return a * np.exp(-((x - mu)**2) / (2 * sigma**2))
+
+
+def fit_double_gaussian(
+    x: np.ndarray,
+    y: np.ndarray,
+    x_fit: np.ndarray,
+    p0: List[float],
+    lower_bounds: Optional[List[float]] = None,
[…]

### 2025-04-03 paper/ms.tex
update

@@
 \usepackage{caption}
+\usepackage{rotating} % sidewaystable
 
@@
 condensations can sustain an optically thick component; the origin
-of the optically thick material and its microphysical opacity remain
+of this optically thick material and its microphysical opacity remain
 unclear.
@@
 % * keck/hires: behavior at v/veq<1
-The data in the H$\alpha$ line core are more complex.  At $|\Delta v /
+The H$\alpha$ line core is more complex.  At $|\Delta v /
 v_{\rm eq}|<1$, most observed H$\alpha$ photons come from the star's
@@
 Neither of these regions shows any notable variability.
+
+\subsection{Detailed Behavior of H$\alpha$: Model and Implications}\phantom{+}
+\label{subsec:halpha}
+
+\begin{figure}[!tp]
+  \centering
+  \includegraphics[width=0.5\textwidth]{figures/sf6.pdf}
+  \caption{Time-variable fit to H$\alpha$ line profiles.
+  {\it Left column:} Raw spectrum at each epoch $f_{\lambda}$ minus
+  the time-averaged spectrum $f_{\langle t \rangle}$ (as in
+  Figure~\ref{fig:spec}e).
+  Underplotted sinusoids are to guide the eye.
+  {\it Middle columns:} Model of emission from the inner clump (sum of
+  two gaussians) and the outer clump (single gaussian), plotted over
+  the data.
+  {\it Right column:} Residual of the left column after subtracting
+  the sum of the two middle columns, leaving variability in the line
+  core.  
+  Section~\ref{subsec:halpha} discusses the use of this model.
+  }
+  \label{fig:halphamodel}
+\end{figure}
+
+{\it A model for the time-dynamic H$\alpha$ spectrum}---While
+Figure~\ref{fig:spec} shows that clumps of circumstellar material
+exist around TIC~141146667, it would be valuable to quantify the exact
+orbital periods, velocities, and velocity dispersions of these clumps.
+These quantities can clarify the precision with which the
+spectroscopic period agrees with the photometric period, and also
+constrain the physical dimensions of the emitting region.
+
+Given that a full radiative transfer simulation was beyond our scope,
+we opted to construct a phenomenological model aimed at capturing 
+the emission from the circumstellar material.  We did this by
+fitting each spectral epoch with a multi-component
+gaussian, after having subtracted the time-average line profile as in
+Figure~\ref{fig:spec}e.  The results of this exercise are shown in
+Figure~\ref{fig:halphamodel}; details in its implementation and
+interpretation follow.
+
+To the implement the model, we assumed that the ``inner'' ($K_{\rm
+inner}$$\approx$2.5\,$v_{\rm eq}$) clump would be well-fit by a sum of
+two gaussians because it visually appears double-peaked in the raw
+data from $\phi$=0.15-0.35 and $\phi$=0.65-0.85
+(Figure~\ref{fig:spec}b).  We assumed the ``outer'' ($K_{\rm
+outer}$$\approx$3.9\,$v_{\rm eq}$) clump would be better fit by a
+single gaussian, based on its behavior from $\phi$=0.6-0.9.  Each
+gaussian component has three free parameters at each spectral epoch:
+the mean $\mu$, standard deviation $\sigma$, and amplitude $A$.
+Denote the two gaussians for the inner component $i=\{ 0, 1 \}$,
+and the single outer component with $i=2$.  Given the complexity of the
+line profile data (Figure~\ref{fig:halphamodel} left column), the
+likelihood function for this model is multimodal.  We therefore
+imposed the prior constraints that $A_i \sim \mathcal{U}[0,1]$,
+$\sigma_i/v_{\rm eq} \sim \mathcal{U}[0,1]$, and further assumed
+$K_i(t) \sim
+\mathcal{U}[
+  K_{\rm inner}\sin(\phi(t)) - v_{\rm eq},
+  K_{\rm inner}\sin(\phi(t)) + v_{\rm eq}
+]$
+for the inner two components, and
+$K_i(t) \sim
+\mathcal{U}[
+  K_{\rm outer}\sin(\phi(t) + \pi) - 2v_{\rm eq},
+  K_{\rm outer}\sin(\phi(t) + \pi) + 2v_{\rm eq}
+]$
+for the outer component.
+This latter assumption constrains the mean velocity of each component
+to be near the value suggested by visual inspection, but provides
+sufficient flexibility for the model to deviate from the assumption of
+a sinusoid if the data dictate such behavior.
+We fitted each component to the data {\it independently} using scipy's
+non-linear least squares \texttt{curve\_fit} method
+\cite{Virtanen2020}, and scaled the resulting parameter covariance
+matrix by a constant factor to match the sample variance of the
+residuals.
+The choice to fit the $i=\{ 0, 1 \}$, and $i=2$ components
+independently generally did not affect the results compared to if we
+have fit all three simultaneously, except for at $\phi=1.00$ (see
+Figure~\ref{fig:halphamodel}).
+
+The resulting mean velocities, widths, and amplitudes are given in
+Table~\ref{tab:halphamodelparams}.
+%FIXME TODO gotta get this table being better... and in particular
+%gotta not quite signal where there is nothing.  (mask out transits +
+%secondary eclipses....)
+
+The main benefit of this model is that it is
+sufficiently flexible to capture the observed variability in
+circumstellar emission, and
+
+quantify the exact
+orbital periods, velocities, and velocity dispersions of these clumps.
+
+Figure~\ref{fig:halphamodel}
+
+functions
+
+{\it Constraints on physical dimensions of emitting region}---
+
+IMPLICATIONS:
+The secondary eclipse of the `inner clump' at $\phi$$\approx$0.5 is not
+associated with a broadband flux dip.   The clump does not therefore
+contribute significant broadband emissivity across the entire TESS
+band; only in H$\alpha$.
 
@@
 
+\begin{sidewaystable}
+%\begin{table}
+  %\small
+  \footnotesize
+  \centering
+  \begin{tabular}{lccccccccc}
+  %\hline 
+  %\hline 
+  %Time [BJD$_{\rm TDB}$] & RV (\kms) & $\sigma_{\rm RV}$ (\kms) \\
+  % from
+  % results/halpha_to_rv_timerseries/multigauss_parametertable.tex
+  \hline
+   & Mean1 & Mean2 & Mean3 & Sigma1 & Sigma2 & Sigma3 & Amplitude1 & Amplitude2 & Amplitude3 \\
+  BTJD &  &  &  &  &  &  &  &  &  \\
+  \hline
+  3357.960099 & -0.725 $\pm$ 0.028 & -1.416 $\pm$ 0.026 & 0.177 $\pm$ 0.019 & 0.39 $\pm$ 0.03 & 0.18 $\pm$ 0.03 & 0.59 $\pm$ 0.02 & 0.51 $\pm$ 0.01 & 0.23 $\pm$ 0.04 & 0.29 $\pm$ 0.01 \\
+  3357.970746 & -0.192 $\pm$ 0.007 & 0.498 $\pm$ 0.010 & 0.100 $\pm$ 0.014 & 0.23 $\pm$ 0.01 & 0.24 $\pm$ 0.01 & 0.55 $\pm$ 0.01 & 0.50 $\pm$ 0.01 & 0.37 $\pm$ 0.01 & 0.42 $\pm$ 0.01 \\
+  3357.981672 & 0.895 $\pm$ 0.051 & 1.771 $\pm$ 0.076 & -1.470 $\pm$ 0.113 & 0.40 $\pm$ 0.02 & 0.40 $\pm$ 0.10 & 0.09 $\pm$ 0.11 & 0.67 $\pm$ 0.05 & 0.34 $\pm$ 0.04 & 0.03 $\pm$ 0.03 \\
+  3357.993524 & 1.536 $\pm$ 0.011 & 2.202 $\pm$ 0.015 & -3.787 $\pm$ 0.049 & 0.25 $\pm$ 0.01 & 0.29 $\pm$ 0.01 & 0.72 $\pm$ 0.05 & 0.55 $\pm$ 0.01 & 0.46 $\pm$ 0.01 & 0.05 $\pm$ 0.00 \\
+  3358.003594 & 1.974 $\pm$ 0.007 & 2.588 $\pm$ 0.006 & -2.749 $\pm$ 0.020 & 0.26 $\pm$ 0.01 & 0.22 $\pm$ 0.00 & 1.00 $\pm$ 0.02 & 0.64 $\pm$ 0.01 & 0.67 $\pm$ 0.01 & 0.43 $\pm$ 0.01 \\
+  3358.015249 & 2.027 $\pm$ 0.003 & 2.666 $\pm$ 0.003 & -2.370 $\pm$ 0.015 & 0.24 $\pm$ 0.00 & 0.20 $\pm$ 0.00 & 1.00 $\pm$ 0.01 & 0.62 $\pm$ 0.00 & 0.60 $\pm$ 0.00 & 0.56 $\pm$ 0.00 \\
+  3358.024971 & 1.790 $\pm$ 0.004 & 2.469 $\pm$ 0.006 & -2.138 $\pm$ 0.011 & 0.24 $\pm$ 0.00 & 0.26 $\pm$ 0.00 & 0.77 $\pm$ 0.01 & 0.53 $\pm$ 0.00 & 0.38 $\pm$ 0.00 & 0.31 $\pm$ 0.00 \\
+  3358.036522 & 0.584 $\pm$ 0.008 & 1.399 $\pm$ 0.009 & -1.584 $\pm$ 0.009 & 0.18 $\pm$ 0.01 & 0.40 $\pm$ 0.01 & 0.89 $\pm$ 0.01 & 0.35 $\pm$ 0.01 & 0.39 $\pm$ 0.00 & 0.62 $\pm$ 0.00 \\
+  3358.047668 & 0.328 $\pm$ 0.014 & 0.685 $\pm$ 0.010 & -0.969 $\pm$ 0.017 & 0.07 $\pm$ 0.01 & 0.13 $\pm$ 0.01 & 0.46 $\pm$ 0.02 & 0.14 $\pm$ 0.02 & 0.28 $\pm$ 0.02 & 0.52 $\pm$ 0.02 \\
+  3358.058824 & -0.646 $\pm$ 0.005 & -1.474 $\pm$ 0.066 & 0.891 $\pm$ 0.079 & 0.23 $\pm$ 0.00 & 0.25 $\pm$ 0.07 & 0.14 $\pm$ 0.08 & 0.51 $\pm$ 0.01 & 0.10 $\pm$ 0.01 & 0.09 $\pm$ 0.04 \\
+  3358.069519 & -0.388 $\pm$ 0.104 & -1.669 $\pm$ 0.023 & 2.646 $\pm$ 0.020 & 0.40 $\pm$ 0.07 & 0.40 $\pm$ 0.02 & 0.53 $\pm$ 0.02 & 0.47 $\pm$ 0.04 & 0.33 $\pm$ 0.01 & 0.22 $\pm$ 0.01 \\
+  3358.080468 & -1.748 $\pm$ 0.009 & -2.483 $\pm$ 0.010 & 3.526 $\pm$ 0.009 & 0.25 $\pm$ 0.01 & 0.33 $\pm$ 0.01 & 0.55 $\pm$ 0.01 & 0.28 $\pm$ 0.01 & 0.32 $\pm$ 0.00 & 0.32 $\pm$ 0.00 \\
+  3358.091255 & -2.119 $\pm$ 0.007 & -2.868 $\pm$ 0.007 & 3.960 $\pm$ 0.005 & 0.26 $\pm$ 0.01 & 0.23 $\pm$ 0.01 & 0.40 $\pm$ 0.01 & 0.34 $\pm$ 0.01 & 0.29 $\pm$ 0.01 & 0.39 $\pm$ 0.00 \\
+  3358.101671 & -2.019 $\pm$ 0.006 & -2.731 $\pm$ 0.008 & 3.758 $\pm$ 0.005 & 0.20 $\pm$ 0.01 & 0.24 $\pm$ 0.01 & 0.43 $\pm$ 0.01 & 0.29 $\pm$ 0.01 & 0.25 $\pm$ 0.01 & 0.23 $\pm$ 0.00 \\
+  3358.112713 & -1.581 $\pm$ 0.020 & -2.141 $\pm$ 0.043 & 2.867 $\pm$ 0.019 & 0.19 $\pm$ 0.02 & 0.29 $\pm$ 0.03 & 0.40 $\pm$ 0.02 & 0.18 $\pm$ 0.02 & 0.13 $\pm$ 0.01 & 0.12 $\pm$ 0.00 \\
+  3358.123928 & -0.624 $\pm$ 0.006 & -1.312 $\pm$ 0.076 & 0.824 $\pm$ 0.012 & 0.09 $\pm$ 0.01 & 0.22 $\pm$ 0.08 & 0.44 $\pm$ 0.01 & 0.18 $\pm$ 0.01 & 0.02 $\pm$ 0.01 & 0.32 $\pm$ 0.01 \\
+  3358.135236 & -0.012 $\pm$ 0.011 & -0.208 $\pm$ 0.012 & -0.192 $\pm$ 0.012 & 0.03 $\pm$ 0.01 & 0.11 $\pm$ 0.01 & 0.12 $\pm$ 0.01 & 0.12 $\pm$ 0.04 & 0.25 $\pm$ 0.02 & 0.25 $\pm$ 0.02 \\
+  3358.146555 & 1.007 $\pm$ 0.100 & 1.622 $\pm$ 0.048 & -1.789 $\pm$ 0.045 & 0.06 $\pm$ 0.11 & 0.31 $\pm$ 0.06 & 0.04 $\pm$ 0.05 & 0.02 $\pm$ 0.04 & 0.12 $\pm$ 0.02 & 0.05 $\pm$ 0.05 \\
+  3358.156693 & 1.603 $\pm$ 0.018 & 2.444 $\pm$ 0.024 & -4.408 $\pm$ 0.197 & 0.14 $\pm$ 0.02 & 0.23 $\pm$ 0.03 & 1.00 $\pm$ 0.17 & 0.14 $\pm$ 0.02 & 0.14 $\pm$ 0.01 & 0.05 $\pm$ 0.00 \\
+  3358.169147 & 1.543 $\pm$ 0.007 & 2.152 $\pm$ 0.013 & -3.885 $\pm$ 0.031 & 0.14 $\pm$ 0.01 & 0.39 $\pm$ 0.01 & 1.00 $\pm$ 0.04 & 0.23 $\pm$ 0.01 & 0.27 $\pm$ 0.00 & 0.10 $\pm$ 0.00 \\
+  3358.177978 & 1.588 $\pm$ 0.037 & 2.828 $\pm$ 0.005 & -4.378 $\pm$ 0.053 & 0.40 $\pm$ 0.03 & 0.02 $\pm$ 0.01 & 0.75 $\pm$ 0.06 & 0.33 $\pm$ 0.01 & 0.11 $\pm$ 0.03 & 0.12 $\pm$ 0.01 \\
+  \hline
+  \end{tabular}
+  \caption{Multi-gaussian model fit results to H$\alpha$ line profiles.}
+  \label{tab:halphamodelparams}
+%\end{table}
+\end{sidewaystable}
+
 \end{methods}

### 2025-04-03 paper/collect_figs.sh

@@ -30,3 +30,5 @@ cp $r/hrd/hrd_smalllim_dereddened.pdf figures/sf3.pdf
 cp $r/sed_fit/TIC_141146667/plots_irexcess/SED.pdf figures/sf4.pdf
 
 cp $r/lineevolnpanel/TIC141146667_j537_lineevolnpanel_removecosmic.pdf figures/sf5.pdf
+
+cp $r/halpha_to_rv_timerseries/halpha_stack_3clumps.pdf figures/sf6.pdf

### 2025-04-03 drivers/halpha_to_rv_timeseries.py
Hα->RV: latex & improvements

@@ -7,8 +7,10 @@ import matplotlib.cm as cm
 import numpy as np
 import pandas as pd
 from aesthetic.plot import savefig, set_style
+from cdips.utils.lcutils import p2p_rms
 from scipy.optimize import curve_fit
 from typing import List, Optional, Tuple
+from matplotlib import rcParams
 
 
 def double_gauss(x: np.ndarray, a1: float, mu1: float, sigma1: float,
@@ -62,7 +64,8 @@ def fit_double_gaussian(
     x_fit: np.ndarray,
     p0: List[float],
     lower_bounds: Optional[List[float]] = None,
-    upper_bounds: Optional[List[float]] = None
+    upper_bounds: Optional[List[float]] = None,
+    y_err: np.ndarray = None
 ) -> Tuple[np.ndarray, np.ndarray, np.ndarray, np.ndarray, np.ndarray, pd.DataFrame]:
     """Fit a double Gaussian model to data.
 
@@ -103,7 +106,8 @@ def fit_double_gaussian(
         upper_bounds = [1, 5, 0.4, 1, 5, 0.4]
 
     params, cov = curve_fit(double_gauss, x, y, p0=p0,
-                            bounds=(lower_bounds, upper_bounds))
+                            bounds=(lower_bounds, upper_bounds),
+                            sigma=y_err, absolute_sigma=False)
 
     y_fit = double_gauss(x_fit, *params)
     y_component1 = single_gauss(x_fit, params[0], params[1], params[2])
@@ -125,7 +129,8 @@ def fit_single_gaussian(
     x_fit: np.ndarray,
     p0: List[float],
     lower_bounds: Optional[List[float]] = None,
-    upper_bounds: Optional[List[float]] = None
+    upper_bounds: Optional[List[float]] = None,
+    y_err: np.ndarray = None
 ) -> Tuple[np.ndarray, np.ndarray, np.ndarray, pd.DataFrame]:
     """Fit a single Gaussian model to data.
 
@@ -163,7 +168,8 @@ def fit_single_gaussian(
 
     params, cov = curve_fit(
         single_gauss, x, y, p0=p0,
-        bounds=(lower_bounds, upper_bounds)
+        bounds=(lower_bounds, upper_bounds),
+        sigma=y_err, absolute_sigma=False
     )
     y_fit = single_gauss(x_fit, *params)
[…]

### 2025-04-03 drivers/fit_orbits.py
stage initial orbit fitter

@@ -1,0 +1,182 @@
+import pandas as pd
+import numpy as np
+import os
+from os.path import join
+from scipy.optimize import curve_fit
+import matplotlib.pyplot as plt
+
+def load_rvs(component_ix=None):
+
+    # innermost (~2veq) clump 
+    mask0 = [1,1,1,1,1,
+             1,1,1,0,0, #9 = phi 0.54
+             0,1,1,1,1,
+             0,0,1,1,1,   #16(start) = phi 0.93       
+             0]
+    # middle (~2.8veq) clump 
+    mask1 = [1,1,1,1,1,
+             1,1,1,1,0,
+             1,1,1,1,1,
+             0,0,1,1,1,
+             0]
+    # outer clump
+    # 8&9 : absorption cancelled out the emission??
+    mask2 = [0,0,0,0,1,
+             1,1,1,0,0, #10 = phi 0.54.  
+             1,1,1,1,1,
+             0,0,0,0,0, #16(start) = phi 0.93
+             0]
+
+    assert component_ix in [1,2,3]
+
+    if component_ix == 1:
+        mask = np.array(mask0).astype(bool)
+    elif component_ix == 2:
+        mask = np.array(mask1).astype(bool)
+    elif component_ix == 3:
+        mask = np.array(mask2).astype(bool)
+
+    csvpath = 'results/halpha_to_rv_timerseries/multigauss_parametervaltable.csv'
+    tdf = pd.read_csv(csvpath)
+    csvpath = 'results/halpha_to_rv_timerseries/multigauss_parameterunctable.csv'
+    tdf_unc = pd.read_csv(csvpath)
+
+    time = np.array(tdf.BTJD)
+    rv = np.array(tdf[f'Mean{component_ix}'])
+    rv_err = np.array(tdf[f'Sigma{component_ix}'])
+
+    time = time[mask]
+    rv = rv[mask]
+    rv_err = rv_err[mask]
+
+    return time, rv, rv_err
+
+def rv_circular(t, K, P, t0):
+    return K * np.sin(2*np.pi/P * (t - t0))
+
+def solve_kepler(M, e, tol=1e-6, max_iter=100):
+    E = M.copy() if isinstance(M, np.ndarray) else M
+    for _ in range(max_iter):
+        delta = (E - e*np.sin(E) - M) / (1 - e*np.cos(E))
+        E -= delta
+        if np.all(np.abs(delta) < tol):
+            break
+    return E
+
+def rv_eccentric(t, K, P, t_peri, e):
[…]

### 2025-04-03 paper/ms.tex
update

@@
 
-Given that a full radiative transfer simulation was beyond our scope,
+Given that a full radiative transfer simulation was outside our scope,
 we opted to construct a phenomenological model aimed at capturing 
@@
 ]$
-for the outer component.
-This latter assumption constrains the mean velocity of each component
-to be near the value suggested by visual inspection, but provides
-sufficient flexibility for the model to deviate from the assumption of
-a sinusoid if the data dictate such behavior.
-We fitted each component to the data {\it independently} using scipy's
-non-linear least squares \texttt{curve\_fit} method
-\cite{Virtanen2020}, and scaled the resulting parameter covariance
-matrix by a constant factor to match the sample variance of the
-residuals.
-The choice to fit the $i=\{ 0, 1 \}$, and $i=2$ components
-independently generally did not affect the results compared to if we
-have fit all three simultaneously, except for at $\phi=1.00$ (see
-Figure~\ref{fig:halphamodel}).
+for the outer component.  This latter assumption mitigates the
+multimodality of the likelihood by requiring the mean velocity of each
+component to be within a one or two $v_{\rm eq}$ of the time-variable
+sinusoid suggested by visual inspection.  We fitted each component to
+the data {\it independently} using scipy's non-linear least squares
+\texttt{curve\_fit} implementation \cite{Virtanen2020}, and scaled the
+resulting parameter covariance matrix by a constant factor to match
+the sample variance of the residuals.  The resulting means,
+amplitudes, and standard devations for each component are given in
+Extended Data Table~\ref{tab:halphamodelparams}.
+
+Caution is required in the interpretation of this model's results.
+The model at times overfits, because it targets the most significant
+spectral feature around the priors discussed above, and sometimes
+these features are not statistically significant.  During such
+spectral epochs, e.g.~the ``outer'' clump at $\phi$=1.07, the model is
+fitting noise, not signal.  
+At times the model underfits.  For instance, the sudden blue rise near
+$\phi$=0.2 is not well-matched by the functional form of a gaussian;
+the assumed functional form is one of convenience.
+A final point of caution is that the model fits the $i=\{ 0, 1 \}$,
+and $i=2$ components independently.  At $\phi=0.0$ and $1.0$,
+Figure~\ref{fig:halphamodel} suggests that this means the emission might
+hypothetically be from either the inner or outer components.  A
+physical interpretation however is that this is the phase during which
+the inner component is in transit, and the outer is in secondary
+occultation and blocked by the star.  At $\phi=0.0$, the double-peaked
+emission profile also matches that seen shortly afterward when the
+inner clump is viewed off-disk.  A physical interpretation of the
+model should therefore discard the results at this particular epoch
+for the outer clump.
+
+Taking these caveats into account, the results from Extended Data
+Table~\ref{tab:halphamodelparams} can be used to evaluate various
+models for the orbits.
+
+, and in particular to assess their periods and
+semi-amplitudes.
 
@@
   \hline
-   & Mean1 & Mean2 & Mean3 & Sigma1 & Sigma2 & Sigma3 & Amplitude1 & Amplitude2 & Amplitude3 \\
-  BTJD &  &  &  &  &  &  &  &  &  \\
+  BTJD & $\mu_0$ & $\mu_1$ & $\mu_2$ & $\sigma_0$ & $\sigma_1$ & $\sigma_2$ & $A_0$ & $A_1$ & $A_2$ \\
   \hline
@@
   \end{tabular}
-  \caption{Multi-gaussian model fit results to H$\alpha$ line profiles.}
+  \caption{Multi-gaussian model fit results to H$\alpha$ line
+  profiles.  The results should be treated with caution; only a
+  subset of spectral epochs provide statistically significant
+  detections of the circumstellar emission (see Extended Data
+  Figure~\ref{fig:halphamodel}).}
   \label{tab:halphamodelparams}

### 2025-04-03 drivers/fit_orbits.py
update fit_orbits

@@ -4,27 +4,36 @@ import os
 from os.path import join
 from scipy.optimize import curve_fit
 import matplotlib.pyplot as plt
+from aesthetic.plot import set_style, savefig
 
-def load_rvs(component_ix=None):
+def load_rvs(component_ix=None, applymask=True):
 
     # innermost (~2veq) clump 
     mask0 = [1,1,1,1,1,
-             1,1,1,0,0, #9 = phi 0.54
+             1,1,0,0,0, #9 = phi 0.54
              0,1,1,1,1,
-             0,0,1,1,1,   #16(start) = phi 0.93       
+             0,0,1,1,0,   #16(start) = phi 0.93       
              0]
     # middle (~2.8veq) clump 
     mask1 = [1,1,1,1,1,
              1,1,1,1,0,
              1,1,1,1,1,
-             0,0,1,1,1,
+             0,0,1,1,0,
              0]
     # outer clump
     # 8&9 : absorption cancelled out the emission??
+    
+    # based on "is there a good signal"?
     mask2 = [0,0,0,0,1,
-             1,1,1,0,0, #10 = phi 0.54.  
+             1,1,1,0,1, #9 = phi 0.54.  
              1,1,1,1,1,
              0,0,0,0,0, #16(start) = phi 0.93
+             0]
+    # based on sinusoid
+    mask2 = [0,0,0,0,0,
+             0,0,0,0,1, #9 = phi 0.54.  
+             1,1,1,1,1,
+             1,0,0,0,0, #16(start) = phi 0.93
              0]
 
     assert component_ix in [1,2,3]
@@ -45,9 +54,10 @@ def load_rvs(component_ix=None):
     rv = np.array(tdf[f'Mean{component_ix}'])
     rv_err = np.array(tdf[f'Sigma{component_ix}'])
 
-    time = time[mask]
-    rv = rv[mask]
-    rv_err = rv_err[mask]
+    if applymask:
+        time = time[mask]
+        rv = rv[mask]
+        rv_err = rv_err[mask]
 
     return time, rv, rv_err
 
@@ -93,8 +103,10 @@ def save_fit_table(filename, params, perr, red_chi2, bic, param_names):
 def main():
     circ_summary = []
     ecc_summary = []
+    all_fits = []  # new: store data for combined plot
     for ix in [1, 2, 3]:
         time, rv, rv_err = load_rvs(component_ix=ix)
+        _time, _rv, _rv_err = load_rvs(component_ix=ix, applymask=False)
         
         # Estimate initial parameters
[…]

### 2025-04-03 paper/ms.tex
update

@@
   Figure~\ref{fig:spec}e).
-  Underplotted sinusoids are to guide the eye.
+  Underplotted sinusoids are not fits; they are meant to guide the eye.
   {\it Middle columns:} Model of emission from the inner clump (sum of
@@
 The model at times overfits, because it targets the most significant
-spectral feature around the priors discussed above, and sometimes
-these features are not statistically significant.  During such
-spectral epochs, e.g.~the ``outer'' clump at $\phi$=1.07, the model is
-fitting noise, not signal.  
-At times the model underfits.  For instance, the sudden blue rise near
-$\phi$=0.2 is not well-matched by the functional form of a gaussian;
-the assumed functional form is one of convenience.
-A final point of caution is that the model fits the $i=\{ 0, 1 \}$,
-and $i=2$ components independently.  At $\phi=0.0$ and $1.0$,
-Figure~\ref{fig:halphamodel} suggests that this means the emission might
-hypothetically be from either the inner or outer components.  A
-physical interpretation however is that this is the phase during which
-the inner component is in transit, and the outer is in secondary
-occultation and blocked by the star.  At $\phi=0.0$, the double-peaked
-emission profile also matches that seen shortly afterward when the
-inner clump is viewed off-disk.  A physical interpretation of the
-model should therefore discard the results at this particular epoch
-for the outer clump.
-
-Taking these caveats into account, the results from Extended Data
-Table~\ref{tab:halphamodelparams} can be used to evaluate various
-models for the orbits.
-
-, and in particular to assess their periods and
-semi-amplitudes.
+spectral feature around each component's prior, and sometimes these
+features are not statistically significant.  During such spectral
+epochs, e.g.~the ``outer'' clump at $\phi$=1.07, the model fits noise,
+not signal.  At other times, the model underfits.  For instance, the
+sudden blue rise near $\phi$=0.2 is not well-described by the
+functional form of a gaussian; the assumed functional form is one of
+convenience.  A final point of caution is that the model fits the
+$i=\{ 0, 1 \}$, and $i=2$ components independently.  At $\phi=0.0$ and
+$1.0$, Figure~\ref{fig:halphamodel} suggests that this means the
+emission might hypothetically be from either the inner or outer
+components.  A physical interpretation however is that this is the
+phase during which the inner component is in transit, and the outer is
+in secondary occultation and blocked by the star.  At $\phi=0.0$, the
+double-peaked emission profile also matches that seen shortly
+afterward when the inner clump is viewed off-disk.  A physical
+interpretation of the model should therefore discard the results at
+this particular epoch for the outer clump.
+
+\begin{figure}[!tp]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/sf7.pdf}
+  \caption{Example orbits fit to velocities extracted from gaussian
+  profile fits in Figure~\ref{fig:halphamodel}.
+  Each marker represents the measured best-fit mean and its best-fit
+  standard deviation at a given epoch.
+  Solid circles were used in the sinusoidal fits; transparent X markers
+  were excluded due to various concerns about their epoch-by-epoch
+  interpretation (see text).  The main purpose of this exercise was to
+  quantify the orbital periods and semi-amplitudes of the
+  circumstellar clumps.  The inner double-peaked clump is shown in
+  orange blue; the outer clump is shown in green.}
+  \label{fig:orbits}
+\end{figure}
+
+Taking these caveats into account, we used the results from Extended
+Data Table~\ref{tab:halphamodelparams} to evaluate various models for
+the orbits.
+Our main goal in this exercise was to quantify the orbital periods,
+velocities, and velocity dispersions of these clumps.
+Figure~\ref{fig:orbitmodel} shows some representative results for the
+circular orbit case.
+For
 

### 2025-04-03 paper/collect_figs.sh

@@ -32,3 +32,5 @@ cp $r/sed_fit/TIC_141146667/plots_irexcess/SED.pdf figures/sf4.pdf
 cp $r/lineevolnpanel/TIC141146667_j537_lineevolnpanel_removecosmic.pdf figures/sf5.pdf
 
 cp $r/halpha_to_rv_timerseries/halpha_stack_3clumps.pdf figures/sf6.pdf
+
+cp $r/halpha_to_rv_timerseries/combined_circular_fit.pdf figures/sf7.pdf

### 2025-04-03 drivers/fit_orbits.py
WIP: stage broken numpyro mcmc orbit fitting

@@ -5,6 +5,12 @@ from os.path import join
 from scipy.optimize import curve_fit
 import matplotlib.pyplot as plt
 from aesthetic.plot import set_style, savefig
+import jax
+import jax.numpy as jnp
+import numpyro
+from numpyro.infer import MCMC, NUTS
+import numpyro.distributions as dist
+numpyro.set_host_device_count(2)
 
 def load_rvs(component_ix=None, applymask=True):
 
@@ -52,7 +58,8 @@ def load_rvs(component_ix=None, applymask=True):
 
     time = np.array(tdf.BTJD)
     rv = np.array(tdf[f'Mean{component_ix}'])
-    rv_err = np.array(tdf[f'Sigma{component_ix}'])
+    #rv_err = np.array(tdf[f'Sigma{component_ix}'])
+    rv_err = np.array(tdf_unc[f'Mean{component_ix}'])
 
     if applymask:
         time = time[mask]
@@ -79,6 +86,25 @@ def rv_eccentric(t, K, P, t_peri, e):
     f = 2 * np.arctan(np.sqrt((1+e)/(1-e)) * np.tan(E/2))
     return K * (np.cos(f) + e)  # assuming ω=0
 
+# NEW: JAX-compatible functions for use in numpyro models
+def rv_circular_jax(t, K, P, t0):
+    return K * jnp.sin(2 * jnp.pi / P * (t - t0))
+
+def solve_kepler_jax(M, e, tol=1e-6, max_iter=100):
+    E = M
+    for _ in range(max_iter):
+        delta = (E - e * jnp.sin(E) - M) / (1 - e * jnp.cos(E))
+        E = E - delta
+        if jnp.all(jnp.abs(delta) < tol):
+            break
+    return E
+
+def rv_eccentric_jax(t, K, P, t_peri, e):
+    M = 2 * jnp.pi / P * (t - t_peri)
+    E = solve_kepler_jax(M, e)
+    f = 2 * jnp.arctan(jnp.sqrt((1+e)/(1-e)) * jnp.tan(E/2))
+    return K * (jnp.cos(f) + e)
+
 def compute_stats(model, t, rv, rv_err, popt):
     fit = model(t, *popt)
     residuals = rv - fit
@@ -100,7 +126,56 @@ def save_fit_table(filename, params, perr, red_chi2, bic, param_names):
     df['BIC'] = bic
     df.to_csv(filename, index=False)
 
-def main():
[…]

### 2025-04-03 drivers/fit_orbits.py
least squares: add red chi2 scaling

@@ -182,6 +182,9 @@ def main(fittingstyle='leastsquares'):
     for ix in [1, 2, 3]:
         time, rv, rv_err = load_rvs(component_ix=ix)
         _time, _rv, _rv_err = load_rvs(component_ix=ix, applymask=False)
+        # NEW: store original error arrays for scaling separately in each fit
+        original_rv_err = rv_err.copy()
+        original__rv_err = _rv_err.copy()
         
         # Estimate initial parameters
         K0 = (np.max(rv) - np.min(rv)) / 2
@@ -205,14 +208,20 @@ def main(fittingstyle='leastsquares'):
         else:
             raise ValueError("Invalid fittingstyle. Choose 'leastsquares' or 'mcmc'.")
         
+        # Compute stats and scale errors for circular fit (leastsquares only)
         perr_circ = np.sqrt(np.diag(pcov_circ))
-        red_chi2_circ, bic_circ = compute_stats(rv_circular, time, rv, rv_err, popt_circ)
-        
+        red_chi2_circ, bic_circ = compute_stats(rv_circular, time, rv, original_rv_err, popt_circ)
+        if fittingstyle == 'leastsquares':
+            scale_circ = np.sqrt(red_chi2_circ) if red_chi2_circ > 0 else 1.0
+            rv_err = original_rv_err * scale_circ
+            perr_circ = perr_circ * scale_circ
+            red_chi2_circ = 1.0
         # Save circular fit table
         circ_csv = join('results/halpha_to_rv_timerseries', f'circular_fit_component_{ix}.csv')
         param_names_circ = ['K', 'P', 't0']
         save_fit_table(circ_csv, popt_circ, perr_circ, red_chi2_circ, bic_circ, param_names_circ)
         
+        # Append data for combined plot (use scaled _rv_err for consistency)
         all_fits.append({
             'ix': ix,
             'time': time,
@@ -220,7 +229,7 @@ def main(fittingstyle='leastsquares'):
             'rv_err': rv_err,
             '_time': _time,
             '_rv': _rv,
-            '_rv_err': _rv_err,
+            '_rv_err': original__rv_err * (scale_circ if fittingstyle=='leastsquares' else 1.0),
             'popt_circ': popt_circ
         })
         
@@ -250,7 +259,7 @@ def main(fittingstyle='leastsquares'):
         e0 = 0.1
[…]

### 2025-04-03 drivers/fit_orbits.py
fit_orbits mcmc jitter helped

@@ -86,7 +86,7 @@ def rv_eccentric(t, K, P, t_peri, e):
     f = 2 * np.arctan(np.sqrt((1+e)/(1-e)) * np.tan(E/2))
     return K * (np.cos(f) + e)  # assuming ω=0
 
-# NEW: JAX-compatible functions for use in numpyro models
+# JAX-compatible functions for use in numpyro models
 def rv_circular_jax(t, K, P, t0):
     return K * jnp.sin(2 * jnp.pi / P * (t - t0))
 
@@ -131,10 +131,11 @@ def model_circular(time, rv_err, rv_obs):
     K = numpyro.sample('K', dist.Uniform(0.0, 6.0))
     P = numpyro.sample('P', dist.Uniform(2/24, 6/24))
     t0 = numpyro.sample('t0', dist.Uniform(time.min(), time.max()))
-    # CHANGED: use JAX-based function
+    jitter = numpyro.sample('jitter', dist.Exponential(1.0))
     mu = rv_circular_jax(time, K, P, t0)
+    effective_err = jnp.sqrt(rv_err**2 + jitter**2)  # Add jitter in quadrature
     with numpyro.plate('data', len(time)):
-        numpyro.sample('obs', dist.Normal(mu, rv_err), obs=rv_obs)
+        numpyro.sample('obs', dist.Normal(mu, effective_err), obs=rv_obs)
 
 def mcmc_fit_circular(time, rv, rv_err, rng_key=None, num_warmup=1000, num_samples=2000, num_chains=2):
     if rng_key is None:
@@ -144,7 +145,6 @@ def mcmc_fit_circular(time, rv, rv_err, rng_key=None, num_warmup=1000, num_sampl
     mcmc.run(rng_key, time=time, rv_err=rv_err, rv_obs=rv)
     mcmc.print_summary()
     samples = mcmc.get_samples()
-    # changed code: convert traced arrays to float
     popt = np.asarray([samples['K'].mean(), samples['P'].mean(), samples['t0'].mean()], dtype=float)
     params = np.vstack([samples['K'], samples['P'], samples['t0']])
     pcov = np.cov(params)
@@ -156,10 +156,11 @@ def model_eccentric(time, rv_err, rv_obs):
     P = numpyro.sample('P', dist.Uniform(2/24, 6/24))
     t_peri = numpyro.sample('t_peri', dist.Uniform(time.min(), time.max()))
     e = numpyro.sample('e', dist.Uniform(0.0, 1.0))
-    # CHANGED: use JAX-based function
[…]

### 2025-04-03 drivers/fit_orbits.py
fit_orbits mcmc viz jitter

@@ -145,10 +145,36 @@ def mcmc_fit_circular(time, rv, rv_err, rng_key=None, num_warmup=1000, num_sampl
     mcmc.run(rng_key, time=time, rv_err=rv_err, rv_obs=rv)
     mcmc.print_summary()
     samples = mcmc.get_samples()
-    popt = np.asarray([samples['K'].mean(), samples['P'].mean(), samples['t0'].mean()], dtype=float)
+    # compute mean jitter parameter from the samples
+    jitter_circ = np.asarray(samples['jitter']).mean()
+    popt = np.asarray([
+        samples['K'].mean(),
+        samples['P'].mean(),
+        samples['t0'].mean()
+    ], dtype=float)
     params = np.vstack([samples['K'], samples['P'], samples['t0']])
     pcov = np.cov(params)
-    return popt, pcov
+    return popt, pcov, jitter_circ
+
+def mcmc_fit_eccentric(time, rv, rv_err, rng_key=None, num_warmup=1000, num_samples=2000, num_chains=2):
+    if rng_key is None:
+        rng_key = jax.random.PRNGKey(1)
+    kernel = NUTS(model_eccentric)
+    mcmc = MCMC(kernel, num_warmup=num_warmup, num_samples=num_samples, num_chains=num_chains)
+    mcmc.run(rng_key, time=time, rv_err=rv_err, rv_obs=rv)
+    mcmc.print_summary()
+    samples = mcmc.get_samples()
+    # compute mean jitter parameter from the samples
+    jitter_ecc = np.asarray(samples['jitter']).mean()
+    popt = np.asarray([
+        samples['K'].mean(),
+        samples['P'].mean(),
+        samples['t_peri'].mean(),
+        samples['e'].mean()
+    ], dtype=float)
+    params = np.vstack([samples['K'], samples['P'], samples['t_peri'], samples['e']])
+    pcov = np.cov(params)
+    return popt, pcov, jitter_ecc
 
 def model_eccentric(time, rv_err, rv_obs):
     # Priors: K Uniform(0,6), P Uniform(2/24,6/24), t_peri Uniform(min(time),max(time)), e Uniform(0,1)
@@ -161,19 +187,6 @@ def model_eccentric(time, rv_err, rv_obs):
     effective_err = jnp.sqrt(rv_err**2 + jitter**2)  # Add jitter in quadrature
     with numpyro.plate('data', len(time)):
         numpyro.sample('obs', dist.Normal(mu, effective_err), obs=rv_obs)
-
[…]

### 2025-04-03 drivers/fit_orbits.py
mcmc: looks good

@@ -154,7 +154,7 @@ def mcmc_fit_circular(time, rv, rv_err, rng_key=None, num_warmup=1000, num_sampl
     ], dtype=float)
     params = np.vstack([samples['K'], samples['P'], samples['t0']])
     pcov = np.cov(params)
-    return popt, pcov, jitter_circ
+    return popt, pcov, jitter_circ, samples
 
 def mcmc_fit_eccentric(time, rv, rv_err, rng_key=None, num_warmup=1000, num_samples=2000, num_chains=2):
     if rng_key is None:
@@ -214,7 +214,7 @@ def main(fittingstyle='leastsquares'):
                 continue
         elif fittingstyle == 'mcmc':
             try:
-                popt_circ, pcov_circ, jitter_circ = mcmc_fit_circular(time, rv, rv_err)
+                popt_circ, pcov_circ, jitter_circ, samples = mcmc_fit_circular(time, rv, rv_err)
             except Exception as e:
                 print(f"Component {ix} MCMC circular fit failed: {e}")
                 continue
@@ -253,7 +253,9 @@ def main(fittingstyle='leastsquares'):
             '_time': _time,
             '_rv': _rv,
             '_rv_err': _rv_err,
-            'popt_circ': popt_circ
+            'popt_circ': popt_circ,
+            # For MCMC, store the posterior samples for plotting draws.
+            **({'samples': samples} if fittingstyle=='mcmc' else {})
         })
         
         t_fit = np.linspace(time.min(), time.max(), 1000)
@@ -334,6 +336,7 @@ def main(fittingstyle='leastsquares'):
     df_ecc = pd.DataFrame(ecc_summary)
     df_ecc.to_csv(join('results/halpha_to_rv_timerseries', 'eccentric_summary.csv'), index=False)
     
+    # FINAL VISUALIZATION PLOT
     set_style('science')
     f = 0.85
     fig, ax = plt.subplots(figsize=(f*3.5, f*3))
@@ -345,13 +348,20 @@ def main(fittingstyle='leastsquares'):
         _t = fit['_time'][mask]
         _rv = fit['_rv'][mask]
         _rv_err = fit['_rv_err'][mask]
-        popt = fit['popt_circ']
         c = f"C{ix}"
[…]

### 2025-04-04 drivers/fit_orbits.py
minor

@@ -364,8 +364,8 @@ def main(fittingstyle='leastsquares'):
                 ax.plot(fn(t_fit), rv_circular(t_fit, *draw), '-', c=c, zorder=-2, alpha=0.3, lw=0.4)
     ax.set_ylim([-4.9, 4.9])
     ax.set_xlim([-0.22, 5.42])
-    ax.set_xlabel('Time [hours]')
-    ax.set_ylabel('RV [v$_{\\mathrm{eq}}$]')
+    ax.set_xlabel('Time from start [hours]')
+    ax.set_ylabel('Clump RV [v$_{\\mathrm{eq}}$]')
     combined_plot_path = join('results/halpha_to_rv_timerseries', 'combined_circular_fit.png')
     savefig(fig, combined_plot_path)
     plt.clf()

### 2025-04-04 paper/ms.tex
update

--- 2025-04-03 paper/ms.tex
@@
 $\sigma_i/v_{\rm eq} \sim \mathcal{U}[0,1]$, and further assumed
-$K_i(t) \sim
+$\mu_i(t) \sim
 \mathcal{U}[
@@
 for the inner two components, and
-$K_i(t) \sim
+$\mu_2(t) \sim
 \mathcal{U}[
@@
 ]$
-for the outer component.
-This latter assumption constrains the mean velocity of each component
-to be near the value suggested by visual inspection, but provides
-sufficient flexibility for the model to deviate from the assumption of
-a sinusoid if the data dictate such behavior.
-We fitted each component to the data {\it independently} using scipy's
-non-linear least squares \texttt{curve\_fit} method
-\cite{Virtanen2020}, and scaled the resulting parameter covariance
-matrix by a constant factor to match the sample variance of the
-residuals.
-The choice to fit the $i=\{ 0, 1 \}$, and $i=2$ components
-independently generally did not affect the results compared to if we
-have fit all three simultaneously, except for at $\phi=1.00$ (see
-Figure~\ref{fig:halphamodel}).
-
-The resulting mean velocities, widths, and amplitudes are given in
-Table~\ref{tab:halphamodelparams}.
-%FIXME TODO gotta get this table being better... and in particular
-%gotta not quite signal where there is nothing.  (mask out transits +
-%secondary eclipses....)
-
-The main benefit of this model is that it is
-sufficiently flexible to capture the observed variability in
-circumstellar emission, and
-
-quantify the exact
-orbital periods, velocities, and velocity dispersions of these clumps.
-
-Figure~\ref{fig:halphamodel}
-
-functions
+for the outer component.  This prior on the means mitigates the
+multimodality of the likelihood by requiring the mean velocity of each
+component to be within a one or two $v_{\rm eq}$ of the time-variable
+sinusoid suggested by visual inspection.  We fitted each component to
+the data {\it independently} using scipy's non-linear least squares
+\texttt{curve\_fit} implementation \cite{Virtanen2020}, and scaled the
+resulting parameter covariance matrix by a constant factor to match
+the sample variance of the residuals.  The resulting means,
+amplitudes, and standard deviations for each component are given in
+Extended Data Table~\ref{tab:halphamodelparams}.
+
+Caution is required in interpreting this model's results.  At times
+the model overfits, because sometimes the most significant spectral
+feature around any component's prior is not statistically significant.
+During such spectral epochs, e.g.~the ``outer'' clump at $\phi$=1.07,
+the model fits noise, not signal.  At other times, the model
+underfits.  For instance, the sudden blue rise near $\phi$=0.2 is not
+well-described by a gaussian; the assumed functional form is one of
+convenience.  Finally, the model fits the $i=\{ 0, 1 \}$, and $i=2$
+components independently.  At $\phi=0.0$ and $1.0$,
+Figure~\ref{fig:halphamodel} suggests that the emission
+might come from either the inner or outer components.
+Physically however, at this time the inner component
+is in transit, and the outer component is in secondary eclipse and
+would likely be blocked by the star.  At $\phi=0.0$, the double-peaked
+emission profile also matches that seen shortly afterward (at
+$\phi$=0.14) when the
+inner clump is viewed off-disk.  A physical interpretation of the
+model should therefore discard the outer clump results at this
+particular epoch.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/sf7.pdf}
+  \caption{Orbits fit to mean radial velocities (RVs) extracted from 
+  H$\alpha$ profile fits in Figure~\ref{fig:halphamodel}.
+  Each marker represents the measured best-fit mean at a given epoch.
+  Solid circles were used in the fits; transparent X markers
+  were excluded due to concerns about their epoch-by-epoch
+  interpretation (see text).  The purpose of this exercise was to
+  quantify the orbital periods and semi-amplitudes of the
+  circumstellar clumps.  The inner double-peaked clump is shown in
+  orange and blue; the outer clump is shown in green.  Five draws from
+  each posterior probability distribution are plotted.}
+  \label{fig:orbits}
+\end{figure}
+
+Taking these caveats into account, we used the results from Extended
+Data Table~\ref{tab:halphamodelparams} to evaluate various models for
+the orbits.  Our main goal in this exercise was to quantify the
+orbital periods and velocity semi-amplitudes of the clumps.
+Figure~\ref{fig:orbits} shows representative results for the
+circular orbit case; we found no reason to extend the exercise to
+eccentric orbits.
+Based on visual inspection of the line profile fits, we manually excluded 
+epochs where we do not believe our gaussian profile fitting provided a
+reliable representation of the circumstellar emission.  We then performed
+the orbit fits using NumPyro to sample over the Gaussian likelihood with the
+NUTS algorithm \cite{Phan2019}.  When performing the fits, we adopted
+the uncertainties on each estimated mean radial velocity value, and
+added a jitter term in quadrature to inflate these nominal measurement
+uncertainties.  This procedure yielded period and semi-amplitude
+values for circular orbits of
+$P_0$=$3.92\pm0.03$\,hr, $K_0/v_{\rm eq}$=2.07$\pm$0.04;
+$P_1$=$3.92\pm0.06$\,hr, $K_1/v_{\rm eq}$=2.88$\pm$0.10;
+and $P_2$=$3.35\pm0.35$\,hr, $K_1/v_{\rm eq}$=4.16$\pm$0.56.
+The periods for the inner double-peaked clump are consistent
+with the photometric 3.930$\pm$0.001\,hr period to a precision of
+about two minutes.
+The ``period'' for the outer clump is more ambiguous because the
+H$\alpha$ data only support the idea of a periodic orbit of material
+well-fit by gaussian emission from $\phi$$\approx$0.5-1.0.
+From $\phi$=0-0.2, there is no detectable emission,
+and from $\phi$=0.2-0.4, the suddenly-detectable emission spans
+1-4\,$v_{\rm eq}$ without taking a clear gaussian shape.
+While the outer-most edge of the $\phi$=0.2-0.4 emission provides a
+closer match to the expectation of a circular orbit, 
+the idea of invoking a particular functional form for this component 
+seems fine-tuned.
+We instead emphasize that although this emission is present, 
+its variability in time is poorly explained by the idea of a
+stable, long-lived clump of material.
+Although additional observations would be needed to conclusively determine whether or not 
+this component of the system
+is long-lived, the lack of any photometric variability in the TESS
+data during its expected transits might suggest that it is not.
 
 {\it Constraints on physical dimensions of emitting region}---
+%TODO FIXME TODO FIXME
 
@@
   \end{tabular}
-  \caption{TIC~141146667 radial velocities relative to the systemic velocity.}
+  \caption{TIC~141146667 radial velocities relative to the systemic
+  velocity based on the 7699\,\AA\ resonance line and TiO bandheads.}
   \label{tab:rv}
@@
   \end{tabular}
-  \caption{Multi-gaussian model fit results to H$\alpha$ line profiles.}
+  \caption{Best-fit parameters from multi-gaussian model fit to H$\alpha$ line
+  profiles.  These results should be treated with caution; only a
+  subset of the spectral epochs provided statistically significant
+  detections of the circumstellar emission (see Extended Data
+  Figure~\ref{fig:halphamodel}).}
   \label{tab:halphamodelparams}

### 2025-04-04 paper/ms.tex
update

@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/sf6.pdf}
+  \includegraphics[width=0.55\textwidth]{figures/sf6.pdf}
   \caption{Time-variable fit to H$\alpha$ line profiles.
@@
   H$\alpha$ profile fits in Figure~\ref{fig:halphamodel}.
-  Each marker represents the measured best-fit mean at a given epoch.
-  Solid circles were used in the fits; transparent X markers
-  were excluded due to concerns about their epoch-by-epoch
-  interpretation (see text).  The purpose of this exercise was to
-  quantify the orbital periods and semi-amplitudes of the
-  circumstellar clumps.  The inner double-peaked clump is shown in
+  Radial velocities on the vertical axis are in units of the
+  equatorial velocity, $v_{\rm eq}$=130\,\kms.
+  Each marker denotes the best-fit mean at a given epoch.
+  Solid circles were adopted in the fits; transparent X markers
+  were excluded due to concerns about their reliability
+  (see text).  The inner double-peaked clump is shown in
   orange and blue; the outer clump is shown in green.  Five draws from
-  each posterior probability distribution are plotted.}
+  each posterior probability distribution are shown.}
   \label{fig:orbits}
@@
 
-Taking these caveats into account, we used the results from Extended
+Accounting for these caveats, we used the results from Extended
 Data Table~\ref{tab:halphamodelparams} to evaluate various models for
-the orbits.  Our main goal in this exercise was to quantify the
-orbital periods and velocity semi-amplitudes of the clumps.
-Figure~\ref{fig:orbits} shows representative results for the
-circular orbit case; we found no reason to extend the exercise to
-eccentric orbits.
-Based on visual inspection of the line profile fits, we manually excluded 
-epochs where we do not believe our gaussian profile fitting provided a
-reliable representation of the circumstellar emission.  We then performed
-the orbit fits using NumPyro to sample over the Gaussian likelihood with the
-NUTS algorithm \cite{Phan2019}.  When performing the fits, we adopted
-the uncertainties on each estimated mean radial velocity value, and
-added a jitter term in quadrature to inflate these nominal measurement
-uncertainties.  This procedure yielded period and semi-amplitude
-values for circular orbits of
+the orbits.  Our main goal was to quantify the orbital periods and
+velocity semi-amplitudes of the clumps.
+Figure~\ref{fig:orbits} shows representative results for the case of a circular
+orbit; eccentric orbits yielded similar results.  Based on visual
+inspection of Extended Data Figure~\ref{fig:halphamodel}, we manually excluded
+epochs when our gaussian profile fitting failed to either detect or
+else adequately represent the circumstellar emission.  We then used
+NumPyro to sample the Gaussian likelihood for a Keplerian orbit
+with the NUTS algorithm \cite{Phan2019}.  We used the measurement
+uncertainties from each estimated mean radial velocity value and
+included an additional jitter term in quadrature.  This procedure
+yielded orbital periods and semi-amplitudes of
 $P_0$=$3.92\pm0.03$\,hr, $K_0/v_{\rm eq}$=2.07$\pm$0.04;
@@
 and $P_2$=$3.35\pm0.35$\,hr, $K_1/v_{\rm eq}$=4.16$\pm$0.56.
-The periods for the inner double-peaked clump are consistent
-with the photometric 3.930$\pm$0.001\,hr period to a precision of
-about two minutes.
-The ``period'' for the outer clump is more ambiguous because the
+The periods for the inner double-peaked clump are consistent with the
+photometric $3.930\pm0.001$\,hr period within a precision of two
+minutes.  The ``period'' for the outer clump is ambiguous because the
 H$\alpha$ data only support the idea of a periodic orbit of material
-well-fit by gaussian emission from $\phi$$\approx$0.5-1.0.
-From $\phi$=0-0.2, there is no detectable emission,
-and from $\phi$=0.2-0.4, the suddenly-detectable emission spans
-1-4\,$v_{\rm eq}$ without taking a clear gaussian shape.
-While the outer-most edge of the $\phi$=0.2-0.4 emission provides a
-closer match to the expectation of a circular orbit, 
-the idea of invoking a particular functional form for this component 
-seems fine-tuned.
-We instead emphasize that although this emission is present, 
-its variability in time is poorly explained by the idea of a
-stable, long-lived clump of material.
-Although additional observations would be needed to conclusively determine whether or not 
-this component of the system
-is long-lived, the lack of any photometric variability in the TESS
-data during its expected transits might suggest that it is not.
-
-{\it Constraints on physical dimensions of emitting region}---
+well-fit by gaussian emission from $\phi$$\approx$0.5-1.0.  From
+$\phi$=0-0.2, there is no detectable emission, and from
+$\phi$=0.2-0.4, the emission spans 1-4\,$v_{\rm eq}$ without taking a
+clear gaussian shape.  While the outer-most edge of this
+$\phi$=0.2-0.4 emission provides a plausible match to the expectation
+of a circular orbit, the idea of invoking a particular functional form
+for this component seems fine-tuned.  We instead emphasize that
+although this emission is present, its variability in time is poorly
+explained by the idea of a stable, long-lived clump of material.
+Although additional observations would be needed to conclusively
+determine whether or not this component of the system is long-lived,
+the lack of any photometric variability in the TESS data during its
+expected transits suggests that it is not.
+
+{\it The physical dimensions of emitting region}---The measured
+velocity widths of the emitting circumstellar material contain
+information about the size of the emitting region via the condition
+for rigid corotation.
+Consider a clump in cylindrical coordinates with arbitrary radial
+extent $r$, azimuthal extent $\ell$, and height $z$.
+At quadrature, the observed velocity width is sensitive to the radial
+extent of this material because it is being viewed face-on.
+During transit, the observed velocity width is sensitive to the
+azimuthal extent.
+Although the vertical height is less constrained for an edge-on system, 
+a rough estimate can follow from assuming that the depth of
+the broadband TESS absorption $\delta$ should scale with the product
+$\ell z$.
+
+At quadrature, the inner clumps show $\sigma_i$$\approx$0.24\,$v_{\rm
+eq}$, implying that 68\% of the emission comes from a volume with
+radial extent $r_i$=$2\sigma_i / \Omega$$=$0.48\,$R_\star$, and
+that 95\% of the emission comes from within 0.96\,$R_\star$.
+These values have relative uncertainties of $\approx$5\%, based on the
+uncertainties in the measured velocity
+dispersions.  The two inner clumps are centered at distances of
+2.07\,$R_\star$ and 2.88\,$R_\star$.  There is therefore 
+physical overlap in their spatial distributions.  These
+two clumps could in fact be a single clump with an optically thick H$\alpha$
+line core.
+Regardless of this nuance, the implication is that the combined 
+extent in the radial dimension of these two inner emitting clumps is
+roughly equal to the star's diameter.
+At mid-transit, these inner clumps seem to have a similar velocity
+dispersion, although with greater uncertainty due to the differences
+between the $\phi$=0 and $\phi$=1 transits.  This nonetheless suggests
+a 1$\sigma$ emission contour in the azimuthal dimension of
+$\ell$$\approx$0.5\,$R_\star$.
+
+%TODO FIXME ADD DISCUSSION OF VERTICAL DIMENSION...
 %TODO FIXME TODO FIXME
-
-IMPLICATIONS:
-The secondary eclipse of the `inner clump' at $\phi$$\approx$0.5 is not
-associated with a broadband flux dip.   The clump does not therefore
-contribute significant broadband emissivity across the entire TESS
-band; only in H$\alpha$.
 

### 2025-04-04 drivers/fit_orbits.py
drivers: minor

@@ -370,7 +370,8 @@ def main(fittingstyle='leastsquares'):
     savefig(fig, combined_plot_path)
     plt.clf()
     
-    import IPython; IPython.embed()  # for debugging purposes, remove in production
+    # PRINT FINAL CIRCULAR ORBIT FIT RESULTS
+    print(df_circ)
 
 
 if __name__ == '__main__':

### 2025-04-04 drivers/halpha_to_rv_timeseries.py

@@ -217,7 +217,7 @@ def halpha_to_rv_timeseries():
     # Initial stack plot of Halpha data
     ##########################################
     set_style('clean')
-    fig, ax = plt.subplots(figsize=(1.8,15))
+    fig, ax = plt.subplots(figsize=(1.8,12))
 
     # Normalize the spectimes values for colormap
     norm = plt.Normalize(min(spectimes), max(spectimes))
@@ -377,7 +377,7 @@ def halpha_to_rv_timeseries():
     set_style('clean')
     rcParams['font.family'] = 'Arial'
     #fig, axs = plt.subplots(ncols=4, figsize=(5.6,15), sharey=True)
-    fig, axs = plt.subplots(ncols=4, figsize=(2.8, 6.2), sharey=True)
+    fig, axs = plt.subplots(ncols=4, figsize=(2.8, 5.5), sharey=True)
 
     # Normalize the spectimes values for colormap
     norm = plt.Normalize(min(spectimes), max(spectimes))

### 2025-04-04 drivers/plot_2dgaussian_viz.py
add plot_2dgaussian_viz

@@ -1,0 +1,43 @@
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Parameters
+sigma_x, sigma_y = 0.24, 0.14
+# Define grid limits and resolution
+lim = 3
+n_points = 1000
+x = np.linspace(-lim, lim, n_points)
+y = np.linspace(-lim, lim, n_points)
+X, Y = np.meshgrid(x, y)
+
+# Compute the 2D Gaussian distribution
+I = np.exp(-((X**2)/(2*sigma_x**2) + (Y**2)/(2*sigma_y**2)))
+
+# Plot the Gaussian image
+plt.figure(figsize=(8, 6))
+plt.imshow(I, extent=[-lim,lim,-lim,lim], cmap='gray_r', origin='lower')
+plt.colorbar(label='Intensity')
+
+# Overplot the circumference of a circle with radius 1
+theta = np.linspace(0, 2*np.pi, 200)
+plt.plot(np.cos(theta), np.sin(theta), color='k', linewidth=2)
+
+plt.title('2D Gaussian Distribution with Circle')
+plt.xlabel('x')
+plt.ylabel('z')
+
+# Calculate the fraction of the circle (radius 1) blocked by the Gaussian numerically
+dx = x[1] - x[0]  # grid spacing in x
+dy = y[1] - y[0]  # grid spacing in y
+mask = (X**2 + Y**2) <= 1  # mask for points inside the circle of radius 1
+integral = np.sum(I[mask]) * dx * dy  # numerical integration over the circle
+circle_area = np.pi  # area of circle with radius 1
+fraction = integral / circle_area
+print("Blocked fraction:", fraction)
+
+# Ensure output directory exists and save the image
+output_dir = os.path.join('results', '2dgaussian_viz')
+os.makedirs(output_dir, exist_ok=True)
+plt.savefig(os.path.join(output_dir, '2dgaussian.png'), dpi=300)
+plt.close()

### 2025-04-04 paper/ms.tex
update

@@
 on average are subject to long circumstellar disk lifetimes
-\cite{Ribas2015}, to large doses of UV radiation \cite{France2013},
+\cite{Ribas2015}, to high doses of UV radiation \cite{France2013},
 and to a high incidence of flares and coronal mass ejections
@@
 
-The two leading hypotheses to explain the CPVs are either that
+The two leading hypotheses for explaining CPVs are either that
 transiting clumps of circumstellar material corotate with the star
@@
 Figure~\ref{fig:spec} compiles the TESS and HIRES data from February
-2024.  Over timescales of years, CPVs maintain a fixed period while
+2024.  Over timescales of years, CPVs maintain fixed periods while
 their photometric morphology evolves.  TIC~141146667 indeed evolved
@@
 v_{\rm eq}|<1$, most observed H$\alpha$ photons come from the star's
-chromosphere; circumstellar material may additionally modulate the
+chromosphere; circumstellar material might also modulate the
 line profile.
@@
 $\phi$=0.4-0.9 cannot be circumstellar in origin; it emits at an
-amplitude greater than that observed from the circumstellar
-components, and it crosses the stellar velocity surface too slowly.
+amplitude greater than that observed from the circumstellar components,
+and it crosses the stellar velocity surface too slowly to be
+circumstellar.
 It must therefore originate from a chromospherically bright region
-near the stellar surface.
+on the star's surface.
 While the origin of the other bright and dark streaks passing across the
@@
 %
-$P_{\rm rot}$\dotfill                   & Rotation period (hr)\dotfill                                   & $3.930\pm 0.001$ & 5 \\
+$P_{\rm rot}$\dotfill                   & Photometric rotation period (hr)\dotfill                       & $3.930\pm 0.001$ & 5 \\
 %
@@
 %
-$a_1$\dotfill                           & Clump 1 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.1-2.7         & 4 \\
-$a_2$\dotfill                           & Clump 2 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  3.9             & 4 \\
+$r_0$\dotfill                           & Inner clump (0) orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.07$\pm$0.04                 & 4 \\
+$r_1$\dotfill                           & Inner clump (1) orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.88$\pm$0.10                 & 4 \\
+$r_2$\dotfill                           & Outer clump orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  4.16$\pm$0.56                 & 4 \\
 %
@@
 2: Gaia DR3 photometry shows the star is on the pre-main sequence,
-   while the spectrum lacks lithium (see~\ref{subsec:stparams}).
+   while the spectrum lacks lithium (see \S~\ref{subsec:stparams}).
 3: PARSEC v1.2S \cite{Chen2014}.
-4: Keck/HIRES.
+4: Keck/HIRES (see \S~\ref{subsec:halpha}).
 5: TESS light curve.
@@
 originate either from the star or from an external source.  Plausible
-external sources include an old and undetected disk, comets, or a
+external sources include an undetected old disk, comets, or a
 close-in exoplanet.  This latter scenario would make CPVs extrasolar
@@
 The other potential analog for the CPVs are the $\sigma$~Ori~E
-variables, a rare subset of B stars with radiatively-driven winds that
+variables, a rare subset of B stars with radiatively-driven winds which
 accumulate into warped plasma tori \cite{Townsend2005,Townsend2008}.
@@
 
-The material's composition -- either pure plasma, or else a dusty
+The material's composition -- either pure plasma or dusty
 plasma -- can be clarified by time-series optical and infrared
@@
 interstellar medium could be indicative of condensed dust in an M
-dwarf wind, similar to that formed in the environments of more evolved
-stars \cite{Marigo2008}.
+dwarf wind, similar to that formed around more evolved stars
+\cite{Marigo2008}.
 
@@
 appreciable minority (10-30\%) of young M dwarfs -- the rapidly
-rotating ones with centrifugal magnetospheres -- host similar
-circumstellar environments to the CPVs.
+rotating ones with centrifugal magnetospheres -- host 
+circumstellar environments similar to the CPVs.
 Future studies that combine spectroscopic, polarimetric, and
@@
 (0$\farcs$86$\times$14$\farcs$0) in the red instrument configuration,
-yielding a spectral resolution $R$$\approx$45{,}0000 ($\delta
+yielding a spectral resolution $R$$\approx$45{,}000 ($\delta
 v$$\approx$6.7\,\kms; $\delta v / v_{\rm eq}$$\approx$0.05).  We binned
@@
 
-{\it Radial Velocity}---We measured radial velocities of TIC~141146667
+{\it Radial Velocity}---We measured the radial velocities of TIC~141146667
 from our HIRES spectra using a pipeline that we developed for
@@
 summary is that sufficiently cool and young M dwarfs show the 6707.8\,\AA\
-doublet in absorption, $\gtrsim$10\% below their ``continua''.  Unlike
-for Sun-like stars, the continuum for M dwarfs is poorly defined due to
+doublet in absorption, $\gtrsim$10\% below their continua.  However unlike
+for Sun-like stars, the continuum for M dwarfs is challenging to define due to
 their molecular absorption.  We therefore attempted a lithium measurement by
@@
 not.  Chromospheric emission from the magnesium triplet is also
-detected, but these lines are sufficiently blended to be rendered
-unusable.
+detected, but these lines are too blended to be usable.
 
@@
 Figure~\ref{fig:spec} shows that clumps of circumstellar material
-exist around TIC~141146667, it would be valuable to quantify the exact
+exist around TIC~141146667, there is value in quantifying the exact
 orbital periods, velocities, and velocity dispersions of these clumps.
-These quantities can clarify the precision with which the
-spectroscopic period agrees with the photometric period, and also
-constrain the physical dimensions of the emitting region.
+These quantities can constrain the physical dimensions of the emitting
+region, and can also clarify the degree to which the spectroscopic
+period agrees with the photometric period.
 
@@
 Figure~\ref{fig:spec}e.  The results of this exercise are shown in
-Figure~\ref{fig:halphamodel}; details in its implementation and
+Figure~\ref{fig:halphamodel}; details in the implementation and
 interpretation follow.
 
-To the implement the model, we assumed that the ``inner'' ($K_{\rm
+To implement the model, we assumed that the ``inner'' ($K_{\rm
 inner}$$\approx$2.5\,$v_{\rm eq}$) clump would be well-fit by a sum of
-two gaussians because it visually appears double-peaked in the raw
+two gaussians because it is visually double-peaked in the raw
 data from $\phi$=0.15-0.35 and $\phi$=0.65-0.85
-(Figure~\ref{fig:spec}b).  We assumed the ``outer'' ($K_{\rm
+(Figure~\ref{fig:spec}b).  We assumed that the ``outer'' ($K_{\rm
 outer}$$\approx$3.9\,$v_{\rm eq}$) clump would be better fit by a
@@
 the mean $\mu$, standard deviation $\sigma$, and amplitude $A$.
-Denote the two gaussians for the inner component $i=\{ 0, 1 \}$,
-and the single outer component with $i=2$.  Given the complexity of the
+We opted to label the inner component's two gaussians $i=\{ 0, 1 \}$,
+and the single outer component as $i=2$.  Given the complexity of the
 line profile data (Figure~\ref{fig:halphamodel} left column), the
@@
 ]$
-for the outer component.  This prior on the means mitigates the
-multimodality of the likelihood by requiring the mean velocity of each
+for the outer component.  This prior on the means mitigates 
+multimodality in the likelihood by requiring the mean velocity of each
 component to be within a one or two $v_{\rm eq}$ of the time-variable
@@
 
-Caution is required in interpreting this model's results.  At times
-the model overfits, because sometimes the most significant spectral
+Caution is required in interpreting this model's results.  
+At certain epochs the most significant spectral
 feature around any component's prior is not statistically significant.
-During such spectral epochs, e.g.~the ``outer'' clump at $\phi$=1.07,
-the model fits noise, not signal.  At other times, the model
-underfits.  For instance, the sudden blue rise near $\phi$=0.2 is not
-well-described by a gaussian; the assumed functional form is one of
+During such epochs, e.g.~the ``outer'' clump at $\phi$=1.07,
+the model is fitting noise, not signal.  At other times, the model
+underfits.  For instance, the sudden blue rise near $\phi$=0.2 is 
+poorly described by a gaussian; the assumed functional form is one of
 convenience.  Finally, the model fits the $i=\{ 0, 1 \}$, and $i=2$
@@
 might come from either the inner or outer components.
-Physically however, at this time the inner component
-is in transit, and the outer component is in secondary eclipse and
-would likely be blocked by the star.  At $\phi=0.0$, the double-peaked
+Physically however, at this epoch the inner clump
+is in transit, and the outer clump is passing behind
+the star.  At $\phi=0.0$, the double-peaked
 emission profile also matches that seen shortly afterward (at
@@
 inner clump is viewed off-disk.  A physical interpretation of the
-model should therefore discard the outer clump results at this
-particular epoch.
+model would therefore discard the outer clump results at this
+particular epoch, because its emission would be blocked by the star.
 
@@
   (see text).  The inner double-peaked clump is shown in
-  orange and blue; the outer clump is shown in green.  Five draws from
+  black and orange; the outer clump is shown in green.  Five draws from
   each posterior probability distribution are shown.}
@@
 
-Accounting for these caveats, we used the results from Extended
-Data Table~\ref{tab:halphamodelparams} to evaluate various models for
-the orbits.  Our main goal was to quantify the orbital periods and
+Accounting for these caveats, we used the results from Extended Data
+Table~\ref{tab:halphamodelparams} to quantify the orbital periods and
 velocity semi-amplitudes of the clumps.
-Figure~\ref{fig:orbits} shows representative results for the case of a circular
-orbit; eccentric orbits yielded similar results.  Based on visual
-inspection of Extended Data Figure~\ref{fig:halphamodel}, we manually excluded
-epochs when our gaussian profile fitting failed to either detect or
+Figure~\ref{fig:orbits} shows the results assuming circular
+orbits; considering the Bayesian information criteria, we found no
+reason to prefer eccentric orbits.  By visually
+inspecting Extended Data Figure~\ref{fig:halphamodel}, we excluded
+epochs where our gaussian profile fitting failed to either detect or
 else adequately represent the circumstellar emission.  We then used
@@
 and $P_2$=$3.35\pm0.35$\,hr, $K_1/v_{\rm eq}$=4.16$\pm$0.56.
-The periods for the inner double-peaked clump are consistent with the
+The periods for the inner double-peaked clump are therefore consistent with the
 photometric $3.930\pm0.001$\,hr period within a precision of two
@@
 for this component seems fine-tuned.  We instead emphasize that
-although this emission is present, its variability in time is poorly
-explained by the idea of a stable, long-lived clump of material.
+although this emission is present, its variability in time is 
+inconsistent with the idea of a stable clump of material.
 Although additional observations would be needed to conclusively
@@
 
-{\it The physical dimensions of emitting region}---The measured
-velocity widths of the emitting circumstellar material contain
-information about the size of the emitting region via the condition
-for rigid corotation.
-Consider a clump in cylindrical coordinates with arbitrary radial
-extent $r$, azimuthal extent $\ell$, and height $z$.
-At quadrature, the observed velocity width is sensitive to the radial
-extent of this material because it is being viewed face-on.
-During transit, the observed velocity width is sensitive to the
-azimuthal extent.
-Although the vertical height is less constrained for an edge-on system, 
-a rough estimate can follow from assuming that the depth of
-the broadband TESS absorption $\delta$ should scale with the product
-$\ell z$.
+{\it Physical dimensions of the emitting region}---The measured velocity
+widths from the circumstellar emission contain information about the
+size of the emitting region via the condition for rigid corotation.
+Consider a clump in cylindrical coordinates with arbitrary radial extent
+$r$, azimuthal extent $\ell$, and height $z$.  A range of shapes,
+including an ``arc'' with $\ell \gg r$, a ``spoke'' with $r \gg \ell$, and
+a ``blob'' with $r \approx \ell \approx z$ are all a priori possible.
+However, at quadrature, the observed velocity width is sensitive to the
+radial extent of the circumstellar material.  At mid-transit, the
+observed velocity width is sensitive to the azimuthal extent.  The arc
+configuration would minimize the observed velocity width $\sigma$ at
+quadrature, and maximize it during transit, with $\gtrsim$100\,\kms\ 
+variations in between.  Since this is not observed the arc geometry,
+and by a similar argument the spoke geometry, can be discarded.
 
 At quadrature, the inner clumps show $\sigma_i$$\approx$0.24\,$v_{\rm
-eq}$, implying that 68\% of the emission comes from a volume with
-radial extent $r_i$=$2\sigma_i / \Omega$$=$0.48\,$R_\star$, and
-that 95\% of the emission comes from within 0.96\,$R_\star$.
-These values have relative uncertainties of $\approx$5\%, based on the
-uncertainties in the measured velocity
-dispersions.  The two inner clumps are centered at distances of
-2.07\,$R_\star$ and 2.88\,$R_\star$.  There is therefore 
-physical overlap in their spatial distributions.  These
-two clumps could in fact be a single clump with an optically thick H$\alpha$
-line core.
-Regardless of this nuance, the implication is that the combined 
-extent in the radial dimension of these two inner emitting clumps is
-roughly equal to the star's diameter.
-At mid-transit, these inner clumps seem to have a similar velocity
-dispersion, although with greater uncertainty due to the differences
-between the $\phi$=0 and $\phi$=1 transits.  This nonetheless suggests
-a 1$\sigma$ emission contour in the azimuthal dimension of
-$\ell$$\approx$0.5\,$R_\star$.
-
-%TODO FIXME ADD DISCUSSION OF VERTICAL DIMENSION...
-%TODO FIXME TODO FIXME
+eq}$, implying that 68\% of the emission comes from a volume with length
+in the radial dimension $r_i$=$2\sigma_i / \Omega$$=$0.48\,$R_\star$,
+and that 95\% of the emission comes from within 0.96\,$R_\star$.  These
+values have relative uncertainties of $\approx$5\%, based on the
+uncertainties in the measured velocity dispersions.  The two inner
+clumps are centered at orbital distances of 2.07\,$R_\star$ and 2.88\,$R_\star$.
+There is therefore physical overlap in their spatial distributions.
+These two clumps could in fact be a single clump with an optically thick
+H$\alpha$ line core.  Regardless of this nuance, the implication is that
+the full length in the radial dimension of these two inner emitting
+clumps is approximately equal to the star's diameter.  At mid-transit, these
+inner clumps likely have a similar velocity dispersion, although with
+greater uncertainty due to the differences between the $\phi$=0 and
+$\phi$=1 transits (see Extended Data Figure~\ref{fig:halphamodel}).
+This suggests a 1$\sigma$ emission contour in the azimuthal dimension
+with a length of $\ell$$\approx$0.5\,$R_\star$.
+
+The vertical height of the emitting region is less constrained because
+the system is consistent with being viewed edge-on.  However, one
+constraint does come from the TESS transit depth scaling with
+the projected area $\ell z$.  More specifically, one can evaluate an
+``effective area'' blocked by a two-dimensional gaussian blob passing over a star by
+integrating the local gaussian weight over the stellar surface.  For
+instance, if $\ell$$\approx$$z$$\approx$0.24\,$R_\star$, then
+$\iint \exp \left(
+  -\left( x^2/2\sigma_x^2 + y^2/2\sigma_y^2 \right)
+\right) {\rm d}x \, {\rm d}y$
+suggests 11.5\% of the star being ``blocked'', a geometric factor which
+would need to be in turn multiplied by an unknown opacity factor to
+produce the observed transit depth ($\delta$$\approx$5\%).  In general
+though, there is a degeneracy between $z$ and this opacity factor; larger
+vertical heights are allowed for lower optical depths in absorption, and
+vice-versa.
 
@@
   profiles.  These results should be treated with caution; only a
-  subset of the spectral epochs provided statistically significant
+  subset of the spectral epochs yielded statistically significant
   detections of the circumstellar emission (see Extended Data
@@
 \item[Acknowledgments]
-  LGB is grateful to M.~Jardine, A.~Weinberger, B.~Tofflemire, and
-  J.~Spake for
-  insightful conversations, and to A.~Howard and H.~Isaacson for their
-  assistance reducing the HIRES spectra.
+  LGB is grateful to M.~Jardine, A.~Weinberger, B.~Tofflemire, J.~Spake,
+  and J.Winn for insightful conversations that significantly informed
+  this work, and to A.~Howard and H.~Isaacson for their assistance
+  reducing the HIRES spectra.
   This work was supported by the Carnegie Fellowship and by the
@@
   directorate.
-  The TESS mission is a product of millions of hours of work by
-  thousands of people; we thank the TESS team for their efforts to
-  make the mission a continued success.
+  TESS is a product of millions of hours of work by thousands of people;
+  we thank the TESS team for their efforts to make the mission a
+  continued success.
   The HIRES data were obtained at the Keck Observatory, which exists
@@
   bouma.luke@gmail.com.
-
-\item[Code availability] We provide access to a GitHub repository
-  including all code created for the analysis of this project that is
-  not already publicly available.
-
 \end{addendum}

### 2025-04-04 drivers/fit_orbits.py
update

@@ -4,6 +4,7 @@ import os
 from os.path import join
 from scipy.optimize import curve_fit
 import matplotlib.pyplot as plt
+from matplotlib import rcParams
 from aesthetic.plot import set_style, savefig
 import jax
 import jax.numpy as jnp
@@ -338,8 +339,10 @@ def main(fittingstyle='leastsquares'):
     
     # FINAL VISUALIZATION PLOT
     set_style('science')
+    rcParams['font.family'] = 'Arial'
     f = 0.85
     fig, ax = plt.subplots(figsize=(f*3.5, f*3))
+    colors = ['#000000', '#E69F00', '#009E73']
     for ix, fit in enumerate(all_fits):
         t = fit['time']
         rv = fit['rv']
@@ -348,8 +351,9 @@ def main(fittingstyle='leastsquares'):
         _t = fit['_time'][mask]
         _rv = fit['_rv'][mask]
         _rv_err = fit['_rv_err'][mask]
-        c = f"C{ix}"
-        t_fit = np.linspace(fit['_time'].min(), fit['_time'].max(), 5000)
+        c = colors[ix]
+        t_fit = np.linspace(fit['_time'].min()-1/24,
+                            fit['_time'].max()+1/24, 5000)
         fn = lambda x: 24 * (x - fit['_time'].min())
         ax.errorbar(fn(t), rv, yerr=rv_err, fmt='o', c=c, ms=2)
         ax.errorbar(fn(_t), _rv, yerr=_rv_err, fmt='x', alpha=0.3, zorder=-1, c=c, ms=4)

### 2025-04-07 paper/ms.tex
update ms

@@
 star's equatorial velocity, directly demonstrating for the first
-time the existence of corotating circumstellar plasma around a CPV.
-Given that long-lived condensations of cool ($10^4$ K) plasma can
-persist in the hot ($10^6$ K) coronae of stars with a wide range of
-masses \cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
-these data support the idea that around the lowest-mass stars, such
-condensations can sustain an optically thick component; the origin
-of this optically thick material and its microphysical opacity remain
-unclear.
+time the existence of corotating clumps of circumstellar plasma around a CPV.
+Given that cool ($10^4$ K) plasma can persist in the hot ($10^6$ K)
+coronae of rapidly-rotating stars with a wide range of masses
+\cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
+these data support the idea that the magnetospheres of the
+lowest-mass stars can support long-lived, optically thick
+clumps of material that explain the sharp photometric features seen in
+CPVs.  The origin of this optically thick material and its
+microphysical opacity remain unclear.
 \end{abstract}
@@
 on average are subject to long circumstellar disk lifetimes
-\cite{Ribas2015}, to high doses of UV radiation \cite{France2013},
+\cite{Ribas2015}, to high doses of UV radiation \cite{France2016},
 and to a high incidence of flares and coronal mass ejections
@@
 limits, none host disks \cite{Stauffer2017,Bouma2024}.
-However, $\approx$3\% of stars a few million years old show complex
+However, $\approx$3\% of stars a few million years old show this complex
 photometric behavior, an observed fraction which decreases to $\approx$0.3\% by
 $\approx$150\,Myr \cite{Rebull2020}.
+CPVs are a known source of astrophysical false positives in searches for
+transiting exoplanets around young M dwarfs
+\cite{vanEyken2012,Johns-Krull2016,Bouma2020}.
 
@@
 decades, reported that stellar coronae contain both hot ($10^6$ K) and
-cool ($10^4$ K) plasma. In particular, time-series spectra of stars
-with a wide range of masses have shown periodic high-velocity
+cool ($10^4$ K) plasma. In particular, time-series spectroscopy of stars
+with a wide range of masses has shown periodic high-velocity
 absorption and emission in Balmer lines such as H$\alpha$, interpreted
@@
 periodic light curves.  We selected the star for spectroscopy because
-its brightness and rotation rate enable efficiently measuring
-variability in its line profile.  We observed it for five hours on
+its brightness and rotation rate enabled an efficient search for 
+variability in its line profiles.  We observed the star for five hours on
 17~February~2024 (UT) using the High Resolution Echelle Spectrometer
@@
 26~February~2024 with a duty cycle of 77\%.  During the HIRES
-observations, TESS was performing a data downlink; TESS data
-collection resumed 12 hours (three rotation cycles) after the spectra
-were acquired.  Extended Data Figure~\ref{fig:fulllc} shows the
-detailed photometric behavior of the star near the epoch of
-observation; the general photometric morphology is similar before and
-after the data gap.
+observations, scattered light from the Earth caused a gap in the TESS
+photometry; TESS data collection resumed 12 hours (three rotation
+cycles) after the spectra were acquired.  Extended Data
+Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
+star near the epoch of observation; the general photometric morphology
+is similar before and after the data gap.
 
@@
 ($v_{\rm eq}$=130\,\kms).  There are at least two distinct emission
-components, separated by half a cycle in phase.  The first component
-has clearer sinusoidal behaviour in time and is double-peaked, with peak
-semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
-There is significant non-periodic variability in the emissivity of
-this double-peaked component: the flux excess begins with an amplitude
-of 70\% above the continuum early in the observation sequence, and
-diminishes to 10\% by its end.  The component 180$^\circ$ opposite in
-phase is detected only from $\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this
-latter component appears connected to the star in velocity space.
-While its peak semi-amplitude of $K_1$=3.9\,$v_{\rm eq}$ is achieved
-at both $\phi$=0.25 and 0.75, its amplitude similarly decreases from a
-60\% excess over the continuum at the beginning of the observation
-sequence to a 10\% excess by its end.  The apparent period for all
-of these emission components is consistent with the photometric
+components, separated by half a cycle in phase.  The inner component at
+lower velocities has clearer sinusoidal behaviour in time and is
+double-peaked, with peak semi-amplitudes of 2.07\,$v_{\rm eq}$ and
+2.88\,$v_{\rm eq}$ (see \S~\ref{subsec:halpha}).  There is significant
+non-periodic variability in the emissivity of this double-peaked
+component: the flux excess begins with an amplitude 70\% that of the
+continuum early in the observation sequence, and diminishes to 10\% by
+its end.  The higher-velocity component 180$^\circ$ opposite in phase is
+detected only from $\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this outer
+component appears connected to the star in velocity space.  While its
+peak semi-amplitude of 3.88\,$v_{\rm eq}$ is achieved at both
+$\phi$=0.25 and 0.75, its amplitude similarly decreases from a 60\%
+excess over the continuum at the beginning of the observation sequence
+to a 10\% excess by its end.  The apparent period for all three
+spectroscopic emission components is consistent with the photometric
 \periodhr\ hour period.
@@
 partially-ionized hydrogen to corotate with the star.  Based on the
-observed sinusoidal period and peak velocity, this material's motion
-is not controlled by gravitational attraction to the star; it can only be
-explained by plasma being dragged along with the rotating stellar
-magnetic field.  The velocity semi-amplitude of the sinusoids gives
-the distance of the clumps from the stellar surface:
-2.1-2.7\,$R_\star$ for the closer clump, and 3.9\,$R_\star$ for the
-other.   These clumps transit in front of the star when passing from
-negative to positive velocity.  This implies that the spectroscopic
-transit of the 2.1-2.7\,$R_\star$ clump occurs simultaneously with the
-sharp photometric spike visible in the TESS data.
+observed sinusoidal periods and peak velocities, this material's motion
+is not controlled by gravitational attraction to the star; it is more
+readily explained as a partially-ionized plasma being dragged along with
+a rigidly rotating stellar magnetic field.  The velocity semi-amplitude
+of the sinusoids gives the mean distance of each clump from the stellar
+surface: 2.07\,$R_\star$ and 2.88\,$R_\star$ for the inner clumps, and
+3.88\,$R_\star$ for the outer clump.   These clumps transit in front of
+the star when passing from negative to positive velocity.  The innermost
+clump transits over $\approx$15\% of the period, at $\phi$=0 and
+$\phi$=1.  This spectroscopic transit happens during the latter half of
+the complex photometric feature in the TESS data.
 
 % * keck/hires: behavior at v/veq<1
-The H$\alpha$ line core is more complex.  At $|\Delta v /
-v_{\rm eq}|<1$, most observed H$\alpha$ photons come from the star's
-chromosphere; circumstellar material might also modulate the
-line profile.
-Figure~\ref{fig:spec}e suggests line core variability caused by both
-bright and dark regions on the star's surface, superposed
-with smaller-amplitude variability from the transiting circumstellar
-material.
-For instance, from $\phi$=0-0.3, the double-peaked emission feature
-is visible when it is being viewed both on and off-limb.
-However, the large emission feature that crosses the star from
-$\phi$=0.4-0.9 cannot be circumstellar in origin; it emits at an
-amplitude greater than that observed from the circumstellar components,
-and it crosses the stellar velocity surface too slowly to be
-circumstellar.
-It must therefore originate from a chromospherically bright region
-on the star's surface.
-While the origin of the other bright and dark streaks passing across the
-line core are more ambiguous,
-a final exercise to quantify the behavior of this region is shown in
-Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes the
-summed flux at $|\Delta v / v_{\rm eq}|<1$.  This panel shows that
-changes in the line core flux correlate with the broadband variability
-throughout most of the light curve, except near $\phi$$\approx$0.5,
-corresponding to the transit of the 3.9\,$R_\star$ clump and the
-occultation of the lower-velocity clump.
+The H$\alpha$ line core is more complex.  At $|\Delta v / v_{\rm
+eq}|<1$, most observed H$\alpha$ photons come from the star's
+chromosphere; circumstellar material might also modulate the line
+profile.  Figure~\ref{fig:spec}e suggests line core variability caused
+by both bright and dark regions on the star's surface, superposed with
+smaller-amplitude variability from the transiting circumstellar
+material.  For instance, from $\phi$=0-0.3, the double-peaked emission
+feature is visible when viewed both on and off-limb; this feature is
+circumstellar in origin.  However, the large emission feature that
+crosses the star from $\phi$=0.4-0.9 emits at an amplitude greater than
+that observed from the circumstellar components, and it crosses the
+stellar velocity surface at a speed that suggests it instead originates
+from a chromospherically bright region on the star's surface.
+Similarly, from $\phi$=0.6-1.15 a 20\% deep absorption feature slowly
+crosses the H$\alpha$ line profile.  This feature suggests either a
+chromospherically dark region (e.g.~a starspot group) crossing the
+star's surface, or an azimuthally extended absorptive component to the
+circumstellar material which is not visible in emission.  Although the
+origin of the other bright and dark streaks passing across the line core
+are similarly ambiguous, a final exercise to quantify the behavior of the
+line core is shown in Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\
+core}$ denotes the summed flux at $|\Delta v / v_{\rm eq}|<1$.  This
+panel shows that changes in the line core flux correlate with the
+broadband variability throughout most of the light curve, except near
+$\phi$$\approx$0.5, corresponding to the transit of the 3.9\,$R_\star$
+clump and the occultation of the lower-velocity clump.
 
@@
 \centering
-\caption{Selected System Parameters for TIC~141146667}
+\caption{Selected system parameters for TIC~141146667}
 \label{tab:params}
@@
 %
-Spec. Type\dotfill                      & Spectral Type\dotfill                                          & M5.5Ve           & 4 \\
+SpT\dotfill                      & Spectral Type\dotfill                                          & M5.5Ve           & 4 \\
 %
@@
 %
-$r_0$\dotfill                           & Inner clump (0) orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.07$\pm$0.04                 & 4 \\
-$r_1$\dotfill                           & Inner clump (1) orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.88$\pm$0.10                 & 4 \\
-$r_2$\dotfill                           & Outer clump orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  4.16$\pm$0.56                 & 4 \\
+$a_0$\dotfill                           & Mean inner clump (0)\hspace{9pt}\dotfill           &  2.07$\pm$0.04   & 4 \\
+                                        & \hspace{3pt} orbital radius ($R_\star$)	                       &                      \\
+%
+$a_1$\dotfill                           & Mean inner clump (1)\hspace{9pt}\dotfill           &  2.88$\pm$0.10   & 4 \\
+                                        & \hspace{3pt} orbital radius ($R_\star$)	                       &                      \\
+%
+$a_2$\dotfill                           & Mean outer clump\hspace{9pt}\dotfill           &  3.88$\pm$0.25   & 4 \\
+                                        & \hspace{3pt} orbital radius ($R_\star$)	                       &                      \\
 %
@@
 \section{Discussion}
-% argue: how does this clarify wider phenomenology?  what general
-% conclusions can be drawn?
-
-Spectra of magnetically-active, rapidly rotating stars with a wide range
-of masses have been known to exhibit both sinusoidal emission features
-in time
-\cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} and
-transient absorption features
-\cite{CollierCameron1989,CollierCameron1992,Cang2020} similar to
+
+Spectra of magnetically-active, rapidly rotating stars with a wide
+range of masses have been previously observed to exhibit both
+sinusoidal time-varying Balmer emission
+\cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} and transient
+absorption features
+\cite{CollierCameron1989,CollierCameron1992,Cang2020}, similar to
 Figure~\ref{fig:spec}.  No such stars were previously known to show
-complex light curves \cite{Bouma2024}.   One interpretation for
-such spectroscopic variability comes from an analogy to quiescent solar
-prominences, which are cool condensations of plasma in the solar corona
-that can last days to weeks \cite{VialEngvold2015}.  These
-condensations fall back to the Sun's surface because gravity is
+complex light curves \cite{Bouma2024}.   One interpretation for the
+spectroscopic variability comes from an analogy to quiescent
+solar prominences, which are cool condensations of plasma in the solar
+corona that can last days to weeks \cite{VialEngvold2015}.  These
+condensations fall back to the Sun's photosphere because gravity is
 stronger than any magnetic tension or centrifugal force capable of
@@
 potential experienced by a charged particle can have a local minimum
-outside $R_{\rm c}$, enabling the material to accumulate over much
-longer timescales \cite{Petit2013,Daley-Yates2024}.  Generally
-speaking, such material need neither transit nor be opaque in
-broadband optical light.
-For instance, the H$\alpha$ emission clump at 3.9\,$R_\star$ shows no 
-photometric signal in the February 2024 photometry.
-
-Our Keck/HIRES observations are the first reported time-series spectra
-of a CPV, and they show that corotating circumstellar plasma clumps
-are present around at least one such star.  This observation rules out
-a ``starspot-only'' origin for the CPVs, \cite{Koen2021} because
-such scenarios have no means of explaining spectroscopic emission
-beyond the stellar disk.  Similarly, scenarios in which the
-circumstellar material is made only of dust are also ruled out.  While
-dust may be present, to explain the H$\alpha$ emission the clumps must
-include plasma with a significant population of hydrogen atoms in the
-$n$=3 excited state, where $n$ denotes the principal quantum number.
-More quantitatively, the observed H$\alpha$ luminosity suggests
+outside $R_{\rm c}$, enabling the material to accumulate in a
+centrifugally-supported magnetosphere
+\cite{Petit2013,Daley-Yates2024}.  Generally speaking, such material
+need neither transit nor be opaque in broadband optical light.  In
+fact, Figure~\ref{fig:spec} suggests that the transits of the
+H$\alpha$ emitting material cannot explain the entirety of the complex
+photometric modulation;  the spectroscopic transits happen too fast, and
+at orbital phases that only partially overlap with the photometric
+modulations.
+
+Nonetheless, our Keck/HIRES observations are the first reported
+time-series spectra of a CPV, and they show for the first time that
+corotating circumstellar plasma clumps exist around at least one such
+star.  While starspots likely do contribute smooth photometric
+variability signals, a ``starspot-only'' scenario for the CPVs
+\cite{Koen2021} seems to be incompatible with our observations.
+Scenarios in which the circumstellar material is made only of dust are
+similarly ruled out.  While starspots and dust may both be present,
+the observed H$\alpha$ emission requires clumps of plasma with a
+significant population of hydrogen atoms in the $n$=3 excited state,
+with most H$\alpha$ emission coming from a region half the size of the
+star (see \S~\ref{subsec:halpha}).  The observed H$\alpha$ luminosity
+suggests
 characteristic densities and masses for the gaseous component of these
 clumps of $n_{\rm H} \sim 10^{11}$-$10^{12}$\,cm$^{-3}$ and $M_{\rm
-gas} \sim 10^{17}$\,g (see Section~\ref{subsec:gas}).  Dust, if
-present, is independently constrained to have a total mass
-$10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm g}$ (see
-Section~\ref{subsec:dust}).  This circumstellar material could
-originate either from the star or from an external source.  Plausible
-external sources include an undetected old disk, comets, or a
-close-in exoplanet.  This latter scenario would make CPVs extrasolar
-analogs of the Jupiter-Io plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
+gas} \sim 10^{17}$\,g (see \S~\ref{subsec:gas}).  Dust, if present, is
+independently constrained to have a total mass $10^{15}\,{\rm g} <
+M_{\rm dust} < 10^{17}\,{\rm g}$ (see \S~\ref{subsec:dust}).  This
+circumstellar material could originate either from the star or from an
+external source.  Plausible external sources include an undetected old
+disk, comets, or a close-in exoplanet.  This latter scenario would
+make CPVs extrasolar analogs of the Jupiter-Io plasma torus
+(e.g.~Ref.~\cite{Bagenal1981}).
 
 The other potential analog for the CPVs are the $\sigma$~Ori~E
-variables, a rare subset of B stars with radiatively-driven winds which
-accumulate into warped plasma tori \cite{Townsend2005,Townsend2008}.
-These tori tend to have dense antipodal accumulations of plasma
-sculpted by tilted-dipole magnetic fields, and the transits of these
-clumps produce broadband photometric variability through bound-free
-scattering \cite{Townsend2005} and Thomson scattering
-\cite{Berry2022}.  
-The plasma accumulates at antipodes 180$^\circ$ apart because the
-deepest local minima in the effective potential exist along the line
-of intersection between the rotational and magnetic equators (see
-Equation~22 of \cite{Townsend2005}).
-For $\sigma$~Ori~E and almost
-all of its analogs, the result is ``simple'' light curves that 
-resemble those of eclipsing binaries, and time-dynamic H$\alpha$
-spectra similar to those in Figure~\ref{fig:spec}
-\cite{Townsend2005,Townsend2008}.  The two known exceptions, HD~37776
-and HD~64740, show complex light curves resembling CPVs
-\cite{Mikulasek2020,Bouma2024} and have spectropolarimetric magnetic
-field maps indicating strong contributions from higher-order magnetic
-moments \cite{Kochukhov2011,Shultz2018}.  There are two implications:
-first, the complexity of CPVs may be a direct consequence of magnetic
-fields with highly multipolar contributions.  Second, CPVs can be a
-source of astrophysical false positives in photometric classification
-of eclipsing binaries and transiting exoplanets around young pre-main
-sequence M dwarfs \cite{Johns-Krull2016,Bouma2020}.
+variables, a rare subset of B stars with radiatively-driven winds
+which accumulate into warped plasma tori
+\cite{Townsend2005,Townsend2008}.  These tori tend to have dense
+antipodal accumulations of plasma sculpted by tilted-dipole magnetic
+fields, and the transits of these clumps produce broadband photometric
+variability through bound-free scattering \cite{Townsend2005} and
+Thomson scattering \cite{Berry2022}.  The plasma accumulates at
+antipodes 180$^\circ$ apart because the deepest local minima in the
+effective potential exist along the line of intersection between the
+rotational and magnetic equators (see Equation~22 of
+\cite{Townsend2005}).  For $\sigma$~Ori~E and almost all of its
+analogs, the result is ``simple'' light curves that resemble those of
+eclipsing binaries, and time-dynamic H$\alpha$ spectra similar to
+those in Figure~\ref{fig:spec} \cite{Townsend2005,Townsend2008}.  The
+two known exceptions, HD~37776 and HD~64740, show complex light curves
+resembling CPVs \cite{Mikulasek2020,Bouma2024} and have
+spectropolarimetric magnetic field maps indicating strong
+contributions from higher-order magnetic moments
+\cite{Kochukhov2011,Shultz2018}.  There are two implications: first, the
+photometric complexity of CPVs may be a direct consequence of magnetic
+fields with highly multipolar contributions.  Second, despite this
+complexity, the observation from Figure~\ref{fig:spec} of two emission
+clumps separated 180$^\circ$ in phase is consistent with the expected
+emission from a warped plasma torus.
 
@@
 
-The material's composition -- either pure plasma or dusty
-plasma -- can be clarified by time-series optical and infrared
-spectrophotometry.  While observations of CPVs in the optical 
-suggest a chromaticity consistent with dust
+The material's composition -- either pure plasma or dusty plasma --
+can be clarified by time-series optical and infrared
+spectrophotometry.  While observations of CPVs in the optical suggest
+a chromaticity consistent with dust
 \cite{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such
-as electron scattering in a plasma transiting over starspots might
-also produce chromatic features \cite{Rackham2018}.  The composition
-and size distribution of any dust that is present could be determined
-by measuring the extinction curve for one or more CPVs from
-1-20\,$\mu$m.  Composition and size distributions similar to debris
-from rocky bodies seen around white dwarfs \cite{Reach2009} would
-indicate a rocky-body origin.  Compositions and sizes similar to the
-interstellar medium could be indicative of condensed dust in an M
-dwarf wind, similar to that formed around more evolved stars
-\cite{Marigo2008}.
+as electron scattering in a plasma transiting over a spotted
+background star might also produce chromatic features
+\cite{Rackham2018}.  The composition and size distribution of any dust
+that is present could be determined by measuring the extinction curve
+for a sample of CPVs from 1-20\,$\mu$m.  Composition and size
+distributions similar to debris from rocky bodies seen around white
+dwarfs \cite{Reach2009} would suggest an extrinsic origin channel.
+Compositions and sizes similar to the interstellar medium would
+suggest that dust can condense out from M dwarf winds, similar to
+processes that occur around more evolved stars \cite{Marigo2008}.
 
@@
 Detecting radio emission produced by an electron cyclotron maser
-instability (e.g. \cite{Callingham2021}) in particular would provide
-a measurement of the field strength at the site of the emitting
-region, further clarifying the magnetosphere's structure.
+instability (e.g. \cite{Callingham2021}) in particular would provide a
+measurement of the field strength at the site of the emitting region,
+further clarifying the magnetosphere's structure.
 
@@
 close-in rocky exoplanets that exist around most M dwarfs
-\cite{Dressing2015}.  However, 0.3-3\% of young M dwarfs show the CPV
-phenomenon \cite{Rebull2020}, and our data show that the complex
-photometric features occur when clumps of circumstellar material
-transit the star.  The implied geometric correction suggests that an
-appreciable minority (10-30\%) of young M dwarfs -- the rapidly
-rotating ones with centrifugal magnetospheres -- host 
-circumstellar environments similar to the CPVs.
-Future studies that combine spectroscopic, polarimetric, and
-multi-wavelength observations, along with magnetohydrodynamic
-modeling, will be key to understanding the complex magnetospheric
-environments of these young stars.
+\cite{Dressing2015}.  However, a few percent of young M dwarfs show the CPV
+phenomenon \cite{Rebull2020}, and our data show that some of the
+complex photometric features occur when clumps of circumstellar
+material transit the star.  The suggested geometric correction implies
+that an appreciable minority (10-30\%) of young M dwarfs -- the
+rapidly rotating ones with centrifugal magnetospheres -- host
+circumstellar environments similar to the CPVs.  Future studies that
+combine spectroscopic, polarimetric, and multi-wavelength
+observations, along with magnetohydrodynamic modeling, will be key to
+understanding the complex magnetospheric environments of these young
+stars.
 
@@
 
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/sf3.pdf}
+  \caption{Dereddened Gaia DR3 color vs.~absolute magnitude diagram of
+  TIC~141146667 and comparison samples. 
+  TIC~141146667 is on the pre-main sequence; stars with the same color
+  on the main sequence are $\approx$1.5\,magnitudes
+  fainter.  The star's location in this diagram suggests an
+  age of 30-150\,Myr.  }
+  \label{fig:camd}
+\end{figure}
+
 {\it Age: Isochrones}---The color and absolute magnitude of
@@
 
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/sf2.pdf}
+  \caption{An upper limit on photospheric lithium for TIC~141146667
+  (green triangle) yields a lower bound on the star's age of
+  $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
+  \cite{Jeffries2023}; rich clusters in each age bin include NGC\,2264
+  (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
+  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2602 and IC\,2391 (42.0\,Myr),
+  and NGC\,2451A (50.0\,Myr). }
+  \label{fig:liew_population}
+\end{figure}
+
 Despite uncertainties in the details, what can be stated with confidence
@@
 
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=0.7\textwidth]{figures/sf3.pdf}
-  \caption{Dereddened Gaia DR3 color vs.~absolute magnitude diagram of
-  TIC~141146667 and comparison samples. 
-  TIC~141146667 is on the pre-main sequence; stars with the same color
-  on the main sequence are $\approx$1.5\,magnitudes
-  fainter.  The star's location in this diagram suggests an
-  age of 30-150\,Myr.  }
-  \label{fig:camd}
-\end{figure}
-
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=0.7\textwidth]{figures/sf2.pdf}
-  \caption{An upper limit on photospheric lithium for TIC~141146667
-  (green triangle) yields a lower bound on the star's age of
-  $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
-  \cite{Jeffries2023}; rich clusters in each age bin include NGC\,2264
-  (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
-  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2602 and IC\,2391 (42.0\,Myr),
-  and NGC\,2451A (50.0\,Myr). }
-  \label{fig:liew_population}
-\end{figure}
-
 {\it Age: Summary}---The main indicators for the youth of
@@
 detections to be in $\lesssim$200\,Myr old clusters \cite{Bouma2024};
-the remaining 10\% could not be associated with any coeval
+the remaining 10\% were not associated with any coeval
 population.
@@
 
-Extended Data Figure~\ref{fig:hirescuts} provides a novel view on the sudden blue
-excess that appeared at $\phi$$\approx$0.2 in H$\alpha$, H$\gamma$,
-H$\delta$, and He 5876\,\AA.  At the same epoch, only H$\alpha$
-clearly shows a resolved red excess as well, although H$\gamma$ and
-H$\delta$ are broadened at this time.  Given the sudden rise of this
-emission in $<$15\,minutes, this sudden blue excess might suggest a
-more sudden flow, rather than a stable, periodic component.  A stellar
-flare could be a plausible explanation for such a sudden rise.
-However this idea seems incompatible with the sinusoidal emission seen
-from $\phi$$\approx$0.5-1.0, and with the fact that flares often
-excite iron lines in the blue HIRES orders, which are not observed.
-More time-series spectroscopy would be needed to provide a definitive
-clarification for this type of non-periodic variability.
+Extended Data Figure~\ref{fig:hirescuts} provides a novel view on the
+blue excess that appeared at $\phi$$\approx$0.2 in H$\alpha$, H$\gamma$,
+H$\delta$, and He 5876\,\AA.  At the same epoch, H$\alpha$ additionally
+shows a red clump of emission, and H$\gamma$ and H$\delta$ are also
+broadened on the red wing.  The rise of this emission in $<$15\,minutes
+might suggest a more sudden flow, rather than a stable, periodic
+component.  For instance, a stellar flare might be connected to such a
+sudden rise.  However, this idea seems incompatible with the sinusoidal
+emission seen later from $\phi$$\approx$0.5-1.0, and with the fact that
+flares typically excite iron lines in the blue HIRES orders, which are
+not observed.  More time-series spectroscopy would be needed to clarify
+this type of variability, in particular whether it is periodic or
+stochastic.
 
@@
 absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ resonance
-line are both shown in Extended Data Figure~\ref{fig:hirescuts}.  In the latter,
+line are both visible in Extended Data Figure~\ref{fig:hirescuts}.  In the latter,
 narrow telluric absorption features overlap the blue wing of the line.
@@
   core.  
-  Section~\ref{subsec:halpha} discusses the use of this model.
+  \S~\ref{subsec:halpha} discusses the use of this model.
   }
@@
 These quantities can constrain the physical dimensions of the emitting
-region, and can also clarify the degree to which the spectroscopic
-period agrees with the photometric period.
+region, and can also clarify whether the spectroscopic period agrees
+with the photometric period.
 
@@
 the mean $\mu$, standard deviation $\sigma$, and amplitude $A$.
-We opted to label the inner component's two gaussians $i=\{ 0, 1 \}$,
+We labelled the inner component's two gaussians $i=\{ 0, 1 \}$,
 and the single outer component as $i=2$.  Given the complexity of the
@@
 During such epochs, e.g.~the ``outer'' clump at $\phi$=1.07,
-the model is fitting noise, not signal.  At other times, the model
+the model fits noise, not signal.  At other times, the model
 underfits.  For instance, the sudden blue rise near $\phi$=0.2 is 
@@
 convenience.  Finally, the model fits the $i=\{ 0, 1 \}$, and $i=2$
-components independently.  At $\phi=0.0$ and $1.0$,
+components independently.  At $\phi$=0.0 and 1.0,
 Figure~\ref{fig:halphamodel} suggests that the emission
@@
 is in transit, and the outer clump is passing behind
-the star.  At $\phi=0.0$, the double-peaked
+the star.  At $\phi$=0.0, the double-peaked
 emission profile also matches that seen shortly afterward (at
@@
 Figure~\ref{fig:orbits} shows the results assuming circular
-orbits; considering the Bayesian information criteria, we found no
+orbits; considering the Bayesian information criterion, we found no
 reason to prefer eccentric orbits.  By visually
@@
 $P_1$=$3.92\pm0.06$\,hr, $K_1/v_{\rm eq}$=2.88$\pm$0.10;
-and $P_2$=$3.35\pm0.35$\,hr, $K_1/v_{\rm eq}$=4.16$\pm$0.56.
+and $P_2$=$3.88\pm0.20$\,hr, $K_1/v_{\rm eq}$=3.88$\pm$0.25.
 The periods for the inner double-peaked clump are therefore consistent with the
@@
 inconsistent with the idea of a stable clump of material.
-Although additional observations would be needed to conclusively
-determine whether or not this component of the system is long-lived,
-the lack of any photometric variability in the TESS data during its
-expected transits suggests that it is not.
+Additional observations would be needed to conclusively
+determine whether or not this component of the system is long-lived.
 
@@
 a ``blob'' with $r \approx \ell \approx z$ are all a priori possible.
-However, at quadrature, the observed velocity width is sensitive to the
-radial extent of the circumstellar material.  At mid-transit, the
-observed velocity width is sensitive to the azimuthal extent.  The arc
-configuration would minimize the observed velocity width $\sigma$ at
-quadrature, and maximize it during transit, with $\gtrsim$100\,\kms\ 
-variations in between.  Since this is not observed the arc geometry,
-and by a similar argument the spoke geometry, can be discarded.
+However, at quadrature, the observed velocity width of emission is
+sensitive to the radial extent of the circumstellar material.  At
+mid-transit, the observed velocity width is sensitive to the azimuthal
+extent.  An arc configuration would minimize the observed velocity width
+$\sigma$ at quadrature, and maximize it during transit, with
+$\gtrsim$100\,\kms\ variations in between.  This is not observed.   The
+arc geometry, and by a similar argument the spoke geometry, can thus be
+discarded.
 
@@
 the system is consistent with being viewed edge-on.  However, one
-constraint does come from the TESS transit depth scaling with
-the projected area $\ell z$.  More specifically, one can evaluate an
-``effective area'' blocked by a two-dimensional gaussian blob passing over a star by
-integrating the local gaussian weight over the stellar surface.  For
-instance, if $\ell$$\approx$$z$$\approx$0.24\,$R_\star$, then
+constraint does come if one assumes that the TESS transit depth scales
+with the projected H$\alpha$ emission area $\ell z$.  
+More specifically,
+one can evaluate an ``effective area'' blocked by a two-dimensional
+gaussian blob passing over a star by integrating the local gaussian
+weight over the stellar surface.  For instance, if
+$\ell$$\approx$$z$$\approx$0.24\,$R_\star$, then
 $\iint \exp \left(
@@
 vice-versa.  
+This constraint also implicitly assumes that the optically thick
+material is well-mixed with the hydrogen, which may not be accurate.
 
@@
   n_{\rm H} &= 
-  %\frac{1}{x}
-  %\left(
-  %  \frac{L_{\rm H\alpha}}{ \alpha^{\rm eff}_{\rm H\alpha} h \nu_{\rm H\alpha} V }
-  %\right)^{1/2},
-  %\\
-  %n_{\rm H} &=
-  5 \cdot 10^{11}\,{\rm cm}^{-3}
+  1 \cdot 10^{11}\,{\rm cm}^{-3}
   \left(
@@
   \left(
-    \frac{ 0.04\,R_\odot }{ r }
+    \frac{ 0.1\,R_\odot }{ r }
   \right)^{3/2}.
@@
 \begin{equation}
-  B_{\rm c} \gtrsim 3\,{\rm G}
+  B_{\rm c} \gtrsim 1\,{\rm G}
   \left(
-  \frac{n_{\rm H}}{5\times10^{11}\,{\rm cm}^{-3}}
-  \frac{T}{5000\,{\rm K}}
+  \frac{n_{\rm H}}{1\times10^{11}\,{\rm cm}^{-3}}
+  \frac{T}{3000\,{\rm K}}
   \right)^{1/2}.
@@
 stars have been measured to span hundreds to thousands of Gauss
-\cite{Donati2009,Kochukhov2021,Reiners2022}, this bound is easily met.
+\cite{Donati2009,Kochukhov2021,Reiners2022}, this bound is easily met at
+orbital distances of 2-4\,$R_\star$.
 
@@
 $M_{\rm gas}$$\approx$8$\times$10$^{16}$\,g from
-Section~\ref{subsec:gas}, the allowed dust masses imply $M_{\rm
+\S~\ref{subsec:gas}, the allowed dust masses imply $M_{\rm
 gas}/M_{\rm dust}$ ranges of 1-100.  More careful measurements of this
@@
 
-\item[Author Contributions] LGB is responsible for all aspects of this
-  work, including conceptualization, data analysis, interpretation,
-  manuscript preparation, and revision.
-
+%\item[Author Contributions] LGB is responsible for all aspects of this
+%  work, including conceptualization, data analysis, interpretation,
+%  manuscript preparation, and revision.
+%
 \item[Data Availability] The TESS two-minute cadence data used in this

### 2025-04-07 drivers/fit_orbits.py
fit_orbits: t0 option

@@ -1,6 +1,6 @@
 import pandas as pd
 import numpy as np
-import os
+import os, pickle
 from os.path import join
 from scipy.optimize import curve_fit
 import matplotlib.pyplot as plt
@@ -38,7 +38,7 @@ def load_rvs(component_ix=None, applymask=True):
              0]
     # based on sinusoid
     mask2 = [0,0,0,0,0,
-             0,0,0,0,1, #9 = phi 0.54.  
+             0,0,1,1,1, #9 = phi 0.54.  
              1,1,1,1,1,
              1,0,0,0,0, #16(start) = phi 0.93
              0]
@@ -336,44 +336,102 @@ def main(fittingstyle='leastsquares'):
     df_circ.to_csv(join('results/halpha_to_rv_timerseries', 'circular_summary.csv'), index=False)
     df_ecc = pd.DataFrame(ecc_summary)
     df_ecc.to_csv(join('results/halpha_to_rv_timerseries', 'eccentric_summary.csv'), index=False)
-    
+
+    # load in t0, period
+    pkldir = '/Users/luke/Dropbox/proj/cpv/results/movie_sixpanel_specriver/TIC_141146667_science_wob'
+    pklpath = join(pkldir, '141146667_specriver_cache.pkl')
+    with open(pklpath, 'rb') as f:
+        d = pickle.load(f)
+    t0 = d['t0'] # time of transit center
+    period = d['period'] # period of the transit
+
     # FINAL VISUALIZATION PLOT
-    set_style('science')
-    rcParams['font.family'] = 'Arial'
-    f = 0.85
-    fig, ax = plt.subplots(figsize=(f*3.5, f*3))
-    colors = ['#000000', '#E69F00', '#009E73']
-    for ix, fit in enumerate(all_fits):
-        t = fit['time']
-        rv = fit['rv']
-        rv_err = fit['rv_err']
-        mask = ~np.in1d(fit['_time'], t)
-        _t = fit['_time'][mask]
-        _rv = fit['_rv'][mask]
-        _rv_err = fit['_rv_err'][mask]
-        c = colors[ix]
-        t_fit = np.linspace(fit['_time'].min()-1/24,
-                            fit['_time'].max()+1/24, 5000)
-        fn = lambda x: 24 * (x - fit['_time'].min())
-        ax.errorbar(fn(t), rv, yerr=rv_err, fmt='o', c=c, ms=2)
[…]

### 2025-04-07 drivers/calc_prefactors.py
add calc_prefactors

@@ -1,0 +1,29 @@
+# n_H hydrogen
+from astropy import units as u, constants as c
+
+lambda_halpha = 6563*u.Angstrom
+nu_halpha = c.c / lambda_halpha
+hnu_Halpha = c.h * nu_halpha
+n_H_pref = (
+    2
+    * (1e27 * u.erg/u.s)**(1/2)
+    * (1e-13 * u.cm**3/u.s)**(-1/2)
+    * (hnu_Halpha)**(-1/2)
+    * (3 / (4*3.141) )**(1/2)
+    * (1 / (0.1*u.Rsun) )**(3/2)
+)
+print(f"n_H = {n_H_pref.cgs:.2e}")
+
+R = 0.1*u.Rsun
+V = 4*3.14/3 * R**3
+M_gas = n_H_pref * c.m_p * V
+
+print(f"M_gas = {M_gas.cgs:.2e}")
+
+B_pref = (
+    (8*3.141*c.k_B.cgs)**(1/2)
+    * (n_H_pref.cgs * 3000*u.K)**(1/2)
+)
+magnetic_field_equiv = [(u.erg**0.5/u.cm**1.5, u.G)]
+print(f"B = {B_pref.to(u.G, equivalencies=magnetic_field_equiv):.2e}")
+

### 2025-04-07 paper/ms.tex
update ms

@@
 star's equatorial velocity, directly demonstrating for the first
-time the existence of corotating clumps of circumstellar plasma around a CPV.
+time that corotating clumps of circumstellar plasma exist around a CPV.
 Given that cool ($10^4$ K) plasma can persist in the hot ($10^6$ K)
@@
 \cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
-these data support the idea that the magnetospheres of the
-lowest-mass stars can support long-lived, optically thick
-clumps of material that explain the sharp photometric features seen in
-CPVs.  The origin of this optically thick material and its
-microphysical opacity remain unclear.
+these data support the idea that the magnetospheres of red dwarfs can
+support long-lived, optically thick clumps of material that produce
+the sharp photometric features seen in CPVs.  The origin of this
+optically thick material and its microphysical opacity remain
+unclear.
 \end{abstract}
@@
 partially-ionized hydrogen to corotate with the star.  Based on the
-observed sinusoidal periods and peak velocities, this material's motion
+observed sinusoidal periods and velocities, this material's motion
 is not controlled by gravitational attraction to the star; it is more
@@
 3.88\,$R_\star$ for the outer clump.   These clumps transit in front of
-the star when passing from negative to positive velocity.  The innermost
-clump transits over $\approx$15\% of the period, at $\phi$=0 and
-$\phi$=1.  This spectroscopic transit happens during the latter half of
-the complex photometric feature in the TESS data.
+the star when passing from negative to positive velocity.  The
+transits of the two inner clumps last $\approx$22\% of each cycle,
+from $\phi$=-0.1 to $\phi$=+0.12 (see \S~\ref{subsec:halpha}).  This
+spectroscopic transit coincides with the latter half of the complex
+eclipse feature in the TESS data.
 
@@
 corotating circumstellar plasma clumps exist around at least one such
-star.  While starspots likely do contribute smooth photometric
-variability signals, a ``starspot-only'' scenario for the CPVs
+star.  While starspots likely do contribute smooth signals to the photometric
+variability, a ``starspot-only'' scenario for the CPVs
 \cite{Koen2021} seems to be incompatible with our observations.
@@
 significant population of hydrogen atoms in the $n$=3 excited state,
-with most H$\alpha$ emission coming from a region half the size of the
-star (see \S~\ref{subsec:halpha}).  The observed H$\alpha$ luminosity
-suggests
+with most H$\alpha$ emission in each clump coming from a region half
+the size of the star (see \S~\ref{subsec:halpha}).  The observed
+H$\alpha$ luminosity suggests
 characteristic densities and masses for the gaseous component of these
-clumps of $n_{\rm H} \sim 10^{11}$-$10^{12}$\,cm$^{-3}$ and $M_{\rm
+clumps of $n_{\rm H} \sim 10^{11}$\,cm$^{-3}$ and $M_{\rm
 gas} \sim 10^{17}$\,g (see \S~\ref{subsec:gas}).  Dust, if present, is
@@
   time-averages to ten minute sampling.
-  {\bf b-c,} Folded light curve before and after spectroscopy.  Raw
+  {\bf b-c,} Folded TESS light curve before and after spectroscopy.  Raw
   two minute data are in gray; black phase-averages to 100 points per
@@
   sequence, its photometric shape evolved during the data gap.
+  The oranges bar denote times of spectroscopic transits for the inner
+  two H$\alpha$ clumps observed with HIRES.
   }
@@
 
-Caution is required in interpreting this model's results.  
-At certain epochs the most significant spectral
-feature around any component's prior is not statistically significant.
-During such epochs, e.g.~the ``outer'' clump at $\phi$=1.07,
-the model fits noise, not signal.  At other times, the model
-underfits.  For instance, the sudden blue rise near $\phi$=0.2 is 
-poorly described by a gaussian; the assumed functional form is one of
-convenience.  Finally, the model fits the $i=\{ 0, 1 \}$, and $i=2$
-components independently.  At $\phi$=0.0 and 1.0,
-Figure~\ref{fig:halphamodel} suggests that the emission
-might come from either the inner or outer components.
-Physically however, at this epoch the inner clump
-is in transit, and the outer clump is passing behind
-the star.  At $\phi$=0.0, the double-peaked
-emission profile also matches that seen shortly afterward (at
-$\phi$=0.14) when the
-inner clump is viewed off-disk.  A physical interpretation of the
+Caution is required in interpreting this model's results.  At certain
+epochs the most significant spectral feature around any component's
+prior is not statistically significant.  During such epochs, e.g.~the
+``outer'' clump at $\phi$=1.07, the model fits noise, not signal.  At
+other times, the model underfits.  For instance, the sudden blue rise
+near $\phi$=0.2 is poorly described by a gaussian; the assumed
+functional form is one of convenience.  Finally, the model fits the
+$i=\{ 0, 1 \}$, and $i=2$ components independently.  At $\phi$=0.0 and
+1.0, Figure~\ref{fig:halphamodel} suggests that the emission might
+come from either the inner or outer components.  Physically however,
+at this epoch the inner clump is in transit, and the outer clump is
+passing behind the star.  At $\phi$=0.0, the double-peaked emission
+profile also matches that seen shortly afterward (at $\phi$=0.14) when
+the inner clump is viewed off-disk.  A physical interpretation of the
 model would therefore discard the outer clump results at this
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/sf7.pdf}
-  \caption{Orbits fit to mean radial velocities (RVs) extracted from 
-  H$\alpha$ profile fits in Figure~\ref{fig:halphamodel}.
-  Radial velocities on the vertical axis are in units of the
-  equatorial velocity, $v_{\rm eq}$=130\,\kms.
-  Each marker denotes the best-fit mean at a given epoch.
-  Solid circles were adopted in the fits; transparent X markers
-  were excluded due to concerns about their reliability
-  (see text).  The inner double-peaked clump is shown in
-  black and orange; the outer clump is shown in green.  Five draws from
-  each posterior probability distribution are shown.}
+  \includegraphics[width=0.99\textwidth]{figures/sf7.pdf}
+  \caption{{\bf a,} Orbits fit to mean radial velocities (RVs)
+  extracted from H$\alpha$ profile fits in
+  Figure~\ref{fig:halphamodel}.  Radial velocities on the vertical
+  axis are in units of the equatorial velocity, $v_{\rm
+  eq}$=130\,\kms.  Each marker denotes the best-fit gaussian mean at a
+  given epoch.  Solid circles were adopted in the fits; transparent X
+  markers were excluded due to reliability concerns (see text).  The
+  inner double-peaked clump is shown in violet and orange; the outer
+  clump is shown in green.  Five model draws from each posterior probability
+  distribution are plotted.  {\bf b,} Idealized emissivity from mean
+  model fits in Panel a, assuming a constant emission amplitude and
+  velocity width $\sigma$=0.25\,$v_{\rm eq}$ over the observation
+  sequence.}
   \label{fig:orbits}
@@
 velocity semi-amplitudes of the clumps.
-Figure~\ref{fig:orbits} shows the results assuming circular
+Figure~\ref{fig:orbits}a shows the results assuming circular
 orbits; considering the Bayesian information criterion, we found no
@@
 determine whether or not this component of the system is long-lived.
+
+For Figure~\ref{fig:orbits}b, we then used the mean orbits
+from Figure~\ref{fig:orbits}a to generate sinusoidal-in-time
+gaussians, similar to the observations.  We assumed a constant
+emission amplitude and velocity width $\sigma$=0.25\,$v_{\rm eq}$ for
+this exercise, and normalized each gaussian to unit amplitude;  the
+colorbar in Figure~\ref{fig:orbits}b thus masks the non-physical
+additive contribution near the zero-crossing of velocity.
+Compared to the behavior of the data at $\phi$=0.2-0.5
+(Figure~\ref{fig:spec}), this is highly idealized.
+Nonetheless, this exercise indicates that the transit of the inner
+clump lasts $\approx$22\% of each cycle, with a slight asymmetry
+around $\phi$=0.
 
@@
 For a uniform density clump, this suggests a total gas mass of $M_{\rm
-gas}\approx 8\times10^{16}$\,g.
+gas}\approx 2\times10^{17}$\,g.
 We emphasize that Equation~\ref{eq:numdensity} in intended to provide
@@
 clumps with masses in the range of $10^{15}$-$10^{17}$\,g.  Given
-$M_{\rm gas}$$\approx$8$\times$10$^{16}$\,g from
+$M_{\rm gas}$$\approx$2$\times$10$^{17}$\,g from
 \S~\ref{subsec:gas}, the allowed dust masses imply $M_{\rm

### 2025-04-07 paper/collect_figs.sh

@@ -33,4 +33,4 @@ cp $r/lineevolnpanel/TIC141146667_j537_lineevolnpanel_removecosmic.pdf figures/s
 
 cp $r/halpha_to_rv_timerseries/halpha_stack_3clumps.pdf figures/sf6.pdf
 
-cp $r/halpha_to_rv_timerseries/combined_circular_fit.pdf figures/sf7.pdf
+cp $r/halpha_to_rv_timerseries/merged_circular_fit.pdf figures/sf7.pdf

### 2025-04-07 drivers/fit_orbits.py
fit_orbits: improve

@@ -11,6 +11,7 @@ import jax.numpy as jnp
 import numpyro
 from numpyro.infer import MCMC, NUTS
 import numpyro.distributions as dist
+from typing import Dict, Tuple
 numpyro.set_host_device_count(2)
 
 def load_rvs(component_ix=None, applymask=True):
@@ -346,17 +347,20 @@ def main(fittingstyle='leastsquares'):
     period = d['period'] # period of the transit
 
     # FINAL VISUALIZATION PLOT
-    for phaseunits in [0, 1]:
+    set_style('science')
+    rcParams['font.family'] = 'Arial'
+    f = 0.85
+    fig, axs = plt.subplots(ncols=2, figsize=(f*6.5, f*3))
+    colors = ['violet', '#E69F00', '#009E73']
 
-        set_style('science')
-        rcParams['font.family'] = 'Arial'
-        f = 0.85
-        fig, ax = plt.subplots(figsize=(f*3.5, f*3))
-        colors = ['#000000', '#E69F00', '#009E73']
-        
+    for _ix, phaseunits in enumerate([0, 1]):
+
+        ax = axs[_ix]
+        phi0 = 0.012 # phase offset from t0 definition
+
         if phaseunits:
             # Initialize the global grid and accumulator for combining gaussian images.
-            fn_global = lambda x: ((x - t0) / period - 110)
+            fn_global = lambda x: ((x - t0) / period - 110) + phi0
             all_times = np.concatenate([fit['_time'] for fit in all_fits])
             global_min = all_times.min() - 1/24
             global_max = all_times.max() + 1/24
@@ -382,7 +386,7 @@ def main(fittingstyle='leastsquares'):
             if not phaseunits:
                 fn = lambda x: 24 * (x - fit['_time'].min())
             else:
-                fn = lambda x: ((x - t0) / period - 110)
+                fn = lambda x: ((x - t0) / period - 110) + phi0
             ax.errorbar(fn(t), rv, yerr=rv_err, fmt='o', c=c, ms=2)
             ax.errorbar(fn(_t), _rv, yerr=_rv_err, fmt='x', alpha=0.3, zorder=-1, c=c, ms=4)
             if fittingstyle == 'leastsquares':
@@ -403,14 +407,26 @@ def main(fittingstyle='leastsquares'):
                     y_mean = rv_circular(global_t_fit, *popt)
                     mean_matrix = np.tile(y_mean, (y_grid.size, 1))
[…]

### 2025-04-07 drivers/fit_orbits.py
minor

@@ -398,15 +398,21 @@ def main(fittingstyle='leastsquares'):
                 for idx in inds:
                     draw = [samp['K'][idx], samp['P'][idx], samp['t0'][idx]]
                     if not phaseunits:
-                        ax.plot(fn(t_fit), rv_circular(t_fit, *draw), '-', c=c, zorder=-2, alpha=0.3, lw=0.4)
+                        ax.plot(fn(t_fit), rv_circular(t_fit, *draw), '-', c=c,
+                                zorder=-2, alpha=0.3, lw=0.4)
                 if phaseunits:
                     popt = fit['popt_circ']
-                    ax.plot(fn(t_fit), rv_circular(t_fit, *popt), '-', c=c, zorder=-2, alpha=0.9, lw=0.8)
+                    ax.plot(fn(t_fit), rv_circular(t_fit, *popt), '-', c=c,
+                            zorder=-2, alpha=0.9, lw=0.8)
                     sigma = 0.25
                     # Compute the mean fit over the global t_fit grid.
                     y_mean = rv_circular(global_t_fit, *popt)
                     mean_matrix = np.tile(y_mean, (y_grid.size, 1))
-                    local_gauss = (1/(sigma * np.sqrt(2*np.pi))) * np.exp(-0.5 * ((Y_global - mean_matrix)/sigma)**2)
+                    local_gauss = (
+                        (1/(sigma * np.sqrt(2*np.pi)))
+                        * np.exp(-0.5 * ((Y_global - mean_matrix)/sigma)**2)
+                    )
+
                     local_gauss /= local_gauss.max()
                     gauss_total += local_gauss
 

### 2025-04-07 paper/ms.tex
update (latex cleaning)

@@
 dwarf's evolution influences its planets---especially the retention of
-their atmospheres--- has in turn become a major theme in
-exoplanet and stellar astrophysics.  Previous work has established
-that most M dwarfs host close-in planets \cite{Dressing2015} that 
-on average are subject to long circumstellar disk lifetimes
-\cite{Ribas2015}, to high doses of UV radiation \cite{France2016},
-and to a high incidence of flares and coronal mass ejections
-\cite{Gunther2020}.  However, despite extensive work in these areas,
-the plasma and magnetospheric environments that bathe young, close-in
-exoplanets remain challenging to quantify.
-Understanding these environments is crucial because they directly
-impact atmospheric retention and habitability of close-in planets.
+their atmospheres--- has in turn become a major theme in exoplanet and
+stellar astrophysics.  Previous work has established that most M
+dwarfs host close-in planets \cite{Dressing2015} that on average are
+subject to long circumstellar disk lifetimes \cite{Ribas2015}, to high
+doses of UV radiation \cite{France2016}, and to a high incidence of
+flares and coronal mass ejections \cite{Gunther2020}.  However,
+despite extensive work in these areas, the plasma and magnetospheric
+environments that bathe young, close-in exoplanets remain challenging
+to quantify.  Understanding these environments is crucial because they
+directly impact atmospheric retention and habitability of close-in
+planets.
 
@@
 rotation periods shorter than two days.  Within current sensitivity
-limits, none host disks \cite{Stauffer2017,Bouma2024}.
-However, $\approx$3\% of stars a few million years old show this complex
-photometric behavior, an observed fraction which decreases to $\approx$0.3\% by
-$\approx$150\,Myr \cite{Rebull2020}.
-CPVs are a known source of astrophysical false positives in searches for
+limits, none host disks \cite{Stauffer2017,Bouma2024}.  However,
+$\approx$3\% of stars a few million years old show this complex
+photometric behavior, an observed fraction which decreases to
+$\approx$0.3\% by $\approx$150\,Myr \cite{Rebull2020}.  CPVs are a
+known source of astrophysical false positives in searches for
 transiting exoplanets around young M dwarfs
@@
 decades, reported that stellar coronae contain both hot ($10^6$ K) and
-cool ($10^4$ K) plasma. In particular, time-series spectroscopy of stars
-with a wide range of masses has shown periodic high-velocity
+cool ($10^4$ K) plasma. In particular, time-series spectroscopy of
+stars with a wide range of masses has shown periodic high-velocity
 absorption and emission in Balmer lines such as H$\alpha$, interpreted
@@
 field, and the exact geometry of where the plasma can accumulate is
-dictated by the field's topology.  For instance, a magnetic dipole field
-tilted with respect to the stellar spin axis
-yields accumulations in a warped torus geometry
-\cite{Townsend2005}, whereas in the limit of a single strong field
-line, accumulation occurs at the line's apex, furthest from the star
-\cite{Waugh2022}.  To date, none of these spectroscopic variables have
-shown any photometric anomalies \cite{Bouma2024}, leaving open the
-issue of whether they are related to CPVs.
+dictated by the field's topology.  For instance, a magnetic dipole
+field tilted with respect to the stellar spin axis yields
+accumulations in a warped torus geometry \cite{Townsend2005}, whereas
+in the limit of a single strong field line, accumulation occurs at the
+line's apex, furthest from the star \cite{Waugh2022}.  To date, none
+of these spectroscopic variables have shown any photometric anomalies
+\cite{Bouma2024}, leaving open the issue of whether they are related
+to CPVs.
 
@@
 its brightness and rotation rate enabled an efficient search for
-variability in its line profiles.  We observed the star for five hours on
-17~February~2024 (UT) using the High Resolution Echelle Spectrometer
-(HIRES \cite{vogt_hires_1994}) on the 10\,m Keck I telescope.  TESS
-observed the star over a four week interval from 30~January~2024 to
-26~February~2024 with a duty cycle of 77\%.  During the HIRES
-observations, scattered light from the Earth caused a gap in the TESS
-photometry; TESS data collection resumed 12 hours (three rotation
-cycles) after the spectra were acquired.  Extended Data
+variability in its line profiles.  We observed the star for five hours
+on 17~February~2024 (UT) using the High Resolution Echelle
+Spectrometer (HIRES \cite{vogt_hires_1994}) on the 10\,m Keck I
+telescope.  TESS observed the star over a four week interval from
+30~January~2024 to 26~February~2024 with a duty cycle of 77\%.  During
+the HIRES observations, scattered light from the Earth caused a gap in
+the TESS photometry; TESS data collection resumed 12 hours (three
+rotation cycles) after the spectra were acquired.  Extended Data
 Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
@@
 
-% ** keck/hires: emission beyond v/veq>1
 The spectroscopy shows emission beyond the star's equatorial velocity
 ($v_{\rm eq}$=130\,\kms).  There are at least two distinct emission
-components, separated by half a cycle in phase.  The inner component at
-lower velocities has clearer sinusoidal behaviour in time and is
+components, separated by half a cycle in phase.  The inner component
+at lower velocities has clearer sinusoidal behaviour in time and is
 double-peaked, with peak semi-amplitudes of 2.07\,$v_{\rm eq}$ and
@@
 continuum early in the observation sequence, and diminishes to 10\% by
-its end.  The higher-velocity component 180$^\circ$ opposite in phase is
-detected only from $\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this outer
+its end.  The higher-velocity component 180$^\circ$ opposite in phase
+is detected only from $\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this outer
 component appears connected to the star in velocity space.  While its
@@
 partially-ionized hydrogen to corotate with the star.  Based on the
-observed sinusoidal periods and velocities, this material's motion
-is not controlled by gravitational attraction to the star; it is more
-readily explained as a partially-ionized plasma being dragged along with
-a rigidly rotating stellar magnetic field.  The velocity semi-amplitude
-of the sinusoids gives the mean distance of each clump from the stellar
-surface: 2.07\,$R_\star$ and 2.88\,$R_\star$ for the inner clumps, and
-3.88\,$R_\star$ for the outer clump.   These clumps transit in front of
-the star when passing from negative to positive velocity.  The
-transits of the two inner clumps last $\approx$22\% of each cycle,
-from $\phi$=-0.1 to $\phi$=+0.12 (see \S~\ref{subsec:halpha}).  This
-spectroscopic transit coincides with the latter half of the complex
-eclipse feature in the TESS data.
-
-% * keck/hires: behavior at v/veq<1
+observed sinusoidal periods and velocities, this material's motion is
+not controlled by gravitational attraction to the star; it is more
+readily explained as a partially-ionized plasma being dragged along
+with a rigidly rotating stellar magnetic field.  The velocity
+semi-amplitude of the sinusoids gives the mean distance of each clump
+from the stellar surface: 2.07\,$R_\star$ and 2.88\,$R_\star$ for the
+inner clumps, and 3.88\,$R_\star$ for the outer clump.   These clumps
+transit in front of the star when passing from negative to positive
+velocity.  The transits of the two inner clumps last $\approx$22\% of
+each cycle, from $\phi$=-0.1 to $\phi$=+0.12 (see
+\S~\ref{subsec:halpha}).  This spectroscopic transit coincides with
+the latter half of the complex eclipse feature in the TESS data.
+
 The H$\alpha$ line core is more complex.  At $|\Delta v / v_{\rm
@@
 circumstellar in origin.  However, the large emission feature that
-crosses the star from $\phi$=0.4-0.9 emits at an amplitude greater than
-that observed from the circumstellar components, and it crosses the
-stellar velocity surface at a speed that suggests it instead originates
-from a chromospherically bright region on the star's surface.
-Similarly, from $\phi$=0.6-1.15 a 20\% deep absorption feature slowly
-crosses the H$\alpha$ line profile.  This feature suggests either a
-chromospherically dark region (e.g.~a starspot group) crossing the
-star's surface, or an azimuthally extended absorptive component to the
-circumstellar material which is not visible in emission.  Although the
-origin of the other bright and dark streaks passing across the line core
-are similarly ambiguous, a final exercise to quantify the behavior of the
-line core is shown in Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\
-core}$ denotes the summed flux at $|\Delta v / v_{\rm eq}|<1$.  This
-panel shows that changes in the line core flux correlate with the
-broadband variability throughout most of the light curve, except near
-$\phi$$\approx$0.5, corresponding to the transit of the 3.9\,$R_\star$
-clump and the occultation of the lower-velocity clump.
+crosses the star from $\phi$=0.4-0.9 emits at an amplitude greater
+than that observed from the circumstellar components, and it crosses
+the stellar velocity surface at a speed that suggests it instead
+originates from a chromospherically bright region on the star's
+surface.  Similarly, from $\phi$=0.6-1.15 a 20\% deep absorption
+feature slowly crosses the H$\alpha$ line profile.  This feature
+suggests either a chromospherically dark region (e.g.~a starspot
+group) crossing the star's surface, or an azimuthally extended
+absorptive component to the circumstellar material which is not
+visible in emission.  Although the origin of the other bright and dark
+streaks passing across the line core are similarly ambiguous, a final
+exercise to quantify the behavior of the line core is shown in
+Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes the
+summed flux at $|\Delta v / v_{\rm eq}|<1$.  This panel shows that
+changes in the line core flux correlate with the broadband variability
+throughout most of the light curve, except near $\phi$$\approx$0.5,
+corresponding to the transit of the 3.9\,$R_\star$ clump and the
+occultation of the lower-velocity clump.
 
@@
 complex light curves \cite{Bouma2024}.   One interpretation for the
-spectroscopic variability comes from an analogy to quiescent
-solar prominences, which are cool condensations of plasma in the solar
+spectroscopic variability comes from an analogy to quiescent solar
+prominences, which are cool condensations of plasma in the solar
 corona that can last days to weeks \cite{VialEngvold2015}.  These
@@
 H$\alpha$ emitting material cannot explain the entirety of the complex
-photometric modulation;  the spectroscopic transits happen too fast, and
-at orbital phases that only partially overlap with the photometric
+photometric modulation;  the spectroscopic transits happen too fast,
+and at orbital phases that only partially overlap with the photometric
 modulations.
@@
 corotating circumstellar plasma clumps exist around at least one such
-star.  While starspots likely do contribute smooth signals to the photometric
-variability, a ``starspot-only'' scenario for the CPVs
+star.  While starspots likely do contribute smooth signals to the
+photometric variability, a ``starspot-only'' scenario for the CPVs
 \cite{Koen2021} seems to be incompatible with our observations.
@@
 the size of the star (see \S~\ref{subsec:halpha}).  The observed
-H$\alpha$ luminosity suggests
-characteristic densities and masses for the gaseous component of these
-clumps of $n_{\rm H} \sim 10^{11}$\,cm$^{-3}$ and $M_{\rm
-gas} \sim 10^{17}$\,g (see \S~\ref{subsec:gas}).  Dust, if present, is
-independently constrained to have a total mass $10^{15}\,{\rm g} <
-M_{\rm dust} < 10^{17}\,{\rm g}$ (see \S~\ref{subsec:dust}).  This
-circumstellar material could originate either from the star or from an
-external source.  Plausible external sources include an undetected old
-disk, comets, or a close-in exoplanet.  This latter scenario would
-make CPVs extrasolar analogs of the Jupiter-Io plasma torus
-(e.g.~Ref.~\cite{Bagenal1981}).
+H$\alpha$ luminosity suggests characteristic densities and masses for
+the gaseous component of these clumps of $n_{\rm H} \sim
+10^{11}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g (see
+\S~\ref{subsec:gas}).  Dust, if present, is independently constrained
+to have a total mass $10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm
+g}$ (see \S~\ref{subsec:dust}).  This circumstellar material could
+originate either from the star or from an external source.  Plausible
+external sources include an undetected old disk, comets, or a close-in
+exoplanet.  This latter scenario would make CPVs extrasolar analogs of
+the Jupiter-Io plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
 
@@
 contributions from higher-order magnetic moments
-\cite{Kochukhov2011,Shultz2018}.  There are two implications: first, the
-photometric complexity of CPVs may be a direct consequence of magnetic
-fields with highly multipolar contributions.  Second, despite this
-complexity, the observation from Figure~\ref{fig:spec} of two emission
-clumps separated 180$^\circ$ in phase is consistent with the expected
-emission from a warped plasma torus.
+\cite{Kochukhov2011,Shultz2018}.  There are two implications: first,
+the photometric complexity of CPVs may be a direct consequence of
+magnetic fields with highly multipolar contributions.  Second, despite
+this complexity, the observation from Figure~\ref{fig:spec} of two
+emission clumps separated 180$^\circ$ in phase is consistent with the
+expected emission from a warped plasma torus.
 
@@
 close-in rocky exoplanets that exist around most M dwarfs
-\cite{Dressing2015}.  However, a few percent of young M dwarfs show the CPV
-phenomenon \cite{Rebull2020}, and our data show that some of the
-complex photometric features occur when clumps of circumstellar
+\cite{Dressing2015}.  However, a few percent of young M dwarfs show
+the CPV phenomenon \cite{Rebull2020}, and our data show that some of
+the complex photometric features occur when clumps of circumstellar
 material transit the star.  The suggested geometric correction implies
@@
   \caption{Photometric evolution of TIC 141146667 near the Keck/HIRES
-  observation (green bar). 
-  {\bf a,} TESS simple aperture photometry.  The main data gaps were
-  caused by scattered light from the Earth (BTJD 3356-3358.5) and Moon
-  (BTJD 3359.5-3360.5).  Raw two minute data are in gray; black
-  time-averages to ten minute sampling.
-  {\bf b-c,} Folded TESS light curve before and after spectroscopy.  Raw
+  observation (green bar).  {\bf a,} TESS simple aperture photometry.
+  The main data gaps were caused by scattered light from the Earth
+  (BTJD 3356-3358.5) and Moon (BTJD 3359.5-3360.5).  Raw two minute
+  data are in gray; black time-averages to ten minute sampling.  {\bf
+  b-c,} Folded TESS light curve before and after spectroscopy.  Raw
   two minute data are in gray; black phase-averages to 100 points per
@@
   large eclipse feature was present both before and after the HIRES
-  sequence, its photometric shape evolved during the data gap.
-  The oranges bar denote times of spectroscopic transits for the inner
-  two H$\alpha$ clumps observed with HIRES.
-  }
+  sequence, its photometric shape evolved during the data gap.  The
+  oranges bar denote times of spectroscopic transits for the inner two
+  H$\alpha$ clumps observed with HIRES.}
   \label{fig:fulllc}
@@
 
-Extended Data Figure~\ref{fig:fulllc} shows the TESS Sector~75 data acquired near
-the epoch of spectroscopy.  The gap in coverage from BTJD
-3356.0~-~3358.5 occurred because the Earth was within 25$^\circ$ of
-the TESS camera's boresight, yielding high levels of scattered light;
-this gap included the Keck/HIRES observation epoch (green bar).  From
-BTJD 3359.4~-~3362.0, the Moon then passed within 25$^\circ$ of the
-camera's boresight.  Based on the observed level of scattered light in
-the optimal TIC~141146667 aperture, we manually masked out times from
-3359.40~-~3360.13, and judged the remainder of the data during the
-lunar approach to be usable.  Small data gaps from BTJD
-3353.55~-~3353.77 and from BTJD 3360.12~-~3360.33 were caused by data
-downlinks at the spacecraft's perigee and apogee, respectively.
-
-Extended Data Figure~\ref{fig:fulllc} shows that a large, complex eclipse
-feature was present before and after the HIRES data were
+Extended Data Figure~\ref{fig:fulllc} shows the TESS Sector~75 data
+acquired near the epoch of spectroscopy.  The gap in coverage from
+BTJD 3356.0~-~3358.5 occurred because the Earth was within
+25$^\circ$ of the TESS camera's boresight, yielding high levels of
+scattered light; this gap included the Keck/HIRES observation epoch
+(green bar).  From BTJD 3359.4~-~3362.0, the Moon then passed within
+25$^\circ$ of the camera's boresight.  Based on the observed level
+of scattered light in the optimal TIC~141146667 aperture, we
+manually masked out times from 3359.40~-~3360.13, and judged the
+remainder of the data during the lunar approach to be usable.  Small
+data gaps from BTJD 3353.55~-~3353.77 and from BTJD
+3360.12~-~3360.33 were caused by data downlinks at the spacecraft's
+perigee and apogee, respectively.
+
+Extended Data Figure~\ref{fig:fulllc} shows that a large, complex
+eclipse feature was present before and after the HIRES data were
 acquired.  From BTJD 3352~-~3356, this eclipse had two sharp local
-minima;  the local minimum at $\phi$$\approx$0.8 disappeared following
-the flare at BTJD 3353, yielding an eclipse more closely resembling a
-long ``V'' than a ``W''.  Similar state changes have previously been
-noted and discussed \cite{Stauffer2017,Bouma2024}.  The photometric
-shape therefore evolved during the twelve cycles spanning the
-3356~-~3358 gap, since the average shape from 3358-3363 more
-closely resembles the initial ``W''.
+minima;  the local minimum at $\phi$$\approx$0.8 disappeared
+following the flare at BTJD 3353, yielding an eclipse more closely
+resembling a long ``V'' than a ``W''.  Similar state changes have
+previously been noted and discussed \cite{Stauffer2017,Bouma2024}.
+The photometric shape therefore evolved during the twelve cycles
+spanning the 3356~-~3358 gap, since the average shape from 3358-3363
+more closely resembles the initial ``W''.
 
@@
 during the second half of the night, spanning 17 February 2024 10:47
-to 16:13 (UT).
-The star's airmass over this window spanned $z$=1.2-2.2, and we opted
-for a fixed 15 minute cadence over the entire sequence, except for a
-final 10 minute exposure due to increasing sky brightness at sunrise.
-We observed without the iodine cell and used the C2 decker
-(0$\farcs$86$\times$14$\farcs$0) in the red instrument configuration,
-yielding a spectral resolution $R$$\approx$45{,}000 ($\delta
-v$$\approx$6.7\,\kms; $\delta v / v_{\rm eq}$$\approx$0.05).  We binned
-the CCD readout by a factor of three in the spatial dimension, yielding
-$\approx$1,000 photons (S/N=33) per pixel in the continuum at 6500\,\AA,
-at minimum airmass.  Strong winds contributed to 1\farcs2$\pm$0\farcs2
-seeing over the night, but conditions were otherwise favorable.  We
-reduced the echelleogram to a one-dimensional spectrum using the
-standard techniques of the California Planet Survey \cite{Howard2010}.
-Figure~\ref{fig:spec}b shows the result in the vicinity of H$\alpha$
-without any additional processing.
+to 16:13 (UT).  The star's airmass over this window spanned
+$z$=1.2-2.2, and we opted for a fixed 15 minute cadence over the
+entire sequence, except for a final 10 minute exposure due to
+increasing sky brightness at sunrise.  We observed without the iodine
+cell and used the C2 decker (0$\farcs$86$\times$14$\farcs$0) in the
+red instrument configuration, yielding a spectral resolution
+$R$$\approx$45{,}000 ($\delta v$$\approx$6.7\,\kms; $\delta v / v_{\rm
+eq}$$\approx$0.05).  We binned the CCD readout by a factor of three in
+the spatial dimension, yielding $\approx$1,000 photons (S/N=33) per
+pixel in the continuum at 6500\,\AA, at minimum airmass.  Strong winds
+contributed to 1\farcs2$\pm$0\farcs2 seeing over the night, but
+conditions were otherwise favorable.  We reduced the echelleogram to a
+one-dimensional spectrum using the standard techniques of the
+California Planet Survey \cite{Howard2010}.  Figure~\ref{fig:spec}b
+shows the result in the vicinity of H$\alpha$ without any additional
+processing.
 
@@
 
-{\it Radial Velocity}---We measured the radial velocities of TIC~141146667
-from our HIRES spectra using a pipeline that we developed for
-rapidly rotating stars.  Our method is based on template-matching
-against synthetic spectra produced by the PHOENIX stellar atmosphere
-code \cite{Husser2013}.  We used the PHOENIX models with solar
-metallicity and alpha element abundances, and calibrated our pipeline
-using the standard stars described by \cite{Chubak2012}.  We used
-velocity standards spanning spectral types from G2 to M4 (Barnard's
-Star), irrespective of rotation rate.  We used \texttt{barycorrpy}
-\cite{Kanodia2018} to calculate the velocity corrections due to Earth's
-motion around the solar system barycenter and due to Earth's daily
-rotation about its axis.  Our analysis code reproduces the systemic
-velocities of known velocity standards \cite{Chubak2012} with an RMS of
-0.66\,\kms.
-
-For TIC~141146667, we measured the radial velocities using regions near
-the K~I (7700\,\AA) resonance line and three TiO bandheads (5160\,\AA,
-5450\,\AA, and 5600\,\AA).  We selected these regions because they
-provided the best matches between the synthetic and observed spectra.
-We then averaged the resulting redshift measurements over each order to
-produce the final measurement.  We used the scatter of resulting
-velocity measurements between orders to assign the RV uncertainty at
-each epoch.  The uncertainty-weighted mean systemic velocity over all
-epochs on 17~February~2024 was $\gamma$=0.6$\pm$1.5\,\kms.  The
-relative radial velocities about this mean are given in
-Table~\ref{tab:rv}.
+{\it Radial Velocity}---We measured the radial velocities of
+TIC~141146667 from our HIRES spectra using a pipeline that we
+developed for rapidly rotating stars.  Our method is based on
+template-matching against synthetic spectra produced by the PHOENIX
+stellar atmosphere code \cite{Husser2013}.  We used the PHOENIX models
+with solar metallicity and alpha element abundances, and calibrated
+our pipeline using the standard stars described by \cite{Chubak2012}.
+We used velocity standards spanning spectral types from G2 to M4
+(Barnard's Star), irrespective of rotation rate.  We used
+\texttt{barycorrpy} \cite{Kanodia2018} to calculate the velocity
+corrections due to Earth's motion around the solar system barycenter
+and due to Earth's daily rotation about its axis.  Our analysis code
+reproduces the systemic velocities of known velocity standards
+\cite{Chubak2012} with an RMS of 0.66\,\kms.
+
+For TIC~141146667, we measured the radial velocities using regions
+near the K~I (7700\,\AA) resonance line and three TiO bandheads
+(5160\,\AA, 5450\,\AA, and 5600\,\AA).  We selected these regions
+because they provided the best matches between the synthetic and
+observed spectra.  We then averaged the resulting redshift
+measurements over each order to produce the final measurement.  We
+used the scatter of resulting velocity measurements between orders to
+assign the RV uncertainty at each epoch.  The uncertainty-weighted
+mean systemic velocity over all epochs on 17~February~2024 was
+$\gamma$=0.6$\pm$1.5\,\kms.  The relative radial velocities about this
+mean are given in Table~\ref{tab:rv}.
 
@@
 K~I (7700\,\AA) resonance line using the kernel suggested by
-\cite{Gray2008}; taking the mean and standard deviation of the resulting
-value over all epochs yielded $v_{\rm eq} \sin i$=138$\pm$8\,\kms,
-consistent with the visual line broadening $\Delta
+\cite{Gray2008}; taking the mean and standard deviation of the
+resulting value over all epochs yielded $v_{\rm eq} \sin
+i$=138$\pm$8\,\kms, consistent with the visual line broadening $\Delta
 \lambda$$\approx$3\,\AA.  The star's equatorial velocity $v_{\rm eq}$
@@
 While this suggests that the viewing orientation could be nearly
-edge-on, the formal constraint is rather weak, with $i$$>$63$^\circ$ at
-2$\sigma$ (2.5$^{\rm th}$ percentile of the inclination posterior).
+edge-on, the formal constraint is rather weak, with $i$$>$63$^\circ$
+at 2$\sigma$ (2.5$^{\rm th}$ percentile of the inclination posterior).
 
@@
 
-{\it No Evidence For Binarity}---Any periodicity in the
-radial velocity time-series is ruled out at the rotation period for
+{\it No Evidence For Binarity}---Any periodicity in the radial
+velocity time-series is ruled out at the rotation period for
 semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This
@@
 astrometric model to the Gaia astrometry, is 1.23, within the usual
-range for apparently single sources.  There are no resolved companions in
-the Gaia DR3 point source catalog.  Finally, we checked the TESS light
-curve for evidence of secondary photometric periods by subtracting the
-mean CPV signal over each sector and performing a phase-dispersion
-minimization analysis \cite{Stellingwerf1978,2021zndo...1011188B}.
-There were no secondary periods in the TESS data.  Previous work
-\cite{Bouma2024} has shown that about 30\% of CPVs show evidence for
-excess noise above the Gaia single-source astrometric model, and about
-40\% of CPVs show evidence for unresolved binary companions based on
-the presence of secondary photometric periods.  This agrees with
-analyses showing that multi-periodic low-mass stars are generally
-unresolved binaries \cite{Tokovinin2018}.  Overall, the CPV binary
-fraction seems consistent with that for field M dwarfs
-\cite{Winters2019}, pointing to a weak or non-existent connection
-between the CPV phenomenon and (wide) binarity.  For TIC~141146667
-specifically, although we find no evidence for stellar multiplicity, our
-data are minimally constraining for the scenario of a low-luminosity
-companion ($F_1$/$F_2$$\lesssim$0.1) with apparent separation
-below 0$\farcs$1.
+range for apparently single sources.  There are no resolved companions
+in the Gaia DR3 point source catalog.  Finally, we checked the TESS
+light curve for evidence of secondary photometric periods by
+subtracting the mean CPV signal over each sector and performing a
+phase-dispersion minimization analysis
+\cite{Stellingwerf1978,2021zndo...1011188B}.  There were no secondary
+periods in the TESS data.  Previous work \cite{Bouma2024} has shown
+that about 30\% of CPVs show evidence for excess noise above the Gaia
+single-source astrometric model, and about 40\% of CPVs show evidence
+for unresolved binary companions based on the presence of secondary
+photometric periods.  This agrees with analyses showing that
+multi-periodic low-mass stars are generally unresolved binaries
+\cite{Tokovinin2018}.  Overall, the CPV binary fraction seems
+consistent with that for field M dwarfs \cite{Winters2019}, pointing
+to a weak or non-existent connection between the CPV phenomenon and
+(wide) binarity.  For TIC~141146667 specifically, although we find no
+evidence for stellar multiplicity, our data are minimally constraining
+for the scenario of a low-luminosity companion
+($F_1$/$F_2$$\lesssim$0.1) with apparent separation below 0$\farcs$1.
 
@@
 Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting
-best-fit SED is shown in Extended Data Figure Figure~\ref{fig:sed}.  This method has the
-most constraining power for the star's effective temperature (2972
-$\pm$ 40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface
-gravity, metallicity, and reddening are only weakly constrained.  We
-determined the star's spectral type to be M5.5Ve by visually comparing
-the HIRES spectra against the photometric standards tabulated by
-\cite{Bochanski2007}.   This result agrees with the effective
-temperature found from the SED fitting \cite{Pecaut2013}.  We measured
-the equivalent width of the H$\alpha$ line by fitting a range of
-models to the time-averaged line profile shown in
-Figure~\ref{fig:spec}, selecting the model that minimized the Bayesian
-information criterion, and numerically integrating this best fit model.  
-We found a sum of two Gaussians to be the preferred model; our quoted
-result, EW$_{{\rm H}\alpha}$=7.2$\pm$0.2\,\AA, comes from numerically
-integrating within $|\Delta v/v_{\rm eq}|<1$.  Integrating over the
-entire line profile, including the broad wings, would yield EW$_{{\rm
-H}\alpha}$=10.2$\pm$0.3\,\AA. Either value would classify the star as
-a weak-lined T Tauri \cite{Briceno2019}.
+best-fit SED is shown in Extended Data Figure Figure~\ref{fig:sed}.
+This method has the most constraining power for the star's effective
+temperature (2972 $\pm$ 40\,K) and radius (0.42 $\pm$
+0.02\,$R_\odot$); the surface gravity, metallicity, and reddening are
+only weakly constrained.  We determined the star's spectral type to be
+M5.5Ve by visually comparing the HIRES spectra against the photometric
+standards tabulated by \cite{Bochanski2007}.   This result agrees with
+the effective temperature found from the SED fitting
+\cite{Pecaut2013}.  We measured the equivalent width of the H$\alpha$
+line by fitting a range of models to the time-averaged line profile
+shown in Figure~\ref{fig:spec}, selecting the model that minimized the
+Bayesian information criterion, and numerically integrating this best
+fit model.  We found a sum of two Gaussians to be the preferred model;
+our quoted result, EW$_{{\rm H}\alpha}$=7.2$\pm$0.2\,\AA, comes from
+numerically integrating within $|\Delta v/v_{\rm eq}|<1$.  Integrating
+over the entire line profile, including the broad wings, would yield
+EW$_{{\rm H}\alpha}$=10.2$\pm$0.3\,\AA. Either value would classify
+the star as a weak-lined T Tauri \cite{Briceno2019}.
 
@@
 {\it Age: Isochrones}---The color and absolute magnitude of
-TIC~141146667 suggest that it is a pre-main sequence M dwarf, similar to
-all other known CPVs \cite{Stauffer2017,Stauffer2021,Bouma2024}.  The
-star's proximity ($d$=58\,pc) and high galactic latitude
+TIC~141146667 suggest that it is a pre-main sequence M dwarf, similar
+to all other known CPVs \cite{Stauffer2017,Stauffer2021,Bouma2024}.
+The star's proximity ($d$=58\,pc) and high galactic latitude
 ($b$=$+$53$^\circ$) yield negligible interstellar reddening along the
-line of sight \cite{Green2019}.  Extended Data Figure~\ref{fig:camd} shows the
-location of TIC~141146667 in the color--absolute magnitude diagram
-(CAMD) relative to young stellar populations including Upper Scorpius
-(USco), IC~2602, and the Pleiades.  To make this diagram, we adopted
-the USco members in the $\delta$~Sco and $\sigma$~Sco sub-associations
-from \cite{Ratzenbock2023}, and the IC~2602 and Pleiades members from
-\cite{Hunt2024}.  We assumed an average $V$-band extinction $A_{\rm
-V}$=$\{0.12, 0.11, 0.10\}\,{\rm mag}$ for USco \cite{Pecaut2016},
-IC~2602 \cite{Hunt2024}, and the Pleiades \cite{Hunt2024}
-respectively, and ages of 8\,Myr \cite{Ratzenbock2023}, 40\,Myr
-\cite{Randich2018}, and 112\,Myr \cite{Dahm2015} for each respective
-cluster.  We dereddened the photometry using the extinction
-coefficients $k_X\equiv A_X/A_0$ tabulated in
-\cite{GaiaCollaboration2018}, assuming that $A_0 = 3.1 E(B-V)$.
-
-Extended Data Figure~\ref{fig:camd} shows that TIC~141146667 falls between the USco
-and Pleiades sequences, and approximately overlaps IC~2602.  However,
-the precision of the implied age is set by the intrinsic scatter of
-these calibration sequences; the most luminous stars in the Pleiades of
-the same color have a similar absolute magnitude as TIC~141146667.
-Previous work \cite{Stauffer2021} has also noted that in the Gaia
-passbands, CPVs tend to be photometrically redder and more luminous than
-single stars in any given cluster, similar to other rapid rotators.
-While this effect complicates any attempt at age inference based on the
-Gaia photometry, it suggests that the Pleiades may be a better
-comparison population than IC~2602.  We take the star's
-location in the color--absolute magnitude diagram to suggest age bounds
-$t_{\rm CAMD}$$\sim$30-150\,Myr.
+line of sight \cite{Green2019}.  Extended Data Figure~\ref{fig:camd}
+shows the location of TIC~141146667 in the color--absolute magnitude
+diagram (CAMD) relative to young stellar populations including Upper
+Scorpius (USco), IC~2602, and the Pleiades.  To make this diagram, we
+adopted the USco members in the $\delta$~Sco and $\sigma$~Sco
+sub-associations from \cite{Ratzenbock2023}, and the IC~2602 and
+Pleiades members from \cite{Hunt2024}.  We assumed an average $V$-band
+extinction $A_{\rm V}$=$\{0.12, 0.11, 0.10\}\,{\rm mag}$ for USco
+\cite{Pecaut2016}, IC~2602 \cite{Hunt2024}, and the Pleiades
+\cite{Hunt2024} respectively, and ages of 8\,Myr
+\cite{Ratzenbock2023}, 40\,Myr \cite{Randich2018}, and 112\,Myr
+\cite{Dahm2015} for each respective cluster.  We dereddened the
+photometry using the extinction coefficients $k_X\equiv A_X/A_0$
+tabulated in \cite{GaiaCollaboration2018}, assuming that $A_0 = 3.1
+E(B-V)$.
+
+Extended Data Figure~\ref{fig:camd} shows that TIC~141146667 falls
+between the USco and Pleiades sequences, and approximately overlaps
+IC~2602.  However, the precision of the implied age is set by the
+intrinsic scatter of these calibration sequences; the most luminous
+stars in the Pleiades of the same color have a similar absolute
+magnitude as TIC~141146667.  Previous work \cite{Stauffer2021} has
+also noted that in the Gaia passbands, CPVs tend to be photometrically
+redder and more luminous than single stars in any given cluster,
+similar to other rapid rotators.  While this effect complicates any
+attempt at age inference based on the Gaia photometry, it suggests
+that the Pleiades may be a better comparison population than IC~2602.
+We take the star's location in the color--absolute magnitude diagram
+to suggest age bounds $t_{\rm CAMD}$$\sim$30-150\,Myr.
 
 {\it Age: Lithium}---The depletion of lithium due to $^7$Li(p,
-$\alpha$)$^4$He burning in the cores of low-mass stars has been studied
-for over sixty years \cite{Hayashi1963,Bildsten1997,Burke2004}.
-\cite{Wood2023} provided a recent overview: an abbreviated
-summary is that sufficiently cool and young M dwarfs show the 6707.8\,\AA\
-doublet in absorption, $\gtrsim$10\% below their continua.  However unlike
-for Sun-like stars, the continuum for M dwarfs is challenging to define due to
-their molecular absorption.  We therefore attempted a lithium measurement by
-constructing a wavelength-binned and Doppler-corrected TIC~141146667
-spectrum, assigning its uncertainties based on the measured scatter
-across the five hour dataset.  We then compared this average spectrum
-against the nearest matching M6 template from \cite{Bochanski2007}.  The
-data show a small depression near the expected lithium wavelength,
-potentially consistent with the $\Delta \lambda$$\approx$3\,\AA\ line
-broadening.  This feature nominally yields ${\rm EW}_{\rm
-Li}$=71$^{+18}_{-13}$\,m\AA, where the statistical uncertainties are
-evaluated using a bootstrap resampling technique from the statistical
-uncertainties in the HIRES spectrum.  However, the systematic uncertainties associated
-with the continuum normalization are likely comparable to
-the amplitude of this feature; we therefore treat the result of this
-measurement as a $2\sigma$ upper limit: ${\rm EW}_{\rm Li}$$<$107\,m\AA.
+$\alpha$)$^4$He burning in the cores of low-mass stars has been
+studied for over sixty years
+\cite{Hayashi1963,Bildsten1997,Burke2004}.  \cite{Wood2023} provided a
+recent overview: an abbreviated summary is that sufficiently cool and
+young M dwarfs show the 6707.8\,\AA\ doublet in absorption,
+$\gtrsim$10\% below their continua.  However unlike for Sun-like
+stars, the continuum for M dwarfs is challenging to define due to
+their molecular absorption.  We therefore attempted a lithium
+measurement by constructing a wavelength-binned and Doppler-corrected
+TIC~141146667 spectrum, assigning its uncertainties based on the
+measured scatter across the five hour dataset.  We then compared this
+average spectrum against the nearest matching M6 template from
+\cite{Bochanski2007}.  The data show a small depression near the
+expected lithium wavelength, potentially consistent with the $\Delta
+\lambda$$\approx$3\,\AA\ line broadening.  This feature nominally
+yields ${\rm EW}_{\rm Li}$=71$^{+18}_{-13}$\,m\AA, where the
+statistical uncertainties are evaluated using a bootstrap resampling
+technique from the statistical uncertainties in the HIRES spectrum.
+However, the systematic uncertainties associated with the continuum
+normalization are likely comparable to the amplitude of this feature;
+we therefore treat the result of this measurement as a $2\sigma$ upper
+limit: ${\rm EW}_{\rm Li}$$<$107\,m\AA.
 
@@
 
-Despite uncertainties in the details, what can be stated with confidence
-is that lithium is not abundant in the spectrum of TIC~141146667.
-Extended Data Figure~\ref{fig:liew_population} compares our upper limit against the
-equivalent width measurements reported by \cite{Jeffries2023}
-based on the Gaia-ESO spectroscopic survey; Extended Data Figure~\ref{fig:hirescuts}
-shows the associated raw spectra.  If the star were $\lesssim$20\,Myr
-old, at its temperature we would expect to see lithium in abundance
+Despite uncertainties in the details, what can be stated with
+confidence is that lithium is not abundant in the spectrum of
+TIC~141146667.  Extended Data Figure~\ref{fig:liew_population}
+compares our upper limit against the equivalent width measurements
+reported by \cite{Jeffries2023} based on the Gaia-ESO spectroscopic
+survey; Extended Data Figure~\ref{fig:hirescuts} shows the associated
+raw spectra.  If the star were $\lesssim$20\,Myr old, at its
+temperature we would expect to see lithium in abundance
 ($>$400\,m\AA).  Since we do not, we can set an empirical bound on the
@@
 detections to be in $\lesssim$200\,Myr old clusters \cite{Bouma2024};
-the remaining 10\% were not associated with any coeval
-population.
-Similarly, studies of rotation in $\lesssim$100\,Myr clusters serendipitously found
-$\approx$50-100 examples of the class
+the remaining 10\% were not associated with any coeval population.
+Similarly, studies of rotation in $\lesssim$100\,Myr clusters
+serendipitously found $\approx$50-100 examples of the class
 \cite{Rebull2016,Stauffer2017,Stauffer2018,Rebull2018,Zhan2019,Rebull2020,Stauffer2021,Rebull2022,Popinchalk2023},
@@
   \includegraphics[width=\textwidth]{figures/sf5.pdf}
-  \caption{Time evolution of select regions in the Keck/HIRES
-  spectra from 17 February 2024.
-  We made this plot by applying a windowed outlier rejection to remove
-  cosmic rays and then smoothing each spectrum with a Gaussian filter.
-  The horizontal axis shows the velocity relative to each
-  line's rest wavelength, normalized by the stellar equatorial
-  velocity.  
-  H$\alpha$ is the only Balmer line to show periodic variability of
-  the form seen in Figure~\ref{fig:spec}.
-  The He 5876\,\AA\ line shows a time-dynamic blueshift that 
-  differs from the Balmer lines.
-  Li 6708\,\AA\ shows no obvious absorption.
-  }
+  \caption{Time evolution of select regions in the Keck/HIRES spectra
+  from 17 February 2024.  We made this plot by applying a windowed
+  outlier rejection to remove cosmic rays and then smoothing each
+  spectrum with a Gaussian filter.  The horizontal axis shows the
+  velocity relative to each line's rest wavelength, normalized by the
+  stellar equatorial velocity.  H$\alpha$ is the only Balmer line to
+  show periodic variability of the form seen in Figure~\ref{fig:spec}.
+  The He 5876\,\AA\ line shows a time-dynamic blueshift that differs
+  from the Balmer lines.  Li 6708\,\AA\ shows no obvious absorption. }
   \label{fig:hirescuts}
@@
 
-Extended Data Figure~\ref{fig:hirescuts} shows a few regions of interest in the
-HIRES spectra, which cover 3650-7960\,\AA.  Higher order Balmer lines
-including H$\gamma$ and H$\delta$ ($n=5\rightarrow2$ and
-$n=6\rightarrow2$) do show variability outside the line core.
-However, this variability is not clearly periodic in the same manner
-as the emission seen in H$\alpha$.  This could be because there are
-insufficient hydrogen ions in the relevant excited states, or because
-the spectra have lower precision in these bluer regions.  The Ca HK
-doublet is also detected in emission, while the continuum near it is
-not.  Chromospheric emission from the magnesium triplet is also
-detected, but these lines are too blended to be usable.
+Extended Data Figure~\ref{fig:hirescuts} shows a few regions of
+interest in the HIRES spectra, which cover 3650-7960\,\AA.  Higher
+order Balmer lines including H$\gamma$ and H$\delta$
+($n=5\rightarrow2$ and $n=6\rightarrow2$) do show variability outside
+the line core.  However, this variability is not clearly periodic in
+the same manner as the emission seen in H$\alpha$.  This could be
+because there are insufficient hydrogen ions in the relevant excited
+states, or because the spectra have lower precision in these bluer
+regions.  The Ca HK doublet is also detected in emission, while the
+continuum near it is not.  Chromospheric emission from the magnesium
+triplet is also detected, but these lines are too blended to be
+usable.
 
 Extended Data Figure~\ref{fig:hirescuts} provides a novel view on the
-blue excess that appeared at $\phi$$\approx$0.2 in H$\alpha$, H$\gamma$,
-H$\delta$, and He 5876\,\AA.  At the same epoch, H$\alpha$ additionally
-shows a red clump of emission, and H$\gamma$ and H$\delta$ are also
-broadened on the red wing.  The rise of this emission in $<$15\,minutes
-might suggest a more sudden flow, rather than a stable, periodic
-component.  For instance, a stellar flare might be connected to such a
-sudden rise.  However, this idea seems incompatible with the sinusoidal
-emission seen later from $\phi$$\approx$0.5-1.0, and with the fact that
-flares typically excite iron lines in the blue HIRES orders, which are
-not observed.  More time-series spectroscopy would be needed to clarify
-this type of variability, in particular whether it is periodic or
-stochastic.
+blue excess that appeared at $\phi$$\approx$0.2 in H$\alpha$,
+H$\gamma$, H$\delta$, and He 5876\,\AA.  At the same epoch, H$\alpha$
+additionally shows a red clump of emission, and H$\gamma$ and
+H$\delta$ are also broadened on the red wing.  The rise of this
+emission in $<$15\,minutes might suggest a more sudden flow, rather
+than a stable, periodic component.  For instance, a stellar flare
+might be connected to such a sudden rise.  However, this idea seems
+incompatible with the sinusoidal emission seen later from
+$\phi$$\approx$0.5-1.0, and with the fact that flares typically excite
+iron lines in the blue HIRES orders, which are not observed.  More
+time-series spectroscopy would be needed to clarify this type of
+variability, in particular whether it is periodic or stochastic.
 
@@
 absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ resonance
-line are both visible in Extended Data Figure~\ref{fig:hirescuts}.  In the latter,
-narrow telluric absorption features overlap the blue wing of the line.
-Neither of these regions shows any notable variability.
+line are both visible in Extended Data Figure~\ref{fig:hirescuts}.  In
+the latter, narrow telluric absorption features overlap the blue wing
+of the line.  Neither of these regions shows any notable variability.
 
@@
   \includegraphics[width=0.55\textwidth]{figures/sf6.pdf}
-  \caption{Time-variable fit to H$\alpha$ line profiles.
-  {\it Left column:} Raw spectrum at each epoch $f_{\lambda}$ minus
-  the time-averaged spectrum $f_{\langle t \rangle}$ (as in
-  Figure~\ref{fig:spec}e).
-  Underplotted sinusoids are not fits; they are meant to guide the eye.
-  {\it Middle columns:} Model of emission from the inner clump (sum of
-  two gaussians) and the outer clump (single gaussian), plotted over
-  the data.
-  {\it Right column:} Residual of the left column after subtracting
-  the sum of the two middle columns, leaving variability in the line
-  core.  
-  \S~\ref{subsec:halpha} discusses the use of this model.
-  }
+  \caption{Time-variable fit to H$\alpha$ line profiles.  {\it Left
+  column:} Raw spectrum at each epoch $f_{\lambda}$ minus the
+  time-averaged spectrum $f_{\langle t \rangle}$ (as in
+  Figure~\ref{fig:spec}e).  Underplotted sinusoids are not fits; they
+  are meant to guide the eye.  {\it Middle columns:} Model of emission
+  from the inner clump (sum of two gaussians) and the outer clump
+  (single gaussian), plotted over the data.  {\it Right column:}
+  Residual of the left column after subtracting the sum of the two
+  middle columns, leaving variability in the line core.
+  \S~\ref{subsec:halpha} discusses the use of this model.  }
   \label{fig:halphamodel}
@@
 Given that a full radiative transfer simulation was outside our scope,
-we opted to construct a phenomenological model aimed at capturing 
-the emission from the circumstellar material.  We did this by
-fitting each spectral epoch with a multi-component
-gaussian, after having subtracted the time-average line profile as in
-Figure~\ref{fig:spec}e.  The results of this exercise are shown in
+we opted to construct a phenomenological model aimed at capturing the
+emission from the circumstellar material.  We did this by fitting each
+spectral epoch with a multi-component gaussian, after having
+subtracted the time-average line profile as in Figure~\ref{fig:spec}e.
+The results of this exercise are shown in
 Figure~\ref{fig:halphamodel}; details in the implementation and
@@
 inner}$$\approx$2.5\,$v_{\rm eq}$) clump would be well-fit by a sum of
-two gaussians because it is visually double-peaked in the raw
-data from $\phi$=0.15-0.35 and $\phi$=0.65-0.85
-(Figure~\ref{fig:spec}b).  We assumed that the ``outer'' ($K_{\rm
-outer}$$\approx$3.9\,$v_{\rm eq}$) clump would be better fit by a
-single gaussian, based on its behavior from $\phi$=0.6-0.9.  Each
-gaussian component has three free parameters at each spectral epoch:
-the mean $\mu$, standard deviation $\sigma$, and amplitude $A$.
-We labelled the inner component's two gaussians $i=\{ 0, 1 \}$,
-and the single outer component as $i=2$.  Given the complexity of the
-line profile data (Figure~\ref{fig:halphamodel} left column), the
-likelihood function for this model is multimodal.  We therefore
-imposed the prior constraints that $A_i \sim \mathcal{U}[0,1]$,
+two gaussians because it is visually double-peaked in the raw data
+from $\phi$=0.15-0.35 and $\phi$=0.65-0.85 (Figure~\ref{fig:spec}b).
+We assumed that the ``outer'' ($K_{\rm outer}$$\approx$3.9\,$v_{\rm
+eq}$) clump would be better fit by a single gaussian, based on its
+behavior from $\phi$=0.6-0.9.  Each gaussian component has three free
+parameters at each spectral epoch: the mean $\mu$, standard deviation
+$\sigma$, and amplitude $A$.  We labelled the inner component's two
+gaussians $i=\{ 0, 1 \}$, and the single outer component as $i=2$.
+Given the complexity of the line profile data
+(Figure~\ref{fig:halphamodel} left column), the likelihood function
+for this model is multimodal.  We therefore imposed the prior
+constraints that $A_i \sim \mathcal{U}[0,1]$,
 $\sigma_i/v_{\rm eq} \sim \mathcal{U}[0,1]$, and further assumed
@@
   inner double-peaked clump is shown in violet and orange; the outer
-  clump is shown in green.  Five model draws from each posterior probability
-  distribution are plotted.  {\bf b,} Idealized emissivity from mean
-  model fits in Panel a, assuming a constant emission amplitude and
-  velocity width $\sigma$=0.25\,$v_{\rm eq}$ over the observation
-  sequence.}
+  clump is shown in green.  Five model draws from each posterior
+  probability distribution are plotted.  {\bf b,} Idealized emissivity
+  from mean model fits in Panel a, assuming a constant emission
+  amplitude and velocity width $\sigma$=0.25\,$v_{\rm eq}$ over the
+  observation sequence.}
   \label{fig:orbits}
@@
 Table~\ref{tab:halphamodelparams} to quantify the orbital periods and
-velocity semi-amplitudes of the clumps.
-Figure~\ref{fig:orbits}a shows the results assuming circular
-orbits; considering the Bayesian information criterion, we found no
-reason to prefer eccentric orbits.  By visually
-inspecting Extended Data Figure~\ref{fig:halphamodel}, we excluded
-epochs where our gaussian profile fitting failed to either detect or
-else adequately represent the circumstellar emission.  We then used
-NumPyro to sample the Gaussian likelihood for a Keplerian orbit
-with the NUTS algorithm \cite{Phan2019}.  We used the measurement
-uncertainties from each estimated mean radial velocity value and
-included an additional jitter term in quadrature.  This procedure
-yielded orbital periods and semi-amplitudes of
+velocity semi-amplitudes of the clumps.  Figure~\ref{fig:orbits}a
+shows the results assuming circular orbits; considering the Bayesian
+information criterion, we found no reason to prefer eccentric orbits.
+By visually inspecting Extended Data Figure~\ref{fig:halphamodel}, we
+excluded epochs where our gaussian profile fitting failed to either
+detect or else adequately represent the circumstellar emission.  We
+then used NumPyro to sample the Gaussian likelihood for a Keplerian
+orbit with the NUTS algorithm \cite{Phan2019}.  We used the
+measurement uncertainties from each estimated mean radial velocity
+value and included an additional jitter term in quadrature.  This
+procedure yielded orbital periods and semi-amplitudes of
 $P_0$=$3.92\pm0.03$\,hr, $K_0/v_{\rm eq}$=2.07$\pm$0.04;
@@
 and $P_2$=$3.88\pm0.20$\,hr, $K_1/v_{\rm eq}$=3.88$\pm$0.25.
-The periods for the inner double-peaked clump are therefore consistent with the
-photometric $3.930\pm0.001$\,hr period within a precision of two
-minutes.  The ``period'' for the outer clump is ambiguous because the
-H$\alpha$ data only support the idea of a periodic orbit of material
-well-fit by gaussian emission from $\phi$$\approx$0.5-1.0.  From
-$\phi$=0-0.2, there is no detectable emission, and from
+The periods for the inner double-peaked clump are therefore consistent
+with the photometric $3.930\pm0.001$\,hr period within a precision of
+two minutes.  The ``period'' for the outer clump is ambiguous because
+the H$\alpha$ data only support the idea of a periodic orbit of
+material well-fit by gaussian emission from $\phi$$\approx$0.5-1.0.
+From $\phi$=0-0.2, there is no detectable emission, and from
 $\phi$=0.2-0.4, the emission spans 1-4\,$v_{\rm eq}$ without taking a
@@
 although this emission is present, its variability in time is
-inconsistent with the idea of a stable clump of material.
-Additional observations would be needed to conclusively
-determine whether or not this component of the system is long-lived.
-
-For Figure~\ref{fig:orbits}b, we then used the mean orbits
-from Figure~\ref{fig:orbits}a to generate sinusoidal-in-time
-gaussians, similar to the observations.  We assumed a constant
-emission amplitude and velocity width $\sigma$=0.25\,$v_{\rm eq}$ for
-this exercise, and normalized each gaussian to unit amplitude;  the
-colorbar in Figure~\ref{fig:orbits}b thus masks the non-physical
-additive contribution near the zero-crossing of velocity.
-Compared to the behavior of the data at $\phi$=0.2-0.5
-(Figure~\ref{fig:spec}), this is highly idealized.
-Nonetheless, this exercise indicates that the transit of the inner
-clump lasts $\approx$22\% of each cycle, with a slight asymmetry
-around $\phi$=0.
-
-{\it Physical dimensions of the emitting region}---The measured velocity
-widths from the circumstellar emission contain information about the
-size of the emitting region via the condition for rigid corotation.
-Consider a clump in cylindrical coordinates with arbitrary radial extent
-$r$, azimuthal extent $\ell$, and height $z$.  A range of shapes,
-including an ``arc'' with $\ell \gg r$, a ``spoke'' with $r \gg \ell$, and
-a ``blob'' with $r \approx \ell \approx z$ are all a priori possible.
-However, at quadrature, the observed velocity width of emission is
-sensitive to the radial extent of the circumstellar material.  At
-mid-transit, the observed velocity width is sensitive to the azimuthal
-extent.  An arc configuration would minimize the observed velocity width
-$\sigma$ at quadrature, and maximize it during transit, with
-$\gtrsim$100\,\kms\ variations in between.  This is not observed.   The
-arc geometry, and by a similar argument the spoke geometry, can thus be
-discarded.
+inconsistent with the idea of a stable clump of material.  Additional
+observations would be needed to conclusively determine whether or not
+this component of the system is long-lived.
+
+For Figure~\ref{fig:orbits}b, we then used the mean orbits from
+Figure~\ref{fig:orbits}a to generate sinusoidal-in-time gaussians,
+similar to the observations.  We assumed a constant emission amplitude
+and velocity width $\sigma$=0.25\,$v_{\rm eq}$ for this exercise, and
+normalized each gaussian to unit amplitude;  the colorbar in
+Figure~\ref{fig:orbits}b thus masks the non-physical additive
+contribution near the zero-crossing of velocity.  Compared to the
+behavior of the data at $\phi$=0.2-0.5 (Figure~\ref{fig:spec}), this
+is highly idealized.  Nonetheless, this exercise indicates that the
+transit of the inner clump lasts $\approx$22\% of each cycle, with a
+slight asymmetry around $\phi$=0.
+
+{\it Physical dimensions of the emitting region}---The measured
+velocity widths from the circumstellar emission contain information
+about the size of the emitting region via the condition for rigid
+corotation.  Consider a clump in cylindrical coordinates with
+arbitrary radial extent $r$, azimuthal extent $\ell$, and height $z$.
+A range of shapes, including an ``arc'' with $\ell \gg r$, a ``spoke''
+with $r \gg \ell$, and a ``blob'' with $r \approx \ell \approx z$ are
+all a priori possible.  However, at quadrature, the observed velocity
+width of emission is sensitive to the radial extent of the
+circumstellar material.  At mid-transit, the observed velocity width
+is sensitive to the azimuthal extent.  An arc configuration would
+minimize the observed velocity width $\sigma$ at quadrature, and
+maximize it during transit, with $\gtrsim$100\,\kms\ variations in
+between.  This is not observed.   The arc geometry, and by a similar
+argument the spoke geometry, can thus be discarded.
 
 At quadrature, the inner clumps show $\sigma_i$$\approx$0.24\,$v_{\rm
-eq}$, implying that 68\% of the emission comes from a volume with length
-in the radial dimension $r_i$=$2\sigma_i / \Omega$$=$0.48\,$R_\star$,
-and that 95\% of the emission comes from within 0.96\,$R_\star$.  These
-values have relative uncertainties of $\approx$5\%, based on the
-uncertainties in the measured velocity dispersions.  The two inner
-clumps are centered at orbital distances of 2.07\,$R_\star$ and 2.88\,$R_\star$.
-There is therefore physical overlap in their spatial distributions.
-These two clumps could in fact be a single clump with an optically thick
-H$\alpha$ line core.  Regardless of this nuance, the implication is that
-the full length in the radial dimension of these two inner emitting
-clumps is approximately equal to the star's diameter.  At mid-transit, these
+eq}$, implying that 68\% of the emission comes from a volume with
+length in the radial dimension $r_i$=$2\sigma_i /
+\Omega$$=$0.48\,$R_\star$, and that 95\% of the emission comes from
+within 0.96\,$R_\star$.  These values have relative uncertainties of
+$\approx$5\%, based on the uncertainties in the measured velocity
+dispersions.  The two inner clumps are centered at orbital distances
+of 2.07\,$R_\star$ and 2.88\,$R_\star$.  There is therefore physical
+overlap in their spatial distributions.  These two clumps could in
+fact be a single clump with an optically thick H$\alpha$ line core.
+Regardless of this nuance, the implication is that the full length in
+the radial dimension of these two inner emitting clumps is
+approximately equal to the star's diameter.  At mid-transit, these
 inner clumps likely have a similar velocity dispersion, although with
@@
 with the projected H$\alpha$ emission area $\ell z$.  
-More specifically,
-one can evaluate an ``effective area'' blocked by a two-dimensional
-gaussian blob passing over a star by integrating the local gaussian
-weight over the stellar surface.  For instance, if
+More specifically, one can evaluate an ``effective area'' blocked by a
+two-dimensional gaussian blob passing over a star by integrating the
+local gaussian weight over the stellar surface.  For instance, if
 $\ell$$\approx$$z$$\approx$0.24\,$R_\star$, then
@@
 \right) {\rm d}x \, {\rm d}y$
-suggests 11.5\% of the star being ``blocked'', a geometric factor which
-would need to be in turn multiplied by an unknown opacity factor to
-produce the observed transit depth ($\delta$$\approx$5\%).  In general
-though, there is a degeneracy between $z$ and this opacity factor; larger
-vertical heights are allowed for lower optical depths in absorption, and
-vice-versa.  
-This constraint also implicitly assumes that the optically thick
-material is well-mixed with the hydrogen, which may not be accurate.
+suggests 11.5\% of the star being ``blocked'', a geometric factor
+which would need to be in turn multiplied by an unknown opacity factor
+to produce the observed transit depth ($\delta$$\approx$5\%).  In
+general though, there is a degeneracy between $z$ and this opacity
+factor; larger vertical heights are allowed for lower optical depths
+in absorption, and vice-versa.  This constraint also implicitly
+assumes that the optically thick material is well-mixed with the
+hydrogen, which may not be accurate.
 
@@
 hydrogen number density, plasma temperature, ionization fraction, and
-magnetic field strength can be estimated from the available data.
-We caution that the following estimates are order of magnitude
+magnetic field strength can be estimated from the available data.  We
+caution that the following estimates are order of magnitude
 calculations that assume a simple uniform-density plasma: detailed
@@
 recombination.  We neglect scattering because Figure~\ref{fig:spec}
-and Extended Data Figure~\ref{fig:hirescuts} show the amplitude of the circumstellar
-H$\alpha$ emission varying by a factor of $\approx$5, in a manner
-uncorrelated with any variability in the chromospheric line core.  The
-volume emissivity under case B recombination can be written
+and Extended Data Figure~\ref{fig:hirescuts} show the amplitude of the
+circumstellar H$\alpha$ emission varying by a factor of $\approx$5, in
+a manner uncorrelated with any variability in the chromospheric line
+core.  The volume emissivity under case B recombination can be written
 \begin{equation} j_{\rm H\alpha} = n_{\rm e} n_{\rm p} \alpha^{\rm
@@
 For a uniform density clump, this suggests a total gas mass of $M_{\rm
-gas}\approx 2\times10^{17}$\,g.
-We emphasize that Equation~\ref{eq:numdensity} in intended to provide
-only an order of magnitude estimate for the number density implied by
-the observed H$\alpha$ emission.  In detail, the effective
-recombination rate and the ionization fraction each vary with density
-and temperature; a more thorough estimate would iteratively solve the
-equations of detailed balance and radiative transfer
-(e.g.~\cite{CollierCameron1989} Figure~8), and potentially also
-consider departures from local thermodynamic equilibrium.
+gas}\approx 2\times10^{17}$\,g.  We emphasize that
+Equation~\ref{eq:numdensity} in intended to provide only an order of
+magnitude estimate for the number density implied by the observed
+H$\alpha$ emission.  In detail, the effective recombination rate and
+the ionization fraction each vary with density and temperature; a more
+thorough estimate would iteratively solve the equations of detailed
+balance and radiative transfer (e.g.~\cite{CollierCameron1989}
+Figure~8), and potentially also consider departures from local
+thermodynamic equilibrium.
 
@@
 the clump follows from the requirement that the magnetic pressure
-exceed the thermal pressure, $B_{\rm c}^2 / 8\pi > n_{\rm H} k T$.  Although
-we do not know the plasma temperature, if it were significantly beyond
-1,000-10,000\,K, we would either fully ionize the hydrogen, or not
-ionize enough of it.  The field strength at the clump must therefore
-exceed
+exceed the thermal pressure, $B_{\rm c}^2 / 8\pi > n_{\rm H} k T$.
+Although we do not know the plasma temperature, if it were
+significantly beyond 1,000-10,000\,K, we would either fully ionize the
+hydrogen, or not ionize enough of it.  The field strength at the clump
+must therefore exceed
 \begin{equation}
@@
 stars have been measured to span hundreds to thousands of Gauss
-\cite{Donati2009,Kochukhov2021,Reiners2022}, this bound is easily met at
-orbital distances of 2-4\,$R_\star$.
+\cite{Donati2009,Kochukhov2021,Reiners2022}, this bound is easily met
+at orbital distances of 2-4\,$R_\star$.
 
@@
 
-Regarding the upper limit, Extended Data Figure~\ref{fig:sed} shows the SED.  While
-AllWISE \cite{Cutri2014} yielded a confident W3 detection
-(9.8$\sigma$) consistent with the photospheric extrapolation from bluer
-bandpasses, the W4 extraction yielded only a marginal indication
-(1.7$\sigma$) of detectable flux.  Similar to other CPVs
+Regarding the upper limit, Extended Data Figure~\ref{fig:sed} shows
+the SED.  While AllWISE \cite{Cutri2014} yielded a confident W3
+detection (9.8$\sigma$) consistent with the photospheric extrapolation
+from bluer bandpasses, the W4 extraction yielded only a marginal
+indication (1.7$\sigma$) of detectable flux.  Similar to other CPVs
 \cite{Stauffer2017,Bouma2024}, the photometric uncertainties from WISE
@@
 from absorption and scattering $\tau$ to be at least unity.  The
-optical depth can be written $\tau = n \sigma \ell$, where
-$\sigma$ is the cross-section, $n$ is the number density, $\ell$ is
-the path length.  For spherical dust
-grains in the optical, $\sigma = Q_{\rm ext} \pi a^2$, where $Q_{\rm
-ext}$ is the extinction efficiency parameter, tabulated e.g.~by
-\cite{Croll2014} in their Figure 13.  \cite{Sanderson2023} calculated
-the relevant cloud mass for this problem assuming a spherical dust
-clump of size $r$, and they found
+optical depth can be written $\tau = n \sigma \ell$, where $\sigma$ is
+the cross-section, $n$ is the number density, $\ell$ is the path
+length.  For spherical dust grains in the optical, $\sigma = Q_{\rm
+ext} \pi a^2$, where $Q_{\rm ext}$ is the extinction efficiency
+parameter, tabulated e.g.~by \cite{Croll2014} in their Figure 13.
+\cite{Sanderson2023} calculated the relevant cloud mass for this
+problem assuming a spherical dust clump of size $r$, and they found
 \begin{equation}
@@
 
-Three relevant objects for comparison include solar
-prominences, planetesimals, and comets.  Prominences of the Sun have
-gas masses of $10^{14}$\,g-$10^{16}$\,g \cite{VialEngvold2015}.
-A planetesimal of mass $\approx$10$^{15}$\,g with a bulk density of
-1\,g\,cm$^{-3}$ would have a diameter of order one kilometer.
-Halley's comet has a mass of order $10^{17}$\,g \cite{Rickman1989}, of
-which $\sim$$10^{14}$\,g is shed per orbit, most of which inspirals
-toward the Sun due to Poynting-Robertson drag.
-
-To summarize, if dust is responsible for
-the broadband variability of CPVs, it would need to be concentrated in
-clumps with masses in the range of $10^{15}$-$10^{17}$\,g.  Given
-$M_{\rm gas}$$\approx$2$\times$10$^{17}$\,g from
-\S~\ref{subsec:gas}, the allowed dust masses imply $M_{\rm
-gas}/M_{\rm dust}$ ranges of 1-100.  More careful measurements of this
-ratio---in particular by inferring the dust mass through high
-precision infrared spectrophotometry---could provide a path for
-distinguishing the scenario of a trapped stellar outflow from an
-accumulation of externally-sourced material.  While there are several
-plausible external sources, feeding through a low-mass disk in
-particular cannot be ruled out based on typical disk depletion times
-\cite{Haisch2001}.  Observations of infrared excesses and accretion
-signatures in low-mass stars tens of millions of years old suggest a
-broad lifetime distribution for such disks
+Three relevant objects for comparison include solar prominences,
+planetesimals, and comets.  Prominences of the Sun have gas masses of
+$10^{14}$\,g-$10^{16}$\,g \cite{VialEngvold2015}.  A planetesimal of
+mass $\approx$10$^{15}$\,g with a bulk density of 1\,g\,cm$^{-3}$
+would have a diameter of order one kilometer.  Halley's comet has a
+mass of order $10^{17}$\,g \cite{Rickman1989}, of which
+$\sim$$10^{14}$\,g is shed per orbit, most of which inspirals toward
+the Sun due to Poynting-Robertson drag.
+
+To summarize, if dust is responsible for the broadband variability of
+CPVs, it would need to be concentrated in clumps with masses in the
+range of $10^{15}$-$10^{17}$\,g.  Given $M_{\rm
+gas}$$\approx$2$\times$10$^{17}$\,g from \S~\ref{subsec:gas}, the
+allowed dust masses imply $M_{\rm gas}/M_{\rm dust}$ ranges of 1-100.
+More careful measurements of this ratio---in particular by inferring
+the dust mass through high precision infrared
+spectrophotometry---could provide a path for distinguishing the
+scenario of a trapped stellar outflow from an accumulation of
+externally-sourced material.  While there are several plausible
+external sources, feeding through a low-mass disk in particular cannot
+be ruled out based on typical disk depletion times \cite{Haisch2001}.
+Observations of infrared excesses and accretion signatures in low-mass
+stars tens of millions of years old suggest a broad lifetime
+distribution for such disks
 \cite{Silverberg2020,Lee2020,Gaidos2022,Pfalzner2024}.
@@
 \begin{sidewaystable}
-%\begin{table}
-  %\small
   \footnotesize
@@
   \begin{tabular}{lccccccccc}
-  %\hline 
-  %\hline 
-  %Time [BJD$_{\rm TDB}$] & RV (\kms) & $\sigma_{\rm RV}$ (\kms) \\
-  % from
-  % results/halpha_to_rv_timerseries/multigauss_parametertable.tex
+  % from results/halpha_to_rv_timerseries/multigauss_parametertable.tex
   \hline
@@
   \label{tab:halphamodelparams}
-%\end{table}
 \end{sidewaystable}
@@
 \item[Acknowledgments]
-  LGB is grateful to M.~Jardine, A.~Weinberger, B.~Tofflemire, J.~Spake,
-  and J.Winn for insightful conversations that significantly informed
-  this work, and to A.~Howard and H.~Isaacson for their assistance
-  reducing the HIRES spectra.
+  LGB is grateful to M.~Jardine, A.~Weinberger, B.~Tofflemire,
+  J.~Spake, J.~Winn, and L.~Hillenbrand for insightful conversations
+  that significantly informed this work, and to A.~Howard and
+  H.~Isaacson for their assistance reducing the HIRES spectra.
   This work was supported by the Carnegie Fellowship and by the

### 2025-04-07 paper/ms.tex
update

@@
 \normalfont
-Roughly one percent of red dwarfs younger than 100 million years show
+A small fraction of red dwarfs younger than 100 million years show
 structured, periodic optical light curves suggestive of transiting
@@
 sinusoidal time-varying Balmer emission at twice to four times the
-star's equatorial velocity, directly demonstrating for the first
-time that corotating clumps of circumstellar plasma exist around a CPV.
-Given that cool ($10^4$ K) plasma can persist in the hot ($10^6$ K)
-coronae of rapidly-rotating stars with a wide range of masses
+star's equatorial velocity, which provides the first direct evidence for
+corotating plasma clumps around a CPV.  While cool ($10^4$ K)
+plasma can persist within the hot ($10^6$ K) coronae of
+rapidly-rotating stars across a broad range of masses
 \cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
-these data support the idea that the magnetospheres of red dwarfs can
-support long-lived, optically thick clumps of material that produce
-the sharp photometric features seen in CPVs.  The origin of this
+our observations suggest that red dwarfs in particular can
+sustain long-lived, optically thick clumps that generate the 
+sharp photometric features seen in CPVs.  The origin of this
 optically thick material and its microphysical opacity remain
@@
 Figure~\ref{fig:spec}.  No such stars were previously known to show
-complex light curves \cite{Bouma2024}.   One interpretation for the
+complex light curves \cite{Bouma2024}.   One interpretation for this
 spectroscopic variability comes from an analogy to quiescent solar
@@
 Nonetheless, our Keck/HIRES observations are the first reported
-time-series spectra of a CPV, and they show for the first time that
+time-series spectra of a CPV, and they demonstrate that
 corotating circumstellar plasma clumps exist around at least one such
@@
 photometric variability, a ``starspot-only'' scenario for the CPVs
-\cite{Koen2021} seems to be incompatible with our observations.
+\cite{Koen2021} is incompatible with our observations.
 Scenarios in which the circumstellar material is made only of dust are
@@
 effective potential exist along the line of intersection between the
-rotational and magnetic equators (see Equation~22 of
+rotational and magnetic planes (see Equation~22 of
 \cite{Townsend2005}).  For $\sigma$~Ori~E and almost all of its
@@
 magnetic fields with highly multipolar contributions.  Second, despite
-this complexity, the observation from Figure~\ref{fig:spec} of two
+this complexity, the observation (Figure~\ref{fig:spec}) of two
 emission clumps separated 180$^\circ$ in phase is consistent with the

### 2025-04-22 paper/ms.tex
update

@@
-\documentclass{nature3}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{verbatim}
+% upon AAS submission
+\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex7}
+%\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex7}
+% drafting / arxiv
+%\documentclass[11pt,twocolumn,modern]{aastex7}
+\turnoffedit
+
+\usepackage{apjfonts}
+\usepackage{url}
 \usepackage{hyperref}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{aas_macros_nature}
-\usepackage{lineno}
-\usepackage{caption}
+\usepackage{natbib}
+\usepackage{amsmath,amstext,amssymb}
+\usepackage[caption=false]{subfig} % for subfloat
+\usepackage{xcolor, fontawesome}
+\usepackage{color}
+\usepackage{enumitem}
 \usepackage{rotating} % sidewaystable
@@
 \linenumbers % turn line numbering on or off
-
-\newcommand{\farcm}{\mbox{\ensuremath{.\mkern-4mu^\prime}}}%    % fractional arcminute symbol: 0.'0
-\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}%  % fractional arcsecond symbol: 0.''0
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
 
@@
 
-\begin{document}
-
-\author{Luke G. Bouma$^{1,2}$}
-
-\maketitle
-
-\scriptsize
-\begin{affiliations}
-\item \carnegie
-\item \caltech
-\item Carnegie Fellow; 51 Pegasi b Fellow
-\end{affiliations}
-\normalsize
+\correspondingauthor{Luke G. Bouma}
+
+\received{--}
+\revised{--}
+\accepted{--}
+\shorttitle{M Dwarf Plasma Torus}
+
+\shortauthors{Bouma et al.}
+
+\author[orcid=0000-0002-0514-5538,sname='Bouma']{Luke~G.~Bouma}
+\altaffiliation{Carnegie Fellow; 51 Pegasi b Fellow}
+\affiliation{\carnegie}
+\affiliation{\caltech}
+\email{lbouma@carnegiescience.edu}
 
@@
 \begin{abstract}
-\normalfont
-A small fraction of red dwarfs younger than 100 million years show
-structured, periodic optical light curves suggestive of transiting
-opaque material that corotates with the star
-\cite{Rebull2016,Stauffer2017,Rebull2018,Bouma2024}.  However, the
-composition, origin, and even the existence of this material are
+A small fraction of red dwarfs younger than $\sim$100 million years
+show structured, periodic optical light curves suggestive of
+transiting opaque material that corotates with the star.  However,
+the composition, origin, and even the existence of this material are
 uncertain. The main alternative hypothesis is that these complex
 periodic variables (CPVs) are explained by complex distributions of
-bright or dark regions on the stellar surfaces \cite{Koen2021}.
-Here, we present time-series spectroscopy and photometry of a
-rapidly-rotating ($P$=3.9\,hr) CPV, TIC~141146667. The spectra show
-sinusoidal time-varying Balmer emission at twice to four times the
-star's equatorial velocity, which provides the first direct evidence for
-corotating plasma clumps around a CPV.  While cool ($10^4$ K)
-plasma can persist within the hot ($10^6$ K) coronae of
-rapidly-rotating stars across a broad range of masses
-\cite{CollierCameron1989,Townsend2005,Dunstone2006,Petit2013,Waugh2022,Daley-Yates2024},
-our observations suggest that red dwarfs in particular can
-sustain long-lived, optically thick clumps that generate the 
-sharp photometric features seen in CPVs.  The origin of this
-optically thick material and its microphysical opacity remain
-unclear.
+bright or dark regions on the stellar surfaces.  Here, we present
+time-series spectroscopy and photometry of a rapidly-rotating
+($P$=3.9\,hr) CPV, TIC\,141146667.  The spectra show sinusoidal
+time-varying Balmer emission at twice to four times the star's
+equatorial velocity, providing direct evidence for cool
+($\lesssim$10$^4$\,K) plasma clumps trapped in corotation around a CPV.
+These data support the idea that young, rapidly-rotating M dwarfs can
+sustain warped plasma tori, similar to massive magnetic stars.  The
+origin of the optically thick material in these tori, and the issue
+of whether this material contains a significant amount of dust,
+remain unclear.
 \end{abstract}
 
-\maketitle
+\keywords{Circumstellar matter (241), Stellar magnetic fields (1610),
+Stellar rotation (1629) Periodic variable stars (1213), Weak-line T
+Tauri stars (1795) }
 
@@
 
-% Main text – up to 3,000 words, excluding abstract, Methods,
-% references and figure legends.
-
-\section{Main}
-\label{sec:main}
-
-M dwarfs, stars with masses below about half that of the Sun, are the
+\section{Introduction}
+\label{sec:intro}
+
+Stars with masses below about half that of the Sun, M dwarfs, are the
 only type of star to offer near-term prospects for detecting the
-atmospheres of rocky exoplanets with surface water \cite{NAP26141}.
-Community investment with JWST has proceeded accordingly
-\cite{Redfield2024,TRAPPIST1JWSTCommunityInitiative2024}.  How an M
-dwarf's evolution influences its planets---especially the retention of
-their atmospheres--- has in turn become a major theme in exoplanet and
-stellar astrophysics.  Previous work has established that most M
-dwarfs host close-in planets \cite{Dressing2015} that on average are
-subject to long circumstellar disk lifetimes \cite{Ribas2015}, to high
-doses of UV radiation \cite{France2016}, and to a high incidence of
-flares and coronal mass ejections \cite{Gunther2020}.  However,
-despite extensive work in these areas, the plasma and magnetospheric
-environments that bathe young, close-in exoplanets remain challenging
-to quantify.  Understanding these environments is crucial because they
-directly impact atmospheric retention and habitability of close-in
-planets.
+atmospheres of rocky exoplanets with surface water.  Community
+investment with JWST is proceeding accordingly
+\citep[see][]{Redfield2024,TRAPPIST1JWSTCommunityInitiative2024}.  The
+question of how an M dwarf's evolution influences its
+planets---especially the retention of their atmospheres---has in turn
+become a major theme in exoplanet and stellar astrophysics.  Previous
+work has established that most M dwarfs host close-in planets
+\citep{Dressing2015} that on average are subject to long circumstellar
+disk lifetimes \citep{Ribas2015}, to high doses of UV radiation
+\citep{France2016}, and to a high incidence of flares and coronal mass
+ejections \citep{Feinstein2020}.  However, despite extensive work in
+these areas, the plasma and magnetospheric environments that bathe
+young, close-in exoplanets remain challenging to quantify.
+Understanding these environments is crucial because they directly
+impact atmospheric retention and habitability of close-in planets.
 
@@
 have now been found by K2 and TESS
-\cite{Rebull2016,Stauffer2017,Rebull2018,Zhan2019,Rebull2020,Bouma2024}.
+\citep{Rebull2016,Stauffer2017,Rebull2018,Zhan2019,Rebull2020,Stauffer2021,Popinchalk2023,Bouma2024}.
 These CPVs are phenomenologically identified based on their
@@
 rotation periods shorter than two days.  Within current sensitivity
-limits, none host disks \cite{Stauffer2017,Bouma2024}.  However,
+limits, none host disks \citep{Stauffer2017,Bouma2024}.  However,
 $\approx$3\% of stars a few million years old show this complex
 photometric behavior, an observed fraction which decreases to
-$\approx$0.3\% by $\approx$150\,Myr \cite{Rebull2020}.  CPVs are a
+$\approx$0.3\% by $\approx$150\,Myr \citep{Rebull2020}.  CPVs are a
 known source of astrophysical false positives in searches for
 transiting exoplanets around young M dwarfs
-\cite{vanEyken2012,Johns-Krull2016,Bouma2020}.
+\citep{vanEyken2012,Johns-Krull2016,Bouma2020}.
 
@@
 transiting clumps of circumstellar material corotate with the star
-\cite{Stauffer2017,Gunther2022,Bouma2024}, or that these stars
+\citep{Stauffer2017,Gunther2022,Bouma2024}, or that these stars
 represent an extreme in naturally-occurring distributions of starspots
-or faculae \cite{Koen2021}.  The main argument against a starspot-only
-explanation invokes the timescales and amplitudes of the sharpest
-photometric features.  However, no independent evidence has yet been
-acquired for the presence of any circumstellar material.
-Geometrically, transiting clumps would imply an occurrence a few to at
-most ten times the observed rate.  The clumps could therefore exist
-around 10-30\% of M dwarfs during their early lives.
+or faculae \citep{Koen2021}.  The main argument against a
+starspot-only explanation invokes the timescales and amplitudes of the
+sharpest photometric features.  However, no independent evidence has
+yet been acquired for the presence of any circumstellar material.  If
+the material exists, then the geometric correction from the transit
+probability would imply an intrinsic occurrence rate at least a few
+times larger than the observed rate, suggesting that these clumps
+could exist around $\gtrsim$10\% of M dwarfs during their early lives.
+
+The dearth of evidence for circumstellar material around CPVs is
+surprising given that separate studies of young stars have, for
+decades, reported that stellar coronae contain both hot
+($\gtrsim$$10^6$ K) and cool ($\lesssim$$10^4$ K) plasma. In
+particular, time-series spectroscopy of stars with a wide range of
+masses has shown periodic high-velocity absorption and emission in
+Balmer lines such as H$\alpha$, interpreted as long-lived, corotating
+clumps of cool plasma
+\citep{CollierCameron1989,CollierCameron1992,Barnes2000,Donati2000,Dunstone2006,Skelly2008,Leitzinger2016,Cang2021}.
+Such clumps are thought to be forced into corotation by the magnetic
+field, and the exact geometry of where the plasma can accumulate is
+dictated by the field's topology.  For instance, a magnetic dipole
+field tilted with respect to the stellar spin axis yields
+accumulations in a warped torus geometry \citep{Townsend2005}, whereas
+in the limit of a single strong field line, accumulation occurs at the
+line's apex, furthest from the star \citep{Waugh2022}.  To date, none
+of these spectroscopic variables have shown any photometric anomalies
+\citep{Bouma2024}, leaving open the issue of whether they are related
+to CPVs.
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/f1.pdf}
-  \captionsetup{labelformat=empty}
-  \caption{{\bf Figure 1 (Movie):  TIC~141146667 is a complex periodic
+  \includegraphics[width=0.47\textwidth]{figures/f1.pdf}
+  \vspace{-0.3cm}
+  \caption{{\bf Figure 1 (Movie):  TIC\,141146667 is a complex periodic
   variable (CPV).}  The online movie,
@@
 
-The dearth of evidence for circumstellar material around CPVs is
-surprising given that separate studies of young stars have, for
-decades, reported that stellar coronae contain both hot ($10^6$ K) and
-cool ($10^4$ K) plasma. In particular, time-series spectroscopy of
-stars with a wide range of masses has shown periodic high-velocity
-absorption and emission in Balmer lines such as H$\alpha$, interpreted
-as long-lived, corotating clumps of cool plasma
-\cite{CollierCameron1989,CollierCameron1992,Barnes2000,Donati2000,Dunstone2006,Skelly2008,Leitzinger2016,Cang2021}.
-Such clumps are thought to be forced into corotation by the magnetic
-field, and the exact geometry of where the plasma can accumulate is
-dictated by the field's topology.  For instance, a magnetic dipole
-field tilted with respect to the stellar spin axis yields
-accumulations in a warped torus geometry \cite{Townsend2005}, whereas
-in the limit of a single strong field line, accumulation occurs at the
-line's apex, furthest from the star \cite{Waugh2022}.  To date, none
-of these spectroscopic variables have shown any photometric anomalies
-\cite{Bouma2024}, leaving open the issue of whether they are related
-to CPVs.
-
 In this study, we present the first spectroscopic detection of
-corotating clumps of cool plasma around a CPV.  We identified
-TIC~141146667 in previous work \cite{Bouma2024} by searching the TESS
-two-minute data \cite{Ricker2015} for stars showing highly structured,
-periodic light curves.  We selected the star for spectroscopy because
-its brightness and rotation rate enabled an efficient search for
-variability in its line profiles.  We observed the star for five hours
-on 17~February~2024 (UT) using the High Resolution Echelle
-Spectrometer (HIRES \cite{vogt_hires_1994}) on the 10\,m Keck I
-telescope.  TESS observed the star over a four week interval from
-30~January~2024 to 26~February~2024 with a duty cycle of 77\%.  During
-the HIRES observations, scattered light from the Earth caused a gap in
-the TESS photometry; TESS data collection resumed 12 hours (three
-rotation cycles) after the spectra were acquired.  Extended Data
-Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
-star near the epoch of observation; the general photometric morphology
-is similar before and after the data gap.
+corotating clumps of cool plasma around a CPV, TIC\,141146667.  The
+observations are presented in Section~\ref{sec:obs}, with the main new
+evidence in Figure~\ref{fig:spec}.  Section~\ref{sec:results} expounds
+on the results; Section~\ref{sec:disc} discusses their interpretation
+and highlights future directions.
+
+\section{Observations}
+\label{sec:obs}
+
+We identified TIC\,141146667 in previous work \citep{Bouma2024} by
+searching TESS two-minute data from 2018-2022 for highly
+structured, periodic light curves \citep{Ricker2015}.  We selected the
+star for spectroscopy because its brightness and rotation rate enabled
+an efficient search for variability in its line profiles.
+As apparently single pre-main sequence M dwarf, its properties are
+typical for the general CPV population (see Table~\ref{tab:params} and
+Appendix~\ref{sec:stparams}).
+
+We observed TIC\,141146667 ($V$=16.2) for five hours on
+17~February~2024 (UT) using the High Resolution Echelle Spectrometer
+(HIRES; \citealt{vogt_hires_1994}) on the 10\,m Keck I telescope.  The
+observations spanned the second half of the night, from 17 February
+2024 10:47 to 16:13 (UT).  The star's airmass spanned $z$=1.2-2.2, and
+we opted for a fixed 15 minute cadence, except for a final 10 minute
+exposure due to increasing sky brightness at sunrise.  We observed
+without the iodine cell and used the C2 decker
+(0$\farcs$86$\times$14$\farcs$0) in the red configuration, yielding a
+spectral resolution $R$$\approx$45{,}000 ($\delta
+v$$\approx$6.7\,\kms; $\delta v / v_{\rm eq}$$\approx$0.05).  We
+binned the CCD readout by a factor of three in the spatial dimension,
+yielding $\approx$1,000 photons (S/N=33) per pixel in the continuum at
+6500\,\AA, at minimum airmass.  Strong winds contributed to
+1$''$-1\farcs5 seeing over the night, but conditions were otherwise
+favorable.  We reduced the echelleogram to a one-dimensional spectrum
+using the standard techniques of the California Planet Survey
+\citep{Howard2010}.  Figure~\ref{fig:spec} shows the result in the
+vicinity of H$\alpha$ without any additional processing.
+
+To date, TESS has observed TIC\,141146667 ($T$=13.3) for a total of six
+non-contiguous months spanning 2019-2024.  Two-minute cadence observations were
+acquired during Sectors 41, 48 (TESS DDT039, PI: Kunimoto), and 75
+(TESS Program G06030, PI: Bouma); the remaining 30-minute data during
+Sectors 14, 15, and 21 smears sharp features over the $<$4\,hour
+period (see \citealt{Gunther2022}).  The concatenated two-minute data
+are shown in the movie associated with Figure~\ref{fig:lc}.  The movie shows that,
+like other CPVs, TIC\,141146667 maintains a fixed period over
+timescales of years while its detailed photometric morphology evolves.
+The nearest known star, TIC\,141146666 ($T$=14.5), is 25$''$ from
+TIC\,141146667 and is photometrically stable in the TESS target pixel
+cutouts; crowding is not a concern.
+
+\begin{figure*}[!t]
+  \centering
+  \includegraphics[width=0.95\textwidth]{figures/sf1.pdf}
+  \vspace{-0.2cm}
+  \caption{{\bf Evolution of TIC\,141146667 during the Keck/HIRES
+  observation (green bar).}  {\bf a,} TESS simple aperture photometry.
+  Data gaps caused by light from the Earth (BTJD 3356-3358.5) and Moon
+  (BTJD 3359.5-3360.5) are visible.  Raw two minute
+  data are in gray; black time-averages to ten minute sampling.  {\bf
+  b-c,} Folded TESS light curve before and after spectroscopy.  Black
+  now phase-averages to 100 points per
+  cycle.  During BTJD 3352-3356, a state switch occurred near BTJD
+  3353, and the dip at $\phi$$\approx$0.8 disappeared.  While the
+  large flux decrement was present both before and after the HIRES
+  sequence, its photometric shape evolved during the data gap.  The
+  orange bar denotes times of spectroscopic transits for the inner two
+  H$\alpha$ clumps observed with HIRES (see Figure~\ref{fig:spec}).}
+  \label{fig:fulllc}
+\end{figure*}
+
+We observed with Keck during Sector~75 in an attempt to obtain
+simultaneous observations.   Figure~\ref{fig:fulllc} shows the result;
+the Earth passed within 25$^\circ$ of the
+TESS camera's boresight from BTJD 3356.0~-~3358.5, which caused a data
+gap that ended twelve hours after the Keck/HIRES observation epoch
+(green bar).  From
+BTJD 3359.4~-~3362.0, the Moon then passed within 25$^\circ$ of the
+camera's boresight.  Based on the level of scattered light in the
+optimal TIC\,141146667 aperture \citep{Jenkins2016}, we manually masked
+out times from 3359.40~-~3360.13; the remainder of the data during the
+lunar approach were usable.  Small data gaps from BTJD
+3353.55~-~3353.77 and from BTJD 3360.12~-~3360.33 were caused by data
+downlinks at the spacecraft's perigee and apogee, respectively.
+
+While the data gap is unfortunate, Figure~\ref{fig:fulllc} shows
+that a large, complex flux decrement spanned roughly half of each
+cycle both before and after the HIRES data were acquired.  From BTJD
+3352~-~3356, this dip had two sharp local minima;  the local minimum
+at $\phi$$\approx$0.8 disappeared following the flare at BTJD 3353,
+yielding a dip more closely resembling an asymmetric ``V'' than a ``W''.
+Similar CPV state changes have been previously noted 
+\citep{Stauffer2017,Bouma2024}.  The photometric shape therefore
+evolved during the twelve cycles spanning the 3356~-~3358 gap, since
+the average shape from 3358-3363 more closely resembles the initial
+``W''.  Nonetheless, the general photometric morphology---a small
+brightening over 45\% of the period, followed by a complex flux dip
+spanning 55\% of the period---is similar before and after the data
+gap.
 
 \section{Results}
-
-\begin{figure}[!tp]
+\label{sec:results}
+
+\begin{figure*}[!t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/f2.pdf}
-  \captionsetup{labelformat=empty}
+  \vspace{-0.2cm}
   \caption{{\bf Figure 2 (Movie):}  
-  Emission from circumstellar plasma orbiting TIC 141146667.
+  Emission from circumstellar plasma orbiting TIC\,141146667.
   The online movie,
@@
   \label{fig:spec}
-\end{figure}
-
-% photometry
+\end{figure*}
+
 Figure~\ref{fig:spec} compiles the TESS and HIRES data from February
-2024.  Over timescales of years, CPVs maintain fixed periods while
-their photometric morphology evolves.  TIC~141146667 indeed evolved
-relative to the February 2022 discovery data (see Figure~\ref{fig:lc}).
-In February 2024, the average photometric signal showed a small
-brightening over 45\% of the period, followed by a complex flux dip
-spanning 55\% of the period.  This eclipse feature shows two to three
-local photometric minima, and one to two local maxima.  Its W-shape is
-suggestive of eclipse geometries seen in forward models of warped
-plasma tori (see \cite{Townsend2008} and the associated
-\href{http://user.astro.wisc.edu/~townsend/static.php?ref=rrm-movies#Download_Bundles}{movies}).
-% particularly ω/ωc = 0.5, beta = 30, i = 90.
-
-The spectroscopy shows emission beyond the star's equatorial velocity
-($v_{\rm eq}$=130\,\kms).  There are at least two distinct emission
-components, separated by half a cycle in phase.  The inner component
-at lower velocities has clearer sinusoidal behaviour in time and is
-double-peaked, with peak semi-amplitudes of 2.07\,$v_{\rm eq}$ and
-2.88\,$v_{\rm eq}$ (see \S~\ref{subsec:halpha}).  There is significant
+2024.  The HIRES spectra show emission in H$\alpha$ beyond the star's
+equatorial velocity, $v_{\rm eq}$, of 130\,\kms.  There are at least
+two distinct emission components, separated by half a cycle in phase.
+The inner component at lower velocities has clearer sinusoidal
+behaviour in time and is double-peaked, with peak semi-amplitudes of
+2.07\,$v_{\rm eq}$ and 2.88\,$v_{\rm eq}$, measured following the
+procedure in Appendix~\ref{subsec:halpha}.  There is significant
 non-periodic variability in the emissivity of this double-peaked
 component: the flux excess begins with an amplitude 70\% that of the
-continuum early in the observation sequence, and diminishes to 10\% by
-its end.  The higher-velocity component 180$^\circ$ opposite in phase
-is detected only from $\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this outer
-component appears connected to the star in velocity space.  While its
-peak semi-amplitude of 3.88\,$v_{\rm eq}$ is achieved at both
-$\phi$=0.25 and 0.75, its amplitude similarly decreases from a 60\%
-excess over the continuum at the beginning of the observation sequence
-to a 10\% excess by its end.  The apparent period for all three
-spectroscopic emission components is consistent with the photometric
-\periodhr\ hour period.
+continuum, and diminishes to 10\% by the end.  The higher-velocity
+component 180$^\circ$ opposite in phase is detected only from
+$\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this outer component appears
+connected to the star in velocity space.  While its peak
+semi-amplitude of 3.88\,$v_{\rm eq}$ is achieved at both $\phi$=0.25
+and 0.75, its amplitude similarly decreases from a 60\% excess over
+the continuum at the beginning of the observation sequence to a 10\%
+excess by its end.  
+From the same procedure in Appendix~\ref{subsec:halpha},
+we measured
+the period for all three spectroscopic
+emission components to be consistent with the photometric \periodhr\ hour
+period, to within two minutes for the lower-velocity component.
 
@@
 not controlled by gravitational attraction to the star; it is more
-readily explained as a partially-ionized plasma being dragged along
+readily explained as a plasma being dragged along
 with a rigidly rotating stellar magnetic field.  The velocity
@@
 each cycle, from $\phi$=-0.1 to $\phi$=+0.12 (see
-\S~\ref{subsec:halpha}).  This spectroscopic transit coincides with
+Appendix~\ref{subsec:halpha}).  This spectroscopic transit coincides with
 the latter half of the complex eclipse feature in the TESS data.
@@
 
-\begin{table*}
+\begin{table}
 \small
@@
 \centering
-\caption{Selected system parameters for TIC~141146667}
+\caption{Selected system parameters for TIC\,141146667}
 \label{tab:params}
@@
 Provenances are:
-1: SED fit \cite{Bouma2024}.
+1: SED fit \citep{Bouma2024}.
 2: Gaia DR3 photometry shows the star is on the pre-main sequence,
-   while the spectrum lacks lithium (see \S~\ref{subsec:stparams}).
-3: PARSEC v1.2S \cite{Chen2014}.
+   while the spectrum lacks lithium (see \S~\ref{sec:stparams}).
+3: PARSEC v1.2S \citep{Chen2014}.
 4: Keck/HIRES (see \S~\ref{subsec:halpha}).
@@
 6: Derived quantity.
-7: Gaia DR3 geometric \cite{GaiaDR3}.
+7: Gaia DR3 geometric \citep{GaiaDR3}.
 }
@@
 \vspace{-0.5cm}
-\end{table*}
+\end{table}
 
 \section{Discussion}
-
-Spectra of magnetically-active, rapidly rotating stars with a wide
-range of masses have been previously observed to exhibit both
-sinusoidal time-varying Balmer emission
-\cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} and transient
-absorption features
-\cite{CollierCameron1989,CollierCameron1992,Cang2020}, similar to
-Figure~\ref{fig:spec}.  No such stars were previously known to show
-complex light curves \cite{Bouma2024}.   One interpretation for this
-spectroscopic variability comes from an analogy to quiescent solar
-prominences, which are cool condensations of plasma in the solar
-corona that can last days to weeks \cite{VialEngvold2015}.  These
-condensations fall back to the Sun's photosphere because gravity is
-stronger than any magnetic tension or centrifugal force capable of
-sustaining them.  However for stars with magnetospheric radii $R_{\rm
-m}$ that exceed their corotation radii $R_{\rm c}$, the effective
-potential experienced by a charged particle can have a local minimum
-outside $R_{\rm c}$, enabling the material to accumulate in a
+\label{sec:disc}
+
+\subsection{Corotating Plasma Clumps}
+
+Our Keck/HIRES observations are the first reported time-series spectra
+of a CPV, and they demonstrate that corotating circumstellar plasma
+clumps exist around at least one such star.  While starspots likely do
+contribute smooth signals to the photometric variability, a
+``starspot-only'' scenario for the CPVs \citep{Koen2021} is
+incompatible with our observations.  Scenarios in which the
+circumstellar material is made only of dust are similarly ruled out.
+While starspots and dust may both be present, the observed H$\alpha$
+emission requires plasma with a significant population of hydrogen
+atoms in the $n$=3 excited state.  Most of this H$\alpha$ emission
+originates in ``clumps'' with size similar to that of the star; radial
+``spokes'' or azimuthally-extended ``arcs'' for the emitting material are
+ruled out by the observed H$\alpha$ velocity dispersion (see
+\S~\ref{subsec:halpha}).  
+The observed H$\alpha$ luminosity suggests characteristic densities
+and masses for the gaseous component of these clumps of $n_{\rm H}
+\sim 10^{11}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g (see
+\S~\ref{subsec:gas}).  Dust, if present, is independently constrained
+to have a total mass $10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm
+g}$ (see \S~\ref{subsec:dust}).  
+The spectra show minimal evidence for significant populations in
+higher-order hydrogen states (see Appendix~\ref{subsec:specvar}).
+
+\subsection{Plasma Tori Could Explain Complex Periodic Variables}
+
+While the H$\alpha$ emission appears consistent with clumps, the
+photometric width of the complex flux dips in TIC\,141146667
+specifically, and CPVs more broadly \citep[Figure~4 of][]{Bouma2024},
+raise the possibility that azimuthally-distributed material may be the
+norm for these objects.  In other words, a torus may be a more
+accurate picture than a clump.
+
+\citet{Townsend2005} outline the physics of how such structures can
+exist: for stars with magnetospheric radii $R_{\rm m}$ that exceed
+their corotation radii $R_{\rm c}$, the effective potential
+experienced by a charged particle can have a local minimum outside
+$R_{\rm c}$, enabling material to accumulate in a
 centrifugally-supported magnetosphere
-\cite{Petit2013,Daley-Yates2024}.  Generally speaking, such material
+\citep{Petit2013,Daley-Yates2024}.  Generally speaking, such material
 need neither transit nor be opaque in broadband optical light.  In
@@
 
-Nonetheless, our Keck/HIRES observations are the first reported
-time-series spectra of a CPV, and they demonstrate that
-corotating circumstellar plasma clumps exist around at least one such
-star.  While starspots likely do contribute smooth signals to the
-photometric variability, a ``starspot-only'' scenario for the CPVs
-\cite{Koen2021} is incompatible with our observations.
-Scenarios in which the circumstellar material is made only of dust are
-similarly ruled out.  While starspots and dust may both be present,
-the observed H$\alpha$ emission requires clumps of plasma with a
-significant population of hydrogen atoms in the $n$=3 excited state,
-with most H$\alpha$ emission in each clump coming from a region half
-the size of the star (see \S~\ref{subsec:halpha}).  The observed
-H$\alpha$ luminosity suggests characteristic densities and masses for
-the gaseous component of these clumps of $n_{\rm H} \sim
-10^{11}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g (see
-\S~\ref{subsec:gas}).  Dust, if present, is independently constrained
-to have a total mass $10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm
-g}$ (see \S~\ref{subsec:dust}).  This circumstellar material could
-originate either from the star or from an external source.  Plausible
-external sources include an undetected old disk, comets, or a close-in
-exoplanet.  This latter scenario would make CPVs extrasolar analogs of
-the Jupiter-Io plasma torus (e.g.~Ref.~\cite{Bagenal1981}).
+Nonetheless, \citet{Townsend2008} synthesized light curves for plasma
+trapped in rigidly rotating magnetospheres of rapidly rotating stars;
+and found that assuming a dipole magnetic geometry, one can obtain
+W-shaped eclipses similar to those seen for TIC\,141146667.  See in
+particular the
+\href{http://user.astro.wisc.edu/~townsend/static.php?ref=rrm-movies#Download_Bundles}{movies}
+associated with their work; for a $\omega/\omega_{\rm c}$$\approx$0.5,
+edge-on system like TIC\,141146667, the eclipses have the correct
+approximate shape, and the H$\alpha$ emission can similarly exhibit
+double-peaked behavior.
+
+\subsection{Origin of Circumstellar Material and Astrophysical Analogs}
+
+The circumstellar material could originate either from the star or
+from an external source.  Plausible external sources include an
+undetected old disk, comets, or a close-in exoplanet.  This latter
+scenario would make CPVs extrasolar analogs of the Jupiter-Io plasma
+torus (e.g.~\citealt{Bagenal1981}), although with a very different
+composition.
 
@@
 which accumulate into warped plasma tori
-\cite{Townsend2005,Townsend2008}.  These tori tend to have dense
+\citep{Townsend2005,Townsend2008}.  These tori tend to have dense
 antipodal accumulations of plasma sculpted by tilted-dipole magnetic
 fields, and the transits of these clumps produce broadband photometric
-variability through bound-free scattering \cite{Townsend2005} and
-Thomson scattering \cite{Berry2022}.  The plasma accumulates at
+variability through bound-free scattering \citep{Townsend2005} and
+Thomson scattering \citep{Berry2022}.  The plasma accumulates at
 antipodes 180$^\circ$ apart because the deepest local minima in the
@@
 rotational and magnetic planes (see Equation~22 of
-\cite{Townsend2005}).  For $\sigma$~Ori~E and almost all of its
+\citealt{Townsend2005}).  For $\sigma$~Ori~E and almost all of its
 analogs, the result is ``simple'' light curves that resemble those of
 eclipsing binaries, and time-dynamic H$\alpha$ spectra similar to
-those in Figure~\ref{fig:spec} \cite{Townsend2005,Townsend2008}.  The
+those in Figure~\ref{fig:spec} \citep{Townsend2005,Townsend2008}.  The
 two known exceptions, HD~37776 and HD~64740, show complex light curves
-resembling CPVs \cite{Mikulasek2020,Bouma2024} and have
+resembling CPVs \citep{Mikulasek2020,Bouma2024} and have
 spectropolarimetric magnetic field maps indicating strong
 contributions from higher-order magnetic moments
-\cite{Kochukhov2011,Shultz2018}.  There are two implications: first,
+\citep{Kochukhov2011,Shultz2018}.  There are two implications: first,
 the photometric complexity of CPVs may be a direct consequence of
@@
 
+\subsection{Connection to Previous Work}
+
+Spectra of magnetically-active, rapidly rotating stars with a wide
+range of masses have been previously observed to exhibit 
+sinusoidal time-varying Balmer emission
+\citep{Donati2000,Townsend2005,Dunstone2006,Skelly2008}, similar to
+that Figure~\ref{fig:spec}.  No such stars were previously known to show
+complex light curves \citep{Bouma2024}.   One interpretation for the
+spectroscopic variability of these stars, and that of the analogous transient
+absorption features
+\citep{CollierCameron1989,CollierCameron1992,Cang2020}, comes from an
+analogy to quiescent solar prominences, cool condensations of plasma
+in the solar corona that can last days to weeks
+\citep{VialEngvold2015}.  In the case of the Sun, these condensations
+fall back to the photosphere because gravity is stronger than any
+magnetic tension or centrifugal force capable of sustaining them.  
+However it has been understood at least since work by
+\citet{Donati2000} that these ``prominence systems'' can be
+longitudinally extended, forming a trapped ring of plasma.
+While the question of why these previously known spectroscopic
+variables do not show complex photometric variability remains open,
+a possible explanation is that they are not in the required transiting
+geometry.
+What we have in the case of TIC\,141146667 is a system that finally
+exhibits both sets of phenomena.
+
+\subsection{Future Work: Composition, Origin, Modelling}
+
 Pressing issues for future work include determining the composition
@@
 experienced by the close-in rocky exoplanets that, statistically
-\cite{Dressing2015}, are likely to be present in most CPV systems.
+\citep{Dressing2015}, are likely to be present in most CPV systems.
 
@@
 a chromaticity consistent with dust
-\cite{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such
+\citep{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such
 as electron scattering in a plasma transiting over a spotted
 background star might also produce chromatic features
-\cite{Rackham2018}.  The composition and size distribution of any dust
+\citep{Rackham2018}.  The composition and size distribution of any dust
 that is present could be determined by measuring the extinction curve
@@
 distributions similar to debris from rocky bodies seen around white
-dwarfs \cite{Reach2009} would suggest an extrinsic origin channel.
+dwarfs \citep{Reach2009} would suggest an extrinsic origin channel.
 Compositions and sizes similar to the interstellar medium would
 suggest that dust can condense out from M dwarf winds, similar to
-processes that occur around more evolved stars \cite{Marigo2008}.
+processes that occur around more evolved stars \citep{Marigo2008}.
 
@@
 magnetohydrodynamic modeling to go beyond previous work
-\cite{Townsend2005,Townsend2008,Krticka2022} and to explore what field
+\citep{Townsend2005,Townsend2008,Krticka2022} and to explore what field
 topologies might explain the observed light curve morphologies
-\cite{Bouma2024}.  In particular, dynamo simulations of
+\citep{Bouma2024}.  In particular, dynamo simulations of
 fully-convective M dwarfs have suggested that global-scale mean fields
-might be confined to a single hemisphere \cite{Brown2020}; such fields
+might be confined to a single hemisphere \citep{Brown2020}; such fields
 would yield accumulation surfaces quite different from those that have
@@
 independent constraint on magnetic field topology may also come from
-radio observations, which have shown \cite{Kaur2024} that CPVs emit
+radio observations, which have shown \citep{Kaur2024} that CPVs emit
 variable radio signals, including persistent and polarized components.
 Detecting radio emission produced by an electron cyclotron maser
-instability (e.g. \cite{Callingham2021}) in particular would provide a
+instability (e.g.~\citealt{Callingham2021}) in particular would provide a
 measurement of the field strength at the site of the emitting region,
@@
 close-in rocky exoplanets that exist around most M dwarfs
-\cite{Dressing2015}.  However, a few percent of young M dwarfs show
-the CPV phenomenon \cite{Rebull2020}, and our data show that some of
+\citep{Dressing2015}.  However, a few percent of young M dwarfs show
+the CPV phenomenon \citep{Rebull2020}, and our data show that some of
 the complex photometric features occur when clumps of circumstellar
@@
 
-\newpage
-\begin{methods}
-
-\renewcommand{\figurename}{Extended Data Figure}
-\renewcommand{\tablename}{Extended Data Table}
-\setcounter{table}{0}  
-\setcounter{figure}{0}
-
-\subsection{Observations \& Data Reduction}\phantom{+}
-
-\begin{figure}[!b]
-  \centering
-  \includegraphics[width=0.99\textwidth]{figures/sf1.pdf}
-  \caption{Photometric evolution of TIC 141146667 near the Keck/HIRES
-  observation (green bar).  {\bf a,} TESS simple aperture photometry.
-  The main data gaps were caused by scattered light from the Earth
-  (BTJD 3356-3358.5) and Moon (BTJD 3359.5-3360.5).  Raw two minute
-  data are in gray; black time-averages to ten minute sampling.  {\bf
-  b-c,} Folded TESS light curve before and after spectroscopy.  Raw
-  two minute data are in gray; black phase-averages to 100 points per
-  cycle.  During BTJD 3352-3356, a state switch occurred near BTJD
-  3353, in which the dip at $\phi$$\approx$0.8 disappeared.  While the
-  large eclipse feature was present both before and after the HIRES
-  sequence, its photometric shape evolved during the data gap.  The
-  oranges bar denote times of spectroscopic transits for the inner two
-  H$\alpha$ clumps observed with HIRES.}
-  \label{fig:fulllc}
-\end{figure}
-
-{\it Photometry:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14,
-15, 21, 41, 48, and 75.  Two-minute data were acquired during Sectors
-41, 48 (TESS DDT039, PI: Kunimoto), and 75 (TESS Program G06030, PI:
-Bouma).  The data from Sectors 14, 15, and 21 had 30-minute cadence,
-which smears sharp features over the $<$4\,hour period (see
-\cite{Gunther2022}).  The field is not crowded:  the nearest known
-star, TIC~141146666 ($T$=14.5), is 25$''$ from TIC~141146667 and is
-photometrically stable in the pixel-level TESS data.
-
-Extended Data Figure~\ref{fig:fulllc} shows the TESS Sector~75 data
-acquired near the epoch of spectroscopy.  The gap in coverage from
-BTJD 3356.0~-~3358.5 occurred because the Earth was within
-25$^\circ$ of the TESS camera's boresight, yielding high levels of
-scattered light; this gap included the Keck/HIRES observation epoch
-(green bar).  From BTJD 3359.4~-~3362.0, the Moon then passed within
-25$^\circ$ of the camera's boresight.  Based on the observed level
-of scattered light in the optimal TIC~141146667 aperture, we
-manually masked out times from 3359.40~-~3360.13, and judged the
-remainder of the data during the lunar approach to be usable.  Small
-data gaps from BTJD 3353.55~-~3353.77 and from BTJD
-3360.12~-~3360.33 were caused by data downlinks at the spacecraft's
-perigee and apogee, respectively.
-
-Extended Data Figure~\ref{fig:fulllc} shows that a large, complex
-eclipse feature was present before and after the HIRES data were
-acquired.  From BTJD 3352~-~3356, this eclipse had two sharp local
-minima;  the local minimum at $\phi$$\approx$0.8 disappeared
-following the flare at BTJD 3353, yielding an eclipse more closely
-resembling a long ``V'' than a ``W''.  Similar state changes have
-previously been noted and discussed \cite{Stauffer2017,Bouma2024}.
-The photometric shape therefore evolved during the twelve cycles
-spanning the 3356~-~3358 gap, since the average shape from 3358-3363
-more closely resembles the initial ``W''.
-
-{\it Spectroscopy:}
-We observed TIC~141146667 ($V$=16.2) with Keck/HIRES for five hours
-during the second half of the night, spanning 17 February 2024 10:47
-to 16:13 (UT).  The star's airmass over this window spanned
-$z$=1.2-2.2, and we opted for a fixed 15 minute cadence over the
-entire sequence, except for a final 10 minute exposure due to
-increasing sky brightness at sunrise.  We observed without the iodine
-cell and used the C2 decker (0$\farcs$86$\times$14$\farcs$0) in the
-red instrument configuration, yielding a spectral resolution
-$R$$\approx$45{,}000 ($\delta v$$\approx$6.7\,\kms; $\delta v / v_{\rm
-eq}$$\approx$0.05).  We binned the CCD readout by a factor of three in
-the spatial dimension, yielding $\approx$1,000 photons (S/N=33) per
-pixel in the continuum at 6500\,\AA, at minimum airmass.  Strong winds
-contributed to 1\farcs2$\pm$0\farcs2 seeing over the night, but
-conditions were otherwise favorable.  We reduced the echelleogram to a
-one-dimensional spectrum using the standard techniques of the
-California Planet Survey \cite{Howard2010}.  Figure~\ref{fig:spec}b
-shows the result in the vicinity of H$\alpha$ without any additional
-processing.
-
-\subsection{Stellar Parameters}\phantom{+}
-\label{subsec:stparams}
+\appendix
+
+\section{Stellar Parameters}
+\label{sec:stparams}
 
 {\it Radial Velocity}---We measured the radial velocities of
-TIC~141146667 from our HIRES spectra using a pipeline that we
+TIC\,141146667 from our HIRES spectra using a pipeline that we
 developed for rapidly rotating stars.  Our method is based on
 template-matching against synthetic spectra produced by the PHOENIX
-stellar atmosphere code \cite{Husser2013}.  We used the PHOENIX models
+stellar atmosphere code \citep{Husser2013}.  We used the PHOENIX models
 with solar metallicity and alpha element abundances, and calibrated
-our pipeline using the standard stars described by \cite{Chubak2012}.
+our pipeline using the standard stars described by \citet{Chubak2012}.
 We used velocity standards spanning spectral types from G2 to M4
 (Barnard's Star), irrespective of rotation rate.  We used
-\texttt{barycorrpy} \cite{Kanodia2018} to calculate the velocity
+\texttt{barycorrpy} \citep{Kanodia2018} to calculate the velocity
 corrections due to Earth's motion around the solar system barycenter
@@
 reproduces the systemic velocities of known velocity standards
-\cite{Chubak2012} with an RMS of 0.66\,\kms.
-
-For TIC~141146667, we measured the radial velocities using regions
+\citep{Chubak2012} with an RMS of 0.66\,\kms.
+
+For TIC\,141146667, we measured the radial velocities using regions
 near the K~I (7700\,\AA) resonance line and three TiO bandheads
@@
 K~I (7700\,\AA) resonance line using the kernel suggested by
-\cite{Gray2008}; taking the mean and standard deviation of the
+\citet{Gray2008}; taking the mean and standard deviation of the
 resulting value over all epochs yielded $v_{\rm eq} \sin
@@
 phase-dispersion minimization analysis
-\cite{Stellingwerf1978,2021zndo...1011188B}.  There were no secondary
-periods in the TESS data.  Previous work \cite{Bouma2024} has shown
+\citep{Stellingwerf1978,2021zndo...1011188B}.  There were no secondary
+periods in the TESS data.  Previous work \citep{Bouma2024} has shown
 that about 30\% of CPVs show evidence for excess noise above the Gaia
@@
 multi-periodic low-mass stars are generally unresolved binaries
-\cite{Tokovinin2018}.  Overall, the CPV binary fraction seems
-consistent with that for field M dwarfs \cite{Winters2019}, pointing
+\citep{Tokovinin2018}.  Overall, the CPV binary fraction seems
+consistent with that for field M dwarfs \citep{Winters2019}, pointing
 to a weak or non-existent connection between the CPV phenomenon and
-(wide) binarity.  For TIC~141146667 specifically, although we find no
+(wide) binarity.  For TIC\,141146667 specifically, although we find no
 evidence for stellar multiplicity, our data are minimally constraining
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/sf4.pdf}
+  \includegraphics[width=0.48\textwidth]{figures/sf4.pdf}
   \caption{
@@
     (filled markers) plotted over the best-fit BT-Settl stellar
-    atmosphere model \cite{Allard2012} and the associated photometric
+    atmosphere model \citep{Allard2012} and the associated photometric
     predictions (empty markers).  This plot was made from an
-    adaptation of \texttt{astroARIADNE} \cite{Vines2022}.  The
+    adaptation of \texttt{astroARIADNE} \citep{Vines2022}.  The
     photometry extends from the Gaia DR3 blue passband to WISE W3;
@@
 radius measured using the spectral energy distribution (SED) fitting
-procedure described by \cite{Bouma2024}.  To summarize, this approach
-used \texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
-atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
-solar abundances and the \cite{Barber2006} water line lists.  This
+procedure described by \citep{Bouma2024}.  To summarize, this approach
+used \texttt{astroARIADNE} \citep{Vines2022} with the BT-Settl stellar
+atmosphere models \citep{Allard2012}, assuming the \citep{Asplund2009}
+solar abundances and the \citep{Barber2006} water line lists.  This
 approach fitted for the stellar effective temperature, radius,
@@
 Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting
-best-fit SED is shown in Extended Data Figure Figure~\ref{fig:sed}.
+best-fit SED is shown in Figure~\ref{fig:sed}.
 This method has the most constraining power for the star's effective
@@
 M5.5Ve by visually comparing the HIRES spectra against the photometric
-standards tabulated by \cite{Bochanski2007}.   This result agrees with
+standards tabulated by \citep{Bochanski2007}.   This result agrees with
 the effective temperature found from the SED fitting
-\cite{Pecaut2013}.  We measured the equivalent width of the H$\alpha$
+\citep{Pecaut2013}.  We measured the equivalent width of the H$\alpha$
 line by fitting a range of models to the time-averaged line profile
@@
 EW$_{{\rm H}\alpha}$=10.2$\pm$0.3\,\AA. Either value would classify
-the star as a weak-lined T Tauri \cite{Briceno2019}.
+the star as a weak-lined T Tauri \citep{Briceno2019}.
 
@@
 (35-150\,Myr) derived below, we then estimated the stellar mass by
-interpolating against the PARSEC v1.2S isochrones \cite{Chen2014}.
+interpolating against the PARSEC v1.2S isochrones \citep{Chen2014}.
 Specifically, we used the distance metric defined in Equation~8 of
-\cite{Bouma2024} to select the model mass closest to a given observed
+\citet{Bouma2024} to select the model mass closest to a given observed
 temperature, radius, and age.  This exercise yielded a mass of
@@
 expected to set the inner boundary at which corotating material might
-accumulate (e.g.~\cite{Townsend2005,Daley-Yates2024}).  Our final
+accumulate (e.g.~\citep{Townsend2005,Daley-Yates2024}).  Our final
 quoted $M_\star$ and $R_{\rm cr}$ values adopt the average of these
@@
 
-{\it Age: No Obvious Association Membership}---Previous work
-\cite{Bouma2024} has found that over 90\% of CPVs are associated with
+{\it Age: No Obvious Association Membership}---In
+\citet{Bouma2024} we previously found that over 90\% of CPVs within
+100\,pc are associated with
 known young moving groups based on their positions and kinematics.
-TIC~141146667 is in the minority.  We calculated the probability of
-TIC~141146667 being part of any nearby known group using
-BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  That particular model
+TIC\,141146667 is in the minority.  We calculated the probability of
+TIC\,141146667 being part of any nearby known group using
+BANYAN\,$\Sigma$ v1.2 \citep{Gagne2018}.  That particular model
 classifies it as a field star at $>$99.9\% confidence.  We also
-searched the local vicinity of TIC~141146667 for neighbors with
+searched the local vicinity of TIC\,141146667 for neighbors with
 similar projected on-sky velocities using \texttt{comove}
-\cite{Tofflemire2021}.  This yielded no strong candidates for
+\citep{Tofflemire2021}.  This yielded no strong candidates for
 co-moving stars with projected tangential velocities $\Delta v_{\rm
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/sf3.pdf}
+  \includegraphics[width=0.48\textwidth]{figures/sf3.pdf}
   \caption{Dereddened Gaia DR3 color vs.~absolute magnitude diagram of
-  TIC~141146667 and comparison samples. 
-  TIC~141146667 is on the pre-main sequence; stars with the same color
+  TIC\,141146667 and comparison samples. 
+  TIC\,141146667 is on the pre-main sequence; stars with the same color
   on the main sequence are $\approx$1.5\,magnitudes
@@
 {\it Age: Isochrones}---The color and absolute magnitude of
-TIC~141146667 suggest that it is a pre-main sequence M dwarf, similar
-to all other known CPVs \cite{Stauffer2017,Stauffer2021,Bouma2024}.
+TIC\,141146667 suggest that it is a pre-main sequence M dwarf, similar
+to all other known CPVs \citep{Stauffer2017,Stauffer2021,Bouma2024}.
 The star's proximity ($d$=58\,pc) and high galactic latitude
 ($b$=$+$53$^\circ$) yield negligible interstellar reddening along the
-line of sight \cite{Green2019}.  Extended Data Figure~\ref{fig:camd}
-shows the location of TIC~141146667 in the color--absolute magnitude
+line of sight \citep{Green2019}.  Figure~\ref{fig:camd}
+shows the location of TIC\,141146667 in the color--absolute magnitude
 diagram (CAMD) relative to young stellar populations including Upper
@@
 adopted the USco members in the $\delta$~Sco and $\sigma$~Sco
-sub-associations from \cite{Ratzenbock2023}, and the IC~2602 and
-Pleiades members from \cite{Hunt2024}.  We assumed an average $V$-band
+sub-associations from \citet{Ratzenbock2023}, and the IC~2602 and
+Pleiades members from \citet{Hunt2024}.  We assumed an average $V$-band
 extinction $A_{\rm V}$=$\{0.12, 0.11, 0.10\}\,{\rm mag}$ for USco
-\cite{Pecaut2016}, IC~2602 \cite{Hunt2024}, and the Pleiades
-\cite{Hunt2024} respectively, and ages of 8\,Myr
-\cite{Ratzenbock2023}, 40\,Myr \cite{Randich2018}, and 112\,Myr
-\cite{Dahm2015} for each respective cluster.  We dereddened the
+\citep{Pecaut2016}, IC~2602 \citep{Hunt2024}, and the Pleiades
+\citep{Hunt2024} respectively, and ages of 8\,Myr
+\citep{Ratzenbock2023}, 40\,Myr \citep{Randich2018}, and 112\,Myr
+\citep{Dahm2015} for each respective cluster.  We dereddened the
 photometry using the extinction coefficients $k_X\equiv A_X/A_0$
-tabulated in \cite{GaiaCollaboration2018}, assuming that $A_0 = 3.1
+tabulated in \citep{GaiaCollaboration2018}, assuming that $A_0 = 3.1
 E(B-V)$.
 
-Extended Data Figure~\ref{fig:camd} shows that TIC~141146667 falls
+Figure~\ref{fig:camd} shows that TIC\,141146667 falls
 between the USco and Pleiades sequences, and approximately overlaps
@@
 stars in the Pleiades of the same color have a similar absolute
-magnitude as TIC~141146667.  Previous work \cite{Stauffer2021} has
+magnitude as TIC\,141146667.  Previous work by \citet{Stauffer2021} has
 also noted that in the Gaia passbands, CPVs tend to be photometrically
@@
 studied for over sixty years
-\cite{Hayashi1963,Bildsten1997,Burke2004}.  \cite{Wood2023} provided a
+\citep{Hayashi1963,Bildsten1997,Burke2004}.  \citet{Wood2023} provided a
 recent overview: an abbreviated summary is that sufficiently cool and
@@
 measurement by constructing a wavelength-binned and Doppler-corrected
-TIC~141146667 spectrum, assigning its uncertainties based on the
+TIC\,141146667 spectrum, assigning its uncertainties based on the
 measured scatter across the five hour dataset.  We then compared this
 average spectrum against the nearest matching M6 template from
-\cite{Bochanski2007}.  The data show a small depression near the
+\citet{Bochanski2007}.  The data show a small depression near the
 expected lithium wavelength, potentially consistent with the $\Delta
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/sf2.pdf}
-  \caption{An upper limit on photospheric lithium for TIC~141146667
+  \includegraphics[width=0.48\textwidth]{figures/sf2.pdf}
+  \caption{An upper limit on photospheric lithium for TIC\,141146667
   (green triangle) yields a lower bound on the star's age of
   $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
-  \cite{Jeffries2023}; rich clusters in each age bin include NGC\,2264
+  \citep{Jeffries2023}; rich clusters in each age bin include NGC\,2264
   (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
@@
 
-Despite uncertainties in the details, what can be stated with
+Despite ambiguity in the details, what can be stated with
 confidence is that lithium is not abundant in the spectrum of
-TIC~141146667.  Extended Data Figure~\ref{fig:liew_population}
+TIC\,141146667.  Figure~\ref{fig:liew_population}
 compares our upper limit against the equivalent width measurements
-reported by \cite{Jeffries2023} based on the Gaia-ESO spectroscopic
-survey; Extended Data Figure~\ref{fig:hirescuts} shows the associated
+reported by \citet{Jeffries2023} based on the Gaia-ESO spectroscopic
+survey; Figure~\ref{fig:hirescuts} shows the associated
 raw spectra.  If the star were $\lesssim$20\,Myr old, at its
@@
 lithium-derived age of $t_{\rm Li,emp}$$\gtrsim$20\,Myr.  The
-\cite{Feiden2016} lithium isochrones provide a point for theoretical
+\citet{Feiden2016} lithium isochrones provide a point for theoretical
 comparison, and suggest that since $M_{\rm K}$$\approx$6.67\,mag,
@@
 complete depletion occurs in a star with this luminosity (see
-e.g.~Figure 7 from \cite{Wood2023}).
+e.g.~Figure 7 from \citealt{Wood2023}).
 
 {\it Age: Summary}---The main indicators for the youth of
-TIC~141146667 are {\it i)} that it is a complex periodic variable, and
+TIC\,141146667 are {\it i)} that it is a complex periodic variable, and
 {\it ii)} that it is 1.5 magnitudes brighter (four times more
@@
 because a previous CPV search unbiased in age found 90\% of its
-detections to be in $\lesssim$200\,Myr old clusters \cite{Bouma2024};
+detections to be in $\lesssim$200\,Myr old clusters \citep{Bouma2024};
 the remaining 10\% were not associated with any coeval population.
@@
 serendipitously found $\approx$50-100 examples of the class
-\cite{Rebull2016,Stauffer2017,Stauffer2018,Rebull2018,Zhan2019,Rebull2020,Stauffer2021,Rebull2022,Popinchalk2023},
+\citep{Rebull2016,Stauffer2017,Stauffer2018,Rebull2018,Zhan2019,Rebull2020,Stauffer2021,Rebull2022,Popinchalk2023},
 whereas analogous studies of Praesepe and the Hyades did not report
 any evidence for CPVs in a set of approximately one thousand
-$\approx$700\,Myr stars \cite{Rebull2017,Douglas2019,Rampalli2021}.
+$\approx$700\,Myr stars \citep{Rebull2017,Douglas2019,Rampalli2021}.
 Regarding the isochronal age constraint, the Pleiades (112\,Myr,
-\cite{Dahm2015}) shows a few stars of equal luminosity and the same
+\citealt{Dahm2015}) shows a few stars of equal luminosity and the same
 temperature, suggesting a photometric isochronal age upper limit
@@
 least 20\,Myr based on an empirical comparison using Gaia-ESO spectra,
-or at least 35\,Myr based on the \cite{Feiden2016} isochrones.  These
+or at least 35\,Myr based on the \citet{Feiden2016} isochrones.  These
 considerations yield our adopted age range of 35-150\,Myr.
 
-\subsection{Spectroscopic Variability}\phantom{+}
-\label{subsec:specvar}
-
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=\textwidth]{figures/sf5.pdf}
-  \caption{Time evolution of select regions in the Keck/HIRES spectra
-  from 17 February 2024.  We made this plot by applying a windowed
-  outlier rejection to remove cosmic rays and then smoothing each
-  spectrum with a Gaussian filter.  The horizontal axis shows the
-  velocity relative to each line's rest wavelength, normalized by the
-  stellar equatorial velocity.  H$\alpha$ is the only Balmer line to
-  show periodic variability of the form seen in Figure~\ref{fig:spec}.
-  The He 5876\,\AA\ line shows a time-dynamic blueshift that differs
-  from the Balmer lines.  Li 6708\,\AA\ shows no obvious absorption. }
-  \label{fig:hirescuts}
-\end{figure}
-
-Extended Data Figure~\ref{fig:hirescuts} shows a few regions of
-interest in the HIRES spectra, which cover 3650-7960\,\AA.  Higher
-order Balmer lines including H$\gamma$ and H$\delta$
-($n=5\rightarrow2$ and $n=6\rightarrow2$) do show variability outside
-the line core.  However, this variability is not clearly periodic in
-the same manner as the emission seen in H$\alpha$.  This could be
-because there are insufficient hydrogen ions in the relevant excited
-states, or because the spectra have lower precision in these bluer
-regions.  The Ca HK doublet is also detected in emission, while the
-continuum near it is not.  Chromospheric emission from the magnesium
-triplet is also detected, but these lines are too blended to be
-usable.
-
-Extended Data Figure~\ref{fig:hirescuts} provides a novel view on the
-blue excess that appeared at $\phi$$\approx$0.2 in H$\alpha$,
-H$\gamma$, H$\delta$, and He 5876\,\AA.  At the same epoch, H$\alpha$
-additionally shows a red clump of emission, and H$\gamma$ and
-H$\delta$ are also broadened on the red wing.  The rise of this
-emission in $<$15\,minutes might suggest a more sudden flow, rather
-than a stable, periodic component.  For instance, a stellar flare
-might be connected to such a sudden rise.  However, this idea seems
-incompatible with the sinusoidal emission seen later from
-$\phi$$\approx$0.5-1.0, and with the fact that flares typically excite
-iron lines in the blue HIRES orders, which are not observed.  More
-time-series spectroscopy would be needed to clarify this type of
-variability, in particular whether it is periodic or stochastic.
-
-Finally, the Li\,\textsc{I} 6708\,\AA\ doublet, which shows no obvious
-absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ resonance
-line are both visible in Extended Data Figure~\ref{fig:hirescuts}.  In
-the latter, narrow telluric absorption features overlap the blue wing
-of the line.  Neither of these regions shows any notable variability.
-
-\subsection{Detailed Behavior of H$\alpha$: Model and Implications}\phantom{+}
+\section{Detailed Behavior of H$\alpha$: Model and Implications}
 \label{subsec:halpha}
 
-\begin{figure}[!tp]
+\begin{figure*}[!tp]
   \centering
@@
   \label{fig:halphamodel}
-\end{figure}
+\end{figure*}
 
@@
 Figure~\ref{fig:spec} shows that clumps of circumstellar material
-exist around TIC~141146667, there is value in quantifying the exact
+exist around TIC\,141146667, there is value in quantifying the exact
 orbital periods, velocities, and velocity dispersions of these clumps.
@@
 the data {\it independently} using scipy's non-linear least squares
-\texttt{curve\_fit} implementation \cite{Virtanen2020}, and scaled the
+\texttt{curve\_fit} implementation \citep{Virtanen2020}, and scaled the
 resulting parameter covariance matrix by a constant factor to match
@@
 amplitudes, and standard deviations for each component are given in
-Extended Data Table~\ref{tab:halphamodelparams}.
+Table~\ref{tab:halphamodelparams}.
 
@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
   \centering
@@
   \label{fig:orbits}
-\end{figure}
-
-Accounting for these caveats, we used the results from Extended Data
+\end{figure*}
+
+Accounting for these caveats, we used the results from
 Table~\ref{tab:halphamodelparams} to quantify the orbital periods and
@@
 information criterion, we found no reason to prefer eccentric orbits.
-By visually inspecting Extended Data Figure~\ref{fig:halphamodel}, we
+By visually inspecting Figure~\ref{fig:halphamodel}, we
 excluded epochs where our gaussian profile fitting failed to either
@@
 then used NumPyro to sample the Gaussian likelihood for a Keplerian
-orbit with the NUTS algorithm \cite{Phan2019}.  We used the
+orbit with the NUTS algorithm \citep{Phan2019}.  We used the
 measurement uncertainties from each estimated mean radial velocity
@@
 approximately equal to the star's diameter.  At mid-transit, these
-inner clumps likely have a similar velocity dispersion, although with
+inner clumps have a similar velocity dispersion, although with
 greater uncertainty due to the differences between the $\phi$=0 and
-$\phi$=1 transits (see Extended Data Figure~\ref{fig:halphamodel}).
+$\phi$=1 transits (see Figure~\ref{fig:halphamodel}).
 This suggests a 1$\sigma$ emission contour in the azimuthal dimension
@@
 
-\subsection{Properties of the Plasma and Magnetospheric Environment}\phantom{+}
+\section{Spectroscopic Variability}
+\label{subsec:specvar}
+
+\begin{figure*}[!t]
+  \centering
+  \includegraphics[width=\textwidth]{figures/sf5.pdf}
+  \caption{Time evolution of select regions in the Keck/HIRES spectra
+  from 17 February 2024.  We made this plot by applying a windowed
+  outlier rejection to remove cosmic rays and then smoothing each
+  spectrum with a Gaussian filter.  The horizontal axis shows the
+  velocity relative to each line's rest wavelength, normalized by the
+  stellar equatorial velocity.  H$\alpha$ is the only Balmer line to
+  show periodic variability of the form seen in Figure~\ref{fig:spec}.
+  The He 5876\,\AA\ line shows a time-dynamic blueshift that differs
+  from the Balmer lines.  Li 6708\,\AA\ shows no obvious absorption. }
+  \label{fig:hirescuts}
+\end{figure*}
+
+Figure~\ref{fig:hirescuts} shows a few regions of
+interest in the HIRES spectra, which cover 3650-7960\,\AA.  Higher
+order Balmer lines including H$\gamma$ and H$\delta$
+($n=5\rightarrow2$ and $n=6\rightarrow2$) do show variability outside
+the line core.  However, this variability is not clearly periodic in
+the same manner as the emission seen in H$\alpha$.  This could be
+because there are insufficient hydrogen ions in the relevant excited
+states, or because the spectra have lower precision in these bluer
+regions.  The Ca HK doublet is also detected in emission, while the
+continuum near it is not.  Chromospheric emission from the magnesium
+triplet is also detected, but these lines are too blended to be
+usable.
+
+Figure~\ref{fig:hirescuts} provides a novel view on the
+blue excess that appeared at $\phi$$\approx$0.2 in H$\alpha$,
+H$\gamma$, H$\delta$, and He 5876\,\AA.  At the same epoch, H$\alpha$
+additionally shows a red clump of emission, and H$\gamma$ and
+H$\delta$ are also broadened on the red wing.  The rise of this
+emission in $<$15\,minutes might suggest a more sudden flow, rather
+than a stable, periodic component.  For instance, a stellar flare
+might be connected to such a sudden rise.  However, this idea seems
+incompatible with the sinusoidal emission seen later from
+$\phi$$\approx$0.5-1.0, and with the fact that flares typically excite
+iron lines in the blue HIRES orders, which are not observed.  More
+time-series spectroscopy would be needed to clarify this type of
+variability, in particular whether it is periodic or stochastic.
+
+Finally, the Li\,\textsc{I} 6708\,\AA\ doublet, which shows no obvious
+absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ resonance
+line are both visible in Figure~\ref{fig:hirescuts}.  In
+the latter, narrow telluric absorption features overlap the blue wing
+of the line.  Neither of these regions shows any notable variability.
+
+\section{Properties of the Plasma and Magnetospheric Environment}
 \label{subsec:gas}
@@
 recombination.  We neglect scattering because Figure~\ref{fig:spec}
-and Extended Data Figure~\ref{fig:hirescuts} show the amplitude of the
+and Figure~\ref{fig:hirescuts} show the amplitude of the
 circumstellar H$\alpha$ emission varying by a factor of $\approx$5, in
@@
 order of $10^{-12}$ to $10^{-13}$\,cm$^3$\,s$^{-1}$
-\cite{Hummer1987,Draine2011}.  Neglecting the effects of atoms other
+\citep{Hummer1987,Draine2011}.  Neglecting the effects of atoms other
 than hydrogen, we can assume an ionization fraction $x$, such that
@@
 thorough estimate would iteratively solve the equations of detailed
-balance and radiative transfer (e.g.~\cite{CollierCameron1989}
+balance and radiative transfer (e.g.~\citealt{CollierCameron1989}
 Figure~8), and potentially also consider departures from local
@@
 stars have been measured to span hundreds to thousands of Gauss
-\cite{Donati2009,Kochukhov2021,Reiners2022}, this bound is easily met
+\citep{Donati2009,Kochukhov2021,Reiners2022}, this bound is easily met
 at orbital distances of 2-4\,$R_\star$.
 
-\subsection{Upper and Lower Bounds on Dust}\phantom{+}
+\section{Upper and Lower Bounds on Dust}
 \label{subsec:dust}
@@
 observations of chromatic transits in analogous objects
-\cite{Tanimoto2020,Gunther2022,Koen2023}.  However, this scenario is
+\citep{Tanimoto2020,Gunther2022,Koen2023}.  However, this scenario is
 highly constrained.  An upper limit on the amount of hot dust follows
@@
 
-Regarding the upper limit, Extended Data Figure~\ref{fig:sed} shows
-the SED.  While AllWISE \cite{Cutri2014} yielded a confident W3
+Regarding the upper limit, Figure~\ref{fig:sed} shows
+the SED.  While AllWISE \citep{Cutri2014} yielded a confident W3
 detection (9.8$\sigma$) consistent with the photospheric extrapolation
@@
 indication (1.7$\sigma$) of detectable flux.  Similar to other CPVs
-\cite{Stauffer2017,Bouma2024}, the photometric uncertainties from WISE
+\citep{Stauffer2017,Bouma2024}, the photometric uncertainties from WISE
 W1 and W2 allow at most a $\lesssim$2\% excess at 3-5\,$\mu$m relative
@@
 temperature $T_{\rm d}$=1500\,K, typical for dust near the star (see
-\cite{Zhan2019} for discussion regarding dust sublimation).  We then
+\citealt{Zhan2019} for discussion regarding dust sublimation).  We then
 treat emission from the dust and star as Planck functions, and require
@@
 ext} \pi a^2$, where $Q_{\rm ext}$ is the extinction efficiency
-parameter, tabulated e.g.~by \cite{Croll2014} in their Figure 13.
-\cite{Sanderson2023} calculated the relevant cloud mass for this
+parameter, tabulated e.g.~by \citet{Croll2014} in their Figure 13.
+\citet{Sanderson2023} calculated the relevant cloud mass for this
 problem assuming a spherical dust clump of size $r$, and they found
@@
 planetesimals, and comets.  Prominences of the Sun have gas masses of
-$10^{14}$\,g-$10^{16}$\,g \cite{VialEngvold2015}.  A planetesimal of
+$10^{14}$\,g-$10^{16}$\,g \citep{VialEngvold2015}.  A planetesimal of
 mass $\approx$10$^{15}$\,g with a bulk density of 1\,g\,cm$^{-3}$
 would have a diameter of order one kilometer.  Halley's comet has a
-mass of order $10^{17}$\,g \cite{Rickman1989}, of which
+mass of order $10^{17}$\,g \citep{Rickman1989}, of which
 $\sim$$10^{14}$\,g is shed per orbit, most of which inspirals toward
@@
 external sources, feeding through a low-mass disk in particular cannot
-be ruled out based on typical disk depletion times \cite{Haisch2001}.
+be ruled out based on typical disk depletion times \citep{Haisch2001}.
 Observations of infrared excesses and accretion signatures in low-mass
@@
 distribution for such disks
-\cite{Silverberg2020,Lee2020,Gaidos2022,Pfalzner2024}.
+\citep{Silverberg2020,Lee2020,Gaidos2022,Pfalzner2024}.
 
@@
     \hline
-    $T_{\rm eff}$ (K) & 2972 $\pm$ 40 & SED fit \cite{Bouma2024} \\
-    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & SED fit \cite{Bouma2024} \\
-    $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & SED fit \cite{Bouma2024} \\
+    $T_{\rm eff}$ (K) & 2972 $\pm$ 40 & SED fit \citep{Bouma2024} \\
+    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & SED fit \citep{Bouma2024} \\
+    $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & SED fit \citep{Bouma2024} \\
     $P_{\rm rot}$ (hours) & 3.930 $\pm$ 0.001 & TESS \\ 
@@
     $i_\star$($^\circ$) & $>$63 & Derived \\
-    $A_V$ (mag) & 0 & \cite{Green2019} \\
-    $M_\star$ ($M_{\odot}$)  & 0.22 $\pm$ 0.02  & PARSEC \cite{Chen2014}\\
+    $A_V$ (mag) & 0 & \citep{Green2019} \\
+    $M_\star$ ($M_{\odot}$)  & 0.22 $\pm$ 0.02  & PARSEC \citep{Chen2014}\\
     ${\rm EW}_{\rm Li}$ (m\AA) & $<$107 & HIRES (2$\sigma$)\\
     $t_{\rm CAMD}$ (Myr) & 30-150 &  Gaia DR3 \\
-    $t_{\rm Li,emp}$ (Myr) & $>$20 &  HIRES, \cite{Jeffries2023} \\
-    $t_{\rm Li,th}$ (Myr) & $>$35 &  HIRES, \cite{Feiden2016} \\
+    $t_{\rm Li,emp}$ (Myr) & $>$20 &  HIRES, \citep{Jeffries2023} \\
+    $t_{\rm Li,th}$ (Myr) & $>$35 &  HIRES, \citep{Feiden2016} \\
     $t_{\rm adopted}$ (Myr) & 35-150 &  -- \\
@@
     \end{tabular}
-		\caption{Properties of TIC~141146667.  References:
-    Gaia DR3 \cite{GaiaDR3}, TESS \cite{Ricker2015},
-    TIC8 \cite{Stassun2019}, 2MASS \cite{Skrutskie2006}, ALLWISE
-    \cite{Cutri2014}.}
+		\caption{Properties of TIC\,141146667.  References:
+    Gaia DR3 \citep{GaiaDR3}, TESS \citep{Ricker2015},
+    TIC8 \citep{Stassun2019}, 2MASS \citep{Skrutskie2006}, ALLWISE
+    \citep{Cutri2014}.}
     \label{tab:stparams}
@@
   \end{tabular}
-  \caption{TIC~141146667 radial velocities relative to the systemic
+  \caption{TIC\,141146667 radial velocities relative to the systemic
   velocity based on the 7699\,\AA\ resonance line and TiO bandheads.}
@@
   subset of the spectral epochs yielded statistically significant
-  detections of the circumstellar emission (see Extended Data
+  detections of the circumstellar emission (see
   Figure~\ref{fig:halphamodel}).}
@@
 
-\end{methods}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\clearpage
+
+\bibliographystyle{aasjournal}
 \bibliography{cpvbib.bib}
-\bibliographystyle{naturemagfixed}
 
@@
 
-\begin{addendum}
-
-\item[Acknowledgments]
-  LGB is grateful to M.~Jardine, A.~Weinberger, B.~Tofflemire,
+\begin{acknowledgements}
+  We thank M.~Jardine, A.~Weinberger, B.~Tofflemire,
   J.~Spake, J.~Winn, and L.~Hillenbrand for insightful conversations
@@
   for the opportunity to conduct observations from this mountain.
-
-%\item[Author Contributions] LGB is responsible for all aspects of this
-%  work, including conceptualization, data analysis, interpretation,
-%  manuscript preparation, and revision.
-%
-\item[Data Availability] The TESS two-minute cadence data used in this
-  work are publicly available from the Mikulski Archive for Space
-  Telescopes (MAST; \url{https://mast.stsci.edu}). The Keck/HIRES
-  spectra analyzed here are accessible via the Keck Observatory
-  Archive (KOA; \url{https://koa.ipac.caltech.edu}).
-
-\item[Competing Interests] The author declares no competing financial
-  interests.
-
-\item[Correspondence] Correspondence and requests for materials should
-  be addressed to Luke Bouma, at either lbouma@carnegiescience.edu or
-  bouma.luke@gmail.com.
-\end{addendum}
+\end{acknowledgements}
+
+\facilities{
+  Gaia \citep{GaiaDR3},
+  TESS \citep{Ricker2015},
+  Keck:I (HIRES) \citep{vogt_hires_1994},
+	2MASS \citep{Skrutskie2006},
+	SDSS \citep{2000AJ....120.1579Y}.
+}
+
+\software{
+  astropy \citep{astropy:2013,astropy:2018,astropy:2022},
+  matplotlib \citep{matplotlib},
+  numpy \citep{numpy},
+  scipy \citep{scipy}.
+}
 

### 2025-04-22 paper/ms.tex
update

@@
 \usepackage[caption=false]{subfig} % for subfloat
+\usepackage{caption}
+\DeclareCaptionLabelFormat{moviefmt}{#1~#2\ (Movie)}
 \usepackage{xcolor, fontawesome}
@@
 investment with JWST is proceeding accordingly
-\citep[see][]{Redfield2024,TRAPPIST1JWSTCommunityInitiative2024}.  The
-question of how an M dwarf's evolution influences its
-planets---especially the retention of their atmospheres---has in turn
-become a major theme in exoplanet and stellar astrophysics.  Previous
-work has established that most M dwarfs host close-in planets
-\citep{Dressing2015} that on average are subject to long circumstellar
-disk lifetimes \citep{Ribas2015}, to high doses of UV radiation
-\citep{France2016}, and to a high incidence of flares and coronal mass
-ejections \citep{Feinstein2020}.  However, despite extensive work in
-these areas, the plasma and magnetospheric environments that bathe
-young, close-in exoplanets remain challenging to quantify.
-Understanding these environments is crucial because they directly
-impact atmospheric retention and habitability of close-in planets.
+\citep[][]{Redfield2024,TRAPPIST1JWSTCommunityInitiative2024}.  The
+question of how M dwarfs influence their planets---especially the
+retention of their atmospheres---has correspondingly grown in
+importance.  Previous work has established
+that most M dwarfs host close-in planets \citep{Dressing2015} that on
+average are subject to long circumstellar disk lifetimes
+\citep{Ribas2015}, to high doses of UV radiation \citep{France2016},
+and to a high incidence of flares and coronal mass ejections
+\citep{Feinstein2020}.  However, despite extensive work in these
+areas, the plasma and magnetospheric environments that bathe young,
+close-in exoplanets remain challenging to quantify.  Understanding
+these environments is crucial because they directly impact atmospheric
+retention and habitability of close-in exoplanets.
 
 One glaring example of our current ignorance is the complex periodic
-variables (CPVs).  While Figure~\ref{fig:lc} highlights the main
-object of interest in this article, over one hundred analogous objects
+variables.  While Figure~\ref{fig:lc} highlights the main
+object of interest in this article, over one hundred analogous systems
 have now been found by K2 and TESS
@@
 $\approx$3\% of stars a few million years old show this complex
-photometric behavior, an observed fraction which decreases to
-$\approx$0.3\% by $\approx$150\,Myr \citep{Rebull2020}.  CPVs are a
-known source of astrophysical false positives in searches for
-transiting exoplanets around young M dwarfs
+behavior, an observed fraction which decreases to
+$\approx$0.3\% by $\approx$110\,Myr \citep{Rebull2020}.  CPVs can and
+have been confused for transiting exoplanets
 \citep{vanEyken2012,Johns-Krull2016,Bouma2020}.
@@
 yet been acquired for the presence of any circumstellar material.  If
-the material exists, then the geometric correction from the transit
+such material exists, then the geometric correction from the transit
 probability would imply an intrinsic occurrence rate at least a few
@@
 \citep{CollierCameron1989,CollierCameron1992,Barnes2000,Donati2000,Dunstone2006,Skelly2008,Leitzinger2016,Cang2021}.
-Such clumps are thought to be forced into corotation by the magnetic
+Such clumps are thought to be forced into corotation by the star's magnetic
 field, and the exact geometry of where the plasma can accumulate is
@@
   \vspace{-0.3cm}
-  \caption{{\bf Figure 1 (Movie):  TIC\,141146667 is a complex periodic
-  variable (CPV).}  The online movie,
-  \href{https://lgbouma.com/movies/TIC141146667_20250116.mp4}{available here},
+  \captionsetup{labelformat=moviefmt,labelsep=colon}
+	\caption{\textbf{TIC\,141146667 is a complex periodic variable (CPV).}  The
+online movie,
+  \href{https://lgbouma.com/movies/TIC141146667_20250116.mp4}{{\bf
+  available here}},
   covers a baseline of 5{,}784 cycles irregularly sampled over three
@@
   stellar rotation, and (we hypothesize) of corotating clumps of
-  circumstellar material.  Raw data acquired with two minute sampling
-  are in gray; black averages to 100 points per cycle.  Similar to
-  other stars of this class, the sharp photometric features persist
+  circumstellar material.  Raw data acquired at two minute dence
+  are in gray; black averages to 100 points per cycle.  
+  The sharp photometric features persist
   for tens to thousands of rotational cycles. }
@@
 In this study, we present the first spectroscopic detection of
-corotating clumps of cool plasma around a CPV, TIC\,141146667.  The
-observations are presented in Section~\ref{sec:obs}, with the main new
-evidence in Figure~\ref{fig:spec}.  Section~\ref{sec:results} expounds
-on the results; Section~\ref{sec:disc} discusses their interpretation
-and highlights future directions.
+corotating clumps of cool plasma around a CPV, TIC\,141146667.
+Section~\ref{sec:obs} describes our observations;
+Section~\ref{sec:results} presents the results; Section~\ref{sec:disc}
+discusses their interpretation and highlights future directions.
 
@@
 structured, periodic light curves \citep{Ricker2015}.  We selected the
-star for spectroscopy because its brightness and rotation rate enabled
+star for spectroscopy because its brightness and rapid rotation enabled
 an efficient search for variability in its line profiles.
-As apparently single pre-main sequence M dwarf, its properties are
-typical for the general CPV population (see Table~\ref{tab:params} and
+As an apparently single pre-main sequence M dwarf, its properties are
+typical for the CPV population (see Table~\ref{tab:params} and
 Appendix~\ref{sec:stparams}).
@@
 We observed TIC\,141146667 ($V$=16.2) for five hours on
-17~February~2024 (UT) using the High Resolution Echelle Spectrometer
+17~February~2024 using the High Resolution Echelle Spectrometer
 (HIRES; \citealt{vogt_hires_1994}) on the 10\,m Keck I telescope.  The
@@
 using the standard techniques of the California Planet Survey
-\citep{Howard2010}.  Figure~\ref{fig:spec} shows the result in the
-vicinity of H$\alpha$ without any additional processing.
-
-To date, TESS has observed TIC\,141146667 ($T$=13.3) for a total of six
-non-contiguous months spanning 2019-2024.  Two-minute cadence observations were
-acquired during Sectors 41, 48 (TESS DDT039, PI: Kunimoto), and 75
-(TESS Program G06030, PI: Bouma); the remaining 30-minute data during
-Sectors 14, 15, and 21 smears sharp features over the $<$4\,hour
-period (see \citealt{Gunther2022}).  The concatenated two-minute data
-are shown in the movie associated with Figure~\ref{fig:lc}.  The movie shows that,
+\citep{Howard2010}.  
+%Figure~\ref{fig:spec} shows the result in the
+%vicinity of H$\alpha$ without any additional processing.
+
+TESS observed TIC\,141146667 ($T$=13.3) for six non-contiguous months
+spanning 2019-2024.  TESS acquired these observations at two-minute
+cadence during Sectors 41, 48 (TESS DDT039, PI: Kunimoto), and 75
+(TESS Program G06030, PI: Bouma).   The 30-minute data during Sectors
+14, 15, and 21 probably smeared sharp features over the $<$4\,hour
+period (see \citealt{Gunther2022}).  The movie in
+Figure~\ref{fig:lc} shows the two-minute data: 
 like other CPVs, TIC\,141146667 maintains a fixed period over
@@
 The nearest known star, TIC\,141146666 ($T$=14.5), is 25$''$ from
-TIC\,141146667 and is photometrically stable in the TESS target pixel
-cutouts; crowding is not a concern.
+TIC\,141146667 and is photometrically stable in the TESS images;
+crowding is not a concern.
 
@@
   \centering
-  \includegraphics[width=0.95\textwidth]{figures/sf1.pdf}
+  \includegraphics[width=0.935\textwidth]{figures/sf1.pdf}
   \vspace{-0.2cm}
@@
   observation (green bar).}  {\bf a,} TESS simple aperture photometry.
-  Data gaps caused by light from the Earth (BTJD 3356-3358.5) and Moon
+  Data gaps caused by light from Earth (BTJD 3356-3358.5) and Moon
   (BTJD 3359.5-3360.5) are visible.  Raw two minute
@@
 simultaneous observations.   Figure~\ref{fig:fulllc} shows the result;
-the Earth passed within 25$^\circ$ of the
-TESS camera's boresight from BTJD 3356.0~-~3358.5, which caused a data
-gap that ended twelve hours after the Keck/HIRES observation epoch
+Earth passed within 25$^\circ$ of the
+TESS camera's boresight from BTJD 3356.0-3358.5, which caused a data
+gap that ended twelve hours after our Keck/HIRES observations
 (green bar).  From
-BTJD 3359.4~-~3362.0, the Moon then passed within 25$^\circ$ of the
+BTJD 3359.4-3362.0, the Moon then passed within 25$^\circ$ of the
 camera's boresight.  Based on the level of scattered light in the
 optimal TIC\,141146667 aperture \citep{Jenkins2016}, we manually masked
-out times from 3359.40~-~3360.13; the remainder of the data during the
-lunar approach were usable.  Small data gaps from BTJD
-3353.55~-~3353.77 and from BTJD 3360.12~-~3360.33 were caused by data
-downlinks at the spacecraft's perigee and apogee, respectively.
+out data in the TESS light curve from 3359.40-3360.13; the remainder
+of the data during the lunar approach were usable.  Small gaps
+from BTJD 3353.55-3353.77 and 3360.12-3360.33 were caused by
+data downlinks at the spacecraft's perigee and apogee.
 
 While the data gap is unfortunate, Figure~\ref{fig:fulllc} shows
-that a large, complex flux decrement spanned roughly half of each
+that a large flux decrement spanned roughly half of each
 cycle both before and after the HIRES data were acquired.  From BTJD
-3352~-~3356, this dip had two sharp local minima;  the local minimum
+3352-3356, this dip had two sharp local minima;  the local minimum
 at $\phi$$\approx$0.8 disappeared following the flare at BTJD 3353,
@@
 \citep{Stauffer2017,Bouma2024}.  The photometric shape therefore
-evolved during the twelve cycles spanning the 3356~-~3358 gap, since
+evolved during the twelve cycles spanning the 3356-3358 gap, since
 the average shape from 3358-3363 more closely resembles the initial
@@
   \includegraphics[width=0.99\textwidth]{figures/f2.pdf}
-  \vspace{-0.2cm}
-  \caption{{\bf Figure 2 (Movie):}  
-  Emission from circumstellar plasma orbiting TIC\,141146667.
+  \vspace{-0.25cm}
+  \captionsetup{labelformat=moviefmt,labelsep=colon}
+	\caption{\textbf{Emission from circumstellar plasma orbiting
+TIC\,141146667.}
   The online movie,
-  \href{https://lgbouma.com/movies/TIC141146667_sixpanel.mp4}{available here},
+  \href{https://lgbouma.com/movies/TIC141146667_sixpanel.mp4}{{\bf
+  available here}},
   shows the spectral evolution over five hours.
@@
 not controlled by gravitational attraction to the star; it is more
-readily explained as a plasma being dragged along
+readily explained as plasma being dragged along
 with a rigidly rotating stellar magnetic field.  The velocity
@@
 of a CPV, and they demonstrate that corotating circumstellar plasma
-clumps exist around at least one such star.  While starspots likely do
+clumps exist around at least one such star.  While starspots do
 contribute smooth signals to the photometric variability, a
-``starspot-only'' scenario for the CPVs \citep{Koen2021} is
-incompatible with our observations.  Scenarios in which the
-circumstellar material is made only of dust are similarly ruled out.
-While starspots and dust may both be present, the observed H$\alpha$
-emission requires plasma with a significant population of hydrogen
-atoms in the $n$=3 excited state.  Most of this H$\alpha$ emission
-originates in ``clumps'' with size similar to that of the star; radial
-``spokes'' or azimuthally-extended ``arcs'' for the emitting material are
-ruled out by the observed H$\alpha$ velocity dispersion (see
-\S~\ref{subsec:halpha}).  
-The observed H$\alpha$ luminosity suggests characteristic densities
-and masses for the gaseous component of these clumps of $n_{\rm H}
-\sim 10^{11}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g (see
-\S~\ref{subsec:gas}).  Dust, if present, is independently constrained
-to have a total mass $10^{15}\,{\rm g} < M_{\rm dust} < 10^{17}\,{\rm
-g}$ (see \S~\ref{subsec:dust}).  
-The spectra show minimal evidence for significant populations in
-higher-order hydrogen states (see Appendix~\ref{subsec:specvar}).
-
+``starspot-only'' scenario to explain the complexity of the CPVs
+\citep{Koen2021} is incompatible with our observations.  Scenarios in
+which the circumstellar material is made only of dust are similarly
+ruled out.  While starspots and dust may both be present, our HIRES
+spectra require plasma with a significant population of hydrogen atoms
+in the $n$=3 excited state, with no evidence for significant
+higher-order excitations (see Appendix~\ref{subsec:specvar}).  Most of
+this H$\alpha$ emission originates in ``clumps'' with size similar to
+that of the star; radial ``spokes'' or azimuthally-extended ``arcs''
+for the emitting material are ruled out by the observed H$\alpha$
+velocity dispersion (see Appendix~\ref{subsec:halpha}).  The observed
+H$\alpha$ luminosity suggests characteristic densities and masses for
+the gaseous component of these clumps of $n_{\rm H} \sim
+10^{11}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g (see
+Appendix~\ref{subsec:gas}).  Dust, if present, is independently
+constrained to have a total mass $10^{15}\,{\rm g} < M_{\rm dust} <
+10^{17}\,{\rm g}$ (see Appendix~\ref{subsec:dust}).
+
+%TODO: improve heading?
 \subsection{Plasma Tori Could Explain Complex Periodic Variables}

### 2025-04-23 paper/ms.tex
update

@@
 2: Gaia DR3 photometry shows the star is on the pre-main sequence,
-   while the spectrum lacks lithium (see \S~\ref{sec:stparams}).
+   while the spectrum lacks lithium (Appendix~\ref{sec:stparams}).
 3: PARSEC v1.2S \citep{Chen2014}.
-4: Keck/HIRES (see \S~\ref{subsec:halpha}).
+4: Keck/HIRES (Appendix~\ref{subsec:halpha}).
 5: TESS light curve.
@@
 
-\subsection{Corotating Plasma Clumps}
+\subsection{Physical Properties of the Corotating Plasma Clumps}
+
+% this paragraph: physical properties that can be inferred with
+% confidence
 
@@
 of a CPV, and they demonstrate that corotating circumstellar plasma
-clumps exist around at least one such star.  While starspots do
-contribute smooth signals to the photometric variability, a
-``starspot-only'' scenario to explain the complexity of the CPVs
-\citep{Koen2021} is incompatible with our observations.  Scenarios in
-which the circumstellar material is made only of dust are similarly
-ruled out.  While starspots and dust may both be present, our HIRES
-spectra require plasma with a significant population of hydrogen atoms
-in the $n$=3 excited state, with no evidence for significant
+clumps exist around at least one such star.  More specifically, our
+HIRES spectra require plasma with a significant population of hydrogen
+in the $n$=3 excited state, with minimal evidence for 
 higher-order excitations (see Appendix~\ref{subsec:specvar}).  Most of
@@
 that of the star; radial ``spokes'' or azimuthally-extended ``arcs''
-for the emitting material are ruled out by the observed H$\alpha$
-velocity dispersion (see Appendix~\ref{subsec:halpha}).  The observed
-H$\alpha$ luminosity suggests characteristic densities and masses for
-the gaseous component of these clumps of $n_{\rm H} \sim
+for the {\it emitting material} are ruled out by the observed H$\alpha$
+velocity dispersion (see Appendix~\ref{subsec:halpha}).  The H$\alpha$
+line luminosity suggests characteristic densities and masses for the
+gaseous component of these clumps of $n_{\rm H} \sim
 10^{11}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g (see
@@
 
-%TODO: improve heading?
-\subsection{Plasma Tori Could Explain Complex Periodic Variables}
-
-While the H$\alpha$ emission appears consistent with clumps, the
-photometric width of the complex flux dips in TIC\,141146667
-specifically, and CPVs more broadly \citep[Figure~4 of][]{Bouma2024},
-raise the possibility that azimuthally-distributed material may be the
-norm for these objects.  In other words, a torus may be a more
+\subsection{Theoretical Context}
+
+While the H$\alpha$ emission appears to mostly originate from clumps,
+the the complex flux dip in TIC\,141146667 spans roughly half of each
+cyle; in CPVs more broadly, dips typically last 5-50\% of each cycle
+\citep{Bouma2024}.  This raises the possibility that
+azimuthally-distributed material may be the norm for these objects.
+In other words, a warped, azimuthally-asymmetric torus may be a more
 accurate picture than a clump.
 
-\citet{Townsend2005} outline the physics of how such structures can
-exist: for stars with magnetospheric radii $R_{\rm m}$ that exceed
-their corotation radii $R_{\rm c}$, the effective potential
-experienced by a charged particle can have a local minimum outside
-$R_{\rm c}$, enabling material to accumulate in a
+\citet{Townsend2005} outline the physics of how such structures might
+exist for the azimuthally symmetric case.
+A charged particle that orbits a 
+star with a magnetospheric radius $R_{\rm m}$ that exceeds
+its Keplerian corotation radius $R_{\rm c}$ experiences an effective potential
+that has a local minimum outside
+$R_{\rm c}$, which enables material to accumulate in these
 centrifugally-supported magnetosphere
@@
 
-Nonetheless, \citet{Townsend2008} synthesized light curves for plasma
-trapped in rigidly rotating magnetospheres of rapidly rotating stars;
-and found that assuming a dipole magnetic geometry, one can obtain
-W-shaped eclipses similar to those seen for TIC\,141146667.  See in
-particular the
+In a follow-up study, \citet{Townsend2008} synthesized light curves
+for plasma trapped in rigidly rotating magnetospheres of rapidly
+rotating stars; and found that assuming a dipole magnetic geometry,
+one can obtain W-shaped eclipses similar to those seen for
+TIC\,141146667.  See in particular the
 \href{http://user.astro.wisc.edu/~townsend/static.php?ref=rrm-movies#Download_Bundles}{movies}
@@
 double-peaked behavior.
+
+\subsection{Plasma Tori and Complex Photometric Morphology}
+
+Microphysically, it is not obvious whether hydrogen alone can produce
+the broadband opacities and chromatic flux variations seen in CPVs.
+For detailed discussion of this point, see Section 5.6 in
+\citet{Bouma2024}.
+With that said, Figures~\ref{fig:fulllc} and~\ref{fig:spec} show that
+at least {\it some} of the complex photometric dip for TIC\,141146667
+is temporally coincident with the transit of the inner clump of
+H$\alpha$ emitting material.
+This could be because
+
+However, the transit lasts $\approx$22\% of the
+
+$\phi$=-0.1 to $\phi$=+0.12 (see
+Appendix~\ref{subsec:halpha}).  This spectroscopic transit coincides with
+the latter half of the complex eclipse feature in the TESS data.
+
+ suggests that the transits of the
+ cannot explain the entirety of the complex
+photometric modulation;  the spectroscopic transits happen too fast,
+and at orbital phases that only partially overlap with the photometric
+modulations.
+
+is not optically thick.
+ discussed the general issue: CPV dips are chromatic,
+
+In
+fact, Figure~\ref{fig:spec} suggests that the transits of the
+H$\alpha$ emitting material cannot explain the entirety of the complex
+photometric modulation;  the spectroscopic transits happen too fast,
+and at orbital phases that only partially overlap with the photometric
+modulations.
+
+While starspots do
+contribute smooth signals to the photometric variability, a
+``starspot-only'' scenario to explain the complexity of the CPVs
+\citep{Koen2021} is incompatible with our observations.  Scenarios in
+which the circumstellar material is made only of dust are similarly
+ruled out.  While starspots and dust may both be present,
 

### 2025-04-23 paper/ms.tex
update

--- 2025-04-22 paper/ms.tex
@@
 \accepted{--}
-\shorttitle{M Dwarf Plasma Torus}
+\shorttitle{CPV Plasma Torus}
 
@@
   show structured, periodic optical light curves suggestive of
-transiting opaque material that corotates with the star.  However,
-the composition, origin, and even the existence of this material are
+  transiting opaque material that corotates with the star.  However, the
+  composition, origin, and even the existence of this material are
   uncertain. The main alternative hypothesis is that these complex
@@
   ($P$=3.9\,hr) CPV, TIC\,141146667.  The spectra show sinusoidal
-time-varying Balmer emission at twice to four times the star's
+  time-varying H$\alpha$ emission at twice to four times the star's
   equatorial velocity, providing direct evidence for cool
-($\lesssim$10$^4$\,K) plasma clumps trapped in corotation around a CPV.
-These data support the idea that young, rapidly-rotating M dwarfs can
-sustain warped plasma tori, similar to massive magnetic stars.  The
-origin of the optically thick material in these tori, and the issue
-of whether this material contains a significant amount of dust,
-remain unclear.
+  ($\lesssim$10$^4$\,K) plasma clumps trapped in corotation around a
+  CPV.  These data support the idea that young, rapidly-rotating M
+  dwarfs can sustain warped plasma tori, similar to massive magnetic
+  stars.  It remains unclear whether these structures originate
+  intrinsically from the star or are fed by external sources. Likewise,
+  the mechanism by which their optically thick clumps arise is still
+  unknown.  Rough estimates suggest $\gtrsim$10\% of M dwarfs host
+  similar structures during their early lives.
 \end{abstract}
@@
 Stellar rotation (1629) Periodic variable stars (1213), Weak-line T
-Tauri stars (1795) }
+Tauri stars (1795)}
 
@@
 
-One glaring example of our current ignorance is the complex periodic
+One example of our current ignorance is the complex periodic
 variables.  While Figure~\ref{fig:lc} highlights the main
@@
 
-We identified TIC\,141146667 in previous work \citep{Bouma2024} by
-searching TESS two-minute data from 2018-2022 for highly
-structured, periodic light curves \citep{Ricker2015}.  We selected the
-star for spectroscopy because its brightness and rapid rotation enabled
-an efficient search for variability in its line profiles.
-As an apparently single pre-main sequence M dwarf, its properties are
-typical for the CPV population (see Table~\ref{tab:params} and
-Appendix~\ref{sec:stparams}).
-
-We observed TIC\,141146667 ($V$=16.2) for five hours on
-17~February~2024 using the High Resolution Echelle Spectrometer
-(HIRES; \citealt{vogt_hires_1994}) on the 10\,m Keck I telescope.  The
-observations spanned the second half of the night, from 17 February
-2024 10:47 to 16:13 (UT).  The star's airmass spanned $z$=1.2-2.2, and
-we opted for a fixed 15 minute cadence, except for a final 10 minute
-exposure due to increasing sky brightness at sunrise.  We observed
-without the iodine cell and used the C2 decker
-(0$\farcs$86$\times$14$\farcs$0) in the red configuration, yielding a
-spectral resolution $R$$\approx$45{,}000 ($\delta
-v$$\approx$6.7\,\kms; $\delta v / v_{\rm eq}$$\approx$0.05).  We
-binned the CCD readout by a factor of three in the spatial dimension,
-yielding $\approx$1,000 photons (S/N=33) per pixel in the continuum at
-6500\,\AA, at minimum airmass.  Strong winds contributed to
-1$''$-1\farcs5 seeing over the night, but conditions were otherwise
-favorable.  We reduced the echelleogram to a one-dimensional spectrum
-using the standard techniques of the California Planet Survey
-\citep{Howard2010}.  
-%Figure~\ref{fig:spec} shows the result in the
-%vicinity of H$\alpha$ without any additional processing.
-
-TESS observed TIC\,141146667 ($T$=13.3) for six non-contiguous months
-spanning 2019-2024.  TESS acquired these observations at two-minute
-cadence during Sectors 41, 48 (TESS DDT039, PI: Kunimoto), and 75
-(TESS Program G06030, PI: Bouma).   The 30-minute data during Sectors
-14, 15, and 21 probably smeared sharp features over the $<$4\,hour
-period (see \citealt{Gunther2022}).  The movie in
-Figure~\ref{fig:lc} shows the two-minute data: 
-like other CPVs, TIC\,141146667 maintains a fixed period over
-timescales of years while its detailed photometric morphology evolves.
-The nearest known star, TIC\,141146666 ($T$=14.5), is 25$''$ from
-TIC\,141146667 and is photometrically stable in the TESS images;
-crowding is not a concern.
+\begin{table}
+\small
+\setlength{\tabcolsep}{2pt}
+\centering
+\caption{Selected system parameters for TIC\,141146667.}
+\label{tab:params}
+\begin{tabular}{llcc}
+\hline \hline
+Parameter & Description & Value & Source\\
+\hline 
+%
+$T_{\rm eff}$\dotfill                   & Effective Temperature (K) \hspace{9pt}\dotfill                 & 2972 $\pm$ 40    & 1 \\
+%
+$R_\star$\dotfill                       & Stellar radius ($R_\odot$)\dotfill                             & 0.42$\pm$0.02    & 1 \\
+%
+Age                                     & Stellar age range (Myr)\dotfill                                & 35-150           & 2 \\
+%
+$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & 0.22$\pm$0.02    & 3 \\
+%
+$\gamma$\dotfill                        & Systemic radial velocity (\kms)\dotfill                        & 0.61 $\pm$ 1.47  & 4 \\
+%
+SpT\dotfill                             & Spectral Type\dotfill                                          & M5.5Ve           & 4 \\
+%
+$P_{\rm rot}$\dotfill                   & Photometric rotation period (hr)\dotfill                       & $3.930\pm 0.001$ & 5 \\
+%
+$v_{\rm eq}$\dotfill		                & Equatorial velocity \dotfill                                   &  130$\pm$4       & 6 \\
+                                        & \hspace{3pt} ($2\pi R_\star/P_{\rm rot}$) (\kms)	             &                      \\
+%
+$v_{\rm eq}\sin{i_\star}$\dotfill		    & Projected rotational\dotfill                                   &  138$\pm$8       & 4 \\
+                                        & \hspace{3pt} velocity (\kms)	                                 &                      \\
+%
+$v_{\rm break}$\dotfill		              & Breakup velocity \dotfill                                      &  316$\pm$16      & 6 \\
+                                        & \hspace{3pt} ($G M_\star / R_\star$)$^{1/2}$ (\kms)	           &                      \\
+%
+$i_\star$\dotfill                       & Stellar inclination\dotfill                                    & 	$>$63           & 4 \\
+                                        & \hspace{3pt}  2$\sigma$ lower limit (deg)	                     &                      \\
+%
+$d$\dotfill                             & Distance (pc)\dotfill                                          & $57.54 \pm 0.09$ & 7 \\
+%
+$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   & $1.82 \pm 0.10$  & 6 \\
+                                        & \hspace{3pt} radius ($R_\star$)	                               &                      \\
+%
+$a_0$\dotfill                           & Mean inner clump (0)\hspace{9pt}\dotfill           &  2.07$\pm$0.04   & 4 \\
+                                        & \hspace{3pt} orbital radius ($R_\star$)	                       &                      \\
+%
+$a_1$\dotfill                           & Mean inner clump (1)\hspace{9pt}\dotfill           &  2.88$\pm$0.10   & 4 \\
+                                        & \hspace{3pt} orbital radius ($R_\star$)	                       &                      \\
+%
+$a_2$\dotfill                           & Mean outer clump\hspace{9pt}\dotfill           &  3.88$\pm$0.25   & 4 \\
+                                        & \hspace{3pt} orbital radius ($R_\star$)	                       &                      \\
+%
+$\langle$EW$_{\rm H\alpha}$$\rangle$    & Time-averaged H$\alpha$ line core                              &  7.2 $\pm$ 0.2   & 4 \\ 
+                                        & \hspace{3pt} equivalent width (\AA)	                           &                      \\
+\hline
+\end{tabular}
+\begin{flushleft}
+\footnotesize{ \textsc{NOTE}---
+Provenances are:
+1: SED fit \citep{Bouma2024}.
+2: Gaia DR3 photometry shows the star is on the pre-main sequence,
+   while the spectrum lacks lithium (Appendix~\ref{sec:stparams}).
+3: PARSEC v1.2S \citep{Chen2014}.
+4: Keck/HIRES (Appendix~\ref{subsec:halpha}).
+5: TESS light curve.
+6: Derived quantity.
+7: Gaia DR3 geometric \citep{GaiaDR3}.
+}
+\end{flushleft}
+\vspace{-0.5cm}
+\end{table}
 
@@
   \centering
-  \includegraphics[width=0.935\textwidth]{figures/sf1.pdf}
+  \includegraphics[width=0.925\textwidth]{figures/sf1.pdf}
   \vspace{-0.2cm}
@@
 \end{figure*}
-
-We observed with Keck during Sector~75 in an attempt to obtain
-simultaneous observations.   Figure~\ref{fig:fulllc} shows the result;
-Earth passed within 25$^\circ$ of the
-TESS camera's boresight from BTJD 3356.0-3358.5, which caused a data
-gap that ended twelve hours after our Keck/HIRES observations
-(green bar).  From
-BTJD 3359.4-3362.0, the Moon then passed within 25$^\circ$ of the
-camera's boresight.  Based on the level of scattered light in the
-optimal TIC\,141146667 aperture \citep{Jenkins2016}, we manually masked
-out data in the TESS light curve from 3359.40-3360.13; the remainder
-of the data during the lunar approach were usable.  Small gaps
-from BTJD 3353.55-3353.77 and 3360.12-3360.33 were caused by
-data downlinks at the spacecraft's perigee and apogee.
-
-While the data gap is unfortunate, Figure~\ref{fig:fulllc} shows
-that a large flux decrement spanned roughly half of each
-cycle both before and after the HIRES data were acquired.  From BTJD
-3352-3356, this dip had two sharp local minima;  the local minimum
-at $\phi$$\approx$0.8 disappeared following the flare at BTJD 3353,
-yielding a dip more closely resembling an asymmetric ``V'' than a ``W''.
-Similar CPV state changes have been previously noted 
-\citep{Stauffer2017,Bouma2024}.  The photometric shape therefore
-evolved during the twelve cycles spanning the 3356-3358 gap, since
-the average shape from 3358-3363 more closely resembles the initial
-``W''.  Nonetheless, the general photometric morphology---a small
-brightening over 45\% of the period, followed by a complex flux dip
-spanning 55\% of the period---is similar before and after the data
-gap.
-
-\section{Results}
-\label{sec:results}
 
@@
 
+We identified TIC\,141146667 in previous work \citep{Bouma2024} by
+searching TESS two-minute data from 2018-2022 for highly
+structured, periodic light curves \citep{Ricker2015}.  We chose the
+star for spectroscopy because its brightness and rapid rotation enabled
+an efficient search for variability in its line profiles.
+As an apparently single pre-main sequence M dwarf, its properties are
+typical for the CPV population (see Table~\ref{tab:params} and
+Appendix~\ref{sec:stparams}).
+
+We observed TIC\,141146667 ($V$=16.2) for five hours on
+17~February~2024 using the High Resolution Echelle Spectrometer
+(HIRES; \citealt{vogt_hires_1994}) on the 10\,m Keck I telescope.  The
+observations spanned the second half of the night, from 17 February
+2024 10:47 to 16:13 (UT).  The star's airmass spanned $z$=1.2-2.2, and
+we opted for a fixed 15 minute cadence, except for a final 10 minute
+exposure due to increasing sky brightness at sunrise.  We observed
+without the iodine cell and used the C2 decker
+(0$\farcs$86$\times$14$\farcs$0) in the red configuration, yielding a
+spectral resolution $R$$\approx$45{,}000 ($\delta
+v$$\approx$6.7\,\kms; $\delta v / v_{\rm eq}$$\approx$0.05).  We
+binned the CCD readout by a factor of three in the spatial dimension,
+yielding $\approx$1,000 photons (S/N=33) per pixel in the continuum at
+6500\,\AA, at minimum airmass.  Strong winds contributed to
+1$''$-1\farcs5 seeing over the night, but conditions were otherwise
+favorable.  We reduced the echelleogram to a one-dimensional spectrum
+using the standard techniques of the California Planet Survey
+\citep{Howard2010}.  
+%Figure~\ref{fig:spec} shows the result in the
+%vicinity of H$\alpha$ without any additional processing.
+
+TESS observed TIC\,141146667 ($T$=13.3) for six non-contiguous months
+spanning 2019-2024.  TESS acquired these observations at two-minute
+cadence during Sectors 41, 48 (TESS DDT039, PI: Kunimoto), and 75
+(TESS Program G06030, PI: Bouma).   The 30-minute data during Sectors
+14, 15, and 21 probably smeared sharp features over the star's 3.93\,hour
+period (see \citealt{Gunther2022}).  The movie in
+Figure~\ref{fig:lc} shows the two-minute data: 
+like other CPVs, TIC\,141146667 maintains a fixed period over
+timescales of years while its detailed photometric morphology evolves.
+The nearest known star, TIC\,141146666 ($T$=14.5), is 25$''$ from
+TIC\,141146667 and is photometrically stable in the TESS images;
+crowding is not a concern.
+
+We observed with Keck during Sector~75 in an attempt to obtain
+simultaneous observations.   Figure~\ref{fig:fulllc} shows the result;
+Earth passed within 25$^\circ$ of the TESS camera's boresight from BTJD
+3356.0-3358.5, which caused a data gap that ended twelve hours after our
+Keck/HIRES observations (green bar).  From BTJD 3359.4-3362.0, the Moon
+then passed within 25$^\circ$ of the camera's boresight.  Based on the
+level of scattered light in the optimal TIC\,141146667 aperture
+\citep{Jenkins2016}, we manually masked out data in the TESS light curve
+from 3359.40-3360.13; the remainder of the data during the lunar
+approach were usable.  Small gaps from BTJD 3353.55-3353.77 and
+3360.12-3360.33 were caused by data downlinks at the spacecraft's
+perigee and apogee.
+
+Although the data gap is unfortunate, Figure~\ref{fig:fulllc} shows that
+both before and after the HIRES data were acquired, a large flux
+decrement spanned roughly half of each cycle.  From BTJD 3352-3356, this
+dip had two sharp local minima;  the minimum at $\phi$$\approx$0.8
+decreased in depth following the flare at BTJD 3353, yielding a dip more
+closely resembling an asymmetric ``V'' than a ``W''.  Similar CPV state
+changes have been previously noted \citep{Stauffer2017,Bouma2024}.  The
+photometric shape therefore evolved during the twelve cycles spanning
+the 3356-3358 gap, since the average shape from 3358-3363 more closely
+resembles the initial ``W''.  Nonetheless, the general photometric
+morphology---a small brightening over 45\% of the period, followed by a
+complex flux dip spanning 55\% of the period---is similar before and
+after the data gap.
+
+\section{Results}
+\label{sec:results}
+
 Figure~\ref{fig:spec} compiles the TESS and HIRES data from February
@@
 equatorial velocity, $v_{\rm eq}$, of 130\,\kms.  There are at least
-two distinct emission components, separated by half a cycle in phase.
+two distinct emission components, separated by 180$^\circ$ in phase.
 The inner component at lower velocities has clearer sinusoidal
@@
 observed sinusoidal periods and velocities, this material's motion is
-not controlled by gravitational attraction to the star; it is more
-readily explained as plasma being dragged along
-with a rigidly rotating stellar magnetic field.  The velocity
-semi-amplitude of the sinusoids gives the mean distance of each clump
-from the stellar surface: 2.07\,$R_\star$ and 2.88\,$R_\star$ for the
-inner clumps, and 3.88\,$R_\star$ for the outer clump.   These clumps
-transit in front of the star when passing from negative to positive
-velocity.  The transits of the two inner clumps last $\approx$22\% of
-each cycle, from $\phi$=-0.1 to $\phi$=+0.12 (see
-Appendix~\ref{subsec:halpha}).  This spectroscopic transit coincides with
-the latter half of the complex eclipse feature in the TESS data.
+not controlled by gravitational attraction to the star; it is 
+a plasma being dragged along with a rigidly rotating stellar magnetic
+field.  The velocity semi-amplitude of the sinusoids gives the mean
+distance of each clump from the stellar surface: 2.07\,$R_\star$ and
+2.88\,$R_\star$ for the inner clumps, and 3.88\,$R_\star$ for the outer
+clump.   These clumps transit in front of the star when passing from
+negative to positive velocity.  The transits of the two inner clumps
+last $\approx$22\% of each cycle, from $\phi$=-0.1 to $\phi$=+0.12 (see
+Appendix~\ref{subsec:halpha}).  This spectroscopic transit coincides
+with the latter half of the complex eclipse feature in the TESS data.
 
@@
 absorptive component to the circumstellar material which is not
-visible in emission.  Although the origin of the other bright and dark
+visible in emission.  While the origin of the other bright and dark
 streaks passing across the line core are similarly ambiguous, a final
@@
 
-\begin{table}
-\small
-\setlength{\tabcolsep}{2pt}
-\centering
-\caption{Selected system parameters for TIC\,141146667}
-\label{tab:params}
-\begin{tabular}{llcc}
-\hline \hline
-Parameter & Description & Value & Source\\
-\hline 
-%
-$T_{\rm eff}$\dotfill                   & Effective Temperature (K) \hspace{9pt}\dotfill                 & 2972 $\pm$ 40    & 1 \\
-%
-$R_\star$\dotfill                       & Stellar radius ($R_\odot$)\dotfill                             & 0.42$\pm$0.02    & 1 \\
-%
-Age                                     & Stellar age range (Myr)\dotfill                                & 35-150           & 2 \\
-%
-$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & 0.22$\pm$0.02    & 3 \\
-%
-$\gamma$\dotfill                        & Systemic radial velocity (\kms)\dotfill                        & 0.61 $\pm$ 1.47  & 4 \\
-%
-SpT\dotfill                             & Spectral Type\dotfill                                          & M5.5Ve           & 4 \\
-%
-$P_{\rm rot}$\dotfill                   & Photometric rotation period (hr)\dotfill                       & $3.930\pm 0.001$ & 5 \\
-%
-$v_{\rm eq}$\dotfill		                & Equatorial velocity \dotfill                                   &  130$\pm$4       & 6 \\
-                                        & \hspace{3pt} ($2\pi R_\star/P_{\rm rot}$) (\kms)	             &                      \\
-%
-$v_{\rm eq}\sin{i_\star}$\dotfill		    & Projected rotational\dotfill                                   &  138$\pm$8       & 4 \\
-                                        & \hspace{3pt} velocity (\kms)	                                 &                      \\
-%
-$v_{\rm break}$\dotfill		              & Breakup velocity \dotfill                                      &  316$\pm$16      & 6 \\
-                                        & \hspace{3pt} ($G M_\star / R_\star$)$^{1/2}$ (\kms)	           &                      \\
-%
-$i_\star$\dotfill                       & Stellar inclination\dotfill                                    & 	$>$63           & 4 \\
-                                        & \hspace{3pt}  2$\sigma$ lower limit (deg)	                     &                      \\
-%
-$d$\dotfill                             & Distance (pc)\dotfill                                          & $57.54 \pm 0.09$ & 7 \\
-%
-$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   & $1.82 \pm 0.10$  & 6 \\
-                                        & \hspace{3pt} radius ($R_\star$)	                               &                      \\
-%
-$a_0$\dotfill                           & Mean inner clump (0)\hspace{9pt}\dotfill           &  2.07$\pm$0.04   & 4 \\
-                                        & \hspace{3pt} orbital radius ($R_\star$)	                       &                      \\
-%
-$a_1$\dotfill                           & Mean inner clump (1)\hspace{9pt}\dotfill           &  2.88$\pm$0.10   & 4 \\
-                                        & \hspace{3pt} orbital radius ($R_\star$)	                       &                      \\
-%
-$a_2$\dotfill                           & Mean outer clump\hspace{9pt}\dotfill           &  3.88$\pm$0.25   & 4 \\
-                                        & \hspace{3pt} orbital radius ($R_\star$)	                       &                      \\
-%
-$\langle$EW$_{\rm H\alpha}$$\rangle$    & Time-averaged H$\alpha$ line core                              &  7.2 $\pm$ 0.2   & 4 \\ 
-                                        & \hspace{3pt} equivalent width (\AA)	                           &                      \\
-\hline
-\end{tabular}
-\begin{flushleft}
-\footnotesize{ \textsc{NOTE}---
-Provenances are:
-1: SED fit \citep{Bouma2024}.
-2: Gaia DR3 photometry shows the star is on the pre-main sequence,
-   while the spectrum lacks lithium (see \S~\ref{sec:stparams}).
-3: PARSEC v1.2S \citep{Chen2014}.
-4: Keck/HIRES (see \S~\ref{subsec:halpha}).
-5: TESS light curve.
-6: Derived quantity.
-7: Gaia DR3 geometric \citep{GaiaDR3}.
-}
-\end{flushleft}
-\vspace{-0.5cm}
-\end{table}
-
 \section{Discussion}
@@
 
-\subsection{Corotating Plasma Clumps}
+\subsection{Physical Properties of the Emitting Region}
+
+% What can be inferred with confidence?
 
@@
 of a CPV, and they demonstrate that corotating circumstellar plasma
-clumps exist around at least one such star.  While starspots do
-contribute smooth signals to the photometric variability, a
-``starspot-only'' scenario to explain the complexity of the CPVs
-\citep{Koen2021} is incompatible with our observations.  Scenarios in
-which the circumstellar material is made only of dust are similarly
-ruled out.  While starspots and dust may both be present, our HIRES
-spectra require plasma with a significant population of hydrogen atoms
-in the $n$=3 excited state, with no evidence for significant
-higher-order excitations (see Appendix~\ref{subsec:specvar}).  Most of
-this H$\alpha$ emission originates in ``clumps'' with size similar to
-that of the star; radial ``spokes'' or azimuthally-extended ``arcs''
-for the emitting material are ruled out by the observed H$\alpha$
-velocity dispersion (see Appendix~\ref{subsec:halpha}).  The observed
-H$\alpha$ luminosity suggests characteristic densities and masses for
-the gaseous component of these clumps of $n_{\rm H} \sim
-10^{11}$\,cm$^{-3}$ and $M_{\rm gas} \sim 10^{17}$\,g (see
-Appendix~\ref{subsec:gas}).  Dust, if present, is independently
-constrained to have a total mass $10^{15}\,{\rm g} < M_{\rm dust} <
-10^{17}\,{\rm g}$ (see Appendix~\ref{subsec:dust}).
-
-%TODO: improve heading?
-\subsection{Plasma Tori Could Explain Complex Periodic Variables}
-
-While the H$\alpha$ emission appears consistent with clumps, the
-photometric width of the complex flux dips in TIC\,141146667
-specifically, and CPVs more broadly \citep[Figure~4 of][]{Bouma2024},
-raise the possibility that azimuthally-distributed material may be the
-norm for these objects.  In other words, a torus may be a more
-accurate picture than a clump.
-
-\citet{Townsend2005} outline the physics of how such structures can
-exist: for stars with magnetospheric radii $R_{\rm m}$ that exceed
-their corotation radii $R_{\rm c}$, the effective potential
-experienced by a charged particle can have a local minimum outside
-$R_{\rm c}$, enabling material to accumulate in a
-centrifugally-supported magnetosphere
-\citep{Petit2013,Daley-Yates2024}.  Generally speaking, such material
-need neither transit nor be opaque in broadband optical light.  In
-fact, Figure~\ref{fig:spec} suggests that the transits of the
-H$\alpha$ emitting material cannot explain the entirety of the complex
-photometric modulation;  the spectroscopic transits happen too fast,
-and at orbital phases that only partially overlap with the photometric
-modulations.
-
-Nonetheless, \citet{Townsend2008} synthesized light curves for plasma
-trapped in rigidly rotating magnetospheres of rapidly rotating stars;
-and found that assuming a dipole magnetic geometry, one can obtain
-W-shaped eclipses similar to those seen for TIC\,141146667.  See in
-particular the
-\href{http://user.astro.wisc.edu/~townsend/static.php?ref=rrm-movies#Download_Bundles}{movies}
-associated with their work; for a $\omega/\omega_{\rm c}$$\approx$0.5,
-edge-on system like TIC\,141146667, the eclipses have the correct
-approximate shape, and the H$\alpha$ emission can similarly exhibit
-double-peaked behavior.
-
-\subsection{Origin of Circumstellar Material and Astrophysical Analogs}
-
-The circumstellar material could originate either from the star or
-from an external source.  Plausible external sources include an
-undetected old disk, comets, or a close-in exoplanet.  This latter
-scenario would make CPVs extrasolar analogs of the Jupiter-Io plasma
-torus (e.g.~\citealt{Bagenal1981}), although with a very different
-composition.
-
-The other potential analog for the CPVs are the $\sigma$~Ori~E
-variables, a rare subset of B stars with radiatively-driven winds
-which accumulate into warped plasma tori
-\citep{Townsend2005,Townsend2008}.  These tori tend to have dense
-antipodal accumulations of plasma sculpted by tilted-dipole magnetic
-fields, and the transits of these clumps produce broadband photometric
-variability through bound-free scattering \citep{Townsend2005} and
-Thomson scattering \citep{Berry2022}.  The plasma accumulates at
-antipodes 180$^\circ$ apart because the deepest local minima in the
+clumps exist around at least one such star.  More specifically, the
+spectra require plasma with a significant population of hydrogen in the
+$n$=3 excited state, with minimal evidence for higher-order excitations
+(see Appendix~\ref{subsec:specvar}).  Most of this H$\alpha$ emission
+originates in ``clumps'' with size comparable to the star; radial
+``spokes'' or azimuthally-extended ``arcs'' for the emitting material
+are ruled out by the $\approx$30\,\kms\ H$\alpha$ velocity dispersion
+(see Appendix~\ref{subsec:halpha}).  The H$\alpha$ line luminosity
+suggests characteristic number densities and masses for the gaseous
+component of these clumps of $n_{\rm H} \sim 10^{11}$\,cm$^{-3}$ and
+$M_{\rm gas} \sim 10^{17}$\,g (see Appendix~\ref{subsec:gas}).  Dust is
+independently constrained to have a total mass $M_{\rm dust} <
+10^{17}\,{\rm g}$ based on the lack of a WISE infrared excess; if one
+assumes that the opacity in the TESS flux dips comes from dust, a lower
+limit $M_{\rm dust} > 10^{15}\,{\rm g}$ follows (see
+Appendix~\ref{subsec:dust}).
+
+\subsection{Clumps Within Warped Plasma Torii}
+
+While the H$\alpha$ emission seems to mostly originate from clumps, the
+complex flux dip in TIC\,141146667 spans roughly half of each cycle; in
+CPVs more broadly, individual dips can last 5-50\% of each cycle, and
+they are often distributed in longitude \citep{Bouma2024}.  This raises
+the possibility that azimuthally-distributed material may be the norm
+for CPVs, and that a warped torus may be a more accurate picture than a
+clump.
+
+\citet{Townsend2005} outlined the physics of how rapidly-rotating stars
+with strong magnetic fields can support plasma tori.  When the
+magnetospheric radii $R_{\rm m}$ of such stars exceeds their Keplerian
+corotation radii $R_{\rm c}$, the effective potential experienced by
+charged particles has a local minimum outside $R_{\rm c}$, which enables
+charged material to accumulate in a torus
+\citep{Petit2013,Daley-Yates2024}.  Warps can occur when there is
+misalignment between the spin and magnetic axes.  In general, the
+material in these centrifugally-supported magnetospheres need neither
+transit nor be opaque in broadband optical light.
+
+In a follow-up study, \citet{Townsend2008} synthesized light curves for
+these systems, assuming that the optical depth scaled linearly with
+density.  They found that W-shaped eclipses, similar to those seen for
+TIC\,141146667, can occur when the spin and magnetic axes are moderately
+(15-45$^\circ$) misaligned.  The movies associated with their work are
+available
+online\footnote{\url{http://user.astro.wisc.edu/\~townsend/static.php?ref=rrm-movies\#Download\_Bundles}
+last accessed 23 April 2025.}; for a $\omega/\omega_{\rm
+c}$$\approx$0.5, edge-on system like TIC\,141146667, the photometric
+eclipses have the correct shape, and the H$\alpha$ emission similarly
+exhibits double-peaked behavior.  The plasma in this model accumulates
+at antipodes 180$^\circ$ apart because the deepest local minima in the
 effective potential exist along the line of intersection between the
 rotational and magnetic planes (see Equation~22 of
-\citealt{Townsend2005}).  For $\sigma$~Ori~E and almost all of its
-analogs, the result is ``simple'' light curves that resemble those of
-eclipsing binaries, and time-dynamic H$\alpha$ spectra similar to
-those in Figure~\ref{fig:spec} \citep{Townsend2005,Townsend2008}.  The
-two known exceptions, HD~37776 and HD~64740, show complex light curves
+\citealt{Townsend2005}).
+
+To summarize, the lines of evidence in favor of warped plasma tori for
+TIC\,141146667 and CPVs more generally are that {\it i)}
+Figure~\ref{fig:spec} shows two emitting plasma clumps separated
+180$^\circ$ in phase, with double-peaked H$\alpha$ morphology at
+quadrature; {\it ii)} the ``W'' shaped photometric eclipses are
+predictions of such a model; {\it iii)} CPV dips last 5-50\% of each
+cycle, suggesting an extended azimuthal distribution of circumstellar
+material.
+
+\subsection{Origin of CPV Photometric Variability and Astrophysical Analogs}
+
+Microphysically, it is not obvious whether hydrogen alone can produce
+the broadband chromatic flux variations seen in CPVs.  The
+alternative idea is that charged dust could provide most of the
+opacity \citep{Sanderson2023}.  For
+TIC\,141146667, Figures~\ref{fig:fulllc}
+and~\ref{fig:spec} show that the transits of the H$\alpha$ emitting
+material only partially overlap the complex photometric modulation.
+This implies that some of the complex photometric dips must involve
+additional opacity sources or spatially distinct structures.
+
+Independent of this opacity question, our observations show that
+corotating clumps of cool plasma exist around a CPV.  While starspots do
+contribute smooth signals to CPV photometric variability, the existence
+of these clumps  would not be predicted by a ``starspot-only'' scenario
+\citep{Koen2021}.  Scenarios in which the circumstellar material is made
+only of dust are similarly ruled out.
+
+The circumstellar material -- either pure plasma or dusty plasma --
+could originate either from the star or from an external source.
+Plausible external sources include an undetected old disk, comets, or a
+close-in exoplanet.  This latter scenario would make CPVs extrasolar
+analogs of the Jupiter-Io torus (e.g.~\citealt{Bagenal1981}),
+although with a very different composition.
+
+The other analog for the CPVs are the $\sigma$~Ori~E variables, a rare
+subset of B stars with radiatively-driven winds which accumulate into
+warped plasma tori \citep{Townsend2005,Townsend2008}.  These tori tend
+to have dense antipodal accumulations of plasma sculpted by
+tilted-dipole magnetic fields, and the transits of these clumps produce
+broadband photometric variability through bound-free scattering
+\citep{Townsend2005} and Thomson scattering \citep{Berry2022}.  For
+$\sigma$~Ori~E and almost all of its analogs, the result is simple
+light curves that resemble those of eclipsing binaries, and time-dynamic
+H$\alpha$ spectra similar to those in Figure~\ref{fig:spec}.  The two
+known exceptions, HD~37776 and HD~64740, show complex light curves
 resembling CPVs \citep{Mikulasek2020,Bouma2024} and have
-spectropolarimetric magnetic field maps indicating strong
-contributions from higher-order magnetic moments
-\citep{Kochukhov2011,Shultz2018}.  There are two implications: first,
-the photometric complexity of CPVs may be a direct consequence of
-magnetic fields with highly multipolar contributions.  Second, despite
-this complexity, the observation (Figure~\ref{fig:spec}) of two
-emission clumps separated 180$^\circ$ in phase is consistent with the
-expected emission from a warped plasma torus.
+spectropolarimetric magnetic field maps indicating strong contributions
+from higher-order magnetic moments \citep{Kochukhov2011,Shultz2018}.
+The main implication is that the photometric complexity of CPVs may be a
+direct consequence of magnetic fields with highly multipolar
+contributions.
 
@@
 
-Spectra of magnetically-active, rapidly rotating stars with a wide
-range of masses have been previously observed to exhibit 
-sinusoidal time-varying Balmer emission
+Spectra of magnetically-active, rapidly rotating stars with a wide range
+of masses have been previously observed to exhibit sinusoidal
+time-varying Balmer emission
 \citep{Donati2000,Townsend2005,Dunstone2006,Skelly2008}, similar to 
-that Figure~\ref{fig:spec}.  No such stars were previously known to show
+Figure~\ref{fig:spec}.  No such stars were previously known to show
 complex light curves \citep{Bouma2024}.   One interpretation for the
-spectroscopic variability of these stars, and that of the analogous transient
-absorption features
+spectroscopic variability of these stars, and that of the analogous
+transient absorption features
 \citep{CollierCameron1989,CollierCameron1992,Cang2020}, comes from an
-analogy to quiescent solar prominences, cool condensations of plasma
-in the solar corona that can last days to weeks
-\citep{VialEngvold2015}.  In the case of the Sun, these condensations
-fall back to the photosphere because gravity is stronger than any
-magnetic tension or centrifugal force capable of sustaining them.  
-However it has been understood at least since work by
-\citet{Donati2000} that these ``prominence systems'' can be
-longitudinally extended, forming a trapped ring of plasma.
-While the question of why these previously known spectroscopic
-variables do not show complex photometric variability remains open,
-a possible explanation is that they are not in the required transiting
-geometry.
-What we have in the case of TIC\,141146667 is a system that finally
-exhibits both sets of phenomena.
+analogy to quiescent solar prominences, cool condensations of plasma in
+the solar corona that can last days to weeks \citep{VialEngvold2015}.
+In the case of the Sun, these condensations fall back to the photosphere
+because gravity is stronger than any magnetic tension or centrifugal
+force capable of sustaining them.  However it has been understood at
+least since work by \citet{Donati2000} that these ``prominence systems''
+can be longitudinally extended, forming a trapped ring of plasma.  While
+the issue of why these previously known spectroscopic variables do
+not show complex photometric variability remains open, plausible
+explanations include that they are not in the required transiting
+geometry, or that they lack the necessary source of opacity.  What we
+have in the case of TIC\,141146667 is a system that finally exhibits
+both sets of phenomena.
 
@@
 
-Pressing issues for future work include determining the composition
-and origin of the circumstellar material, understanding the exact role
-of the stellar magnetic field, and exploring the implied space weather
-experienced by the close-in rocky exoplanets that, statistically
-\citep{Dressing2015}, are likely to be present in most CPV systems.
-
-The material's composition -- either pure plasma or dusty plasma --
-can be clarified by time-series optical and infrared
-spectrophotometry.  While observations of CPVs in the optical suggest
-a chromaticity consistent with dust
-\citep{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such
-as electron scattering in a plasma transiting over a spotted
-background star might also produce chromatic features
+Pressing issues include determining the composition and origin of the
+circumstellar material, understanding the exact role of the stellar
+magnetic field, and exploring the implied space weather experienced by
+the close-in rocky exoplanets that, statistically \citep{Dressing2015},
+are likely to be present in most CPV systems.
+
+The material's composition -- either pure plasma or dusty plasma -- can
+be clarified by time-series optical and infrared spectrophotometry.
+While observations of CPVs in the optical suggest a chromaticity
+consistent with dust \citep{Tanimoto2020,Gunther2022,Koen2023}, a gray
+opacity source such as electron scattering in a plasma transiting over a
+spotted background star might also produce chromatic features
 \citep{Rackham2018}.  The composition and size distribution of any dust
@@
 dwarfs \citep{Reach2009} would suggest an extrinsic origin channel.
-Compositions and sizes similar to the interstellar medium would
-suggest that dust can condense out from M dwarf winds, similar to
-processes that occur around more evolved stars \citep{Marigo2008}.
-
-The role of the star's magnetic field could be better understood
-through new observations, and new theory.  From the theoretical
-perspective, there is an urgent need for rigid-field
-magnetohydrodynamic modeling to go beyond previous work
-\citep{Townsend2005,Townsend2008,Krticka2022} and to explore what field
-topologies might explain the observed light curve morphologies
-\citep{Bouma2024}.  In particular, dynamo simulations of
+Compositions and sizes similar to the interstellar medium would suggest
+that dust can condense out from M dwarf winds, similar to processes that
+occur around more evolved stars \citep{Marigo2008}.
+
+The role of the star's magnetic field could be better understood through
+new observations, and new theory.  From the modeling perspective,
+there is an urgent need for rigid-field magnetohydrodynamic models to
+go beyond previous work \citep{Townsend2005,Townsend2008,Krticka2022}
+and to explore what field topologies might explain the observed light
+curve morphologies.  In particular, dynamo simulations of
 fully-convective M dwarfs have suggested that global-scale mean fields
@@
 Detecting radio emission produced by an electron cyclotron maser
-instability (e.g.~\citealt{Callingham2021}) in particular would provide a
-measurement of the field strength at the site of the emitting region,
+instability (e.g.~\citealt{Callingham2021}) in particular would provide
+a measurement of the field strength at the site of the emitting region,
 further clarifying the magnetosphere's structure.
@@
 material transit the star.  The suggested geometric correction implies
-that an appreciable minority (10-30\%) of young M dwarfs -- the
+that an appreciable minority ($\gtrsim$10\%) of young M dwarfs -- the
 rapidly rotating ones with centrifugal magnetospheres -- host
@@
 stars.
+
+\begin{acknowledgements}
+  We thank M.~Jardine, A.~Weinberger, B.~Tofflemire,
+  J.~Spake, J.~Winn, and L.~Hillenbrand for insightful conversations
+  that significantly informed this work, and to A.~Howard and
+  H.~Isaacson for their assistance reducing the HIRES spectra.
+
+  This work was supported by the Carnegie Fellowship and by the
+  Heising-Simons 51~Pegasi~b Fellowship.
+  %
+  Funding for the TESS mission is provided by NASA’s Science Mission
+  directorate.
+  TESS is a product of millions of hours of work by thousands of people;
+  we thank the TESS team for their efforts to make the mission a
+  continued success.
+  The HIRES data were obtained at the Keck Observatory, which exists
+  through a similar scale of community effort.
+  We recognize the importance that the summit of Maunakea has always had
+  within the indigenous Hawaiian community, and we are deeply grateful 
+  for the opportunity to conduct observations from this mountain.
+\end{acknowledgements}
+
+\facilities{
+  Gaia \citep{GaiaDR3},
+  TESS \citep{Ricker2015},
+  Keck:I (HIRES) \citep{vogt_hires_1994},
+	2MASS \citep{Skrutskie2006},
+	SDSS \citep{2000AJ....120.1579Y}.
+}
+
+\software{
+  astropy \citep{astropy:2013,astropy:2018,astropy:2022},
+  matplotlib \citep{matplotlib},
+  numpy \citep{numpy},
+  scipy \citep{scipy}.
+}
 
@@
 \begin{figure}[!t]
-  \centering
-  \includegraphics[width=0.48\textwidth]{figures/sf3.pdf}
-  \caption{Dereddened Gaia DR3 color vs.~absolute magnitude diagram of
+	\begin{center}
+		\subfloat{
+			\includegraphics[width=0.47\textwidth]{figures/sf3.pdf}
+		}
+		\subfloat{
+			\includegraphics[width=0.47\textwidth]{figures/sf2.pdf}
+		}
+	\end{center}
+	\vspace{0.0cm}
+  \caption{{\bf TIC\,141146667 age diagnostics.}
+  {\it Left:} Dereddened Gaia DR3 color vs.~absolute magnitude diagram of
   TIC\,141146667 and comparison samples. 
@@
   fainter.  The star's location in this diagram suggests an
-  age of 30-150\,Myr.  }
-  \label{fig:camd}
+  age of 30-150\,Myr. 
+  {\it Right:} An upper limit on photospheric lithium for TIC\,141146667
+  (green triangle) yields a lower bound on the star's age of
+  $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
+  \citep{Jeffries2023}; rich clusters in each age bin include NGC\,2264
+  (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
+  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2602 and IC\,2391 (42.0\,Myr),
+  and NGC\,2451A (50.0\,Myr). }
+  \label{fig:age_diagnostics}
 \end{figure}
+
+%  \label{fig:camd}
+%  \label{fig:liew_population}
+%\begin{figure}[!t]
+%  \centering
+%  \includegraphics[width=0.48\textwidth]{figures/sf2.pdf}
+%  \caption{}
+%\end{figure}
 
@@
 ($b$=$+$53$^\circ$) yield negligible interstellar reddening along the
-line of sight \citep{Green2019}.  Figure~\ref{fig:camd}
+line of sight \citep{Green2019}.  Figure~\ref{fig:age_diagnostics}
 shows the location of TIC\,141146667 in the color--absolute magnitude
@@
 
-Figure~\ref{fig:camd} shows that TIC\,141146667 falls
+Figure~\ref{fig:age_diagnostics} shows that TIC\,141146667 falls
 between the USco and Pleiades sequences, and approximately overlaps
@@
 
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=0.48\textwidth]{figures/sf2.pdf}
-  \caption{An upper limit on photospheric lithium for TIC\,141146667
-  (green triangle) yields a lower bound on the star's age of
-  $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
-  \citep{Jeffries2023}; rich clusters in each age bin include NGC\,2264
-  (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
-  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2602 and IC\,2391 (42.0\,Myr),
-  and NGC\,2451A (50.0\,Myr). }
-  \label{fig:liew_population}
-\end{figure}
-
 Despite ambiguity in the details, what can be stated with
 confidence is that lithium is not abundant in the spectrum of
-TIC\,141146667.  Figure~\ref{fig:liew_population}
+TIC\,141146667.  Figure~\ref{fig:age_diagnostics}
 compares our upper limit against the equivalent width measurements
@@
   middle columns, leaving variability in the line core.
-  \S~\ref{subsec:halpha} discusses the use of this model.  }
+  Appendix~\ref{subsec:halpha} discusses the use of this model.  }
   \label{fig:halphamodel}
@@
 
-To implement the model, we assumed that the ``inner'' ($K_{\rm
+To implement this model, we assumed that the ``inner'' ($K_{\rm
 inner}$$\approx$2.5\,$v_{\rm eq}$) clump would be well-fit by a sum of
@@
 
-Caution is required in interpreting this model's results.  At certain
-epochs the most significant spectral feature around any component's
-prior is not statistically significant.  During such epochs, e.g.~the
+Caution is required in interpreting this model's results.  At some
+epochs there are no significant spectral features around any component's
+prior.  During such epochs, e.g.~the
 ``outer'' clump at $\phi$=1.07, the model fits noise, not signal.  At
@@
   from mean model fits in Panel a, assuming a constant emission
-  amplitude and velocity width $\sigma$=0.25\,$v_{\rm eq}$ over the
-  observation sequence.}
+  amplitude and velocity width $\sigma$=0.25\,$v_{\rm eq}$ and
+  neglecting eclipses.}
   \label{fig:orbits}
@@
 Figure~\ref{fig:hirescuts} shows a few regions of
-interest in the HIRES spectra, which cover 3650-7960\,\AA.  Higher
-order Balmer lines including H$\gamma$ and H$\delta$
+interest in the HIRES spectra, which cover 3650-7960\,\AA.  
+H$\beta$ falls in an inter-order gap and was not observed.
+Higher order Balmer lines including H$\gamma$ and H$\delta$
 ($n=5\rightarrow2$ and $n=6\rightarrow2$) do show variability outside
-the line core.  However, this variability is not clearly periodic in
-the same manner as the emission seen in H$\alpha$.  This could be
-because there are insufficient hydrogen ions in the relevant excited
-states, or because the spectra have lower precision in these bluer
-regions.  The Ca HK doublet is also detected in emission, while the
-continuum near it is not.  Chromospheric emission from the magnesium
-triplet is also detected, but these lines are too blended to be
-usable.
+the line core.  However, this variability is not clearly periodic in the
+same manner as the emission seen in H$\alpha$.  This could be because
+there are insufficient hydrogen ions in the relevant excited states, or
+because the spectra have lower precision in these bluer regions.  The Ca
+HK doublet is also detected in emission, while the continuum near it is
+not.  Chromospheric emission from the magnesium triplet is also
+detected, but these lines are too blended to be usable.
 
@@
 range of $10^{15}$-$10^{17}$\,g.  Given $M_{\rm
-gas}$$\approx$2$\times$10$^{17}$\,g from \S~\ref{subsec:gas}, the
+gas}$$\approx$2$\times$10$^{17}$\,g from Appendix~\ref{subsec:gas}, the
 allowed dust masses imply $M_{\rm gas}/M_{\rm dust}$ ranges of 1-100.
@@
     \hline
-    $T_{\rm eff}$ (K) & 2972 $\pm$ 40 & SED fit \citep{Bouma2024} \\
-    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & SED fit \citep{Bouma2024} \\
-    $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & SED fit \citep{Bouma2024} \\
+    $T_{\rm eff}$ (K) & 2972 $\pm$ 40 & SED fit \\
+    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & SED fit  \\
+    $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & SED fit \\
     $P_{\rm rot}$ (hours) & 3.930 $\pm$ 0.001 & TESS \\ 
@@
   \caption{Best-fit parameters from multi-gaussian model fit to H$\alpha$ line
-  profiles.  These results should be treated with caution; only a
+  profiles.  Units for $\mu_i$ and $\sigma_i$ are $v_{\rm eq}$
+  (130\,\kms). These results should be treated with caution; only a
   subset of the spectral epochs yielded statistically significant
@@
 
-\begin{acknowledgements}
-  We thank M.~Jardine, A.~Weinberger, B.~Tofflemire,
-  J.~Spake, J.~Winn, and L.~Hillenbrand for insightful conversations
-  that significantly informed this work, and to A.~Howard and
-  H.~Isaacson for their assistance reducing the HIRES spectra.
-  This work was supported by the Carnegie Fellowship and by the
-  Heising-Simons 51~Pegasi~b Fellowship.
-  %
-  Funding for the TESS mission is provided by NASA’s Science Mission
-  directorate.
-  TESS is a product of millions of hours of work by thousands of people;
-  we thank the TESS team for their efforts to make the mission a
-  continued success.
-  The HIRES data were obtained at the Keck Observatory, which exists
-  through a similar scale of community effort.
-  We recognize the importance that the summit of Maunakea has always had
-  within the indigenous Hawaiian community, and we are deeply grateful 
-  for the opportunity to conduct observations from this mountain.
-\end{acknowledgements}
-
-\facilities{
-  Gaia \citep{GaiaDR3},
-  TESS \citep{Ricker2015},
-  Keck:I (HIRES) \citep{vogt_hires_1994},
-	2MASS \citep{Skrutskie2006},
-	SDSS \citep{2000AJ....120.1579Y}.
-}
-
-\software{
-  astropy \citep{astropy:2013,astropy:2018,astropy:2022},
-  matplotlib \citep{matplotlib},
-  numpy \citep{numpy},
-  scipy \citep{scipy}.
-}
-
 \end{document}

### 2025-04-23 paper/ms.tex
update

@@
 from higher-order magnetic moments \citep{Kochukhov2011,Shultz2018}.
-The main implication is that the photometric complexity of CPVs may be a
-direct consequence of magnetic fields with highly multipolar
-contributions.
+This suggests that the photometric complexity of CPVs may be related to
+magnetic fields with highly multipolar contributions.
 
@@
 new observations, and new theory.  From the modeling perspective,
-there is an urgent need for rigid-field magnetohydrodynamic models to
+there is a need for rigid-field magnetohydrodynamic models to
 go beyond previous work \citep{Townsend2005,Townsend2008,Krticka2022}
-and to explore what field topologies might explain the observed light
-curve morphologies.  In particular, dynamo simulations of
+and to explore what field topologies explain the observed light
+curve shapes.  In particular, dynamo simulations of
 fully-convective M dwarfs have suggested that global-scale mean fields
@@
 a measurement of the field strength at the site of the emitting region,
-further clarifying the magnetosphere's structure.
+which could help clarify the magnetosphere's structure.
 
@@
 observations, along with magnetohydrodynamic modeling, will be key to
-understanding the complex magnetospheric environments of these young
+understanding the complex environments of these young
 stars.
@@
   \caption{
-    Spectral energy distribution of broadband photometric magnitudes
+    {\bf Spectral energy distribution} of broadband photometric magnitudes
     (filled markers) plotted over the best-fit BT-Settl stellar
@@
   \centering
-  \includegraphics[width=0.55\textwidth]{figures/sf6.pdf}
-  \caption{Time-variable fit to H$\alpha$ line profiles.  {\it Left
+  \includegraphics[width=0.5\textwidth]{figures/sf6.pdf}
+  \caption{{\bf Time-variable fit to H$\alpha$ line profiles.}  {\it Left
   column:} Raw spectrum at each epoch $f_{\lambda}$ minus the
@@
   \includegraphics[width=\textwidth]{figures/sf5.pdf}
-  \caption{Time evolution of select regions in the Keck/HIRES spectra
-  from 17 February 2024.  We made this plot by applying a windowed
+  \vspace{-0.25cm}
+  \caption{{\bf Time evolution of the Keck/HIRES spectra
+  from 17 February 2024.}  We made this plot by applying a windowed
   outlier rejection to remove cosmic rays and then smoothing each
@@
   stellar equatorial velocity.  H$\alpha$ is the only Balmer line to
-  show periodic variability of the form seen in Figure~\ref{fig:spec}.
-  The He 5876\,\AA\ line shows a time-dynamic blueshift that differs
-  from the Balmer lines.  Li 6708\,\AA\ shows no obvious absorption. }
+  show periodic variability similar to Figure~\ref{fig:spec}.
+	The He 5876\,\AA\ line shows a time-dynamic blueshift.  Li 6708\,\AA\ shows
+	no obvious absorption. }
   \label{fig:hirescuts}
@@
 might be connected to such a sudden rise.  However, this idea seems
-incompatible with the sinusoidal emission seen later from
-$\phi$$\approx$0.5-1.0, and with the fact that flares typically excite
+incompatible with the sinusoidal emission seen from
+$\phi$$\approx$0.3-1.0, and with the fact that flares typically excite
 iron lines in the blue HIRES orders, which are not observed.  More
@@
 variability, in particular whether it is periodic or stochastic.
+The gap in the TESS photometry (Figure~\ref{fig:fulllc}) additionally
+clouds the interpretability of this event.
 

### 2025-04-23 paper/ms.tex
update

@@
 		\subfloat{
-			\includegraphics[width=0.47\textwidth]{figures/sf3.pdf}
+			\includegraphics[width=0.46\textwidth]{figures/sf3.pdf}
 		}
@@
 	\end{center}
-	\vspace{0.0cm}
+	\vspace{-0.3cm}
   \caption{{\bf TIC\,141146667 age diagnostics.}
-  {\it Left:} Dereddened Gaia DR3 color vs.~absolute magnitude diagram of
-  TIC\,141146667 and comparison samples. 
-  TIC\,141146667 is on the pre-main sequence; stars with the same color
-  on the main sequence are $\approx$1.5\,magnitudes
-  fainter.  The star's location in this diagram suggests an
-  age of 30-150\,Myr. 
-  {\it Right:} An upper limit on photospheric lithium for TIC\,141146667
+  {\bf a,} Dereddened Gaia DR3 color vs.~absolute magnitude for
+  TIC\,141146667, USco (8\,Myr), IC\,2602 (40\,Myr), the Pleiades
+  (112\,Myr) and stars within 100\,pc. 
+  The location of TIC\,141146667 in this diagram suggests an age of
+  30-150\,Myr. 
+  {\bf b,} An upper limit on photospheric lithium for TIC\,141146667
   (green triangle) yields a lower bound on the star's age of
   $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
-  \citep{Jeffries2023}; rich clusters in each age bin include NGC\,2264
+  \citep{Jeffries2023}; rich clusters in these data include NGC\,2264
   (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
-  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2602 and IC\,2391 (42.0\,Myr),
+  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2391 (42.0\,Myr),
   and NGC\,2451A (50.0\,Myr). }
@@
   \includegraphics[width=\textwidth]{figures/sf5.pdf}
-  \vspace{-0.25cm}
+  \vspace{-0.5cm}
   \caption{{\bf Time evolution of the Keck/HIRES spectra

### 2025-04-23 drivers/plot_hrd.py
update

@@ -16,6 +16,7 @@ from complexrotators.paths import DATADIR, RESULTSDIR
 from astropy import units as u
 from aesthetic.plot import set_style, savefig
 from matplotlib import rcParams
+from typing import Dict, Tuple
 
 from cdips.utils.gaiaqueries import given_source_ids_get_gaia_data
 
@@ -233,6 +234,38 @@ def get_cpv_hrd_data():
 
 
 
+def label_panels_figure(
+    fig: plt.Figure,
+    label_dict: Dict[str, Tuple[float, float]],
+    fontsize: str = 'medium'
+) -> None:
+    """Place boldface panel labels in figure (not axes) coordinates.
+
+    Generated by ChatGPT o3-mini-high on March 20 2025.
+
+    Args:
+        fig (matplotlib.figure.Figure):
+            The figure object to place text in.
+        label_dict (Dict[str, Tuple[float, float]]):
+            A dictionary whose keys are single-letter panel labels (e.g. 'a'),
+            and whose values are (x, y) in figure coordinates (0–1 range).
+
+    Returns:
+        None
+    """
+    for letter, (xx, yy) in label_dict.items():
+        fig.text(
+            xx,
+            yy,
+            f"{letter}",
+            transform=fig.transFigure,
+            fontsize=fontsize,
+            fontweight='bold',
+            ha="left",
+            va="top"
+        )
+
+
 def plot_hrd(deredden=0, smalllims=0, cpvcomparison=0):
 
     ##############################
@@ -277,8 +310,10 @@ def plot_hrd(deredden=0, smalllims=0, cpvcomparison=0):
     # plot
     dfs = [df_usco, df_ic2602, df_ple, df_bkgd, df_1411]
     colors = ['limegreen', 'C1', 'cyan', 'gray', 'yellow']
-    names = ['USco (8 Myr)', 'IC2602 (40 Myr)', 'Pleiades (112 Myr)',
-             'Nearby Stars', 'TIC 141146667']
+    names = ['8 Myr', '40 Myr', '112 Myr', 'Nearby Stars',
+             'TIC 141146667']
+    #names = ['USco (8 Myr)', 'IC2602 (40 Myr)', 'Pleiades (112 Myr)',
+    #         'Nearby Stars', 'TIC 141146667']
     zorders = [1,2,3,-1,99]
     if cpvcomparison:
[…]

### 2025-04-23 drivers/plot_li_vs_population.py

@@ -6,7 +6,38 @@ from matplotlib import rcParams
 
 from matplotlib.colors import ListedColormap, LinearSegmentedColormap
 from aesthetic.plot import set_style, savefig
+from typing import Dict, Tuple
 
+def label_panels_figure(
+    fig: plt.Figure,
+    label_dict: Dict[str, Tuple[float, float]],
+    fontsize: str = 'medium'
+) -> None:
+    """Place boldface panel labels in figure (not axes) coordinates.
+
+    Generated by ChatGPT o3-mini-high on March 20 2025.
+
+    Args:
+        fig (matplotlib.figure.Figure):
+            The figure object to place text in.
+        label_dict (Dict[str, Tuple[float, float]]):
+            A dictionary whose keys are single-letter panel labels (e.g. 'a'),
+            and whose values are (x, y) in figure coordinates (0–1 range).
+
+    Returns:
+        None
+    """
+    for letter, (xx, yy) in label_dict.items():
+        fig.text(
+            xx,
+            yy,
+            f"{letter}",
+            transform=fig.transFigure,
+            fontsize=fontsize,
+            fontweight='bold',
+            ha="left",
+            va="top"
+        )
 
 def truncate_colormap(
     cmap: LinearSegmentedColormap, minval: float = 0.0, maxval: float = 1.0,
@@ -83,7 +114,7 @@ def plot_li_vs_population() -> None:
         )
 
     ax.scatter(
-        2972, 107, marker='v', linewidth=0.6, color='greenyellow', s=50,
+        2972, 107, marker='*', linewidth=0.5, color='yellow', s=110,
         zorder=99, edgecolor='k'
     )
 
@@ -98,6 +129,11 @@ def plot_li_vs_population() -> None:
     ax.set_xlim([7100, 2800])
     ax.set_ylim([ -220, 860 ])
     #ax.set_title("LiEW vs TEFF for stars with AGE < 100")
+
+    labels = {
+        "b": (-0.07, 0.88),
+    }
+    label_panels_figure(fig, labels, fontsize='large')
 
     # Ensure output directory exists and save the figure.
     plot_dir = "results/li_ew"

### 2025-04-23 paper/collect_figs.sh
update

@@ -3,34 +3,36 @@ r="/Users/luke/Dropbox/proj/cpv/results"
 ##########################################
 # figure1: TIC 141146667 is a complex periodic variable.
 # still: c1265-1268, s48, 2022-02-16 to 2022-02-17
-cp $r/movie_phase_timegroups/TIC_141146667/TIC_141146667_0081_2min_phase_timegroups.pdf figures/f1.pdf
+cp $r/movie_phase_timegroups/TIC_141146667/TIC_141146667_0081_2min_phase_timegroups.pdf f1.pdf
 
 # Animated supporting: Movie of S41, S48, S75 TESS photometry, cycle-grouped
-cp $r/movie_phase_timegroups/TIC_141146667/movie_TIC1411_flux_phase_wob.mov movies/m1.mov
+cp $r/movie_phase_timegroups/TIC_141146667/movie_TIC1411_flux_phase_wob.mov m1.mov
 
 ##########################################
-# figure2: Hydrogen emission from circumstellar plasma orbiting TIC 141146667.
+# f2: The data are nearly but not exactly simultaneous
+cp $r/tic1411_obsepoch/tic1411_obsepoch.pdf f2.pdf
+
+##########################################
+# figure3: Hydrogen emission from circumstellar plasma orbiting TIC 141146667.
 # -still: index 0012.  t=3.1hr
-cp $r/movie_sixpanel_specriver/TIC_141146667_science/specriver_141146667_Hα_0012_2min_remove25pct_normbyveq_showlinecoresum.pdf figures/f2.pdf
+cp $r/movie_sixpanel_specriver/TIC_141146667_science/specriver_141146667_Hα_0012_2min_remove25pct_normbyveq_showlinecoresum.pdf f3.pdf
 
 # Animated supporting: Movie of spectral timeseries
-cp $r/movie_sixpanel_specriver/TIC_141146667_science_wob/TIC141146667_sixpanel.mov movies/m2.mov
+cp $r/movie_sixpanel_specriver/TIC_141146667_science_wob/TIC141146667_sixpanel.mov m3.mov
 
 ##########################################
 # supplementary
 
-# sf1: The data are nearly but not exactly simultaneous
[…]

### 2025-04-24 paper/ms.tex
update
apjl submit

@@
 %%%%%%%%%%
-% NOTE: might need to be ingested before submission 
-\input{vals_manuscript}
+\newcommand{\periodhr}{3.930}
 
@@
 
-\received{--}
+\received{23 April 2025}
 \revised{--}
@@
   \centering
-  \includegraphics[width=0.47\textwidth]{figures/f1.pdf}
-  \vspace{-0.3cm}
+  \includegraphics[width=0.47\textwidth]{f1.pdf}
+  \vspace{-0.4cm}
   \captionsetup{labelformat=moviefmt,labelsep=colon}
@@
 \caption{Selected system parameters for TIC\,141146667.}
+\vspace{-0.2cm}
 \label{tab:params}
@@
   \centering
-  \includegraphics[width=0.925\textwidth]{figures/sf1.pdf}
+  \includegraphics[width=0.925\textwidth]{f2.pdf}
   \vspace{-0.2cm}
@@
   \centering
-  \includegraphics[width=0.99\textwidth]{figures/f2.pdf}
+  \includegraphics[width=0.99\textwidth]{f3.pdf}
   \vspace{-0.25cm}
@@
 subset of B stars with radiatively-driven winds which accumulate into
-warped plasma tori \citep{Townsend2005,Townsend2008}.  These tori tend
+warped plasma tori \citep{Townsend2005}.  These tori tend
 to have dense antipodal accumulations of plasma sculpted by
@@
 be clarified by time-series optical and infrared spectrophotometry.
-While observations of CPVs in the optical suggest a chromaticity
-consistent with dust \citep{Tanimoto2020,Gunther2022,Koen2023}, a gray
-opacity source such as electron scattering in a plasma transiting over a
+While observations of CPVs in the optical suggest chromaticity
+consistent with dust \citep{Tanimoto2020,Gunther2022,Koen2023}, 
+electron scattering in a plasma transiting over a
 spotted background star might also produce chromatic features
@@
 that dust can condense out from M dwarf winds, similar to processes that
-occur around more evolved stars \citep{Marigo2008}.
+occur around evolved stars \citep{Marigo2008}.
 
@@
 there is a need for rigid-field magnetohydrodynamic models to
-go beyond previous work \citep{Townsend2005,Townsend2008,Krticka2022}
+go beyond previous work \citep{Townsend2008,Krticka2022}
 and to explore what field topologies explain the observed light
@@
   J.~Spake, J.~Winn, and L.~Hillenbrand for insightful conversations
-  that significantly informed this work, and to A.~Howard and
+  that significantly informed this work, as well as A.~Howard and
   H.~Isaacson for their assistance reducing the HIRES spectra.
@@
   %
+
+	The analyses in this article used data from TESS; the specific
+	2-minute cadence observations can be accessed via
+	DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
   Funding for the TESS mission is provided by NASA’s Science Mission
   directorate.
-  TESS is a product of millions of hours of work by thousands of people;
+  TESS is a product of millions of hours of work by thousands of people, and
   we thank the TESS team for their efforts to make the mission a
@@
 \software{
+  astroariadne \citep{Vines2022},
   astropy \citep{astropy:2013,astropy:2018,astropy:2022},
+  chatgpt \citep{chatgpt2025openai},
+	dustmaps \citep{2018JOSS....3..695M},
   matplotlib \citep{matplotlib},
   numpy \citep{numpy},
+  numpyro \citep{Phan2019},
   scipy \citep{scipy}.
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{figures/sf4.pdf}
+  \includegraphics[width=0.48\textwidth]{f4.pdf}
   \caption{
@@
 		\subfloat{
-			\includegraphics[width=0.46\textwidth]{figures/sf3.pdf}
+			\includegraphics[width=0.46\textwidth]{f5a.pdf}
 		}
 		\subfloat{
-			\includegraphics[width=0.47\textwidth]{figures/sf2.pdf}
+			\includegraphics[width=0.47\textwidth]{f5b.pdf}
 		}
@@
 \end{figure}
-
-%  \label{fig:camd}
-%  \label{fig:liew_population}
-%\begin{figure}[!t]
-%  \centering
-%  \includegraphics[width=0.48\textwidth]{figures/sf2.pdf}
-%  \caption{}
-%\end{figure}
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{figures/sf6.pdf}
+  \includegraphics[width=0.5\textwidth]{f6.pdf}
   \caption{{\bf Time-variable fit to H$\alpha$ line profiles.}  {\it Left
@@
   \centering
-  \includegraphics[width=0.99\textwidth]{figures/sf7.pdf}
+  \includegraphics[width=0.99\textwidth]{f7.pdf}
   \caption{{\bf a,} Orbits fit to mean radial velocities (RVs)
@@
   \centering
-  \includegraphics[width=\textwidth]{figures/sf5.pdf}
+  \includegraphics[width=\textwidth]{f8.pdf}
   \vspace{-0.5cm}

### 2025-04-25 paper/ms.tex
update

@@
 % upon AAS submission
-\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex7}
-%\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex7}
+%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex7}
+\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex7}
 % drafting / arxiv
 %\documentclass[11pt,twocolumn,modern]{aastex7}
-\turnoffedit
+%\turnoffedit
 
@@
 
-\shortauthors{Bouma et al.}
+\shortauthors{L.~G.~Bouma}
 
@@
   stellar rotation, and (we hypothesize) of corotating clumps of
-  circumstellar material.  Raw data acquired at two minute dence
+  circumstellar material.  Raw data acquired at two minute cadence
   are in gray; black averages to 100 points per cycle.  
@@
 
-\subsection{Clumps Within Warped Plasma Torii}
+\subsection{Clumps Within Warped Plasma Tori}
 
@@
 
-\subsection{Future Work: Composition, Origin, Modelling}
+\subsection{Future Work: Composition, Origin, Modeling}
 
@@
 radius measured using the spectral energy distribution (SED) fitting
-procedure described by \citep{Bouma2024}.  To summarize, this approach
+procedure described by \citet{Bouma2024}.  To summarize, this approach
 used \texttt{astroARIADNE} \citep{Vines2022} with the BT-Settl stellar
-atmosphere models \citep{Allard2012}, assuming the \citep{Asplund2009}
-solar abundances and the \citep{Barber2006} water line lists.  This
+atmosphere models \citep{Allard2012}, assuming the \citet{Asplund2009}
+solar abundances and the \citet{Barber2006} water line lists.  This
 approach fitted for the stellar effective temperature, radius,
@@
 M5.5Ve by visually comparing the HIRES spectra against the photometric
-standards tabulated by \citep{Bochanski2007}.   This result agrees with
+standards tabulated by \citet{Bochanski2007}.   This result agrees with
 the effective temperature found from the SED fitting
@@
   (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2391 (42.0\,Myr),
-  and NGC\,2451A (50.0\,Myr). }
+  and NGC\,2451A (50.0\,Myr).\added{ Measurement uncertainties are
+  large below $+$50\,m\AA; negative EW does not correspond to significant
+  emission.}}
   \label{fig:age_diagnostics}

### 2025-05-01 paper/ms.tex
update

@@
 \newcommand{\caltech}{Department of Astronomy, California Institute of Technology, Pasadena, CA 91125, USA}
+\newcommand{\standrews}{School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, Fife, Scotland KY16 YSS, UK}
 %%%%%%%%%%%%%%%%
@@
 
-\shortauthors{L.~G.~Bouma}
+\shortauthors{Bouma et al.}
 
@@
 \email{lbouma@carnegiescience.edu}
+
+\author[orcid=0000-0002-1466-5236,sname='Jardine']{Moira~M.~Jardine}
+\affiliation{\standrews}
+\email{mmj@st-andrews.ac.uk}
 
@@
 although with a very different composition.
+% (Because the Io ring has lots of sodium and S II (6717) emission.
+% Sodium is ambiguous in HIRES due to order placement, but the sulfur
+% is not there.  With that said, it is much hotter in an M dwarf
+% magnetosphere than around Jupiter; the ionization balance would be
+% quite different.)
 
@@
 time-varying Balmer emission
-\citep{Donati2000,Townsend2005,Dunstone2006,Skelly2008}, similar to 
+\citep{Donati2000,Townsend2005b,Dunstone2006,Skelly2008}, similar to 
 Figure~\ref{fig:spec}.  No such stars were previously known to show
@@
 \begin{acknowledgements}
-  We thank M.~Jardine, A.~Weinberger, B.~Tofflemire,
+  We thank B.~Tofflemire, A.~Weinberger, 
   J.~Spake, J.~Winn, and L.~Hillenbrand for insightful conversations
@@
 
-  This work was supported by the Carnegie Fellowship and by the
+  LGB acknowledges support from the Carnegie Fellowship and the
   Heising-Simons 51~Pegasi~b Fellowship.
+  MMJ acknowledges support from STFC consolidated grant
+  number ST/R000824/1.
   %
@@
 \end{acknowledgements}
+
+{\it \large Contributions}: 
+LGB led the inception, design, execution, and interpretation of the
+research.  MMJ contributed to the interpretation.
 
@@
 same manner as the emission seen in H$\alpha$.  This could be because
-there are insufficient hydrogen ions in the relevant excited states, or
+there are insufficient hydrogen atoms in the relevant excited states, or
 because the spectra have lower precision in these bluer regions.  The Ca
@@
 
-Finally, the Li\,\textsc{I} 6708\,\AA\ doublet, which shows no obvious
+Finally, the Li\,\textsc{I} 6708\,\AA\ region, which shows no obvious
 absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ resonance

### 2025-05-23 paper/ms.tex
update

@@
 % upon AAS submission
-%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex7}
-\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex7}
+\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex7}
+%\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex7}
 % drafting / arxiv
@@
   observation (green bar).}  {\bf a,} TESS simple aperture photometry.
-  Data gaps caused by light from Earth (BTJD 3356-3358.5) and Moon
+  Data gaps caused by light from the Earth (BTJD 3356-3358.5) and Moon
   (BTJD 3359.5-3360.5) are visible.  Raw two minute
@@
   now phase-averages to 100 points per
-  cycle.  During BTJD 3352-3356, a state switch occurred near BTJD
+	3.93\ hour cycle.  During BTJD 3352-3356, a state switch occurred near BTJD
   3353, and the dip at $\phi$$\approx$0.8 disappeared.  While the
@@
 corotation radii $R_{\rm c}$, the effective potential experienced by
-charged particles has a local minimum outside $R_{\rm c}$, which enables
+charged particles \added{along any given field line }has a local minimum outside $R_{\rm c}$, which enables
 charged material to accumulate in a torus
@@
 close-in exoplanet.  This latter scenario would make CPVs extrasolar
-analogs of the Jupiter-Io torus (e.g.~\citealt{Bagenal1981}),
+analogs of the Jupiter-Io torus (e.g.~\citealt{Bagenal1981}, \citealt{Kislyakova2018}),
 although with a very different composition.
@@
 spectroscopic variability of these stars, and that of the analogous
-transient absorption features
+transient \added{H$\alpha$ }absorption features
 \citep{CollierCameron1989,CollierCameron1992,Cang2020}, comes from an

### 2025-05-23 drivers/plot_m_dwarf_planet_comparison.py
add drivers/plot_m_dwarf_planet_comparison.py

@@ -1,0 +1,163 @@
+import numpy as np
+from isochrones import get_ichrone
+
+from astroquery.ipac.nexsci.nasa_exoplanet_archive import \
+    NasaExoplanetArchive
+from astropy.table import Table
+import pandas as pd
+import astropy.units as u
+from astropy.constants import R_sun
+import matplotlib.pyplot as plt
+
+
+def fetch_m_dwarf_planets() -> Table:
+    """Fetch PSCompPars for confirmed planets around M-dwarfs.
+
+    Generated by ChatGPT o4-mini on April 26 2025.
+
+    Returns:
+        Table: PSCompPars rows with st_mass < 0.3 Msun.
+    """
+    table = NasaExoplanetArchive.query_criteria(
+        table="pscomppars",
+        select="pl_name, st_mass, st_rad, pl_orbsmax, pl_rade",
+        where="st_mass < 0.3"
+    )
+    return table
+
+
+def compute_a_rstar(df: pd.DataFrame) -> pd.DataFrame:
+    """Compute a/Rstar and return sorted DataFrame.
+
+    Generated by ChatGPT o4-mini on April 26 2025.
+
+    Args:
+        df: DataFrame with pl_orbsmax, st_rad.
+
+    Returns:
+        DataFrame with new column a_Rstar, sorted ascending.
+    """
+    df = df.dropna(subset=["pl_orbsmax", "st_rad", "pl_rade"])
+    a = df["pl_orbsmax"].values * u.AU
+    r = df["st_rad"].values * R_sun
+    df["a_Rstar"] = (a / r).to_value(u.dimensionless_unscaled)
+    return df.sort_values("a_Rstar").reset_index(drop=True)
+
+
+def compute_pre_ms_radius(df: pd.DataFrame,
+                          age_myr: float = 10.0) -> np.ndarray:
+    """Estimate stellar radius at a given pre-main-sequence age.
+
+    Generated by ChatGPT o4-mini-high on April 26 2025.
+
+    Args:
+        df: DataFrame with 'st_mass' in solar masses.
+        age_myr: Age in Myr for pre-main-sequence evaluation.
+
+    Returns:
+        np.ndarray: Stellar radii in units of R_sun.
+    """
+    mist = get_ichrone('mist', tracks=True)
+    log_age = np.log10(age_myr * 1e6)
+    radii = []
+    for mass in df['st_mass'].values:
+        try:
+            props = mist.generate(mass, log_age, 0.0, return_dict=True)
[…]

### 2025-05-24 paper/ms.tex
update
MMJ first ~half

@@
   CPV.  These data support the idea that young, rapidly-rotating M
-  dwarfs can sustain warped plasma tori, similar to massive magnetic
-  stars.  It remains unclear whether these structures originate
-  intrinsically from the star or are fed by external sources. Likewise,
-  the mechanism by which their optically thick clumps arise is still
-  unknown.  Rough estimates suggest $\gtrsim$10\% of M dwarfs host
+  dwarfs can sustain warped \added{tori of cool plasma, similar to
+  other rapid magnetic rotators.}
+  \added{Outstanding questions include whether dust clumps 
+  in these plasma tori explain CPV light curves, and
+  whether the tori originate from the star or are fed by external
+  sources.}
+  %It remains unclear whether these structures originate intrinsically
+  %from the star or are fed by external sources. Likewise,
+  %the mechanism by which their optically thick clumps arise is still
+  %unknown.
+  Rough estimates suggest $\gtrsim$10\% of M dwarfs host
   similar structures during their early lives.
@@
 \citep{Ribas2015}, to high doses of UV radiation \citep{France2016},
-and to a high incidence of flares and coronal mass ejections
+and to a high incidence of flares 
 \citep{Feinstein2020}.  However, despite extensive work in these
@@
 field, and the exact geometry of where the plasma can accumulate is
-dictated by the field's topology.  For instance, a magnetic dipole
+dictated by the field's topology \citep{Waugh2022}.  For instance, a magnetic dipole
 field tilted with respect to the stellar spin axis yields
-accumulations in a warped torus geometry \citep{Townsend2005}, whereas
-in the limit of a single strong field line, accumulation occurs at the
-line's apex, furthest from the star \citep{Waugh2022}.  To date, none
-of these spectroscopic variables have shown any photometric anomalies
-\citep{Bouma2024}, leaving open the issue of whether they are related
-to CPVs.
+accumulations in a warped torus geometry \citep{Townsend2005}.  To
+date, none of these spectroscopic variables have shown any photometric
+anomalies \citep{Bouma2024}, leaving open the issue of whether they
+are related to CPVs.
 
@@
 %
-$v_{\rm break}$\dotfill		              & Breakup velocity \dotfill                                      &  316$\pm$16      & 6 \\
+$v_{\rm crit}$\dotfill		              & Critical velocity \dotfill                                      &  316$\pm$16      & 6 \\
                                         & \hspace{3pt} ($G M_\star / R_\star$)$^{1/2}$ (\kms)	           &                      \\
@@
 spectral resolution $R$$\approx$45{,}000 ($\delta
-v$$\approx$6.7\,\kms; $\delta v / v_{\rm eq}$$\approx$0.05).  We
+v$$\approx$6.7\,\kms).  We
 binned the CCD readout by a factor of three in the spatial dimension,
 yielding $\approx$1,000 photons (S/N=33) per pixel in the continuum at
-6500\,\AA, at minimum airmass.  Strong winds contributed to
+6500\,\AA.  Strong winds contributed to
 1$''$-1\farcs5 seeing over the night, but conditions were otherwise
@@
 (TESS Program G06030, PI: Bouma).   The 30-minute data during Sectors
-14, 15, and 21 probably smeared sharp features over the star's 3.93\,hour
+14, 15, and 21 smeared sharp features over the star's 3.93\,hour
 period (see \citealt{Gunther2022}).  The movie in
@@
 then passed within 25$^\circ$ of the camera's boresight.  Based on the
-level of scattered light in the optimal TIC\,141146667 aperture
+level of scattered light in the optimal aperture
 \citep{Jenkins2016}, we manually masked out data in the TESS light curve
@@
 dip had two sharp local minima;  the minimum at $\phi$$\approx$0.8
-decreased in depth following the flare at BTJD 3353, yielding a dip more
+became less pronounced following the flare at BTJD 3353, yielding a dip more
 closely resembling an asymmetric ``V'' than a ``W''.  Similar CPV state
@@
 field.  The velocity semi-amplitude of the sinusoids gives the mean
-distance of each clump from the stellar surface: 2.07\,$R_\star$ and
+distance of each clump from the stellar \added{rotation axis}: 2.07\,$R_\star$ and
 2.88\,$R_\star$ for the inner clumps, and 3.88\,$R_\star$ for the outer
@@
 \begin{acknowledgements}
-  We thank B.~Tofflemire, A.~Weinberger, 
-  J.~Spake, J.~Winn, and L.~Hillenbrand for insightful conversations
-  that significantly informed this work, as well as A.~Howard and
-  H.~Isaacson for their assistance reducing the HIRES spectra.
+  We thank B.~Tofflemire, A.~Weinberger, and L.~Hillenbrand for
+  conversations that significantly informed this work; J.~Spake,
+  J.~Winn, J.-F~Donati, and R.~Townsend for feedback on the
+  manuscript; and A.~Howard and H.~Isaacson for their assistance
+  reducing the HIRES spectra.
 
@@
 based on its apparent size and rotation period is 130$\pm$4\,\kms.
-While this suggests that the viewing orientation could be nearly
-edge-on, the formal constraint is rather weak, with $i$$>$63$^\circ$
-at 2$\sigma$ (2.5$^{\rm th}$ percentile of the inclination posterior).
+\added{While these measurements are consistent with an edge-on
+viewing geometry}, the formal constraint is rather weak, with
+$i$$>$63$^\circ$ at 2$\sigma$ (2.5$^{\rm th}$ percentile of the
+inclination posterior).
 
@@
 
+% NOTE: Uniformly rotating roche model would have fractional
+% oblateness 1/2(veq/crit)^2 ~= 8%.
 {\it Effective temperature, radius, mass, and spectral
@@
 For a uniform density clump, this suggests a total gas mass of $M_{\rm
-gas}\approx 2\times10^{17}$\,g.  We emphasize that
+gas}\approx 2\times10^{17}$\,g\added{, similar to those derived for
+other cool stars \citep{VillarrealDAngelo2019}.}.  We emphasize that
 Equation~\ref{eq:numdensity} in intended to provide only an order of

### 2025-05-25 paper/ms.tex
update

@@
 % upon AAS submission
-\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex7}
-%\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex7}
+%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex7}
+\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex7}
 % drafting / arxiv
@@
   dwarfs can sustain warped \added{tori of cool plasma, similar to
-  other rapid magnetic rotators.}
+  other rapidly-rotating magnetic stars.}
   \added{Outstanding questions include whether dust clumps 
@@
 
-\citet{Townsend2005} outlined the physics of how rapidly-rotating stars
-with strong magnetic fields can support plasma tori.  When the
-magnetospheric radii $R_{\rm m}$ of such stars exceeds their Keplerian
-corotation radii $R_{\rm c}$, the effective potential experienced by
-charged particles \added{along any given field line }has a local minimum outside $R_{\rm c}$, which enables
-charged material to accumulate in a torus
-\citep{Petit2013,Daley-Yates2024}.  Warps can occur when there is
-misalignment between the spin and magnetic axes.  In general, the
-material in these centrifugally-supported magnetospheres need neither
-transit nor be opaque in broadband optical light.
+\citet{Townsend2005} outlined the physics of how rapidly-rotating
+stars with strong magnetic fields can support plasma tori \added{\citep[see
+also][]{Nakajima1985,Ferreira2000,Petit2013,Daley-Yates2024}}.  When
+the magnetospheric radii $R_{\rm m}$ of such stars exceeds their
+Keplerian corotation radii $R_{\rm c}$, the effective potential
+experienced by charged particles \added{along any given field line
+}has a local minimum outside $R_{\rm c}$, which enables charged
+material to accumulate in a torus.  Warps can occur when there is
+misalignment between the spin and magnetic axes.  In general,
+the\added{ regions} in these centrifugally-supported
+magnetospheres\added{ with the densest plasma accumulations} need
+neither transit nor be opaque in broadband optical light.
 
@@
 these systems, assuming that the optical depth scaled linearly with
-density.  They found that W-shaped eclipses, similar to those seen for
+plasma density.  They found that W-shaped eclipses, similar to those seen for
 TIC\,141146667, can occur when the spin and magnetic axes are moderately
@@
 For a uniform density clump, this suggests a total gas mass of $M_{\rm
-gas}\approx 2\times10^{17}$\,g\added{, similar to those derived for
-other cool stars \citep{VillarrealDAngelo2019}.}.  We emphasize that
+gas}\approx 2\times10^{17}$\,g\added{, which is similar to masses derived for
+plasma clumps around other cool stars \citep{VillarrealDAngelo2019}.}.  We emphasize that
 Equation~\ref{eq:numdensity} in intended to provide only an order of
@@
 thorough estimate would iteratively solve the equations of detailed
-balance and radiative transfer (e.g.~\citealt{CollierCameron1989}
-Figure~8), and potentially also consider departures from local
-thermodynamic equilibrium.
+balance and radiative transfer (e.g.~Figure~8 of \citealt{CollierCameron1989}),
+and potentially also consider departures from local thermodynamic equilibrium.
 

### 2025-05-25 paper/ms.tex
update

@@
 
-The material's composition -- either pure plasma or dusty plasma -- can
-be clarified by time-series optical and infrared spectrophotometry.
-While observations of CPVs in the optical suggest chromaticity
-consistent with dust \citep{Tanimoto2020,Gunther2022,Koen2023}, 
-electron scattering in a plasma transiting over a
-spotted background star might also produce chromatic features
-\citep{Rackham2018}.  The composition and size distribution of any dust
-that is present could be determined by measuring the extinction curve
-for a sample of CPVs from 1-20\,$\mu$m.  Composition and size
-distributions similar to debris from rocky bodies seen around white
-dwarfs \citep{Reach2009} would suggest an extrinsic origin channel.
-Compositions and sizes similar to the interstellar medium would suggest
-that dust can condense out from M dwarf winds, similar to processes that
-occur around evolved stars \citep{Marigo2008}.
-
-The role of the star's magnetic field could be better understood through
-new observations, and new theory.  From the modeling perspective,
-there is a need for rigid-field magnetohydrodynamic models to
-go beyond previous work \citep{Townsend2008,Krticka2022}
-and to explore what field topologies explain the observed light
-curve shapes.  In particular, dynamo simulations of
-fully-convective M dwarfs have suggested that global-scale mean fields
-might be confined to a single hemisphere \citep{Brown2020}; such fields
-would yield accumulation surfaces quite different from those that have
-previously been explored.  Observationally, spectropolarimetry has the
-potential to assess both the field strength and topology.  An
-independent constraint on magnetic field topology may also come from
-radio observations, which have shown \citep{Kaur2024} that CPVs emit
-variable radio signals, including persistent and polarized components.
-Detecting radio emission produced by an electron cyclotron maser
-instability (e.g.~\citealt{Callingham2021}) in particular would provide
-a measurement of the field strength at the site of the emitting region,
-which could help clarify the magnetosphere's structure.
+The material's composition -- either pure plasma or dusty plasma --
+can be clarified by time-series infrared spectrophotometry.  While
+observations of CPVs in the optical suggest chromaticity consistent
+with dust \citep{Tanimoto2020,Gunther2022,Koen2023}, electron
+scattering in a plasma transiting over a spotted background star might
+also produce chromatic features \citep{Rackham2018}.  \added{This
+degeneracy is alleviated in the infrared, where the} composition and
+size distribution of any dust that is present could be determined by
+measuring the extinction curve for a sample of CPVs from 1-20\,$\mu$m.
+Composition and size distributions similar to debris from rocky bodies
+seen around white dwarfs \citep{Reach2009} would suggest an extrinsic
+origin channel.  Compositions and sizes similar to the interstellar
+medium would suggest that dust can condense out from M dwarf winds,
+similar to processes that occur around evolved stars
+\citep{Marigo2008}.
+
+\added{Future models could take a range of steps to clarify the origin
+of CPVs.  A first step for magnetohydrodynamic models that can
+currently explain the H$\alpha$ features \citep[e.g.][]{Waugh2022}
+would be to incorporate an opacity source that can also reproduce the
+photometric dips.  It is likely that this effort will require
+exploring what stellar magnetic field topologies reproduce the
+observed light curve shapes \citep[e.g.][]{Bouma2024}. While previous
+models in the rigid-field approximation have explored both dipolar
+\citep{Townsend2008} and multipolar fields \citep{Krticka2022}, dynamo
+simulations of fully-convective M dwarfs have suggested that
+global-scale mean fields might be confined to a single hemisphere
+\citep{Brown2020}; such fields would yield accumulation surfaces quite
+different from those that have been explored.  One related challenge
+is that CPVs currently suffer a dearth of stellar surface field
+measurements, unlike benchmark systems such as AB Dor and V374~Peg
+\citep{Jardine2002,Vidotto2011}. This might be alleviated through
+future spectropolarimetric observations, or from radio observations
+sensitive to the magnetic field structure around the star
+\citep[see][]{Callingham2021,Kaur2024}.  Finally, the question of what
+microphysical process yields the opaque material also merits future
+theoretical attention. While recent advances can produce the
+catastrophic cooling that leads to dense, cool clumps embedded in a
+hot corona \citep{Daley-Yates2023,Daley-Yates2024}, a self-consistent
+treatment of radiation propagating through such clumps remains to be
+performed. The question of whether dust grains can nucleate in such
+clumps, or whether they need to be externally sourced, deserves
+careful attention.}
+
+%The role of the star's magnetic field could be better understood through
+%new observations, and new theory.  From the modeling perspective,
+%there is a need for rigid-field magnetohydrodynamic models to
+%go beyond previous work \citep{Townsend2008,Krticka2022}
+%and to explore what field topologies explain the observed light
+%curve shapes.  In particular, dynamo simulations of
+%fully-convective M dwarfs have suggested that global-scale mean fields
+%might be confined to a single hemisphere \citep{Brown2020}; such fields
+%would yield accumulation surfaces quite different from those that have
+%previously been explored.  Observationally, spectropolarimetry has the
+%potential to assess both the field strength and topology.  An
+%independent constraint on magnetic field topology may also come from
+%radio observations, which have shown \citep{Kaur2024} that CPVs emit
+%variable radio signals, including persistent and polarized components.
+%Detecting radio emission produced by an electron cyclotron maser
+%instability (e.g.~\citealt{Callingham2021}) in particular would provide
+%a measurement of the field strength at the site of the emitting region,
+%which could help clarify the magnetosphere's structure.
 
@@
 LGB led the inception, design, execution, and interpretation of the
-research.  MMJ contributed to the interpretation.
+project.  MMJ contributed to the interpretation.
 

### 2025-05-26 drivers/plot_hrd.py
hrd: variants

@@ -26,7 +26,10 @@ from rudolf.extinction import append_corrected_gaia_phot_Gaia2018
 EXTINCTIONDICT = {
     'Pleiades': 0.10209450, # from Hunt+24, table1, A_V
     'IC_2602': 0.11434174, # from Hunt+24, table1, A_V
-    'UCL/LCC': 0.12 # Pecaut&Mamajek 2016 table7 median
+    'UCL/LCC': 0.12, # Pecaut&Mamajek 2016 table7 median
+    'NGC_2516': 0.2046, # from Hunt+24, table1, A_V
+    'NGC_6475': 0.20822802, # from Hunt+24, table1, A_V
+    'NGC_2632': 0.15869616, # Hunt+24 table1 Praesepe
 }
 
 def get_kerr21_usco():
@@ -167,6 +170,69 @@ def get_ic2602():
     return gdf
 
 
+def get_ngc2516():
+
+    fitspath = '../data/literature/Hunt_2024_table2.fits'
+    hl = fits.open(fitspath)
+    df_h24 = Table(hl[1].data).to_pandas()
+
+    # Pleiades
+    df_ple = df_h24[(df_h24['Name'] == 'NGC_2516') & (df_h24.Prob > 0.5)]
+
+    dr3_source_ids = np.array(df_ple['GaiaDR3'])
+    groupname = 'Hunt2024_t2_ngc2516'
+    gdf = given_source_ids_get_gaia_data(dr3_source_ids, groupname,
+                                         n_max=20000, overwrite=False,
+                                         enforce_all_sourceids_viable=True,
+                                         which_columns='*',
+                                         table_name='gaia_source_lite',
+                                         gaia_datarelease='gaiadr3')
+
+    return gdf
+
+
+def get_ngc6475():
+
+    fitspath = '../data/literature/Hunt_2024_table2.fits'
+    hl = fits.open(fitspath)
+    df_h24 = Table(hl[1].data).to_pandas()
+
+    # Pleiades
+    df_ple = df_h24[(df_h24['Name'] == 'NGC_6475') & (df_h24.Prob > 0.5)]
+
+    dr3_source_ids = np.array(df_ple['GaiaDR3'])
+    groupname = 'Hunt2024_t2_ngc6475'
+    gdf = given_source_ids_get_gaia_data(dr3_source_ids, groupname,
+                                         n_max=20000, overwrite=False,
[…]

### 2025-05-26 paper/ms.tex
update

@@
     {\bf Spectral energy distribution} of broadband photometric magnitudes
-    (filled markers) plotted over the best-fit BT-Settl stellar
+    (filled \added{cyan circles}) plotted over the best-fit BT-Settl stellar
     atmosphere model \citep{Allard2012} and the associated photometric
-    predictions (empty markers).  This plot was made from an
+    predictions (empty \added{purple diamonds}).  This plot was made from an
     adaptation of \texttt{astroARIADNE} \citep{Vines2022}.  The
@@
 expected to set the inner boundary at which corotating material might
-accumulate (e.g.~\citep{Townsend2005,Daley-Yates2024}).  Our final
+accumulate (e.g.~\citealt{Townsend2005,Daley-Yates2024}).  Our final
 quoted $M_\star$ and $R_{\rm cr}$ values adopt the average of these
@@
 also noted that in the Gaia passbands, CPVs tend to be photometrically
-redder and more luminous than single stars in any given cluster,
-similar to other rapid rotators.  While this effect complicates any
-attempt at age inference based on the Gaia photometry, it suggests
-that the Pleiades may be a better comparison population than IC~2602.
-We take the star's location in the color--absolute magnitude diagram
+redder and more luminous than single stars in any given
+cluster\added{; they also found suggestive evidence for either
+hotspots or emission from dust based on analysis
+of Gaia and WISE photometry.  The implication is that isochronal age
+dating of individual field CPVs suffers significant systematic
+uncertainty due to factors including dark and bright spots, magnetic
+inflation, dust emission, and photometric binarity. Rather than
+adopting a particular model isochrone framework, we instead visually}
+take the star's location in the color--absolute magnitude diagram
 to suggest age bounds $t_{\rm CAMD}$$\sim$30-150\,Myr.

### 2025-05-27 drivers/fit_orbits.py
fit_orbits: add csvcache

@@ -404,6 +404,17 @@ def main(fittingstyle='leastsquares'):
                     popt = fit['popt_circ']
                     ax.plot(fn(t_fit), rv_circular(t_fit, *popt), '-', c=c,
                             zorder=-2, alpha=0.9, lw=0.8)
+
+                    outdf = pd.DataFrame(
+                        {'phase': fn(t_fit), 'rv': rv_circular(t_fit, *popt)}
+                    )
+                    csvpath = join(
+                        'results/halpha_to_rv_timerseries',
+                        f'circular_fit_compt_{ix}.csv'
+                    )
+                    outdf.to_csv(csvpath, index=False)
+                    print(f'wrote {csvpath}')
+
                     sigma = 0.25
                     # Compute the mean fit over the global t_fit grid.
                     y_mean = rv_circular(global_t_fit, *popt)

### 2025-05-27 paper/ms.tex
update

@@
 Figure~\ref{fig:spec} compiles the TESS and HIRES data from February
-2024.  The HIRES spectra show emission in H$\alpha$ beyond the star's
+2024.  The HIRES spectra \added{(Panels b,c,e,f)} show emission in H$\alpha$ beyond the star's
 equatorial velocity, $v_{\rm eq}$, of 130\,\kms.  There are at least
@@
 Appendix~\ref{subsec:halpha}).  This spectroscopic transit coincides
-with the latter half of the complex eclipse feature in the TESS data.
-
-The H$\alpha$ line core is more complex.  At $|\Delta v / v_{\rm
+with the latter half of the complex eclipse feature in the TESS data
+\added{(see Figure~\ref{fig:fulllc} and Panels a and b of Figure~\ref{fig:spec})}.
+
+The H$\alpha$ line core\added{, visible in Panels e and f of
+Figure~\ref{fig:spec}, }is more complex.  At $|\Delta v / v_{\rm
 eq}|<1$, most observed H$\alpha$ photons come from the star's
@@
 absorptive component to the circumstellar material which is not
-visible in emission.  While the origin of the other bright and dark
-streaks passing across the line core are similarly ambiguous, a final
-exercise to quantify the behavior of the line core is shown in
-Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes the
-summed flux at $|\Delta v / v_{\rm eq}|<1$.  This panel shows that
-changes in the line core flux correlate with the broadband variability
-throughout most of the light curve, except near $\phi$$\approx$0.5,
-corresponding to the transit of the 3.9\,$R_\star$ clump and the
-occultation of the lower-velocity clump.
+visible in emission.  The origin of the other bright and dark
+streaks passing across the line core \added{in Figure~\ref{fig:spec}e
+}are similarly ambiguous.  \added{Figure~\ref{fig:spec}d shows} a
+final exercise to quantify the behavior of the line core, where
+$f_{\rm H\alpha\ core}$ denotes the summed \added{H$\alpha$} flux at
+$|\Delta v / v_{\rm eq}|<1$.  This panel shows that changes in the
+line core flux correlate with the broadband variability throughout
+most of the light curve, except near $\phi$$\approx$0.5, corresponding
+to the transit of the 3.9\,$R_\star$ clump and the occultation of the
+lower-velocity clump.  \added{Spectroscopic transits therefore do not
+necessarily yield photometric transits.}
 
@@
 	The analyses in this article used data from TESS; the specific
-	2-minute cadence observations can be accessed via
+	2-minute cadence observations can be accessed \added{through MAST }via
 	DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.

### 2025-05-28 paper/ms.tex
update

@@
 that most M dwarfs host close-in planets \citep{Dressing2015} that on
-average are subject to long circumstellar disk lifetimes
-\citep{Ribas2015}, to high doses of UV radiation \citep{France2016},
-and to a high incidence of flares 
+average are subject to long disk lifetimes
+\citep{Ribas2015}, intense UV radiation \citep{France2016},
+and frequent stellar flares 
 \citep{Feinstein2020}.  However, despite extensive work in these
@@
 these environments is crucial because they directly impact atmospheric
-retention and habitability of close-in exoplanets.
+retention and\added{, ultimately,} habitability.
 
@@
 transiting clumps of circumstellar material corotate with the star
-\citep{Stauffer2017,Gunther2022,Bouma2024}, or that these stars
+\citep{Stauffer2017}, or that these stars
 represent an extreme in naturally-occurring distributions of starspots
@@
   observation (green bar).}  {\bf a,} TESS simple aperture photometry.
-  Data gaps caused by light from the Earth (BTJD 3356-3358.5) and Moon
-  (BTJD 3359.5-3360.5) are visible.  Raw two minute
+  Data gaps were caused by light from the Earth (BTJD 3356-3358.5) and
+  Moon (BTJD 3359.5-3360.5).  Raw two minute
   data are in gray; black time-averages to ten minute sampling.  {\bf
@@
 	3.93\ hour cycle.  During BTJD 3352-3356, a state switch occurred near BTJD
-  3353, and the dip at $\phi$$\approx$0.8 disappeared.  While the
-  large flux decrement was present both before and after the HIRES
-  sequence, its photometric shape evolved during the data gap.  The
-  orange bar denotes times of spectroscopic transits for the inner two
-  H$\alpha$ clumps observed with HIRES (see Figure~\ref{fig:spec}).}
+  3353, and the dip at $\phi$$\approx$0.8 \added{became less
+  pronounced}.  While the \added{dip spanning $\phi$=0.6-1.1} was present both before and after the
+  HIRES sequence, its photometric shape evolved during the data gap.
+  The orange bar denotes times of spectroscopic transits for the inner
+  two H$\alpha$ clumps observed with HIRES (see
+  Figure~\ref{fig:spec}).}
   \label{fig:fulllc}
@@
   \includegraphics[width=0.99\textwidth]{f3.pdf}
-  \vspace{-0.25cm}
+  \vspace{-0.3cm}
   \captionsetup{labelformat=moviefmt,labelsep=colon}
@@
   is at twice the continuum to accentuate emission outside the line
-  core ($|v/v_{\rm eq}|>1$, for $v_{\rm eq}$=130\,\kms).  While
-  emission in the line core originates in the star's chromosphere,
+  core ($|v/v_{\rm eq}|>1$, for the equatorial velocity $v_{\rm eq}$=130\,\kms).  While
+  emission in the line core comes from the star's chromosphere,
   the sinusoidal emission features are most readily described by a
@@
 (HIRES; \citealt{vogt_hires_1994}) on the 10\,m Keck I telescope.  The
-observations spanned the second half of the night, from 17 February
-2024 10:47 to 16:13 (UT).  The star's airmass spanned $z$=1.2-2.2, and
-we opted for a fixed 15 minute cadence, except for a final 10 minute
-exposure due to increasing sky brightness at sunrise.  We observed
-without the iodine cell and used the C2 decker
+observations spanned the second half of the night, from 10:47 to 16:13
+(UT). 
+%The star's airmass spanned $z$=1.2-2.2, and we opted for a fixed 15
+%minute cadence, except for a final 10 minute exposure due to
+%increasing sky brightness at sunrise. 
+\added{We opted for a fixed 15 minute cadence, and} used the C2 decker
 (0$\farcs$86$\times$14$\farcs$0) in the red configuration, yielding a
-spectral resolution $R$$\approx$45{,}000 ($\delta
-v$$\approx$6.7\,\kms).  We
-binned the CCD readout by a factor of three in the spatial dimension,
-yielding $\approx$1,000 photons (S/N=33) per pixel in the continuum at
-6500\,\AA.  Strong winds contributed to
-1$''$-1\farcs5 seeing over the night, but conditions were otherwise
-favorable.  We reduced the echelleogram to a one-dimensional spectrum
+resolution $R$$\approx$45{,}000 ($\delta
+v$$\approx$6.7\,\kms).
+%We binned the CCD readout by a factor of three in the spatial
+%dimension, yielding $\approx$1,000 photons (S/N=33) per pixel in the
+%continuum at 6500\,\AA. 
+Strong winds contributed to 1$''$-1\farcs5 seeing, but conditions were
+otherwise
+favorable.  We reduced the echelleogram %to a one-dimensional spectrum
 using the standard techniques of the California Planet Survey
@@
 spanning 2019-2024.  TESS acquired these observations at two-minute
-cadence during Sectors 41, 48 (TESS DDT039, PI: Kunimoto), and 75
-(TESS Program G06030, PI: Bouma).   The 30-minute data during Sectors
-14, 15, and 21 smeared sharp features over the star's 3.93\,hour
+cadence during Sectors 41, 48, and 75.   The 30-minute data during Sectors
+14, 15, and 21 smeared sharp features over the star's 3.93~hour
 period (see \citealt{Gunther2022}).  The movie in
@@
 The nearest known star, TIC\,141146666 ($T$=14.5), is 25$''$ from
-TIC\,141146667 and is photometrically stable in the TESS images;
+TIC\,141146667 and is photometrically \added{quiet};
 crowding is not a concern.
@@
 \citep{Jenkins2016}, we manually masked out data in the TESS light curve
-from 3359.40-3360.13; the remainder of the data during the lunar
-approach were usable.  Small gaps from BTJD 3353.55-3353.77 and
-3360.12-3360.33 were caused by data downlinks at the spacecraft's
+from 3359.4-3360.1; the remainder of the data during the lunar
+approach were usable.  Small gaps from BTJD 3353.6-3353.8 and
+3360.1-3360.3 were caused by data downlinks at the spacecraft's
 perigee and apogee.
 
-Although the data gap is unfortunate, Figure~\ref{fig:fulllc} shows that
+While the data gap is unfortunate, Figure~\ref{fig:fulllc} shows that
 both before and after the HIRES data were acquired, a large flux
@@
 closely resembling an asymmetric ``V'' than a ``W''.  Similar CPV state
-changes have been previously noted \citep{Stauffer2017,Bouma2024}.  The
+changes have been previously seen \citep{Stauffer2017,Bouma2024}.  The
 photometric shape therefore evolved during the twelve cycles spanning
 the 3356-3358 gap, since the average shape from 3358-3363 more closely
-resembles the initial ``W''.  Nonetheless, the general photometric
+resembles the initial ``W''.  Nonetheless, the global photometric
 morphology---a small brightening over 45\% of the period, followed by a
@@
 
-Figure~\ref{fig:spec} compiles the TESS and HIRES data from February
-2024.  The HIRES spectra \added{(Panels b,c,e,f)} show emission in H$\alpha$ beyond the star's
-equatorial velocity, $v_{\rm eq}$, of 130\,\kms.  There are at least
-two distinct emission components, separated by 180$^\circ$ in phase.
-The inner component at lower velocities has clearer sinusoidal
-behaviour in time and is double-peaked, with peak semi-amplitudes of
-2.07\,$v_{\rm eq}$ and 2.88\,$v_{\rm eq}$, measured following the
-procedure in Appendix~\ref{subsec:halpha}.  There is significant
-non-periodic variability in the emissivity of this double-peaked
-component: the flux excess begins with an amplitude 70\% that of the
-continuum, and diminishes to 10\% by the end.  The higher-velocity
-component 180$^\circ$ opposite in phase is detected only from
-$\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this outer component appears
-connected to the star in velocity space.  While its peak
+Figure~\ref{fig:spec} shows the TESS and HIRES data from February
+2024.  The spectra \added{(Panels b,c)} show emission in
+H$\alpha$ beyond the star's equatorial velocity, $v_{\rm eq}$, of
+130\,\kms.  There are at least two distinct emission components,
+180$^\circ$ apart in phase.  The inner component at lower
+velocities has clearer sinusoidal behaviour in time and is
+double-peaked, with peak semi-amplitudes of 2.07\,$v_{\rm eq}$ and
+2.88\,$v_{\rm eq}$ (see Appendix~\ref{subsec:halpha}).  There
+is significant non-periodic variability in the emissivity of this
+double-peaked component: the flux excess begins with an amplitude 70\%
+above the continuum, and diminishes to 10\% by sunrise.  The
+higher-velocity component 180$^\circ$ opposite in phase is detected
+only from $\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this outer component
+appears connected to the star in velocity space.  While its peak
 semi-amplitude of 3.88\,$v_{\rm eq}$ is achieved at both $\phi$=0.25
-and 0.75, its amplitude similarly decreases from a 60\% excess over
-the continuum at the beginning of the observation sequence to a 10\%
-excess by its end.  
-From the same procedure in Appendix~\ref{subsec:halpha},
-we measured
-the period for all three spectroscopic
-emission components to be consistent with the photometric \periodhr\ hour
-period, to within two minutes for the lower-velocity component.
+and $\phi$=0.75, its amplitude similarly decreases from a 60\% excess 
+to a 10\% excess over the observation sequence.  In
+Appendix~\ref{subsec:halpha}, we measured the period for all three
+emission components to be consistent with the
+photometric \periodhr\ hour period, to within two minutes for the
+\added{inner} component.
 
@@
 partially-ionized hydrogen to corotate with the star.  Based on the
-observed sinusoidal periods and velocities, this material's motion is
-not controlled by gravitational attraction to the star; it is 
-a plasma being dragged along with a rigidly rotating stellar magnetic
-field.  The velocity semi-amplitude of the sinusoids gives the mean
-distance of each clump from the stellar \added{rotation axis}: 2.07\,$R_\star$ and
-2.88\,$R_\star$ for the inner clumps, and 3.88\,$R_\star$ for the outer
-clump.   These clumps transit in front of the star when passing from
-negative to positive velocity.  The transits of the two inner clumps
-last $\approx$22\% of each cycle, from $\phi$=-0.1 to $\phi$=+0.12 (see
-Appendix~\ref{subsec:halpha}).  This spectroscopic transit coincides
-with the latter half of the complex eclipse feature in the TESS data
-\added{(see Figure~\ref{fig:fulllc} and Panels a and b of Figure~\ref{fig:spec})}.
+observed sinusoidal periods and velocities, this \added{material is
+not moving on a Keplerian orbit}; it is \added{magnetically forced to
+co-rotate with the star}.  The velocity
+semi-amplitude of the sinusoids gives the mean distance of each clump
+from the stellar \added{rotation axis}: 2.07\,$R_\star$ and
+2.88\,$R_\star$ for the inner clumps, and 3.88\,$R_\star$ for the
+outer clump.   These clumps transit in front of the star when passing
+from negative to positive velocity.  The transits of the two inner
+clumps last $\approx$22\% of each cycle, from $\phi$=-0.1 to
+$\phi$=+0.12.  This spectroscopic
+transit coincides with the latter half of the complex eclipse feature
+in the TESS data \added{(see Figure~\ref{fig:fulllc} and Panels a and
+b of Figure~\ref{fig:spec})}.
 
@@
 eq}|<1$, most observed H$\alpha$ photons come from the star's
-chromosphere; circumstellar material might also modulate the line
-profile.  Figure~\ref{fig:spec}e suggests line core variability caused
-by both bright and dark regions on the star's surface, superposed with
-smaller-amplitude variability from the transiting circumstellar
-material.  For instance, from $\phi$=0-0.3, the double-peaked emission
-feature is visible when viewed both on and off-limb; this feature is
-circumstellar in origin.  However, the large emission feature that
-crosses the star from $\phi$=0.4-0.9 emits at an amplitude greater
-than that observed from the circumstellar components, and it crosses
-the stellar velocity surface at a speed that suggests it instead
-originates from a chromospherically bright region on the star's
-surface.  Similarly, from $\phi$=0.6-1.15 a 20\% deep absorption
-feature slowly crosses the H$\alpha$ line profile.  This feature
-suggests either a chromospherically dark region (e.g.~a starspot
-group) crossing the star's surface, or an azimuthally extended
-absorptive component to the circumstellar material which is not
-visible in emission.  The origin of the other bright and dark
-streaks passing across the line core \added{in Figure~\ref{fig:spec}e
-}are similarly ambiguous.  \added{Figure~\ref{fig:spec}d shows} a
-final exercise to quantify the behavior of the line core, where
-$f_{\rm H\alpha\ core}$ denotes the summed \added{H$\alpha$} flux at
-$|\Delta v / v_{\rm eq}|<1$.  This panel shows that changes in the
-line core flux correlate with the broadband variability throughout
-most of the light curve, except near $\phi$$\approx$0.5, corresponding
-to the transit of the 3.9\,$R_\star$ clump and the occultation of the
-lower-velocity clump.  \added{Spectroscopic transits therefore do not
-necessarily yield photometric transits.}
+chromosphere; \added{variability in the stellar emission line can be caused
+by circumstellar material, bright regions, or dark regions
+crossing the star's surface}. 
+Figure~\ref{fig:spec}e suggests that \added{all three effects occur in
+TIC\,141146667}.
+For instance, from $\phi$=0-0.3, double-peaked emission is visible
+both on and off-limb; this feature is circumstellar in origin.
+However, the emission feature that crosses the star from
+$\phi$=0.4-0.9 is brighter than the circumstellar clumps, and its slow
+speed instead suggests it is associated with bright region on the
+star's surface.  Similarly, from $\phi$=0.6-1.15 a 20\% deep
+absorption feature slowly crosses the H$\alpha$ line profile.  This
+feature could be either a chromospherically dark region (e.g.~a spot
+group), or an azimuthally extended component of the circumstellar
+material.  The origin of the other bright and dark streaks passing
+across the line core \added{in Figure~\ref{fig:spec}e }are similarly
+ambiguous.
+
+\added{Figure~\ref{fig:spec}d shows} a final exercise to
+quantify the behavior of the line core, 
+by summing the \added{H$\alpha$} flux at $|\Delta v / v_{\rm
+eq}|<1$.  This panel shows that changes in the line core flux
+\added{($f_{\rm H\alpha\ core}$)} correlate with the broadband
+variability throughout most of the light curve, except near
+$\phi$$\approx$0.5, corresponding to the transit of the 3.9\,$R_\star$
+clump and the occultation of the lower-velocity clump.
+\added{Spectroscopic transits may therefore not always be associated
+with photometric transits.}
 
@@
 
-While the H$\alpha$ emission seems to mostly originate from clumps, the
-complex flux dip in TIC\,141146667 spans roughly half of each cycle; in
-CPVs more broadly, individual dips can last 5-50\% of each cycle, and
-they are often distributed in longitude \citep{Bouma2024}.  This raises
-the possibility that azimuthally-distributed material may be the norm
-for CPVs, and that a warped torus may be a more accurate picture than a
-clump.
+While the H$\alpha$ emission seems to mostly originate from clumps,
+the complex flux dip in Figure~\ref{fig:spec} spans roughly half of
+each cycle; in CPVs more broadly, individual dips can last 5-50\% of
+each cycle \citep{Bouma2024}.  This implies that
+azimuthally-distributed material may be the norm for CPVs; a warped
+torus may be a more accurate picture than a clump.
 
@@
 the magnetospheric radii $R_{\rm m}$ of such stars exceeds their
-Keplerian corotation radii $R_{\rm c}$, the effective potential
-experienced by charged particles \added{along any given field line
-}has a local minimum outside $R_{\rm c}$, which enables charged
-material to accumulate in a torus.  Warps can occur when there is
-misalignment between the spin and magnetic axes.  In general,
-the\added{ regions} in these centrifugally-supported
+Keplerian corotation radii $R_{\rm c}$, the effective potential\added{
+  (gravitational plus centrifugal)} experienced by \added{plasma
+along any given field line }has a local minimum outside $R_{\rm c}$,
+which enables charged material to accumulate in a torus.  Warps can
+occur when there is misalignment between the spin and magnetic axes.
+In general, the\added{ regions} in these centrifugally-supported
 magnetospheres\added{ with the densest plasma accumulations} need
@@
 
-To summarize, the lines of evidence in favor of warped plasma tori for
-TIC\,141146667 and CPVs more generally are that {\it i)}
+To summarize, the evidence for warped plasma tori
+in TIC\,141146667 and CPVs more broadly is that {\it i)}
 Figure~\ref{fig:spec} shows two emitting plasma clumps separated
 180$^\circ$ in phase, with double-peaked H$\alpha$ morphology at
-quadrature; {\it ii)} the ``W'' shaped photometric eclipses are
+quadrature; {\it ii)} ``W'' shaped photometric eclipses are
 predictions of such a model; {\it iii)} CPV dips last 5-50\% of each
-cycle, suggesting an extended azimuthal distribution of circumstellar
-material.
+cycle, suggesting an azimuthally-extended distribution of circumstellar
+material.  \added{Two key challenges however are that the warped torus
+model predicts two W-shaped eclipses per cycle, and it also predicts
+that the antipodal clumps should be equidistant from the star.
+Plausible resolutions could invoke different opacities for each clump, 
+and non-dipolar stellar magnetic fields.
+Generally, the evidence seems to support a warped torus as a
+reasonable first approximation, which we hope will be refined by
+future efforts.}
 
@@
 the broadband chromatic flux variations seen in CPVs.  The
-alternative idea is that charged dust could provide most of the
+alternative is that charged dust could provide most of the
 opacity \citep{Sanderson2023}.  For
 TIC\,141146667, Figures~\ref{fig:fulllc}
-and~\ref{fig:spec} show that the transits of the H$\alpha$ emitting
-material only partially overlap the complex photometric modulation.
-This implies that some of the complex photometric dips must involve
-additional opacity sources or spatially distinct structures.
+and~\ref{fig:spec} show that the transits of the 
+inner H$\alpha$ clump only partially overlap the complex
+photometric modulation.  This implies that some of the complex
+photometric dips must involve additional opacity sources or spatially
+distinct structures.
 
@@
 H$\alpha$ spectra similar to those in Figure~\ref{fig:spec}.  The two
-known exceptions, HD~37776 and HD~64740, show complex light curves
-resembling CPVs \citep{Mikulasek2020,Bouma2024} and have
-spectropolarimetric magnetic field maps indicating strong contributions
-from higher-order magnetic moments \citep{Kochukhov2011,Shultz2018}.
+known exceptions, HD~37776 and HD~64740, 
+have spectropolarimetric magnetic field maps indicating strong
+contributions from higher-order magnetic moments
+\citep{Kochukhov2011,Shultz2018} and complex light curves
+resembling CPVs \citep{Mikulasek2020,Bouma2024}.
 This suggests that the photometric complexity of CPVs may be related to
 magnetic fields with highly multipolar contributions.  
+\added{While this suggestion is consistent with the wide range of
+axisymmetric and non-axisymmetric topologies seen in mid- and late-M
+dwarfs
+(e.g.~\citealt{Donati2006,Kochukhov2017,Shulyak2019,Bellotti2024}),
+future work is needed to verify whether CPVs indeed select for
+complex, non-axisymmetric fields.}
 
@@
 the close-in rocky exoplanets that, statistically \citep{Dressing2015},
-are likely to be present in most CPV systems.
+are likely to be present in many CPV systems.
 
@@
 with dust \citep{Tanimoto2020,Gunther2022,Koen2023}, electron
-scattering in a plasma transiting over a spotted background star might
+scattering in a plasma transiting over a spotted star might
 also produce chromatic features \citep{Rackham2018}.  \added{This
@@
 currently explain the H$\alpha$ features \citep[e.g.][]{Waugh2022}
-would be to incorporate an opacity source that can also reproduce the
-photometric dips.  It is likely that this effort will require
+would be to incorporate an opacity source that can reproduce the
+photometric dips.  This effort will also require
 exploring what stellar magnetic field topologies reproduce the
-observed light curve shapes \citep[e.g.][]{Bouma2024}. While previous
+observed light curve shapes.  While previous
 models in the rigid-field approximation have explored both dipolar
@@
 global-scale mean fields might be confined to a single hemisphere
-\citep{Brown2020}; such fields would yield accumulation surfaces quite
+\citep{Brown2020}; such fields would yield accumulation surfaces 
 different from those that have been explored.  One related challenge
@@
 measurements, unlike benchmark systems such as AB Dor and V374~Peg
-\citep{Jardine2002,Vidotto2011}. This might be alleviated through
-future spectropolarimetric observations, or from radio observations
+\citep{Jardine2002,Vidotto2011}. This might be alleviated by
+future spectropolarimetry, or by radio observations
 sensitive to the magnetic field structure around the star
-\citep[see][]{Callingham2021,Kaur2024}.  Finally, the question of what
+\citep[][]{Callingham2021,Kaur2024}.  Finally, the question of what
 microphysical process yields the opaque material also merits future
@@
 hot corona \citep{Daley-Yates2023,Daley-Yates2024}, a self-consistent
-treatment of radiation propagating through such clumps remains to be
-performed. The question of whether dust grains can nucleate in such
-clumps, or whether they need to be externally sourced, deserves
-careful attention.}
+treatment of radiation propagating through such clumps has yet to be
+performed. Whether dust grains can form in these plasma clumps
+similarly deserves attention.}
 
@@
 the complex photometric features occur when clumps of circumstellar
-material transit the star.  The suggested geometric correction implies
-that an appreciable minority ($\gtrsim$10\%) of young M dwarfs -- the
-rapidly rotating ones with centrifugal magnetospheres -- host
+material transit the star.  The geometric correction implies
+that an appreciable minority ($\gtrsim$10\%) of young M dwarfs---the
+rapidly rotating ones with centrifugal magnetospheres---host
 circumstellar environments similar to the CPVs.  Future studies that
@@
 
-	The analyses in this article used data from TESS; the specific
-	2-minute cadence observations can be accessed \added{through MAST }via
+  The analyses in this article used data from TESS.  \added{The 2-minute
+  cadence observations from Sectors 41 \& 48 were from TESS DDT039
+  (PI: M.~Kunimoto) and the observations from Sector 75 were from TESS
+  G06030 (PI: L.~Bouma).}
+  The TESS data
+  can be accessed \added{through MAST }via
 	DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
@@
   We recognize the importance that the summit of Maunakea has always had
-  within the indigenous Hawaiian community, and we are deeply grateful 
+  within the indigenous Hawaiian community, and we are grateful 
   for the opportunity to conduct observations from this mountain.
@@
 magnitude as TIC\,141146667.  Previous work by \citet{Stauffer2021} has
-also noted that in the Gaia passbands, CPVs tend to be photometrically
+noted that in the Gaia passbands, CPVs tend to be photometrically
 redder and more luminous than single stars in any given
@@
 young M dwarfs show the 6707.8\,\AA\ doublet in absorption,
-$\gtrsim$10\% below their continua.  However unlike for Sun-like
+$\gtrsim$10\% below their continua.  However, unlike for Sun-like
 stars, the continuum for M dwarfs is challenging to define due to
@@
 parameters at each spectral epoch: the mean $\mu$, standard deviation
-$\sigma$, and amplitude $A$.  We labelled the inner component's two
+$\sigma$, and amplitude $A$.  We labeled the inner component's two
 gaussians $i=\{ 0, 1 \}$, and the single outer component as $i=2$.
@@
 detect or else adequately represent the circumstellar emission.  We
-then used NumPyro to sample the Gaussian likelihood for a Keplerian
+then used NumPyro to sample the Gaussian likelihood for a circular
 orbit with the NUTS algorithm \citep{Phan2019}.  We used the

### 2025-05-28 paper/ms.tex
update

@@
 spectra require plasma with a significant population of hydrogen in the
-$n$=3 excited state, with minimal evidence for higher-order excitations
-(see Appendix~\ref{subsec:specvar}).  Most of this H$\alpha$ emission
-originates in ``clumps'' with size comparable to the star; radial
-``spokes'' or azimuthally-extended ``arcs'' for the emitting material
-are ruled out by the $\approx$30\,\kms\ H$\alpha$ velocity dispersion
-(see Appendix~\ref{subsec:halpha}).  The H$\alpha$ line luminosity
-suggests characteristic number densities and masses for the gaseous
-component of these clumps of $n_{\rm H} \sim 10^{11}$\,cm$^{-3}$ and
-$M_{\rm gas} \sim 10^{17}$\,g (see Appendix~\ref{subsec:gas}).  Dust is
+$n$=3 excited state, \added{with }minimal evidence for
+higher-order excitations.  Most of this H$\alpha$ emission originates
+in ``clumps'' with size comparable to the star; radial ``spokes'' or
+azimuthally extended ``arcs'' for the emitting material are ruled out
+by the $\approx$30\,\kms\ H$\alpha$ velocity dispersion (see
+Appendix~\ref{subsec:halpha}).  The H$\alpha$ line luminosity suggests
+characteristic number densities and masses for the gaseous component
+of these clumps of $n_{\rm H} \sim 10^{11}$\,cm$^{-3}$ and $M_{\rm
+gas} \sim 10^{17}$\,g (see Appendix~\ref{subsec:gas}).  Dust is
 independently constrained to have a total mass $M_{\rm dust} <
 10^{17}\,{\rm g}$ based on the lack of a WISE infrared excess; if one
-assumes that the opacity in the TESS flux dips comes from dust, a lower
-limit $M_{\rm dust} > 10^{15}\,{\rm g}$ follows (see
+assumes that the opacity in the TESS flux dips comes from dust, a
+lower limit $M_{\rm dust} > 10^{15}\,{\rm g}$ follows (see
 Appendix~\ref{subsec:dust}).
@@
 
-While the H$\alpha$ emission seems to mostly originate from clumps,
-the complex flux dip in Figure~\ref{fig:spec} spans roughly half of
-each cycle; in CPVs more broadly, individual dips can last 5-50\% of
-each cycle \citep{Bouma2024}.  This implies that
+While the H$\alpha$ emission mostly comes from clumps,
+the broadband flux dip in Figure~\ref{fig:spec} spans roughly half of
+each cycle.  In CPVs more generally, individual flux dips last 5-50\% of
+each cycle\added{, and there are often multiple dips per cycle }\citep{Bouma2024}.  This implies that
 azimuthally-distributed material may be the norm for CPVs; a warped
@@
 To summarize, the evidence for warped plasma tori
-in TIC\,141146667 and CPVs more broadly is that {\it i)}
-Figure~\ref{fig:spec} shows two emitting plasma clumps separated
-180$^\circ$ in phase, with double-peaked H$\alpha$ morphology at
-quadrature; {\it ii)} ``W'' shaped photometric eclipses are
-predictions of such a model; {\it iii)} CPV dips last 5-50\% of each
-cycle, suggesting an azimuthally-extended distribution of circumstellar
-material.  \added{Two key challenges however are that the warped torus
-model predicts two W-shaped eclipses per cycle, and it also predicts
-that the antipodal clumps should be equidistant from the star.
-Plausible resolutions could invoke different opacities for each clump, 
-and non-dipolar stellar magnetic fields.
-Generally, the evidence seems to support a warped torus as a
-reasonable first approximation, which we hope will be refined by
-future efforts.}
+in TIC\,141146667 and CPVs more broadly is that 
+Figure~\ref{fig:spec} shows two plasma clumps separated
+by 180$^\circ$ in phase; the warped-torus model predicts both
+``W'' shaped photometric eclipses and double-peaked H$\alpha$
+morphology at quadrature; and CPV dips last 5-50\% of each cycle,
+indicating an azimuthally extended distribution of material.
+\added{However, two challenges remain. First, the model predicts {\it
+two} W-shaped eclipses per cycle.  Second, it predicts that the
+antipodal clumps should lie at equal distances from the star.
+Different clump opacities or non-dipolar magnetic fields might resolve
+these discrepancies.  Overall, the evidence suggests a warped torus is
+a good first approximation---one that will need refinement in future
+work.}
 
@@
 
-The other analog for the CPVs are the $\sigma$~Ori~E variables, a rare
-subset of B stars with radiatively-driven winds which accumulate into
+The other CPV analog is the $\sigma$~Ori~E variables, a rare
+subset of B stars with radiatively-driven winds that accumulate into
 warped plasma tori \citep{Townsend2005}.  These tori tend
 to have dense antipodal accumulations of plasma sculpted by
-tilted-dipole magnetic fields, and the transits of these clumps produce
-broadband photometric variability through bound-free scattering
+tilted-dipole magnetic fields; these clumps produce
+broadband optical variability through bound-free scattering
 \citep{Townsend2005} and Thomson scattering \citep{Berry2022}.  For
-$\sigma$~Ori~E and almost all of its analogs, the result is simple
-light curves that resemble those of eclipsing binaries, and time-dynamic
-H$\alpha$ spectra similar to those in Figure~\ref{fig:spec}.  The two
+$\sigma$~Ori~E and most of its analogs, the result is simple
+light curves that resemble eclipsing binaries, and time-dynamic
+H$\alpha$ spectra similar to Figure~\ref{fig:spec}.  The two
 known exceptions, HD~37776 and HD~64740, 
@@
 {\it Radial Velocity}---We measured the radial velocities of
-TIC\,141146667 from our HIRES spectra using a pipeline that we
-developed for rapidly rotating stars.  Our method is based on
-template-matching against synthetic spectra produced by the PHOENIX
-stellar atmosphere code \citep{Husser2013}.  We used the PHOENIX models
-with solar metallicity and alpha element abundances, and calibrated
-our pipeline using the standard stars described by \citet{Chubak2012}.
-We used velocity standards spanning spectral types from G2 to M4
-(Barnard's Star), irrespective of rotation rate.  We used
-\texttt{barycorrpy} \citep{Kanodia2018} to calculate the velocity
-corrections due to Earth's motion around the solar system barycenter
-and due to Earth's daily rotation about its axis.  Our analysis code
-reproduces the systemic velocities of known velocity standards
-\citep{Chubak2012} with an RMS of 0.66\,\kms.
+TIC\,141146667 from our HIRES spectra using a \added{custom }pipeline.
+Our method is based on template-matching against synthetic
+\added{PHOENIX }spectra \citep{Husser2013}, \added{and is }calibrated
+\added{against }the standard stars described by \citet{Chubak2012}.
+We used velocity standards spanning G2-M4, irrespective of rotation
+rate.  We included velocity corrections due to Earth's motion around
+the solar system barycenter and due to Earth's daily rotation about
+its axis, calculated using \texttt{barycorrpy} \citep{Kanodia2018}.
+Our analysis code reproduces the systemic velocities of known velocity
+standards \citep{Chubak2012} with an RMS of 0.66\,\kms.
 
@@
 $\gamma$=0.6$\pm$1.5\,\kms.  The relative radial velocities about this
-mean are given in Table~\ref{tab:rv}.
+mean are listed in Table~\ref{tab:rv}.
 
@@
 periods in the TESS data.  Previous work \citep{Bouma2024} has shown
-that about 30\% of CPVs show evidence for excess noise above the Gaia
-single-source astrometric model, and about 40\% of CPVs show evidence
-for unresolved binary companions based on the presence of secondary
-photometric periods.  This agrees with analyses showing that
+that $\approx$30\% of CPVs show evidence for excess noise above the
+Gaia single-source astrometric model, and $\approx$40\% of CPVs show
+evidence for unresolved binary companions based on the presence of
+secondary photometric periods.  This agrees with analyses showing that
 multi-periodic low-mass stars are generally unresolved binaries
@@
 to a weak or non-existent connection between the CPV phenomenon and
-(wide) binarity.  For TIC\,141146667 specifically, although we find no
-evidence for stellar multiplicity, our data are minimally constraining
-for the scenario of a low-luminosity companion
-($F_1$/$F_2$$\lesssim$0.1) with apparent separation below 0$\farcs$1.
+(wide) binarity.  For TIC\,141146667 specifically, we find no
+evidence for stellar multiplicity. %, our data are minimally constraining
+%for the scenario of a low-luminosity companion
+%($F_1$/$F_2$$\lesssim$0.1) with apparent separation below 0$\farcs$1.
 
@@
 procedure described by \citet{Bouma2024}.  To summarize, this approach
-used \texttt{astroARIADNE} \citep{Vines2022} with the BT-Settl stellar
-atmosphere models \citep{Allard2012}, assuming the \citet{Asplund2009}
-solar abundances and the \citet{Barber2006} water line lists.  This
-approach fitted for the stellar effective temperature, radius,
-reddening, surface gravity, metallicity, and distance by comparing the
-measured broadband magnitudes against pre-computed model grids.
-Specifically, we performed the fit using the broadband magnitudes from
-Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting
-best-fit SED is shown in Figure~\ref{fig:sed}.
-This method has the most constraining power for the star's effective
-temperature (2972 $\pm$ 40\,K) and radius (0.42 $\pm$
-0.02\,$R_\odot$); the surface gravity, metallicity, and reddening are
-only weakly constrained.  We determined the star's spectral type to be
-M5.5Ve by visually comparing the HIRES spectra against the photometric
-standards tabulated by \citet{Bochanski2007}.   This result agrees with
-the effective temperature found from the SED fitting
-\citep{Pecaut2013}.  We measured the equivalent width of the H$\alpha$
-line by fitting a range of models to the time-averaged line profile
-shown in Figure~\ref{fig:spec}, selecting the model that minimized the
-Bayesian information criterion, and numerically integrating this best
-fit model.  We found a sum of two Gaussians to be the preferred model;
-our quoted result, EW$_{{\rm H}\alpha}$=7.2$\pm$0.2\,\AA, comes from
-numerically integrating within $|\Delta v/v_{\rm eq}|<1$.  Integrating
-over the entire line profile, including the broad wings, would yield
-EW$_{{\rm H}\alpha}$=10.2$\pm$0.3\,\AA. Either value would classify
-the star as a weak-lined T Tauri \citep{Briceno2019}.
+used \texttt{astroARIADNE} \citep{Vines2022} \added{to fit broadband magnitudes
+from Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$ with the
+BT-Settl stellar atmosphere models \citep{Allard2012}}.  \added{Free
+parameters included } the stellar effective temperature, radius,
+reddening, surface gravity, and metallicity.  The resulting best-fit
+SED is shown in Figure~\ref{fig:sed}.  This method has the most
+constraining power for the star's effective temperature (2972 $\pm$
+40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$).  We measured
+the star's spectral type to be M5.5Ve by visually comparing the HIRES
+spectra against the photometric standards tabulated by
+\citet{Bochanski2007}.   We measured the equivalent width of the
+H$\alpha$ line by fitting a range of models to the time-averaged line
+profile shown in Figure~\ref{fig:spec}, selecting the model that
+minimized the Bayesian information criterion, and numerically
+integrating this best fit model.  We found a sum of two Gaussians to
+be preferred; our quoted result, EW$_{{\rm
+H}\alpha}$=7.2$\pm$0.2\,\AA, comes from numerically integrating within
+$|\Delta v/v_{\rm eq}|<1$.  Integrating over the entire line profile,
+including the broad wings, would yield EW$_{{\rm
+H}\alpha}$=10.2$\pm$0.3\,\AA. Either value would classify the star as
+a weak-lined T Tauri \citep{Briceno2019}.
 
@@
 (35-150\,Myr) derived below, we then estimated the stellar mass by
-interpolating against the PARSEC v1.2S isochrones \citep{Chen2014}.
-Specifically, we used the distance metric defined in Equation~8 of
-\citet{Bouma2024} to select the model mass closest to a given observed
-temperature, radius, and age.  This exercise yielded a mass of
+interpolating against the PARSEC v1.2S isochrones \citep{Chen2014}, as
+in \citet{Bouma2024}.  This exercise yielded a mass of
 $M_\star$=$0.20\pm0.01$\,$M_\odot$ assuming an age of 35\,Myr, or a
@@
 cr}/R_\star$=1.75$\pm$0.07 and $R_{\rm cr}/R_\star$=1.89$\pm$0.07,
-respectively; this size scale is relevant because it is theoretically
-expected to set the inner boundary at which corotating material might
-accumulate (e.g.~\citealt{Townsend2005,Daley-Yates2024}).  Our final
-quoted $M_\star$ and $R_{\rm cr}$ values adopt the average of these
-extremes and a quadrature sum of their statistical uncertainties; we
-caution however that a more precise age would be needed to resolve the
-systematic uncertainties in these parameters.
+respectively; this size scale is expected to set the inner boundary at
+which corotating material might accumulate
+(e.g.~\citealt{Townsend2005,Daley-Yates2024}).  Our final quoted
+$M_\star$ and $R_{\rm cr}$ values adopt the average of these extremes
+and a quadrature sum of their statistical uncertainties; a more
+precise age would be needed to resolve the systematic uncertainties in
+these parameters.
 
@@
 
-{\it Age: Lithium}---The depletion of lithium due to $^7$Li(p,
-$\alpha$)$^4$He burning in the cores of low-mass stars has been
+{\it Age: Lithium}---Lithium burning in the cores of low-mass stars has been
 studied for over sixty years
-\citep{Hayashi1963,Bildsten1997,Burke2004}.  \citet{Wood2023} provided a
-recent overview: an abbreviated summary is that sufficiently cool and
+\citep[e.g.][]{Hayashi1963,Bildsten1997}.  \citet{Wood2023} provided a
+recent overview; the brief summary is that sufficiently cool and
 young M dwarfs show the 6707.8\,\AA\ doublet in absorption,
@@
 measurement by constructing a wavelength-binned and Doppler-corrected
-TIC\,141146667 spectrum, assigning its uncertainties based on the
+TIC\,141146667 spectrum, and assigned its uncertainties based on the
 measured scatter across the five hour dataset.  We then compared this
@@
 expected lithium wavelength, potentially consistent with the $\Delta
-\lambda$$\approx$3\,\AA\ line broadening.  This feature nominally
+\lambda$$\approx$3\,\AA\ line broadening.  This feature 
 yields ${\rm EW}_{\rm Li}$=71$^{+18}_{-13}$\,m\AA, where the
@@
 technique from the statistical uncertainties in the HIRES spectrum.
-However, the systematic uncertainties associated with the continuum
-normalization are likely comparable to the amplitude of this feature;
-we therefore treat the result of this measurement as a $2\sigma$ upper
+However, the systematic uncertainty associated with the continuum
+normalization is likely comparable to the amplitude of the feature;
+we therefore treat this measurement as a $2\sigma$ upper
 limit: ${\rm EW}_{\rm Li}$$<$107\,m\AA.
 
-Despite ambiguity in the details, what can be stated with
-confidence is that lithium is not abundant in the spectrum of
-TIC\,141146667.  Figure~\ref{fig:age_diagnostics}
+What can be stated with confidence is that lithium is not abundant in
+the spectrum of TIC\,141146667.  Figure~\ref{fig:age_diagnostics}
 compares our upper limit against the equivalent width measurements
 reported by \citet{Jeffries2023} based on the Gaia-ESO spectroscopic
-survey; Figure~\ref{fig:hirescuts} shows the associated
-raw spectra.  If the star were $\lesssim$20\,Myr old, at its
-temperature we would expect to see lithium in abundance
-($>$400\,m\AA).  Since we do not, we can set an empirical bound on the
-lithium-derived age of $t_{\rm Li,emp}$$\gtrsim$20\,Myr.  The
-\citet{Feiden2016} lithium isochrones provide a point for theoretical
-comparison, and suggest that since $M_{\rm K}$$\approx$6.67\,mag,
-$t_{\rm Li,th}$$\gtrsim$35\,Myr is the theoretical age at which
-complete depletion occurs in a star with this luminosity (see
-e.g.~Figure 7 from \citealt{Wood2023}).
+survey.  If the star were $\lesssim$20\,Myr old, at its temperature we
+would expect to see lithium in abundance ($>$400\,m\AA).  Since we do
+not, we can set an empirical bound on the lithium-derived age of
+$t_{\rm Li,emp}$$\gtrsim$20\,Myr.  The \citet{Feiden2016} lithium
+isochrones provide a point for theoretical comparison, and suggest
+that since $M_{\rm K}$$\approx$6.67\,mag, $t_{\rm
+Li,th}$$\gtrsim$35\,Myr is the theoretical age at which complete
+depletion occurs in a star with this luminosity (see e.g.~Figure 7
+from \citealt{Wood2023}).
 
@@
 resulting parameter covariance matrix by a constant factor to match
-the sample variance of the residuals.  The resulting means,
-amplitudes, and standard deviations for each component are given in
-Table~\ref{tab:halphamodelparams}.
+the sample variance of the residuals.
+\added{The results are shown in the middle columns of
+Figure~\ref{fig:halphamodel}, and a table of the fitted means,
+amplitudes, and standard deviations for each component is available
+upon request.}
 
@@
 
-Accounting for these caveats, we used the results from
-Table~\ref{tab:halphamodelparams} to quantify the orbital periods and
+Accounting for these caveats, we used the \added{best-fit parameters
+from the multi-gaussian model }to quantify the orbital periods and
 velocity semi-amplitudes of the clumps.  Figure~\ref{fig:orbits}a
@@
 
-\section{Spectroscopic Variability}
-\label{subsec:specvar}
-
-\begin{figure*}[!t]
-  \centering
-  \includegraphics[width=\textwidth]{f8.pdf}
-  \vspace{-0.5cm}
-  \caption{{\bf Time evolution of the Keck/HIRES spectra
-  from 17 February 2024.}  We made this plot by applying a windowed
-  outlier rejection to remove cosmic rays and then smoothing each
-  spectrum with a Gaussian filter.  The horizontal axis shows the
-  velocity relative to each line's rest wavelength, normalized by the
-  stellar equatorial velocity.  H$\alpha$ is the only Balmer line to
-  show periodic variability similar to Figure~\ref{fig:spec}.
-	The He 5876\,\AA\ line shows a time-dynamic blueshift.  Li 6708\,\AA\ shows
-	no obvious absorption. }
-  \label{fig:hirescuts}
-\end{figure*}
-
-Figure~\ref{fig:hirescuts} shows a few regions of
-interest in the HIRES spectra, which cover 3650-7960\,\AA.  
-H$\beta$ falls in an inter-order gap and was not observed.
-Higher order Balmer lines including H$\gamma$ and H$\delta$
-($n=5\rightarrow2$ and $n=6\rightarrow2$) do show variability outside
-the line core.  However, this variability is not clearly periodic in the
-same manner as the emission seen in H$\alpha$.  This could be because
-there are insufficient hydrogen atoms in the relevant excited states, or
-because the spectra have lower precision in these bluer regions.  The Ca
-HK doublet is also detected in emission, while the continuum near it is
-not.  Chromospheric emission from the magnesium triplet is also
-detected, but these lines are too blended to be usable.
-
-Figure~\ref{fig:hirescuts} provides a novel view on the
-blue excess that appeared at $\phi$$\approx$0.2 in H$\alpha$,
-H$\gamma$, H$\delta$, and He 5876\,\AA.  At the same epoch, H$\alpha$
-additionally shows a red clump of emission, and H$\gamma$ and
-H$\delta$ are also broadened on the red wing.  The rise of this
-emission in $<$15\,minutes might suggest a more sudden flow, rather
-than a stable, periodic component.  For instance, a stellar flare
-might be connected to such a sudden rise.  However, this idea seems
-incompatible with the sinusoidal emission seen from
-$\phi$$\approx$0.3-1.0, and with the fact that flares typically excite
-iron lines in the blue HIRES orders, which are not observed.  More
-time-series spectroscopy would be needed to clarify this type of
-variability, in particular whether it is periodic or stochastic.
-The gap in the TESS photometry (Figure~\ref{fig:fulllc}) additionally
-clouds the interpretability of this event.
-
-Finally, the Li\,\textsc{I} 6708\,\AA\ region, which shows no obvious
-absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ resonance
-line are both visible in Figure~\ref{fig:hirescuts}.  In
-the latter, narrow telluric absorption features overlap the blue wing
-of the line.  Neither of these regions shows any notable variability.
+%  \section{Spectroscopic Variability}
+%  \label{subsec:specvar}
+%  
+%  \begin{figure*}[!t]
+%    \centering
+%    \includegraphics[width=\textwidth]{f8.pdf}
+%    \vspace{-0.5cm}
+%    \caption{{\bf Time evolution of the Keck/HIRES spectra
+%    from 17 February 2024.}  We made this plot by applying a windowed
+%    outlier rejection to remove cosmic rays and then smoothing each
+%    spectrum with a Gaussian filter.  The horizontal axis shows the
+%    velocity relative to each line's rest wavelength, normalized by the
+%    stellar equatorial velocity.  H$\alpha$ is the only Balmer line to
+%    show periodic variability similar to Figure~\ref{fig:spec}.
+%  	The He 5876\,\AA\ line shows a time-dynamic blueshift.  Li 6708\,\AA\ shows
+%  	no obvious absorption. }
+%    \label{fig:hirescuts}
+%  \end{figure*}
+%  
+%  Figure~\ref{fig:hirescuts} shows a few regions of
+%  interest in the HIRES spectra, which cover 3650-7960\,\AA.  
+%  H$\beta$ falls in an inter-order gap and was not observed.
+%  Higher order Balmer lines including H$\gamma$ and H$\delta$
+%  ($n=5\rightarrow2$ and $n=6\rightarrow2$) do show variability outside
+%  the line core.  However, this variability is not clearly periodic in the
+%  same manner as the emission seen in H$\alpha$.  This could be because
+%  there are insufficient hydrogen atoms in the relevant excited states, or
+%  because the spectra have lower precision in these bluer regions.  The Ca
+%  HK doublet is also detected in emission, while the continuum near it is
+%  not.  Chromospheric emission from the magnesium triplet is also
+%  detected, but these lines are too blended to be usable.
+%  
+%  Figure~\ref{fig:hirescuts} provides a novel view on the
+%  blue excess that appeared at $\phi$$\approx$0.2 in H$\alpha$,
+%  H$\gamma$, H$\delta$, and He 5876\,\AA.  At the same epoch, H$\alpha$
+%  additionally shows a red clump of emission, and H$\gamma$ and
+%  H$\delta$ are also broadened on the red wing.  The rise of this
+%  emission in $<$15\,minutes might suggest a more sudden flow, rather
+%  than a stable, periodic component.  For instance, a stellar flare
+%  might be connected to such a sudden rise.  However, this idea seems
+%  incompatible with the sinusoidal emission seen from
+%  $\phi$$\approx$0.3-1.0, and with the fact that flares typically excite
+%  iron lines in the blue HIRES orders, which are not observed.  More
+%  time-series spectroscopy would be needed to clarify this type of
+%  variability, in particular whether it is periodic or stochastic.
+%  The gap in the TESS photometry (Figure~\ref{fig:fulllc}) additionally
+%  clouds the interpretability of this event.
+%  
+%  
+%  Finally, the Li\,\textsc{I} 6708\,\AA\ region, which shows no obvious
+%  absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ resonance
+%  line are both visible in Figure~\ref{fig:hirescuts}.  In
+%  the latter, narrow telluric absorption features overlap the blue wing
+%  of the line.  Neither of these regions shows any notable variability.
 
@@
 recombination.  We neglect scattering because Figure~\ref{fig:spec}
-and Figure~\ref{fig:hirescuts} show the amplitude of the
+shows the amplitude of the
 circumstellar H$\alpha$ emission varying by a factor of $\approx$5, in
@@
 
-\begin{sidewaystable}
-  \footnotesize
-  \centering
-  \begin{tabular}{lccccccccc}
-  % from results/halpha_to_rv_timerseries/multigauss_parametertable.tex
-  \hline
-  BTJD & $\mu_0$ & $\mu_1$ & $\mu_2$ & $\sigma_0$ & $\sigma_1$ & $\sigma_2$ & $A_0$ & $A_1$ & $A_2$ \\
-  \hline
-  3357.960099 & -0.725 $\pm$ 0.028 & -1.416 $\pm$ 0.026 & 0.177 $\pm$ 0.019 & 0.39 $\pm$ 0.03 & 0.18 $\pm$ 0.03 & 0.59 $\pm$ 0.02 & 0.51 $\pm$ 0.01 & 0.23 $\pm$ 0.04 & 0.29 $\pm$ 0.01 \\
-  3357.970746 & -0.192 $\pm$ 0.007 & 0.498 $\pm$ 0.010 & 0.100 $\pm$ 0.014 & 0.23 $\pm$ 0.01 & 0.24 $\pm$ 0.01 & 0.55 $\pm$ 0.01 & 0.50 $\pm$ 0.01 & 0.37 $\pm$ 0.01 & 0.42 $\pm$ 0.01 \\
-  3357.981672 & 0.895 $\pm$ 0.051 & 1.771 $\pm$ 0.076 & -1.470 $\pm$ 0.113 & 0.40 $\pm$ 0.02 & 0.40 $\pm$ 0.10 & 0.09 $\pm$ 0.11 & 0.67 $\pm$ 0.05 & 0.34 $\pm$ 0.04 & 0.03 $\pm$ 0.03 \\
-  3357.993524 & 1.536 $\pm$ 0.011 & 2.202 $\pm$ 0.015 & -3.787 $\pm$ 0.049 & 0.25 $\pm$ 0.01 & 0.29 $\pm$ 0.01 & 0.72 $\pm$ 0.05 & 0.55 $\pm$ 0.01 & 0.46 $\pm$ 0.01 & 0.05 $\pm$ 0.00 \\
-  3358.003594 & 1.974 $\pm$ 0.007 & 2.588 $\pm$ 0.006 & -2.749 $\pm$ 0.020 & 0.26 $\pm$ 0.01 & 0.22 $\pm$ 0.00 & 1.00 $\pm$ 0.02 & 0.64 $\pm$ 0.01 & 0.67 $\pm$ 0.01 & 0.43 $\pm$ 0.01 \\
-  3358.015249 & 2.027 $\pm$ 0.003 & 2.666 $\pm$ 0.003 & -2.370 $\pm$ 0.015 & 0.24 $\pm$ 0.00 & 0.20 $\pm$ 0.00 & 1.00 $\pm$ 0.01 & 0.62 $\pm$ 0.00 & 0.60 $\pm$ 0.00 & 0.56 $\pm$ 0.00 \\
-  3358.024971 & 1.790 $\pm$ 0.004 & 2.469 $\pm$ 0.006 & -2.138 $\pm$ 0.011 & 0.24 $\pm$ 0.00 & 0.26 $\pm$ 0.00 & 0.77 $\pm$ 0.01 & 0.53 $\pm$ 0.00 & 0.38 $\pm$ 0.00 & 0.31 $\pm$ 0.00 \\
-  3358.036522 & 0.584 $\pm$ 0.008 & 1.399 $\pm$ 0.009 & -1.584 $\pm$ 0.009 & 0.18 $\pm$ 0.01 & 0.40 $\pm$ 0.01 & 0.89 $\pm$ 0.01 & 0.35 $\pm$ 0.01 & 0.39 $\pm$ 0.00 & 0.62 $\pm$ 0.00 \\
-  3358.047668 & 0.328 $\pm$ 0.014 & 0.685 $\pm$ 0.010 & -0.969 $\pm$ 0.017 & 0.07 $\pm$ 0.01 & 0.13 $\pm$ 0.01 & 0.46 $\pm$ 0.02 & 0.14 $\pm$ 0.02 & 0.28 $\pm$ 0.02 & 0.52 $\pm$ 0.02 \\
-  3358.058824 & -0.646 $\pm$ 0.005 & -1.474 $\pm$ 0.066 & 0.891 $\pm$ 0.079 & 0.23 $\pm$ 0.00 & 0.25 $\pm$ 0.07 & 0.14 $\pm$ 0.08 & 0.51 $\pm$ 0.01 & 0.10 $\pm$ 0.01 & 0.09 $\pm$ 0.04 \\
-  3358.069519 & -0.388 $\pm$ 0.104 & -1.669 $\pm$ 0.023 & 2.646 $\pm$ 0.020 & 0.40 $\pm$ 0.07 & 0.40 $\pm$ 0.02 & 0.53 $\pm$ 0.02 & 0.47 $\pm$ 0.04 & 0.33 $\pm$ 0.01 & 0.22 $\pm$ 0.01 \\
-  3358.080468 & -1.748 $\pm$ 0.009 & -2.483 $\pm$ 0.010 & 3.526 $\pm$ 0.009 & 0.25 $\pm$ 0.01 & 0.33 $\pm$ 0.01 & 0.55 $\pm$ 0.01 & 0.28 $\pm$ 0.01 & 0.32 $\pm$ 0.00 & 0.32 $\pm$ 0.00 \\
-  3358.091255 & -2.119 $\pm$ 0.007 & -2.868 $\pm$ 0.007 & 3.960 $\pm$ 0.005 & 0.26 $\pm$ 0.01 & 0.23 $\pm$ 0.01 & 0.40 $\pm$ 0.01 & 0.34 $\pm$ 0.01 & 0.29 $\pm$ 0.01 & 0.39 $\pm$ 0.00 \\
-  3358.101671 & -2.019 $\pm$ 0.006 & -2.731 $\pm$ 0.008 & 3.758 $\pm$ 0.005 & 0.20 $\pm$ 0.01 & 0.24 $\pm$ 0.01 & 0.43 $\pm$ 0.01 & 0.29 $\pm$ 0.01 & 0.25 $\pm$ 0.01 & 0.23 $\pm$ 0.00 \\
-  3358.112713 & -1.581 $\pm$ 0.020 & -2.141 $\pm$ 0.043 & 2.867 $\pm$ 0.019 & 0.19 $\pm$ 0.02 & 0.29 $\pm$ 0.03 & 0.40 $\pm$ 0.02 & 0.18 $\pm$ 0.02 & 0.13 $\pm$ 0.01 & 0.12 $\pm$ 0.00 \\
-  3358.123928 & -0.624 $\pm$ 0.006 & -1.312 $\pm$ 0.076 & 0.824 $\pm$ 0.012 & 0.09 $\pm$ 0.01 & 0.22 $\pm$ 0.08 & 0.44 $\pm$ 0.01 & 0.18 $\pm$ 0.01 & 0.02 $\pm$ 0.01 & 0.32 $\pm$ 0.01 \\
-  3358.135236 & -0.012 $\pm$ 0.011 & -0.208 $\pm$ 0.012 & -0.192 $\pm$ 0.012 & 0.03 $\pm$ 0.01 & 0.11 $\pm$ 0.01 & 0.12 $\pm$ 0.01 & 0.12 $\pm$ 0.04 & 0.25 $\pm$ 0.02 & 0.25 $\pm$ 0.02 \\
-  3358.146555 & 1.007 $\pm$ 0.100 & 1.622 $\pm$ 0.048 & -1.789 $\pm$ 0.045 & 0.06 $\pm$ 0.11 & 0.31 $\pm$ 0.06 & 0.04 $\pm$ 0.05 & 0.02 $\pm$ 0.04 & 0.12 $\pm$ 0.02 & 0.05 $\pm$ 0.05 \\
-  3358.156693 & 1.603 $\pm$ 0.018 & 2.444 $\pm$ 0.024 & -4.408 $\pm$ 0.197 & 0.14 $\pm$ 0.02 & 0.23 $\pm$ 0.03 & 1.00 $\pm$ 0.17 & 0.14 $\pm$ 0.02 & 0.14 $\pm$ 0.01 & 0.05 $\pm$ 0.00 \\
-  3358.169147 & 1.543 $\pm$ 0.007 & 2.152 $\pm$ 0.013 & -3.885 $\pm$ 0.031 & 0.14 $\pm$ 0.01 & 0.39 $\pm$ 0.01 & 1.00 $\pm$ 0.04 & 0.23 $\pm$ 0.01 & 0.27 $\pm$ 0.00 & 0.10 $\pm$ 0.00 \\
-  3358.177978 & 1.588 $\pm$ 0.037 & 2.828 $\pm$ 0.005 & -4.378 $\pm$ 0.053 & 0.40 $\pm$ 0.03 & 0.02 $\pm$ 0.01 & 0.75 $\pm$ 0.06 & 0.33 $\pm$ 0.01 & 0.11 $\pm$ 0.03 & 0.12 $\pm$ 0.01 \\
-  \hline
-  \end{tabular}
-  \caption{Best-fit parameters from multi-gaussian model fit to H$\alpha$ line
-  profiles.  Units for $\mu_i$ and $\sigma_i$ are $v_{\rm eq}$
-  (130\,\kms). These results should be treated with caution; only a
-  subset of the spectral epochs yielded statistically significant
-  detections of the circumstellar emission (see
-  Figure~\ref{fig:halphamodel}).}
-  \label{tab:halphamodelparams}
-\end{sidewaystable}
+%  \begin{sidewaystable}
+%    \footnotesize
+%    \centering
+%    \begin{tabular}{lccccccccc}
+%    % from results/halpha_to_rv_timerseries/multigauss_parametertable.tex
+%    \hline
+%    BTJD & $\mu_0$ & $\mu_1$ & $\mu_2$ & $\sigma_0$ & $\sigma_1$ & $\sigma_2$ & $A_0$ & $A_1$ & $A_2$ \\
+%    \hline
+%    3357.960099 & -0.725 $\pm$ 0.028 & -1.416 $\pm$ 0.026 & 0.177 $\pm$ 0.019 & 0.39 $\pm$ 0.03 & 0.18 $\pm$ 0.03 & 0.59 $\pm$ 0.02 & 0.51 $\pm$ 0.01 & 0.23 $\pm$ 0.04 & 0.29 $\pm$ 0.01 \\
+%    3357.970746 & -0.192 $\pm$ 0.007 & 0.498 $\pm$ 0.010 & 0.100 $\pm$ 0.014 & 0.23 $\pm$ 0.01 & 0.24 $\pm$ 0.01 & 0.55 $\pm$ 0.01 & 0.50 $\pm$ 0.01 & 0.37 $\pm$ 0.01 & 0.42 $\pm$ 0.01 \\
+%    3357.981672 & 0.895 $\pm$ 0.051 & 1.771 $\pm$ 0.076 & -1.470 $\pm$ 0.113 & 0.40 $\pm$ 0.02 & 0.40 $\pm$ 0.10 & 0.09 $\pm$ 0.11 & 0.67 $\pm$ 0.05 & 0.34 $\pm$ 0.04 & 0.03 $\pm$ 0.03 \\
+%    3357.993524 & 1.536 $\pm$ 0.011 & 2.202 $\pm$ 0.015 & -3.787 $\pm$ 0.049 & 0.25 $\pm$ 0.01 & 0.29 $\pm$ 0.01 & 0.72 $\pm$ 0.05 & 0.55 $\pm$ 0.01 & 0.46 $\pm$ 0.01 & 0.05 $\pm$ 0.00 \\
+%    3358.003594 & 1.974 $\pm$ 0.007 & 2.588 $\pm$ 0.006 & -2.749 $\pm$ 0.020 & 0.26 $\pm$ 0.01 & 0.22 $\pm$ 0.00 & 1.00 $\pm$ 0.02 & 0.64 $\pm$ 0.01 & 0.67 $\pm$ 0.01 & 0.43 $\pm$ 0.01 \\
+%    3358.015249 & 2.027 $\pm$ 0.003 & 2.666 $\pm$ 0.003 & -2.370 $\pm$ 0.015 & 0.24 $\pm$ 0.00 & 0.20 $\pm$ 0.00 & 1.00 $\pm$ 0.01 & 0.62 $\pm$ 0.00 & 0.60 $\pm$ 0.00 & 0.56 $\pm$ 0.00 \\
+%    3358.024971 & 1.790 $\pm$ 0.004 & 2.469 $\pm$ 0.006 & -2.138 $\pm$ 0.011 & 0.24 $\pm$ 0.00 & 0.26 $\pm$ 0.00 & 0.77 $\pm$ 0.01 & 0.53 $\pm$ 0.00 & 0.38 $\pm$ 0.00 & 0.31 $\pm$ 0.00 \\
+%    3358.036522 & 0.584 $\pm$ 0.008 & 1.399 $\pm$ 0.009 & -1.584 $\pm$ 0.009 & 0.18 $\pm$ 0.01 & 0.40 $\pm$ 0.01 & 0.89 $\pm$ 0.01 & 0.35 $\pm$ 0.01 & 0.39 $\pm$ 0.00 & 0.62 $\pm$ 0.00 \\
+%    3358.047668 & 0.328 $\pm$ 0.014 & 0.685 $\pm$ 0.010 & -0.969 $\pm$ 0.017 & 0.07 $\pm$ 0.01 & 0.13 $\pm$ 0.01 & 0.46 $\pm$ 0.02 & 0.14 $\pm$ 0.02 & 0.28 $\pm$ 0.02 & 0.52 $\pm$ 0.02 \\
+%    3358.058824 & -0.646 $\pm$ 0.005 & -1.474 $\pm$ 0.066 & 0.891 $\pm$ 0.079 & 0.23 $\pm$ 0.00 & 0.25 $\pm$ 0.07 & 0.14 $\pm$ 0.08 & 0.51 $\pm$ 0.01 & 0.10 $\pm$ 0.01 & 0.09 $\pm$ 0.04 \\
+%    3358.069519 & -0.388 $\pm$ 0.104 & -1.669 $\pm$ 0.023 & 2.646 $\pm$ 0.020 & 0.40 $\pm$ 0.07 & 0.40 $\pm$ 0.02 & 0.53 $\pm$ 0.02 & 0.47 $\pm$ 0.04 & 0.33 $\pm$ 0.01 & 0.22 $\pm$ 0.01 \\
+%    3358.080468 & -1.748 $\pm$ 0.009 & -2.483 $\pm$ 0.010 & 3.526 $\pm$ 0.009 & 0.25 $\pm$ 0.01 & 0.33 $\pm$ 0.01 & 0.55 $\pm$ 0.01 & 0.28 $\pm$ 0.01 & 0.32 $\pm$ 0.00 & 0.32 $\pm$ 0.00 \\
+%    3358.091255 & -2.119 $\pm$ 0.007 & -2.868 $\pm$ 0.007 & 3.960 $\pm$ 0.005 & 0.26 $\pm$ 0.01 & 0.23 $\pm$ 0.01 & 0.40 $\pm$ 0.01 & 0.34 $\pm$ 0.01 & 0.29 $\pm$ 0.01 & 0.39 $\pm$ 0.00 \\
+%    3358.101671 & -2.019 $\pm$ 0.006 & -2.731 $\pm$ 0.008 & 3.758 $\pm$ 0.005 & 0.20 $\pm$ 0.01 & 0.24 $\pm$ 0.01 & 0.43 $\pm$ 0.01 & 0.29 $\pm$ 0.01 & 0.25 $\pm$ 0.01 & 0.23 $\pm$ 0.00 \\
+%    3358.112713 & -1.581 $\pm$ 0.020 & -2.141 $\pm$ 0.043 & 2.867 $\pm$ 0.019 & 0.19 $\pm$ 0.02 & 0.29 $\pm$ 0.03 & 0.40 $\pm$ 0.02 & 0.18 $\pm$ 0.02 & 0.13 $\pm$ 0.01 & 0.12 $\pm$ 0.00 \\
+%    3358.123928 & -0.624 $\pm$ 0.006 & -1.312 $\pm$ 0.076 & 0.824 $\pm$ 0.012 & 0.09 $\pm$ 0.01 & 0.22 $\pm$ 0.08 & 0.44 $\pm$ 0.01 & 0.18 $\pm$ 0.01 & 0.02 $\pm$ 0.01 & 0.32 $\pm$ 0.01 \\
+%    3358.135236 & -0.012 $\pm$ 0.011 & -0.208 $\pm$ 0.012 & -0.192 $\pm$ 0.012 & 0.03 $\pm$ 0.01 & 0.11 $\pm$ 0.01 & 0.12 $\pm$ 0.01 & 0.12 $\pm$ 0.04 & 0.25 $\pm$ 0.02 & 0.25 $\pm$ 0.02 \\
+%    3358.146555 & 1.007 $\pm$ 0.100 & 1.622 $\pm$ 0.048 & -1.789 $\pm$ 0.045 & 0.06 $\pm$ 0.11 & 0.31 $\pm$ 0.06 & 0.04 $\pm$ 0.05 & 0.02 $\pm$ 0.04 & 0.12 $\pm$ 0.02 & 0.05 $\pm$ 0.05 \\
+%    3358.156693 & 1.603 $\pm$ 0.018 & 2.444 $\pm$ 0.024 & -4.408 $\pm$ 0.197 & 0.14 $\pm$ 0.02 & 0.23 $\pm$ 0.03 & 1.00 $\pm$ 0.17 & 0.14 $\pm$ 0.02 & 0.14 $\pm$ 0.01 & 0.05 $\pm$ 0.00 \\
+%    3358.169147 & 1.543 $\pm$ 0.007 & 2.152 $\pm$ 0.013 & -3.885 $\pm$ 0.031 & 0.14 $\pm$ 0.01 & 0.39 $\pm$ 0.01 & 1.00 $\pm$ 0.04 & 0.23 $\pm$ 0.01 & 0.27 $\pm$ 0.00 & 0.10 $\pm$ 0.00 \\
+%    3358.177978 & 1.588 $\pm$ 0.037 & 2.828 $\pm$ 0.005 & -4.378 $\pm$ 0.053 & 0.40 $\pm$ 0.03 & 0.02 $\pm$ 0.01 & 0.75 $\pm$ 0.06 & 0.33 $\pm$ 0.01 & 0.11 $\pm$ 0.03 & 0.12 $\pm$ 0.01 \\
+%    \hline
+%    \end{tabular}
+%    \caption{Best-fit parameters from multi-gaussian model fit to H$\alpha$ line
+%    profiles.  Units for $\mu_i$ and $\sigma_i$ are $v_{\rm eq}$
+%    (130\,\kms). These results should be treated with caution; only a
+%    subset of the spectral epochs yielded statistically significant
+%    detections of the circumstellar emission (see
+%    Figure~\ref{fig:halphamodel}).}
+%    \label{tab:halphamodelparams}
+%  \end{sidewaystable}
 

### 2025-05-28 paper/ms.tex
update

@@
   sources.}
-  %It remains unclear whether these structures originate intrinsically
-  %from the star or are fed by external sources. Likewise,
-  %the mechanism by which their optically thick clumps arise is still
-  %unknown.
   Rough estimates suggest $\gtrsim$10\% of M dwarfs host
@@
 \centering
-\caption{Selected system parameters for TIC\,141146667.}
+  \caption{Selected properties of TIC\,141146667.}
 \vspace{-0.2cm}
@@
 
-In a follow-up study, \citet{Townsend2008} synthesized light curves for
-these systems, assuming that the optical depth scaled linearly with
-plasma density.  They found that W-shaped eclipses, similar to those seen for
-TIC\,141146667, can occur when the spin and magnetic axes are moderately
-(15-45$^\circ$) misaligned.  The movies associated with their work are
-available
+In a follow-up study, \citet{Townsend2008} made synthetic light
+curves, assuming that the optical depth scaled linearly with plasma
+density.  They found that W-shaped eclipses, similar to those seen for
+TIC\,141146667, can occur when the spin and magnetic axes are
+moderately (15-45$^\circ$) misaligned.  The movies associated with
+their work are available
 online\footnote{\url{http://user.astro.wisc.edu/\~townsend/static.php?ref=rrm-movies\#Download\_Bundles}
@@
 these discrepancies.  Overall, the evidence suggests a warped torus is
-a good first approximation---one that will need refinement in future
+a good first approximation, but one that will need refinement in future
 work.}
@@
 the CPV phenomenon \citep{Rebull2020}, and our data show that some of
-the complex photometric features occur when clumps of circumstellar
+the flux dips occur when clumps of circumstellar
 material transit the star.  The geometric correction implies
@@
 {\it Radial Velocity}---We measured the radial velocities of
-TIC\,141146667 from our HIRES spectra using a \added{custom }pipeline.
-Our method is based on template-matching against synthetic
-\added{PHOENIX }spectra \citep{Husser2013}, \added{and is }calibrated
-\added{against }the standard stars described by \citet{Chubak2012}.
-We used velocity standards spanning G2-M4, irrespective of rotation
-rate.  We included velocity corrections due to Earth's motion around
-the solar system barycenter and due to Earth's daily rotation about
-its axis, calculated using \texttt{barycorrpy} \citep{Kanodia2018}.
-Our analysis code reproduces the systemic velocities of known velocity
+TIC\,141146667 \added{(Gaia DR3 860453786736413568) }from our HIRES
+spectra using a \added{custom }pipeline.  Our method was based on
+template-matching against synthetic \added{PHOENIX }spectra
+\citep{Husser2013}, \added{and was }calibrated \added{against }the
+standard stars described by \citet{Chubak2012}.  We used velocity
+standards spanning G2-M4, irrespective of rotation rate.  We included
+velocity corrections due to Earth's motion around the solar system
+barycenter and due to Earth's daily rotation about its axis,
+calculated using \texttt{barycorrpy} \citep{Kanodia2018}.  Our
+analysis code reproduced the systemic velocities of known velocity
 standards \citep{Chubak2012} with an RMS of 0.66\,\kms.
@@
 because they provided the best matches between the synthetic and
-observed spectra.  We then averaged the resulting redshift
-measurements over each order to produce the final measurement.  We
+observed spectra.  We averaged the redshift
+measurements over each order, and
 used the scatter of resulting velocity measurements between orders to
@@
 semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This
-sets an upper limit on the mass of any putative companion at the four
-hour period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
+sets an upper limit on the mass of any putative companion on a four
+hour orbit of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
 companions at wider separations, the Gaia DR3 renormalized unit weight
-error (RUWE), a proxy for the goodness of fit for a single-source
-astrometric model to the Gaia astrometry, is 1.23, within the usual
+error (RUWE) is 1.23, within the usual
 range for apparently single sources.  There are no resolved companions
@@
 periods in the TESS data.  Previous work \citep{Bouma2024} has shown
-that $\approx$30\% of CPVs show evidence for excess noise above the
-Gaia single-source astrometric model, and $\approx$40\% of CPVs show
-evidence for unresolved binary companions based on the presence of
+that $\approx$30\% of CPVs show evidence for binarity from RUWE, and $\approx$40\% of CPVs show
+evidence for binarity based on the presence of
 secondary photometric periods.  This agrees with analyses showing that
-multi-periodic low-mass stars are generally unresolved binaries
+multi-periodic low-mass stars are usually unresolved binaries
 \citep{Tokovinin2018}.  Overall, the CPV binary fraction seems
-consistent with that for field M dwarfs \citep{Winters2019}, pointing
+consistent with that of field M dwarfs \citep{Winters2019}, pointing
 to a weak or non-existent connection between the CPV phenomenon and
@@
 the sample variance of the residuals.
-\added{The results are shown in the middle columns of
-Figure~\ref{fig:halphamodel}, and a table of the fitted means,
+\added{The middle columns of
+Figure~\ref{fig:halphamodel} show the results; a table of the fitted means,
 amplitudes, and standard deviations for each component is available
@@
 $P_1$=$3.92\pm0.06$\,hr, $K_1/v_{\rm eq}$=2.88$\pm$0.10;
-and $P_2$=$3.88\pm0.20$\,hr, $K_1/v_{\rm eq}$=3.88$\pm$0.25.
+and $P_2$=$3.88\pm0.20$\,hr, $K_2/v_{\rm eq}$=3.88$\pm$0.25.
 The periods for the inner double-peaked clump are therefore consistent
@@
 
-{\it Physical dimensions of the emitting region}---The measured
-velocity widths from the circumstellar emission contain information
-about the size of the emitting region via the condition for rigid
+{\it Physical dimensions of emitting region}---The H$\alpha$
+velocity widths in Figure~\ref{fig:halphamodel} constrain
+the size of the emitting region via the condition for rigid
 corotation.  Consider a clump in cylindrical coordinates with
@@
 maximize it during transit, with $\gtrsim$100\,\kms\ variations in
-between.  This is not observed.   The arc geometry, and by a similar
-argument the spoke geometry, can thus be discarded.
+between.  Since this is not observed, the arc geometry, and by a similar
+argument the spoke geometry, can be discarded.
 
@@
 fact be a single clump with an optically thick H$\alpha$ line core.
-Regardless of this nuance, the implication is that the full length in
-the radial dimension of these two inner emitting clumps is
-approximately equal to the star's diameter.  At mid-transit, these
+Regardless, the implication is that the full length in the radial
+dimension of these two inner emitting clumps is approximately equal to
+the star's diameter.  At mid-transit, these
 inner clumps have a similar velocity dispersion, although with
@@
 the system is consistent with being viewed edge-on.  However, one
-constraint does come if one assumes that the TESS transit depth scales
+possible constraint follows by assuming that the TESS transit depth scales
 with the projected H$\alpha$ emission area $\ell z$.  
@@
 which would need to be in turn multiplied by an unknown opacity factor
-to produce the observed transit depth ($\delta$$\approx$5\%).  In
-general though, there is a degeneracy between $z$ and this opacity
+to produce the observed transit depth ($\delta$$\approx$5\%).  
+There is a degeneracy between $z$ and this opacity
 factor; larger vertical heights are allowed for lower optical depths
@@
 
-The physical conditions inside the plasma clumps, in particular the
-hydrogen number density, plasma temperature, ionization fraction, and
-magnetic field strength can be estimated from the available data.  We
-caution that the following estimates are order of magnitude
-calculations that assume a simple uniform-density plasma: detailed
+The hydrogen number density, plasma temperature, and magnetic field
+strength inside the clumps can be estimated from the available data.  
+The following order-of-magnitude calculations assume a simple
+uniform-density plasma in a spherical geometry: more careful
 considerations of radiative transfer are a worthy topic for future
-work, but are beyond the scope of this article.
-
-Circumstellar H$\alpha$ emission might be sourced either from resonant
+work.
+
+Circumstellar H$\alpha$ emission could come either from resonant
 scattering of stellar H$\alpha$ photons, or from radiative
 recombination.  We neglect scattering because Figure~\ref{fig:spec}
-shows the amplitude of the
-circumstellar H$\alpha$ emission varying by a factor of $\approx$5, in
-a manner uncorrelated with any variability in the chromospheric line
-core.  The volume emissivity under case B recombination can be written
-\begin{equation} j_{\rm H\alpha} = n_{\rm e} n_{\rm p} \alpha^{\rm
-eff}_{\rm H\alpha} h \nu_{\rm H\alpha}, \end{equation} where $n_{\rm
-e}$ and $n_{\rm p}$ are the electron and proton densities, and
-$\alpha^{\rm eff}_{\rm H\alpha}$ is the effective recombination
-coefficient, defined to include all recombination routes that produce
-an H$\alpha$ photon.  For hydrogen with temperatures between
-1,000-10,000\,K, $\alpha^{\rm eff}_{\rm H\alpha}$ is typically on the
-order of $10^{-12}$ to $10^{-13}$\,cm$^3$\,s$^{-1}$
-\citep{Hummer1987,Draine2011}.  Neglecting the effects of atoms other
-than hydrogen, we can assume an ionization fraction $x$, such that
-$n_{\rm e} = n_{\rm p} = x n_{\rm H}$, for $n_{\rm H}$ the hydrogen
-number density.  Let $L_{\rm H\alpha} = j_{\rm H\alpha} V$, for $V$
-the volume of the emitting hydrogen.  The luminosity of circumstellar
-hydrogen emission, $L_{\rm H\alpha}$, is an observable: our SED
-fitting routine yields $L_\star$$\approx$0.012\,$L_\odot$, which
-implies that the stellar H$\alpha$ line radiates at
-$\approx$1.0$\times$$10^{28}$erg\,s$^{-1}$.  The luminosity of the
-clumps $L_{\rm H\alpha}$ are of order one tenth that of the star.  If
-we approximate the emitting volume as a homogeneous sphere of radius
-$r$, we can write
+shows the
+circumstellar H$\alpha$ emission varying by a factor of $\approx$5
+while the chromospheric line core is stable.  The volume emissivity
+under case B recombination can be written \begin{equation}
+  j_{\rm H\alpha} = n_{\rm e} n_{\rm p} \alpha^{\rm eff}_{\rm H\alpha} h \nu_{\rm H\alpha},
+\end{equation} where $n_{\rm e}$ and $n_{\rm p}$ are the electron and
+proton densities, and $\alpha^{\rm eff}_{\rm H\alpha}$ is the
+effective recombination coefficient, defined to include all
+recombination routes that produce an H$\alpha$ photon.  For hydrogen
+with temperatures between 1,000-10,000\,K, $\alpha^{\rm eff}_{\rm
+H\alpha}$ is typically $10^{-12}$ to
+$10^{-13}$\,cm$^3$\,s$^{-1}$ \citep{Hummer1987,Draine2011}.
+Neglecting atoms other than hydrogen, we can assume an
+ionization fraction $x$, such that $n_{\rm e} = n_{\rm p} = x n_{\rm
+H}$, for $n_{\rm H}$ the hydrogen number density.  Let $L_{\rm
+H\alpha} = j_{\rm H\alpha} V$, for $V$ the volume of the emitting
+hydrogen.  The luminosity of circumstellar hydrogen emission, $L_{\rm
+H\alpha}$, is an observable: our SED fitting routine yields
+$L_\star$$\approx$0.012\,$L_\odot$, which implies that the stellar
+H$\alpha$ line radiates at $\approx$1.0$\times$$10^{28}$erg\,s$^{-1}$.
+The luminosity of the clumps $L_{\rm H\alpha}$ are of order one tenth
+that of the star.  If we approximate the emitting volume as a
+homogeneous sphere of radius $r$, we can write
 \begin{align}
@@
 gas}\approx 2\times10^{17}$\,g\added{, which is similar to masses derived for
-plasma clumps around other cool stars \citep{VillarrealDAngelo2019}.}.  We emphasize that
+plasma clumps around other cool stars \citep{VillarrealDAngelo2019}}.  We emphasize that
 Equation~\ref{eq:numdensity} in intended to provide only an order of
@@
 exceed the thermal pressure, $B_{\rm c}^2 / 8\pi > n_{\rm H} k T$.
-Although we do not know the plasma temperature, if it were
+Although we do not know the exact plasma temperature, if it were
 significantly beyond 1,000-10,000\,K, we would either fully ionize the
@@
 
+%\begin{table}
+%    \centering
+%    \begin{tabular}{lcr}
+%    \hline 
+%    \hline
+%    Parameter & Host & Source \\
+%    \hline 
+%    \multicolumn{3}{c}{Identifiers} \\
+%    \hline
+%    TIC & 141146667 & TESS \\
+%    Gaia & 860453786736413568 & Gaia\ DR3 \\
+%    \hline
+%    \multicolumn{3}{c}{Astrometry \& Radial Velocity} \\ 
+%    \hline
+%    $\alpha_{2000}$ & 11:05:15.09   & Gaia\ DR3 \\
+%    $\delta_{2000}$ & +59 15 05.57  & Gaia\ DR3 \\
+%    $\mu_{\alpha}$ (mas yr$^{-1}$ ) & -73.933 $\pm$ 0.022 & Gaia\ DR3 \\
+%    $\mu_{\delta}$ (mas yr$^{-1}$ ) &  32.262 $\pm$ 0.024 & Gaia\ DR3 \\
+%    $\pi$ (mas)                     &  17.324 $\pm$ 0.025 & Gaia\ DR3 \\
+%    RUWE                            &  1.23               & Gaia\ DR3 \\
+%    RV (\kms)                       & 0.61 $\pm$ 1.47     & HIRES \\
+%    \hline
+%    \multicolumn{3}{c}{Photometry} \\
+%    \hline
+%    $TESS$ (mag)                    & 13.283 $\pm$ 0.010 & TIC8\     \\
+%    $G$ (mag)                       & 14.701 $\pm$ 0.002 & Gaia\ DR3 \\
+%    $G_{\rm BP}$ (mag)              & 16.664 $\pm$ 0.008 & Gaia\ DR3 \\
+%    $G_{\rm RP}$ (mag)              & 13.398 $\pm$ 0.006 & Gaia\ DR3 \\
+%    $G_{\rm BP}$-$G_{\rm RP}$ (mag) &  3.276 $\pm$ 0.010 & Gaia\ DR3 \\
+%    $J$ (mag)                       & 11.401 $\pm$ 0.022 & 2MASS     \\
+%    $H$ (mag)                       & 10.793 $\pm$ 0.021 & 2MASS     \\
+%    $K_s$ (mag)                     & 10.473 $\pm$ 0.016 & 2MASS     \\
+%    $W1$ (mag)                      & 10.276 $\pm$ 0.023 & ALLWISE   \\ % Cutri+2013 II/328/allwise
+%    $W2$ (mag)                      & 10.070 $\pm$ 0.020 & ALLWISE   \\
+%    $W3$ (mag)                      &  9.838 $\pm$ 0.045 & ALLWISE   \\
+%    %$W4$ (mag)                      &  8.392 $\pm$ NOUNC & ALLWISE \\
+%	  %
+%    % NOTE: ROSAT is an emitter.  GALEX detection.
+%    % ROSAT: 3.25e-13 mW/m^2 = erg/cm^2/s
+%    % Ofek+2011 1.4Ghz emitter.  Helfand+2015 ditto.  Bruzewski+2021.
+%    \hline
+%    \multicolumn{3}{c}{Physical Properties} \\
+%    \hline
+%    $T_{\rm eff}$ (K) & 2972 $\pm$ 40 & SED fit \\
+%    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & SED fit  \\
+%    $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & SED fit \\
+%    $P_{\rm rot}$ (hours) & 3.930 $\pm$ 0.001 & TESS \\ 
+%    $v_{\rm eq}$ (\kms)  &  130$\pm$4  & Derived \\
+%    $v_{\rm eq} \sin i_\star$ (\kms) & 138 $\pm$ 8 & HIRES \\
+%    $i_\star$($^\circ$) & $>$63 & Derived \\
+%    $A_V$ (mag) & 0 & \citep{Green2019} \\
+%    $M_\star$ ($M_{\odot}$)  & 0.22 $\pm$ 0.02  & PARSEC \citep{Chen2014}\\
+%    ${\rm EW}_{\rm Li}$ (m\AA) & $<$107 & HIRES (2$\sigma$)\\
+%    $t_{\rm CAMD}$ (Myr) & 30-150 &  Gaia DR3 \\
+%    $t_{\rm Li,emp}$ (Myr) & $>$20 &  HIRES, \citep{Jeffries2023} \\
+%    $t_{\rm Li,th}$ (Myr) & $>$35 &  HIRES, \citep{Feiden2016} \\
+%    $t_{\rm adopted}$ (Myr) & 35-150 &  -- \\
+%    \hline
+%    \end{tabular}
+%		\caption{Properties of TIC\,141146667.  References:
+%    Gaia DR3 \citep{GaiaDR3}, TESS \citep{Ricker2015},
+%    TIC8 \citep{Stassun2019}, 2MASS \citep{Skrutskie2006}, ALLWISE
+%    \citep{Cutri2014}.}
+%    \label{tab:stparams}
+%\end{table}
+
 \begin{table}
-    \centering
-    \begin{tabular}{lcr}
-    \hline 
-    \hline
-    Parameter & Host & Source \\
-    \hline 
-    \multicolumn{3}{c}{Identifiers} \\
-    \hline
-    TIC & 141146667 & TESS \\
-    Gaia & 860453786736413568 & Gaia\ DR3 \\
-    \hline
-    \multicolumn{3}{c}{Astrometry \& Radial Velocity} \\ 
-    \hline
-    $\alpha_{2000}$ & 11:05:15.09   & Gaia\ DR3 \\
-    $\delta_{2000}$ & +59 15 05.57  & Gaia\ DR3 \\
-    $\mu_{\alpha}$ (mas yr$^{-1}$ ) & -73.933 $\pm$ 0.022 & Gaia\ DR3 \\
-    $\mu_{\delta}$ (mas yr$^{-1}$ ) &  32.262 $\pm$ 0.024 & Gaia\ DR3 \\
-    $\pi$ (mas)                     &  17.324 $\pm$ 0.025 & Gaia\ DR3 \\
-    RUWE                            &  1.23               & Gaia\ DR3 \\
-    RV (\kms)                       & 0.61 $\pm$ 1.47     & HIRES \\
-    \hline
-    \multicolumn{3}{c}{Photometry} \\
-    \hline
-    $TESS$ (mag)                    & 13.283 $\pm$ 0.010 & TIC8\     \\
-    $G$ (mag)                       & 14.701 $\pm$ 0.002 & Gaia\ DR3 \\
-    $G_{\rm BP}$ (mag)              & 16.664 $\pm$ 0.008 & Gaia\ DR3 \\
-    $G_{\rm RP}$ (mag)              & 13.398 $\pm$ 0.006 & Gaia\ DR3 \\
-    $G_{\rm BP}$-$G_{\rm RP}$ (mag) &  3.276 $\pm$ 0.010 & Gaia\ DR3 \\
-    $J$ (mag)                       & 11.401 $\pm$ 0.022 & 2MASS     \\
-    $H$ (mag)                       & 10.793 $\pm$ 0.021 & 2MASS     \\
-    $K_s$ (mag)                     & 10.473 $\pm$ 0.016 & 2MASS     \\
-    $W1$ (mag)                      & 10.276 $\pm$ 0.023 & ALLWISE   \\ % Cutri+2013 II/328/allwise
-    $W2$ (mag)                      & 10.070 $\pm$ 0.020 & ALLWISE   \\
-    $W3$ (mag)                      &  9.838 $\pm$ 0.045 & ALLWISE   \\
-    %$W4$ (mag)                      &  8.392 $\pm$ NOUNC & ALLWISE \\
-	  %
-    % NOTE: ROSAT is an emitter.  GALEX detection.
-    % ROSAT: 3.25e-13 mW/m^2 = erg/cm^2/s
-    % Ofek+2011 1.4Ghz emitter.  Helfand+2015 ditto.  Bruzewski+2021.
-    \hline
-    \multicolumn{3}{c}{Physical Properties} \\
-    \hline
-    $T_{\rm eff}$ (K) & 2972 $\pm$ 40 & SED fit \\
-    $R_\star$ ($R_{\odot}$) & 0.42 $\pm$ 0.02 & SED fit  \\
-    $L_\star$ ($L_\odot$) & 0.0126 $\pm$ 0.0012 & SED fit \\
-    $P_{\rm rot}$ (hours) & 3.930 $\pm$ 0.001 & TESS \\ 
-    $v_{\rm eq}$ (\kms)  &  130$\pm$4  & Derived \\
-    $v_{\rm eq} \sin i_\star$ (\kms) & 138 $\pm$ 8 & HIRES \\
-    $i_\star$($^\circ$) & $>$63 & Derived \\
-    $A_V$ (mag) & 0 & \citep{Green2019} \\
-    $M_\star$ ($M_{\odot}$)  & 0.22 $\pm$ 0.02  & PARSEC \citep{Chen2014}\\
-    ${\rm EW}_{\rm Li}$ (m\AA) & $<$107 & HIRES (2$\sigma$)\\
-    $t_{\rm CAMD}$ (Myr) & 30-150 &  Gaia DR3 \\
-    $t_{\rm Li,emp}$ (Myr) & $>$20 &  HIRES, \citep{Jeffries2023} \\
-    $t_{\rm Li,th}$ (Myr) & $>$35 &  HIRES, \citep{Feiden2016} \\
-    $t_{\rm adopted}$ (Myr) & 35-150 &  -- \\
-    \hline
-    \end{tabular}
-		\caption{Properties of TIC\,141146667.  References:
-    Gaia DR3 \citep{GaiaDR3}, TESS \citep{Ricker2015},
-    TIC8 \citep{Stassun2019}, 2MASS \citep{Skrutskie2006}, ALLWISE
-    \citep{Cutri2014}.}
-    \label{tab:stparams}
-\end{table}
-
-\begin{table}
+  \footnotesize
   \centering
@@
 
-\clearpage
+%\clearpage
 

### 2025-05-28 paper/ms.tex
update
ms width format

@@
 retention of their atmospheres---has correspondingly grown in
-importance.  Previous work has established
-that most M dwarfs host close-in planets \citep{Dressing2015} that on
-average are subject to long disk lifetimes
-\citep{Ribas2015}, intense UV radiation \citep{France2016},
-and frequent stellar flares 
-\citep{Feinstein2020}.  However, despite extensive work in these
-areas, the plasma and magnetospheric environments that bathe young,
-close-in exoplanets remain challenging to quantify.  Understanding
-these environments is crucial because they directly impact atmospheric
-retention and\added{, ultimately,} habitability.
+importance.  Previous work has established that most M dwarfs host
+close-in planets \citep{Dressing2015} that on average are subject to
+long disk lifetimes \citep{Ribas2015}, intense UV radiation
+\citep{France2016}, and frequent stellar flares \citep{Feinstein2020}.
+However, despite extensive work in these areas, the plasma and
+magnetospheric environments that bathe young, close-in exoplanets
+remain challenging to quantify.  Understanding these environments is
+crucial because they directly impact atmospheric retention and\added{,
+ultimately,} habitability.
 
 One example of our current ignorance is the complex periodic
-variables.  While Figure~\ref{fig:lc} highlights the main
-object of interest in this article, over one hundred analogous systems
-have now been found by K2 and TESS
+variables.  While Figure~\ref{fig:lc} highlights the main object of
+interest in this article, over one hundred analogous systems have now
+been found by K2 and TESS
 \citep{Rebull2016,Stauffer2017,Rebull2018,Zhan2019,Rebull2020,Stauffer2021,Popinchalk2023,Bouma2024}.
@@
 $\approx$3\% of stars a few million years old show this complex
-behavior, an observed fraction which decreases to
-$\approx$0.3\% by $\approx$110\,Myr \citep{Rebull2020}.  CPVs can and
-have been confused for transiting exoplanets
+behavior, an observed fraction which decreases to $\approx$0.3\% by
+$\approx$110\,Myr \citep{Rebull2020}.  CPVs can and have been confused
+for transiting exoplanets
 \citep{vanEyken2012,Johns-Krull2016,Bouma2020}.
@@
 transiting clumps of circumstellar material corotate with the star
-\citep{Stauffer2017}, or that these stars
-represent an extreme in naturally-occurring distributions of starspots
-or faculae \citep{Koen2021}.  The main argument against a
-starspot-only explanation invokes the timescales and amplitudes of the
-sharpest photometric features.  However, no independent evidence has
-yet been acquired for the presence of any circumstellar material.  If
-such material exists, then the geometric correction from the transit
+\citep{Stauffer2017}, or that these stars represent an extreme in
+naturally-occurring distributions of starspots or faculae
+\citep{Koen2021}.  The main argument against a starspot-only
+explanation invokes the timescales and amplitudes of the sharpest
+photometric features.  However, no independent evidence has yet been
+acquired for the presence of any circumstellar material.  If such
+material exists, then the geometric correction from the transit
 probability would imply an intrinsic occurrence rate at least a few
@@
 \citep{CollierCameron1989,CollierCameron1992,Barnes2000,Donati2000,Dunstone2006,Skelly2008,Leitzinger2016,Cang2021}.
-Such clumps are thought to be forced into corotation by the star's magnetic
-field, and the exact geometry of where the plasma can accumulate is
-dictated by the field's topology \citep{Waugh2022}.  For instance, a magnetic dipole
-field tilted with respect to the stellar spin axis yields
-accumulations in a warped torus geometry \citep{Townsend2005}.  To
-date, none of these spectroscopic variables have shown any photometric
-anomalies \citep{Bouma2024}, leaving open the issue of whether they
-are related to CPVs.
+Such clumps are thought to be forced into corotation by the star's
+magnetic field, and the exact geometry of where the plasma can
+accumulate is dictated by the field's topology \citep{Waugh2022}.  For
+instance, a magnetic dipole field tilted with respect to the stellar
+spin axis yields accumulations in a warped torus geometry
+\citep{Townsend2005}.  To date, none of these spectroscopic variables
+have shown any photometric anomalies \citep{Bouma2024}, leaving open
+the issue of whether they are related to CPVs.
 
@@
   Data gaps were caused by light from the Earth (BTJD 3356-3358.5) and
-  Moon (BTJD 3359.5-3360.5).  Raw two minute
-  data are in gray; black time-averages to ten minute sampling.  {\bf
-  b-c,} Folded TESS light curve before and after spectroscopy.  Black
-  now phase-averages to 100 points per
-	3.93\ hour cycle.  During BTJD 3352-3356, a state switch occurred near BTJD
-  3353, and the dip at $\phi$$\approx$0.8 \added{became less
-  pronounced}.  While the \added{dip spanning $\phi$=0.6-1.1} was present both before and after the
-  HIRES sequence, its photometric shape evolved during the data gap.
-  The orange bar denotes times of spectroscopic transits for the inner
-  two H$\alpha$ clumps observed with HIRES (see
-  Figure~\ref{fig:spec}).}
+  Moon (BTJD 3359.5-3360.5).  Raw two minute data are in gray; black
+  time-averages to ten minute sampling.  {\bf b-c,} Folded TESS light
+  curve before and after spectroscopy.  Black now phase-averages to
+  100 points per 3.93\ hour cycle.  During BTJD 3352-3356, a state
+  switch occurred near BTJD 3353, and the dip at $\phi$$\approx$0.8
+  \added{became less pronounced}.  While the \added{dip spanning
+  $\phi$=0.6-1.1} was present both before and after the HIRES
+  sequence, its photometric shape evolved during the data gap.  The
+  orange bar denotes times of spectroscopic transits for the inner two
+  H$\alpha$ clumps observed with HIRES (see Figure~\ref{fig:spec}).}
   \label{fig:fulllc}
@@
   points are phase-averaged; gray are the raw data.
-  {\bf b,} Keck/HIRES H$\alpha$ spectra acquired on 17
-  February 2024.  The continuum is set to unity, and the darkest color
-  is at twice the continuum to accentuate emission outside the line
-  core ($|v/v_{\rm eq}|>1$, for the equatorial velocity $v_{\rm eq}$=130\,\kms).  While
-  emission in the line core comes from the star's chromosphere,
-  the sinusoidal emission features are most readily described by a
-  warped plasma torus.
-  {\bf c,} Individual epochs of Panel b, visible in the
-  online movie.  The dotted line shows the time-averaged spectrum,
-  $f_{\langle t \rangle}$.
+  {\bf b,} Keck/HIRES H$\alpha$ spectra acquired on 17 February 2024.
+  The continuum is set to unity, and the darkest color is at twice the
+  continuum to accentuate emission outside the line core ($|v/v_{\rm
+  eq}|>1$, for the equatorial velocity $v_{\rm eq}$=130\,\kms).  While
+  emission in the line core comes from the star's chromosphere, the
+  sinusoidal emission features are most readily described by a warped
+  plasma torus.
+  {\bf c,} Individual epochs of Panel b, visible in the online movie.
+  The dotted line shows the time-averaged spectrum, $f_{\langle t
+  \rangle}$.
   {\bf d,} As in Panel a, but overplotting the
@@
 We identified TIC\,141146667 in previous work \citep{Bouma2024} by
-searching TESS two-minute data from 2018-2022 for highly
-structured, periodic light curves \citep{Ricker2015}.  We chose the
-star for spectroscopy because its brightness and rapid rotation enabled
-an efficient search for variability in its line profiles.
-As an apparently single pre-main sequence M dwarf, its properties are
+searching TESS two-minute data from 2018-2022 for highly structured,
+periodic light curves \citep{Ricker2015}.  We chose the star for
+spectroscopy because its brightness and rapid rotation enabled an
+efficient search for variability in its line profiles.  As an
+apparently single pre-main sequence M dwarf, its properties are
 typical for the CPV population (see Table~\ref{tab:params} and
@@
 observations spanned the second half of the night, from 10:47 to 16:13
-(UT). 
-%The star's airmass spanned $z$=1.2-2.2, and we opted for a fixed 15
-%minute cadence, except for a final 10 minute exposure due to
-%increasing sky brightness at sunrise. 
-\added{We opted for a fixed 15 minute cadence, and} used the C2 decker
-(0$\farcs$86$\times$14$\farcs$0) in the red configuration, yielding a
-resolution $R$$\approx$45{,}000 ($\delta
-v$$\approx$6.7\,\kms).
-%We binned the CCD readout by a factor of three in the spatial
-%dimension, yielding $\approx$1,000 photons (S/N=33) per pixel in the
-%continuum at 6500\,\AA. 
-Strong winds contributed to 1$''$-1\farcs5 seeing, but conditions were
-otherwise
-favorable.  We reduced the echelleogram %to a one-dimensional spectrum
-using the standard techniques of the California Planet Survey
-\citep{Howard2010}.  
-%Figure~\ref{fig:spec} shows the result in the
-%vicinity of H$\alpha$ without any additional processing.
+(UT).  \added{We opted for a fixed 15 minute cadence, and} used the C2
+decker (0$\farcs$86$\times$14$\farcs$0) in the red configuration,
+yielding a resolution $R$$\approx$45{,}000 ($\delta
+v$$\approx$6.7\,\kms).  Strong winds contributed to 1$''$-1\farcs5
+seeing, but conditions were otherwise favorable.  We reduced the
+echelleogram using the standard techniques of the California Planet
+Survey \citep{Howard2010}.
 
@@
 spanning 2019-2024.  TESS acquired these observations at two-minute
-cadence during Sectors 41, 48, and 75.   The 30-minute data during Sectors
-14, 15, and 21 smeared sharp features over the star's 3.93~hour
-period (see \citealt{Gunther2022}).  The movie in
-Figure~\ref{fig:lc} shows the two-minute data: 
-like other CPVs, TIC\,141146667 maintains a fixed period over
-timescales of years while its detailed photometric morphology evolves.
-The nearest known star, TIC\,141146666 ($T$=14.5), is 25$''$ from
-TIC\,141146667 and is photometrically \added{quiet};
-crowding is not a concern.
+cadence during Sectors 41, 48, and 75.   The 30-minute data during
+Sectors 14, 15, and 21 smeared sharp features over the star's
+3.93~hour period (see \citealt{Gunther2022}).  The movie in
+Figure~\ref{fig:lc} shows the two-minute data: like other CPVs,
+TIC\,141146667 maintains a fixed period over timescales of years while
+its detailed photometric morphology evolves.  The nearest known star,
+TIC\,141146666 ($T$=14.5), is 25$''$ from TIC\,141146667 and is
+photometrically \added{quiet}; crowding is not a concern.
 
@@
 simultaneous observations.   Figure~\ref{fig:fulllc} shows the result;
-Earth passed within 25$^\circ$ of the TESS camera's boresight from BTJD
-3356.0-3358.5, which caused a data gap that ended twelve hours after our
-Keck/HIRES observations (green bar).  From BTJD 3359.4-3362.0, the Moon
-then passed within 25$^\circ$ of the camera's boresight.  Based on the
-level of scattered light in the optimal aperture
-\citep{Jenkins2016}, we manually masked out data in the TESS light curve
-from 3359.4-3360.1; the remainder of the data during the lunar
-approach were usable.  Small gaps from BTJD 3353.6-3353.8 and
+Earth passed within 25$^\circ$ of the TESS camera's boresight from
+BTJD 3356.0-3358.5, which caused a data gap that ended twelve hours
+after our Keck/HIRES observations (green bar).  From BTJD
+3359.4-3362.0, the Moon then passed within 25$^\circ$ of the camera's
+boresight.  Based on the level of scattered light in the optimal
+aperture \citep{Jenkins2016}, we manually masked out data in the TESS
+light curve from 3359.4-3360.1; the remainder of the data during the
+lunar approach were usable.  Small gaps from BTJD 3353.6-3353.8 and
 3360.1-3360.3 were caused by data downlinks at the spacecraft's
@@
 both before and after the HIRES data were acquired, a large flux
-decrement spanned roughly half of each cycle.  From BTJD 3352-3356, this
-dip had two sharp local minima;  the minimum at $\phi$$\approx$0.8
-became less pronounced following the flare at BTJD 3353, yielding a dip more
-closely resembling an asymmetric ``V'' than a ``W''.  Similar CPV state
-changes have been previously seen \citep{Stauffer2017,Bouma2024}.  The
-photometric shape therefore evolved during the twelve cycles spanning
-the 3356-3358 gap, since the average shape from 3358-3363 more closely
-resembles the initial ``W''.  Nonetheless, the global photometric
-morphology---a small brightening over 45\% of the period, followed by a
-complex flux dip spanning 55\% of the period---is similar before and
-after the data gap.
+decrement spanned roughly half of each cycle.  From BTJD 3352-3356,
+this dip had two sharp local minima;  the minimum at
+$\phi$$\approx$0.8 became less pronounced following the flare at BTJD
+3353, yielding a dip more closely resembling an asymmetric ``V'' than
+a ``W''.  Similar CPV state changes have been previously seen
+\citep{Stauffer2017,Bouma2024}.  The photometric shape therefore
+evolved during the twelve cycles spanning the 3356-3358 gap, since the
+average shape from 3358-3363 more closely resembles the initial ``W''.
+Nonetheless, the global photometric morphology---a small brightening
+over 45\% of the period, followed by a complex flux dip spanning 55\%
+of the period---is similar before and after the data gap.
 
@@
 Figure~\ref{fig:spec} shows the TESS and HIRES data from February
-2024.  The spectra \added{(Panels b,c)} show emission in
-H$\alpha$ beyond the star's equatorial velocity, $v_{\rm eq}$, of
-130\,\kms.  There are at least two distinct emission components,
-180$^\circ$ apart in phase.  The inner component at lower
-velocities has clearer sinusoidal behaviour in time and is
-double-peaked, with peak semi-amplitudes of 2.07\,$v_{\rm eq}$ and
-2.88\,$v_{\rm eq}$ (see Appendix~\ref{subsec:halpha}).  There
-is significant non-periodic variability in the emissivity of this
-double-peaked component: the flux excess begins with an amplitude 70\%
-above the continuum, and diminishes to 10\% by sunrise.  The
-higher-velocity component 180$^\circ$ opposite in phase is detected
-only from $\phi$=0.2-1.0.  From $\phi$=0.2-0.5, this outer component
-appears connected to the star in velocity space.  While its peak
-semi-amplitude of 3.88\,$v_{\rm eq}$ is achieved at both $\phi$=0.25
-and $\phi$=0.75, its amplitude similarly decreases from a 60\% excess 
-to a 10\% excess over the observation sequence.  In
-Appendix~\ref{subsec:halpha}, we measured the period for all three
-emission components to be consistent with the
-photometric \periodhr\ hour period, to within two minutes for the
-\added{inner} component.
+2024.  The spectra \added{(Panels b,c)} show emission in H$\alpha$
+beyond the star's equatorial velocity, $v_{\rm eq}$, of 130\,\kms.
+There are at least two distinct emission components, 180$^\circ$ apart
+in phase.  The inner component at lower velocities has clearer
+sinusoidal behaviour in time and is double-peaked, with peak
+semi-amplitudes of 2.07\,$v_{\rm eq}$ and 2.88\,$v_{\rm eq}$ (see
+Appendix~\ref{subsec:halpha}).  There is significant non-periodic
+variability in the emissivity of this double-peaked component: the
+flux excess begins with an amplitude 70\% above the continuum, and
+diminishes to 10\% by sunrise.  The higher-velocity component
+180$^\circ$ opposite in phase is detected only from $\phi$=0.2-1.0.
+From $\phi$=0.2-0.5, this outer component appears connected to the
+star in velocity space.  While its peak semi-amplitude of
+3.88\,$v_{\rm eq}$ is achieved at both $\phi$=0.25 and $\phi$=0.75,
+its amplitude similarly decreases from a 60\% excess to a 10\% excess
+over the observation sequence.  In Appendix~\ref{subsec:halpha}, we
+measured the period for all three emission components to be consistent
+with the photometric \periodhr\ hour period, to within two minutes for
+the \added{inner} component.
 
@@
 not moving on a Keplerian orbit}; it is \added{magnetically forced to
-co-rotate with the star}.  The velocity
-semi-amplitude of the sinusoids gives the mean distance of each clump
-from the stellar \added{rotation axis}: 2.07\,$R_\star$ and
-2.88\,$R_\star$ for the inner clumps, and 3.88\,$R_\star$ for the
-outer clump.   These clumps transit in front of the star when passing
-from negative to positive velocity.  The transits of the two inner
-clumps last $\approx$22\% of each cycle, from $\phi$=-0.1 to
-$\phi$=+0.12.  This spectroscopic
+co-rotate with the star}.  The velocity semi-amplitude of the
+sinusoids gives the mean distance of each clump from the stellar
+\added{rotation axis}: 2.07\,$R_\star$ and 2.88\,$R_\star$ for the
+inner clumps, and 3.88\,$R_\star$ for the outer clump.   These clumps
+transit in front of the star when passing from negative to positive
+velocity.  The transits of the two inner clumps last $\approx$22\% of
+each cycle, from $\phi$=-0.1 to $\phi$=+0.12.  This spectroscopic
 transit coincides with the latter half of the complex eclipse feature
@@
 eq}|<1$, most observed H$\alpha$ photons come from the star's
-chromosphere; \added{variability in the stellar emission line can be caused
-by circumstellar material, bright regions, or dark regions
-crossing the star's surface}. 
-Figure~\ref{fig:spec}e suggests that \added{all three effects occur in
-TIC\,141146667}.
-For instance, from $\phi$=0-0.3, double-peaked emission is visible
-both on and off-limb; this feature is circumstellar in origin.
-However, the emission feature that crosses the star from
-$\phi$=0.4-0.9 is brighter than the circumstellar clumps, and its slow
-speed instead suggests it is associated with bright region on the
-star's surface.  Similarly, from $\phi$=0.6-1.15 a 20\% deep
-absorption feature slowly crosses the H$\alpha$ line profile.  This
-feature could be either a chromospherically dark region (e.g.~a spot
-group), or an azimuthally extended component of the circumstellar
-material.  The origin of the other bright and dark streaks passing
-across the line core \added{in Figure~\ref{fig:spec}e }are similarly
-ambiguous.
-
-\added{Figure~\ref{fig:spec}d shows} a final exercise to
-quantify the behavior of the line core, 
-by summing the \added{H$\alpha$} flux at $|\Delta v / v_{\rm
-eq}|<1$.  This panel shows that changes in the line core flux
-\added{($f_{\rm H\alpha\ core}$)} correlate with the broadband
-variability throughout most of the light curve, except near
+chromosphere; \added{variability in the stellar emission line can be
+caused by circumstellar material, bright regions, or dark regions
+crossing the star's surface}.  Figure~\ref{fig:spec}e suggests that
+\added{all three effects occur in TIC\,141146667}.  For instance, from
+$\phi$=0-0.3, double-peaked emission is visible both on and off-limb;
+this feature is circumstellar in origin.  However, the emission
+feature that crosses the star from $\phi$=0.4-0.9 is brighter than the
+circumstellar clumps, and its slow speed instead suggests it is
+associated with bright region on the star's surface.  Similarly, from
+$\phi$=0.6-1.15 a 20\% deep absorption feature slowly crosses the
+H$\alpha$ line profile.  This feature could be either a
+chromospherically dark region (e.g.~a spot group), or an azimuthally
+extended component of the circumstellar material.  The origin of the
+other bright and dark streaks passing across the line core \added{in
+Figure~\ref{fig:spec}e }are similarly ambiguous.
+
+\added{Figure~\ref{fig:spec}d shows} a final exercise to quantify the
+behavior of the line core, by summing the \added{H$\alpha$} flux at
+$|\Delta v / v_{\rm eq}|<1$.  This panel shows that changes in the
+line core flux \added{($f_{\rm H\alpha\ core}$)} correlate with the
+broadband variability throughout most of the light curve, except near
 $\phi$$\approx$0.5, corresponding to the transit of the 3.9\,$R_\star$
@@
 clumps exist around at least one such star.  More specifically, the
-spectra require plasma with a significant population of hydrogen in the
-$n$=3 excited state, \added{with }minimal evidence for
+spectra require plasma with a significant population of hydrogen in
+the $n$=3 excited state, \added{with }minimal evidence for
 higher-order excitations.  Most of this H$\alpha$ emission originates
@@
 
-While the H$\alpha$ emission mostly comes from clumps,
-the broadband flux dip in Figure~\ref{fig:spec} spans roughly half of
-each cycle.  In CPVs more generally, individual flux dips last 5-50\% of
-each cycle\added{, and there are often multiple dips per cycle }\citep{Bouma2024}.  This implies that
-azimuthally-distributed material may be the norm for CPVs; a warped
-torus may be a more accurate picture than a clump.
+While the H$\alpha$ emission mostly comes from clumps, the broadband
+flux dip in Figure~\ref{fig:spec} spans roughly half of each cycle.
+In CPVs more generally, individual flux dips last 5-50\% of each
+cycle\added{, and there are often multiple dips per cycle
+}\citep{Bouma2024}.  This implies that azimuthally-distributed
+material may be the norm for CPVs; a warped torus may be a more
+accurate picture than a clump.
 
 \citet{Townsend2005} outlined the physics of how rapidly-rotating
-stars with strong magnetic fields can support plasma tori \added{\citep[see
+stars with strong magnetic fields can support plasma tori
+\added{\citep[see
 also][]{Nakajima1985,Ferreira2000,Petit2013,Daley-Yates2024}}.  When
@@
 Keplerian corotation radii $R_{\rm c}$, the effective potential\added{
-  (gravitational plus centrifugal)} experienced by \added{plasma
-along any given field line }has a local minimum outside $R_{\rm c}$,
-which enables charged material to accumulate in a torus.  Warps can
-occur when there is misalignment between the spin and magnetic axes.
-In general, the\added{ regions} in these centrifugally-supported
+  (gravitational plus centrifugal)} experienced by \added{plasma along
+any given field line }has a local minimum outside $R_{\rm c}$, which
+enables charged material to accumulate in a torus.  Warps can occur
+when there is misalignment between the spin and magnetic axes.  In
+general, the\added{ regions} in these centrifugally-supported
 magnetospheres\added{ with the densest plasma accumulations} need
@@
 last accessed 23 April 2025.}; for a $\omega/\omega_{\rm
-c}$$\approx$0.5, edge-on system like TIC\,141146667, the photometric
+c}$$\approx$0.5 edge-on system like TIC\,141146667, the photometric
 eclipses have the correct shape, and the H$\alpha$ emission similarly
-exhibits double-peaked behavior.  The plasma in this model accumulates
-at antipodes 180$^\circ$ apart because the deepest local minima in the
-effective potential exist along the line of intersection between the
-rotational and magnetic planes (see Equation~22 of
-\citealt{Townsend2005}).
-
-To summarize, the evidence for warped plasma tori
-in TIC\,141146667 and CPVs more broadly is that 
-Figure~\ref{fig:spec} shows two plasma clumps separated
-by 180$^\circ$ in phase; the warped-torus model predicts both
-``W'' shaped photometric eclipses and double-peaked H$\alpha$
-morphology at quadrature; and CPV dips last 5-50\% of each cycle,
-indicating an azimuthally extended distribution of material.
+exhibits double-peaked behavior.  The plasma clumps in this model are
+180$^\circ$ apart because the deepest local minima in the effective
+potential exist along the line of intersection between the rotational
+and magnetic planes (see Equation~22 of \citealt{Townsend2005}).
+
+To summarize, the evidence for warped plasma tori in TIC\,141146667
+and CPVs more broadly is that Figure~\ref{fig:spec} shows two plasma
+clumps separated by 180$^\circ$ in phase; the warped-torus model
+predicts both ``W'' shaped photometric eclipses and double-peaked
+H$\alpha$ morphology at quadrature; and CPV dips last 5-50\% of each
+cycle, indicating an azimuthally extended distribution of material.
 \added{However, two challenges remain. First, the model predicts {\it
@@
 these discrepancies.  Overall, the evidence suggests a warped torus is
-a good first approximation, but one that will need refinement in future
-work.}
+a good first approximation, but one that will need refinement in
+future work.}
 
@@
 Microphysically, it is not obvious whether hydrogen alone can produce
-the broadband chromatic flux variations seen in CPVs.  The
-alternative is that charged dust could provide most of the
-opacity \citep{Sanderson2023}.  For
-TIC\,141146667, Figures~\ref{fig:fulllc}
-and~\ref{fig:spec} show that the transits of the 
-inner H$\alpha$ clump only partially overlap the complex
-photometric modulation.  This implies that some of the complex
-photometric dips must involve additional opacity sources or spatially
-distinct structures.
+the broadband chromatic flux variations seen in CPVs.  The alternative
+is that charged dust could provide most of the opacity
+\citep{Sanderson2023}.  For TIC\,141146667, Figures~\ref{fig:fulllc}
+and~\ref{fig:spec} show that the transits of the inner H$\alpha$ clump
+only partially overlap the complex photometric modulation.  This
+implies that some of the complex photometric dips must involve
+additional opacity sources or spatially distinct structures.
 
 Independent of this opacity question, our observations show that
-corotating clumps of cool plasma exist around a CPV.  While starspots do
-contribute smooth signals to CPV photometric variability, the existence
-of these clumps  would not be predicted by a ``starspot-only'' scenario
-\citep{Koen2021}.  Scenarios in which the circumstellar material is made
-only of dust are similarly ruled out.
+corotating clumps of cool plasma exist around a CPV.  While starspots
+do contribute smooth signals to CPV photometric variability, the
+existence of these clumps  would not be predicted by a
+``starspot-only'' scenario \citep{Koen2021}.  Scenarios in which the
+circumstellar material is made only of dust are similarly ruled out.
 
@@
 could originate either from the star or from an external source.
-Plausible external sources include an undetected old disk, comets, or a
-close-in exoplanet.  This latter scenario would make CPVs extrasolar
-analogs of the Jupiter-Io torus (e.g.~\citealt{Bagenal1981}, \citealt{Kislyakova2018}),
-although with a very different composition.
+Plausible external sources include an undetected old disk, comets, or
+a close-in exoplanet.  This latter scenario would make CPVs extrasolar
+analogs of the Jupiter-Io torus (e.g.~\citealt{Bagenal1981},
+\citealt{Kislyakova2018}), although with a very different composition.
 % (Because the Io ring has lots of sodium and S II (6717) emission.
@@
 
-The other CPV analog is the $\sigma$~Ori~E variables, a rare
-subset of B stars with radiatively-driven winds that accumulate into
-warped plasma tori \citep{Townsend2005}.  These tori tend
-to have dense antipodal accumulations of plasma sculpted by
-tilted-dipole magnetic fields; these clumps produce
-broadband optical variability through bound-free scattering
-\citep{Townsend2005} and Thomson scattering \citep{Berry2022}.  For
-$\sigma$~Ori~E and most of its analogs, the result is simple
-light curves that resemble eclipsing binaries, and time-dynamic
-H$\alpha$ spectra similar to Figure~\ref{fig:spec}.  The two
-known exceptions, HD~37776 and HD~64740, 
-have spectropolarimetric magnetic field maps indicating strong
-contributions from higher-order magnetic moments
-\citep{Kochukhov2011,Shultz2018} and complex light curves
-resembling CPVs \citep{Mikulasek2020,Bouma2024}.
-This suggests that the photometric complexity of CPVs may be related to
-magnetic fields with highly multipolar contributions.  
-\added{While this suggestion is consistent with the wide range of
-axisymmetric and non-axisymmetric topologies seen in mid- and late-M
-dwarfs
+The other CPV analog is the $\sigma$~Ori~E variables, a rare subset of
+B stars with radiatively-driven winds that accumulate into warped
+plasma tori \citep{Townsend2005}.  These tori tend to have dense
+antipodal accumulations of plasma sculpted by tilted-dipole magnetic
+fields; these clumps produce broadband optical variability through
+bound-free scattering \citep{Townsend2005} and Thomson scattering
+\citep{Berry2022}.  For $\sigma$~Ori~E and most of its analogs, the
+result is simple light curves that resemble eclipsing binaries, and
+time-dynamic H$\alpha$ spectra similar to Figure~\ref{fig:spec}.  The
+two known exceptions, HD~37776 and HD~64740, have spectropolarimetric
+magnetic field maps indicating strong contributions from higher-order
+magnetic moments \citep{Kochukhov2011,Shultz2018} and complex light
+curves resembling CPVs \citep{Mikulasek2020,Bouma2024}.  This suggests
+that the photometric complexity of CPVs may be related to magnetic
+fields with highly multipolar contributions.  \added{While this
+suggestion is consistent with the wide range of axisymmetric and
+non-axisymmetric topologies seen in mid- and late-M dwarfs
 (e.g.~\citealt{Donati2006,Kochukhov2017,Shulyak2019,Bellotti2024}),
@@
 
-Spectra of magnetically-active, rapidly rotating stars with a wide range
-of masses have been previously observed to exhibit sinusoidal
+Spectra of magnetically-active, rapidly rotating stars with a wide
+range of masses have been previously observed to exhibit sinusoidal
 time-varying Balmer emission
@@
 \citep{CollierCameron1989,CollierCameron1992,Cang2020}, comes from an
-analogy to quiescent solar prominences, cool condensations of plasma in
-the solar corona that can last days to weeks \citep{VialEngvold2015}.
-In the case of the Sun, these condensations fall back to the photosphere
-because gravity is stronger than any magnetic tension or centrifugal
-force capable of sustaining them.  However it has been understood at
-least since work by \citet{Donati2000} that these ``prominence systems''
-can be longitudinally extended, forming a trapped ring of plasma.  While
-the issue of why these previously known spectroscopic variables do
-not show complex photometric variability remains open, plausible
+analogy to quiescent solar prominences, cool condensations of plasma
+in the solar corona that can last days to weeks
+\citep{VialEngvold2015}.  In the case of the Sun, these condensations
+fall back to the photosphere because gravity is stronger than any
+magnetic tension or centrifugal force capable of sustaining them.
+However it has been understood at least since work by
+\citet{Donati2000} that these ``prominence systems'' can be
+longitudinally extended, forming a trapped ring of plasma.  While the
+issue of why these previously known spectroscopic variables do not
+show complex photometric variability remains open, plausible
 explanations include that they are not in the required transiting
@@
 
-%The role of the star's magnetic field could be better understood through
-%new observations, and new theory.  From the modeling perspective,
-%there is a need for rigid-field magnetohydrodynamic models to
-%go beyond previous work \citep{Townsend2008,Krticka2022}
-%and to explore what field topologies explain the observed light
-%curve shapes.  In particular, dynamo simulations of
-%fully-convective M dwarfs have suggested that global-scale mean fields
-%might be confined to a single hemisphere \citep{Brown2020}; such fields
-%would yield accumulation surfaces quite different from those that have
-%previously been explored.  Observationally, spectropolarimetry has the
-%potential to assess both the field strength and topology.  An
-%independent constraint on magnetic field topology may also come from
-%radio observations, which have shown \citep{Kaur2024} that CPVs emit
-%variable radio signals, including persistent and polarized components.
-%Detecting radio emission produced by an electron cyclotron maser
-%instability (e.g.~\citealt{Callingham2021}) in particular would provide
-%a measurement of the field strength at the site of the emitting region,
-%which could help clarify the magnetosphere's structure.
-
 It is currently unclear what, if any, relationship CPVs have to the
@@
 the CPV phenomenon \citep{Rebull2020}, and our data show that some of
-the flux dips occur when clumps of circumstellar
-material transit the star.  The geometric correction implies
-that an appreciable minority ($\gtrsim$10\%) of young M dwarfs---the
-rapidly rotating ones with centrifugal magnetospheres---host
-circumstellar environments similar to the CPVs.  Future studies that
-combine spectroscopic, polarimetric, and multi-wavelength
-observations, along with magnetohydrodynamic modeling, will be key to
-understanding the complex environments of these young
-stars.
+the flux dips occur when clumps of circumstellar material transit the
+star.  The geometric correction implies that an appreciable minority
+($\gtrsim$10\%) of young M dwarfs---the rapidly rotating ones with
+centrifugal magnetospheres---host circumstellar environments similar
+to the CPVs.  Future studies that combine spectroscopic, polarimetric,
+and multi-wavelength observations, along with magnetohydrodynamic
+modeling, will be key to understanding the complex environments of
+these young stars.
 
@@
 
-  The analyses in this article used data from TESS.  \added{The 2-minute
-  cadence observations from Sectors 41 \& 48 were from TESS DDT039
-  (PI: M.~Kunimoto) and the observations from Sector 75 were from TESS
-  G06030 (PI: L.~Bouma).}
-  The TESS data
-  can be accessed \added{through MAST }via
+  The analyses in this article used data from TESS.  \added{The
+  2-minute cadence observations from Sectors 41 \& 48 were from TESS
+  DDT039 (PI: M.~Kunimoto) and the observations from Sector 75 were
+  from TESS G06030 (PI: L.~Bouma).}
+  The TESS data can be accessed \added{through MAST }via
   DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
@@
   directorate.
-  TESS is a product of millions of hours of work by thousands of people, and
-  we thank the TESS team for their efforts to make the mission a
-  continued success.
+  TESS is a product of millions of hours of work by thousands of
+  people, and we thank the TESS team for their efforts to make the
+  mission a continued success.
   The HIRES data were obtained at the Keck Observatory, which exists
   through a similar scale of community effort.
-  We recognize the importance that the summit of Maunakea has always had
-  within the indigenous Hawaiian community, and we are grateful 
+  We recognize the importance that the summit of Maunakea has always
+  had within the indigenous Hawaiian community, and we are grateful
   for the opportunity to conduct observations from this mountain.
@@
 because they provided the best matches between the synthetic and
-observed spectra.  We averaged the redshift
-measurements over each order, and
-used the scatter of resulting velocity measurements between orders to
-assign the RV uncertainty at each epoch.  The uncertainty-weighted
-mean systemic velocity over all epochs on 17~February~2024 was
-$\gamma$=0.6$\pm$1.5\,\kms.  The relative radial velocities about this
-mean are listed in Table~\ref{tab:rv}.
+observed spectra.  We averaged the redshift measurements over each
+order, and used the scatter of resulting velocity measurements between
+orders to assign the RV uncertainty at each epoch.  The
+uncertainty-weighted mean systemic velocity over all epochs on
+17~February~2024 was $\gamma$=0.6$\pm$1.5\,\kms.  The relative radial
+velocities about this mean are listed in Table~\ref{tab:rv}.
 
@@
 based on its apparent size and rotation period is 130$\pm$4\,\kms.
-\added{While these measurements are consistent with an edge-on
-viewing geometry}, the formal constraint is rather weak, with
-$i$$>$63$^\circ$ at 2$\sigma$ (2.5$^{\rm th}$ percentile of the
-inclination posterior).
+\added{While these measurements are consistent with an edge-on viewing
+geometry}, the formal constraint is rather weak, with $i$$>$63$^\circ$
+at 2$\sigma$ (2.5$^{\rm th}$ percentile of the inclination posterior).
 
@@
 periods in the TESS data.  Previous work \citep{Bouma2024} has shown
-that $\approx$30\% of CPVs show evidence for binarity from RUWE, and $\approx$40\% of CPVs show
-evidence for binarity based on the presence of
-secondary photometric periods.  This agrees with analyses showing that
-multi-periodic low-mass stars are usually unresolved binaries
+that $\approx$30\% of CPVs show evidence for binarity from RUWE, and
+$\approx$40\% of CPVs show evidence for binarity based on the presence
+of secondary photometric periods.  This agrees with analyses showing
+that multi-periodic low-mass stars are usually unresolved binaries
 \citep{Tokovinin2018}.  Overall, the CPV binary fraction seems
@@
 (wide) binarity.  For TIC\,141146667 specifically, we find no
-evidence for stellar multiplicity. %, our data are minimally constraining
-%for the scenario of a low-luminosity companion
-%($F_1$/$F_2$$\lesssim$0.1) with apparent separation below 0$\farcs$1.
+evidence for stellar multiplicity.
 
@@
   \caption{
-    {\bf Spectral energy distribution} of broadband photometric magnitudes
-    (filled \added{cyan circles}) plotted over the best-fit BT-Settl stellar
-    atmosphere model \citep{Allard2012} and the associated photometric
-    predictions (empty \added{purple diamonds}).  This plot was made from an
-    adaptation of \texttt{astroARIADNE} \citep{Vines2022}.  The
-    photometry extends from the Gaia DR3 blue passband to WISE W3;
-    the W4 passband (22 $\mu$m) did not yield a confident detection.
-    This fit yields the star's temperature and size.  The lack of
-    excess infrared flux relative to the photospheric model sets an
-    upper limit on emission from circumstellar dust.
+    {\bf Spectral energy distribution} of broadband photometric
+    magnitudes (filled \added{cyan circles}) plotted over the best-fit
+    BT-Settl stellar atmosphere model \citep{Allard2012} and the
+    associated photometric predictions (empty \added{purple
+    diamonds}).  This plot was made from an adaptation of
+    \texttt{astroARIADNE} \citep{Vines2022}.  The photometry extends
+    from the Gaia DR3 blue passband to WISE W3; the W4 passband (22
+    $\mu$m) did not yield a confident detection.  This fit yields the
+    star's temperature and size.  The lack of excess infrared flux
+    relative to the photospheric model sets an upper limit on emission
+    from circumstellar dust.
     }
@@
 procedure described by \citet{Bouma2024}.  To summarize, this approach
-used \texttt{astroARIADNE} \citep{Vines2022} \added{to fit broadband magnitudes
-from Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$ with the
-BT-Settl stellar atmosphere models \citep{Allard2012}}.  \added{Free
-parameters included } the stellar effective temperature, radius,
-reddening, surface gravity, and metallicity.  The resulting best-fit
-SED is shown in Figure~\ref{fig:sed}.  This method has the most
-constraining power for the star's effective temperature (2972 $\pm$
-40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$).  We measured
-the star's spectral type to be M5.5Ve by visually comparing the HIRES
+used \texttt{astroARIADNE} \citep{Vines2022} \added{to fit broadband
+magnitudes from Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$
+with the BT-Settl stellar atmosphere models \citep{Allard2012}}.
+\added{Free parameters included } the stellar effective temperature,
+radius, reddening, surface gravity, and metallicity.  The resulting
+best-fit SED is shown in Figure~\ref{fig:sed}.  This method has the
+most constraining power for the star's effective temperature (2972
+$\pm$ 40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$).  We measured the
+star's spectral type to be M5.5Ve by visually comparing the HIRES
 spectra against the photometric standards tabulated by
@@
 
-{\it Age: No Obvious Association Membership}---In
-\citet{Bouma2024} we previously found that over 90\% of CPVs within
-100\,pc are associated with
-known young moving groups based on their positions and kinematics.
-TIC\,141146667 is in the minority.  We calculated the probability of
-TIC\,141146667 being part of any nearby known group using
-BANYAN\,$\Sigma$ v1.2 \citep{Gagne2018}.  That particular model
+{\it Age: No Obvious Association Membership}---In \citet{Bouma2024} we
+previously found that over 90\% of CPVs within 100\,pc are associated
+with known young moving groups based on their positions and
+kinematics.  TIC\,141146667 is in the minority.  We calculated the
+probability of TIC\,141146667 being part of any nearby known group
+using BANYAN\,$\Sigma$ v1.2 \citep{Gagne2018}.  That particular model
 classifies it as a field star at $>$99.9\% confidence.  We also
@@
 
-{\it Age: Lithium}---Lithium burning in the cores of low-mass stars has been
-studied for over sixty years
+{\it Age: Lithium}---Lithium burning in the cores of low-mass stars
+has been studied for over sixty years
 \citep[e.g.][]{Hayashi1963,Bildsten1997}.  \citet{Wood2023} provided a

### 2025-05-28 paper/ms.tex
update

@@
   \captionsetup{labelformat=moviefmt,labelsep=colon}
-	\caption{\textbf{Emission from circumstellar plasma orbiting
+	\caption{\textbf{Emission from plasma clumps orbiting
 TIC\,141146667.}
@@
   shows the spectral evolution over five hours.
-  {\bf a,} Average TESS light curve from 5 February 2024 to 26
+  {\bf a,} TESS light curve from 5 February 2024 to 26
   February 2024 folded on the \periodhr\ hour period.  Black
@@
   median-normalized H$\alpha$ light curve at $|v/v_{\rm eq}|<1$.
-  {\bf e,} As in Panel b, after subtracting the time-averaged
-  spectrum.  The line core shows H$\alpha$ excesses and decrements
+  {\bf e,} As in Panel b, after subtracting $f_{\langle t
+  \rangle}$.  The line core shows H$\alpha$ excesses and decrements
   advancing from the blue to red wings.
-  The asymmetric color stretch
-  is set to mirror the dynamic range of the data.
+  The asymmetric color stretch mirrors the dynamic range of the data.
   {\bf f,} Individual epochs of Panel e, visible in the online
-  movie.}
+  movie.  \added{A separate version with overplotted best-fit sinusoids is also
+  \href{https://lgbouma.com/movies/TIC141146667_sixpanel_sinusoids.mp4}{{\bf
+  available}}.}}
   \label{fig:spec}
@@
 circumstellar clumps, and its slow speed instead suggests it is
-associated with bright region on the star's surface.  Similarly, from
+associated with a bright region on the star's surface.  Similarly, from
 $\phi$=0.6-1.15 a 20\% deep absorption feature slowly crosses the
@@
 other bright and dark streaks passing across the line core \added{in
-Figure~\ref{fig:spec}e }are similarly ambiguous.
+Figure~\ref{fig:spec}e }is similarly ambiguous.
 
@@
 magnetic tension or centrifugal force capable of sustaining them.
-However it has been understood at least since work by
+However, it has been understood at least since work by
 \citet{Donati2000} that these ``prominence systems'' can be

### 2025-05-29 paper/ms.tex
update

@@
   \vspace{-0.2cm}
-  \caption{{\bf Evolution of TIC\,141146667 during the Keck/HIRES
+  \caption{{\bf Photometric evolution of TIC\,141146667 during the Keck/HIRES
   observation (green bar).}  {\bf a,} TESS simple aperture photometry.
-  Data gaps were caused by light from the Earth (BTJD 3356-3358.5) and
+  Data gaps were caused by stray light from the Earth (BTJD 3356-3358.5) and
   Moon (BTJD 3359.5-3360.5).  Raw two minute data are in gray; black
@@
   {\bf a,} TESS light curve from 5 February 2024 to 26
-  February 2024 folded on the \periodhr\ hour period.  Black
+  February 2024 folded on the 3.93\ hour period.  Black
   points are phase-averaged; gray are the raw data.
-  {\bf b,} Keck/HIRES H$\alpha$ spectra acquired on 17 February 2024.
+  {\bf b,} Keck/HIRES H$\alpha$ spectra from 17 February 2024.
   The continuum is set to unity, and the darkest color is at twice the
@@
   eq}|>1$, for the equatorial velocity $v_{\rm eq}$=130\,\kms).  While
-  emission in the line core comes from the star's chromosphere, the
+  emission within the line core comes from the star's chromosphere, the
   sinusoidal emission features are most readily described by a warped
@@
   {\bf f,} Individual epochs of Panel e, visible in the online
-  movie.  \added{A separate version with overplotted best-fit sinusoids is also
+  movie.  \added{A separate version with best-fit sinusoids overplotted is also
   \href{https://lgbouma.com/movies/TIC141146667_sixpanel_sinusoids.mp4}{{\bf
@@
 online\footnote{\url{http://user.astro.wisc.edu/\~townsend/static.php?ref=rrm-movies\#Download\_Bundles}
-last accessed 23 April 2025.}; for a $\omega/\omega_{\rm
+last accessed 28 May 2025.}; for a $\omega/\omega_{\rm
 c}$$\approx$0.5 edge-on system like TIC\,141146667, the photometric
@@
 Microphysically, it is not obvious whether hydrogen alone can produce
-the broadband chromatic flux variations seen in CPVs.  The alternative
+the chromatic broadband flux variations seen in CPVs.  The alternative
 is that charged dust could provide most of the opacity
@@
   30-150\,Myr. 
-  {\bf b,} An upper limit on photospheric lithium for TIC\,141146667
-  (green triangle) yields a lower bound on the star's age of
-  $\gtrsim$20\,Myr.  Comparison stars are from the Gaia-ESO survey
-  \citep{Jeffries2023}; rich clusters in these data include NGC\,2264
-  (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm \gamma}^2$\,Vel
-  (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2391 (42.0\,Myr),
-  and NGC\,2451A (50.0\,Myr).\added{ Measurement uncertainties are
-  large below $+$50\,m\AA; negative EW does not correspond to significant
-  emission.}}
+  {\bf b,} A dearth of photospheric lithium for TIC\,141146667 (yellow
+  triangle denotes 2$\sigma$ upper limit) yields a lower bound on the
+  star's age of $\gtrsim$20\,Myr.  Comparison stars are from the
+  Gaia-ESO survey \citep{Jeffries2023}; rich clusters in these data
+  include NGC\,2264 (4.5\,Myr), $\lambda$~Ori (8.7\,Myr), ${\rm
+  \gamma}^2$\,Vel (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2391
+  (42.0\,Myr), and NGC\,2451A (50.0\,Myr).\added{ Measurement
+  uncertainties are large below $+$50\,m\AA; negative EW does not
+  correspond to significant emission.}}
   \label{fig:age_diagnostics}

### 2025-05-29 drivers/plot_li_vs_population.py

@@ -114,9 +114,13 @@ def plot_li_vs_population() -> None:
         )
 
     ax.scatter(
-        2972, 107, marker='*', linewidth=0.5, color='yellow', s=110,
+        2972, 107, marker='v', linewidth=0.5, color='yellow', s=80,
         zorder=99, edgecolor='k'
     )
+    #ax.scatter(
+    #    2972, 107, marker='*', linewidth=0.5, color='yellow', s=110,
+    #    zorder=99, edgecolor='k'
+    #)
 
     # Add legend to indicate the age bins.
     ax.legend(loc="upper left", fontsize='x-small', framealpha=1,

### 2025-05-29 drivers/fit_orbits.py
cleaning for staging

@@ -30,7 +30,7 @@ def load_rvs(component_ix=None, applymask=True):
              0]
     # outer clump
     # 8&9 : absorption cancelled out the emission??
-    
+
     # based on "is there a good signal"?
     mask2 = [0,0,0,0,1,
              1,1,1,0,1, #9 = phi 0.54.  
@@ -201,12 +201,12 @@ def main(fittingstyle='leastsquares'):
         # store original error arrays for scaling separately in each fit
         original_rv_err = rv_err.copy()
         original__rv_err = _rv_err.copy()
-        
+
         # Estimate initial parameters
         K0 = (np.max(rv) - np.min(rv)) / 2
         P0 = 4/24
         t0_0 = time.min()
-        
+
         if fittingstyle == 'leastsquares':
             # Circular orbit fit using curve_fit
             try:
@@ -222,7 +222,7 @@ def main(fittingstyle='leastsquares'):
                 continue
         else:
             raise ValueError("Invalid fittingstyle. Choose 'leastsquares' or 'mcmc'.")
-        
+
         # Compute stats and scale errors for circular fit (leastsquares only)
         perr_circ = np.sqrt(np.diag(pcov_circ))
         red_chi2_circ, bic_circ = compute_stats(rv_circular, time, rv, original_rv_err, popt_circ)
@@ -238,7 +238,7 @@ def main(fittingstyle='leastsquares'):
         circ_csv = join('results/halpha_to_rv_timerseries', f'circular_fit_component_{ix}.csv')
         param_names_circ = ['K', 'P', 't0']
         save_fit_table(circ_csv, popt_circ, perr_circ, red_chi2_circ, bic_circ, param_names_circ)
-        
+
         # Append data for combined plot (use scaled _rv_err for consistency)
         if fittingstyle == 'leastsquares':
             rv_err = rv_err * scale_circ
@@ -259,7 +259,7 @@ def main(fittingstyle='leastsquares'):
             # For MCMC, store the posterior samples for plotting draws.
             **({'samples': samples} if fittingstyle=='mcmc' else {})
         })
-        
+
         t_fit = np.linspace(time.min(), time.max(), 1000)
         plt.errorbar(time, rv, yerr=rv_err, fmt='o', label='Data')
         plt.plot(t_fit, rv_circular(t_fit, *popt_circ), 'r-', label='Circular Fit')
[…]

### 2025-05-29 drivers/halpha_to_rv_timeseries.py

@@ -622,18 +622,6 @@ def halpha_to_rv_timeseries():
              0,0,0,0,0, #16(start) = phi 0.93
              0]
 
-    ##########################################
-    # Fit some sinusoids to RV vs time...
-    import IPython; IPython.embed()
-
-
-
-    #FIXME FIXME FIXME TODO TODO TODO
-    # GOTTA FIGURE OUT HOW TO DEAL WITH THE TRANSIT / SEOCONDAARY ECLIPSE WINDOW MASK.
-    # E.G. AROUND PHI = 0.0, THERE IS SUPPOSED EMISSION FROM TH EOUTER CLUMP WHICH SHOULD BE GONE 
-
-
-
 
 if __name__ == "__main__":
     halpha_to_rv_timeseries()

### 2025-05-29 drivers/plot_hrd.py
update

@@ -456,7 +456,7 @@ def plot_hrd(deredden=0, smalllims=0, cpvcomparison=0, addngc2516=0, showgrp=0,
         r = 0
         _l = l
         if '1411' in l:
-            s = 110
+            s = 140
             m = '*'
             lw = 0.3
         if 'Nearby' in l:
@@ -545,12 +545,11 @@ def plot_hrd(deredden=0, smalllims=0, cpvcomparison=0, addngc2516=0, showgrp=0,
 
 if __name__ == "__main__":
 
-    for showgrp in [0,1]:
-        plot_hrd(cpvcomparison=0, smalllims=1, deredden=1, addngc2516=0,
-                 showgrp=showgrp, addngc6475=0, addngc2632=1)
-    assert 0
-
     # cluster comparison
     for smalllim in [1,0]:
         for dr in [1,0]:
             plot_hrd(smalllims=smalllim, deredden=dr)
+
+    for showgrp in [0,1]:
+        plot_hrd(cpvcomparison=0, smalllims=1, deredden=1, addngc2516=0,
+                 showgrp=showgrp, addngc6475=0, addngc2632=1)

### 2025-05-29 paper/collect_figs.sh

@@ -19,6 +19,7 @@ cp $r/movie_sixpanel_specriver/TIC_141146667_science/specriver_141146667_Hα_001
 
 # Animated supporting: Movie of spectral timeseries
 cp $r/movie_sixpanel_specriver/TIC_141146667_science_wob/TIC141146667_sixpanel.mov m3.mov
+cp $r/movie_sixpanel_specriver/TIC_141146667_science_wob/TIC141146667_sixpanel_sinusoids.mov m3_bonus.mov
 
 ##########################################
 # supplementary
@@ -27,7 +28,7 @@ r="/Users/luke/Dropbox/proj/hotcold/drivers/results"
 
 cp $r/sed_fit/TIC_141146667/plots_irexcess/SED.pdf f4.pdf
 
-cp $r/hrd/hrd_smalllim_dereddened.pdf f5a.pdf
+cp $r/hrd/hrd_bprp_smalllim_dereddened.pdf f5a.pdf
 
 cp $r/li_ew/li_vs_population.pdf f5b.pdf
 

### 2025-05-29 drivers/run_SED_analysis.py
run_SED_analysis: add Ks/W1/W2 drop option

@@ -5,7 +5,8 @@ environment: (py38_ariadne)
 Citations: https://github.com/jvines/astroARIADNE/blob/master/citations.md
 """
 
-from astroARIADNE.star import Star
+#from astroARIADNE.star import Star
+from astroARIADNE.bonusstar import Star
 from astroARIADNE.fitter import Fitter
 #from astroARIADNE.plotter import SEDPlotter
 from astroARIADNE.bonusplotter import SEDPlotter
@@ -52,7 +53,7 @@ knownfailures = {
     ] },
 }
 
-def run_SED_analysis(ticid, trimlist=None, uniformpriors=0):
+def run_SED_analysis(ticid, trimlist=None, uniformpriors=0, dropWISE=0):
     """
     Run CQV-specific SED analysis.  Priors assume the star is a nearby M-dwarf
     if uniformpriors==0, else assumes uniform priors.
@@ -68,6 +69,9 @@ def run_SED_analysis(ticid, trimlist=None, uniformpriors=0):
 
     Args:
         ticid (str): e.g. "402980664"
+
+        dropWISE (bool): if true, drops WISE (all bands) from the fitting (not from
+        plots).  Drops 2MASS KS too.
 
     Kwargs: list of quad tuples, each entry in form (>xmin, <xmax, >ymin, <ymax).
     E.g., to exclude everything above 1e-9 erg/cm2/s, and below 0.4 micron in
@@ -89,13 +93,15 @@ def run_SED_analysis(ticid, trimlist=None, uniformpriors=0):
     starname = f'TIC_{ticid}'
     g_id = int(gdr2_df.dr2_source_id)
 
-    out_folder = join(RESULTSDIR, f'{starname}')
+    dwise = '' if not dropWISE else '_dropWISE'
+    out_folder = join(RESULTSDIR, f'{starname}{dwise}')
     if not os.path.exists(out_folder): os.mkdir(out_folder)
 
     if ticid != '368129164':
         # NOTE: the "g_id" constructor here is actually (incorrectly!) assuming Gaia DR3 source_id's.
         # for TIC 141146667, this is ok because they are the same.
-        s = Star(starname.replace("_"," "), ra, dec, g_id=g_id)
+        s = Star(starname.replace("_"," "), ra, dec, g_id=g_id,
+                 dropWISE=dropWISE)
 
     if ticid == '368129164':
         # missing parallax
[…]

### 2025-06-09 paper/ms.tex
update

@@
 % upon AAS submission
-\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex7}
+%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex7}
 %\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex7}
 % drafting / arxiv
-%\documentclass[11pt,twocolumn,modern]{aastex7}
+\documentclass[11pt,twocolumn,tighten]{aastex7}
 %\turnoffedit
@@
 \received{23 April 2025}
-\revised{--}
-\accepted{--}
+\revised{29 May 2025}
+\accepted{6 June 2025}
 \shorttitle{CPV Plasma Torus}
@@
   \vspace{-0.2cm}
-  \caption{{\bf Photometric evolution of TIC\,141146667 during the Keck/HIRES
+  \caption{{\bf Photometric evolution of TIC\,141146667 around the Keck/HIRES
   observation (green bar).}  {\bf a,} TESS simple aperture photometry.
@@
   {\bf f,} Individual epochs of Panel e, visible in the online
-  movie.  \added{A separate version with best-fit sinusoids overplotted is also
+  movie.  \added{A separate version with best-fit sinusoids from
+  Appendix~\ref{subsec:halpha} overplotted is also
   \href{https://lgbouma.com/movies/TIC141146667_sixpanel_sinusoids.mp4}{{\bf
@@
 result is simple light curves that resemble eclipsing binaries, and
-time-dynamic H$\alpha$ spectra similar to Figure~\ref{fig:spec}.  The
-two known exceptions, HD~37776 and HD~64740, have spectropolarimetric
-magnetic field maps indicating strong contributions from higher-order
-magnetic moments \citep{Kochukhov2011,Shultz2018} and complex light
-curves resembling CPVs \citep{Mikulasek2020,Bouma2024}.  This suggests
-that the photometric complexity of CPVs may be related to magnetic
-fields with highly multipolar contributions.  \added{While this
-suggestion is consistent with the wide range of axisymmetric and
-non-axisymmetric topologies seen in mid- and late-M dwarfs
+time-dynamic H$\alpha$ spectra similar to Figure~\ref{fig:spec}. 
+\added{The few known exceptions---HD~37776, HD~64740, and HD~176582---}have complex
+light curves resembling CPVs \citep{Mikulasek2020,Bouma2024} and
+spectropolarimetric measurements that suggest non-dipolar field
+contributions \citep{Kochukhov2011,Shultz2018}.  This suggests that
+the photometric complexity of CPVs may be related to magnetic fields
+with highly multipolar contributions.  \added{While this suggestion is
+consistent with the wide range of axisymmetric and non-axisymmetric
+topologies seen in mid- and late-M dwarfs
 (e.g.~\citealt{Donati2006,Kochukhov2017,Shulyak2019,Bellotti2024}),
@@
   conversations that significantly informed this work; J.~Spake,
-  J.~Winn, J.-F~Donati, and R.~Townsend for feedback on the
+  J.~Winn, J.-F~Donati, R.~Townsend, and O.~Kochukhov for feedback on the
   manuscript; and A.~Howard and H.~Isaacson for their assistance

### 2025-06-09 paper/ms.tex
update

@@
 
-  The analyses in this article used data from TESS.  \added{The
+  The analyses in this article used data from TESS \citep{TESS2min}.  \added{The
   2-minute cadence observations from Sectors 41 \& 48 were from TESS
@@
   from TESS G06030 (PI: L.~Bouma).}
-  The TESS data can be accessed \added{through MAST }via
-  DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
   Funding for the TESS mission is provided by NASA’s Science Mission

### 2025-06-10 paper/ms.tex
ran clean.html

@@
   CPV.  These data support the idea that young, rapidly-rotating M
-  dwarfs can sustain warped \added{tori of cool plasma, similar to
-  other rapidly-rotating magnetic stars.}
-  \added{Outstanding questions include whether dust clumps 
+  dwarfs can sustain warped tori of cool plasma, similar to
+  other rapidly-rotating magnetic stars.
+  Outstanding questions include whether dust clumps 
   in these plasma tori explain CPV light curves, and
   whether the tori originate from the star or are fed by external
-  sources.}
+  sources.
   Rough estimates suggest $\gtrsim$10\% of M dwarfs host
@@
 remain challenging to quantify.  Understanding these environments is
-crucial because they directly impact atmospheric retention and\added{,
-ultimately,} habitability.
+crucial because they directly impact atmospheric retention and,
+ultimately, habitability.
 
@@
   switch occurred near BTJD 3353, and the dip at $\phi$$\approx$0.8
-  \added{became less pronounced}.  While the \added{dip spanning
-  $\phi$=0.6-1.1} was present both before and after the HIRES
+  became less pronounced.  While the dip spanning
+  $\phi$=0.6-1.1 was present both before and after the HIRES
   sequence, its photometric shape evolved during the data gap.  The
@@
   {\bf f,} Individual epochs of Panel e, visible in the online
-  movie.  \added{A separate version with best-fit sinusoids from
+  movie.  A separate version with best-fit sinusoids from
   Appendix~\ref{subsec:halpha} overplotted is also
   \href{https://lgbouma.com/movies/TIC141146667_sixpanel_sinusoids.mp4}{{\bf
-  available}}.}}
+  available}}.}
   \label{fig:spec}
@@
 observations spanned the second half of the night, from 10:47 to 16:13
-(UT).  \added{We opted for a fixed 15 minute cadence, and} used the C2
+(UT).  We opted for a fixed 15 minute cadence, and used the C2
 decker (0$\farcs$86$\times$14$\farcs$0) in the red configuration,
@@
 TIC\,141146666 ($T$=14.5), is 25$''$ from TIC\,141146667 and is
-photometrically \added{quiet}; crowding is not a concern.
+photometrically quiet; crowding is not a concern.
 
@@
 Figure~\ref{fig:spec} shows the TESS and HIRES data from February
-2024.  The spectra \added{(Panels b,c)} show emission in H$\alpha$
+2024.  The spectra (Panels b,c) show emission in H$\alpha$
 beyond the star's equatorial velocity, $v_{\rm eq}$, of 130\,\kms.
@@
 with the photometric \periodhr\ hour period, to within two minutes for
-the \added{inner} component.
+the inner component.
 
@@
 partially-ionized hydrogen to corotate with the star.  Based on the
-observed sinusoidal periods and velocities, this \added{material is
-not moving on a Keplerian orbit}; it is \added{magnetically forced to
-co-rotate with the star}.  The velocity semi-amplitude of the
+observed sinusoidal periods and velocities, this material is
+not moving on a Keplerian orbit; it is magnetically forced to
+co-rotate with the star.  The velocity semi-amplitude of the
 sinusoids gives the mean distance of each clump from the stellar
-\added{rotation axis}: 2.07\,$R_\star$ and 2.88\,$R_\star$ for the
+rotation axis: 2.07\,$R_\star$ and 2.88\,$R_\star$ for the
 inner clumps, and 3.88\,$R_\star$ for the outer clump.   These clumps
@@
 transit coincides with the latter half of the complex eclipse feature
-in the TESS data \added{(see Figure~\ref{fig:fulllc} and Panels a and
-b of Figure~\ref{fig:spec})}.
-
-The H$\alpha$ line core\added{, visible in Panels e and f of
-Figure~\ref{fig:spec}, }is more complex.  At $|\Delta v / v_{\rm
+in the TESS data (see Figure~\ref{fig:fulllc} and Panels a and
+b of Figure~\ref{fig:spec}).
+
+The H$\alpha$ line core, visible in Panels e and f of
+Figure~\ref{fig:spec}, is more complex.  At $|\Delta v / v_{\rm
 eq}|<1$, most observed H$\alpha$ photons come from the star's
-chromosphere; \added{variability in the stellar emission line can be
+chromosphere; variability in the stellar emission line can be
 caused by circumstellar material, bright regions, or dark regions
-crossing the star's surface}.  Figure~\ref{fig:spec}e suggests that
-\added{all three effects occur in TIC\,141146667}.  For instance, from
+crossing the star's surface.  Figure~\ref{fig:spec}e suggests that
+all three effects occur in TIC\,141146667.  For instance, from
 $\phi$=0-0.3, double-peaked emission is visible both on and off-limb;
@@
 extended component of the circumstellar material.  The origin of the
-other bright and dark streaks passing across the line core \added{in
-Figure~\ref{fig:spec}e }is similarly ambiguous.
-
-\added{Figure~\ref{fig:spec}d shows} a final exercise to quantify the
-behavior of the line core, by summing the \added{H$\alpha$} flux at
+other bright and dark streaks passing across the line core in
+Figure~\ref{fig:spec}e is similarly ambiguous.
+
+Figure~\ref{fig:spec}d shows a final exercise to quantify the
+behavior of the line core, by summing the H$\alpha$ flux at
 $|\Delta v / v_{\rm eq}|<1$.  This panel shows that changes in the
-line core flux \added{($f_{\rm H\alpha\ core}$)} correlate with the
+line core flux ($f_{\rm H\alpha\ core}$) correlate with the
 broadband variability throughout most of the light curve, except near
@@
 clump and the occultation of the lower-velocity clump.
-\added{Spectroscopic transits may therefore not always be associated
-with photometric transits.}
+Spectroscopic transits may therefore not always be associated
+with photometric transits.
 
@@
 spectra require plasma with a significant population of hydrogen in
-the $n$=3 excited state, \added{with }minimal evidence for
+the $n$=3 excited state, with minimal evidence for
 higher-order excitations.  Most of this H$\alpha$ emission originates
@@
 In CPVs more generally, individual flux dips last 5-50\% of each
-cycle\added{, and there are often multiple dips per cycle
-}\citep{Bouma2024}.  This implies that azimuthally-distributed
+cycle, and there are often multiple dips per cycle
+\citep{Bouma2024}.  This implies that azimuthally-distributed
 material may be the norm for CPVs; a warped torus may be a more
@@
 stars with strong magnetic fields can support plasma tori
-\added{\citep[see
-also][]{Nakajima1985,Ferreira2000,Petit2013,Daley-Yates2024}}.  When
+\citep[see
+also][]{Nakajima1985,Ferreira2000,Petit2013,Daley-Yates2024}.  When
 the magnetospheric radii $R_{\rm m}$ of such stars exceeds their
-Keplerian corotation radii $R_{\rm c}$, the effective potential\added{
-  (gravitational plus centrifugal)} experienced by \added{plasma along
-any given field line }has a local minimum outside $R_{\rm c}$, which
+Keplerian corotation radii $R_{\rm c}$, the effective potential
+  (gravitational plus centrifugal) experienced by plasma along
+any given field line has a local minimum outside $R_{\rm c}$, which
 enables charged material to accumulate in a torus.  Warps can occur
 when there is misalignment between the spin and magnetic axes.  In
-general, the\added{ regions} in these centrifugally-supported
-magnetospheres\added{ with the densest plasma accumulations} need
+general, the regions in these centrifugally-supported
+magnetospheres with the densest plasma accumulations need
 neither transit nor be opaque in broadband optical light.
@@
 cycle, indicating an azimuthally extended distribution of material.
-\added{However, two challenges remain. First, the model predicts {\it
+However, two challenges remain. First, the model predicts {\it
 two} W-shaped eclipses per cycle.  Second, it predicts that the
@@
 a good first approximation, but one that will need refinement in
-future work.}
+future work.
 
@@
 time-dynamic H$\alpha$ spectra similar to Figure~\ref{fig:spec}. 
-\added{The few known exceptions---HD~37776, HD~64740, and HD~176582---}have complex
+The few known exceptions---HD~37776, HD~64740, and HD~176582---have complex
 light curves resembling CPVs \citep{Mikulasek2020,Bouma2024} and
-spectropolarimetric measurements that suggest non-dipolar field
-contributions \citep{Kochukhov2011,Shultz2018}.  This suggests that
-the photometric complexity of CPVs may be related to magnetic fields
-with highly multipolar contributions.  \added{While this suggestion is
-consistent with the wide range of axisymmetric and non-axisymmetric
-topologies seen in mid- and late-M dwarfs
+spectropolarimetric measurements that may suggest non-dipolar field
+contributions \citep{Kochukhov2011,Shultz2018}.  
+The photometric complexity of CPVs may therefore be related to
+magnetic fields with highly multipolar contributions.  While this
+suggestion is consistent with the wide range of axisymmetric and
+non-axisymmetric topologies seen in mid- and late-M dwarfs
 (e.g.~\citealt{Donati2006,Kochukhov2017,Shulyak2019,Bellotti2024}),
 future work is needed to verify whether CPVs indeed select for
-complex, non-axisymmetric fields.}
+complex, non-axisymmetric fields.
 
@@
 spectroscopic variability of these stars, and that of the analogous
-transient \added{H$\alpha$ }absorption features
+transient H$\alpha$ absorption features
 \citep{CollierCameron1989,CollierCameron1992,Cang2020}, comes from an
@@
 scattering in a plasma transiting over a spotted star might
-also produce chromatic features \citep{Rackham2018}.  \added{This
-degeneracy is alleviated in the infrared, where the} composition and
+also produce chromatic features \citep{Rackham2018}.  This
+degeneracy is alleviated in the infrared, where the composition and
 size distribution of any dust that is present could be determined by
@@
 
-\added{Future models could take a range of steps to clarify the origin
+Future models could take a range of steps to clarify the origin
 of CPVs.  A first step for magnetohydrodynamic models that can
@@
 performed. Whether dust grains can form in these plasma clumps
-similarly deserves attention.}
+similarly deserves attention.
 
@@
 
-  The analyses in this article used data from TESS \citep{TESS2min}.  \added{The
+  The analyses in this article used data from TESS \citep{TESS2min}.  The
   2-minute cadence observations from Sectors 41 \& 48 were from TESS
   DDT039 (PI: M.~Kunimoto) and the observations from Sector 75 were
-  from TESS G06030 (PI: L.~Bouma).}
+  from TESS G06030 (PI: L.~Bouma).
   Funding for the TESS mission is provided by NASA’s Science Mission
@@
 {\it Radial Velocity}---We measured the radial velocities of
-TIC\,141146667 \added{(Gaia DR3 860453786736413568) }from our HIRES
-spectra using a \added{custom }pipeline.  Our method was based on
-template-matching against synthetic \added{PHOENIX }spectra
-\citep{Husser2013}, \added{and was }calibrated \added{against }the
+TIC\,141146667 (Gaia DR3 860453786736413568) from our HIRES
+spectra using a custom pipeline.  Our method was based on
+template-matching against synthetic PHOENIX spectra
+\citep{Husser2013}, and was calibrated against the
 standard stars described by \citet{Chubak2012}.  We used velocity
@@
 based on its apparent size and rotation period is 130$\pm$4\,\kms.
-\added{While these measurements are consistent with an edge-on viewing
-geometry}, the formal constraint is rather weak, with $i$$>$63$^\circ$
+While these measurements are consistent with an edge-on viewing
+geometry, the formal constraint is rather weak, with $i$$>$63$^\circ$
 at 2$\sigma$ (2.5$^{\rm th}$ percentile of the inclination posterior).
@@
     {\bf Spectral energy distribution} of broadband photometric
-    magnitudes (filled \added{cyan circles}) plotted over the best-fit
+    magnitudes (filled cyan circles) plotted over the best-fit
     BT-Settl stellar atmosphere model \citep{Allard2012} and the
-    associated photometric predictions (empty \added{purple
-    diamonds}).  This plot was made from an adaptation of
+    associated photometric predictions (empty purple
+    diamonds).  This plot was made from an adaptation of
     \texttt{astroARIADNE} \citep{Vines2022}.  The photometry extends
@@
 procedure described by \citet{Bouma2024}.  To summarize, this approach
-used \texttt{astroARIADNE} \citep{Vines2022} \added{to fit broadband
+used \texttt{astroARIADNE} \citep{Vines2022} to fit broadband
 magnitudes from Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$
-with the BT-Settl stellar atmosphere models \citep{Allard2012}}.
-\added{Free parameters included } the stellar effective temperature,
+with the BT-Settl stellar atmosphere models \citep{Allard2012}.
+Free parameters included  the stellar effective temperature,
 radius, reddening, surface gravity, and metallicity.  The resulting
@@
   \gamma}^2$\,Vel (16.4\,Myr), NGC\,2547 (35.0\,Myr), IC\,2391
-  (42.0\,Myr), and NGC\,2451A (50.0\,Myr).\added{ Measurement
+  (42.0\,Myr), and NGC\,2451A (50.0\,Myr). Measurement
   uncertainties are large below $+$50\,m\AA; negative EW does not
-  correspond to significant emission.}}
+  correspond to significant emission.}
   \label{fig:age_diagnostics}
@@
 redder and more luminous than single stars in any given
-cluster\added{; they also found suggestive evidence for either
+cluster; they also found suggestive evidence for either
 hotspots or emission from dust based on analysis
@@
 inflation, dust emission, and photometric binarity. Rather than
-adopting a particular model isochrone framework, we instead visually}
+adopting a particular model isochrone framework, we instead visually
 take the star's location in the color--absolute magnitude diagram
@@
 the sample variance of the residuals.
-\added{The middle columns of
+The middle columns of
 Figure~\ref{fig:halphamodel} show the results; a table of the fitted means,
 amplitudes, and standard deviations for each component is available
-upon request.}
+upon request.
 
@@
 
-Accounting for these caveats, we used the \added{best-fit parameters
-from the multi-gaussian model }to quantify the orbital periods and
+Accounting for these caveats, we used the best-fit parameters
+from the multi-gaussian model to quantify the orbital periods and
 velocity semi-amplitudes of the clumps.  Figure~\ref{fig:orbits}a
@@
 For a uniform density clump, this suggests a total gas mass of $M_{\rm
-gas}\approx 2\times10^{17}$\,g\added{, which is similar to masses derived for
-plasma clumps around other cool stars \citep{VillarrealDAngelo2019}}.  We emphasize that
+gas}\approx 2\times10^{17}$\,g, which is similar to masses derived for
+plasma clumps around other cool stars \citep{VillarrealDAngelo2019}.  We emphasize that
 Equation~\ref{eq:numdensity} in intended to provide only an order of

### 2025-06-10 paper/ms.tex
update

@@
   show structured, periodic optical light curves suggestive of
-  transiting opaque material that corotates with the star.  However, the
-  composition, origin, and even the existence of this material are
+  transiting opaque material that corotates with the star.  However,
+  the composition, origin, and even the existence of this material are
   uncertain. The main alternative hypothesis is that these complex
@@
   CPV.  These data support the idea that young, rapidly-rotating M
-  dwarfs can sustain warped tori of cool plasma, similar to
-  other rapidly-rotating magnetic stars.
-  Outstanding questions include whether dust clumps 
-  in these plasma tori explain CPV light curves, and
-  whether the tori originate from the star or are fed by external
-  sources.
-  Rough estimates suggest $\gtrsim$10\% of M dwarfs host
+  dwarfs can sustain warped tori of cool plasma, similar to other
+  rapidly-rotating magnetic stars.  Outstanding questions include
+  whether dust clumps in these plasma tori explain CPV light curves,
+  and whether the tori originate from the star or are fed by external
+  sources.  Rough estimates suggest $\gtrsim$10\% of M dwarfs host
   similar structures during their early lives.
@@
   stellar rotation, and (we hypothesize) of corotating clumps of
-  circumstellar material.  Raw data acquired at two minute cadence
-  are in gray; black averages to 100 points per cycle.  
-  The sharp photometric features persist
-  for tens to thousands of rotational cycles. }
+  circumstellar material.  Raw data acquired at two minute cadence are
+  in gray; black averages to 100 points per cycle.  The sharp
+  photometric features persist for tens to thousands of rotational
+  cycles. }
   \label{fig:lc}
@@
 %
-$\langle$EW$_{\rm H\alpha}$$\rangle$    & Time-averaged H$\alpha$ line core                              &  7.2 $\pm$ 0.2   & 4 \\ 
+$\langle$EW$_{\rm H\alpha}$$\rangle$\dotfill
+                                        & Time-averaged H$\alpha$ line core\dotfill                      &  7.2 $\pm$ 0.2   & 4 \\ 
                                         & \hspace{3pt} equivalent width (\AA)	                           &                      \\
@@
   \vspace{-0.2cm}
-  \caption{{\bf Photometric evolution of TIC\,141146667 around the Keck/HIRES
-  observation (green bar).}  {\bf a,} TESS simple aperture photometry.
-  Data gaps were caused by stray light from the Earth (BTJD 3356-3358.5) and
-  Moon (BTJD 3359.5-3360.5).  Raw two minute data are in gray; black
-  time-averages to ten minute sampling.  {\bf b-c,} Folded TESS light
-  curve before and after spectroscopy.  Black now phase-averages to
-  100 points per 3.93\ hour cycle.  During BTJD 3352-3356, a state
-  switch occurred near BTJD 3353, and the dip at $\phi$$\approx$0.8
-  became less pronounced.  While the dip spanning
-  $\phi$=0.6-1.1 was present both before and after the HIRES
-  sequence, its photometric shape evolved during the data gap.  The
-  orange bar denotes times of spectroscopic transits for the inner two
-  H$\alpha$ clumps observed with HIRES (see Figure~\ref{fig:spec}).}
+  \caption{{\bf Photometric evolution of TIC\,141146667 around the
+  Keck/HIRES observation (green bar).}  {\bf a,} TESS simple aperture
+  photometry.  Data gaps were caused by stray light from the Earth
+  (BTJD 3356-3358.5) and Moon (BTJD 3359.5-3360.5).  Raw two minute
+  data are in gray; black time-averages to ten minute sampling.  {\bf
+  b-c,} Folded TESS light curve before and after spectroscopy.  Black
+  now phase-averages to 100 points per 3.93\ hour cycle.  During BTJD
+  3352-3356, a state switch occurred near BTJD 3353, and the dip at
+  $\phi$$\approx$0.8 became less pronounced.  While the dip spanning
+  $\phi$=0.6-1.1 was present both before and after the HIRES sequence,
+  its photometric shape evolved during the data gap.  The orange bar
+  denotes times of spectroscopic transits for the inner two H$\alpha$
+  clumps observed with HIRES (see Figure~\ref{fig:spec}).}
   \label{fig:fulllc}
@@
   \href{https://lgbouma.com/movies/TIC141146667_sixpanel.mp4}{{\bf
-  available here}},
-  shows the spectral evolution over five hours.
-  {\bf a,} TESS light curve from 5 February 2024 to 26
-  February 2024 folded on the 3.93\ hour period.  Black
-  points are phase-averaged; gray are the raw data.
-  {\bf b,} Keck/HIRES H$\alpha$ spectra from 17 February 2024.
-  The continuum is set to unity, and the darkest color is at twice the
+  available here}}, shows the spectral evolution over five hours.
+  {\bf a,} TESS light curve from 5 February 2024 to 26 February 2024
+  folded on the 3.93\ hour period.  Black points are phase-averaged;
+  gray are the raw data.
+  {\bf b,} Keck/HIRES H$\alpha$ spectra from 17 February 2024.  The
+  continuum is set to unity, and the darkest color is at twice the
   continuum to accentuate emission outside the line core ($|v/v_{\rm
   eq}|>1$, for the equatorial velocity $v_{\rm eq}$=130\,\kms).  While
-  emission within the line core comes from the star's chromosphere, the
-  sinusoidal emission features are most readily described by a warped
-  plasma torus.
+  emission within the line core comes from the star's chromosphere,
+  the sinusoidal emission features are most readily described by a
+  warped plasma torus.
   {\bf c,} Individual epochs of Panel b, visible in the online movie.
@@
   \rangle}$.
-  {\bf d,} As in Panel a, but overplotting the
-  median-normalized H$\alpha$ light curve at $|v/v_{\rm eq}|<1$.
-  {\bf e,} As in Panel b, after subtracting $f_{\langle t
-  \rangle}$.  The line core shows H$\alpha$ excesses and decrements
-  advancing from the blue to red wings.
-  The asymmetric color stretch mirrors the dynamic range of the data.
-  {\bf f,} Individual epochs of Panel e, visible in the online
-  movie.  A separate version with best-fit sinusoids from
+  {\bf d,} As in Panel a, but overplotting the median-normalized
+  H$\alpha$ light curve at $|v/v_{\rm eq}|<1$.
+  {\bf e,} As in Panel b, after subtracting $f_{\langle t \rangle}$.
+  The line core shows H$\alpha$ excesses and decrements advancing from
+  the blue to red wings.  The asymmetric color stretch mirrors the
+  dynamic range of the data.
+  {\bf f,} Individual epochs of Panel e, visible in the online movie.
+  A separate version with best-fit sinusoids from
   Appendix~\ref{subsec:halpha} overplotted is also
@@
 observations spanned the second half of the night, from 10:47 to 16:13
-(UT).  We opted for a fixed 15 minute cadence, and used the C2
-decker (0$\farcs$86$\times$14$\farcs$0) in the red configuration,
-yielding a resolution $R$$\approx$45{,}000 ($\delta
-v$$\approx$6.7\,\kms).  Strong winds contributed to 1$''$-1\farcs5
-seeing, but conditions were otherwise favorable.  We reduced the
-echelleogram using the standard techniques of the California Planet
-Survey \citep{Howard2010}.
+(UT).  We opted for a fixed 15 minute cadence, and used the C2 decker
+(0$\farcs$86$\times$14$\farcs$0) in the red configuration, yielding a
+resolution $R$$\approx$45{,}000 ($\delta v$$\approx$6.7\,\kms).
+Strong winds contributed to 1$''$-1\farcs5 seeing, but conditions were
+otherwise favorable.  We reduced the echelleogram using the standard
+techniques of the California Planet Survey \citep{Howard2010}.
 
@@
 Figure~\ref{fig:spec} shows the TESS and HIRES data from February
-2024.  The spectra (Panels b,c) show emission in H$\alpha$
-beyond the star's equatorial velocity, $v_{\rm eq}$, of 130\,\kms.
-There are at least two distinct emission components, 180$^\circ$ apart
-in phase.  The inner component at lower velocities has clearer
-sinusoidal behaviour in time and is double-peaked, with peak
-semi-amplitudes of 2.07\,$v_{\rm eq}$ and 2.88\,$v_{\rm eq}$ (see
+2024.  The spectra (Panels b,c) show emission in H$\alpha$ beyond the
+star's equatorial velocity, $v_{\rm eq}$, of 130\,\kms.  There are at
+least two distinct emission components, 180$^\circ$ apart in phase.
+The inner component at lower velocities has clearer sinusoidal
+behaviour in time and is double-peaked, with peak semi-amplitudes of
+2.07\,$v_{\rm eq}$ and 2.88\,$v_{\rm eq}$ (see
 Appendix~\ref{subsec:halpha}).  There is significant non-periodic
@@
 partially-ionized hydrogen to corotate with the star.  Based on the
-observed sinusoidal periods and velocities, this material is
-not moving on a Keplerian orbit; it is magnetically forced to
-co-rotate with the star.  The velocity semi-amplitude of the
-sinusoids gives the mean distance of each clump from the stellar
-rotation axis: 2.07\,$R_\star$ and 2.88\,$R_\star$ for the
-inner clumps, and 3.88\,$R_\star$ for the outer clump.   These clumps
-transit in front of the star when passing from negative to positive
-velocity.  The transits of the two inner clumps last $\approx$22\% of
-each cycle, from $\phi$=-0.1 to $\phi$=+0.12.  This spectroscopic
-transit coincides with the latter half of the complex eclipse feature
-in the TESS data (see Figure~\ref{fig:fulllc} and Panels a and
-b of Figure~\ref{fig:spec}).
+observed sinusoidal periods and velocities, this material is not
+moving on a Keplerian orbit; it is magnetically forced to co-rotate
+with the star.  The velocity semi-amplitude of the sinusoids gives the
+mean distance of each clump from the stellar rotation axis:
+2.07\,$R_\star$ and 2.88\,$R_\star$ for the inner clumps, and
+3.88\,$R_\star$ for the outer clump.   These clumps transit in front
+of the star when passing from negative to positive velocity.  The
+transits of the two inner clumps last $\approx$22\% of each cycle,
+from $\phi$=-0.1 to $\phi$=+0.12.  This spectroscopic transit
+coincides with the latter half of the complex eclipse feature in the
+TESS data (see Figure~\ref{fig:fulllc} and Panels a and b of
+Figure~\ref{fig:spec}).
 
@@
 eq}|<1$, most observed H$\alpha$ photons come from the star's
-chromosphere; variability in the stellar emission line can be
-caused by circumstellar material, bright regions, or dark regions
-crossing the star's surface.  Figure~\ref{fig:spec}e suggests that
-all three effects occur in TIC\,141146667.  For instance, from
-$\phi$=0-0.3, double-peaked emission is visible both on and off-limb;
-this feature is circumstellar in origin.  However, the emission
-feature that crosses the star from $\phi$=0.4-0.9 is brighter than the
+chromosphere; variability in the stellar emission line can be caused
+by circumstellar material, bright regions, or dark regions crossing
+the star's surface.  Figure~\ref{fig:spec}e suggests that all three
+effects occur in TIC\,141146667.  For instance, from $\phi$=0-0.3,
+double-peaked emission is visible both on and off-limb; this feature
+is circumstellar in origin.  However, the emission feature that
+crosses the star from $\phi$=0.4-0.9 is brighter than the
 circumstellar clumps, and its slow speed instead suggests it is
-associated with a bright region on the star's surface.  Similarly, from
-$\phi$=0.6-1.15 a 20\% deep absorption feature slowly crosses the
+associated with a bright region on the star's surface.  Similarly,
+from $\phi$=0.6-1.15 a 20\% deep absorption feature slowly crosses the
 H$\alpha$ line profile.  This feature could be either a
@@
 
-Figure~\ref{fig:spec}d shows a final exercise to quantify the
-behavior of the line core, by summing the H$\alpha$ flux at
-$|\Delta v / v_{\rm eq}|<1$.  This panel shows that changes in the
-line core flux ($f_{\rm H\alpha\ core}$) correlate with the
-broadband variability throughout most of the light curve, except near
-$\phi$$\approx$0.5, corresponding to the transit of the 3.9\,$R_\star$
-clump and the occultation of the lower-velocity clump.
-Spectroscopic transits may therefore not always be associated
-with photometric transits.
+Figure~\ref{fig:spec}d shows a final exercise to quantify the behavior
+of the line core, by summing the H$\alpha$ flux at $|\Delta v / v_{\rm
+eq}|<1$.  This panel shows that changes in the line core flux ($f_{\rm
+H\alpha\ core}$) correlate with the broadband variability throughout
+most of the light curve, except near $\phi$$\approx$0.5, corresponding
+to the transit of the 3.9\,$R_\star$ clump and the occultation of the
+lower-velocity clump.  Spectroscopic transits may therefore not always
+be associated with photometric transits.
 
@@
 spectra require plasma with a significant population of hydrogen in
-the $n$=3 excited state, with minimal evidence for
-higher-order excitations.  Most of this H$\alpha$ emission originates
-in ``clumps'' with size comparable to the star; radial ``spokes'' or
-azimuthally extended ``arcs'' for the emitting material are ruled out
-by the $\approx$30\,\kms\ H$\alpha$ velocity dispersion (see
+the $n$=3 excited state, with minimal evidence for higher-order
+excitations.  Most of this H$\alpha$ emission originates in ``clumps''
+with size comparable to the star; radial ``spokes'' or azimuthally
+extended ``arcs'' for the emitting material are ruled out by the
+$\approx$30\,\kms\ H$\alpha$ velocity dispersion (see
 Appendix~\ref{subsec:halpha}).  The H$\alpha$ line luminosity suggests
@@
 In CPVs more generally, individual flux dips last 5-50\% of each
-cycle, and there are often multiple dips per cycle
-\citep{Bouma2024}.  This implies that azimuthally-distributed
-material may be the norm for CPVs; a warped torus may be a more
-accurate picture than a clump.
+cycle, and there are often multiple dips per cycle \citep{Bouma2024}.
+This implies that azimuthally-distributed material may be the norm for
+CPVs; a warped torus may be a more accurate picture than a clump.
 
 \citet{Townsend2005} outlined the physics of how rapidly-rotating
-stars with strong magnetic fields can support plasma tori
-\citep[see
+stars with strong magnetic fields can support plasma tori \citep[see
 also][]{Nakajima1985,Ferreira2000,Petit2013,Daley-Yates2024}.  When
@@
 Keplerian corotation radii $R_{\rm c}$, the effective potential
-  (gravitational plus centrifugal) experienced by plasma along
-any given field line has a local minimum outside $R_{\rm c}$, which
-enables charged material to accumulate in a torus.  Warps can occur
-when there is misalignment between the spin and magnetic axes.  In
-general, the regions in these centrifugally-supported
-magnetospheres with the densest plasma accumulations need
-neither transit nor be opaque in broadband optical light.
+(gravitational plus centrifugal) experienced by plasma along any given
+field line has a local minimum outside $R_{\rm c}$, which enables
+charged material to accumulate in a torus.  Warps can occur when there
+is misalignment between the spin and magnetic axes.  In general, the
+regions in these centrifugally-supported magnetospheres with the
+densest plasma accumulations need neither transit nor be opaque in
+broadband optical light.
 
@@
 online\footnote{\url{http://user.astro.wisc.edu/\~townsend/static.php?ref=rrm-movies\#Download\_Bundles}
-last accessed 28 May 2025.}; for a $\omega/\omega_{\rm
-c}$$\approx$0.5 edge-on system like TIC\,141146667, the photometric
-eclipses have the correct shape, and the H$\alpha$ emission similarly
-exhibits double-peaked behavior.  The plasma clumps in this model are
+last accessed 28 May 2025.}; for a $\omega/\omega_{\rm c}$$\approx$0.5
+edge-on system like TIC\,141146667, the photometric eclipses have the
+correct shape, and the H$\alpha$ emission similarly exhibits
+double-peaked behavior.  The plasma clumps in this model are
 180$^\circ$ apart because the deepest local minima in the effective
@@
 cycle, indicating an azimuthally extended distribution of material.
-However, two challenges remain. First, the model predicts {\it
-two} W-shaped eclipses per cycle.  Second, it predicts that the
-antipodal clumps should lie at equal distances from the star.
-Different clump opacities or non-dipolar magnetic fields might resolve
-these discrepancies.  Overall, the evidence suggests a warped torus is
-a good first approximation, but one that will need refinement in
-future work.
+However, two challenges remain. First, the model predicts {\it two}
+W-shaped eclipses per cycle.  Second, it predicts that the antipodal
+clumps should lie at equal distances from the star.  Different clump
+opacities or non-dipolar magnetic fields might resolve these
+discrepancies.  Overall, the evidence suggests a warped torus is a
+good first approximation, but one that will need refinement in future
+work.
 
@@
 result is simple light curves that resemble eclipsing binaries, and
-time-dynamic H$\alpha$ spectra similar to Figure~\ref{fig:spec}. 
-The few known exceptions---HD~37776, HD~64740, and HD~176582---have complex
-light curves resembling CPVs \citep{Mikulasek2020,Bouma2024} and
-spectropolarimetric measurements that may suggest non-dipolar field
-contributions \citep{Kochukhov2011,Shultz2018}.  
-The photometric complexity of CPVs may therefore be related to
-magnetic fields with highly multipolar contributions.  While this
-suggestion is consistent with the wide range of axisymmetric and
-non-axisymmetric topologies seen in mid- and late-M dwarfs
+time-dynamic H$\alpha$ spectra similar to Figure~\ref{fig:spec}.  The
+few known exceptions---HD~37776, HD~64740, and HD~176582---have
+complex light curves resembling CPVs \citep{Mikulasek2020,Bouma2024}
+and spectropolarimetric measurements that may suggest non-dipolar
+field contributions \citep{Kochukhov2011,Shultz2018}.  The photometric
+complexity of CPVs may therefore be related to magnetic fields with
+highly multipolar contributions.  While this suggestion is consistent
+with the wide range of axisymmetric and non-axisymmetric topologies
+seen in mid- and late-M dwarfs
 (e.g.~\citealt{Donati2006,Kochukhov2017,Shulyak2019,Bellotti2024}),
@@
 magnetic field, and exploring the implied space weather experienced by
-the close-in rocky exoplanets that, statistically \citep{Dressing2015},
-are likely to be present in many CPV systems.
+the close-in rocky exoplanets that, statistically
+\citep{Dressing2015}, are likely to be present in many CPV systems.
 
@@
 with dust \citep{Tanimoto2020,Gunther2022,Koen2023}, electron
-scattering in a plasma transiting over a spotted star might
-also produce chromatic features \citep{Rackham2018}.  This
-degeneracy is alleviated in the infrared, where the composition and
-size distribution of any dust that is present could be determined by
+scattering in a plasma transiting over a spotted star might also
+produce chromatic features \citep{Rackham2018}.  This degeneracy is
+alleviated in the infrared, where the composition and size
+distribution of any dust that is present could be determined by
 measuring the extinction curve for a sample of CPVs from 1-20\,$\mu$m.
@@
 
-Future models could take a range of steps to clarify the origin
-of CPVs.  A first step for magnetohydrodynamic models that can
-currently explain the H$\alpha$ features \citep[e.g.][]{Waugh2022}
-would be to incorporate an opacity source that can reproduce the
-photometric dips.  This effort will also require
-exploring what stellar magnetic field topologies reproduce the
-observed light curve shapes.  While previous
+Future models could take a range of steps to clarify the origin of
+CPVs.  A first step for magnetohydrodynamic models that can currently
+explain the H$\alpha$ features \citep[e.g.][]{Waugh2022} would be to
+incorporate an opacity source that can reproduce the photometric dips.
+This effort will also require exploring what stellar magnetic field
+topologies reproduce the observed light curve shapes.  While previous
 models in the rigid-field approximation have explored both dipolar
@@
 measurements, unlike benchmark systems such as AB Dor and V374~Peg
-\citep{Jardine2002,Vidotto2011}. This might be alleviated by
-future spectropolarimetry, or by radio observations
-sensitive to the magnetic field structure around the star
-\citep[][]{Callingham2021,Kaur2024}.  Finally, the question of what
-microphysical process yields the opaque material also merits future
-theoretical attention. While recent advances can produce the
-catastrophic cooling that leads to dense, cool clumps embedded in a
-hot corona \citep{Daley-Yates2023,Daley-Yates2024}, a self-consistent
-treatment of radiation propagating through such clumps has yet to be
-performed. Whether dust grains can form in these plasma clumps
-similarly deserves attention.
+\citep{Jardine2002,Vidotto2011}. This might be alleviated by future
+spectropolarimetry, or by radio observations sensitive to the magnetic
+field structure around the star \citep[][]{Callingham2021,Kaur2024}.
+Finally, the question of what microphysical process yields the opaque
+material also merits future theoretical attention. While recent
+advances can produce the catastrophic cooling that leads to dense,
+cool clumps embedded in a hot corona
+\citep{Daley-Yates2023,Daley-Yates2024}, a self-consistent treatment
+of radiation propagating through such clumps has yet to be performed.
+Whether dust grains can form in these plasma clumps similarly deserves
+attention.
 
@@
   conversations that significantly informed this work; J.~Spake,
-  J.~Winn, J.-F~Donati, R.~Townsend, and O.~Kochukhov for feedback on the
-  manuscript; and A.~Howard and H.~Isaacson for their assistance
+  J.~Winn, J.-F~Donati, R.~Townsend, and O.~Kochukhov for feedback on
+  the manuscript; and A.~Howard and H.~Isaacson for their assistance
   reducing the HIRES spectra.
@@
   Heising-Simons 51~Pegasi~b Fellowship.
-  MMJ acknowledges support from STFC consolidated grant
-  number ST/R000824/1.
-  %
-
-  The analyses in this article used data from TESS \citep{TESS2min}.  The
-  2-minute cadence observations from Sectors 41 \& 48 were from TESS
-  DDT039 (PI: M.~Kunimoto) and the observations from Sector 75 were
-  from TESS G06030 (PI: L.~Bouma).
-  Funding for the TESS mission is provided by NASA’s Science Mission
+  MMJ acknowledges support from STFC consolidated grant number
+  ST/R000824/1.
+  %
+
+  The analyses in this article used data from TESS \citep{TESS2min}.
+  The 2-minute cadence observations from Sectors 41 \& 48 were from
+  TESS DDT039 (PI: M.~Kunimoto) and the observations from Sector 75
+  were from TESS G06030 (PI: L.~Bouma).
+  Funding for the TESS mission is provided by NASA's Science Mission
   directorate.
@@
   people, and we thank the TESS team for their efforts to make the
-  mission a continued success.
-  The HIRES data were obtained at the Keck Observatory, which exists
-  through a similar scale of community effort.
+  mission a continued success.  The HIRES data were obtained at the
+  Keck Observatory, which exists through a similar scale of community
+  effort.
   We recognize the importance that the summit of Maunakea has always
@@
 {\it Radial Velocity}---We measured the radial velocities of
-TIC\,141146667 (Gaia DR3 860453786736413568) from our HIRES
-spectra using a custom pipeline.  Our method was based on
-template-matching against synthetic PHOENIX spectra
-\citep{Husser2013}, and was calibrated against the
-standard stars described by \citet{Chubak2012}.  We used velocity
-standards spanning G2-M4, irrespective of rotation rate.  We included
-velocity corrections due to Earth's motion around the solar system
-barycenter and due to Earth's daily rotation about its axis,
-calculated using \texttt{barycorrpy} \citep{Kanodia2018}.  Our
-analysis code reproduced the systemic velocities of known velocity
+TIC\,141146667 (Gaia DR3 860453786736413568) from our HIRES spectra
+using a custom pipeline.  Our method was based on template-matching
+against synthetic PHOENIX spectra \citep{Husser2013}, and was
+calibrated against the standard stars described by \citet{Chubak2012}.
+We used velocity standards spanning G2-M4, irrespective of rotation
+rate.  We included velocity corrections due to Earth's motion around
+the solar system barycenter and due to Earth's daily rotation about
+its axis, calculated using \texttt{barycorrpy} \citep{Kanodia2018}.
+Our analysis code reproduced the systemic velocities of known velocity
 standards \citep{Chubak2012} with an RMS of 0.66\,\kms.
@@
 companions at wider separations, the Gaia DR3 renormalized unit weight
-error (RUWE) is 1.23, within the usual
-range for apparently single sources.  There are no resolved companions
-in the Gaia DR3 point source catalog.  Finally, we checked the TESS
-light curve for evidence of secondary photometric periods by
-subtracting the mean CPV signal over each sector and performing a
-phase-dispersion minimization analysis
-\citep{Stellingwerf1978,2021zndo...1011188B}.  There were no secondary
-periods in the TESS data.  Previous work \citep{Bouma2024} has shown
-that $\approx$30\% of CPVs show evidence for binarity from RUWE, and
-$\approx$40\% of CPVs show evidence for binarity based on the presence
-of secondary photometric periods.  This agrees with analyses showing
-that multi-periodic low-mass stars are usually unresolved binaries
-\citep{Tokovinin2018}.  Overall, the CPV binary fraction seems
-consistent with that of field M dwarfs \citep{Winters2019}, pointing
-to a weak or non-existent connection between the CPV phenomenon and
-(wide) binarity.  For TIC\,141146667 specifically, we find no
-evidence for stellar multiplicity.
+error (RUWE) is 1.23, within the usual range for apparently single
+sources.  There are no resolved companions in the Gaia DR3 point
+source catalog.  Finally, we checked the TESS light curve for evidence
+of secondary photometric periods by subtracting the mean CPV signal
+over each sector and performing a phase-dispersion minimization
+analysis \citep{Stellingwerf1978,2021zndo...1011188B}.  There were no
+secondary periods in the TESS data.  Previous work \citep{Bouma2024}
+has shown that $\approx$30\% of CPVs show evidence for binarity from
+RUWE, and $\approx$40\% of CPVs show evidence for binarity based on
+the presence of secondary photometric periods.  This agrees with
+analyses showing that multi-periodic low-mass stars are usually
+unresolved binaries \citep{Tokovinin2018}.  Overall, the CPV binary
+fraction seems consistent with that of field M dwarfs
+\citep{Winters2019}, pointing to a weak or non-existent connection
+between the CPV phenomenon and (wide) binarity.  For TIC\,141146667
+specifically, we find no evidence for stellar multiplicity.
 
@@
     BT-Settl stellar atmosphere model \citep{Allard2012} and the
-    associated photometric predictions (empty purple
-    diamonds).  This plot was made from an adaptation of
-    \texttt{astroARIADNE} \citep{Vines2022}.  The photometry extends
-    from the Gaia DR3 blue passband to WISE W3; the W4 passband (22
-    $\mu$m) did not yield a confident detection.  This fit yields the
-    star's temperature and size.  The lack of excess infrared flux
-    relative to the photospheric model sets an upper limit on emission
-    from circumstellar dust.
+    associated photometric predictions (empty purple diamonds).  This
+    plot was made from an adaptation of \texttt{astroARIADNE}
+    \citep{Vines2022}.  The photometry extends from the Gaia DR3 blue
+    passband to WISE W3; the W4 passband (22 $\mu$m) did not yield a
+    confident detection.  This fit yields the star's temperature and
+    size.  The lack of excess infrared flux relative to the
+    photospheric model sets an upper limit on emission from
+    circumstellar dust.
     }
@@
 magnitudes from Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$
-with the BT-Settl stellar atmosphere models \citep{Allard2012}.
-Free parameters included  the stellar effective temperature,
-radius, reddening, surface gravity, and metallicity.  The resulting
-best-fit SED is shown in Figure~\ref{fig:sed}.  This method has the
-most constraining power for the star's effective temperature (2972
-$\pm$ 40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$).  We measured the
+with the BT-Settl stellar atmosphere models \citep{Allard2012}.  Free
+parameters included  the stellar effective temperature, radius,
+reddening, surface gravity, and metallicity.  The resulting best-fit
+SED is shown in Figure~\ref{fig:sed}.  This method has the most
+constraining power for the star's effective temperature (2972 $\pm$
+40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$).  We measured the
 star's spectral type to be M5.5Ve by visually comparing the HIRES
@@
   TIC\,141146667, USco (8\,Myr), IC\,2602 (40\,Myr), the Pleiades
-  (112\,Myr) and stars within 100\,pc. 
-  The location of TIC\,141146667 in this diagram suggests an age of
-  30-150\,Myr. 
+  (112\,Myr) and stars within 100\,pc.  The location of TIC\,141146667
+  in this diagram suggests an age of 30-150\,Myr. 
   {\bf b,} A dearth of photospheric lithium for TIC\,141146667 (yellow
@@
 sub-associations from \citet{Ratzenbock2023}, and the IC~2602 and
-Pleiades members from \citet{Hunt2024}.  We assumed an average $V$-band
-extinction $A_{\rm V}$=$\{0.12, 0.11, 0.10\}\,{\rm mag}$ for USco
-\citep{Pecaut2016}, IC~2602 \citep{Hunt2024}, and the Pleiades
+Pleiades members from \citet{Hunt2024}.  We assumed an average
+$V$-band extinction $A_{\rm V}$=$\{0.12, 0.11, 0.10\}\,{\rm mag}$ for
+USco \citep{Pecaut2016}, IC~2602 \citep{Hunt2024}, and the Pleiades
 \citep{Hunt2024} respectively, and ages of 8\,Myr
@@
 stars in the Pleiades of the same color have a similar absolute
-magnitude as TIC\,141146667.  Previous work by \citet{Stauffer2021} has
-noted that in the Gaia passbands, CPVs tend to be photometrically
-redder and more luminous than single stars in any given
-cluster; they also found suggestive evidence for either
-hotspots or emission from dust based on analysis
-of Gaia and WISE photometry.  The implication is that isochronal age
-dating of individual field CPVs suffers significant systematic
-uncertainty due to factors including dark and bright spots, magnetic
-inflation, dust emission, and photometric binarity. Rather than
-adopting a particular model isochrone framework, we instead visually
-take the star's location in the color--absolute magnitude diagram
-to suggest age bounds $t_{\rm CAMD}$$\sim$30-150\,Myr.
+magnitude as TIC\,141146667.  Previous work by \citet{Stauffer2021}
+has noted that in the Gaia passbands, CPVs tend to be photometrically
+redder and more luminous than single stars in any given cluster; they
+also found suggestive evidence for either hotspots or emission from
+dust based on analysis of Gaia and WISE photometry.  The implication
+is that isochronal age dating of individual field CPVs suffers
+significant systematic uncertainty due to factors including dark and
+bright spots, magnetic inflation, dust emission, and photometric
+binarity. Rather than adopting a particular model isochrone framework,
+we instead visually take the star's location in the color--absolute
+magnitude diagram to suggest age bounds $t_{\rm
+CAMD}$$\sim$30-150\,Myr.
 
@@
 \citep[e.g.][]{Hayashi1963,Bildsten1997}.  \citet{Wood2023} provided a
-recent overview; the brief summary is that sufficiently cool and
-young M dwarfs show the 6707.8\,\AA\ doublet in absorption,
-$\gtrsim$10\% below their continua.  However, unlike for Sun-like
-stars, the continuum for M dwarfs is challenging to define due to
-their molecular absorption.  We therefore attempted a lithium
-measurement by constructing a wavelength-binned and Doppler-corrected
-TIC\,141146667 spectrum, and assigned its uncertainties based on the
-measured scatter across the five hour dataset.  We then compared this
-average spectrum against the nearest matching M6 template from
-\citet{Bochanski2007}.  The data show a small depression near the
-expected lithium wavelength, potentially consistent with the $\Delta
-\lambda$$\approx$3\,\AA\ line broadening.  This feature 
-yields ${\rm EW}_{\rm Li}$=71$^{+18}_{-13}$\,m\AA, where the
-statistical uncertainties are evaluated using a bootstrap resampling
-technique from the statistical uncertainties in the HIRES spectrum.
-However, the systematic uncertainty associated with the continuum
-normalization is likely comparable to the amplitude of the feature;
-we therefore treat this measurement as a $2\sigma$ upper
-limit: ${\rm EW}_{\rm Li}$$<$107\,m\AA.
+recent overview; the brief summary is that sufficiently cool and young
+M dwarfs show the 6707.8\,\AA\ doublet in absorption, $\gtrsim$10\%
+below their continua.  However, unlike for Sun-like stars, the
+continuum for M dwarfs is challenging to define due to their molecular
+absorption.  We therefore attempted a lithium measurement by
+constructing a wavelength-binned and Doppler-corrected TIC\,141146667
+spectrum, and assigned its uncertainties based on the measured scatter
+across the five hour dataset.  We then compared this average spectrum
+against the nearest matching M6 template from \citet{Bochanski2007}.
+The data show a small depression near the expected lithium wavelength,
+potentially consistent with the $\Delta \lambda$$\approx$3\,\AA\ line
+broadening.  This feature yields ${\rm EW}_{\rm
+Li}$=71$^{+18}_{-13}$\,m\AA, where the statistical uncertainties are
+evaluated using a bootstrap resampling technique from the statistical
+uncertainties in the HIRES spectrum.  However, the systematic
+uncertainty associated with the continuum normalization is likely
+comparable to the amplitude of the feature; we therefore treat this
+measurement as a $2\sigma$ upper limit: ${\rm EW}_{\rm
+Li}$$<$107\,m\AA.
 
@@
 {\it Age: Summary}---The main indicators for the youth of
-TIC\,141146667 are {\it i)} that it is a complex periodic variable, and
-{\it ii)} that it is 1.5 magnitudes brighter (four times more
+TIC\,141146667 are {\it i)} that it is a complex periodic variable,
+and {\it ii)} that it is 1.5 magnitudes brighter (four times more
 luminous) than main sequence stars of the same color, while showing no
@@
   \includegraphics[width=0.5\textwidth]{f6.pdf}
-  \caption{{\bf Time-variable fit to H$\alpha$ line profiles.}  {\it Left
-  column:} Raw spectrum at each epoch $f_{\lambda}$ minus the
+  \caption{{\bf Time-variable fit to H$\alpha$ line profiles.}  {\it
+  Left column:} Raw spectrum at each epoch $f_{\lambda}$ minus the
   time-averaged spectrum $f_{\langle t \rangle}$ (as in
@@
 the data {\it independently} using scipy's non-linear least squares
-\texttt{curve\_fit} implementation \citep{Virtanen2020}, and scaled the
-resulting parameter covariance matrix by a constant factor to match
-the sample variance of the residuals.
-The middle columns of
-Figure~\ref{fig:halphamodel} show the results; a table of the fitted means,
-amplitudes, and standard deviations for each component is available
-upon request.
+\texttt{curve\_fit} implementation \citep{Virtanen2020}, and scaled
+the resulting parameter covariance matrix by a constant factor to
+match the sample variance of the residuals.  The middle columns of
+Figure~\ref{fig:halphamodel} show the results; a table of the fitted
+means, amplitudes, and standard deviations for each component is
+available upon request.
 
 Caution is required in interpreting this model's results.  At some
-epochs there are no significant spectral features around any component's
-prior.  During such epochs, e.g.~the
-``outer'' clump at $\phi$=1.07, the model fits noise, not signal.  At
-other times, the model underfits.  For instance, the sudden blue rise
-near $\phi$=0.2 is poorly described by a gaussian; the assumed
-functional form is one of convenience.  Finally, the model fits the
-$i=\{ 0, 1 \}$, and $i=2$ components independently.  At $\phi$=0.0 and
-1.0, Figure~\ref{fig:halphamodel} suggests that the emission might
-come from either the inner or outer components.  Physically however,
-at this epoch the inner clump is in transit, and the outer clump is
+epochs there are no significant spectral features around any
+component's prior.  During such epochs, e.g.~the ``outer'' clump at
+$\phi$=1.07, the model fits noise, not signal.  At other times, the
+model underfits.  For instance, the sudden blue rise near $\phi$=0.2
+is poorly described by a gaussian; the assumed functional form is one
+of convenience.  Finally, the model fits the $i=\{ 0, 1 \}$, and $i=2$
+components independently.  At $\phi$=0.0 and 1.0,
+Figure~\ref{fig:halphamodel} suggests that the emission might come
+from either the inner or outer components.  Physically however, at
+this epoch the inner clump is in transit, and the outer clump is
 passing behind the star.  At $\phi$=0.0, the double-peaked emission
@@
 
-Accounting for these caveats, we used the best-fit parameters
-from the multi-gaussian model to quantify the orbital periods and
-velocity semi-amplitudes of the clumps.  Figure~\ref{fig:orbits}a
-shows the results assuming circular orbits; considering the Bayesian
-information criterion, we found no reason to prefer eccentric orbits.
-By visually inspecting Figure~\ref{fig:halphamodel}, we
-excluded epochs where our gaussian profile fitting failed to either
-detect or else adequately represent the circumstellar emission.  We
-then used NumPyro to sample the Gaussian likelihood for a circular
-orbit with the NUTS algorithm \citep{Phan2019}.  We used the
-measurement uncertainties from each estimated mean radial velocity
-value and included an additional jitter term in quadrature.  This
-procedure yielded orbital periods and semi-amplitudes of
+Accounting for these caveats, we used the best-fit parameters from the
+multi-gaussian model to quantify the orbital periods and velocity
+semi-amplitudes of the clumps.  Figure~\ref{fig:orbits}a shows the
+results assuming circular orbits; considering the Bayesian information
+criterion, we found no reason to prefer eccentric orbits.  By visually
+inspecting Figure~\ref{fig:halphamodel}, we excluded epochs where our
+gaussian profile fitting failed to either detect or else adequately
+represent the circumstellar emission.  We then used NumPyro to sample
+the Gaussian likelihood for a circular orbit with the NUTS algorithm
+\citep{Phan2019}.  We used the measurement uncertainties from each
+estimated mean radial velocity value and included an additional jitter
+term in quadrature.  This procedure yielded orbital periods and
+semi-amplitudes of
 $P_0$=$3.92\pm0.03$\,hr, $K_0/v_{\rm eq}$=2.07$\pm$0.04;
@@
 
-{\it Physical dimensions of emitting region}---The H$\alpha$
-velocity widths in Figure~\ref{fig:halphamodel} constrain
-the size of the emitting region via the condition for rigid
-corotation.  Consider a clump in cylindrical coordinates with
-arbitrary radial extent $r$, azimuthal extent $\ell$, and height $z$.
-A range of shapes, including an ``arc'' with $\ell \gg r$, a ``spoke''
-with $r \gg \ell$, and a ``blob'' with $r \approx \ell \approx z$ are
-all a priori possible.  However, at quadrature, the observed velocity
-width of emission is sensitive to the radial extent of the
-circumstellar material.  At mid-transit, the observed velocity width
-is sensitive to the azimuthal extent.  An arc configuration would
-minimize the observed velocity width $\sigma$ at quadrature, and
-maximize it during transit, with $\gtrsim$100\,\kms\ variations in
-between.  Since this is not observed, the arc geometry, and by a similar
-argument the spoke geometry, can be discarded.
+{\it Physical dimensions of emitting region}---The H$\alpha$ velocity
+widths in Figure~\ref{fig:halphamodel} constrain the size of the
+emitting region via the condition for rigid corotation.  Consider a
+clump in cylindrical coordinates with arbitrary radial extent $r$,
+azimuthal extent $\ell$, and height $z$.  A range of shapes, including
+an ``arc'' with $\ell \gg r$, a ``spoke'' with $r \gg \ell$, and a
+``blob'' with $r \approx \ell \approx z$ are all a priori possible.
+However, at quadrature, the observed velocity width of emission is
+sensitive to the radial extent of the circumstellar material.  At
+mid-transit, the observed velocity width is sensitive to the azimuthal
+extent.  An arc configuration would minimize the observed velocity
+width $\sigma$ at quadrature, and maximize it during transit, with
+$\gtrsim$100\,\kms\ variations in between.  Since this is not
+observed, the arc geometry, and by a similar argument the spoke
+geometry, can be discarded.
 
@@
 dimension of these two inner emitting clumps is approximately equal to
-the star's diameter.  At mid-transit, these
-inner clumps have a similar velocity dispersion, although with
-greater uncertainty due to the differences between the $\phi$=0 and
-$\phi$=1 transits (see Figure~\ref{fig:halphamodel}).
-This suggests a 1$\sigma$ emission contour in the azimuthal dimension
-with a length of $\ell$$\approx$0.5\,$R_\star$.
+the star's diameter.  At mid-transit, these inner clumps have a
+similar velocity dispersion, although with greater uncertainty due to
+the differences between the $\phi$=0 and $\phi$=1 transits (see
+Figure~\ref{fig:halphamodel}).  This suggests a 1$\sigma$ emission
+contour in the azimuthal dimension with a length of
+$\ell$$\approx$0.5\,$R_\star$.
 
@@
 the system is consistent with being viewed edge-on.  However, one
-possible constraint follows by assuming that the TESS transit depth scales
-with the projected H$\alpha$ emission area $\ell z$.  
-More specifically, one can evaluate an ``effective area'' blocked by a
+possible constraint follows by assuming that the TESS transit depth
+scales with the projected H$\alpha$ emission area $\ell z$.  More
+specifically, one can evaluate an ``effective area'' blocked by a
 two-dimensional gaussian blob passing over a star by integrating the
@@
 which would need to be in turn multiplied by an unknown opacity factor
-to produce the observed transit depth ($\delta$$\approx$5\%).  
-There is a degeneracy between $z$ and this opacity
-factor; larger vertical heights are allowed for lower optical depths
-in absorption, and vice-versa.  This constraint also implicitly
-assumes that the optically thick material is well-mixed with the
-hydrogen, which may not be accurate.
+to produce the observed transit depth ($\delta$$\approx$5\%).  There
+is a degeneracy between $z$ and this opacity factor; larger vertical
+heights are allowed for lower optical depths in absorption, and
+vice-versa.  This constraint also implicitly assumes that the
+optically thick material is well-mixed with the hydrogen, which may
+not be accurate.
 
@@
 recombination.  We neglect scattering because Figure~\ref{fig:spec}
-shows the
-circumstellar H$\alpha$ emission varying by a factor of $\approx$5
-while the chromospheric line core is stable.  The volume emissivity
-under case B recombination can be written \begin{equation}
-  j_{\rm H\alpha} = n_{\rm e} n_{\rm p} \alpha^{\rm eff}_{\rm H\alpha} h \nu_{\rm H\alpha},
-\end{equation} where $n_{\rm e}$ and $n_{\rm p}$ are the electron and
-proton densities, and $\alpha^{\rm eff}_{\rm H\alpha}$ is the
-effective recombination coefficient, defined to include all
-recombination routes that produce an H$\alpha$ photon.  For hydrogen
-with temperatures between 1,000-10,000\,K, $\alpha^{\rm eff}_{\rm
-H\alpha}$ is typically $10^{-12}$ to
+shows the circumstellar H$\alpha$ emission varying by a factor of
+$\approx$5 while the chromospheric line core is stable.  The volume
+emissivity under case B recombination can be written \begin{equation}
+  j_{\rm H\alpha} = n_{\rm e} n_{\rm p} \alpha^{\rm eff}_{\rm H\alpha}
+h \nu_{\rm H\alpha}, \end{equation} where $n_{\rm e}$ and $n_{\rm p}$
+are the electron and proton densities, and $\alpha^{\rm eff}_{\rm
+H\alpha}$ is the effective recombination coefficient, defined to
+include all recombination routes that produce an H$\alpha$ photon.
+For hydrogen with temperatures between 1,000-10,000\,K, $\alpha^{\rm
+eff}_{\rm H\alpha}$ is typically $10^{-12}$ to
 $10^{-13}$\,cm$^3$\,s$^{-1}$ \citep{Hummer1987,Draine2011}.
-Neglecting atoms other than hydrogen, we can assume an
-ionization fraction $x$, such that $n_{\rm e} = n_{\rm p} = x n_{\rm
-H}$, for $n_{\rm H}$ the hydrogen number density.  Let $L_{\rm
-H\alpha} = j_{\rm H\alpha} V$, for $V$ the volume of the emitting
-hydrogen.  The luminosity of circumstellar hydrogen emission, $L_{\rm
-H\alpha}$, is an observable: our SED fitting routine yields
+Neglecting atoms other than hydrogen, we can assume an ionization
+fraction $x$, such that $n_{\rm e} = n_{\rm p} = x n_{\rm H}$, for
+$n_{\rm H}$ the hydrogen number density.  Let $L_{\rm H\alpha} =
+j_{\rm H\alpha} V$, for $V$ the volume of the emitting hydrogen.  The
+luminosity of circumstellar hydrogen emission, $L_{\rm H\alpha}$, is
+an observable: our SED fitting routine yields
 $L_\star$$\approx$0.012\,$L_\odot$, which implies that the stellar
@@
 gas}\approx 2\times10^{17}$\,g, which is similar to masses derived for
-plasma clumps around other cool stars \citep{VillarrealDAngelo2019}.  We emphasize that
-Equation~\ref{eq:numdensity} in intended to provide only an order of
-magnitude estimate for the number density implied by the observed
-H$\alpha$ emission.  In detail, the effective recombination rate and
-the ionization fraction each vary with density and temperature; a more
-thorough estimate would iteratively solve the equations of detailed
-balance and radiative transfer (e.g.~Figure~8 of \citealt{CollierCameron1989}),
-and potentially also consider departures from local thermodynamic equilibrium.
+plasma clumps around other cool stars \citep{VillarrealDAngelo2019}.
+We emphasize that Equation~\ref{eq:numdensity} in intended to provide
+only an order of magnitude estimate for the number density implied by
+the observed H$\alpha$ emission.  In detail, the effective
+recombination rate and the ionization fraction each vary with density
+and temperature; a more thorough estimate would iteratively solve the
+equations of detailed balance and radiative transfer (e.g.~Figure~8 of
+\citealt{CollierCameron1989}), and potentially also consider
+departures from local thermodynamic equilibrium.
 
@@
 
-Regarding the upper limit, Figure~\ref{fig:sed} shows
-the SED.  While AllWISE \citep{Cutri2014} yielded a confident W3
-detection (9.8$\sigma$) consistent with the photospheric extrapolation
-from bluer bandpasses, the W4 extraction yielded only a marginal
-indication (1.7$\sigma$) of detectable flux.  Similar to other CPVs
-\citep{Stauffer2017,Bouma2024}, the photometric uncertainties from WISE
-W1 and W2 allow at most a $\lesssim$2\% excess at 3-5\,$\mu$m relative
-to the stellar photosphere, and a $\lesssim$5\% excess at 10\,$\mu$m
-(W3).  To estimate the implied mass bound, we assume a dust
+Regarding the upper limit, Figure~\ref{fig:sed} shows the SED.  While
+AllWISE \citep{Cutri2014} yielded a confident W3 detection
+(9.8$\sigma$) consistent with the photospheric extrapolation from
+bluer bandpasses, the W4 extraction yielded only a marginal indication
+(1.7$\sigma$) of detectable flux.  Similar to other CPVs
+\citep{Stauffer2017,Bouma2024}, the photometric uncertainties from
+WISE W1 and W2 allow at most a $\lesssim$2\% excess at 3-5\,$\mu$m
+relative to the stellar photosphere, and a $\lesssim$5\% excess at
+10\,$\mu$m (W3).  To estimate the implied mass bound, we assume a dust
 temperature $T_{\rm d}$=1500\,K, typical for dust near the star (see
-\citealt{Zhan2019} for discussion regarding dust sublimation).  We then
-treat emission from the dust and star as Planck functions, and require
-$L_{\rm d} < f L_\star$, where the factor $f$ is set by the
+\citealt{Zhan2019} for discussion regarding dust sublimation).  We
+then treat emission from the dust and star as Planck functions, and
+require $L_{\rm d} < f L_\star$, where the factor $f$ is set by the
 photometric precision of WISE and $L_{\rm d}$ is the bolometric dust
@@
 range of $10^{15}$-$10^{17}$\,g.  Given $M_{\rm
-gas}$$\approx$2$\times$10$^{17}$\,g from Appendix~\ref{subsec:gas}, the
-allowed dust masses imply $M_{\rm gas}/M_{\rm dust}$ ranges of 1-100.
-More careful measurements of this ratio---in particular by inferring
-the dust mass through high precision infrared
+gas}$$\approx$2$\times$10$^{17}$\,g from Appendix~\ref{subsec:gas},
+the allowed dust masses imply $M_{\rm gas}/M_{\rm dust}$ ranges of
+1-100.  More careful measurements of this ratio---in particular by
+inferring the dust mass through high precision infrared
 spectrophotometry---could provide a path for distinguishing the
